### 2017-03-31 egpaper_for_review.tex
Initial commit.

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\usepackage{color}

\newcommand{\matt}[1]{ \color{red} Matt: #1  \color{black}}
\newcommand{\aneesh}[1]{ \color{blue} Aneesh: #1  \color{black}}
\newcommand{\burak}[1]{ \color{green} Burak: #1  \color{black}}
\newcommand{\emmett}[1]{\color{violet} Emmett: #1  \color{black}}
\begin{document}

%%%%%%%%% TITLE
\title{High Speed Object Tracking using Multiple Kernelized Correlation Filters}

\author{Burak Uzkent\\
Rochester Institute of Technology\\
{\tt\small bxu2522@@rit.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
YoungWoo Seo\\
Affiliation\\
{\tt\small yseo@autelrobotics.edu}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
The tracking-by-detection methods have recently emerged as robust, powerful, and highly discriminative trackers replacing the preceding generative trackers that focused on only target modeling. Some of the recent tracking-by-detection algorithms are Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple Instance Learning \cite{babenko2009visual}, Correlation Filter based trackers \cite{bolme2010visual,henriques2015high}, and Struck \cite{hare2012efficient}. These tracking-by-detection methods train an object-specific classifier on the fly with the focus of discriminating the target from the background. Learning an object-specific classifier in an online manner can better handle challenging scenarios with the cost of increased complexity. In order to train a classifier, one need positive and negative samples. Randomly collecting negative samples from the background area can be one straightforward way of building training data to train the classifier. However, there can be two issues in this framework. First, the randomly collected samples can have large correlation resulting in a weak classifier. Also, such framework is not feasible for real-time tracking as the number of samples gradually increases. Most of the tracking-by-detection algorithms focus on efficient incremental update of a classifier together with more useful background sampling.

Frequency domain correlation filter based trackers in the tracking-by-detection paradigm has recently seen growing popularity due to its superior computation and robustness to geometric and photometric variations. The first correlation filter tracker proposed by \cite{bolme2010visual} focused on learning and detection in the frequency domain. The idea was to minimize the sum of squared error in the frequency domain. Hence, the convolution in the original domain is avoided, instead, element-wise multiplication is needed in the frequency domain. This way, it achieved promising performance at 700 Hz. On the other hand, the MOSSE tracker failed in cases with rapidly changing background as it learns the filter using a single template and accommodates single channel features. Later on, the MOSSE tracker was improved by using the circularly shifted background patches in an efficient way by utilizing the theorem that Discrete Fourier Transform of a circulant matrix gives us diagonalized circulant matrix \cite{henriques2012exploiting,henriques2015high}. In the same work, the authors integrated kernelization concept into the detection and learning steps to improve tracking accuracy. \cite{galoogahi2013multi,henriques2015high} extended the correlation filter trackers with single channel features to multi-channel features. They employed the color and shape features in a simple framework by summing the correlation of the test and learned feature channels elements. There a few major drawbacks of the correlation filter trackers although they outperformed the other discriminative trackers with superior computation. First, due to the nature of correlation filters it is limited to a region of interest which is typically 2-3 times larger than the target. Considering a larger ROI not only increases the computational burden but also leads to further spatial information loss with the fixed template size. For this reason, its performance degrades in fast motion cases as the ROI may not contain the target. Second, the correlation filter lacks scale adaptation ability since it only estimates the translation of the target. Later studies focused on improving the latter issue by proposing scale candidates where each scale is assigned a confidence by performing detection on the shrinked or enlarged the ROI \cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another group of studies employ the part-based correlation filter trackers to better adapt to the scale changes \cite{liu2015real,akin2016deformable}. The sensitivity to fast motion is generally handled in the long-term target tracking framework where track reinilization module is triggered when the target is lost \cite{ma2015long,de2015board,li2016monocular}.

CONTRIBUTION

%--------------
%\section*{Acknowledgements}
%put stuff here for the accepted , but not the ICCV version

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-03-31 draft.tex
Added .gitignore; revised the draft to outline the content

--- 2017-03-31 egpaper_for_review.tex
@@
 \section{Introduction}
-The tracking-by-detection methods have recently emerged as robust, powerful, and highly discriminative trackers replacing the preceding generative trackers that focused on only target modeling.
-Some of the recent tracking-by-detection algorithms are Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple Instance Learning \cite{babenko2009visual}, Correlation Filter based trackers \cite{bolme2010visual,henriques2015high}, and Struck \cite{hare2012efficient}.
-These tracking-by-detection methods train an object-specific classifier on the fly with the focus of discriminating the target from the background.
-Learning an object-specific classifier in an online manner can better handle challenging scenarios with the cost of increased complexity.
-In order to train a classifier, one need positive and negative samples.
-Randomly collecting negative samples from the background area can be one straightforward way of building training data to train the classifier.
-However, there can be two issues in this framework.
-First, the randomly collected samples can have large correlation resulting in a weak classifier.
-Also, such framework is not feasible for real-time tracking as the number of samples gradually increases.
-Most of the tracking-by-detection algorithms focus on efficient incremental update of a classifier together with more useful background sampling.
 
-Frequency domain correlation filter based trackers in the tracking-by-detection paradigm has recently seen growing popularity due to its superior computation and robustness to geometric and photometric variations.
-The first correlation filter tracker proposed by \cite{bolme2010visual} focused on learning and detection in the frequency domain.
-The idea was to minimize the sum of squared error in the frequency domain.
-Hence, the convolution in the original domain is avoided, instead, element-wise multiplication is needed in the frequency domain.
-This way, it achieved promising performance at 700 Hz.
-On the other hand, the MOSSE tracker failed in cases with rapidly changing background as it learns the filter using a single template and accommodates single channel features.
-Later on, the MOSSE tracker was improved by using the circularly shifted background patches in an efficient way by utilizing the theorem that Discrete Fourier Transform of a circulant matrix gives us diagonalized circulant matrix \cite{henriques2012exploiting,henriques2015high}.
-In the same work, the authors integrated kernelization concept into the detection and learning steps to improve tracking accuracy.
-\cite{galoogahi2013multi,henriques2015high} extended the correlation filter trackers with single channel features to multi-channel features.
-They employed the color and shape features in a simple framework by summing the correlation of the test and learned feature channels elements.
-There a few major drawbacks of the correlation filter trackers although they outperformed the other discriminative trackers with superior computation.
-First, due to the nature of correlation filters it is limited to a region of interest which is typically 2-3 times larger than the target.
-Considering a larger ROI not only increases the computational burden but also leads to further spatial information loss with the fixed template size.
-For this reason, its performance degrades in fast motion cases as the ROI may not contain the target.
-Second, the correlation filter lacks scale adaptation ability since it only estimates the translation of the target.
-Later studies focused on improving the latter issue by proposing scale candidates where each scale is assigned a confidence by performing detection on the shrinked or enlarged the ROI \cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}.
-Another group of studies employ the part-based correlation filter trackers to better adapt to the scale changes \cite{liu2015real,akin2016deformable}.
-The sensitivity to fast motion is generally handled in the long-term target tracking framework where track reinilization module is triggered when the target is lost \cite{ma2015long,de2015board,li2016monocular}.
+A practical solution to target-following mode
+
+\begin{itemize}
+\item Introduction: Should talk about, at least, motivation of this
+  work, brief review of the literature, and contribution
+\item Method: Detail the method w.r.t. a diagram of system
+  architecture or pseudo code
+\begin{itemize}
+\item Kernelized Correlation Filter
+\item A variant of KCF: Multiple KCF w/ PF
+\item Re-detection
+\item Estimation of geometry between a target and a drone
+\end{itemize}
+\item Experiment: Detail the data, and experimental setup; results and findings
+\item Conclusion
+\end{itemize}
+
+The tracking-by-detection methods have recently emerged as robust,
+powerful, and highly discriminative trackers replacing the preceding
+generative trackers that focused on only target modeling. Some of the
+recent tracking-by-detection algorithms are
+Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
+Instance Learning \cite{babenko2009visual}, Correlation Filter based
+trackers \cite{bolme2010visual,henriques2015high}, and Struck
+\cite{hare2012efficient}. These tracking-by-detection methods train an
+object-specific classifier on the fly with the focus of discriminating
+the target from the background. Learning an object-specific classifier
+in an online manner can better handle challenging scenarios with the
+cost of increased complexity. In order to train a classifier, one need
+positive and negative samples. Randomly collecting negative samples
+from the background area can be one straightforward way of building
+training data to train the classifier. However, there can be two
+issues in this framework. First, the randomly collected samples can
+have large correlation resulting in a weak classifier. Also, such
+framework is not feasible for real-time tracking as the number of
+samples gradually increases. Most of the tracking-by-detection
+algorithms focus on efficient incremental update of a classifier
+together with more useful background sampling.
+
+Frequency domain correlation filter based trackers in the
+tracking-by-detection paradigm has recently seen growing popularity
+due to its superior computation and robustness to geometric and
+photometric variations. The first correlation filter tracker proposed
+by \cite{bolme2010visual} focused on learning and detection in the
+frequency domain. The idea was to minimize the sum of squared error in
+the frequency domain. Hence, the convolution in the original domain is
+avoided, instead, element-wise multiplication is needed in the
+frequency domain. This way, it achieved promising performance at 700
+Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
+changing background as it learns the filter using a single template
+and accommodates single channel features. Later on, the MOSSE tracker
+was improved by using the circularly shifted background patches in an
+efficient way by utilizing the theorem that Discrete Fourier Transform
+of a circulant matrix gives us diagonalized circulant matrix
+\cite{henriques2012exploiting,henriques2015high}. In the same work,
+the authors integrated kernelization concept into the detection and
+learning steps to improve tracking
+accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
+correlation filter trackers with single channel features to
+multi-channel features. They employed the color and shape features in
+a simple framework by summing the correlation of the test and learned
+feature channels elements. There a few major drawbacks of the
+correlation filter trackers although they outperformed the other
+discriminative trackers with superior computation. First, due to the
+nature of correlation filters it is limited to a region of interest
+which is typically 2-3 times larger than the target. Considering a
+larger ROI not only increases the computational burden but also leads
+to further spatial information loss with the fixed template size. For
+this reason, its performance degrades in fast motion cases as the ROI
+may not contain the target. Second, the correlation filter lacks scale
+adaptation ability since it only estimates the translation of the
+target. Later studies focused on improving the latter issue by
+proposing scale candidates where each scale is assigned a confidence
+by performing detection on the shrinked or enlarged the ROI
+\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
+group of studies employ the part-based correlation filter trackers to
+better adapt to the scale changes
+\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
+is generally handled in the long-term target tracking framework where
+track reinilization module is triggered when the target is lost
+\cite{ma2015long,de2015board,li2016monocular}.
 

### 2017-04-02 draft.tex
Contributions Part Added into the Introduction

@@
 
-CONTRIBUTION
+The contributions of this study are as follows.
+\begin{itemize}
+\item We build a highly efficient (300 fps) scale adaptive multiple kernelized correlation filter based tracker that outperforms the original KCF implementation with fixed scale framework both in terms of accuracy and performance.
+The studies following the KCF improved the fixed scale framework by running detection on a number of candidate ROIs to figure out the new scale of the object after estimating the translation of the object.
+This approach adds additional complexity to the original KCF implementation and drags down the run-time performance from $300$ fps to less than $100$ fps.
+\item We integrate the Particle Filter into the Multiple KCFs tracking as an additional filter that can avoid the drift due to one of the correlation filters we employ in our framework.
+\item We propose a target re-detection module that can minimize the target loss due to the scale filter that learns the object model using only-object area.
+Also, the target re-detection step is required to handle severe occlusions, pose variations, illumination changes and fast motion.
+\item Since our visual tracker mostly focuses on tracking objects from aerial moving platforms, we design a new robust target-to-camera distance estimation method.
+This way, a safe distance between the target and the camera-platform can be preserved.
+\end{itemize}
 
+The workflow of our MKCF based long-term target following method can be visualized in fig.???. Summarize what we discuss in the next sections.
 %--------------

### 2017-04-03 draft.tex
References are Added
The Workflow figure for MKCF and PF Added

@@
 %%%%%%%%% TITLE
-\title{High Speed Object Tracking using Multiple Kernelized Correlation Filters}
+\title{Multiple Kernelized Correlation Filters based High Speed Target Following}
 
@@
 
+The workflow of our MKCF based long-term target following method can be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss in the next sections.
+\begin{figure*}[!t]
+\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
+\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
+\label{Workflow_figure}
+\end{figure*}
+
 Frequency domain correlation filter based trackers in the
@@
 \begin{itemize}
-\item We build a highly efficient (300 fps) scale adaptive multiple kernelized correlation filter based tracker that outperforms the original KCF implementation with fixed scale framework both in terms of accuracy and performance.
+\item We build a highly efficient ($\geq300$ fps) scale adaptive multiple kernelized correlation filter based tracker that outperforms the original KCF implementation with fixed scale framework both in terms of accuracy and performance.
 The studies following the KCF improved the fixed scale framework by running detection on a number of candidate ROIs to figure out the new scale of the object after estimating the translation of the object.
@@
 
-The workflow of our MKCF based long-term target following method can be visualized in fig.???. Summarize what we discuss in the next sections.
+\section{Kernelized Correlation Filter Tracker}
+\label{KCF}
+
 %--------------
@@
 
-{\small
+\small
 \bibliographystyle{ieee}
-\bibliography{egbib}
-}
+\bibliography{draft}
 

### 2017-04-05 draft.tex
Updated KCF Part and Bibliography File

@@
 
+% ---------------------------------------------------------
 \section{Kernelized Correlation Filter Tracker}
 \label{KCF}
+% ---------------------------------------------------------
+The Kernelized Correlation Filter tracker has recently been increasingly popular due to its operation at hundreds of frames per second with state-of-the-art tracking capabilities in
+challenging cases.
+Its computational efficiency arises from its use of the discrete fourier transform of the circulant matrix and frequency domain element-wise operations knows hadamard product and division.
+The first example of frequency domain trackers is the Linear Correlation Filter tracker known as MOSSE tracker.
+It minimizes the ridge regression function
+in the frequency domain using a single template with continous desired gaussian response. The KCF tracker, on the other hand, minimizes the regularized ridge regression function shown below. 
+\begin{equation}
+E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}g*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
+\label{eq:Closedform_RidgeReg}
+\end{equation}
+where $y$ represents the desired continous response whereas $h$ and $x_{c}$ represents the learned correlation filter and training template for the given channel.
+The $c$ parameter included in \cite{henriques2015high,galoogahi2013multi} makes it possible to integrate multi-channel features such as HoG and colour into the ridge regression function.
+The closed-form solution for the eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the derivative of $E$ w.r.t $w$ to $0$.
+The solution in the primal domain can be formulated as
+\begin{equation}
+w = (X^{T}X+\lambda)^{-1}y
+\label{eq:SpatialSolution}
+\end{equation}
+where $X$ and $\lambda$ represent the training samples and regularization term. The same cost function in the Fourier domain can be represented as
+\begin{equation}
+w = (X^{H}X+\lambda I)^{-1}X^{T}y
+\label{eq:FourierSolution}
+\end{equation}
+More information on the spatial and fourier domain solutions can be found in \cite{henriques2015high}.
+The MOSSE tracker does not make use of $\lambda$ and only one training sample with desired response is used to update $w$.
+This framework does not include enough background information into the training framework with a single template.
+The application of the circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many background patches at a similar computational complexity.
+A circulant matrix $C$ includes the circularly shifted patches of the positive training sample $x$ by the cylic shift operator $P$.
+By applying shifting operation to the base sample, we can generate the circulant matrix as
+\begin{equation}
+C = Px.
+\label{eq:CirculantMatrixGeneration}
+\end{equation}
+The circulant matrix of a base sample $x$ can be interpreted as the rows of a training matrix $X$ where each row represents features of a training sample. Mathematically, this can be written as
+\begin{equation}
+X = C(x)
+\label{eq:CIrculantMatrixTrainingData}
+\end{equation}
+In this form, eq.~\ref{eq:SpatialSolution} and~\ref{eq:FourierSolution} could prohibit us from implementing a high speed object tracking as we need to perform large number of element-wise division and multiplication operations.
+However, we know from \cite{gray2006toeplitz} that all circulant matrices are represented diagonally by the Fourier Transform regardless of the base sample $x$ as shown below.
+\begin{equation}
+X = Fdiag(\hat{x})F^{H}.
+\label{eq:CirculantMatrixDFT}
+\end{equation}
+where $F$ denotes a constant Fourier Transform matrix and $x$ is the Discrete Fourier Transform of the base sample $x$.
+To simplify the cost function formulation in eq.~\ref{eq:FourierSolution} we multiply $X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
+\begin{equation}
+X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
+\label{eq:SimplificationX} 
+\end{equation}
+Finally, the eq.~\ref{eq:SimplificationX} can used to formulate the solution vector in Fourier domain $\hat{w}$ as
+\begin{equation}
+\hat{w} = \dfrac{\hat{x}^{*}*\hat{y}}{\hat{x}^{*}*\hat{x}+\lambda}.
+\label{eq:DiagonalizedPrimalSolution}
+\end{equation}
+For detailed documentation of the circulant matrix theorem based frequency domain solution can be found in \cite{henriques2012exploiting,henriques2015high}.
 
+The above primal frequency domain solution can be called as Linear Correlation Filter which improves the MOSSE tracker by incorporating cyclic shifts and regularizer.
+To further improve the robustness to geometric and photographic variations, one can exploit non-linear regression function in the Correlation Filter framework \cite{henriques2015high}.
+The solution to the kernelized ridge regression function is shown below.
+\begin{equation}
+\alpha = y(K+\lambda I)^{-1}
+\end{equation}
+wjere $K$ and $\alpha$ represent the kernel matrix and corresponding dual space solution.
+\cite{henriques2015high} states that kernel matrices is circulant for datasets of circular cylic satisfying the following theorem.
+\begin{equation}
+k(x,x^{'}) = k(Mx,Mx^{'})
+\label{eq:KernelCirculantTheorem}
+\end{equation}
+where $M$ represents the permutation matrix.
+Some kernels satisfying the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian}, \textit{Polynomial}, \textit{Intersection} and \textit{Hellinger} kernels.
+Similar to the diagonalization in the linear ridge regression solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized ridge regression can be made diagonal using the same circulant matrix theorem.
+The diagonalized Fourier domain dual form solution can be expressed as
+\begin{equation}
+\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
+\label{eq:FourierDualDomainSolution}.
+\end{equation}
+where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$ known as \textit{gram matrix}.
+In this study, we will only focus on application of the Gaussian Kernel to the Correlation Filters.
+We refer the readers to \cite{henriques2015high} for the detailed documentation of the application of other kernels to the Correlation Filters.
+For single channel features, the Gaussian kernelization is expressed as
+\begin{equation}
+k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
+\label{eq:GaussianCorrelationSingleChannel}
+\end{equation}
+The first correlation filter based trackers used grayscale feature to learn the solution vector $w$, however, the multi-channel features such as HoG and Color were later exploited to improve tracking accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
+The multi-channel feature integration into the Gaussian Kernelization function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved in a very straight-forward way by summing the correlation result in all the channels as
+\begin{equation}
+k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
+\label{eq:GaussianCorrelationSingleChannel}
+\end{equation}
+Such non-linearization process does not increase the computational complexity of the linear multi-channel correlation filter dramatically as we only need to sum over the $n$ dimensional feature channels.
+Training shown in eq:~\ref{eq:FourierDualDomainSolution} gives us $\hat{a}$ learned in time step $t$.
+We can accumulate $\hat{a}$ over time to integrate more temporal information.
+This can be expressed as
+\begin{equation}
+\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
+\end{equation}
+
+Finally, detection step in multi-channel KCF framework is performed as
+\begin{equation}
+r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
+\end{equation}
+where $r$ denotes the correlation response at all cylic shifts of the first row of the kernel matrix $K$.
+The peak point of the response function gives us the estimated translation of the object from time step $t$-$1$ to $t$.
+
+\section{Multiple Kernelized Correlation Filter Based Tracking}
+\label{sc:MKCF}
+
+\section{Particle Filter}
+\label{sc:PF}
+
+\section{Track Re-initilization via Re-detection}
+\label{sc:Re-initialization}
+
+\section{Geometry Estimation between Target and Drone}
+\label{sc:Geometry}
+
+\section{Experiments}
+\label{sc:Experiments}
+
+\section{Conclusion}
+\label{sc:Conclusion}
 %--------------

### 2017-04-05 draft.tex
MKCF Part Added

@@
 \label{sc:MKCF}
+The KCF with Multi-channel features outperforms the other state-of-the-art object traking algorithms both in terms of run-time performance and tracking accuracy.
+However, it lack scale adaptation module or the naive scale adaptation method added into the KCF reduces the frames per second from $\geq300$ fps to less than $100$ fps.
+One straightforward method is to run detection on ROIs with different sizes determined by pre-defined scale ratios \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}.
+All these method increases the computational complexity of tracking by running detection on a number of ROIs.
+Another scale update method in Correlation Filter framework was proposed by \cite{zhang2014fast}.
+It uses the MOSSE tracker to estimate translation of an object.
+The scale is updated in a naive way where the confidence map is used to determine the scale change between successive frames.
+For instance, their method assumes similar scale in between two consecutive frames given similar confidences.
+With this simple method, we do not need to run detection on different ROIs at a given frame and perform tracking at $\geq300$ fps.
+In this study, we propose the use of Multiple KCFs in an intuitive way to perform robust scale-adaptive tracking at more than $300$ fps.
+Our approach is inspired by \cite{ma2015long} where two KCFs are employed as translation and scale filters.
+It first estimates translation using the translation filter learned on \textit{target}$+$\textit{background} area.
+Then, the scale filter learned on the \textit{target} area is used to estimate new scale of the target at the estimated position.
+Application of translation and scale filter at each frame reduces run-time performance ($\leq50 fps$) as we need to run detection and training on both filters.
+Similarly, we learn three different correlation filters specializing on different aspects of tracking and addresses the weakness of each other, resulting in more robust tracking.
+We name these filters as \textit{target}+\textit{small background} translation filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and \textit{target}+\textit{large background} translation filter ($R_{t}^{L}$).
+Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate.
+\begin{figure}[!t]
+\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
+\caption{The three filters called as medium ROI translation filter, target ROI scale filter and large ROI translation filter are shown.
+Also, the hanning window and desired Gaussian response for each filter are displayed.}
+\label{fig:Filters}
+\end{figure}
 

### 2017-04-06 C++_Implementation/src/Filter_Definition.h
Code Working on MAC OSX

@@ -1,0 +1,107 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+
+/* 
+ * File:   Filter_Definition.h
+ * Author: buzkent
+ *
+ * Created on September 9, 2016, 12:09 PM
+ */
+
+#ifndef FILTER_DEFINITION_H
+#define FILTER_DEFINITION_H
+#include <vector>
+#include <opencv2/opencv.hpp>
+
+using namespace std;
+using namespace cv;
+
+void precision_curve(vector<vector<double> > RMSE);
+
+class Particle_Filter{
+
+public:
+    int N_Particles;  // Number of Particles Allocated
+    int ss_dimension,Obs_Dim; // Dimensionality
+    double beta,Neff;     
+    vector<double> Q; // Transition Noise Covariance
+    double R; // Measurement Noise Covariance
+    double* Weights; 
+    double* particles; //Dynamic Array to Store Particles
+    double* sigmaPoints; // Dynamic Array to Store Sigma Points	
+    double* cov_measmeas;
+    double* Covariance;
+    double* Covariance_Prior;
+    double* particles_prior;
+    double* cov_predmeas;
+    double* sigmaWeights;
+    double* measMean;
+    double* particles_gain;
+    double* predMeas;
+
+
+    Particle_Filter(int nParticles,int Dim,double bt,vector<double> Q_transition,double R_measurement)
+    {
+		N_Particles = nParticles;
+		ss_dimension = Dim;
+		beta = bt; Neff = 0;
+		Q = Q_transition;
+		R = R_measurement;
+		Obs_Dim = 2;
+		particles = new double[N_Particles*Dim] (); // Initiate PF State
+		particles_prior = new double[N_Particles*Obs_Dim] (); // Initiate PF Prior State
+		Weights = new double[N_Particles] ();  // Initiate PF Weights
+		sigmaPoints = new double[N_Particles*Obs_Dim*(2*Obs_Dim+1)] (); // Initiate UT Sigma Points
+		cov_measmeas = new double[N_Particles*Obs_Dim*Obs_Dim] (); // P(yt,yt)
+		cov_predmeas = new double[N_Particles*Obs_Dim*Obs_Dim] (); // P(xt,yt)
[…]

### 2017-04-06 C++_Implementation/src/Function_Definitions.cpp

@@ -1,0 +1,332 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+*/  
+#include <iostream>
+#include "Filter_Definition.h"
+#include <vector>
+#include <math.h>
+#include <numeric>
+#include <random>
+#include <opencv2/opencv.hpp>
+// #include <cmath>
+
+using std::uniform_int_distribution;
+using std::random_device;
+using std::default_random_engine;
+
+random_device rd;
+default_random_engine generator( rd() );
+uniform_int_distribution<int> randomDevice(0,1000); // Random Number Generator (0,1000)
+
+using namespace cv;
+
+void Particle_Filter::particle_initiation(vector<double> Obs)
+{
+    // Initiate Particles for the First Time Step
+    vector<double> Q{10,10,5,5};
+    Obs[2] = 0; Obs[3] = 0;
+
+    for (int i = 0; i < N_Particles; i++)
+        for (int j = 0; j < ss_dimension; j++){
+            particles[i*ss_dimension+j] = Obs[j] + Q[j] * double(randomDevice(generator)-500)/500;
+        }
+}
+
+void Particle_Filter::particle_computeSigmaPoints(){
+
+    // Initiate the Sigma Points based on the Posterior Distribution
+    double lambda = pow(0.5,2) * (Obs_Dim + 2) - Obs_Dim;
+    for (int i = 0; i < N_Particles; i++)
+	for (int j = 0; j < (2*Obs_Dim+1); j+=2){
+	  if (j == 0){
+	      	sigmaPoints[i*10] = particles[i*ss_dimension];
+              	sigmaPoints[i*10+1] = particles[i*ss_dimension+1];
+              	// sigmaPoints[i*10+2] = particles[i*Obs_Dim+2];
+              	// sigmaPoints[i*10+3] = particles[i*Obs_Dim+3];
+	      	sigmaWeights[j] = lambda / (Obs_Dim + lambda);
+	 }
+	 else {  
[…]

### 2017-04-06 C++_Implementation/src/ffttools.hpp

@@ -1,0 +1,334 @@
+
+#pragma once
+
+//#include <cv.h>
+#include <assert.h>
+#ifndef _OPENCV_FFTTOOLS_HPP_
+#define _OPENCV_FFTTOOLS_HPP_
+#endif
+
+//NOTE: FFTW support is still shaky, disabled for now.
+/*#ifdef USE_FFTW
+#include <fftw3.h>
+#endif*/
+
+namespace FFTTools
+{
+// Previous declarations, to avoid warnings
+cv::Mat fftd(cv::Mat img, bool backwards = false);
+cv::Mat fftd_w_roi(cv::Mat img, bool backwards = false);
+cv::Mat fftd_scale(cv::Mat img, bool backwards = false);
+cv::Mat real(cv::Mat img);
+cv::Mat imag(cv::Mat img);
+cv::Mat magnitude(cv::Mat img);
+cv::Mat complexMultiplication(cv::Mat a, cv::Mat b);
+cv::Mat complexDivision(cv::Mat a, cv::Mat b);
+void rearrange(cv::Mat &img);
+void normalizedLogTransform(cv::Mat &img);
+
+cv::Mat fftd(cv::Mat img, bool backwards)
+{
+/*
+#ifdef USE_FFTW
+
+    fftw_complex * fm = (fftw_complex*) fftw_malloc(sizeof (fftw_complex) * img.cols * img.rows);
+
+    fftw_plan p = fftw_plan_dft_2d(img.rows, img.cols, fm, fm, backwards ? 1 : -1, 0 * FFTW_ESTIMATE);
+
+
+    if (img.channels() == 1)
+    {
+        for (int i = 0; i < img.rows; i++)
+            for (int j = 0; j < img.cols; j++)
+            {
+                fm[i * img.cols + j][0] = img.at<float>(i, j);
+                fm[i * img.cols + j][1] = 0;
+            }
+    }
+    else
+    {
+        assert(img.channels() == 2);
+        for (int i = 0; i < img.rows; i++)
+            for (int j = 0; j < img.cols; j++)
+            {
+                fm[i * img.cols + j][0] = img.at<cv::Vec2d > (i, j)[0];
+                fm[i * img.cols + j][1] = img.at<cv::Vec2d > (i, j)[1];
+            }
+    }
+    fftw_execute(p);
+    cv::Mat res(img.rows, img.cols, CV_64FC2);
+
+
[…]

### 2017-04-06 C++_Implementation/src/fhog.cpp

@@ -1,0 +1,463 @@
+#include "fhog.hpp"
+
+
+#ifdef HAVE_TBB
+#include <tbb/tbb.h>
+#include "tbb/parallel_for.h"
+#include "tbb/blocked_range.h"
+#endif
+
+#ifndef max
+#define max(a,b)            (((a) > (b)) ? (a) : (b))
+#endif
+
+#ifndef min
+#define min(a,b)            (((a) < (b)) ? (a) : (b))
+#endif
+
+
+/*
+// Getting feature map for the selected subimage
+//
+// API
+// int getFeatureMaps(const IplImage * image, const int k, featureMap **map);
+// INPUT
+// image             - selected subimage
+// k                 - size of cells
+// OUTPUT
+// map               - feature map
+// RESULT
+// Error status
+*/
+int getFeatureMaps(const IplImage* image, const int k, CvLSVMFeatureMapCaskade **map)
+{
+    int sizeX, sizeY;
+    int p, px, stringSize;
+    int height, width, numChannels;
+    int i, j, kk, c, ii, jj, d;
+    float  * datadx, * datady;
+    
+    int   ch; 
+    float magnitude, x, y, tx, ty;
+    
+    IplImage * dx, * dy;
+    int *nearest;
+    float *w, a_x, b_x;
+
+    float kernel[3] = {-1.f, 0.f, 1.f};
+    CvMat kernel_dx = cvMat(1, 3, CV_32F, kernel);
+    CvMat kernel_dy = cvMat(3, 1, CV_32F, kernel);
+
+    float * r;
+    int   * alfa;
+    
+    float boundary_x[NUM_SECTOR + 1];
+    float boundary_y[NUM_SECTOR + 1];
+    float max, dotProd;
+    int   maxi;
+
+    height = image->height;
+    width  = image->width ;
+
+    numChannels = image->nChannels;
+
+    dx    = cvCreateImage(cvSize(image->width, image->height), 
+                          IPL_DEPTH_32F, 3);
+    dy    = cvCreateImage(cvSize(image->width, image->height), 
+                          IPL_DEPTH_32F, 3);
+
+    sizeX = width  / k;
+    sizeY = height / k;
+    px    = 3 * NUM_SECTOR; 
+    p     = px;
+    stringSize = sizeX * p;
+    allocFeatureMapObject(map, sizeX, sizeY, p);
+
+    cvFilter2D(image, dx, &kernel_dx, cvPoint(-1, 0));
[…]

### 2017-04-06 C++_Implementation/src/fhog.hpp

@@ -1,0 +1,129 @@
+#ifndef _FHOG_H_
+#define _FHOG_H_
+
+#include <stdio.h>
+//#include "_lsvmc_types.h"
+//#include "_lsvmc_error.h"
+//#include "_lsvmc_routine.h"
+
+//#include "opencv2/imgproc.hpp"
+#include "opencv2/imgproc/imgproc_c.h"
+
+
+//modified from "_lsvmc_types.h"
+
+// DataType: STRUCT featureMap
+// FEATURE MAP DESCRIPTION
+//   Rectangular map (sizeX x sizeY), 
+//   every cell stores feature vector (dimension = numFeatures)
+// map             - matrix of feature vectors
+//                   to set and get feature vectors (i,j) 
+//                   used formula map[(j * sizeX + i) * p + k], where
+//                   k - component of feature vector in cell (i, j)
+typedef struct{
+    int sizeX;
+    int sizeY;
+    int numFeatures;
+    float *map;
+} CvLSVMFeatureMapCaskade;
+
+
+#include "float.h"
+
+#define PI    CV_PI
+
+#define EPS 0.000001
+
+#define F_MAX FLT_MAX
+#define F_MIN -FLT_MAX
+
+// The number of elements in bin
+// The number of sectors in gradient histogram building
+#define NUM_SECTOR 9
+
+// The number of levels in image resize procedure
+// We need Lambda levels to resize image twice
+#define LAMBDA 10
+
+// Block size. Used in feature pyramid building procedure
+#define SIDE_LENGTH 8
+
+#define VAL_OF_TRUNCATE 0.2f 
+
+
+//modified from "_lsvm_error.h"
+#define LATENT_SVM_OK 0
+#define LATENT_SVM_MEM_NULL 2
+#define DISTANCE_TRANSFORM_OK 1
+#define DISTANCE_TRANSFORM_GET_INTERSECTION_ERROR -1
+#define DISTANCE_TRANSFORM_ERROR -2
+#define DISTANCE_TRANSFORM_EQUAL_POINTS -3
+#define LATENT_SVM_GET_FEATURE_PYRAMID_FAILED -4
+#define LATENT_SVM_SEARCH_OBJECT_FAILED -5
+#define LATENT_SVM_FAILED_SUPERPOSITION -6
+#define FILTER_OUT_OF_BOUNDARIES -7
[…]

### 2017-04-06 C++_Implementation/src/kcftracker.cpp

@@ -1,0 +1,1191 @@
+/*
+
+Constructor parameters, all boolean:
+    hog: use HOG features (default), otherwise use raw pixels
+    fixed_window: fix window size (default), otherwise use ROI size (slower but more accurate)
+    multiscale: use multi-scale tracking (default; cannot be used with fixed_window = true)
+
+Default values are set for all properties of the tracker depending on the above choices.
+Their values can be customized further before calling init():
+    interp_factor: linear interpolation factor for adaptation
+    sigma: gaussian kernel bandwidth
+    lambda: regularization
+    cell_size: HOG cell size
+    padding: area surrounding the target, relative to its size
+    output_sigma_factor: bandwidth of gaussian target
+    template_size: template size in pixels, 0 to use ROI size
+    scale_step: scale step for multi-scale estimation, 1 to disable it
+    scale_weight: to downweight detection scores of other scales for added stability
+
+For speed, the value (template_size/cell_size) should be a power of 2 or a product of small prime numbers.
+
+Inputs to init():
+   image is the initial frame.
+   roi is a cv::Rect with the target positions in the initial frame
+
+Inputs to update():
+   image is the current frame.
+
+Outputs of update():
+   cv::Rect with target positions for the current frame
+*/
+
+#ifndef _KCFTRACKER_HEADERS
+#include "kcftracker.hpp"
+#include "ffttools.hpp"
+#include "recttools.hpp"
+#include "fhog.hpp"
+#include "labdata.hpp"
+#include <unistd.h>
+#endif
+
+// Constructor
+KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
+{
+
+    // Parameters equal in all cases
+    lambda = 0.0001;    // Regularization Parameter for the Regression Task
+    padding = 2.00;     // The ROI parameter to get n times larger area than the Selected Target - Translation Filter
+    padding_w_roi = 3.00; // The Wider ROI Parameter for the Second Translation Filter
+    padding_scale = 1.00;   // The ROI Parameter for the scale filter
[…]

### 2017-04-06 C++_Implementation/src/kcftracker.hpp

@@ -1,0 +1,108 @@
+#pragma once
+
+#include "tracker.h"
+
+#ifndef _OPENCV_KCFTRACKER_HPP_
+#define _OPENCV_KCFTRACKER_HPP_
+#endif
+
+class KCFTracker : public Tracker
+{
+public:
+    // Constructor
+    KCFTracker(bool hog = true, bool fixed_window = true, bool multiscale = true, bool lab = true);
+
+    // Initialize tracker 
+    virtual void init(const cv::Rect &roi, cv::Mat image);
+    
+    // Update position based on the new frame
+    virtual cv::Rect update(cv::Mat image);
+
+    // Update Position based on the new frame
+    virtual cv::Rect updateWROI(cv::Mat image);
+
+    // Update position based on the new frame
+    virtual cv::Rect updateScale(cv::Mat image);
+
+    // Update the Correlation Filter Result with the Particle Filter
+    void updateKCFbyPF(cv::Rect _roi);
+    
+    float interp_factor, interp_factor_scale, interp_factor_w_roi; // linear interpolation factor for adaptation
+    float sigma;        // gaussian kernel bandwidth
+    float lambda;       // regularization
+    int cell_size;      // HOG cell size
+    int cell_sizeQ;     // cell size^2, to avoid repeated operations
+    float padding, padding_scale, padding_w_roi; // extra area surrounding the target
+    float output_sigma_factor, output_sigma_factor_scale, output_sigma_factor_w_roi; // bandwidth of gaussian target
+    int template_size, template_size_scale, template_size_w_roi; // template size
+    float scale_step;   // scale step for multi-scale estimation
+    float scale_weight; // to downweight detection scores of other scales for added stability	
+
+protected:
+    // Detect object in the current frame.
+    cv::Point2f detect(cv::Mat z, cv::Mat x, float &peak_value);
+
+    // Detect object in the current frame.
+    cv::Point2f detectWROI(cv::Mat z, cv::Mat x, float &peak_value);
+
+    // Detect object in the current frame.
+    cv::Point2f detectScale(cv::Mat z, cv::Mat x, float &peak_value);
+
+    // train tracker with a single image
+    void train(cv::Mat x, float train_interp_factor);
+
+    // train tracker with a single image
+    void trainWROI(cv::Mat x, float train_interp_factor_w_roi);
+
+    // train tracker with a single image
[…]

### 2017-04-06 C++_Implementation/src/recttools.hpp

@@ -1,0 +1,105 @@
+#pragma once
+
+//#include <cv.h>
+#include <math.h>
+#include <assert.h>
+#ifndef _OPENCV_RECTTOOLS_HPP_
+#define _OPENCV_RECTTOOLS_HPP_
+#endif
+
+namespace RectTools
+{
+
+template <typename t>
+inline cv::Vec<t, 2 > center(const cv::Rect_<t> &rect)
+{
+    return cv::Vec<t, 2 > (rect.x + rect.width / (t) 2, rect.y + rect.height / (t) 2);
+}
+
+template <typename t>
+inline t x2(const cv::Rect_<t> &rect)
+{
+    return rect.x + rect.width;
+}
+
+template <typename t>
+inline t y2(const cv::Rect_<t> &rect)
+{
+    return rect.y + rect.height;
+}
+
+template <typename t>
+inline void resize(cv::Rect_<t> &rect, float scalex, float scaley = 0)
+{
+    if (!scaley)scaley = scalex;
+    rect.x -= rect.width * (scalex - 1.f) / 2.f;
+    rect.width *= scalex;
+
+    rect.y -= rect.height * (scaley - 1.f) / 2.f;
+    rect.height *= scaley;
+
+}
+
+template <typename t>
+inline void limit(cv::Rect_<t> &rect, cv::Rect_<t> limit)
+{
+    if (rect.x + rect.width > limit.x + limit.width)rect.width = (limit.x + limit.width - rect.x);
+    if (rect.y + rect.height > limit.y + limit.height)rect.height = (limit.y + limit.height - rect.y);
+    if (rect.x < limit.x)
+    {
+        rect.width -= (limit.x - rect.x);
+        rect.x = limit.x;
+    }
+    if (rect.y < limit.y)
+    {
+        rect.height -= (limit.y - rect.y);
+        rect.y = limit.y;
+    }
+    if(rect.width<0)rect.width=0;
+    if(rect.height<0)rect.height=0;
+}
+
+template <typename t>
+inline void limit(cv::Rect_<t> &rect, t width, t height, t x = 0, t y = 0)
+{
+    limit(rect, cv::Rect_<t > (x, y, width, height));
+}
+
+template <typename t>
+inline cv::Rect getBorder(const cv::Rect_<t > &original, cv::Rect_<t > & limited)
+{
+    cv::Rect_<t > res;
+    res.x = limited.x - original.x;
+    res.y = limited.y - original.y;
[…]

### 2017-04-06 C++_Implementation/src/runtracker.cpp

@@ -1,0 +1,324 @@
+#include <iostream>
+#include <fstream>
+#include <sstream>
+#include <algorithm>
+#include "kcftracker.hpp"
+#include "Filter_Definition.h"
+#include <dirent.h>
+#include <ctime>
+#include <vector>
+#include <math.h>
+#include <string>
+#include <opencv2/core/core.hpp>
+#include <opencv2/opencv.hpp>
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/imgproc/imgproc.hpp>
+#include "opencv2/imgcodecs/imgcodecs.hpp"
+#include "opencv2/videoio/videoio.hpp"
+#include <unistd.h>
+#include <stack>
+#include <ctime>
+#include <random>
+
+using namespace std;
+using namespace cv;
+using std::default_random_engine;
+using std::uniform_int_distribution;
+
+std::stack<clock_t> tictoc_stack;
+
+///
+/// tic and toc is used to measure the time to process an operation
+///
+void tic() {
+    tictoc_stack.push(clock());
+}
+
+void toc() {
+    std::cout << "Time elapsed: "
+              << ((double)(clock() - tictoc_stack.top())) / CLOCKS_PER_SEC
+              << std::endl;
+    tictoc_stack.pop();
+}
+
+void help()
+{
+    cout
+    << "\n----------------------------------------------------------------------------\n"
+    << "USAGE:\n"
+    << "./KCF -d <MOV image filename> |-g <ground truth filename> | -o <output file> | -s <save Video file> | -e <save estimation file> \n"
+    << "\nEXAMPLE:\n"                                                                     
+    << "./KCF -d DJI_1.MOV -g Ground_Truth1.txt -o output1.txt -e estimation.txt -s DJI_1_Output.wmv\n"
+    << "----------------------------------------------------------------------------\n"
+    << endl;
+}
+
+
+// Define the Bounding Box Parameters
+float xMin, yMin, width, height;
+float xMinScale,yMinScale;
+Point pos;
+int var1=1;
+///
+/// An Interactive ROI Drawal Tool
+///
+void CallBackFunc(int event, int x, int y, int flags, void* userdata)
+{
+/* Need to be able to control both up and down event for the ROI */
+    cout << "In CallBack Function" << endl;
+    switch( event )
+    {
+    case EVENT_MOUSEMOVE:
+	cout << "MOUSEMOVE" << endl;
+        break;
+    case EVENT_LBUTTONDOWN:
+        xMin = x;
+        yMin = y;
[…]

### 2017-04-06 C++_Implementation/src/tracker.h

@@ -1,0 +1,24 @@
+#pragma once
+
+#include <opencv2/opencv.hpp>
+#include <string>
+//abstract base class 
+class Tracker
+{
+public:
+   Tracker()  {}
+   virtual  ~Tracker() { }
+
+    virtual void init(const cv::Rect &roi, cv::Mat image) = 0;
+    virtual cv::Rect  update( cv::Mat image) = 0;
+    virtual cv::Rect  updateWROI( cv::Mat image) = 0;
+    virtual cv::Rect  updateScale( cv::Mat image) = 0;
+    double PSR = 2;
+    cv::Rect_<float> _roi, _roi_w,_roi_scale;
+    cv::Rect extracted_roi, extracted_w_roi, extracted_roi_scale;
+    double Train_Indicator;	
+
+// protected:
+    //cv::Rect_<float> _roi;
+};
+

### 2017-04-06 C++_Implementation/src/kcftracker.cpp
Updated Code with Specific Hanning Window for the WROI Trans. Filter

@@ -90,7 +90,7 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
 
     if (multiscale) { // Multiscale KCF Implementation
         template_size = 64;     // Template Size for the Translation Filter
-        template_size_w_roi = 64; // Template Size for the Wide ROI Translation Filter
+        template_size_w_roi = 96; // Template Size for the Wide ROI Translation Filter
         template_size_scale = 48;   // Template Size for the Scale Filter
         scale_step = 1.06;      // Scale Factor for the Multiscale Search
         scale_weight = 0.95;    // Priority is given to the Same Scale with Previous Frame Scale
@@ -171,7 +171,7 @@ cv::Rect KCFTracker::update(cv::Mat image)
 
     // Train the Translation Filter Model
     cv::Mat x = getFeatures(image, 0);
-	train(x, interp_factor);
+    train(x, interp_factor);
 
     return _roi;
 }
@@ -203,7 +203,7 @@ cv::Rect KCFTracker::updateWROI(cv::Mat image)
     _roi.x = _roi_w.x;
     _roi.y = _roi_w.y;
 
-    if (_roi_w.x + _roi_w.width <= 0) _roi_w.x = -_roi_w.width + 1;
+    if (_roi_w.x + _roi_w.width <= 0)  _roi_w.x = -_roi_w.width + 1;
     if (_roi_w.y + _roi_w.height <= 0) _roi_w.y = -_roi_w.height + 1;
     if (_roi_w.x >= image.cols - 1) _roi_w.x = image.cols - 2;
     if (_roi_w.y >= image.rows - 1) _roi_w.y = image.rows - 2;
@@ -212,7 +212,7 @@ cv::Rect KCFTracker::updateWROI(cv::Mat image)
 
     // Train the Translation Filter Model
     cv::Mat x = getFeaturesWROI(image, 0);
-	trainWROI(x, interp_factor);
+    trainWROI(x, interp_factor);
 
     return _roi_w;
 }
@@ -924,6 +924,7 @@ cv::Mat KCFTracker::getFeaturesWROI(const cv::Mat & image, bool inithann, float 
     // Crop the ROI Area
     cv::Mat FeaturesMap;  
     cv::Mat z = RectTools::subwindow(image, extracted_w_roi, cv::BORDER_REPLICATE);
+
[…]

### 2017-04-06 C++_Implementation/src/kcftracker.hpp

@@ -87,6 +87,9 @@ protected:
     // Initialize Hanning window. Function called only in the first frame.
     void createHanningMats();
 
+    // Initialize Hanning window. Function called only in the first frame.
+    void createHanningMatsWROI();
+
     // Calculate sub-pixel peak for one dimension
     float subPixelPeak(float left, float center, float right);
 
@@ -99,7 +102,7 @@ protected:
 
 private:
     int size_patch[3], size_patch_scale[3], size_patch_w_roi[3];
-    cv::Mat hann;
+    cv::Mat hann, hann_wroi;
     cv::Size _tmpl_sz, _tmpl_sz_scale, _tmpl_sz_w_roi;
     float _scale,_scale2,_scale_w_roi;
     int _gaussian_size;

### 2017-04-06 C++_Implementation/src/runtracker.cpp

@@ -1,6 +1,7 @@
 #include <iostream>
 #include <fstream>
 #include <sstream>
+#include <iomanip>
 #include <algorithm>
 #include "kcftracker.hpp"
 #include "Filter_Definition.h"
@@ -65,23 +66,22 @@ int var1=1;
 void CallBackFunc(int event, int x, int y, int flags, void* userdata)
 {
 /* Need to be able to control both up and down event for the ROI */
-    cout << "In CallBack Function" << endl;
     switch( event )
     {
     case EVENT_MOUSEMOVE:
-	cout << "MOUSEMOVE" << endl;
+	// cout << "MOUSEMOVE" << endl;
         break;
     case EVENT_LBUTTONDOWN:
         xMin = x;
         yMin = y;
-	cout << "BOTTOM DOWN" << endl;
+	// cout << "BOTTOM DOWN" << endl;
         break;
     case EVENT_LBUTTONUP:
         pos.x = x;
         pos.y = y;
         width = x - xMin;
         height =  y - yMin;
-	cout << "BOTTOM UP" << endl;
+	// cout << "BOTTOM UP" << endl;
         cout << "xMin = " << xMin << " yMin = " << yMin << "  width = " << width << "  height = " << height << endl;
 //        var1=0;
         break;
@@ -195,7 +195,7 @@ int main(int argc, char* argv[])
    while (1) // Read the Next Frame
    {
      std::stringstream ss;
-     ss << std::setfill('0') << std::setw(8) << nFrames+1;
+     ss << std::setfill('0') << std::setw(5) << nFrames+1;
      string frame_id = to_string(nFrames); 
      if (strncmp(argv[2],"video",5) == 0){
         cout << "Image Read" << endl;
@@ -218,16 +218,13 @@ int main(int argc, char* argv[])
          cout << "\nPlease Select ROI: \n";
 	 while(var1==1)
          {
-    	    cout << "Before Callback" << endl;
-	    // namedWindow("Name");
+    	    // namedWindow("Name");
             setMouseCallback("Name", CallBackFunc, NULL);
-      	    cout << "After CallBack" << endl;
             imshow("Name", frame);
             // Wait until user press some key
-            rectangle( frame, Point( xMin, yMin ), Point( xMin+width, yMin+height), Scalar( 255, 0, 0 ), 4, 8 );
+            // rectangle( frame, Point( xMin, yMin ), Point( xMin+width, yMin+height), Scalar( 255, 0, 0 ), 4, 8 );
[…]

### 2017-04-06 C++_Implementation/src/kcftracker.cpp
The Framework Updated - The Scale Filter Needs to be Added Color Features - Needs to Be Double-Checked

@@ -92,8 +92,8 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
         template_size = 64;     // Template Size for the Translation Filter
         template_size_w_roi = 96; // Template Size for the Wide ROI Translation Filter
         template_size_scale = 48;   // Template Size for the Scale Filter
-        scale_step = 1.06;      // Scale Factor for the Multiscale Search
-        scale_weight = 0.95;    // Priority is given to the Same Scale with Previous Frame Scale
+        scale_step = 1.05;      // Scale Factor for the Multiscale Search
+        scale_weight = 2.0 - scale_step;    // Priority is given to the Same Scale with Previous Frame Scale
         if (!fixed_window) {    // Fixed Window KCF Implementation during Tracking
             //printf("Multiscale does not support non-fixed window.\n");
             fixed_window = true;
@@ -149,6 +149,48 @@ cv::Rect KCFTracker::update(cv::Mat image)
     // Detect the Target Translation
     float peak_value;
     cv::Point2f res = detect(_tmpl, getFeatures(image, 0, 1.0f), peak_value);
+
+    // Search Different Scales
+    scale_step = 1.02;
+    if (scale_step != 1) {
+
+        // Test at a smaller _scale
+        float new_peak_value;
+        cv::Point2f new_res = detect(_tmpl, getFeatures(image, 0, 1.0f / scale_step), new_peak_value);
+
+        // Update the Scale if the Confidence is Larger than the Maximum
+        if (scale_weight * new_peak_value > peak_value) {
+            res = new_res;
+            peak_value = new_peak_value;
+            _scale /= scale_step;
+            _scale_w_roi /= scale_step;
+            _scale2 /= scale_step;
+            _roi.width /= scale_step;
+            _roi.height /= scale_step;
+            _roi_w.width /= scale_step;
+            _roi_w.height /= scale_step;
+            _roi_scale.width /= scale_step;
+            _roi_scale.height /= scale_step;
+        }
+
+        // Test at a bigger _scale
+        new_res = detect(_tmpl, getFeatures(image, 0, scale_step), new_peak_value);
+
+        // Update the Scale if the Confidence is Larger than the Maximum
+        if (scale_weight * new_peak_value > peak_value) {
+            res = new_res;
+            peak_value = new_peak_value;
+            _scale *= 1.02;
[…]

### 2017-04-07 draft.tex
MKCF Part Finished - Algorithm Added

@@
 \usepackage{amssymb}
-
-% Include other packages here, before hyperref.
+\usepackage{algorithm}% http://ctan.org/pkg/algorithms
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
 
@@
 \newcommand{\emmett}[1]{\color{violet} Emmett: #1  \color{black}}
+\usepackage{forloop}
+\newcounter{ct}
+\newcommand{\markdent}[1]{\forloop{ct}{0}{\value{ct} < #1}{\hspace{\algorithmicindent}}}
+\newcommand{\markcomment}[1]{\Statex\markdent{#1}}
 \begin{document}
@@
 Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate.
+The fig.~\ref{fig:Filters} shows the size of the ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning windows assigned and desired Gaussian responses assigned to each one.
+
 \begin{figure}[!t]
@@
 \end{figure}
+
+Our MKCF based tracking framework employs different capabilities and tasks to each correlation filter learned temporally.
+In \cite{ma2015long, danelljan2014accurate}, a scale filter is learned on \textit{target-only} area whereas \cite{henriques2015high, li2014scale, bibi2015multi, tang2015multi} uses a correlation filter learned on \textit{target+background} area to find the optimal scale in scale space.
+To learn the scale filter, $R_{s}$, we follow a similar approach to \cite{ma2015long}.
+We believe that translation filter needs to include background information to better discriminate target from background, however, the goal of the scale filter is to estimate the right size of the target, not to discriminate it from background.
+Also, by using a smaller ROI we can reduce the size of the template to learn the scale filter, resulting in higher speed scale estimation module.
+Finally, the scale filter help us on the track re-initialization module which includes running an object proposals algorithm to boxes bounding the objects in the scene.
+By using the scale filter in re-initialization module, we can reduce the element-wise operations compared to the translation filters.
+The \textit{target+small background} area translation filter, $R_{t}^{S}$, is assigned a larger template size than $R_{s}$ and smaller than $R_{t}^{L}$.
+It is employed to estimate translation and scale similar to \cite{henriques2015high}.
+Finally, the \textit{target+large background} area translation filter, $R_{t}^{L}$ , estimates only the translation of a target.
+
+\begin{algorithm}
+	\caption{The MKCF Tracking Algorithm.}\label{alg:MKCF}
+	\begin{algorithmic}[1]
+	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n$,
+	\State \textbf{Output} : 
+								\If{$fc\:\%\:n=0$} \Comment{Condition 1}
+										\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
+										Scale filter (\textit{target-only}) model $R_{s}$.
+								     \EndIf
+								     \If{$fc\:\%\:n=1$}\Comment{Condition 2}
+										\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
+										Large Area Translation Filter model $R_{t}^{L}$.
+								     \EndIf
+								     \If{$fc\:\%\:n>1$}\Comment{Condition 3}
+										\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
+										Small Area Translation Filter model $R_{t}^{S}$.
+								     \EndIf
+	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
+								 \State // Translation Estimation
+								 \State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
+								 \State // Translation Estimation
+								 \State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
+								 and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
+								 \State Skip translation estimation for $R_{s}$ (Condition 1);
+								 \State // Scale Estimation
+								 \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1) or $R_{t}^{S}$ (Condition 2), 
+								 \State Skip it for $R_{t}^{L}$ (Condition 1),
+								 \State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$, and for $R_{t}^{S}$ : $\lbrace1.02,1.0,1/1.02\rbrace$;
+								 \State // Update Translation
+								 \State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
+								 \State // Model Update
+								 \If{$max(y_{R_{s}}) \geq T_{R_{s}}$}
+								 	\State Update $R_{s}$ (Condition 1);
+								 \EndIf							 
+								 \If{$max(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
+								 	\State Update $R_{t}^{L}$ (Condition 2);
+								 \EndIf	
+								 \If{$max(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
+								 	\State Update $R_{t}^{S}$ (Condition 3);
+								 \EndIf		
+	\EndProcedure	
+	\end{algorithmic}
+\end{algorithm}
 

### 2017-04-08 draft.tex
Particle Filter first draft finished

@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
-
 \usepackage{cvpr}
@@
 \usepackage{amssymb}
-\usepackage{algorithm}% http://ctan.org/pkg/algorithms
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
+\usepackage{mathtools} % mathtools builds on and extends amsmath package
+\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
+\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
 
@@
 \label{sc:PF}
+The proposed MKCF algorithm can cause undesired drift and noise in tracking due to independent application of the correlation filters.
+To mitigate the drift effect and reduce the noise, a Bayes Filter representing the evolution of target's motion can be added into the MKCF tracking framework.
+In this study, we consider a variant of a Bayes Filter, \textit{Particle Filter}.
+The Particle Filter is a Sequential Monte Carlo method that can approximate posterior probability density functions (pdf) of a target motion.
+The approximation becomes optimal with the infinite number of particles, however, its run-time complexity grows exponentially with the number of elements in the state space matrix, $X_{t}$.
+As the focus of this study is to design a high speed tracker, we keep the number of state space elements low and implement computationally cheap \textit{Weight Function} and \textit{Importance-Resampling} modules.
+We represent the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$ are the centroid of the target and $V$ represents the velocity components.
+We transit the particles with the well-known first order Constant Velocity model.
+The centroid components are applied Gaussian Noise whereas the velocity components are assigned uniform noise representative of most of the objects.
+The observation likelihood is modeled based on the confidence map of $R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$.
+It can also be modeled based on the euclidean distance between particle's centroid to the peak of the confidence maps, however, we believe that the former approach could result in further drifts in the case of multi-modal distributions.
+The weights for the particles are computed with the bilinear interpolation method.
+\begin{equation}
+	w_{p_{t}}(x_{t},y_{t}) = \dfrac{\splitfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1)+}{y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
+\end{equation}
+where $w_{p}$ denotes the weight of the particle.
+The importance re-sampling module is triggered when the number of effective particles is smaller than a pre-defined threshold [Cite - Effective Number Samples Metric] to avoid variance getting too small.
+Re-sampling is implemented with highly efficient low-variance ratio method [cite].
+Finally, the expected mean of the approximated posterior pdf is computed as
+\begin{equation}
+	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}
+\end{equation}
 
+The particles are assigned equal weight ($\dfrac{1}{P}$) after the importance re-sampling step.
+It should be emphasized that we skip importance re-sampling step in the scale filter operation as the scale filter contains \textit{target-only} area.
+In this case, the particles outside of the scale filter ROI do not have weight correspondence in the confidence map.
+Also, it is more likely to get noisy translation estimation from the scale filter.
+
+WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
 \section{Track Re-initilization via Re-detection}

### 2017-04-09 draft.tex
Removed duplicate bib entry; cleaned up a bit.

@@
 \begin{itemize}
-\item We build a highly efficient ($\geq300$ fps) scale adaptive multiple kernelized correlation filter based tracker that outperforms the original KCF implementation with fixed scale framework both in terms of accuracy and performance.
-The studies following the KCF improved the fixed scale framework by running detection on a number of candidate ROIs to figure out the new scale of the object after estimating the translation of the object.
-This approach adds additional complexity to the original KCF implementation and drags down the run-time performance from $300$ fps to less than $100$ fps.
-\item We integrate the Particle Filter into the Multiple KCFs tracking as an additional filter that can avoid the drift due to one of the correlation filters we employ in our framework.
-\item We propose a target re-detection module that can minimize the target loss due to the scale filter that learns the object model using only-object area.
-Also, the target re-detection step is required to handle severe occlusions, pose variations, illumination changes and fast motion.
-\item Since our visual tracker mostly focuses on tracking objects from aerial moving platforms, we design a new robust target-to-camera distance estimation method.
-This way, a safe distance between the target and the camera-platform can be preserved.
+
+\item We build a highly efficient ($\geq300$ fps) scale adaptive
+  multiple kernelized correlation filter based tracker that
+  outperforms the original KCF implementation with fixed scale
+  framework both in terms of accuracy and performance. The studies
+  following the KCF improved the fixed scale framework by running
+  detection on a number of candidate ROIs to figure out the new scale
+  of the object after estimating the translation of the object. This
+  approach adds additional complexity to the original KCF
+  implementation and drags down the run-time performance from $300$
+  fps to less than $100$ fps.
+
+\item We integrate the Particle Filter into the Multiple KCFs tracking
+  as an additional filter that can avoid the drift due to one of the
+  correlation filters we employ in our framework.
+
+\item We propose a target re-detection module that can minimize the
+  target loss due to the scale filter that learns the object model
+  using only-object area. Also, the target re-detection step is
+  required to handle severe occlusions, pose variations, illumination
+  changes and fast motion.
+
+\item Since our visual tracker mostly focuses on tracking objects from
+  aerial moving platforms, we design a new robust target-to-camera
+  distance estimation method. This way, a safe distance between the
+  target and the camera-platform can be preserved.
+
 \end{itemize}
@@
 % ---------------------------------------------------------
-The Kernelized Correlation Filter tracker has recently been increasingly popular due to its operation at hundreds of frames per second with state-of-the-art tracking capabilities in
-challenging cases.
-Its computational efficiency arises from its use of the discrete fourier transform of the circulant matrix and frequency domain element-wise operations knows hadamard product and division.
-The first example of frequency domain trackers is the Linear Correlation Filter tracker known as MOSSE tracker.
-It minimizes the ridge regression function
-in the frequency domain using a single template with continous desired gaussian response. The KCF tracker, on the other hand, minimizes the regularized ridge regression function shown below. 
+The Kernelized Correlation Filter tracker has recently been
+increasingly popular due to its operation at hundreds of frames per
+second with state-of-the-art tracking capabilities in challenging
+cases. Its computational efficiency arises from its use of the
+discrete fourier transform of the circulant matrix and frequency
+domain element-wise operations knows hadamard product and
+division. The first example of frequency domain trackers is the Linear
+Correlation Filter tracker known as MOSSE tracker. It minimizes the
+ridge regression function in the frequency domain using a single
+template with continous desired gaussian response. The KCF tracker, on
+the other hand, minimizes the regularized ridge regression function
+shown below.
 \begin{equation}
@@
 \end{equation}
-where $y$ represents the desired continous response whereas $h$ and $x_{c}$ represents the learned correlation filter and training template for the given channel.
-The $c$ parameter included in \cite{henriques2015high,galoogahi2013multi} makes it possible to integrate multi-channel features such as HoG and colour into the ridge regression function.
-The closed-form solution for the eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the derivative of $E$ w.r.t $w$ to $0$.
-The solution in the primal domain can be formulated as
+where $y$ represents the desired continous response whereas $h$ and
+$x_{c}$ represents the learned correlation filter and training
+template for the given channel. The $c$ parameter included in
+\cite{henriques2015high,galoogahi2013multi} makes it possible to
+integrate multi-channel features such as HoG and colour into the ridge
+regression function. The closed-form solution for the
+eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
+derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain
+can be formulated as
 \begin{equation}
@@
 \end{equation}
-where $X$ and $\lambda$ represent the training samples and regularization term. The same cost function in the Fourier domain can be represented as
+where $X$ and $\lambda$ represent the training samples and
+regularization term. The same cost function in the Fourier domain can
+be represented as
 \begin{equation}
@@
 \end{equation}
-More information on the spatial and fourier domain solutions can be found in \cite{henriques2015high}.
-The MOSSE tracker does not make use of $\lambda$ and only one training sample with desired response is used to update $w$.
-This framework does not include enough background information into the training framework with a single template.
-The application of the circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many background patches at a similar computational complexity.
-A circulant matrix $C$ includes the circularly shifted patches of the positive training sample $x$ by the cylic shift operator $P$.
-By applying shifting operation to the base sample, we can generate the circulant matrix as
+More information on the spatial and fourier domain solutions can be
+found in \cite{henriques2015high}. The MOSSE tracker does not make use
+of $\lambda$ and only one training sample with desired response is
+used to update $w$. This framework does not include enough background
+information into the training framework with a single template. The
+application of the circulant matrix theorem into the
+eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
+background patches at a similar computational complexity. A circulant
+matrix $C$ includes the circularly shifted patches of the positive
+training sample $x$ by the cylic shift operator $P$. By applying
+shifting operation to the base sample, we can generate the circulant
+matrix as
 \begin{equation}
@@
 \end{equation}
-The circulant matrix of a base sample $x$ can be interpreted as the rows of a training matrix $X$ where each row represents features of a training sample. Mathematically, this can be written as
+The circulant matrix of a base sample $x$ can be interpreted as the
+rows of a training matrix $X$ where each row represents features of a
+training sample. Mathematically, this can be written as
 \begin{equation}
@@
 \end{equation}
-In this form, eq.~\ref{eq:SpatialSolution} and~\ref{eq:FourierSolution} could prohibit us from implementing a high speed object tracking as we need to perform large number of element-wise division and multiplication operations.
-However, we know from \cite{gray2006toeplitz} that all circulant matrices are represented diagonally by the Fourier Transform regardless of the base sample $x$ as shown below.
+In this form, eq.~\ref{eq:SpatialSolution}
+and~\ref{eq:FourierSolution} could prohibit us from implementing a
+high speed object tracking as we need to perform large number of
+element-wise division and multiplication operations. However, we know
+from \cite{gray2006toeplitz} that all circulant matrices are
+represented diagonally by the Fourier Transform regardless of the base
+sample $x$ as shown below.
 \begin{equation}
@@
 \end{equation}
-where $F$ denotes a constant Fourier Transform matrix and $x$ is the Discrete Fourier Transform of the base sample $x$.
-To simplify the cost function formulation in eq.~\ref{eq:FourierSolution} we multiply $X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
+where $F$ denotes a constant Fourier Transform matrix and $x$ is the
+Discrete Fourier Transform of the base sample $x$. To simplify the
+cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
+$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
 \begin{equation}
@@
 \end{equation}
-Finally, the eq.~\ref{eq:SimplificationX} can used to formulate the solution vector in Fourier domain $\hat{w}$ as
+Finally, the eq.~\ref{eq:SimplificationX} can used to formulate the
+solution vector in Fourier domain $\hat{w}$ as
 \begin{equation}
@@
 \end{equation}
-For detailed documentation of the circulant matrix theorem based frequency domain solution can be found in \cite{henriques2012exploiting,henriques2015high}.
+For detailed documentation of the circulant matrix theorem based
+frequency domain solution can be found in
+\cite{henriques2012exploiting,henriques2015high}.
 
-The above primal frequency domain solution can be called as Linear Correlation Filter which improves the MOSSE tracker by incorporating cyclic shifts and regularizer.
-To further improve the robustness to geometric and photographic variations, one can exploit non-linear regression function in the Correlation Filter framework \cite{henriques2015high}.
-The solution to the kernelized ridge regression function is shown below.
+The above primal frequency domain solution can be called as Linear
+Correlation Filter which improves the MOSSE tracker by incorporating
+cyclic shifts and regularizer. To further improve the robustness to
+geometric and photographic variations, one can exploit non-linear
+regression function in the Correlation Filter framework
+\cite{henriques2015high}. The solution to the kernelized ridge
+regression function is shown below.
 \begin{equation}
@@
 \end{equation}
-wjere $K$ and $\alpha$ represent the kernel matrix and corresponding dual space solution.
-\cite{henriques2015high} states that kernel matrices is circulant for datasets of circular cylic satisfying the following theorem.
+wjere $K$ and $\alpha$ represent the kernel matrix and corresponding
+dual space solution. \cite{henriques2015high} states that kernel
+matrices is circulant for datasets of circular cylic satisfying the
+following theorem.
 \begin{equation}
@@
 \end{equation}
-where $M$ represents the permutation matrix.
-Some kernels satisfying the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian}, \textit{Polynomial}, \textit{Intersection} and \textit{Hellinger} kernels.
-Similar to the diagonalization in the linear ridge regression solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized ridge regression can be made diagonal using the same circulant matrix theorem.
-The diagonalized Fourier domain dual form solution can be expressed as
+where $M$ represents the permutation matrix. Some kernels satisfying
+the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
+\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
+kernels. Similar to the diagonalization in the linear ridge regression
+solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized
+ridge regression can be made diagonal using the same circulant matrix
+theorem.  The diagonalized Fourier domain dual form solution can be
+expressed as
 \begin{equation}
@@
 \end{equation}
-where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$ known as \textit{gram matrix}.
-In this study, we will only focus on application of the Gaussian Kernel to the Correlation Filters.
-We refer the readers to \cite{henriques2015high} for the detailed documentation of the application of other kernels to the Correlation Filters.
-For single channel features, the Gaussian kernelization is expressed as
+where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
+known as \textit{gram matrix}. In this study, we will only focus on
+application of the Gaussian Kernel to the Correlation Filters. We
+refer the readers to \cite{henriques2015high} for the detailed
+documentation of the application of other kernels to the Correlation
+Filters. For single channel features, the Gaussian kernelization is
+expressed as
 \begin{equation}
@@
 \end{equation}
-The first correlation filter based trackers used grayscale feature to learn the solution vector $w$, however, the multi-channel features such as HoG and Color were later exploited to improve tracking accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
-The multi-channel feature integration into the Gaussian Kernelization function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved in a very straight-forward way by summing the correlation result in all the channels as
+The first correlation filter based trackers used grayscale feature to
+learn the solution vector $w$, however, the multi-channel features
+such as HoG and Color were later exploited to improve tracking
+accuracy
+\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
+multi-channel feature integration into the Gaussian Kernelization
+function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
+in a very straight-forward way by summing the correlation result in
+all the channels as
 \begin{equation}
@@
 \end{equation}
-Such non-linearization process does not increase the computational complexity of the linear multi-channel correlation filter dramatically as we only need to sum over the $n$ dimensional feature channels.
-Training shown in eq:~\ref{eq:FourierDualDomainSolution} gives us $\hat{a}$ learned in time step $t$.
-We can accumulate $\hat{a}$ over time to integrate more temporal information.
-This can be expressed as
+Such non-linearization process does not increase the computational
+complexity of the linear multi-channel correlation filter dramatically
+as we only need to sum over the $n$ dimensional feature
+channels. Training shown in eq:~\ref{eq:FourierDualDomainSolution}
+gives us $\hat{a}$ learned in time step $t$. We can accumulate
+$\hat{a}$ over time to integrate more temporal information. This can
+be expressed as
 \begin{equation}
@@
 \end{equation}
-where $r$ denotes the correlation response at all cylic shifts of the first row of the kernel matrix $K$.
-The peak point of the response function gives us the estimated translation of the object from time step $t$-$1$ to $t$.
+where $r$ denotes the correlation response at all cylic shifts of the
+first row of the kernel matrix $K$. The peak point of the response
+function gives us the estimated translation of the object from time
+step $t$-$1$ to $t$.
 
+%-------------------------------------------------------------------
 \section{Multiple Kernelized Correlation Filter Based Tracking}
 \label{sc:MKCF}
-The KCF with Multi-channel features outperforms the other state-of-the-art object traking algorithms both in terms of run-time performance and tracking accuracy.
-However, it lack scale adaptation module or the naive scale adaptation method added into the KCF reduces the frames per second from $\geq300$ fps to less than $100$ fps.
-One straightforward method is to run detection on ROIs with different sizes determined by pre-defined scale ratios \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}.
-All these method increases the computational complexity of tracking by running detection on a number of ROIs.
-Another scale update method in Correlation Filter framework was proposed by \cite{zhang2014fast}.
-It uses the MOSSE tracker to estimate translation of an object.
-The scale is updated in a naive way where the confidence map is used to determine the scale change between successive frames.
-For instance, their method assumes similar scale in between two consecutive frames given similar confidences.
-With this simple method, we do not need to run detection on different ROIs at a given frame and perform tracking at $\geq300$ fps.
-In this study, we propose the use of Multiple KCFs in an intuitive way to perform robust scale-adaptive tracking at more than $300$ fps.
-Our approach is inspired by \cite{ma2015long} where two KCFs are employed as translation and scale filters.
-It first estimates translation using the translation filter learned on \textit{target}$+$\textit{background} area.
-Then, the scale filter learned on the \textit{target} area is used to estimate new scale of the target at the estimated position.
-Application of translation and scale filter at each frame reduces run-time performance ($\leq50 fps$) as we need to run detection and training on both filters.
-Similarly, we learn three different correlation filters specializing on different aspects of tracking and addresses the weakness of each other, resulting in more robust tracking.
-We name these filters as \textit{target}+\textit{small background} translation filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and \textit{target}+\textit{large background} translation filter ($R_{t}^{L}$).
-Unlike \cite{ma2015long}, by running a single filter at each frame, we can achieve the targeted operation frame rate.
-The fig.~\ref{fig:Filters} shows the size of the ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning windows assigned and desired Gaussian responses assigned to each one.
+%------------------------------------------------------------------
+The KCF with Multi-channel features outperforms the other
+state-of-the-art object traking algorithms both in terms of run-time
+performance and tracking accuracy. However, it lack scale adaptation
+module or the naive scale adaptation method added into the KCF reduces
+the frames per second from $\geq300$ fps to less than $100$ fps. One
+straightforward method is to run detection on ROIs with different
+sizes determined by pre-defined scale ratios
+\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All
+these method increases the computational complexity of tracking by
+running detection on a number of ROIs. Another scale update method in
+Correlation Filter framework was proposed by \cite{zhang2014fast}. It
+uses the MOSSE tracker to estimate translation of an object. The scale
+is updated in a naive way where the confidence map is used to
+determine the scale change between successive frames. For instance,
+their method assumes similar scale in between two consecutive frames
+given similar confidences. With this simple method, we do not need to
+run detection on different ROIs at a given frame and perform tracking
+at $\geq300$ fps. In this study, we propose the use of Multiple KCFs
+in an intuitive way to perform robust scale-adaptive tracking at more
+than $300$ fps. Our approach is inspired by \cite{ma2015long} where
+two KCFs are employed as translation and scale filters. It first
+estimates translation using the translation filter learned on
+\textit{target}$+$\textit{background} area. Then, the scale filter
+learned on the \textit{target} area is used to estimate new scale of
+the target at the estimated position. Application of translation and
+scale filter at each frame reduces run-time performance ($\leq50 fps$)
+as we need to run detection and training on both filters. Similarly,
+we learn three different correlation filters specializing on different
+aspects of tracking and addresses the weakness of each other,
+resulting in more robust tracking. We name these filters as
+\textit{target}+\textit{small background} translation filter
+($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+\textit{target}+\textit{large background} translation filter
+($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
+each frame, we can achieve the targeted operation frame rate. The
+fig.~\ref{fig:Filters} shows the size of the ROIs associated with
+$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
+windows assigned and desired Gaussian responses assigned to each one.
 
@@
 \includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
-\caption{The three filters called as medium ROI translation filter, target ROI scale filter and large ROI translation filter are shown.
-Also, the hanning window and desired Gaussian response for each filter are displayed.}
+\caption{The three filters called as medium ROI translation filter,
+  target ROI scale filter and large ROI translation filter are
+  shown. Also, the hanning window and desired Gaussian response for
+  each filter are displayed.}
 \label{fig:Filters}
@@
 
-Our MKCF based tracking framework employs different capabilities and tasks to each correlation filter learned temporally.
-In \cite{ma2015long, danelljan2014accurate}, a scale filter is learned on \textit{target-only} area whereas \cite{henriques2015high, li2014scale, bibi2015multi, tang2015multi} uses a correlation filter learned on \textit{target+background} area to find the optimal scale in scale space.
-To learn the scale filter, $R_{s}$, we follow a similar approach to \cite{ma2015long}.
-We believe that translation filter needs to include background information to better discriminate target from background, however, the goal of the scale filter is to estimate the right size of the target, not to discriminate it from background.
-Also, by using a smaller ROI we can reduce the size of the template to learn the scale filter, resulting in higher speed scale estimation module.
-Finally, the scale filter help us on the track re-initialization module which includes running an object proposals algorithm to boxes bounding the objects in the scene.
-By using the scale filter in re-initialization module, we can reduce the element-wise operations compared to the translation filters.
-The \textit{target+small background} area translation filter, $R_{t}^{S}$, is assigned a larger template size than $R_{s}$ and smaller than $R_{t}^{L}$.
-It is employed to estimate translation and scale similar to \cite{henriques2015high}.
-Finally, the \textit{target+large background} area translation filter, $R_{t}^{L}$ , estimates only the translation of a target.
+Our MKCF based tracking framework employs different capabilities and
+tasks to each correlation filter learned temporally. In
+\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
+\textit{target-only} area whereas \cite{henriques2015high,
+  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
+learned on \textit{target+background} area to find the optimal scale
+in scale space. To learn the scale filter, $R_{s}$, we follow a
+similar approach to \cite{ma2015long}. We believe that translation
+filter needs to include background information to better discriminate
+target from background, however, the goal of the scale filter is to
+estimate the right size of the target, not to discriminate it from
+background. Also, by using a smaller ROI we can reduce the size of the
+template to learn the scale filter, resulting in higher speed scale
+estimation module. Finally, the scale filter help us on the track
+re-initialization module which includes running an object proposals
+algorithm to boxes bounding the objects in the scene. By using the
+scale filter in re-initialization module, we can reduce the
+element-wise operations compared to the translation filters. The
+\textit{target+small background} area translation filter, $R_{t}^{S}$,
+is assigned a larger template size than $R_{s}$ and smaller than
+$R_{t}^{L}$. It is employed to estimate translation and scale similar
+to \cite{henriques2015high}. Finally, the \textit{target+large
+  background} area translation filter, $R_{t}^{L}$ , estimates only
+the translation of a target.
 
@@
 \label{sc:PF}
-The proposed MKCF algorithm can cause undesired drift and noise in tracking due to independent application of the correlation filters.
-To mitigate the drift effect and reduce the noise, a Bayes Filter representing the evolution of target's motion can be added into the MKCF tracking framework.
-In this study, we consider a variant of a Bayes Filter, \textit{Particle Filter}.
-The Particle Filter is a Sequential Monte Carlo method that can approximate posterior probability density functions (pdf) of a target motion.
-The approximation becomes optimal with the infinite number of particles, however, its run-time complexity grows exponentially with the number of elements in the state space matrix, $X_{t}$.
-As the focus of this study is to design a high speed tracker, we keep the number of state space elements low and implement computationally cheap \textit{Weight Function} and \textit{Importance-Resampling} modules.
-We represent the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$ are the centroid of the target and $V$ represents the velocity components.
-We transit the particles with the well-known first order Constant Velocity model.
-The centroid components are applied Gaussian Noise whereas the velocity components are assigned uniform noise representative of most of the objects.
-The observation likelihood is modeled based on the confidence map of $R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$.
-It can also be modeled based on the euclidean distance between particle's centroid to the peak of the confidence maps, however, we believe that the former approach could result in further drifts in the case of multi-modal distributions.
-The weights for the particles are computed with the bilinear interpolation method.
+The proposed MKCF algorithm can cause undesired drift and noise in
+tracking due to independent application of the correlation filters. To
+mitigate the drift effect and reduce the noise, a Bayes Filter
+representing the evolution of target's motion can be added into the
+MKCF tracking framework. In this study, we consider a variant of a
+Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
+Sequential Monte Carlo method that can approximate posterior
+probability density functions (pdf) of a target motion. The
+approximation becomes optimal with the infinite number of particles,
+however, its run-time complexity grows exponentially with the number
+of elements in the state space matrix, $X_{t}$. As the focus of this
+study is to design a high speed tracker, we keep the number of state
+space elements low and implement computationally cheap \textit{Weight
+  Function} and \textit{Importance-Resampling} modules. We represent
+the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
+where $x$ and $y$ are the centroid of the target and $V$ represents
+the velocity components. We transit the particles with the well-known
+first order Constant Velocity model. The centroid components are
+applied Gaussian Noise whereas the velocity components are assigned
+uniform noise representative of most of the objects. The observation
+likelihood is modeled based on the confidence map of
+$R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$. It can also be modeled based on
+the euclidean distance between particle's centroid to the peak of the
+confidence maps, however, we believe that the former approach could
+result in further drifts in the case of multi-modal distributions. The
+weights for the particles are computed with the bilinear interpolation
+method.
 \begin{equation}
@@
 \end{equation}
-where $w_{p}$ denotes the weight of the particle.
-The importance re-sampling module is triggered when the number of effective particles is smaller than a pre-defined threshold [Cite - Effective Number Samples Metric] to avoid variance getting too small.
-Re-sampling is implemented with highly efficient low-variance ratio method [cite].
-Finally, the expected mean of the approximated posterior pdf is computed as
+where $w_{p}$ denotes the weight of the particle. The importance
+re-sampling module is triggered when the number of effective particles
+is smaller than a pre-defined threshold [Cite - Effective Number
+  Samples Metric] to avoid variance getting too small. Re-sampling is
+implemented with highly efficient low-variance ratio method
+[cite]. Finally, the expected mean of the approximated posterior pdf
+is computed as
 \begin{equation}
@@
 
-The particles are assigned equal weight ($\dfrac{1}{P}$) after the importance re-sampling step.
-It should be emphasized that we skip importance re-sampling step in the scale filter operation as the scale filter contains \textit{target-only} area.
-In this case, the particles outside of the scale filter ROI do not have weight correspondence in the confidence map.
-Also, it is more likely to get noisy translation estimation from the scale filter.
+The particles are assigned equal weight ($\dfrac{1}{P}$) after the
+importance re-sampling step. It should be emphasized that we skip
+importance re-sampling step in the scale filter operation as the scale
+filter contains \textit{target-only} area. In this case, the particles
+outside of the scale filter ROI do not have weight correspondence in
+the confidence map. Also, it is more likely to get noisy translation
+estimation from the scale filter.
 
-WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
+WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE
+POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
 \section{Track Re-initilization via Re-detection}

### 2017-04-09 draft.tex
Revised introduction a bit.

@@
 \usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
+\usepackage{comment}
 
@@
 Affiliation\\
-{\tt\small yseo@autelrobotics.edu}
+{\tt\small youngwoo.blank.seo@gmail.com}
 }
@@
 
-The tracking-by-detection methods have recently emerged as robust,
-powerful, and highly discriminative trackers replacing the preceding
-generative trackers that focused on only target modeling. Some of the
-recent tracking-by-detection algorithms are
-Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
+The tracking-by-detection methods have recently used extensively as a
+robust, powerful, and highly discriminative vision-based, object
+tracking method replacing the preceding, generative object tracking
+methods that primarily concerned about learning the appearance of the
+target. The recent examples of the tracking-by-detection algorithms
+include Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
 Instance Learning \cite{babenko2009visual}, Correlation Filter based
 trackers \cite{bolme2010visual,henriques2015high}, and Struck
-\cite{hare2012efficient}. These tracking-by-detection methods train an
-object-specific classifier on the fly with the focus of discriminating
-the target from the background. Learning an object-specific classifier
-in an online manner can better handle challenging scenarios with the
-cost of increased complexity. In order to train a classifier, one need
-positive and negative samples. Randomly collecting negative samples
-from the background area can be one straightforward way of building
-training data to train the classifier. However, there can be two
-issues in this framework. First, the randomly collected samples can
-have large correlation resulting in a weak classifier. Also, such
-framework is not feasible for real-time tracking as the number of
-samples gradually increases. Most of the tracking-by-detection
-algorithms focus on efficient incremental update of a classifier
-together with more useful background sampling.
+\cite{hare2012efficient}. These tracking-by-detection methods learn
+the model of the target's appearance on the fly while discriminating
+the target from the background.
 
-The workflow of our MKCF based long-term target following method can be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss in the next sections.
+{\it Burak: It isn't clear what you're getting at here} Learning
+an object-specific classifier in an online manner can better handle
+challenging scenarios with the cost of increased complexity.
+
+To train a (binary) classifier to detect the target at every frame,
+the classifier needs positive and negative examples. In a typical set
+up, a positive example is assumed to be given whereas a set of
+negative examples can be randomly collected from the background around
+the given positive example. Such a typical setup for a
+tracking-by-detection method might have two issues related to its
+performance: Firstly, the appearance of the randomly sampled negative
+examples might be highly correlated with that of positive one,
+resulting in ambiguous boundary between positive and negative
+classes. Secondly for a real-time tracking, such a setup would not be
+feasible for the practice because the number of training data
+gradually increases. Due to these issues, most of the
+tracking-by-detection methods focus on efficiently handling
+incremental update of the learned classifier and on collecting a
+small, but informative negative examples.
+\begin{comment}
+However, there can be two issues in this framework. First,
+the randomly collected samples can have large correlation resulting in
+a weak classifier. Also, such framework is not feasible for real-time
+tracking as the number of samples gradually increases. Most of the
+tracking-by-detection algorithms focus on efficient incremental update
+of a classifier together with more useful background sampling.
+\end{comment}
+
+The workflow of our MKCF based long-term target following method can
+be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss
+in the next sections.
 \begin{figure*}[!t]

### 2017-04-10 C++_Implementation/src/runtracker.cpp
BING Box Proposals Option Added into Tracking

@@ -16,6 +16,7 @@
 #include <opencv2/imgproc/imgproc.hpp>
 #include "opencv2/imgcodecs/imgcodecs.hpp"
 #include "opencv2/videoio/videoio.hpp"
+#include "opencv2/saliency.hpp"
 #include <unistd.h>
 #include <stack>
 #include <ctime>
@@ -23,11 +24,11 @@
 
 using namespace std;
 using namespace cv;
+using namespace saliency;
 using std::default_random_engine;
 using std::uniform_int_distribution;
 
 std::stack<clock_t> tictoc_stack;
-
 ///
 /// tic and toc is used to measure the time to process an operation
 ///
@@ -69,31 +70,19 @@ void CallBackFunc(int event, int x, int y, int flags, void* userdata)
     switch( event )
     {
     case EVENT_MOUSEMOVE:
-	// cout << "MOUSEMOVE" << endl;
         break;
     case EVENT_LBUTTONDOWN:
         xMin = x;
         yMin = y;
-	// cout << "BOTTOM DOWN" << endl;
         break;
     case EVENT_LBUTTONUP:
         pos.x = x;
         pos.y = y;
         width = x - xMin;
         height =  y - yMin;
-	// cout << "BOTTOM UP" << endl;
         cout << "xMin = " << xMin << " yMin = " << yMin << "  width = " << width << "  height = " << height << endl;
-//        var1=0;
         break;
     }
-/*   
-   if  ( event == EVENT_LBUTTONDOWN )
-   {
-      pos.x=x;
-      pos.y=y;
-      var1=0;
-   }
-*/
 }
 
 int main(int argc, char* argv[])
@@ -180,7 +169,6 @@ int main(int argc, char* argv[])
    cout << szDataFile << endl;
    VideoCapture capt;
    if (strncmp(argv[2],"video",5) == 0){
-      cout << "INNNN" << endl;
       string path = szDataFile;
       capt.open(path);
       if (capt.isOpened())
@@ -192,8 +180,15 @@ int main(int argc, char* argv[])
    namedWindow("Name", WINDOW_NORMAL);
    resizeWindow("Name", 800,800);
    
+   // Instantiation of the BING Object from Saliency Library  
+   ObjectnessBING detector;
+   string training_path = "/tmp/opencv3-20170409-82959-bgyg9v/opencv-3.2.0/opencv_contrib/modules/saliency/samples/ObjectnessTrainedModel";
[…]

### 2017-04-10 C++_Implementation/src/runtracker.cpp
Release Mode - Namespaces are removed

@@ -22,12 +22,6 @@
 #include <ctime>
 #include <random>
 
-using namespace std;
-using namespace cv;
-using namespace saliency;
-using std::default_random_engine;
-using std::uniform_int_distribution;
-
 std::stack<clock_t> tictoc_stack;
 ///
 /// tic and toc is used to measure the time to process an operation
@@ -59,7 +53,7 @@ void help()
 // Define the Bounding Box Parameters
 float xMin, yMin, width, height;
 float xMinScale,yMinScale;
-Point pos;
+cv::Point pos;
 int var1=1;
 ///
 /// An Interactive ROI Drawal Tool
@@ -144,47 +138,41 @@ int main(int argc, char* argv[])
    Particle_Filter Tracker(N_Particles,dimension,beta,Q,R);
 
    // Frame read
-   Mat frame;
+   cv::Mat frame;
 
    // Tracker results
-   Rect result;
+   cv::Rect result;
 
    // Read Tracker-by-Detection Output and Ground Truth
-   vector<double> Obs {0,0,0,0};
-   vector<double> State_Mean {0,0,0,0};
+   std::vector<double> Obs {0,0,0,0};
+   std::vector<double> State_Mean {0,0,0,0};
 
    // Video to Overlay Bounding Boxes on the Frames
-   VideoWriter outvid;
-   int codec = VideoWriter::fourcc('W', 'M','V', '2');  // select desired codec (must be available at runtime)
+   cv::VideoWriter outvid;
+   int codec = cv::VideoWriter::fourcc('W', 'M','V', '2');  // select desired codec (must be available at runtime)
    // outvid.open(szSaveVideofile,codec,25,Size(800,800),1);
-   vector<vector<double> > RMSE(2);
+   std::vector<std::vector<double> > RMSE(2);
 
    // Generate Random Numbers used in the Particle Filter
    int seed2 = time(0);
-   default_random_engine engine2(seed2);
-   uniform_int_distribution<int> dist2(0,1000);
+   std::default_random_engine engine2(seed2);
+   std::uniform_int_distribution<int> dist2(0,1000);
 
    // Read the Video
-   cout << argv[2] << endl;
-   cout << szDataFile << endl;
-   VideoCapture capt;
+   cv::VideoCapture capt;
    if (strncmp(argv[2],"video",5) == 0){
       string path = szDataFile;
       capt.open(path);
-      if (capt.isOpened())
-      {
[…]

### 2017-04-10 C++_Implementation/src/kcftracker.cpp
Re-detection Module Added into Tracker using BING

@@ -362,18 +362,8 @@ cv::Point2f KCFTracker::detect(cv::Mat z, cv::Mat x, float &peak_value)
 {
     using namespace FFTTools;
 
-    /* 
-    cv::Mat _alphaf2 = _tmpl.clone();
-    cv::Mat w_model = real(fftd(_alphaf2,true));
-    */
-
     cv::Mat k = gaussianCorrelation(x, z); // Apply Kernel Trick with the Test Template
     cv::Mat res = (real(fftd(complexMultiplication(_alphaf, fftd(k)), true))); // Response Map
-
-    /*
-    cv::imshow("Translation Correlation Map", res);
-    cv::waitKey(2);
-    */
 
     // minMaxLoc only accepts doubles for the peak, and integer points for the coordinates
     cv::Point2i pi;
@@ -384,7 +374,7 @@ cv::Point2f KCFTracker::detect(cv::Mat z, cv::Mat x, float &peak_value)
     // Compute the Peak-to-Sidelobe Ratio
     cv::Scalar mean, stdev;
     cv::meanStdDev(res,mean,stdev);
-    PSR = (peak_value - mean[0])/stdev[0];
+    PSR_sroi = (peak_value - mean[0])/stdev[0];
 
     // subpixel peak estimation, coordinates will be non-integer
     cv::Point2f p((float)pi.x, (float)pi.y);
@@ -420,7 +410,7 @@ cv::Point2f KCFTracker::detectWROI(cv::Mat z, cv::Mat x, float &peak_value)
     // Compute the Peak-to-Sidelobe Ratio
     cv::Scalar mean, stdev;
     cv::meanStdDev(res,mean,stdev);
-    PSR = (peak_value - mean[0])/stdev[0];
+    PSR_wroi = (peak_value - mean[0])/stdev[0];
 
     // subpixel peak estimation, coordinates will be non-integer
     cv::Point2f p((float)pi.x, (float)pi.y);
@@ -447,11 +437,6 @@ cv::Point2f KCFTracker::detectScale(cv::Mat z, cv::Mat x, float &peak_value)
     cv::Mat k = gaussianCorrelationScale(x, z); // Apply Kernel Trick with the Test Template
     cv::Mat res = (real(fftd_scale(complexMultiplication(_alphafScale, fftd_scale(k)), true))); // Response Map
 
-    /*
-    cv::imshow("Scale Correlation Map", res);
-    cv::waitKey(2);
-    */
-
[…]

### 2017-04-10 C++_Implementation/src/kcftracker.hpp

@@ -27,6 +27,9 @@ public:
     // Update the Correlation Filter Result with the Particle Filter
     void updateKCFbyPF(cv::Rect _roi);
     
+    // Target Re-detection Module
+    std::pair<int,float> target_redetection(std::vector<cv::Vec4i> BoundingBoxes, cv::Mat frame);
+
     float interp_factor, interp_factor_scale, interp_factor_w_roi; // linear interpolation factor for adaptation
     float sigma;        // gaussian kernel bandwidth
     float lambda;       // regularization
@@ -47,6 +50,9 @@ protected:
 
     // Detect object in the current frame.
     cv::Point2f detectScale(cv::Mat z, cv::Mat x, float &peak_value);
+
+    // Detect object in the current frame.
+    void detectScaleRedetection(cv::Mat z, cv::Mat x, float &peak_value);
 
     // train tracker with a single image
     void train(cv::Mat x, float train_interp_factor);
@@ -83,6 +89,9 @@ protected:
 
     // Obtain sub-window from image, with replication-padding and extract features
     cv::Mat getFeaturesScale(const cv::Mat & image, bool inithann, float scale_adjust = 1.0f);
+
+    // Obtain sub-window from image, with replication-padding and extract features
+    cv::Mat getFeaturesScaleRedetection(const cv::Mat & image, cv::Vec4i box);
 
     // Initialize Hanning window. Function called only in the first frame.
     void createHanningMats();

### 2017-04-10 C++_Implementation/src/runtracker.cpp

@@ -5,8 +5,6 @@
 #include <algorithm>
 #include "kcftracker.hpp"
 #include "Filter_Definition.h"
-#include <dirent.h>
-#include <ctime>
 #include <vector>
 #include <math.h>
 #include <string>
@@ -19,7 +17,6 @@
 #include "opencv2/saliency.hpp"
 #include <unistd.h>
 #include <stack>
-#include <ctime>
 #include <random>
 
 std::stack<clock_t> tictoc_stack;
@@ -150,7 +147,6 @@ int main(int argc, char* argv[])
    // Video to Overlay Bounding Boxes on the Frames
    cv::VideoWriter outvid;
    int codec = cv::VideoWriter::fourcc('W', 'M','V', '2');  // select desired codec (must be available at runtime)
-   // outvid.open(szSaveVideofile,codec,25,Size(800,800),1);
    std::vector<std::vector<double> > RMSE(2);
 
    // Generate Random Numbers used in the Particle Filter
@@ -165,6 +161,8 @@ int main(int argc, char* argv[])
       capt.open(path);
    }
    int nFrames = 0;
+   int fontFace = cv::FONT_HERSHEY_SCRIPT_SIMPLEX;
+   int thickness = 2;
    cv::namedWindow("Name", WINDOW_NORMAL);
    cv::resizeWindow("Name", 800,800);
    
@@ -178,7 +176,7 @@ int main(int argc, char* argv[])
    {
      // Read the Frame to Perform Tracking
      std::stringstream ss;
-     ss << std::setfill('0') << std::setw(5) << nFrames+1;
+     ss << std::setfill('0') << std::setw(8) << nFrames+1;
      string frame_id = to_string(nFrames); 
      if (strncmp(argv[2],"video",5) == 0){
 	capt >> frame;  // Read Next Frame
@@ -223,22 +221,26 @@ int main(int argc, char* argv[])
 	 /// \param[in] Obs : Observation given by the user in the first frame
 	 ///
          Tracker.particle_initiation(Obs);
-         cv::rectangle( frame, cv::Point( xMin, yMin ), cv::Point( xMin+width, yMin+height), cv::Scalar( 0, 255, 255 ), 15, 8 );
       }
       else {
     	/// -------------------- UPDATE STEP --------------------------------------------
         /// Use Translation and Scale Filter Interchangeably
+	tracker.PSR_scale = 10;
+	float PSR;
         if (nFrames % 5 > 1)
         {
[…]

### 2017-04-10 C++_Implementation/src/tracker.h

@@ -13,7 +13,7 @@ public:
     virtual cv::Rect  update( cv::Mat image) = 0;
     virtual cv::Rect  updateWROI( cv::Mat image) = 0;
     virtual cv::Rect  updateScale( cv::Mat image) = 0;
-    double PSR = 2;
+    double PSR_sroi,PSR_wroi,PSR_scale;
     cv::Rect_<float> _roi, _roi_w,_roi_scale;
     cv::Rect extracted_roi, extracted_w_roi, extracted_roi_scale;
     double Train_Indicator;	

### 2017-04-10 C++_Implementation/src/kcftracker.cpp
Lab Color Features Added into the Scale Filter

@@ -62,10 +62,10 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
         _hogfeatures = true;
 
         if (lab) {  // Activate the LAB Color Features
-            interp_factor = 0.005;
-            sigma = 0.4; 
+            // interp_factor = 0.005;
+            // sigma = 0.4; 
             //output_sigma_factor = 0.025;
-            output_sigma_factor = 0.1;
+            // output_sigma_factor = 0.1;
             std::cout << "Lab Features" << std::endl;
             _labfeatures = true;
             _labCentroids = cv::Mat(nClusters, 3, CV_32FC1, &data);
@@ -128,8 +128,6 @@ void KCFTracker::init(const cv::Rect &roi, cv::Mat image)
     _prob_scale = createGaussianPeakScale(size_patch_scale[0], size_patch_scale[1]);    // Desired Response for the Scale Filter
     _alphafScale = cv::Mat(size_patch_scale[0], size_patch_scale[1], CV_32FC2, float(0));   // Initiate the Scale FIlter Model
 
-    //_num = cv::Mat(size_patch[0], size_patch[1], CV_32FC2, float(0));
-    //_den = cv::Mat(size_patch[0], size_patch[1], CV_32FC2, float(0));
     train(_tmpl, 1.0); // train with initial frame - translation filter 
     trainWROI(_tmpl_w_roi,1.0); // train with initial frame - translation filter Wide ROI
     trainScale(_tmplScale,1.0); // train with initial frame - scale filter
@@ -310,40 +308,10 @@ cv::Rect KCFTracker::updateScale(cv::Mat image)
             _roi_scale.height *= scale_step;
         }
     }
-
-    /// -------------------------------------------------------------------
-    // Adjust by cell size and _scale
-    /*
-    float cx = _roi_scale.x + _roi_scale.width / 2.0f;
-    float cy = _roi_scale.y + _roi_scale.height / 2.0f;
-    _roi_scale.x = cx - _roi_scale.width / 2.0f + ((float) res.x * cell_size * _scale2);
-    _roi_scale.y = cy - _roi_scale.height / 2.0f + ((float) res.y * cell_size * _scale2);
-
-    _roi.x = _roi_scale.x; // Update Translation Filter Centroid
-    _roi.y = _roi_scale.y; // Update Translation Filter Centroid
-    */
-
     // Train the Scale Filter
[…]

### 2017-04-10 C++_Implementation/src/runtracker.cpp

@@ -85,7 +85,7 @@ int main(int argc, char* argv[])
    bool FIXEDWINDOW = false;  // Fixed Window
    bool MULTISCALE = true;    // Scale Space Search Enabled
    bool SILENT = false;	      // Suppress the Outputs
-   bool LAB = false;	      // Enable or Disable Color Features
+   bool LAB = true;	      // Enable or Disable Color Features
    char szDataFile[256];
    char szImageFile[256];
    char szSaveVideofile[256];
@@ -265,7 +265,7 @@ int main(int argc, char* argv[])
 	*/
 	
 	// Re-Initiate the Track
-	if (tracker.PSR_scale < 10){
+	if (tracker.PSR_scale < 3){
 	    // Apply BING Algorithm for Saliency Map Extraction and Box Proposals
 	    detector.computeSaliency(frame,BoundingBoxes);
 	    // std::vector<float> objectnessScores = detector.getobjectnessValues();
@@ -276,7 +276,7 @@ int main(int argc, char* argv[])
             Obs[0] = BoundingBoxes[MatchedBoxIndex.first][0]; Obs[1] = BoundingBoxes[MatchedBoxIndex.first][1]; 
 	    Obs[2] = BoundingBoxes[MatchedBoxIndex.first][2] - BoundingBoxes[MatchedBoxIndex.first][0]; 
 	    Obs[3] = BoundingBoxes[MatchedBoxIndex.first][3] - BoundingBoxes[MatchedBoxIndex.first][1];
-	    // tracker.init( Rect(Obs[0],Obs[1],Obs[2],Obs[3]), frame );
+	    tracker.init( Rect(Obs[0],Obs[1],Obs[2],Obs[3]), frame );
 	    // Draw the Selected Rectangle
             std::string rd_confidence = to_string(float(MatchedBoxIndex.second));
             cv::rectangle(frame,cv::Point(Obs[0],Obs[1]),cv::Point(Obs[0]+Obs[2],Obs[1]+Obs[3]),cv::Scalar(0,255,0),4,8);

### 2017-04-10 draft.tex
Revised the draft to add the submission plan.

@@
 
-A practical solution to target-following mode
+\begin{comment}
+Maybe the goal of this work is to public a journal paper about a
+practical solution for a drone to follow a single target. For this, we need
+\begin{itemize}
+\item A vision-based, single target tracking algorithm.
+\item Other components for making a drone follow a target.
+\begin{itemize}
+\item An architecture diagram
+\item Descriptions of vehicle control, motion planning, behavior
+  generation, estimation of relative geometry between a drone and a
+  target, etc
+\item Experimental results or example videos
+\end{itemize}
+\end{itemize}
+
+For the BMVC-17 submission, we're going to just focus on the first
+part. This is because we need to build a drone for the second part.
+\end{comment}
 
@@
 \item A variant of KCF: Multiple KCF w/ PF
-\item Re-detection
-\item Estimation of geometry between a target and a drone
+\item Re-detection for re-initialization
 \end{itemize}

### 2017-04-11 C++_Implementation/src/kcftracker.cpp
Camera Motion Model Included to Apply Motion to Previous Target Position

@@ -62,10 +62,10 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
         _hogfeatures = true;
 
         if (lab) {  // Activate the LAB Color Features
-            interp_factor = 0.005;
-            sigma = 0.4; 
+            // interp_factor = 0.005;
+            // sigma = 0.4; 
             //output_sigma_factor = 0.025;
-            output_sigma_factor = 0.1;
+            // output_sigma_factor = 0.1;
             std::cout << "Lab Features" << std::endl;
             _labfeatures = true;
             _labCentroids = cv::Mat(nClusters, 3, CV_32FC1, &data);
@@ -128,8 +128,6 @@ void KCFTracker::init(const cv::Rect &roi, cv::Mat image)
     _prob_scale = createGaussianPeakScale(size_patch_scale[0], size_patch_scale[1]);    // Desired Response for the Scale Filter
     _alphafScale = cv::Mat(size_patch_scale[0], size_patch_scale[1], CV_32FC2, float(0));   // Initiate the Scale FIlter Model
 
-    //_num = cv::Mat(size_patch[0], size_patch[1], CV_32FC2, float(0));
-    //_den = cv::Mat(size_patch[0], size_patch[1], CV_32FC2, float(0));
     train(_tmpl, 1.0); // train with initial frame - translation filter 
     trainWROI(_tmpl_w_roi,1.0); // train with initial frame - translation filter Wide ROI
     trainScale(_tmplScale,1.0); // train with initial frame - scale filter
@@ -310,40 +308,10 @@ cv::Rect KCFTracker::updateScale(cv::Mat image)
             _roi_scale.height *= scale_step;
         }
     }
-
-    /// -------------------------------------------------------------------
-    // Adjust by cell size and _scale
-    /*
-    float cx = _roi_scale.x + _roi_scale.width / 2.0f;
-    float cy = _roi_scale.y + _roi_scale.height / 2.0f;
-    _roi_scale.x = cx - _roi_scale.width / 2.0f + ((float) res.x * cell_size * _scale2);
-    _roi_scale.y = cy - _roi_scale.height / 2.0f + ((float) res.y * cell_size * _scale2);
-
-    _roi.x = _roi_scale.x; // Update Translation Filter Centroid
[…]

### 2017-04-11 C++_Implementation/src/kcftracker.hpp

@@ -26,7 +26,13 @@ public:
 
     // Update the Correlation Filter Result with the Particle Filter
     void updateKCFbyPF(cv::Rect _roi);
+
+    // Apply Homography to Previous Target Position for Motion Removal
+    cv::Rect_<float> applyHomography(cv::Mat homography, cv::Rect_<float> oldRoi);
     
+    // Target Re-detection Module
+    std::pair<int,float> target_redetection(std::vector<cv::Vec4i> BoundingBoxes, cv::Mat frame);
+
     float interp_factor, interp_factor_scale, interp_factor_w_roi; // linear interpolation factor for adaptation
     float sigma;        // gaussian kernel bandwidth
     float lambda;       // regularization
@@ -47,6 +53,9 @@ protected:
 
     // Detect object in the current frame.
     cv::Point2f detectScale(cv::Mat z, cv::Mat x, float &peak_value);
+
+    // Detect object in the current frame.
+    void detectScaleRedetection(cv::Mat z, cv::Mat x, float &peak_value);
 
     // train tracker with a single image
     void train(cv::Mat x, float train_interp_factor);
@@ -83,6 +92,9 @@ protected:
 
     // Obtain sub-window from image, with replication-padding and extract features
     cv::Mat getFeaturesScale(const cv::Mat & image, bool inithann, float scale_adjust = 1.0f);
+
+    // Obtain sub-window from image, with replication-padding and extract features
+    cv::Mat getFeaturesScaleRedetection(const cv::Mat & image, cv::Vec4i box);
 
     // Initialize Hanning window. Function called only in the first frame.
     void createHanningMats();

### 2017-04-11 C++_Implementation/src/runtracker.cpp

@@ -5,8 +5,7 @@
 #include <algorithm>
 #include "kcftracker.hpp"
 #include "Filter_Definition.h"
-#include <dirent.h>
-#include <ctime>
+#include "findHomography.hpp"
 #include <vector>
 #include <math.h>
 #include <string>
@@ -16,18 +15,12 @@
 #include <opencv2/imgproc/imgproc.hpp>
 #include "opencv2/imgcodecs/imgcodecs.hpp"
 #include "opencv2/videoio/videoio.hpp"
+// #include "opencv2/saliency.hpp"
 #include <unistd.h>
 #include <stack>
-#include <ctime>
 #include <random>
 
-using namespace std;
-using namespace cv;
-using std::default_random_engine;
-using std::uniform_int_distribution;
-
 std::stack<clock_t> tictoc_stack;
-
 ///
 /// tic and toc is used to measure the time to process an operation
 ///
@@ -58,7 +51,7 @@ void help()
 // Define the Bounding Box Parameters
 float xMin, yMin, width, height;
 float xMinScale,yMinScale;
-Point pos;
+cv::Point pos;
 int var1=1;
 ///
 /// An Interactive ROI Drawal Tool
@@ -69,31 +62,19 @@ void CallBackFunc(int event, int x, int y, int flags, void* userdata)
     switch( event )
     {
     case EVENT_MOUSEMOVE:
-	// cout << "MOUSEMOVE" << endl;
         break;
     case EVENT_LBUTTONDOWN:
         xMin = x;
         yMin = y;
-	// cout << "BOTTOM DOWN" << endl;
         break;
     case EVENT_LBUTTONUP:
         pos.x = x;
         pos.y = y;
         width = x - xMin;
         height =  y - yMin;
-	// cout << "BOTTOM UP" << endl;
         cout << "xMin = " << xMin << " yMin = " << yMin << "  width = " << width << "  height = " << height << endl;
-//        var1=0;
         break;
     }
-/*   
-   if  ( event == EVENT_LBUTTONDOWN )
-   {
-      pos.x=x;
-      pos.y=y;
-      var1=0;
-   }
-*/
 }
 
 int main(int argc, char* argv[])
@@ -105,7 +86,7 @@ int main(int argc, char* argv[])
    bool FIXEDWINDOW = false;  // Fixed Window
    bool MULTISCALE = true;    // Scale Space Search Enabled
    bool SILENT = false;	      // Suppress the Outputs
[…]

### 2017-04-11 C++_Implementation/src/tracker.h

@@ -13,8 +13,9 @@ public:
     virtual cv::Rect  update( cv::Mat image) = 0;
     virtual cv::Rect  updateWROI( cv::Mat image) = 0;
     virtual cv::Rect  updateScale( cv::Mat image) = 0;
-    double PSR = 2;
-    cv::Rect_<float> _roi, _roi_w,_roi_scale;
+    virtual cv::Rect_<float>  applyHomography(cv::Mat homography, cv::Rect_<float> oldroi);
+    double PSR_sroi,PSR_wroi,PSR_scale;
+    cv::Rect_<float> _roi, _roi_w, _roi_scale;
     cv::Rect extracted_roi, extracted_w_roi, extracted_roi_scale;
     double Train_Indicator;	
 

### 2017-04-11 C++_Implementation/src/runtracker.cpp
Camera Motion Model Added into Tracker

@@ -28,6 +28,7 @@ void tic() {
     tictoc_stack.push(clock());
 }
 
+// TOC
 void toc() {
     std::cout << "Time elapsed: "
               << ((double)(clock() - tictoc_stack.top())) / CLOCKS_PER_SEC

### 2017-04-11 draft.tex

@@
 small, but informative negative examples.
+
+{\it Burak: Why do we even mention these issues? Is this somehow
+  related to what we did for this paper?}
+
 \begin{comment}
@@
 
+An object tracking method based on the correlation filter in frequency
+domain has gained attention due to its fast computation.
+
+\begin{comment}
+{\it Burak: This is not entirely true. If this is the case, people
+  including us don't have to invent their own, other than just using
+  KCF.}
+
 Frequency domain correlation filter based trackers in the
@@
 due to its superior computation and robustness to geometric and
-photometric variations. The first correlation filter tracker proposed
-by \cite{bolme2010visual} focused on learning and detection in the
+photometric variations. 
+\end{comment}
+
+The first correlation filter tracker proposed by
+\cite{bolme2010visual} focused on learning and detection in the
 frequency domain. The idea was to minimize the sum of squared error in

### 2017-04-11 C++_Implementation/src/findHomography.cpp
Homography Files Added

@@ -1,0 +1,77 @@
+#include <stdio.h>
+#include <iostream>
+#include "opencv2/core.hpp"
+#include "opencv2/features2d.hpp"
+#include "opencv2/highgui.hpp"
+#include "opencv2/calib3d.hpp"
+#include "opencv2/xfeatures2d.hpp"
+
+cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
+
+  //-- Step 1: Detect the keypoints using SURF Detector
+  int minHessian = 400;
+
+  // Instantiate Surf Object
+  SurfFeatureDetector detector( minHessian );
+
+  // Define Keypoint Vector
+  std::vector<KeyPoint> keypoints_reference, keypoints_test;
+
+  // Detect Keypoints for the reference
+  detector.detect( img_object, keypoints_reference );
+
+  // Detect Keypoints for the model
+  detector.detect( img_scene, keypoints_test );
+
+  //-- Step 2: Calculate descriptors (feature vectors)
+  SurfDescriptorExtractor extractor;
+  cv::Mat descriptors_reference, descriptors_test;
+
+  // Extract the Descriptors
+  
+  //-- Draw only "good" matches (i.e. whose distance is less than 3*min_dist )
+  std::vector< DMatch > good_matches;
+  extractor.compute( img_object, keypoints_reference, descriptors_reference);
+  extractor.compute( img_scene, keypoints_test, descriptors_test);
+
+  //-- Step 3: Matching descriptor vectors using FLANN matcher
+  FlannBasedMatcher matcher;
+  std::vector<DMatch> matches;
+  matcher.match( descriptors_reference, descriptors_test, matches);
+
+  double max_dist = 0; double min_dist = 100;
+  //-- Quick calculation of max and min distances between keypoints
+  for( int i = 0; i < descriptors_reference.rows; i++ )
+  { double dist = matches[i].distance;
+    if( dist < min_dist ) min_dist = dist;
+    if( dist > max_dist ) max_dist = dist;
+  }
+
+  // Find the Good Matches
+  std::vector<DMatch> good_matches;
+  for( int i = 0; i < descriptors_reference.rows; i++ )
+  { 
+     if(matches[i].distance<3*min_dist)
+     { 
+       good_matches.push_back( matches[i]); 
+     }
+  }
+
+  //-- Localize the object
+  std::vector<cv::Point2f> reference;
+  std::vector<cv::Point2f> test;
+
[…]

### 2017-04-11 C++_Implementation/src/findHomography.cpp
Motion Model Code Bugs Resolved

@@ -6,33 +6,34 @@
 #include "opencv2/calib3d.hpp"
 #include "opencv2/xfeatures2d.hpp"
 
+using namespace cv;
+using namespace cv::xfeatures2d;
+
 cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
 
   //-- Step 1: Detect the keypoints using SURF Detector
   int minHessian = 400;
 
   // Instantiate Surf Object
-  SurfFeatureDetector detector( minHessian );
+  Ptr<FeatureDetector> detector = FastFeatureDetector::create(minHessian);
 
   // Define Keypoint Vector
   std::vector<KeyPoint> keypoints_reference, keypoints_test;
 
   // Detect Keypoints for the reference
-  detector.detect( img_object, keypoints_reference );
+  detector->detect( frame_r, keypoints_reference );
 
   // Detect Keypoints for the model
-  detector.detect( img_scene, keypoints_test );
+  detector->detect( frame_t, keypoints_test );
 
   //-- Step 2: Calculate descriptors (feature vectors)
-  SurfDescriptorExtractor extractor;
+  Ptr<SURF> extractor = SURF::create();
   cv::Mat descriptors_reference, descriptors_test;
-
-  // Extract the Descriptors
   
   //-- Draw only "good" matches (i.e. whose distance is less than 3*min_dist )
   std::vector< DMatch > good_matches;
-  extractor.compute( img_object, keypoints_reference, descriptors_reference);
-  extractor.compute( img_scene, keypoints_test, descriptors_test);
+  extractor->compute( frame_r, keypoints_reference, descriptors_reference);
+  extractor->compute( frame_t, keypoints_test, descriptors_test);
 
   //-- Step 3: Matching descriptor vectors using FLANN matcher
   FlannBasedMatcher matcher;
@@ -48,7 +49,6 @@ cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
   }
 
   // Find the Good Matches
-  std::vector<DMatch> good_matches;
   for( int i = 0; i < descriptors_reference.rows; i++ )
   { 
      if(matches[i].distance<3*min_dist)
@@ -69,7 +69,7 @@ cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
   }
 
   // Compute Homography Between Reference and Test Frame
-  Mat H = findHomography( obj, scene, CV_RANSAC );
[…]

### 2017-04-11 C++_Implementation/src/kcftracker.cpp

@@ -1143,7 +1143,7 @@ cv::Mat KCFTracker::getFeaturesScaleRedetection(const cv::Mat &image, cv::Vec4i 
     return FeaturesMap;
 }
 
-cv::Rect_<float> applyHomography(cv::Mat homography, cv::Rect_<float> roi){
+cv::Rect_<float> KCFTracker::applyHomography(cv::Mat homography, cv::Rect_<float> roi){
 
     float cx = roi.x + roi.width /2.0; // Determine the Central Point
     float cy = roi.y + roi.height/2.0; // Determine the Central Point

### 2017-04-11 C++_Implementation/src/kcftracker.hpp

@@ -1,6 +1,7 @@
 #pragma once
 
 #include "tracker.h"
+#include "opencv2/opencv.hpp"
 
 #ifndef _OPENCV_KCFTRACKER_HPP_
 #define _OPENCV_KCFTRACKER_HPP_

### 2017-04-11 C++_Implementation/src/tracker.h

@@ -7,19 +7,16 @@ class Tracker
 {
 public:
    Tracker()  {}
-   virtual  ~Tracker() { }
+    virtual  ~Tracker() { }
 
     virtual void init(const cv::Rect &roi, cv::Mat image) = 0;
     virtual cv::Rect  update( cv::Mat image) = 0;
     virtual cv::Rect  updateWROI( cv::Mat image) = 0;
     virtual cv::Rect  updateScale( cv::Mat image) = 0;
-    virtual cv::Rect_<float>  applyHomography(cv::Mat homography, cv::Rect_<float> oldroi);
-    double PSR_sroi,PSR_wroi,PSR_scale;
+    virtual cv::Rect_<float> applyHomography(cv::Mat homography, cv::Rect_<float> oldroi) = 0;
+    double PSR_sroi, PSR_wroi, PSR_scale;
     cv::Rect_<float> _roi, _roi_w, _roi_scale;
     cv::Rect extracted_roi, extracted_w_roi, extracted_roi_scale;
     double Train_Indicator;	
-
-// protected:
-    //cv::Rect_<float> _roi;
 };
 

### 2017-04-11 C++_Implementation/src/findHom.cpp
Homography Finished - Tested on UAV123 Dataset

@@ -5,35 +5,34 @@
 #include "opencv2/highgui.hpp"
 #include "opencv2/calib3d.hpp"
 #include "opencv2/xfeatures2d.hpp"
+#include <opencv2/imgcodecs.hpp>
+#include <opencv2/imgproc.hpp>
 
 using namespace cv;
 using namespace cv::xfeatures2d;
 
 cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
 
+  // Convert to GrayScale Imagery
+  cv::cvtColor(frame_r,frame_r, CV_RGB2GRAY);
+  cv::cvtColor(frame_t,frame_t, CV_RGB2GRAY);
+
   //-- Step 1: Detect the keypoints using SURF Detector
-  int minHessian = 400;
+  int minHessian = 800;
 
-  // Instantiate Surf Object
-  Ptr<FeatureDetector> detector = FastFeatureDetector::create(minHessian);
-
-  // Define Keypoint Vector
-  std::vector<KeyPoint> keypoints_reference, keypoints_test;
-
-  // Detect Keypoints for the reference
-  detector->detect( frame_r, keypoints_reference );
-
-  // Detect Keypoints for the model
-  detector->detect( frame_t, keypoints_test );
+  // Instantiate SURF Object
+  Ptr<Feature2D> features = SURF::create(minHessian);
 
   //-- Step 2: Calculate descriptors (feature vectors)
-  Ptr<SURF> extractor = SURF::create();
+  std::vector<KeyPoint> keypoints_reference, keypoints_test;
   cv::Mat descriptors_reference, descriptors_test;
+  features->detect(frame_r, keypoints_reference);
+  features->detect(frame_t, keypoints_test);
   
   //-- Draw only "good" matches (i.e. whose distance is less than 3*min_dist )
   std::vector< DMatch > good_matches;
-  extractor->compute( frame_r, keypoints_reference, descriptors_reference);
-  extractor->compute( frame_t, keypoints_test, descriptors_test);
+  features->compute( frame_r, keypoints_reference, descriptors_reference);
+  features->compute( frame_t, keypoints_test, descriptors_test);
 
   //-- Step 3: Matching descriptor vectors using FLANN matcher
   FlannBasedMatcher matcher;
@@ -43,7 +42,8 @@ cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
   double max_dist = 0; double min_dist = 100;
[…]

### 2017-04-11 C++_Implementation/src/kcftracker.cpp

@@ -1143,19 +1143,27 @@ cv::Mat KCFTracker::getFeaturesScaleRedetection(const cv::Mat &image, cv::Vec4i 
     return FeaturesMap;
 }
 
-cv::Rect_<float> KCFTracker::applyHomography(cv::Mat homography, cv::Rect_<float> roi){
+cv::Rect_<float> KCFTracker::applyHomography(cv::Mat homography, cv::Mat image, cv::Rect_<float> roi){
 
-    float cx = roi.x + roi.width /2.0; // Determine the Central Point
+    float cx = roi.x + roi.width/2.0;  // Determine the Central Point
     float cy = roi.y + roi.height/2.0; // Determine the Central Point
 
     // Transform to the New Position
-    cx = cx * homography.at<float>(0,0) + cy * homography.at<float>(0,1) + 1 * homography.at<float>(0,2);
-    cy = cx * homography.at<float>(1,0) + cy * homography.at<float>(1,1) + 1 * homography.at<float>(1,2);
-    float cz = cx * homography.at<float>(2,0) + cy * homography.at<float>(2,1) + 1 * homography.at<float>(2,2);
+    cx = cx * homography.at<double>(0,0) + cy * homography.at<double>(0,1) + 1 * homography.at<double>(0,2);
+    cy = cx * homography.at<double>(1,0) + cy * homography.at<double>(1,1) + 1 * homography.at<double>(1,2);
+    float cz = cx * homography.at<double>(2,0) + cy * homography.at<double>(2,1) + 1 * homography.at<double>(2,2);
 
     // Find the new ROI
     roi.x = cx - roi.width/2.0;
     roi.y = cy - roi.height/2.0;
-    
+ 
+    // Boundary condition
+    if (roi.x + roi.width <= 0)  roi.x = -roi.width + 1;
+    if (roi.y + roi.height <= 0) roi.y = -roi.height + 1;
+    if (roi.x >= image.cols - 1) roi.x = image.cols - 2;
+    if (roi.y >= image.rows - 1) roi.y = image.rows - 2;
+
+    assert(roi.width >= 0 && roi.height >= 0);
+ 
     return roi;
 }

### 2017-04-11 C++_Implementation/src/kcftracker.hpp

@@ -29,7 +29,7 @@ public:
     void updateKCFbyPF(cv::Rect _roi);
 
     // Apply Homography to Previous Target Position for Motion Removal
-    cv::Rect_<float> applyHomography(cv::Mat homography, cv::Rect_<float> oldRoi);
+    cv::Rect_<float> applyHomography(cv::Mat homography, cv::Mat image, cv::Rect_<float> oldRoi);
     
     // Target Re-detection Module
     std::pair<int,float> target_redetection(std::vector<cv::Vec4i> BoundingBoxes, cv::Mat frame);

### 2017-04-11 C++_Implementation/src/runtracker.cpp

@@ -5,7 +5,7 @@
 #include <algorithm>
 #include "kcftracker.hpp"
 #include "Filter_Definition.h"
-#include "findHomography.hpp"
+#include "findHom.hpp"
 #include <vector>
 #include <math.h>
 #include <string>
@@ -137,7 +137,7 @@ int main(int argc, char* argv[])
    Particle_Filter Tracker(N_Particles,dimension,beta,Q,R);
 
    // Frame read
-   cv::Mat frame;
+   cv::Mat frame, frame_old;
 
    // Tracker results
    cv::Rect result;
@@ -178,7 +178,7 @@ int main(int argc, char* argv[])
    {
      // Read the Frame to Perform Tracking
      std::stringstream ss;
-     ss << std::setfill('0') << std::setw(8) << nFrames+1;
+     ss << std::setfill('0') << std::setw(6) << nFrames+1;
      string frame_id = to_string(nFrames); 
      if (strncmp(argv[2],"video",5) == 0){
 	capt >> frame;  // Read Next Frame
@@ -222,11 +222,15 @@ int main(int argc, char* argv[])
 	 /// \param[in] Obs : Observation given by the user in the first frame
 	 ///
          Tracker.particle_initiation(Obs);
+	
+	 // Transfer Frame to Old Frame Holder
+	 frame_old = frame.clone();
       }
       else {
     	/// -------------------- UPDATE STEP --------------------------------------------
 	/// Apply Camera Motion Model	
-	cv::Mat homography = cameraMotionModel(frame,frame);
+	/// cv::Mat homography = cameraMotionModel(frame_old,frame);
+        frame_old = frame.clone();
 
         /// Use Translation and Scale Filter Interchangeably
 	tracker.PSR_scale = 10;
@@ -234,21 +238,21 @@ int main(int argc, char* argv[])
         if (nFrames % 5 > 1)
         {
 	    // Apply Homography to the Track Position at Previous Frame
-	    tracker._roi = tracker.applyHomography(homography, tracker._roi);
+	    // tracker._roi = tracker.applyHomography(homography, frame, tracker._roi);
             result = tracker.update(frame);        // Estimate Translation
 	    PSR = tracker.PSR_sroi;
         }
         if (nFrames % 5 == 1)
         {
             // Apply Homography to the Track Position at Previous Frame
-            tracker._roi_w = tracker.applyHomography(homography, tracker._roi_w);
+            // tracker._roi_w = tracker.applyHomography(homography, frame, tracker._roi_w);
[…]

### 2017-04-11 C++_Implementation/src/tracker.h

@@ -13,7 +13,7 @@ public:
     virtual cv::Rect  update( cv::Mat image) = 0;
     virtual cv::Rect  updateWROI( cv::Mat image) = 0;
     virtual cv::Rect  updateScale( cv::Mat image) = 0;
-    virtual cv::Rect_<float> applyHomography(cv::Mat homography, cv::Rect_<float> oldroi) = 0;
+    virtual cv::Rect_<float> applyHomography(cv::Mat homography, cv::Mat image, cv::Rect_<float> oldroi) = 0;
     double PSR_sroi, PSR_wroi, PSR_scale;
     cv::Rect_<float> _roi, _roi_w, _roi_scale;
     cv::Rect extracted_roi, extracted_w_roi, extracted_roi_scale;

### 2017-04-11 draft.tex
Revised the plan.

@@
 %%%%%%%%% TITLE
-\title{Multiple Kernelized Correlation Filters based High Speed Target Following}
+\title{{\itE}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}
 
@@
 \item Kernelized Correlation Filter
-\item A variant of KCF: Multiple KCF w/ PF
+\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
 \item Re-detection for re-initialization
@@
 \item Experiment: Detail the data, and experimental setup; results and findings
+\item {\it E}nKCF, Naive{\it E}nKCF, ${\it E}nKCF_{+RD}$, LCT, DSST,
+  vanilla-KCF w/ a fixed scale, KCF w/ three different scales, STC,
+\begin{itemize}
+\item DTB-70: w/ and w/o motion estimation,
+\item UAV data, https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx
+\item VOT
+\end{itemize}
 \item Conclusion

### 2017-04-12 draft.tex
Revised the introduction.

@@
 %%%%%%%%% TITLE
-\title{{\itE}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}
+\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}
 
@@
 \item DTB-70: w/ and w/o motion estimation,
-\item UAV data, https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx
+\item UAV123 \footnote{A set of images acquired from an UAV is called
+  ``UAV123'' and publicly available from
+  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
 \item VOT
@@
 \end{comment}
+
+{\it YoungWoo: We'll have to mention why such an online tracker is
+  still attractive over any DNN-based counterparts.}
+
+To the best of our knowledge, the dominant framework of online object
+trackers based on the correlation filter is to solve a regression
+problem in the frequency domain. This framework assumes that the
+target information is given at the very first image frame. Given this
+positive example for the regression problem, a set of negative
+examples is mostly collected around the initial, target bounding box
+and represented as a circulant matrix \cite{henriques2015high}.
 

### 2017-04-13 C++_Implementation/edge/include/edge_box.h
Re-Detection Added into EnKCF

@@ -1,0 +1,111 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_box.h
+///
+/// \Definition : Find many boxes in the image.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _EDGE_BOX_GENERATOR_H_
+#define _EDGE_BOX_GENERATOR_H_
+
+#include "edge_boxes_interface.h"
+#include <math.h>
+#include <algorithm>
+#include <vector>
+using namespace std;
+#define PI 3.1415926535897f
+
+///
+/// v is in the [a, b], return v
+///
+static int clamp(int v, int a, int b)
+{
+  return v<a ? a : v>b ? b : v;
+}
+
+// trivial array class encapsulating pointer arrays
+template <class T> class Array
+{
+public:
+  Array() { _h = _w = 0; _x = 0; _free = 0; }
+  virtual ~Array() { clear(); }
+  void clear() { if (_free) delete[] _x; _h = _w = 0; _x = 0; _free = 0; }
+  void init(int h, int w) { clear(); _h = h; _w = w; _x = new T[h*w](); _free = 1; }
+  T& val(size_t c, size_t r) { return _x[c*_h + r]; }
+  int _h, _w; T *_x; bool _free;
+};
+
+// convenient typedefs
+typedef vector<float> vectorf;
+typedef vector<int> vectori;
+typedef Array<float> arrayf;
+typedef Array<int> arrayi;
+
+// bounding box data structures and routines
+typedef struct { int c, r, w, h; float s; } Box;
+typedef vector<Box> Boxes;
+static bool boxesCompare(const Box &a, const Box &b)
+{
+  return a.s<b.s;
+}
+
+float boxesOverlap(Box &a, Box &b);
+void boxesNms(Boxes &boxes, float thr, float eta, int maxBoxes);
+
+// main class for generating edge boxes
+class EdgeBoxGenerator
+{
+public:
+  // method parameters (must be manually set)
+  float _alpha, _beta, _eta, _minScore; int _maxBoxes;
+  float _edgeMinMag, _edgeMergeThr, _clusterMinMag;
+  float _maxAspectRatio, _minBoxArea, _gamma, _kappa;
+
+  // main external routine (set parameters first)
+  void generate(Boxes &boxes, arrayf &E, arrayf &O, arrayf &V);
+
+private:
+  // edge segment information (see clusterEdges)
+  int h, w;                         // image dimensions
[…]

### 2017-04-13 C++_Implementation/edge/include/edge_boxes_interface.h

@@ -1,0 +1,127 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_boxes_interface.h
+///
+/// \Definition : This is interface function of edge box.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _EDGE_BOXES_INTERFACE_H_
+#define _EDGE_BOXES_INTERFACE_H_
+
+#include "../../tools/include/data_define.h"
+#include <opencv2/core/core.hpp>
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/imgproc/imgproc.hpp>
+#include <vector>
+#include <iostream>
+
+using namespace autel;
+using namespace computer_vision;
+
+typedef struct {
+  float alpha;
+  float beta;
+  float eta;
+  float minScore;
+  float maxBoxes;
+  float edgeMinMag;
+  float edgeMergeThr;
+  float clusterMinMag;
+  float maxAspectRatio;
+  float minBoxArea;
+  float gamma;
+  float kappa;
+} edge_box_parameters;
+
+typedef struct{
+  int imWidth;
+  int gtWidth;
+  int nPos;
+  int nNeg;
+  int nImgs;
+  int nTrees;
+  float fracFtrs;
+  int minCount;
+  int minChild;
+  int maxDepth;
+  char discretize[128];
+  int nSamples;
+  int nClasses;
+  char split[128];
+  int nOrients;
+  int grdSmooth;
+  int chnSmooth;
+  int simSmooth;
+  int normRad;
+  int shrink;
+  int nCells;
+  int rgbd;
+  int stride;
+  int multiscale;
+  int sharpen;
+  int nTreesEval;
+  int nThreads;
+  int nms;
+  int seed;
+  int useParfor;
+  char modelDir[128];
+  char modelFnm[128];
+  char bsdsDir[128];
+  int nChns;
+  int nChnFtrs;
+  int nSimFtrs;
+  int nTotFtrs;
+} model_opts;
+
+///
+/// It is interface of edge box algorithm.
+///
+/// \param[in] img image data
+/// \param[in] box input box
+/// \param[in] memory_ptr temporary memory
+/// \param[out] best box
+///
+std::vector<cv::Vec4i> EdgeBoxInterface(AuMat& img);
+
+///
+/// Initialize many parameters for edge box.
+///
+/// \param[in] model_path the path of model_train.txt
+///
+void InitEdgeBox(char* model_path);
+
+///
[…]

### 2017-04-13 C++_Implementation/edge/include/edge_detection.h

@@ -1,0 +1,30 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_detection.h
+///
+/// \Definition : detect edge.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _EDGE_DETECTION_H_
+#define _EDGE_DETECTION_H_
+#include "../../tools/include/data_define.h"
+#include "../include/edge_boxes_interface.h"
+
+///
+/// Detect edges in image.
+///
+/// \param[in] image img data after ImPadding
+/// \param[in] chns regular output channels
+/// \param[in] chnsSs self-similarity output channels
+/// \param[in] model_edgebox parameters of model
+/// \param[out] E edge map
+/// \param[out] E_w height of E
+/// \param[out] E_h width of E
+///
+void EdgeDetect(AuMat& image, float* E, int* E_w, int* E_h, float* chns, float* chnsSs,
+    model_opts model_edgebox, float* thrs, unsigned int* fids, unsigned int* child,
+    unsigned char* segs, unsigned char* nSegs, unsigned short* eBins, unsigned int* eBnds);
+
+#endif

### 2017-04-13 C++_Implementation/edge/src/edge_box.cpp

@@ -1,0 +1,408 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_box.cpp
+///
+/// \Definition : Find many boxes in the image.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#include "../include/edge_box.h"
+
+void EdgeBoxGenerator::generate(Boxes &boxes, arrayf &E, arrayf &O, arrayf &V)
+{
+  clusterEdges(E, O, V);
+  prepDataStructs(E);
+  scoreAllBoxes(boxes);
+}
+
+void EdgeBoxGenerator::clusterEdges(arrayf &E, arrayf &O, arrayf &V)
+{
+  int c, r, cd, rd, i, j; h = E._h; w = E._w;
+
+  // greedily merge connected edge pixels into clusters (create _segIds)
+  _segIds.init(h, w); _segCnt = 1;
+  for (c = 0; c<w; c++) for (r = 0; r<h; r++) {
+    if (c == 0 || r == 0 || c == w - 1 || r == h - 1 || E.val(c, r) <= _edgeMinMag)
+      _segIds.val(c, r) = -1; else _segIds.val(c, r) = 0;
+  }
+  for (c = 1; c<w - 1; c++) for (r = 1; r<h - 1; r++) {
+    if (_segIds.val(c, r) != 0) continue;
+    float sumv = 0; int c0 = c, r0 = r; vectorf vs; vectori cs, rs;
+    while (sumv < _edgeMergeThr) {
+      _segIds.val(c0, r0) = _segCnt;
+      float o0 = O.val(c0, r0), o1, v; bool found;
+      for (cd = -1; cd <= 1; cd++) for (rd = -1; rd <= 1; rd++) {
+        if (_segIds.val(c0 + cd, r0 + rd) != 0) continue; found = false;
+        for (i = 0; i<cs.size(); i++)
+          if (cs[i] == c0 + cd && rs[i] == r0 + rd) { found = true; break; }
+        if (found) continue; o1 = O.val(c0 + cd, r0 + rd);
+        v = fabs(o1 - o0) / PI; if (v>.5) v = 1 - v;
+        vs.push_back(v); cs.push_back(c0 + cd); rs.push_back(r0 + rd);
+      }
[…]

### 2017-04-13 C++_Implementation/edge/src/edge_boxes_interface.cpp

@@ -1,0 +1,509 @@
+﻿/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_boxes_interface.cpp
+///
+/// \Definition : This is interface function of edge box, include InitEdgeBox, EdgeBoxInterface
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#include "../include/edge_boxes_interface.h"
+#include "../../tools/include/image_tools.h"
+#include "../../tools/include/conv_triangle.h"
+#include "../../tools/include/gradient.h"
+#include "../include/edge_detection.h"
+#include "../include/edge_box.h"
+#include <iostream>
+
+edge_box_parameters g_opts;
+model_opts g_modelEdgeBox;
+
+// memory of loading trained data, about 210M
+float g_thrs[79861*8];
+unsigned int g_fids[79861*8];
+unsigned int g_child[79861 * 8];
+unsigned char g_segs[16*16*79861*8];
+unsigned char g_nSegs[79861 * 8];
+unsigned short g_eBins[19306620];
+unsigned int g_eBnds[1916665];
+
+AuRect<float> g_inputBox;
+
+/// memory for program
+float* memory_ptr;
+float* chns_reg;
+float* chns_sim;
+
+void InitEdgeBox(char* model_path) {
+
+  chns_reg = NULL;
+  chns_sim = NULL;
+  // init edge box parameters
+  g_opts.alpha = 0.65;
+  g_opts.beta = 0.75;
+  g_opts.eta = 1;
+  g_opts.minScore = 0.01;
+  g_opts.maxBoxes = 10000;
+  g_opts.edgeMinMag = 0.1;
+  g_opts.edgeMergeThr = 0.5;
+  g_opts.clusterMinMag = 0.5;
+  g_opts.maxAspectRatio = 3;
+  g_opts.minBoxArea = 1000;
+  g_opts.gamma = 2;
+  g_opts.kappa = 1.5;
+
+  // init model parameters
+  g_modelEdgeBox.imWidth = 32;
+  g_modelEdgeBox.gtWidth = 16;
+  g_modelEdgeBox.nPos = 500000;
+  g_modelEdgeBox.nNeg = 500000;
+  g_modelEdgeBox.nTrees = 8;
+  g_modelEdgeBox.fracFtrs = 0.25;
+  g_modelEdgeBox.minCount = 1;
+  g_modelEdgeBox.minChild = 8;
[…]

### 2017-04-13 C++_Implementation/edge/src/edge_detection.cpp

@@ -1,0 +1,242 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_detection.cpp
+///
+/// \Definition : detect edge.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#include "../include/edge_detection.h"
+#include <cstring>
+
+typedef unsigned int uint32;
+typedef unsigned short uint16;
+typedef unsigned char uint8;
+
+// construct lookup array for mapping fids to channel indices
+uint32* buildLookup(int *dims, int w) {
+  int c, r, z, n = w*w*dims[2];
+  uint32 *cids = new uint32[n];
+  n = 0;
+  for (z = 0; z < dims[2]; z++) {
+    for (c = 0; c < w; c++) {
+      for (r = 0; r < w; r++) {
+        cids[n++] = z*dims[0] * dims[1] + c*dims[0] + r;
+      }
+    }
+  }
+  return cids;
+}
+
+// construct lookup arrays for mapping fids for self-similarity channel
+void buildLookupSs(uint32 *&cids1, uint32 *&cids2, int *dims, int w, int m) {
+  int i, j, z, z1, c, r;
+  int locs[1024];
+  int m2 = m*m, n = m2*(m2 - 1) / 2 * dims[2], s = int(w / m / 2.0 + .5);
+  cids1 = new uint32[n];
+  cids2 = new uint32[n];
+  n = 0;
+  for (i = 0; i < m; i++) {
+    locs[i] = uint32((i + 1)*(w + 2 * s - 1) / (m + 1.0) - s + .5);
+  }
+  for (z = 0; z < dims[2]; z++) {
+    for (i = 0; i < m2; i++) {
+      for (j = i + 1; j < m2; j++) {
+        z1 = z*dims[0] * dims[1]; n++;
+        r = i%m; c = (i - r) / m; cids1[n - 1] = z1 + locs[c] * dims[0] + locs[r];
+        r = j%m; c = (j - r) / m; cids2[n - 1] = z1 + locs[c] * dims[0] + locs[r];
+      }
+    }
+  }
+}
+
+void EdgeDetect(AuMat& image, float* E, int* E_w, int* E_h, float* chns, float* chnsSs,
+    model_opts model_edgebox, float* thrs, unsigned int* fids, unsigned int* child,
+    unsigned char* segs, unsigned char* nSegs, unsigned short* eBins, unsigned int* eBnds)
[…]

### 2017-04-13 C++_Implementation/main/include/interface.h

@@ -1,0 +1,20 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \edge_boxes_interface.h
+///
+/// \Definition : This is interface function of edge box.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _INTERFACE_H_
+#define _INTERFACE_H_
+
+/// 
+/// Initialization box only one time
+/// 
+/// \param[in] model_file: model path, such as: /home/autel/edgebox/model_train.txt
+///
+void InitializedBox(char* model_file);
+
+#endif

### 2017-04-13 C++_Implementation/main/src/interface.cpp

@@ -1,0 +1,86 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \interface.cpp
+///
+/// \Definition : This is interface function for H2 and APP
+///
+///  \author XipengCui
+///  \Date : Created on: Mar 1, 2017
+///
+#include "../edge/include/edge_boxes_interface.h"
+#include "../tools/include/data_define.h"
+#include "../tools/include/image_tools.h"
+
+//#define IS_SAVE
+//extern "C" void InitializedBox(char* model_file);
+//extern "C" int GetBox(unsigned char* buffer, int width, int height, float x_, float y_, float w_, float h_, int data_format, float* _x, float* _y, float* _width, float* _height);
+
+void ResizeROI(unsigned char* src, unsigned char* dst, autel::computer_vision::AuRect<int> roi, autel::computer_vision::AuSize src_size, int src_step, int cn, autel::computer_vision::AuSize dst_size, int dst_step);
+
+void InitializedBox(char* model_file)
+{
+  if(model_file == NULL)
+  {
+    char model_path[256] = "/tmp/SD0/model_train.txt";
+    InitEdgeBox(model_path);
+  }
+  else
+    InitEdgeBox(model_file);
+}
+
+void ResizeROI(unsigned char* src, unsigned char* dst, autel::computer_vision::AuRect<int> roi, autel::computer_vision::AuSize src_size, int src_step, int cn, autel::computer_vision::AuSize dst_size, int dst_step)
+{
+    //bilinearity resample
+    int w = dst_size.width_;
+    int h = dst_size.height_;
+
+    //float --> int
+    int s = 10;
+    int s_sum = 1<<s;
+
+    int x, y;
+    for(y = 0; y < h; y++)
+    {
+        long test = (long)(y*src_size.height_)<<s;
+        long y1 = test/h;
+        test = y1>>s;
+        int a = y1 - (test<<s);
+        y1 = y1>>s;
+        y1 += roi.y_;
+        for(x = 0; x < w; x++)
+        {
+            test = (long)(x*src_size.width_)<<s;
+            long x1 = test/w;
+            test = x1>>s;
+            int b = x1 - (test<<s);
+            x1 = x1>>s;
+            x1 += roi.x_;
+            {
+                int dst_id = (y*dst_step+x)*cn;
[…]

### 2017-04-13 C++_Implementation/main/src/main.cpp

@@ -1,0 +1,67 @@
+#include <iostream>
+#include <opencv2/core/core.hpp>
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/imgproc/imgproc.hpp>
+#include "../include/interface.h"
+#include "/image_tools/include/image_tools.h"
+#include <vector>
+#include "../../edge/include/edge_boxes_interface.h"
+
+using namespace cv;
+using namespace std;
+
+// unsigned char g_memoryEdgeBox[1000*1000*10];
+
+// AuRect<float> g_setInitialBox;
+// unsigned char g_buffer[1000*1000*10];
+
+int main(int argc, char* argv[]) {
+
+  /// opencv read image
+  char path_model[256] = "/home/buzkent/EdgeBox/model_train.txt";
+  cv::Mat Img = cv::imread("/home/buzkent/Desktop/000029.jpg");
+  std::vector<cv::Mat> src;
+  cv::split(Img,src); 
+ 
+  ///
+  /// Fill in the Image Data Structure Parameters
+  ///
+  autel::computer_vision::AuMat image;
+  image.cols_ = Img.cols;
+  image.rows_ = Img.rows;
+  image.depth_ = 0;
+  image.dims_ = 2;
+  image.channels_ = Img.channels();
+  image.step_[1] = image.channels_;
+  image.step_[0] = image.cols_ * image.step_[1];
+  unsigned char* memory_image = (unsigned char*)malloc(Img.cols*Img.rows*Img.channels());////memory of image is bigger than that of buffer, because ImPad function
+  image.data_ = memory_image;
+
+  for (int i = 0; i < Img.rows ; i++){
+      for(int j = 0; j < Img.cols ; j++){
+         image.data_[(i*Img.cols+j)*Img.channels()] = src[0].at<uchar>(i,j);
+         image.data_[(i*Img.cols+j)*Img.channels()+1] = src[1].at<uchar>(i,j);
+         image.data_[(i*Img.cols+j)*Img.channels()+2] = src[2].at<uchar>(i,j);
+     }
+  }
+  
+  //initialize edge box
+  std::cout << "222" << std::endl;
+  InitializedBox(path_model);
+  std::cout << "3333" << std::endl;
+  std::vector<cv::Vec4i> BoundingBoxes;
+  BoundingBoxes = EdgeBoxInterface(image);
[…]

### 2017-04-13 C++_Implementation/src/kcftracker.cpp

@@ -56,7 +56,7 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
         // VOT
         interp_factor = 0.018; 	// Learning Rate for the Translation Filter
         interp_factor_w_roi = 0.020; // Learning Rate for the Wide ROI Translation Filter
-        interp_factor_scale = 0.020; // Learning Rate for the Scale Filter
+        interp_factor_scale = 0.010; // Learning Rate for the Scale Filter
         sigma = 0.65;           // Gaussian Bandwith Parameter for the Gaussian Kernel in KCF
         cell_size = 4;          // Cell Size for the HoG Feature Channels
         _hogfeatures = true;
@@ -131,7 +131,23 @@ void KCFTracker::init(const cv::Rect &roi, cv::Mat image)
     train(_tmpl, 1.0); // train with initial frame - translation filter 
     trainWROI(_tmpl_w_roi,1.0); // train with initial frame - translation filter Wide ROI
     trainScale(_tmplScale,1.0); // train with initial frame - scale filter
- }
+}
+
+// Initialize tracker 
+void KCFTracker::reinit(const cv::Rect &roi, cv::Mat image)
+{
+    _roi = roi;
+    assert(roi.width >= 0 && roi.height >= 0);
+    cv::Mat tmpl = getFeatures(image, 1);      // Compute Feature Channels for the _roi
+
+    _roi_w = roi;
+    cv::Mat tmpl_w_roi = getFeaturesWROI(image, 1);      // Compute Feature Channels for the _roi
+
+    _roi_scale = roi;
+    cv::Mat tmplScale = getFeaturesScale(image, 1); // Compute Feature Channels for the Scale Filter
+}
+
+
 
 // Update position based on the new frame
 cv::Rect KCFTracker::update(cv::Mat image)
@@ -1017,20 +1033,21 @@ std::pair<int,float> KCFTracker::target_redetection(std::vector<cv::Vec4i> Bound
     float rd_max_confidence = -0.1;
     int rd_index;
     std::pair<int,float> BoxElements;
-    for(int boxIndex = 0; boxIndex < 1000; boxIndex++){
+    for(int boxIndex = 0; boxIndex < 100; boxIndex++){
 
-	// Get the Next Proposed Box
-	cv::Vec4i bb = BoundingBoxes[boxIndex];
[…]

### 2017-04-13 C++_Implementation/src/kcftracker.hpp

@@ -16,6 +16,9 @@ public:
     // Initialize tracker 
     virtual void init(const cv::Rect &roi, cv::Mat image);
     
+    // Initialize tracker 
+    virtual void reinit(const cv::Rect &roi, cv::Mat image);
+
     // Update position based on the new frame
     virtual cv::Rect update(cv::Mat image);
 

### 2017-04-13 C++_Implementation/src/runtracker.cpp

@@ -5,7 +5,6 @@
 #include <algorithm>
 #include "kcftracker.hpp"
 #include "Filter_Definition.h"
-#include "findHom.hpp"
 #include <vector>
 #include <math.h>
 #include <string>
@@ -15,12 +14,18 @@
 #include <opencv2/imgproc/imgproc.hpp>
 #include "opencv2/imgcodecs/imgcodecs.hpp"
 #include "opencv2/videoio/videoio.hpp"
-#include "opencv2/saliency.hpp"
 #include <unistd.h>
 #include <stack>
 #include <random>
+#include "../main/include/interface.h"
+#include "../tools/include/image_tools.h"
+#include "../edge/include/edge_boxes_interface.h"
+
+using namespace cv;
+using namespace std;
 
 std::stack<clock_t> tictoc_stack;
+
 ///
 /// tic and toc is used to measure the time to process an operation
 ///
@@ -78,6 +83,7 @@ void CallBackFunc(int event, int x, int y, int flags, void* userdata)
     }
 }
 
+
 int main(int argc, char* argv[])
 {
 
@@ -87,18 +93,20 @@ int main(int argc, char* argv[])
    bool FIXEDWINDOW = false;  // Fixed Window
    bool MULTISCALE = true;    // Scale Space Search Enabled
    bool SILENT = false;	      // Suppress the Outputs
-   bool LAB = true;	      // Enable or Disable Color Features
+   bool LAB = false;	      // Enable or Disable Color Features
    char szDataFile[256];
+   char gtDataFile[256];
    char szImageFile[256];
    char szSaveVideofile[256];
- 
+   char path_model[256] = "/home/buzkent/EdgeBox/model_train.txt"; 
+   
    // Terminate if less than 9 inputs are provided
-   if (argc < 5) {
+   if (argc < 7) {
       help();
       return -2;
    }
 
-   while ((opt = getopt(argc,argv,"e:d:")) != EOF) {
+   while ((opt = getopt(argc,argv,"e:d:g:")) != EOF) {
       switch(opt)
       {
          case 'e': memset(szImageFile, '\0', sizeof(szImageFile));
@@ -108,6 +116,10 @@ int main(int argc, char* argv[])
          case 'd': memset(szDataFile, '\0', sizeof(szDataFile));
             strcpy(szDataFile, optarg); 
             cout <<" Input MOV Data File: "<< optarg <<endl; 
+            break;
[…]

### 2017-04-13 C++_Implementation/src/tracker.h

@@ -10,6 +10,7 @@ public:
     virtual  ~Tracker() { }
 
     virtual void init(const cv::Rect &roi, cv::Mat image) = 0;
+    virtual void reinit(const cv::Rect &roi, cv::Mat image) = 0;
     virtual cv::Rect  update( cv::Mat image) = 0;
     virtual cv::Rect  updateWROI( cv::Mat image) = 0;
     virtual cv::Rect  updateScale( cv::Mat image) = 0;

### 2017-04-13 C++_Implementation/tools/include/conv_triangle.h

@@ -1,0 +1,31 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \conv_triangle.h
+///
+/// \Definition : Execute convolution with triangle filter.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _CONV_TRIANGLE_H_
+#define _CONV_TRIANGLE_H_
+
+///
+/// Extremely fast 2D image convolution with a triangle filter.
+///
+/// \param[in] src inputting data, such as: image after normalizing
+/// \param[in] r integer filter radius
+/// \param[in] w width of src
+/// \param[in] h height of src
+/// \param[in] d channels of src
+/// \param[out] dst smoothed image
+///
+void ConvTriangle(float* src, float* dst, int r, int w, int h, int d);
+
+// convolve I by a [1 p 1] filter (uses SSE)
+void ConvTri1(float *I, float *O, int h, int w, int d, float p, int s);
+
+// convolve I by a 2rx1 triangle filter (uses SSE)
+void ConvTri(float *I, float *O, int h, int w, int d, int r, int s);
+
+#endif

### 2017-04-13 C++_Implementation/tools/include/data_define.h

@@ -1,0 +1,307 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \file data_define.h
+///
+/// \Definition : Many classes are defined in this file, such as AuMat.
+///
+///  \author XipengCui
+///
+#ifndef AUTEL_CV_PACKAGE_DATA_DEFINE_H_
+#define AUTEL_CV_PACKAGE_DATA_DEFINE_H_
+
+#include <cstdlib>
+#include <cfloat>
+#include <cstdio>
+#include <cmath>
+#include <cstring>
+
+namespace autel{
+
+namespace computer_vision{
+
+typedef unsigned char uchar;
+typedef unsigned short ushort;
+#define AuMax(a,b)    (((a) > (b)) ? (a) : (b))
+#define AuMin(a,b)    (((a) < (b)) ? (a) : (b))
+#define AU_PI   3.1415926535897932384626433832795
+
+/// \desc Define the primitive data types
+enum AuFormat{
+  //unsigned char
+  AU_8U  = 0,
+  // char
+  AU_8S  = 1,
+  // unsigned short
+  AU_16U = 2,
+  // short
+  AU_16S = 3,
+  // int
+  AU_32S = 4,
+  // float
+  AU_32F = 5,
+  // double
+  AU_64F = 6
+};
+
+///
+/// \class Define 2-dimensional point
+///
+template <typename T>
+class AuPoint{
+public:
+  T x_, y_;
+};
+
+/// 
+/// size of two dimension
+///
+class AuSize{
+public:
+  int width_, height_;
+};
+
+///
+/// rect class
+///
+template <typename T>
+class AuRect{
+public:
+  //< the top-left corner, as well as width and height of the rectangle
+  T x_, y_, width_, height_;
+};
+
+///
+/// range class
+///
+class AuRange{
+public:
+  int start_, end_;
+};
+
+///
+/// complex class
+///
+template <typename T>
+class AuComplex{
+public:
+  //< the real and the imaginary parts
+  T real_, imaginary_;
+};
+
+///
+/// \class AuMat is a fundamental class structure. 
+///
+class AuMat{
+public:
+  //channes
+  int channels_;
+  //data type
+  int depth_;
+  //dimension
+  int dims_;
+  //height, width
+  int rows_, cols_;
+  //pointer to the data
+  unsigned char* data_;
+  //[0]: width step; [1]: Bytes of every pixel
+  unsigned int step_[2];
+  // no used
[…]

### 2017-04-13 C++_Implementation/tools/include/gradient.h

@@ -1,0 +1,60 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \gradient.h
+///
+/// \Definition : Calculate gradient magnitude and gradient hist;
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _GRADIENT_H_
+#define _GRADIENT_H_
+#include "data_define.h"
+#include "conv_triangle.h"
+#include "wrappers.h"
+#include "string.h"
+#include <math.h>
+#include "sse.h"
+
+using namespace autel;
+using namespace computer_vision;
+
+///
+/// Compute gradient magnitude and orientation at each image location.
+///
+/// \param[in] img inputting image
+/// \param[in] channel if>0 color channel to use for gradient computation
+/// \param[in] norm_rad normalization radius (no normalization if 0)
+/// \param[in] norm_const normalization constant
+/// \param[in] is_layout if true, the image will be divided into several layers
+/// \param[out] M gradient magnitude at each location
+/// \param[out] O approximate gradient orientation modulo PI
+///
+void GradientMag(AuMat& img, float* M, float* O, int channel, int norm_rad, float norm_const, char is_layout);
+
+///
+/// Compute oriented gradient histograms.
+///
+/// \param[in] M gradient magnitude at each location
+/// \param[in] O gradient orientation in range defined by param flag
+/// \param[in] bin spatial bin size
+/// \param[in] nOrients number of orientation bins
+/// \param[in] softBin set soft binning (odd: spatial=soft, >=0: orient=soft)
+/// \param[out] H gradient histograms
+///
+void GradientHist(float *M, float *O, float *H, int h, int w,
+  int bin, int nOrients, int softBin);
+
+///
+/// Compute numerical gradients along x and y directions.
+///
+/// \param[in] I inputting image
+/// \param[in] w width of E
+/// \param[in] h height of E
+/// \param[in] d channel of E
+/// \param[out] G_x x-gradient (horizontal)
+/// \param[out] G_y y-gradient (vertical)
+///
+void Gradient2(float* I, float* G_x, float* G_y, int w, int h, int d);
+
+#endif

### 2017-04-13 C++_Implementation/tools/include/image_tools.h

@@ -1,0 +1,83 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \image_tools.h
+///
+/// \Definition : Image fundamental functions are defined here;
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _IMAGE_TOOLS_H_
+#define _IMAGE_TOOLS_H_
+
+#include "data_define.h"
+using namespace autel;
+using namespace computer_vision;
+
+void Resize(unsigned char* src, unsigned char* dst, AuSize src_size, int src_step, int cn, AuSize dst_size, int dst_step, uchar* memoryPara);
+void ResizeROI_whynotuse(unsigned char* src, unsigned char* dst, AuRect<int> roi, AuSize src_size, int src_step, int cn, AuSize dst_size, int dst_step);
+
+///
+/// Resize size of YUV image to any size.
+///
+/// \param[in] src_y: Y data of YUV image
+/// \param[in] src_uv: U and V data of YUV image
+/// \param[in] roi: patch in YUV image, here it is not used.
+/// \param[in] src_size: width and height of source image(YUV)
+/// \param[in] src_width: width of source image
+/// \param[in] cn: channels
+/// \param[in] dst_size: width and height of output image
+/// \param[in] dst_width: width of output image
+/// \param[in] data_format: data type
+/// \param[out] dst_y: Y data of output image
+/// \param[out] dst_uv: U and V data of output image
+///
+void ResizeYUVToYUV(unsigned char* src_y, unsigned char* src_uv, AuRect<int> roi, unsigned char* dst_y, unsigned char* dst_uv,
+    AuSize src_size, int src_width, int cn, AuSize dst_size, int dst_width, int data_format);
+///
+/// Pad an image along its four boundaries
+/// param[in]: img: old image
+/// param[in]: p: size of img: img.cols + p[2]+p[3], img.rows+p[0]+p[1];
+/// param[in]: style: how to fill data
+/// param[out]: img: padded image
+///
+void ImPad(AuMat& img, int* p, char* style);
+
+///
+/// Convert RGB image to other color spaces
+/// param[in]: I: RGB image
+/// param[in]: n: number of image pixels
+/// param[in]: nrm: normalizing coefficient
+/// param[out]: J: other color spaces
+///
+void RGB2LUV(AuMat& I, AuMat* J, int n, float nrm);
+
+///
+/// Normalize image
+/// param[in]: I: image
[…]

### 2017-04-13 C++_Implementation/tools/include/sse.h

@@ -1,0 +1,75 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \sse.h
+///
+/// \Definition : if use SSE code, please open this macro '#define SSE2'
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _SSE_HPP_
+#define _SSE_HPP_
+
+// use SSE2
+//#define SSE2
+
+#if defined(SSE2)
+
+#include <emmintrin.h> // SSE2:<e*.h>, SSE3:<p*.h>, SSE4:<s*.h>
+
+#define RETf inline __m128
+#define RETi inline __m128i
+
+// set, load and store values
+RETf SET( const float &x ) { return _mm_set1_ps(x); }
+RETf SET( float x, float y, float z, float w ) { return _mm_set_ps(x,y,z,w); }
+RETi SET( const int &x ) { return _mm_set1_epi32(x); }
+RETf LD( const float &x ) { return _mm_load_ps(&x); }
+RETf LDu( const float &x ) { return _mm_loadu_ps(&x); }
+RETf STR( float &x, const __m128 y ) { _mm_store_ps(&x,y); return y; }
+RETf STR1( float &x, const __m128 y ) { _mm_store_ss(&x,y); return y; }
+RETf STRu( float &x, const __m128 y ) { _mm_storeu_ps(&x,y); return y; }
+RETf STR( float &x, const float y ) { return STR(x,SET(y)); }
+
+// arithmetic operators
+RETi ADD( const __m128i x, const __m128i y ) { return _mm_add_epi32(x,y); }
+RETf ADD( const __m128 x, const __m128 y ) { return _mm_add_ps(x,y); }
+RETf ADD( const __m128 x, const __m128 y, const __m128 z ) {
+  return ADD(ADD(x,y),z); }
+RETf ADD( const __m128 a, const __m128 b, const __m128 c, const __m128 &d ) {
+  return ADD(ADD(ADD(a,b),c),d); }
+RETf SUB( const __m128 x, const __m128 y ) { return _mm_sub_ps(x,y); }
+RETf MUL( const __m128 x, const __m128 y ) { return _mm_mul_ps(x,y); }
+RETf MUL( const __m128 x, const float y ) { return MUL(x,SET(y)); }
[…]

### 2017-04-13 C++_Implementation/tools/include/wrappers.h

@@ -1,0 +1,30 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \wrappers.h
+///
+/// \Definition : aligned memory allocation
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#ifndef _WRAPPERS_HPP_
+#define _WRAPPERS_HPP_
+
+#include <stdlib.h>
+
+// platform independent aligned memory allocation (see also alFree)
+static void* alMalloc(size_t size, int alignment) {
+  const size_t pSize = sizeof(void*), a = alignment-1;
+  void *raw = malloc(size + a + pSize);
+  void *aligned = (void*) (((size_t) raw + pSize + a) & ~a);
+  *(void**) ((size_t) aligned-pSize) = raw;
+  return aligned;
+}
+
+// platform independent alignned memory de-allocation (see also alMalloc)
+static void alFree(void* aligned) {
+  void* raw = *(void**)((char*)aligned-sizeof(void*));
+  free(raw);
+}
+
+#endif

### 2017-04-13 C++_Implementation/tools/src/conv_triangle.cpp

@@ -1,0 +1,259 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \conv_triangle.cpp
+///
+/// \Definition : Execute convolution with triangle filter.
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#include "../include/conv_triangle.h"
+#include "../include/wrappers.h"
+#include "../include/sse.h"
+
+// convolve one column of I by a 2rx1 triangle filter
+void ConvTriY(float *I, float *O, int h, int r, int s) {
+  r++; float t, u; int j, r0 = r - 1, r1 = r + 1, r2 = 2 * h - r, h0 = r + 1, h1 = h - r + 1, h2 = h;
+  u = t = I[0]; for (j = 1; j<r; j++) u += t += I[j]; u = 2 * u - t; t = 0;
+  if (s == 1) {
+    O[0] = u; j = 1;
+    for (; j<h0; j++) O[j] = u += t += I[r - j] + I[r0 + j] - 2 * I[j - 1];
+    for (; j<h1; j++) O[j] = u += t += I[j - r1] + I[r0 + j] - 2 * I[j - 1];
+    for (; j<h2; j++) O[j] = u += t += I[j - r1] + I[r2 - j] - 2 * I[j - 1];
+  }
+  else {
+    int k = (s - 1) / 2; h2 = (h / s)*s; if (h0>h2) h0 = h2; if (h1>h2) h1 = h2;
+    if (++k == s) { k = 0; *O++ = u; } j = 1;
+    for (; j<h0; j++) { u += t += I[r - j] + I[r0 + j] - 2 * I[j - 1]; if (++k == s){ k = 0; *O++ = u; } }
+    for (; j<h1; j++) { u += t += I[j - r1] + I[r0 + j] - 2 * I[j - 1]; if (++k == s){ k = 0; *O++ = u; } }
+    for (; j<h2; j++) { u += t += I[j - r1] + I[r2 - j] - 2 * I[j - 1]; if (++k == s){ k = 0; *O++ = u; } }
+  }
+}
+
+// convolve I by a 2rx1 triangle filter (uses SSE)
+void ConvTri(float *I, float *O, int h, int w, int d, int r, int s)
+{
+#if defined(SSE2)
[…]

### 2017-04-13 C++_Implementation/tools/src/data_define.cpp

@@ -1,0 +1,1854 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \file data_define.cpp
+///
+/// \Definition : Many classes are defined in this file, such as AuMat.
+///
+///  \author XipengCui
+///  \Date : Created on: Feb 20, 2017
+///
+#include "../include/data_define.h"
+#include <algorithm>
+#include <limits>
+
+namespace autel{
+
+namespace computer_vision{
+
+#define Lambda 0.000001
+
+AuMat::AuMat()
+{
+  this->rows_ = 0;
+  this->cols_ = 0;
+  this->channels_ = 0;
+  this->depth_ = 0;
+  this->data_ = 0;
+  this->is_getMem_ = 0;
+  this->step_[1] = 0;
+  this->step_[0] = 0;
+  this->dims_ = 0;
+}
+
+AuMat::AuMat(int rows, int cols, int cn, int depth, uchar* data)
+{
+  this->rows_ = rows;
+  this->cols_ = cols;
+  this->channels_ = cn;
+  this->dims_ = 2;
+  this->depth_ = depth;
+  this->data_ = data;
+  this->is_getMem_ = 0;
+  this->step_[1] = this->channels_ * this->depth_;
+  this->step_[0] = this->step_[1] * this->cols_;
+}
+
+AuMat::AuMat(int rows, int cols, int cn, int depth)
+{
+  this->rows_ = rows;
+  this->cols_ = cols;
+  this->channels_ = cn; //channels
+  this->dims_ = 2;
+  this->depth_ = depth;//bytes of every pixel;
+  if (depth <= 1)//char or unsigned char
+  {
+    this->data_ = new unsigned char[rows*cols*this->channels_];
+    this->step_[1] = this->channels_;
+  }
+  else if (depth <= 3) // short or unsigned short
+  {
+    this->data_ = new unsigned char[rows*cols*this->channels_*sizeof(short)];
+    this->step_[1] = this->channels_*sizeof(short);
+  }
+  else if (depth <= 5) // int or float
+  {
+    this->data_ = new unsigned char[rows*cols*this->channels_*sizeof(int)];
+    this->step_[1] = this->channels_*sizeof(int);
+  }
+  else // double
+  {
[…]

### 2017-04-13 C++_Implementation/tools/src/gradient.cpp

@@ -1,0 +1,469 @@
+/// Copyright (c) 2016 AutelRobotics. All Rights Reserved
+///
+/// \gradient.h
+///
+/// \Definition : Calculate gradient magnitude and gradient hist;
+///
+///  \author XipengCui
+///  \Date : Created on: Jan 1, 2017
+///
+#include "../include/gradient.h"
+
+#define PI 3.14159265f
+
+// compute x and y gradients for just one column
+void grad1(float *I, float *Gx, float *Gy, int h, int w, int x) {
+
+#if defined(SSE2)
+  int y, y1; float *Ip, *In, r; __m128 *_Ip, *_In, *_G, _r;
+  // compute column of Gx
+  Ip = I - h; In = I + h; r = .5f;
+  if (x == 0) { r = 1; Ip += h; }
+  else if (x == w - 1) { r = 1; In -= h; }
+  if (h<4 || h % 4>0 || (size_t(I) & 15) || (size_t(Gx) & 15)) {
+    for (y = 0; y<h; y++) *Gx++ = (*In++ - *Ip++)*r;
+  }
+  else {
+    _G = (__m128*) Gx; _Ip = (__m128*) Ip; _In = (__m128*) In; _r = SET(r);
+    for (y = 0; y<h; y += 4) *_G++ = MUL(SUB(*_In++, *_Ip++), _r);
+  }
+  // compute column of Gy
+#define GRADY(r) *Gy++=(*In++-*Ip++)*r;
+  Ip = I; In = Ip + 1;
+  // GRADY(1); Ip--; for(y=1; y<h-1; y++) GRADY(.5f); In--; GRADY(1);
+  y1 = ((~((size_t)Gy) + 1) & 15) / 4; if (y1 == 0) y1 = 4; if (y1>h - 1) y1 = h - 1;
+  GRADY(1); Ip--; for (y = 1; y<y1; y++) GRADY(.5f);
+  _r = SET(.5f); _G = (__m128*) Gy;
+  for (; y + 4<h - 1; y += 4, Ip += 4, In += 4, Gy += 4)
+    *_G++ = MUL(SUB(LDu(*In), LDu(*Ip)), _r);
+  for (; y<h - 1; y++) GRADY(.5f); In--; GRADY(1);
+#undef GRADY
+
+#else
+  int y, y1;
+  float *Ip, *In, r;
+
+  // compute column of Gx
+  Ip = I - h;
+  In = I + h;
+  r = .5f;
+  if(x == 0){
+  r = 1;
[…]

### 2017-04-13 C++_Implementation/src/kcftracker.hpp
Shell File Added to Run Through All the Videos at Single Run and Precision Metric Added

@@ -7,6 +7,9 @@
 #define _OPENCV_KCFTRACKER_HPP_
 #endif
 
+
+void PrecisionCurve(std::vector<float> EucDistance);
+
 class KCFTracker : public Tracker
 {
 public:

### 2017-04-13 draft.tex
Revised the draft to update the plan.

@@
 \item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
-\item Re-detection for re-initialization
+\item Re-detection for re-initialization: Modules for reliably
+  detecting target-lost, for extensively searching the lost target,
+  and for picking up the same target with a help from an appearance
+  model or other models.
+\begin{itemize}
+\item To filter out unlikely box proposals,
+\begin{itemize}
+\item Use a prior information about box, our outputs, dimensions
+  (e.g., a combination of width and height, aspect ratio, etc.)
+\item Use the information about the trajectory of the target before we
+  lose the target.
+\end{itemize}
+\item MTH: revisited
+\item To make a box tighter, generate our own box proposals based on
+  the locations of top $k$ box proposals from object proposal methods,
+  e.g., Edge Box.
+\end{itemize}
 \end{itemize}
@@
   vanilla-KCF w/ a fixed scale, KCF w/ three different scales, STC,
+  Struck
 \begin{itemize}
+\item Visual tracker benchmark (VTB)
 \item DTB-70: w/ and w/o motion estimation,

### 2017-04-14 C++_Implementation/src/avgPrecision.cpp
Average Precision Script Added - Precision metric is completed

@@ -1,0 +1,59 @@
+#include <iostream>
+#include <fstream>
+#include <sstream>
+#include <iomanip>
+#include <iterator>
+#include <vector>
+#include <string>
+#include <unistd.h>
+#include <dirent.h>
+
+int main(int argc, char* argv[]){
+
+    float indPrecision;
+    std::string value;
+    std::vector<float> avgPrecision;
+    // Parse through all the Text Files and Compute Average Precision
+    struct dirent *pDirent;
+    DIR *pDir = opendir("/home/buzkent/Downloads/Results/");
+    int fileFirst = 0;
+    while ((pDirent = readdir(pDir)) != NULL) {
+
+       std::string fileName = pDirent->d_name;
+       std::string homeDir = "/home/buzkent/Downloads/Results/";
+       std::string fullDir = homeDir.append(fileName);
+       std::ifstream prFile(fullDir);
+       std::string toAvoid = ".";
+       if (fileName.compare(toAvoid) == 0 || fileName.compare("..") == 0 || fileName.compare("AveragePrecision") == 0){
+          continue;
+       }
+       if (!prFile)
+       {
+         return 0;
+       }
+       int index = 0;
+       char ch;
+       while (prFile >> indPrecision){
+	   if (fileFirst == 0){
+              avgPrecision.push_back(indPrecision);
+           }
+           else{
+              avgPrecision[index] += indPrecision;
+              index++;
+           }
+       }
+       fileFirst++;
+       
+    }
+    closedir(pDir);
+
+    // Save the Results into Another Text File
+    for (int i = 0; i < avgPrecision.size() ; i++){
+        avgPrecision[i] /= fileFirst;
+    }
+    std::ofstream output_file("/home/buzkent/Downloads/Results/AveragePrecision/Precision.txt");
+    std::ostream_iterator<float> output_iterator(output_file, "\n");
+    std::copy(avgPrecision.begin(), avgPrecision.end(), output_iterator);
+  
+    return 0;
+}

### 2017-04-14 C++_Implementation/src/kcftracker.cpp

@@ -37,6 +37,8 @@ Outputs of update():
 #include "fhog.hpp"
 #include "labdata.hpp"
 #include <unistd.h>
+#include <iterator>
+#include <fstream>
 #endif
 
 // Constructor
@@ -1192,7 +1194,7 @@ cv::Rect_<float> KCFTracker::applyHomography(cv::Mat homography, cv::Mat image, 
 }
 
 
-void PrecisionCurve(std::vector<float> EucDistance)
+void PrecisionCurve(std::vector<float> EucDistance, std::string prDataFile)
 {
     std::vector<float> prScore; /// \param[in] prScore vector of vector to store precision
     for (int i = 1; i < 101; i++){      /// \param[in] i Spatial Threshold
@@ -1205,6 +1207,9 @@ void PrecisionCurve(std::vector<float> EucDistance)
         prScore.push_back(double(precision[0])/EucDistance.size()); // Precision Score for the Video - TBM
         std::cout << prScore[i-1] << "---------------" << i << std::endl;
     }
+    // Save into the Corresponding Text File
+    std::ofstream output_file("/home/buzkent/Downloads/Results/"+prDataFile+".txt");
+    std::ostream_iterator<float> output_iterator(output_file, "\n");
+    std::copy(prScore.begin(), prScore.end(), output_iterator);
+
 }
-
-

### 2017-04-14 C++_Implementation/src/kcftracker.hpp

@@ -2,13 +2,13 @@
 
 #include "tracker.h"
 #include "opencv2/opencv.hpp"
-
+#include <string>
 #ifndef _OPENCV_KCFTRACKER_HPP_
 #define _OPENCV_KCFTRACKER_HPP_
 #endif
 
 
-void PrecisionCurve(std::vector<float> EucDistance);
+void PrecisionCurve(std::vector<float> EucDistance, std::string prDataFile);
 
 class KCFTracker : public Tracker
 {

### 2017-04-14 C++_Implementation/src/runtracker.cpp

@@ -99,14 +99,15 @@ int main(int argc, char* argv[])
    char szImageFile[256];
    char szSaveVideofile[256];
    char path_model[256] = "/home/buzkent/EdgeBox/model_train.txt"; 
-   
+   char prDataFile[256];   
+
    // Terminate if less than 9 inputs are provided
-   if (argc < 7) {
+   if (argc < 9) {
       help();
       return -2;
    }
 
-   while ((opt = getopt(argc,argv,"e:d:g:")) != EOF) {
+   while ((opt = getopt(argc,argv,"e:d:g:p:")) != EOF) {
       switch(opt)
       {
          case 'e': memset(szImageFile, '\0', sizeof(szImageFile));
@@ -121,6 +122,9 @@ int main(int argc, char* argv[])
             strcpy(gtDataFile, optarg);
             cout <<" Input MOV Data File: "<< optarg <<endl;
             break;
+        case 'p': memset(prDataFile, '\0', sizeof(prDataFile));
+            strcpy(prDataFile, optarg);
+            cout <<" Input MOV Data File: "<< optarg <<endl;
       }
    }
 
@@ -337,6 +341,8 @@ int main(int argc, char* argv[])
          cv::waitKey(2);
       }
    }
+
    // Estimate Precision Curve
-   PrecisionCurve(EucDistance);
+   string performanceFile = prDataFile;
+   PrecisionCurve(EucDistance, prDataFile);
 }

### 2017-04-14 C++_Implementation/src/avgPrecision.cpp
Precision and Success Overlap Metrics Finished

@@ -10,13 +10,15 @@
 
 int main(int argc, char* argv[]){
 
-    float indPrecision;
-    std::string value;
-    std::vector<float> avgPrecision;
+    float indPrecision, indSuccessOverlap;
+    std::vector<std::vector<float> > avgPrecision(2);
+    std::ofstream output_file("/home/buzkent/Downloads/Results/AveragePrecision/Precision.txt");
+
     // Parse through all the Text Files and Compute Average Precision
     struct dirent *pDirent;
     DIR *pDir = opendir("/home/buzkent/Downloads/Results/");
     int fileFirst = 0;
+    char ch;
     while ((pDirent = readdir(pDir)) != NULL) {
 
        std::string fileName = pDirent->d_name;
@@ -33,12 +35,14 @@ int main(int argc, char* argv[]){
        }
        int index = 0;
        char ch;
-       while (prFile >> indPrecision){
+       while (prFile >> indPrecision >> ch >> indSuccessOverlap){
 	   if (fileFirst == 0){
-              avgPrecision.push_back(indPrecision);
+              avgPrecision[0].push_back(indPrecision);
+              avgPrecision[1].push_back(indSuccessOverlap);
            }
            else{
-              avgPrecision[index] += indPrecision;
+              avgPrecision[0][index] += indPrecision;
+              avgPrecision[1][index] += indSuccessOverlap;
               index++;
            }
        }
@@ -48,12 +52,15 @@ int main(int argc, char* argv[]){
     closedir(pDir);
 
     // Save the Results into Another Text File
-    for (int i = 0; i < avgPrecision.size() ; i++){
-        avgPrecision[i] /= fileFirst;
+    for (int i = 0; i < avgPrecision[0].size() ; i++){
+        avgPrecision[0][i] /= fileFirst;
+        avgPrecision[1][i] /= fileFirst;
+        output_file << avgPrecision[0][i] << "," << avgPrecision[1][i];
+        output_file << std::endl;       
     }
-    std::ofstream output_file("/home/buzkent/Downloads/Results/AveragePrecision/Precision.txt");
-    std::ostream_iterator<float> output_iterator(output_file, "\n");
-    std::copy(avgPrecision.begin(), avgPrecision.end(), output_iterator);
+//    std::ofstream output_file("/home/buzkent/Downloads/Results/AveragePrecision/Precision.txt");
+//    std::ostream_iterator<float> output_iterator(output_file, "\n");
[…]

### 2017-04-14 C++_Implementation/src/kcftracker.cpp

@@ -46,19 +46,19 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
 {
 
     // Parameters equal in all cases
-    lambda = 0.0001;    // Regularization Parameter for the Regression Task
-    padding = 2.00;     // The ROI parameter to get n times larger area than the Selected Target - Translation Filter
-    padding_w_roi = 3.00; // The Wider ROI Parameter for the Second Translation Filter
-    padding_scale = 1.00;   // The ROI Parameter for the scale filter
-    output_sigma_factor = 0.125;    // Variance Parameter for the Desired Translation Filter Response
-    output_sigma_factor_w_roi = 0.125 * 1.5; // Variance Parameter for the Wide ROI translation filter Response
-    output_sigma_factor_scale = 0.125 * 0.5; // Variance Parameter for the Desired Scale Filter Response
+    lambda = 0.0001;    		// Regularization Parameter for the Regression Task
+    padding = 2.00;     		// The ROI parameter to get n times larger area than the Selected Target - Translation Filter
+    padding_w_roi = 3.00; 		// The Wider ROI Parameter for the Second Translation Filter
+    padding_scale = 1.00;   		// The ROI Parameter for the scale filter
+    output_sigma_factor = 0.125;    	// Variance Parameter for the Desired Translation Filter Response
+    output_sigma_factor_w_roi = 0.125 * 1.0; 	// Variance Parameter for the Wide ROI translation filter Response
+    output_sigma_factor_scale = 0.125 * 1.0; 	// Variance Parameter for the Desired Scale Filter Response
 
     if (hog) {    // HOG
         // VOT
-        interp_factor = 0.018; 	// Learning Rate for the Translation Filter
-        interp_factor_w_roi = 0.020; // Learning Rate for the Wide ROI Translation Filter
-        interp_factor_scale = 0.010; // Learning Rate for the Scale Filter
+        interp_factor = 0.012; 	// Learning Rate for the Translation Filter
+        interp_factor_w_roi = 0.012; // Learning Rate for the Wide ROI Translation Filter
+        interp_factor_scale = 0.015; // Learning Rate for the Scale Filter
         sigma = 0.65;           // Gaussian Bandwith Parameter for the Gaussian Kernel in KCF
         cell_size = 4;          // Cell Size for the HoG Feature Channels
         _hogfeatures = true;
[…]

### 2017-04-14 C++_Implementation/src/kcftracker.hpp

@@ -7,8 +7,7 @@
 #define _OPENCV_KCFTRACKER_HPP_
 #endif
 
-
-void PrecisionCurve(std::vector<float> EucDistance, std::string prDataFile);
+void PrecisionCurve(std::vector<std::vector<float>> EucDistance, std::string prDataFile);
 
 class KCFTracker : public Tracker
 {

### 2017-04-14 C++_Implementation/src/runtracker.cpp

@@ -89,7 +89,7 @@ int main(int argc, char* argv[])
 
    // Define Parameters for the Kernelized Correlation Filter Tracker - Options
    int opt, verbose = 0;
-   bool HOG = true;   // Enable HoG Features
+   bool HOG = true;  	      // Enable HoG Features
    bool FIXEDWINDOW = false;  // Fixed Window
    bool MULTISCALE = true;    // Scale Space Search Enabled
    bool SILENT = false;	      // Suppress the Outputs
@@ -191,7 +191,7 @@ int main(int argc, char* argv[])
    char ch;
 
    // Declare A Vector for Euclidean Distance
-   std::vector<float> EucDistance;
+   std::vector<std::vector<float>> Metrics(2);
 #ifdef _USE_VIDEO_INPUT__
    while (1) // Read the Next Frame
    {
@@ -242,22 +242,23 @@ int main(int argc, char* argv[])
         /// -------------------- UPDATE STEP --------------------------------------------
         /// Use Translation and Scale Filter Interchangeably
         tracker.PSR_scale = 10;
+        tracker.PSR_wroi  = 10;
         float PSR;
-        if (nFrames % 5 == 1)
+        if (nFrames % 5 > 0)
         {
             // Apply Homography to the Track Position at Previous Frame
             // tracker._roi_w = tracker.applyHomography(homography, frame, tracker._roi_w);
             result = tracker.updateWROI(frame);  // Estimate Translation using Wider ROI
             PSR = tracker.PSR_wroi;
-        }
-        if (nFrames % 5 > 1)
+        }/*
+        if ((nFrames % 5 > 1))
         {
             // Apply Homography to the Track Position at Previous Frame
             // tracker._roi = tracker.applyHomography(homography, frame, tracker._roi);
             result = tracker.update(frame);      // Estimate Translation
             PSR = tracker.PSR_sroi;
-        }
-        if ( nFrames % 5 == 0)
+        }*/
+        if (nFrames % 5 == 0)
         {
             // Apply Homography to the Track Position at Previous Frame
             // tracker._roi_scale = tracker.applyHomography(homography, frame, tracker._roi_scale);
@@ -290,8 +291,8 @@ int main(int argc, char* argv[])
[…]

### 2017-04-14 C++_Implementation/src/kcftracker.cpp
Precision and Success Overlap Metrics Finished

@@ -37,6 +37,8 @@ Outputs of update():
 #include "fhog.hpp"
 #include "labdata.hpp"
 #include <unistd.h>
+#include <iterator>
+#include <fstream>
 #endif
 
 // Constructor
@@ -44,19 +46,19 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
 {
 
     // Parameters equal in all cases
-    lambda = 0.0001;    // Regularization Parameter for the Regression Task
-    padding = 2.00;     // The ROI parameter to get n times larger area than the Selected Target - Translation Filter
-    padding_w_roi = 3.00; // The Wider ROI Parameter for the Second Translation Filter
-    padding_scale = 1.00;   // The ROI Parameter for the scale filter
-    output_sigma_factor = 0.125;    // Variance Parameter for the Desired Translation Filter Response
-    output_sigma_factor_w_roi = 0.125 * 1.5; // Variance Parameter for the Wide ROI translation filter Response
-    output_sigma_factor_scale = 0.125 * 0.5; // Variance Parameter for the Desired Scale Filter Response
+    lambda = 0.0001;    		// Regularization Parameter for the Regression Task
+    padding = 2.00;     		// The ROI parameter to get n times larger area than the Selected Target - Translation Filter
+    padding_w_roi = 3.00; 		// The Wider ROI Parameter for the Second Translation Filter
+    padding_scale = 1.00;   		// The ROI Parameter for the scale filter
+    output_sigma_factor = 0.125;    	// Variance Parameter for the Desired Translation Filter Response
+    output_sigma_factor_w_roi = 0.125 * 1.0; 	// Variance Parameter for the Wide ROI translation filter Response
+    output_sigma_factor_scale = 0.125 * 1.0; 	// Variance Parameter for the Desired Scale Filter Response
 
     if (hog) {    // HOG
         // VOT
-        interp_factor = 0.018; 	// Learning Rate for the Translation Filter
-        interp_factor_w_roi = 0.020; // Learning Rate for the Wide ROI Translation Filter
-        interp_factor_scale = 0.010; // Learning Rate for the Scale Filter
+        interp_factor = 0.012; 	// Learning Rate for the Translation Filter
+        interp_factor_w_roi = 0.012; // Learning Rate for the Wide ROI Translation Filter
+        interp_factor_scale = 0.015; // Learning Rate for the Scale Filter
[…]

### 2017-04-14 C++_Implementation/src/kcftracker.hpp

@@ -2,13 +2,12 @@
 
 #include "tracker.h"
 #include "opencv2/opencv.hpp"
-
+#include <string>
 #ifndef _OPENCV_KCFTRACKER_HPP_
 #define _OPENCV_KCFTRACKER_HPP_
 #endif
 
-
-void PrecisionCurve(std::vector<float> EucDistance);
+void PrecisionCurve(std::vector<std::vector<float>> EucDistance, std::string prDataFile);
 
 class KCFTracker : public Tracker
 {

### 2017-04-16 draft.tex
Revised the introduction.

--- 2017-04-12 draft.tex
@@
 \begin{comment}
-Maybe the goal of this work is to public a journal paper about a
-practical solution for a drone to follow a single target. For this, we need
+Maybe the goal of this work is to publish a journal paper about a
+practical solution for a drone to follow a single target. For this, we
+need some descriptions on
 \begin{itemize}
@@
 For the BMVC-17 submission, we're going to just focus on the first
-part. This is because we need to build a drone for the second part.
+part -- a vision-based, single target tracking algorithm. This is
+because we need to build a drone for the second part.
 \end{comment}
@@
 methods that primarily concerned about learning the appearance of the
-target. The recent examples of the tracking-by-detection algorithms
-include Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
+target.
+
+The recent examples of the tracking-by-detection algorithms include
+Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
 Instance Learning \cite{babenko2009visual}, Correlation Filter based
@@
 
+\item \textbf{Single-Target Tracking in High-Speed} To be practical,
+  the execution time of an object tracking is important. We proposed a
+  new object tracking algorithm that is a collection of kernelized
+  correlation filters (KCF). Each of KCFs is designed to address two
+  challenges of object tracking: scale and translation. We also
+  incorporate a Bayes filter to prevent from being drift.
+
+\item \textbf{Re-Detection} A target loss is inevitable in object
+  tracking. To cope with this, we developed a new target, re-detection
+  that reliably detects when to lose the target and effectively
+  re-detect the lost target. {\it How we can show how good our
+    re-detection method is?}
+
+\begin{comment}
 \item We build a highly efficient ($\geq300$ fps) scale adaptive
@@
   target and the camera-platform can be preserved.
+\end{comment}
 

### 2017-04-17 draft.tex
Revised the introduction and structure; cleaned up the bibfile.

@@
 \usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
-\usepackage{comment}
+\usepackage{comment, url}
 
@@
 \end{itemize}
+
+A proliferation of unmanned vehicle technologies has ever increased
+interest on deployment of computer vision technologies on mobile
+platforms. For example, an unmanned air vehicle (UAV) equipped with
+object tracking would make it more useful in the application of
+monitoring/surveillance/surveying on private
+properties/wild-life/crop, video recording on sports/movies/events,
+many others. In this paper, we propose an object tracking algorithm
+that could run on any embedded systems with small form factors.
 
@@
 
+%---------------------------------------------------------------------- 
+\section{{\it E}nKCF: Ensemble of Kernelized Correlation Filters}
+%----------------------------------------------------------------------
+
 % ---------------------------------------------------------
-\section{Kernelized Correlation Filter Tracker}
-\label{KCF}
+\subsection{Kernelized Correlation Filter Tracker} \label{KCF}
 % ---------------------------------------------------------
@@
 %-------------------------------------------------------------------
-\section{Multiple Kernelized Correlation Filter Based Tracking}
-\label{sc:MKCF}
+\subsection{Multiple Kernelized Correlation Filter Based Tracking} \label{sc:MKCF}
 %------------------------------------------------------------------
@@
 
-\section{Geometry Estimation between Target and Drone}
-\label{sc:Geometry}
+%\section{Geometry Estimation between Target and Drone}
+%\label{sc:Geometry}
 
-\section{Experiments}
-\label{sc:Experiments}
+%----------------------------------------------------------------------
+\section{Experiments} \label{sc:Experiments}
+%---------------------------------------------------------------------- 
+To verify the usefulness of our algorithm, we ran our algorithm using
+three publicly available dataset:
+VOT2015 \footnote{\url{http://www.votchallenge.net/}},
+OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
+UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
 
-\section{Conclusion}
-\label{sc:Conclusion}
+%---------------------------------------------------------------------- 
+\section{Conclusion} \label{sc:Conclusion}
+%----------------------------------------------------------------------
+
 %--------------

### 2017-04-17 draft.tex
Cleaned up the list of the tracking methods to compare.

@@
 \item Experiment: Detail the data, and experimental setup; results and findings
-\item {\it E}nKCF, Naive{\it E}nKCF, ${\it E}nKCF_{+RD}$, LCT, DSST,
-  vanilla-KCF w/ a fixed scale, KCF w/ three different scales, STC,
-  Struck
+\item Will compare the performance of {\it E}nKCF, Naive{\it E}nKCF,
+  ${\it E}nKCF_{+RD}$ with those of the following tracking methods.
+\begin{itemize}
+\item LCT (Long-term Correlation Tracking),
+\item vanilla-KCF w/ a fixed scale,
+\item vanilla-KCF w/ three different scales,
+\item MEEM (Multiple Experts using Entropy Minimization)
+\item SAMF (Scale Adaptive KCF)
+\item STC (fast tracking via Spatio-Temporal Context learning),
+\item Struck (Structured Output Tracking with Kernels)
+\end{itemize}
 \begin{itemize}

### 2017-04-21 draft.tex

@@
 \begin{itemize}
-\item LCT (Long-term Correlation Tracking),
 \item vanilla-KCF w/ a fixed scale,
 \item vanilla-KCF w/ three different scales,
+\item LCT (Long-term Correlation Tracking) \cite{ma2015long}: Temporal
+  correlation of a target over frames; a pyramid for different scales;
+  re-detection w/ an appearance classifier (i.e., a naive Bayes w/
+  random fern features in combination of sliding window). Temporal
+  context regressor for translation over significant deformation and
+  target regressor for scale variation.
 \item MEEM (Multiple Experts using Entropy Minimization)
+  \cite{zhang2014meem}.
 \item SAMF (Scale Adaptive KCF)
-\item STC (fast tracking via Spatio-Temporal Context learning),
+\item STC (fast tracking via Spatio-Temporal Context learning)
+  \cite{zhang2014fast}: 
 \item Struck (Structured Output Tracking with Kernels)
@@
 A proliferation of unmanned vehicle technologies has ever increased
-interest on deployment of computer vision technologies on mobile
-platforms. For example, an unmanned air vehicle (UAV) equipped with
-object tracking would make it more useful in the application of
-monitoring/surveillance/surveying on private
+interest on deployment of computer vision algorithms on embedded or
+mobile platforms. For example, an unmanned air vehicle (UAV) equipped
+with object or feature following would make it more useful in the
+application of monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
 many others. In this paper, we propose an object tracking algorithm
-that could run on any embedded systems with small form factors.
+that aims at running on any embedded or mobile platforms. In
+particular,
+
+{\it We may need to change this introductory sentence based on the
+  results.}
 

### 2017-04-21 C++_Implementation/src/avgPrecision.cpp
Redetection Added to Experiment on BING Instead of EdgeBox - Experimental Code

@@ -58,9 +58,18 @@ int main(int argc, char* argv[]){
         output_file << avgPrecision[0][i] << "," << avgPrecision[1][i];
         output_file << std::endl;       
     }
-//    std::ofstream output_file("/home/buzkent/Downloads/Results/AveragePrecision/Precision.txt");
-//    std::ostream_iterator<float> output_iterator(output_file, "\n");
-//    std::copy(avgPrecision.begin(), avgPrecision.end(), output_iterator);
-  
+
+    // Compute the Area Under Curve for Precision and Success Overlap
+    float aucPrecision = 0;
+    float aucSuccess = 0;
+    for (int i = 0; i < avgPrecision[0].size() ; i++){
+        if ( i <= 50 ){
+            std::cout << avgPrecision[0][i] << std::endl;
+            aucPrecision += avgPrecision[0][i];
+        }
+        aucSuccess += avgPrecision[1][i];
+    }    
+    output_file << aucPrecision * 2 << "," << aucSuccess << std::endl;
+       
     return 0;
 }

### 2017-04-21 C++_Implementation/src/kcftracker.hpp

@@ -18,9 +18,6 @@ public:
     // Initialize tracker 
     virtual void init(const cv::Rect &roi, cv::Mat image);
     
-    // Initialize tracker 
-    virtual void reinit(const cv::Rect &roi, cv::Mat image);
-
     // Update position based on the new frame
     virtual cv::Rect update(cv::Mat image);
 
@@ -37,10 +34,10 @@ public:
     cv::Rect_<float> applyHomography(cv::Mat homography, cv::Mat image, cv::Rect_<float> oldRoi);
     
     // Target Re-detection Module
-    std::pair<int,float> target_redetection(std::vector<cv::Vec4i> BoundingBoxes, cv::Mat frame);
+    std::pair<int,float> target_redetection(std::vector<cv::Vec4i> BoundingBoxes, cv::Mat frame, cv::Rect result, int rdIndex, std::vector<std::pair<int,float>>& boxProposed);
 
     float interp_factor, interp_factor_scale, interp_factor_w_roi; // linear interpolation factor for adaptation
-    float sigma;        // gaussian kernel bandwidth
+    float sigma, sigma_scale;        // gaussian kernel bandwidth
     float lambda;       // regularization
     int cell_size;      // HOG cell size
     int cell_sizeQ;     // cell size^2, to avoid repeated operations
@@ -61,7 +58,10 @@ protected:
     cv::Point2f detectScale(cv::Mat z, cv::Mat x, float &peak_value);
 
     // Detect object in the current frame.
-    void detectScaleRedetection(cv::Mat z, cv::Mat x, float &peak_value);
+    void detectScaleRedetection(cv::Mat z, cv::Mat Model, cv::Mat x, float &peak_value);
+
+    // Detect object in the current frame.
+    void detectRedetection(cv::Mat z, cv::Mat Model, cv::Mat x, float &peak_value);
 
     // train tracker with a single image
     void train(cv::Mat x, float train_interp_factor);
@@ -102,6 +102,9 @@ protected:
     // Obtain sub-window from image, with replication-padding and extract features
     cv::Mat getFeaturesScaleRedetection(const cv::Mat & image, cv::Vec4i box);
 
+    // Obtain sub-window from image, with replication-padding and extract features
+    cv::Mat getFeaturesRedetection(const cv::Mat & image, cv::Vec4i box);
+
[…]

### 2017-04-21 C++_Implementation/src/runtracker.cpp

@@ -93,7 +93,7 @@ int main(int argc, char* argv[])
    bool FIXEDWINDOW = false;  // Fixed Window
    bool MULTISCALE = true;    // Scale Space Search Enabled
    bool SILENT = false;	      // Suppress the Outputs
-   bool LAB = false;	      // Enable or Disable Color Features
+   bool LAB = true;	      // Enable or Disable Color Features
    char szDataFile[256];
    char gtDataFile[256];
    char szImageFile[256];
@@ -171,7 +171,8 @@ int main(int argc, char* argv[])
    int seed2 = time(0);
    std::default_random_engine engine2(seed2);
    std::uniform_int_distribution<int> dist2(0,1000);
-
+   float rdThresholds[3] = {4.00,2.50,1.00};
+   int rdIndex = 0, rdTriggerIndex = 0; // Indexes for ReDetection
    // Read the Video
    cv::VideoCapture capt;
    if (strncmp(argv[2],"video",5) == 0){
@@ -185,26 +186,75 @@ int main(int argc, char* argv[])
    cv::resizeWindow("Name", 800,800);
    
    // Read the Ground Truth Text File
+char ch;
+#ifdef _VOT15_DATASET_
+   float g1X, g1Y, g2X, g2Y, g3X, g3Y, g4X, g4Y;
+#endif
+
+#ifdef _UAV123_DATASET_
    int gX, gY, gWidth, gHeight;
+   int fFrame,lFrame,frameID;
+   std::string seqName; 
+   std::string seqNameID;
+   std::string matchString = prDataFile;
+   std::ifstream startFrame("/home/buzkent/Desktop/startFrames_UAV123.txt");
+   // Matched Frame
+   while(startFrame >> fFrame >> lFrame >> seqNameID >> seqName){
+     if (seqNameID.compare(matchString) == 0){
+         frameID = fFrame;
+         break;
+      }	
+   }
+#endif
+
+   // Read the Ground Truth File for the Object of Interest
    std::ifstream groundTruth(gtDataFile);
    std::cout << gtDataFile << std::endl;
-   char ch;
 
    // Declare A Vector for Euclidean Distance
    std::vector<std::vector<float>> Metrics(2);
+   int cfIndex = 0;
+
 #ifdef _USE_VIDEO_INPUT__
    while (1) // Read the Next Frame
    {
 #endif
 
-#ifdef _USE_IMAGE_INPUT_
[…]

### 2017-04-21 draft.tex
Revised the introduction and added more reference.

@@
 
-A proliferation of unmanned vehicle technologies has ever increased
-interest on deployment of computer vision algorithms on embedded or
-mobile platforms. For example, an unmanned air vehicle (UAV) equipped
-with object or feature following would make it more useful in the
-application of monitoring/surveillance/surveying on private
+A recent proliferation of air/ground/water unmanned vehicle
+technologies has ever increased interest on deployment of intelligent
+algorithms on embedded or mobile platforms. Particularly, computer
+vision algorithms are getting more attention primarily because those
+platforms have limited payload to accommodate various sensors like
+lidars or radars and installing a monocular camera even stereo rigs
+would increase the usefulness of a mobile platform without increasing
+much cost on it. For example, instead of being equipped with a bare
+flight function with video recording, an unmanned air vehicle (UAV)
+equipped with object or feature following would make it more useful in
+the application of monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
@@
   results.}
+
+For being a turnkey or ready-to-execute mission solution, an online
+learning framework is more attractive. An object-following with a
+self-supervised learning framework would work, but easy to fail to
+serve a long-term solution.
+
+One of the dominant frameworks for online object tracking based on the
+correlation filter is to solve a regression problem in the frequency
+domain. This framework assumes that the target information is given at
+the very first image frame. Given this positive example for the
+regression problem, a set of negative examples is mostly collected
+around the initial, target bounding box and represented as a circulant
+matrix \cite{henriques2015high}. One can optimally solve this
+regression problem using a ridge regression in a closed form. However,
+such a solution involves in expensive matrix operation
+$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
+cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
+multiplication in a frequecny domain
+\cite{bolme2010visual,henriques2015high}. Due to such a reformulation,
+a complete pipeline of an object tracker based on the correlation
+filter can be easily implemented and run in an online fashion with a
+high speed. However, the vanilla form of such an online tracker is
+prone to drift and fails to track a target over a long period of
+time. This is explained well by the dilemma of stability-plasticity in
+updating appearance model in that the appearance model will be
+overfitted to only the images used to train and a compromise on the
+frequency of updating the model is carefully implemented
+\cite{santner2010prost}.
+
+{\it YoungWoo: Need to clean up the following paragraphs until Section
+  2.}
 
@@
 
-To the best of our knowledge, the dominant framework of online object
-trackers based on the correlation filter is to solve a regression
-problem in the frequency domain. This framework assumes that the
-target information is given at the very first image frame. Given this
-positive example for the regression problem, a set of negative
-examples is mostly collected around the initial, target bounding box
-and represented as a circulant matrix \cite{henriques2015high}.
+\begin{itemize}
+\item Need lots of manually labelled examples.
+\item Too expensive to deploy a DNN, even a trained one, due to its
+  power consumption. Do we have a reference on this?
+\end{itemize}
 
@@
 %----------------------------------------------------------------------
+
+{\it Burak: We need an overview of EnKCF by doing following.}
+\begin{itemize}
+\item Put a pseudo code here; Need to go over the pseudo code to explain what EnKCF is from the very high-level first.
+\item Briefly explain KCF at the middle of EnKCF description.
+\end{itemize}
 

### 2017-04-21 egpaper_final.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
 \usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the CVPR 2017 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for
  CVPR 2017.}

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2017 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-04-21 draft.tex
Revised the introduction and added more reference.

@@
 
-\begin{itemize}
-\item Need lots of manually labelled examples.
-\item Too expensive to deploy a DNN, even a trained one, due to its
-  power consumption. Do we have a reference on this?
-\end{itemize}
+The recent progress on development of convolutional neural networks
+(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
+the record for the ImageNet competition, at every year, new and better
+results are reported. Moreover, there have been many attempts to
+deploy CNN on the mobile devices
+\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
+a supervised learning based object tracking is that an either online
+\cite{nam2016} or offline \cite{held2016} training tracker has to be
+prior to deploy the algorithm.
 

### 2017-04-22 draft.tex
Comments Answered in the Introduction Section

@@
 
-{\it Burak: It isn't clear what you're getting at here} Learning
+{\it Burak: It isn't clear what you're getting at here}
+
+{\it YoungWoo : Here, I am making an introduction
+into the tracking-by-detection paradigm.
+I wanted to explain that they improve tracking as they learn an appearance model representative of the background and object.
+However, as I want to point out, the tracking-by-detection algorithms can be unfeasible as training a robust classifier can be costly.
+} Learning
 an object-specific classifier in an online manner can better handle
@@
   related to what we did for this paper?}
+
+{\it YoungWoo : They are not related at all, however, I wanted to give a brief idea about tracking-by-detection challenges.
+I feel like the text in between line 147 - 187 can precede the paragraph starting at line 122.
+Do you think it makes sense?
+This way, we give an introduction on tracking-by-detection.}
 
@@
 prior to deploy the algorithm.
+
+{\it YoungWoo : I think the following paragraph and paragraph in between line 118-143 give a brief idea about CF and KCF.
+We can probably combine them in a single paragraph followed by our contributions.}
 

### 2017-04-23 draft.tex
Cleaned up the introduction a bit.

@@
 
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
 A recent proliferation of air/ground/water unmanned vehicle
-technologies has ever increased interest on deployment of intelligent
-algorithms on embedded or mobile platforms. Particularly, computer
-vision algorithms are getting more attention primarily because those
-platforms have limited payload to accommodate various sensors like
-lidars or radars and installing a monocular camera even stereo rigs
-would increase the usefulness of a mobile platform without increasing
-much cost on it. For example, instead of being equipped with a bare
-flight function with video recording, an unmanned air vehicle (UAV)
-equipped with object or feature following would make it more useful in
-the application of monitoring/surveillance/surveying on private
+technologies has ever increased interests on deployment of intelligent
+algorithms on embedded or mobile platforms. Among those technologies,
+computer vision algorithms are getting more attentions primarily
+because those mobile platforms have limited payload to carry other
+active sensors and, without increasing much cost, installation of a
+monocular camera even stereo rigs would increase the usefulness of a
+mobile platform. For example, instead of just bare flight function
+with video recording, an unmanned air vehicle (UAV) equipped with
+object or feature following would make it more useful in the
+application of monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
-many others. In this paper, we propose an object tracking algorithm
-that aims at running on any embedded or mobile platforms. In
-particular,
+many others.
+
+In this paper, we propose a single-target tracking that aims at
+running on any embedded or mobile platforms that doesn't require an
+offline training, and can run on an embedded system. In particular, we
+would like to make our algorithm 1) learn the appearance model of a
+target on the fly and 2) run as fast on a typical desktop as up to
+300Hz so that it could run up to 30Hz when it is deployed on a
+low-end, embedded system. With these features, our tracking algorithm
+is ready to track an object of interest when it is deployed on an
+embedded system. To this end, an online object tracking is more
+appropriate.
 
@@
 
-For being a turnkey or ready-to-execute mission solution, an online
-learning framework is more attractive. An object-following with a
-self-supervised learning framework would work, but easy to fail to
-serve a long-term solution.
-
-One of the dominant frameworks for online object tracking based on the
-correlation filter is to solve a regression problem in the frequency
-domain. This framework assumes that the target information is given at
-the very first image frame. Given this positive example for the
-regression problem, a set of negative examples is mostly collected
-around the initial, target bounding box and represented as a circulant
-matrix \cite{henriques2015high}. One can optimally solve this
-regression problem using a ridge regression in a closed form. However,
-such a solution involves in expensive matrix operation
+One of the dominant frameworks for online object tracking is one based
+on the correlation filter that essentially solves a regression problem
+in the frequency domain. This framework assumes that the target
+information is given at the very first image frame like other online
+tracking algorithms. Given this positive example for the regression
+problem, a set of negative examples is collected around the initial,
+target bounding box and represented as a circulant matrix
+\cite{henriques2015high}. One can optimally solve this regression
+problem using a ridge regression in a closed form. However, such a
+solution involves in expensive matrix operations
 $\mathcal{O}(n^{3})$. The correlation filter provides one with a much
@@
 a complete pipeline of an object tracker based on the correlation
-filter can be easily implemented and run in an online fashion with a
-high speed. However, the vanilla form of such an online tracker is
-prone to drift and fails to track a target over a long period of
+filter can be easily implemented and run in an online fashion
+efficiently. However, the vanilla form of such an online tracker is
+prone to drift, and fails to track a target over a long period of
 time. This is explained well by the dilemma of stability-plasticity in

### 2017-04-25 draft.tex
ENKCF Updated - The WorkFlow Figure Updated - KCF Part needs to be shortened

@@
 
-{\it Burak: We need an overview of EnKCF by doing following.}
-\begin{itemize}
-\item Put a pseudo code here; Need to go over the pseudo code to explain what EnKCF is from the very high-level first.
-\item Briefly explain KCF at the middle of EnKCF description.
-\end{itemize}
+The KCF with multi-channel features outperform the other
+state-of-the-art object traking algorithms in VOT15 challenge in terms of run-time
+performance and tracking accuracy. However, it lacks scale adaptation
+module or the naive scale adaptation method added into the KCF reduces
+the frames per second from $\geq300$ fps to less than $100$ fps. One
+straightforward method is to run detection on ROIs with different
+sizes determined by pre-defined scale ratios
+\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All
+these method increases the computational complexity of tracking by
+running detection on a number of ROIs. Another scale update method in
+Correlation Filter framework was proposed by \cite{zhang2014fast}. It
+uses the MOSSE tracker to estimate translation of an object. The scale
+is updated in a naive way where the confidence map is used to
+determine the scale change between successive frames. For instance,
+their method assumes similar scale in between two consecutive frames
+given similar confidences. With this simple method, we do not need to
+run detection on different ROIs at a given frame and perform tracking
+at $\geq300$ fps. In this study, we propose the use of Ensemble KCFs
+in an intuitive way to perform robust scale-adaptive tracking at more
+than $300$ fps. Our approach is inspired by \cite{ma2015long} where
+two KCFs are employed as translation and scale filters. It first
+estimates translation using the translation filter learned on
+\textit{target}$+$\textit{background} area. Then, the scale filter
+learned on the \textit{target} area is used to estimate new scale of
+the target at the estimated position. Application of translation and
+scale filter at each frame reduces run-time performance ($\leq50 fps$)
+as we need to run detection on each scale candidate and perform training on both filters. Similarly,
+we learn three different correlation filters specializing on different
+aspects of tracking and addresses the weakness of each other,
+resulting in more robust tracking. We name these filters as
+\textit{target}+\textit{small background} translation filter
+($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+\textit{target}+\textit{large background} translation filter
+($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
+each frame, we can achieve the targeted operation frame rate. The
+fig.~\ref{fig:Filters} shows the size of the ROIs associated with
+$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
+windows assigned and desired Gaussian responses assigned to each one.
 
-% ---------------------------------------------------------
-\subsection{Kernelized Correlation Filter Tracker} \label{KCF}
-% ---------------------------------------------------------
+\begin{figure}[!t]
+\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
+\caption{The three filters called as medium ROI translation filter,
+  target ROI scale filter and large ROI translation filter are
+  shown. Also, the hanning window and desired Gaussian response for
+  each filter are displayed.}
+\label{fig:Filters}
+\end{figure}
+
+Our MKCF based tracking framework employs different capabilities and
+tasks to each correlation filter learned temporally. In
+\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
+\textit{target-only} area whereas \cite{henriques2015high,
+  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
+learned on \textit{target+background} area to find the optimal scale
+in scale space. To learn the scale filter, $R_{s}$, we follow a
+similar approach to \cite{ma2015long}. We believe that translation
+filter needs to include background information to better discriminate
+target from background, however, the goal of the scale filter is to
+estimate the right size of the target, not to discriminate it from
+background. Also, by using a smaller ROI we can reduce the template size
+ to learn the scale filter, resulting in higher speed scale
+estimation module. Finally, the scale filter help us on the track
+re-initialization module which includes running an object proposals
+algorithm to boxes bounding the objects in the scene. By using the
+scale filter in re-initialization module, we can reduce the
+element-wise operations compared to the translation filters. Also, we can 
+avoid false target re-initialization in the case of rapid background change as $R_{t}^{s}$ and
+$R_{t}^{L}$ learn background in addition to target. The \textit{target+small background} area translation filter, $R_{t}^{S}$,
+is assigned a larger template size than $R_{s}$ and smaller than
+$R_{t}^{L}$. It is employed to estimate translation and scale similar
+to \cite{henriques2015high}. Finally, the \textit{target+large
+  background} area translation filter, $R_{t}^{L}$ , estimates only
+the translation of a target. We propose scale estimation at every $n$ number of frames using the scale filter. In our experiments on $OTB100$ and $UAV123$,
+we observed that $n$ = 5 gives the best results in terms of precision and success overlap rates. The \textit{target+large background} translation filter is run
+in the next frame after the scale filter as we want to avoid drifts.
+Considering large ROI for $R_{t}^{L}$ can degrade its performance due to low resolution template.
+For this reason, we employ \textit{Color} and \textit{HoG} features for $R_{t}^{L}$ correlation filter.
+Finally, $R_{t}^{S}$ is applied after $R_{t}^{L}$ to avoid any target loss due to low resolution template used by $R_{t}^{L}$.
+Unlike $R_{t}^{L}$, we only employ the \textit{HoG} features for the $R_{t}^{S}$ correlation filter.
+Fig.~\ref{Workflow_figure} displays the proposed tracking framework using Ensemble of KCFs.
+Also, the pseudo-code of the proposed $EnKCF$ is shown in alg.~\ref{alg:MKCF}.
+
+\begin{algorithm}
+	\caption{The MKCF Tracking Algorithm.}\label{alg:MKCF}
+	\begin{algorithmic}[1]
+	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n$,
+	\State \textbf{Output} : 
+				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
+						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
+						Scale filter (\textit{target-only}) model $R_{s}$.
+			     \EndIf
+				\If{$fc\:\%\:n=1$}\Comment{Condition 2}
+						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
+						Large Area Translation Filter model $R_{t}^{L}$.
+				\EndIf
+				\If{$fc\:\%\:n>1$}\Comment{Condition 3}
+						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
+						Small Area Translation Filter model $R_{t}^{S}$.
+				\EndIf
+	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
+				\State // Translation Estimation
+				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
+				\State // Translation Estimation
+				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
+				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
+				\State Skip translation estimation for $R_{s}$ (Condition 1);
+				\State // Scale Estimation
+			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1) or $R_{t}^{S}$ (Condition 2), 
+		         \State Skip it for $R_{t}^{L}$ (Condition 1),
+				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$, and for $R_{t}^{S}$ : $\lbrace1.02,1.0,1/1.02\rbrace$;
+				\State // Update Translation
+				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
+			    \State // Model Update
+				\If{$max(y_{R_{s}}) \geq T_{R_{s}}$}
+				\State Update $R_{s}$ (Condition 1);
+				\EndIf							 
+				\If{$max(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
+				\State Update $R_{t}^{L}$ (Condition 2);
+				\EndIf	
+			     \If{$max(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
+				\State Update $R_{t}^{S}$ (Condition 3);
+			     \EndIf		
+	\EndProcedure	
+	\end{algorithmic}
+\end{algorithm}
+
 The Kernelized Correlation Filter tracker has recently been
@@
 
-%-------------------------------------------------------------------
-\subsection{Multiple Kernelized Correlation Filter Based Tracking} \label{sc:MKCF}
-%------------------------------------------------------------------
-The KCF with Multi-channel features outperforms the other
-state-of-the-art object traking algorithms both in terms of run-time
-performance and tracking accuracy. However, it lack scale adaptation
-module or the naive scale adaptation method added into the KCF reduces
-the frames per second from $\geq300$ fps to less than $100$ fps. One
-straightforward method is to run detection on ROIs with different
-sizes determined by pre-defined scale ratios
-\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All
-these method increases the computational complexity of tracking by
-running detection on a number of ROIs. Another scale update method in
-Correlation Filter framework was proposed by \cite{zhang2014fast}. It
-uses the MOSSE tracker to estimate translation of an object. The scale
-is updated in a naive way where the confidence map is used to
-determine the scale change between successive frames. For instance,
-their method assumes similar scale in between two consecutive frames
-given similar confidences. With this simple method, we do not need to
-run detection on different ROIs at a given frame and perform tracking
-at $\geq300$ fps. In this study, we propose the use of Multiple KCFs
-in an intuitive way to perform robust scale-adaptive tracking at more
-than $300$ fps. Our approach is inspired by \cite{ma2015long} where
-two KCFs are employed as translation and scale filters. It first
-estimates translation using the translation filter learned on
-\textit{target}$+$\textit{background} area. Then, the scale filter
-learned on the \textit{target} area is used to estimate new scale of
-the target at the estimated position. Application of translation and
-scale filter at each frame reduces run-time performance ($\leq50 fps$)
-as we need to run detection and training on both filters. Similarly,
-we learn three different correlation filters specializing on different
-aspects of tracking and addresses the weakness of each other,
-resulting in more robust tracking. We name these filters as
-\textit{target}+\textit{small background} translation filter
-($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
-\textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
-each frame, we can achieve the targeted operation frame rate. The
-fig.~\ref{fig:Filters} shows the size of the ROIs associated with
-$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
-windows assigned and desired Gaussian responses assigned to each one.
-
-\begin{figure}[!t]
-\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
-\caption{The three filters called as medium ROI translation filter,
-  target ROI scale filter and large ROI translation filter are
-  shown. Also, the hanning window and desired Gaussian response for
-  each filter are displayed.}
-\label{fig:Filters}
-\end{figure}
-
-Our MKCF based tracking framework employs different capabilities and
-tasks to each correlation filter learned temporally. In
-\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
-\textit{target-only} area whereas \cite{henriques2015high,
-  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
-learned on \textit{target+background} area to find the optimal scale
-in scale space. To learn the scale filter, $R_{s}$, we follow a
-similar approach to \cite{ma2015long}. We believe that translation
-filter needs to include background information to better discriminate
-target from background, however, the goal of the scale filter is to
-estimate the right size of the target, not to discriminate it from
-background. Also, by using a smaller ROI we can reduce the size of the
-template to learn the scale filter, resulting in higher speed scale
-estimation module. Finally, the scale filter help us on the track
-re-initialization module which includes running an object proposals
-algorithm to boxes bounding the objects in the scene. By using the
-scale filter in re-initialization module, we can reduce the
-element-wise operations compared to the translation filters. The
-\textit{target+small background} area translation filter, $R_{t}^{S}$,
-is assigned a larger template size than $R_{s}$ and smaller than
-$R_{t}^{L}$. It is employed to estimate translation and scale similar
-to \cite{henriques2015high}. Finally, the \textit{target+large
-  background} area translation filter, $R_{t}^{L}$ , estimates only
-the translation of a target.
-
-\begin{algorithm}
-	\caption{The MKCF Tracking Algorithm.}\label{alg:MKCF}
-	\begin{algorithmic}[1]
-	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n$,
-	\State \textbf{Output} : 
-				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
-						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
-						Scale filter (\textit{target-only}) model $R_{s}$.
-			     \EndIf
-				\If{$fc\:\%\:n=1$}\Comment{Condition 2}
-						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
-						Large Area Translation Filter model $R_{t}^{L}$.
-				\EndIf
-				\If{$fc\:\%\:n>1$}\Comment{Condition 3}
-						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
-						Small Area Translation Filter model $R_{t}^{S}$.
-				\EndIf
-	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
-				\State // Translation Estimation
-				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
-				\State // Translation Estimation
-				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
-				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
-				\State Skip translation estimation for $R_{s}$ (Condition 1);
-				\State // Scale Estimation
-			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1) or $R_{t}^{S}$ (Condition 2), 
-		         \State Skip it for $R_{t}^{L}$ (Condition 1),
-				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$, and for $R_{t}^{S}$ : $\lbrace1.02,1.0,1/1.02\rbrace$;
-				\State // Update Translation
-				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
-			    \State // Model Update
-				\If{$max(y_{R_{s}}) \geq T_{R_{s}}$}
-				\State Update $R_{s}$ (Condition 1);
-				\EndIf							 
-				\If{$max(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
-				\State Update $R_{t}^{L}$ (Condition 2);
-				\EndIf	
-			     \If{$max(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
-				\State Update $R_{t}^{S}$ (Condition 3);
-			     \EndIf		
-	\EndProcedure	
-	\end{algorithmic}
-\end{algorithm}
-
 \section{Particle Filter}

### 2017-04-25 draft.tex
Pseudo-code updated

@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
 % \cvprfinalcopy % *** Uncomment this line for the final submission
@@
 \includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
-\caption{The three filters called as medium ROI translation filter,
-  target ROI scale filter and large ROI translation filter are
+\caption{The three filters denoted as \textit{target+small background} translation filter,
+  \textit{target-only} scale filter and \textit{target+large background} translation filters are
   shown. Also, the hanning window and desired Gaussian response for
-  each filter are displayed.}
+  each filter is displayed.}
 \label{fig:Filters}
@@
 \begin{algorithm}
-	\caption{The MKCF Tracking Algorithm.}\label{alg:MKCF}
+	\caption{The EnKCF Tracking Algorithm.}\label{alg:MKCF}
 	\begin{algorithmic}[1]
-	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n$,
+	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
 	\State \textbf{Output} : 
@@
 			     \EndIf
-				\If{$fc\:\%\:n=1$}\Comment{Condition 2}
+				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
 						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
@@
 				\EndIf
-				\If{$fc\:\%\:n>1$}\Comment{Condition 3}
+				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
 						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
@@
 				\State // Scale Estimation
-			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1) or $R_{t}^{S}$ (Condition 2), 
+			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
 		         \State Skip it for $R_{t}^{L}$ (Condition 1),
-				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$, and for $R_{t}^{S}$ : $\lbrace1.02,1.0,1/1.02\rbrace$;
+				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
 				\State // Update Translation
@@
 			    \State // Model Update
-				\If{$max(y_{R_{s}}) \geq T_{R_{s}}$}
+				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
 				\State Update $R_{s}$ (Condition 1);
 				\EndIf							 
-				\If{$max(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
+				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
 				\State Update $R_{t}^{L}$ (Condition 2);
 				\EndIf	
-			     \If{$max(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
+			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
 				\State Update $R_{t}^{S}$ (Condition 3);

### 2017-04-26 draft.tex
Pseudo-code updated
Wrote an abstract.

--- 2017-04-25 draft.tex
@@
 %%%%%%%%% TITLE
-\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}
+\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed}
 
@@
 YoungWoo Seo\\
-Affiliation\\
+Independent Robotics Research\\
 {\tt\small youngwoo.blank.seo@gmail.com}
@@
 \begin{abstract}
-
+Computer vision technologies are very attractive for practical
+application of embedded systems in that most of the embedded systems
+already includes image acquisition pipeline and a tremendous amount of
+progresses on research has been made. However, to successfully deploy
+a computer vision algorithm on any existing embedded systems, a vision
+algorithm needs to satisfy some criteria: minimal, manual intervention
+after deployment and small footprint of computing resource consumption
+and executable size. This criteria assumes the performance of the
+algorithm is reasonably good. To this end, in this paper, we propose an
+ensemble of the kernelized correlation filters (KCF), aka {\it E}nKCF,
+for a single-target object tracking. In particular, we developed a
+committee of KCFs to specifically address the scale-change and the
+translation over frames. In addition, we devised a Bayes filter to
+minimize the gap of interactions between KCFs. It is well known that
+an online, model-free tracker like ours is prone to drift over
+time. To cope with such drifts, we developed a re-detection module
+that reliably identifies when to lose the target, hand-picks a small
+number of object proposals from existing object proposal methods
+(e.g., ``Edge Box''), and re-initializes the track to track the object
+for a longer period. To verify the usefulness of the proposed method,
+we compared the performance of ours to those of existing online
+tracking methods. Experimental results showed that the performance of
+ours are precision on 20 pixels, 69.53\%, AUC 52.90\% for OTB100 data
+and 54.11\% and 40.21\% for UAV123 data. This confirmed that our
+method outperformed the existing ones over 5\% on precision on 20
+pixels and 3\% on AUC on average. Our implementation ran at 340 fps
+for OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
+fps) for OTB100.
 \end{abstract}

### 2017-04-26 draft.tex
Abstract Edited

@@
 tracking methods. Experimental results showed that the performance of
-ours are precision on 20 pixels, 69.53\%, AUC 52.90\% for OTB100 data
-and 54.11\% and 40.21\% for UAV123 data. This confirmed that our
-method outperformed the existing ones over 5\% on precision on 20
-pixels and 3\% on AUC on average. Our implementation ran at 340 fps
-for OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
-fps) for OTB100.
+ours are precision on 20 pixels, 72.53\%, AUC 52.90\% for OTB100 data
+and 55.71\% and 41.71\% for UAV123 data.
+This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in terms of precision and $15\%$-$20\%$ in AUC.
+Finally,  our implementation ran at 340 fps for OTB100 dataset and at 416 fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($300$ fps) for UAV123.
 \end{abstract}

### 2017-04-26 draft.tex
Abstract Edited

--- 2017-04-26 draft.tex
@@
 tracking methods. Experimental results showed that the performance of
-ours are precision on 20 pixels, 69.53\%, AUC 52.90\% for OTB100 data
-and 54.11\% and 40.21\% for UAV123 data. This confirmed that our
-method outperformed the existing ones over 5\% on precision on 20
-pixels and 3\% on AUC on average. Our implementation ran at 340 fps
-for OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
-fps) for OTB100.
+our tracker are $72.53\%$ \textit{precision} at $20$ px, $52.90\%$ \textit{AUC} for OTB100 data
+and $55.71\%$ and $41.71\%$ for UAV123 data.
+This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in terms of precision and $10\%$-$20\%$ in AUC.
+Finally,  our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.
 \end{abstract}

### 2017-04-26 draft.tex
Abstract Edited

@@
 for a longer period. To verify the usefulness of the proposed method,
-we compared the performance of ours to those of existing online
+we compared the performance of ours to those of existing other online high speed
 tracking methods. Experimental results showed that the performance of
@@
 and $55.71\%$ and $41.71\%$ for UAV123 data.
-This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in terms of precision and $10\%$-$20\%$ in AUC.
+This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in precision and $10\%$-$20\%$ in AUC.
 Finally,  our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.

### 2017-04-26 draft.tex
Revised the abstract.

--- 2017-04-26 draft.tex
@@
 Computer vision technologies are very attractive for practical
-application of embedded systems in that most of the embedded systems
+applications for embedded systems in that most of the embedded systems
 already includes image acquisition pipeline and a tremendous amount of
-progresses on research has been made. However, to successfully deploy
-a computer vision algorithm on any existing embedded systems, a vision
-algorithm needs to satisfy some criteria: minimal, manual intervention
-after deployment and small footprint of computing resource consumption
-and executable size. This criteria assumes the performance of the
-algorithm is reasonably good. To this end, in this paper, we propose an
-ensemble of the kernelized correlation filters (KCF), aka {\it E}nKCF,
-for a single-target object tracking. In particular, we developed a
-committee of KCFs to specifically address the scale-change and the
-translation over frames. In addition, we devised a Bayes filter to
-minimize the gap of interactions between KCFs. It is well known that
-an online, model-free tracker like ours is prone to drift over
-time. To cope with such drifts, we developed a re-detection module
-that reliably identifies when to lose the target, hand-picks a small
-number of object proposals from existing object proposal methods
-(e.g., ``Edge Box''), and re-initializes the track to track the object
-for a longer period. To verify the usefulness of the proposed method,
-we compared the performance of ours to those of existing online
-tracking methods. Experimental results showed that the performance of
-ours are precision on 20 pixels, 72.53\%, AUC 52.90\% for OTB100 data
-and 55.71\% and 41.71\% for UAV123 data.
-This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in terms of precision and $15\%$-$20\%$ in AUC.
-Finally,  our implementation ran at 340 fps for OTB100 dataset and at 416 fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($300$ fps) for UAV123.
+progresses on research has been made for many areas. However, to
+successfully deploy a computer vision algorithm on any existing
+embedded systems, a vision algorithm needs to satisfy some criteria:
+minimal, manual intervention after deployment and small footprint of
+computing resource consumption and on executable code, with the
+assumption of reasonably good performance. To this end, in this paper,
+we propose an ensemble of the kernelized correlation filters (KCF), we
+call {\it E}nKCF, for a single-target object tracking. In particular,
+we developed a committee of KCFs to specifically address the
+scale-change and dynamic maneuver of the target over frames. In
+addition, we devised a Bayes filter for a smooth transition on
+execution of individual KCFs. To minimize the effect of drifting, we
+developed a re-detection module that detects target-lost, uses an
+existing object proposal method (e.g., ``Edge Box'') to re-detect the
+lost target, and re-initializes the previous tracking for a long-term
+tracking. To verify the usefulness of the proposed method, we compared
+the performance of ours to those of the existing online tracking
+methods. Experimental results showed that the performance of ours are
+69.53\% for precision on 20 pixels and 52.90\% for success rate for
+OTB100 data, and 54.11\% and 40.21\% for UAV123 data. These results
+confirmed that our method outperformed the existing ones over 5\% on
+precision on 20 pixels and 3\% on AUC on average. Our implementation
+ran at 340 fps for OTB100 and at 416 fps for UAV123 data that is
+faster than DCF (292 fps) for OTB100.
 \end{abstract}

### 2017-04-26 draft.tex

@@
 methods. Experimental results showed that the performance of ours are
-69.53\% for precision on 20 pixels and 52.90\% for success rate for
-OTB100 data, and 54.11\% and 40.21\% for UAV123 data. These results
+72.53\% for precision on 20 pixels and 52.90\% for success rate for
+OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
 confirmed that our method outperformed the existing ones over 5\% on
-precision on 20 pixels and 3\% on AUC on average. Our implementation
-ran at 340 fps for OTB100 and at 416 fps for UAV123 data that is
-faster than DCF (292 fps) for OTB100.
+precision on 20 pixels and 10-20\% on AUC on average. Our
+implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
+DCF (457 fps), and STC (350 fps) for UAV123.
 \end{abstract}

### 2017-04-26 draft.tex
Results Section Added

--- 2017-04-26 draft.tex
@@
  %%%%%%%%% TITLE
-\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed}
+\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz}
 
@@
 YoungWoo Seo\\
-Independent Robotics Research\\
+Affiliation\\
 {\tt\small youngwoo.blank.seo@gmail.com}
@@
 \begin{abstract}
-Computer vision technologies are very attractive for practical
-applications for embedded systems in that most of the embedded systems
-already includes image acquisition pipeline and a tremendous amount of
-progresses on research has been made for many areas. However, to
-successfully deploy a computer vision algorithm on any existing
-embedded systems, a vision algorithm needs to satisfy some criteria:
-minimal, manual intervention after deployment and small footprint of
-computing resource consumption and on executable code, with the
-assumption of reasonably good performance. To this end, in this paper,
-we propose an ensemble of the kernelized correlation filters (KCF), we
-call {\it E}nKCF, for a single-target object tracking. In particular,
-we developed a committee of KCFs to specifically address the
-scale-change and dynamic maneuver of the target over frames. In
-addition, we devised a Bayes filter for a smooth transition on
-execution of individual KCFs. To minimize the effect of drifting, we
-developed a re-detection module that detects target-lost, uses an
-existing object proposal method (e.g., ``Edge Box'') to re-detect the
-lost target, and re-initializes the previous tracking for a long-term
-tracking. To verify the usefulness of the proposed method, we compared
-the performance of ours to those of the existing online tracking
-methods. Experimental results showed that the performance of ours are
-69.53\% for precision on 20 pixels and 52.90\% for success rate for
-OTB100 data, and 54.11\% and 40.21\% for UAV123 data. These results
-confirmed that our method outperformed the existing ones over 5\% on
-precision on 20 pixels and 3\% on AUC on average. Our implementation
-ran at 340 fps for OTB100 and at 416 fps for UAV123 data that is
-faster than DCF (292 fps) for OTB100.
+
 \end{abstract}
@@
 To verify the usefulness of our algorithm, we ran our algorithm using
-three publicly available dataset:
-VOT2015 \footnote{\url{http://www.votchallenge.net/}},
+two publicly available datasets:
+%VOT2015 \footnote{\url{http://www.votchallenge.net/}},
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
 UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
+OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects.
+The proposed $EnKCF$ method can better handle slow motions.
+Also, the UAVs use mobiles platforms with limited computational power.
+We believe that the proposed tracker can better fit for tracking from such platforms as it is highly efficient and scale adaptive.
+Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.
+
+We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success} metrics. Precision is computed as the eucl%
 

### 2017-04-26 draft.tex
Long Abstract Added

@@
 \begin{abstract}
-
+Computer vision technologies are very attractive for practical application of embedded systems in that most of the embedded systems already includes image acquisition pipeline and a tremendous amount of progresses on research has been made.
+However, to successfully deploy a computer vision algorithm on any existing embedded systems, a vision algorithm needs to satisfy some criteria: minimal, manual intervention after deployment and small footprint of computing resource consumption and executable size.
+This criteria assumes the performance of the algorithm is reasonably good.
+To this end, in this paper, we propose an ensemble of the kernelized correlation filters (KCF), aka EnKCF, for a single-target object tracking.
+In particular, we developed a
+committee of KCFs to specifically address the scale-change and the translation over frames in an independent manner.
+Scale and translation tasks are distributed to this group of KCFs in a way to keep the frame rate per second as high as a single naive KCF tracker without scale adaptation module.
+In addition, we devised a Bayes filter to minimize the gap of interactions between KCFs.
+It is well known that an online, model-free tracker like ours is prone to drift over time.
+To cope with such drifts, we developed a re-detection module that reliably identifies when to lose the target, hand-picks a small number of object proposals from existing object proposal methods (e.g., "Edge Box"), and re-initializes the track to track the object for a longer period.
+The proposed EnKCF tracker also leads to a more robust re-detection module then a naive KCF as it includes target-only area scale filter and target+background area translation filters with different feature modalities which can be used to search for the target box among the object proposals.
+To verify the usefulness of the proposed method, we compared the performance of ours to those of existing other online high speed tracking methods.
+Experimental results showed that the performance of our tracker are $72.53\%$ precision at $20$ px, $52.90\%$ area under the success curve (AUC) for OTB100 data and $55.71\%$ and $41.71\%$ for UAV123 data.
+This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in precision at $20$ px and $10\%$-$20\%$ in AUC.
+These numbers also compete well with other scale adaptive lower speed trackers such as SAMF, DSST, and Struct.
+Finally, our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.
 \end{abstract}

### 2017-04-26 old_draft.tex
Cleaning up and re-structuring the intro.

--- 2017-04-26 draft.tex
@@
 scale-change and dynamic maneuver of the target over frames. In
-addition, we devised a Bayes filter for a smooth transition on
-execution of individual KCFs. To minimize the effect of drifting, we
-developed a re-detection module that detects target-lost, uses an
+addition, we devised a Bayes filter for a smooth transition between
+individual KCFs' executions. To minimize the effect of drifting, we
+also developed another algorithm that detects target-lost, uses an
 existing object proposal method (e.g., ``Edge Box'') to re-detect the
@@
 because those mobile platforms have limited payload to carry other
-active sensors and, without increasing much cost, installation of a
-monocular camera even stereo rigs would increase the usefulness of a
-mobile platform. For example, instead of just bare flight function
-with video recording, an unmanned air vehicle (UAV) equipped with
-object or feature following would make it more useful in the
-application of monitoring/surveillance/surveying on private
+active sensors than a lightweight, monocular camera and, without
+increasing much cost, installation of a monocular camera even stereo
+rigs would increase the usefulness of a mobile platform. For example,
+instead of having just bare flight function with video recording, an
+unmanned air vehicle (UAV) equipped with object or feature following
+would make it more useful in the application of
+monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
@@
 
-{\it YoungWoo: Need to clean up the following paragraphs until Section
-  2.}
-
+\begin{comment}
 The tracking-by-detection methods have recently used extensively as a
@@
 This way, we give an introduction on tracking-by-detection.}
+\end{comment}
 
@@
 \end{comment}
-
-The workflow of our MKCF based long-term target following method can
-be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss
-in the next sections.
-\begin{figure*}[!t]
-\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
-\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
-\label{Workflow_figure}
-\end{figure*}
-
-An object tracking method based on the correlation filter in frequency
-domain has gained attention due to its fast computation.
 
@@
 
-{\it YoungWoo : I think the following paragraph and paragraph in between line 118-143 give a brief idea about CF and KCF.
-We can probably combine them in a single paragraph followed by our contributions.}
+The KCF with multi-channel features outperform the other
+state-of-the-art object traking algorithms in VOT15 challenge in terms of run-time
+performance and tracking accuracy. However, it lacks scale adaptation
+module or the naive scale adaptation method added into the KCF reduces
+the frames per second from $\geq300$ fps to less than $100$ fps. One
+straightforward method is to run detection on ROIs with different
+sizes determined by pre-defined scale ratios
+\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All
+these method increases the computational complexity of tracking by
+running detection on a number of ROIs. Another scale update method in
+Correlation Filter framework was proposed by \cite{zhang2014fast}. It
+uses the MOSSE tracker to estimate translation of an object. The scale
+is updated in a naive way where the confidence map is used to
+determine the scale change between successive frames. For instance,
+their method assumes similar scale in between two consecutive frames
+given similar confidences. With this simple method, we do not need to
+run detection on different ROIs at a given frame and perform tracking
+at $\geq300$ fps. In this study, we propose the use of Ensemble KCFs
+in an intuitive way to perform robust scale-adaptive tracking at more
+than $300$ fps. Our approach is inspired by \cite{ma2015long} where
+two KCFs are employed as translation and scale filters. It first
+estimates translation using the translation filter learned on
+\textit{target}$+$\textit{background} area. Then, the scale filter
+learned on the \textit{target} area is used to estimate new scale of
+the target at the estimated position. Application of translation and
+scale filter at each frame reduces run-time performance ($\leq50 fps$)
+as we need to run detection on each scale candidate and perform training on both filters. Similarly,
+we learn three different correlation filters specializing on different
+aspects of tracking and addresses the weakness of each other,
+resulting in more robust tracking. We name these filters as
+\textit{target}+\textit{small background} translation filter
+($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+\textit{target}+\textit{large background} translation filter
+($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
+each frame, we can achieve the targeted operation frame rate. The
+fig.~\ref{fig:Filters} shows the size of the ROIs associated with
+$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
+windows assigned and desired Gaussian responses assigned to each one.
 
+\begin{comment}
 The first correlation filter tracker proposed by
@@
 \cite{ma2015long,de2015board,li2016monocular}.
+\end{comment}
 
@@
 %----------------------------------------------------------------------
+
+The workflow of our MKCF based long-term target following method can
+be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss
+in the next sections.
+\begin{figure*}[!t]
+\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
+\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
+\label{Workflow_figure}
+\end{figure*}
 

### 2017-04-28 draft.tex
Revised the introduction and todo list.

--- 2017-04-26 draft.tex
@@
 \begin{abstract}
-
+Computer vision technologies are very attractive for practical
+applications for embedded systems in that most of the embedded systems
+already includes image acquisition pipeline and a tremendous amount of
+progresses on research has been made for many areas. However, to
+successfully deploy a computer vision algorithm on any existing
+embedded systems, a vision algorithm needs to satisfy some criteria:
+minimal, manual intervention after deployment and small footprint of
+computing resource consumption and on executable code, with the
+assumption of reasonably good performance. To this end, in this paper,
+we propose an ensemble of the kernelized correlation filters (KCF), we
+call {\it E}nKCF, for a single-target object tracking. In particular,
+we developed a committee of KCFs to specifically address the
+scale-change and dynamic maneuver of the target over frames. In
+addition, we devised a Bayes filter for a smooth transition between
+individual KCFs' executions. To minimize the effect of drifting, we
+also developed another algorithm that detects target-lost, uses an
+existing object proposal method (e.g., ``Edge Box'') to re-detect the
+lost target, and re-initializes the previous tracking for a long-term
+tracking. To verify the usefulness of the proposed method, we compared
+the performance of ours to those of the existing online tracking
+methods. Experimental results showed that the performance of ours are
+72.53\% for precision on 20 pixels and 52.90\% for success rate for
+OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
+confirmed that our method outperformed the existing ones over 5\% on
+precision on 20 pixels and 10-20\% on AUC on average. Our
+implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
+DCF (457 fps), and STC (350 fps) for UAV123.
 \end{abstract}
@@
 \section{Introduction}
-
-\begin{comment}
-Maybe the goal of this work is to publish a journal paper about a
-practical solution for a drone to follow a single target. For this, we
-need some descriptions on
 \begin{itemize}
-\item A vision-based, single target tracking algorithm.
-\item Other components for making a drone follow a target.
-\begin{itemize}
-\item An architecture diagram
-\item Descriptions of vehicle control, motion planning, behavior
-  generation, estimation of relative geometry between a drone and a
-  target, etc
-\item Experimental results or example videos
+\item YoungWoo: Clean up the introduction
+\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
+\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
+\item By Monday, we'll have a draft ready to submit.
 \end{itemize}
-\end{itemize}
-
-For the BMVC-17 submission, we're going to just focus on the first
-part -- a vision-based, single target tracking algorithm. This is
-because we need to build a drone for the second part.
-\end{comment}
-
-\begin{comment}
-\begin{itemize}
-\item Introduction: Should talk about, at least, motivation of this
-  work, brief review of the literature, and contribution
-\item Method: Detail the method w.r.t. a diagram of system
-  architecture or pseudo code
-\begin{itemize}
-\item Kernelized Correlation Filter
-\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
-\item Re-detection for re-initialization: Modules for reliably
-  detecting target-lost, for extensively searching the lost target,
-  and for picking up the same target with a help from an appearance
-  model or other models.
-\begin{itemize}
-\item To filter out unlikely box proposals,
-\begin{itemize}
-\item Use a prior information about box, our outputs, dimensions
-  (e.g., a combination of width and height, aspect ratio, etc.)
-\item Use the information about the trajectory of the target before we
-  lose the target.
-\end{itemize}
-\item MTH: revisited
-\item To make a box tighter, generate our own box proposals based on
-  the locations of top $k$ box proposals from object proposal methods,
-  e.g., Edge Box.
-\end{itemize}
-\end{itemize}
-\item Experiment: Detail the data, and experimental setup; results and findings
-\item Will compare the performance of {\it E}nKCF, Naive{\it E}nKCF,
-  ${\it E}nKCF_{+RD}$ with those of the following tracking methods.
-\begin{itemize}
-\item vanilla-KCF w/ a fixed scale,
-\item vanilla-KCF w/ three different scales,
-\item LCT (Long-term Correlation Tracking) \cite{ma2015long}: Temporal
-  correlation of a target over frames; a pyramid for different scales;
-  re-detection w/ an appearance classifier (i.e., a naive Bayes w/
-  random fern features in combination of sliding window). Temporal
-  context regressor for translation over significant deformation and
-  target regressor for scale variation.
-\item MEEM (Multiple Experts using Entropy Minimization)
-  \cite{zhang2014meem}.
-\item SAMF (Scale Adaptive KCF)
-\item STC (fast tracking via Spatio-Temporal Context learning)
-  \cite{zhang2014fast}: 
-\item Struck (Structured Output Tracking with Kernels)
-\end{itemize}
-\begin{itemize}
-\item Visual tracker benchmark (VTB)
-\item DTB-70: w/ and w/o motion estimation,
-\item UAV123 \footnote{A set of images acquired from an UAV is called
-  ``UAV123'' and publicly available from
-  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
-\item VOT
-\end{itemize}
-\item Conclusion
-\end{itemize}
-\end{comment}
 
@@
 
-One of the dominant frameworks for online object tracking is one based
-on the correlation filter that essentially solves a regression problem
-in the frequency domain. This framework assumes that the target
-information is given at the very first image frame like other online
-tracking algorithms. Given this positive example for the regression
-problem, a set of negative examples is collected around the initial,
-target bounding box and represented as a circulant matrix
+One of the dominant frameworks for online object tracking is the
+correlation filter that essentially solves a single-target tracking
+problem as a regression problem in the frequency domain. This
+framework assumes that the target location is given at the very first
+image frame like other online tracking algorithms
+\cite{smeulders2014survey}. Given this positive example for the
+regression problem, a set of negative examples is collected around the
+initial, target bounding box and represented as a circulant matrix
 \cite{henriques2015high}. One can optimally solve this regression
@@
 multiplication in a frequecny domain
-\cite{bolme2010visual,henriques2015high}. Due to such a reformulation,
+\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
 a complete pipeline of an object tracker based on the correlation
-filter can be easily implemented and run in an online fashion
-efficiently. However, the vanilla form of such an online tracker is
-prone to drift, and fails to track a target over a long period of
-time. This is explained well by the dilemma of stability-plasticity in
-updating appearance model in that the appearance model will be
-overfitted to only the images used to train and a compromise on the
-frequency of updating the model is carefully implemented
-\cite{santner2010prost}.
+filter can be easily implemented and run very efficiently in an online
+fashion. In fact, a variant of the correlation filter, kernelized
+correlation filter with multi-channel features, outperformed other
+state-of-the-art tracking algorithms in VOT15 challenge, in terms of
+run-time and tracking accuracy. However, the vanilla form of such an
+online tracker is prone to drift, and fails to track a target over a
+long period of time primarily \cite{henriques2015high} because of the
+dilemma of stability-plasticity in updating appearance model, where
+the appearance model will be overfitted to only the images used to
+train and a compromise on the frequency of updating the model is
+carefully implemented \cite{santner2010prost}. For example, a naive
+way of handling a scale change of a target could reduce the run-time
+performance from 300 to 100 fps. A seemingly obvious way of addressing
+the scale change is to scan the region of interest (ROI) with
+templates in different dimensions based on pre-defined scale ratios to
+find the target
+\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
+because of computational nature of correlation filter, this approach
+would just increase the computational complexity of tracking by
+running detection with multiple possibilities.
 
-{\it YoungWoo: Need to clean up the following paragraphs until Section
-  2.}
+Another way of handling the scale change for the correlation filter
+based approach is to find a correct scale at a location where a target
+highly likely appears \cite{zhang2014fast}. In particular, they uses
+the MOSSE tracker to estimate a target's translation. The scale is
+updated in a naive way where the confidence map is used to determine
+the scale change between successive frames.
 
-The tracking-by-detection methods have recently used extensively as a
-robust, powerful, and highly discriminative vision-based, object
-tracking method replacing the preceding, generative object tracking
-methods that primarily concerned about learning the appearance of the
-target.
-
-The recent examples of the tracking-by-detection algorithms include
-Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
-Instance Learning \cite{babenko2009visual}, Correlation Filter based
-trackers \cite{bolme2010visual,henriques2015high}, and Struck
-\cite{hare2012efficient}. These tracking-by-detection methods learn
-the model of the target's appearance on the fly while discriminating
-the target from the background.
-
-{\it Burak: It isn't clear what you're getting at here}
-
-{\it YoungWoo : Here, I am making an introduction
-into the tracking-by-detection paradigm.
-I wanted to explain that they improve tracking as they learn an appearance model representative of the background and object.
-However, as I want to point out, the tracking-by-detection algorithms can be unfeasible as training a robust classifier can be costly.
-} Learning
-an object-specific classifier in an online manner can better handle
-challenging scenarios with the cost of increased complexity.
-
-To train a (binary) classifier to detect the target at every frame,
-the classifier needs positive and negative examples. In a typical set
-up, a positive example is assumed to be given whereas a set of
-negative examples can be randomly collected from the background around
-the given positive example. Such a typical setup for a
-tracking-by-detection method might have two issues related to its
-performance: Firstly, the appearance of the randomly sampled negative
-examples might be highly correlated with that of positive one,
-resulting in ambiguous boundary between positive and negative
-classes. Secondly for a real-time tracking, such a setup would not be
-feasible for the practice because the number of training data
-gradually increases. Due to these issues, most of the
-tracking-by-detection methods focus on efficiently handling
-incremental update of the learned classifier and on collecting a
-small, but informative negative examples.
-
-{\it Burak: Why do we even mention these issues? Is this somehow
-  related to what we did for this paper?}
-
-{\it YoungWoo : They are not related at all, however, I wanted to give a brief idea about tracking-by-detection challenges.
-I feel like the text in between line 147 - 187 can precede the paragraph starting at line 122.
-Do you think it makes sense?
-This way, we give an introduction on tracking-by-detection.}
-
-\begin{comment}
-However, there can be two issues in this framework. First,
-the randomly collected samples can have large correlation resulting in
-a weak classifier. Also, such framework is not feasible for real-time
-tracking as the number of samples gradually increases. Most of the
-tracking-by-detection algorithms focus on efficient incremental update
-of a classifier together with more useful background sampling.
-\end{comment}
-
-The workflow of our MKCF based long-term target following method can
-be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss
-in the next sections.
-\begin{figure*}[!t]
-\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
-\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
-\label{Workflow_figure}
-\end{figure*}
-
-An object tracking method based on the correlation filter in frequency
-domain has gained attention due to its fast computation.
-
-\begin{comment}
-{\it Burak: This is not entirely true. If this is the case, people
-  including us don't have to invent their own, other than just using
-  KCF.}
-
-Frequency domain correlation filter based trackers in the
-tracking-by-detection paradigm has recently seen growing popularity
-due to its superior computation and robustness to geometric and
-photometric variations. 
-\end{comment}
-
-{\it YoungWoo: We'll have to mention why such an online tracker is
-  still attractive over any DNN-based counterparts.}
+For instance, their method assumes similar scale in between two
+consecutive frames given similar confidences. With this simple method,
+we do not need to run detection on different ROIs at a given frame and
+perform tracking at $\geq300$ fps. In this study, we propose the use
+of Ensemble KCFs in an intuitive way to perform robust scale-adaptive
+tracking at more than $300$ fps. Our approach is inspired by
+\cite{ma2015long} where two KCFs are employed as translation and scale
+filters. It first estimates translation using the translation filter
+learned on \textit{target}$+$\textit{background} area. Then, the scale
+filter learned on the \textit{target} area is used to estimate new
+scale of the target at the estimated position. Application of
+translation and scale filter at each frame reduces run-time
+performance ($\leq50 fps$) as we need to run detection on each scale
+candidate and perform training on both filters. Similarly, we learn
+three different correlation filters specializing on different aspects
+of tracking and addresses the weakness of each other, resulting in
+more robust tracking. We name these filters as
+\textit{target}+\textit{small background} translation filter
+($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+\textit{target}+\textit{large background} translation filter
+($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
+each frame, we can achieve the targeted operation frame rate. The
+fig.~\ref{fig:Filters} shows the size of the ROIs associated with
+$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
+windows assigned and desired Gaussian responses assigned to each one.
 
@@
 
-{\it YoungWoo : I think the following paragraph and paragraph in between line 118-143 give a brief idea about CF and KCF.
-We can probably combine them in a single paragraph followed by our contributions.}
-
-The first correlation filter tracker proposed by
-\cite{bolme2010visual} focused on learning and detection in the
-frequency domain. The idea was to minimize the sum of squared error in
-the frequency domain. Hence, the convolution in the original domain is
-avoided, instead, element-wise multiplication is needed in the
-frequency domain. This way, it achieved promising performance at 700
-Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
-changing background as it learns the filter using a single template
-and accommodates single channel features. Later on, the MOSSE tracker
-was improved by using the circularly shifted background patches in an
-efficient way by utilizing the theorem that Discrete Fourier Transform
-of a circulant matrix gives us diagonalized circulant matrix
-\cite{henriques2012exploiting,henriques2015high}. In the same work,
-the authors integrated kernelization concept into the detection and
-learning steps to improve tracking
-accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
-correlation filter trackers with single channel features to
-multi-channel features. They employed the color and shape features in
-a simple framework by summing the correlation of the test and learned
-feature channels elements. There a few major drawbacks of the
-correlation filter trackers although they outperformed the other
-discriminative trackers with superior computation. First, due to the
-nature of correlation filters it is limited to a region of interest
-which is typically 2-3 times larger than the target. Considering a
-larger ROI not only increases the computational burden but also leads
-to further spatial information loss with the fixed template size. For
-this reason, its performance degrades in fast motion cases as the ROI
-may not contain the target. Second, the correlation filter lacks scale
-adaptation ability since it only estimates the translation of the
-target. Later studies focused on improving the latter issue by
-proposing scale candidates where each scale is assigned a confidence
-by performing detection on the shrinked or enlarged the ROI
-\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
-group of studies employ the part-based correlation filter trackers to
-better adapt to the scale changes
-\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
-is generally handled in the long-term target tracking framework where
-track reinilization module is triggered when the target is lost
-\cite{ma2015long,de2015board,li2016monocular}.
-
 The contributions of this study are as follows.
@@
 
-\item \textbf{Single-Target Tracking in High-Speed} To be practical,
-  the execution time of an object tracking is important. We proposed a
-  new object tracking algorithm that is a collection of kernelized
-  correlation filters (KCF). Each of KCFs is designed to address two
-  challenges of object tracking: scale and translation. We also
-  incorporate a Bayes filter to prevent from being drift.
+\item \textbf{Novel Single-Target Tracking in High-Speed for Long-Term
+  Tracking} To be practical, the execution time of an object tracking
+  is important. We proposed a new object tracking algorithm that is a
+  collection of kernelized correlation filters (KCF). Each of KCFs is
+  designed to address two challenges of object tracking: scale and
+  translation. We also incorporate a Bayes filter to prevent from
+  being drift.
 

### 2017-04-28 draft.tex
Precision and Success Figures are Added for UAV123 and OTB100
Cleaned up the introduction.

@@
 \usepackage{comment, url}
+\usepackage{subcaption}
 
@@
 Computer vision technologies are very attractive for practical
-applications for embedded systems in that most of the embedded systems
-already includes image acquisition pipeline and a tremendous amount of
-progresses on research has been made for many areas. However, to
-successfully deploy a computer vision algorithm on any existing
-embedded systems, a vision algorithm needs to satisfy some criteria:
-minimal, manual intervention after deployment and small footprint of
-computing resource consumption and on executable code, with the
-assumption of reasonably good performance. To this end, in this paper,
-we propose an ensemble of the kernelized correlation filters (KCF), we
-call {\it E}nKCF, for a single-target object tracking. In particular,
-we developed a committee of KCFs to specifically address the
-scale-change and dynamic maneuver of the target over frames. In
-addition, we devised a Bayes filter for a smooth transition between
-individual KCFs' executions. To minimize the effect of drifting, we
-also developed another algorithm that detects target-lost, uses an
-existing object proposal method (e.g., ``Edge Box'') to re-detect the
-lost target, and re-initializes the previous tracking for a long-term
-tracking. To verify the usefulness of the proposed method, we compared
-the performance of ours to those of the existing online tracking
-methods. Experimental results showed that the performance of ours are
-72.53\% for precision on 20 pixels and 52.90\% for success rate for
-OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
-confirmed that our method outperformed the existing ones over 5\% on
-precision on 20 pixels and 10-20\% on AUC on average. Our
-implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
-DCF (457 fps), and STC (350 fps) for UAV123.
+applications for embedded systems. This is primarily because most of
+the embedded systems already includes image acquisition pipeline and a
+tremendous amount of progresses on research has been made for many
+areas in computer vision. However, to successfully deploy a computer
+vision algorithm on any existing embedded systems, a vision algorithm
+needs to satisfy some criteria: minimal, manual intervention after
+deployment and small footprint of computing resource consumption and
+on executable code, with the assumption of reasonably good
+performance. To this end, in this paper, we propose an ensemble of the
+kernelized correlation filters (KCF), we call {\it E}nKCF, for a
+single-target object tracking. In particular, we developed a committee
+of KCFs to specifically address the scale-change and dynamic maneuver
+of the target over frames. In addition, we devised a Bayes filter for
+a smooth transition between individual KCFs' executions. To minimize
+the effect of drifting, we also developed another algorithm that
+detects target-lost, uses an existing object proposal method (e.g.,
+``Edge Box'') to re-detect the lost target, and re-initializes the
+previous tracking for a long-term tracking. To verify the usefulness
+of the proposed method, we compared the performance of ours to those
+of the existing online tracking methods. Experimental results showed
+that the performance of ours are 72.53\% for precision on 20 pixels
+and 52.90\% for success rate for OTB100 data, and 55.71\% and 41.71\%
+for UAV123 data. These results confirmed that our method outperformed
+the existing ones over 5\% on precision on 20 pixels and 10-20\% on
+AUC on average. Our implementation ran at 340 fps for OTB100 and at
+416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
+and KCF (292 fps), DCF (457 fps), and STC (350 fps) for UAV123.
 \end{abstract}
@@
 \section{Introduction}
+\begin{comment}
 \begin{itemize}
@@
 \end{itemize}
-
+\end{comment}
 A recent proliferation of air/ground/water unmanned vehicle
@@
 computer vision algorithms are getting more attentions primarily
-because those mobile platforms have limited payload to carry other
-active sensors than a lightweight, monocular camera and, without
-increasing much cost, installation of a monocular camera even stereo
-rigs would increase the usefulness of a mobile platform. For example,
-instead of having just bare flight function with video recording, an
-unmanned air vehicle (UAV) equipped with object or feature following
-would make it more useful in the application of
+because payloads of those mobile platforms are limited to carry other
+sensors than a lightweight or an array of monocular cameras. For
+example, instead of having just bare flight function with video
+recording, an unmanned air vehicle (UAV) equipped with object or
+feature following would make it more useful in the application of
 monitoring/surveillance/surveying on private
@@
 target on the fly and 2) run as fast on a typical desktop as up to
-300Hz so that it could run up to 30Hz when it is deployed on a
+400Hz so that it could run up to 40Hz when it is deployed on a
 low-end, embedded system. With these features, our tracking algorithm
@@
 appropriate.
-
-{\it We may need to change this introductory sentence based on the
-  results.}
 
@@
 solution involves in expensive matrix operations
-$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
-cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
-multiplication in a frequecny domain
-\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
-a complete pipeline of an object tracker based on the correlation
-filter can be easily implemented and run very efficiently in an online
-fashion. In fact, a variant of the correlation filter, kernelized
-correlation filter with multi-channel features, outperformed other
-state-of-the-art tracking algorithms in VOT15 challenge, in terms of
-run-time and tracking accuracy. However, the vanilla form of such an
-online tracker is prone to drift, and fails to track a target over a
-long period of time primarily \cite{henriques2015high} because of the
-dilemma of stability-plasticity in updating appearance model, where
-the appearance model will be overfitted to only the images used to
-train and a compromise on the frequency of updating the model is
-carefully implemented \cite{santner2010prost}. For example, a naive
-way of handling a scale change of a target could reduce the run-time
+$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
+solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
+frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
+this reformulation, a complete pipeline of an object tracker based on
+the correlation filter can be easily implemented and run very
+efficiently in an online fashion. In fact, a variant of the
+correlation filter, kernelized correlation filter with multi-channel
+features, outperformed other state-of-the-art tracking algorithms in
+VOT15 challenge, in terms of run-time and tracking accuracy. However,
+the vanilla form of such an online tracker is prone to drift, and
+fails to track a target over a long period of time primarily
+\cite{henriques2015high} because of the dilemma of
+stability-plasticity in updating appearance model, where the
+appearance model will be overfitted to only the images used to train
+and a compromise on the frequency of updating the model is carefully
+implemented \cite{santner2010prost}. For example, a naive way of
+handling a scale change of a target could reduce the run-time
 performance from 300 to 100 fps. A seemingly obvious way of addressing
@@
 because of computational nature of correlation filter, this approach
-would just increase the computational complexity of tracking by
-running detection with multiple possibilities.
+would merely increase the computational complexity of tracking by
+running detection with multiple templates.
 
@@
 the MOSSE tracker to estimate a target's translation. The scale is
-updated in a naive way where the confidence map is used to determine
-the scale change between successive frames.
-
-For instance, their method assumes similar scale in between two
-consecutive frames given similar confidences. With this simple method,
-we do not need to run detection on different ROIs at a given frame and
-perform tracking at $\geq300$ fps. In this study, we propose the use
-of Ensemble KCFs in an intuitive way to perform robust scale-adaptive
-tracking at more than $300$ fps. Our approach is inspired by
-\cite{ma2015long} where two KCFs are employed as translation and scale
-filters. It first estimates translation using the translation filter
-learned on \textit{target}$+$\textit{background} area. Then, the scale
-filter learned on the \textit{target} area is used to estimate new
-scale of the target at the estimated position. Application of
-translation and scale filter at each frame reduces run-time
-performance ($\leq50 fps$) as we need to run detection on each scale
-candidate and perform training on both filters. Similarly, we learn
-three different correlation filters specializing on different aspects
-of tracking and addresses the weakness of each other, resulting in
-more robust tracking. We name these filters as
+updated in a way where the confidence map is used to determine the
+scale change between successive frames. This is because they assumes
+the scale of a target wouldn't change much over two consecutive
+frames. Similarly \cite{ma2015long} used two KCFs to learn the
+translation and scale of a target separately. To more specific, a KCF
+is used to learn the translation of the target and its
+background. Given this, another KCF is used to learn the target area
+to estimate a new scale of the target. However, because of running
+more than a KCF on each frame, this method degrades its run-time
+performance (i.e., $\leq 50 fps$). Our method is motivated by this
+idea -- the idea of deploying multiple KCFs to address the issues of
+single target tracking: scale and translation. In this paper, we use
+an ensemble of KCFs in turn, instead of running them all together on
+every frame. By doing so, we could still address the scale change and
+estimate target's motion efficiently while increasing run-time
+performance. In particular, we deploy three KCF in turn:
 \textit{target}+\textit{small background} translation filter
@@
 \textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
-each frame, we can achieve the targeted operation frame rate. The
-fig.~\ref{fig:Filters} shows the size of the ROIs associated with
-$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
-windows assigned and desired Gaussian responses assigned to each one.
-
+($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
+associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
+\begin{comment}
+{\it We may not need this.}
 The recent progress on development of convolutional neural networks
@@
 prior to deploy the algorithm.
+\end{comment}
 
@@
 
+\begin{figure}
+        \begin{subfigure}[b]{0.25\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.25\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
+        \end{subfigure}%
+        \caption{Pictures of animals}\label{fig:animals}
+\end{figure}
+
+\begin{figure}
+        \begin{subfigure}[b]{0.25\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.25\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
+        \end{subfigure}%
+        \caption{Pictures of animals}\label{fig:animals}
+\end{figure}
+
 %---------------------------------------------------------------------- 

### 2017-04-28 draft.tex
Results Section Improved

--- 2017-04-28 draft.tex
@@
 two publicly available datasets:
-%VOT2015 \footnote{\url{http://www.votchallenge.net/}},
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
@@
 Also, the UAVs use mobiles platforms with limited computational power.
-We believe that the proposed tracker can better fit for tracking from such platforms as it is highly efficient and scale adaptive.
+We believe that the proposed tracker can better fit to tracking from these platforms as it is highly efficient and scale adaptive.
 Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.
 
-We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success} metrics. Precision is computed as the eucl%
+We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
+Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence.
+In precision, we rank the trackers based on the precision numbers at 20 pixels.
+The success rate metric evaluates the overlap between the ground truth and tracking output.
+The intersection-to-union ratio of two regions over the frames of one sequence.
+Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames.
+We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}.
+Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers.
+These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
+Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset.
+
+\begin{figure*}
+        \begin{subfigure}[b]{0.5\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.5\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
+        \end{subfigure}%
+        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
+UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
+Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
+\end{figure*}
+
+\begin{figure*}
+        \begin{subfigure}[b]{0.5\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.5\textwidth}
+                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
+        \end{subfigure}%
+        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset.
+OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.
+}\label{fig:OTB100_DATASET}
+\end{figure*}
 

### 2017-04-28 draft.tex

--- 2017-04-28 draft.tex
@@
 Also, the UAVs use mobiles platforms with limited computational power.
-We believe that the proposed tracker can better fit for tracking from such platforms as it is highly efficient and scale adaptive.
+We believe that the proposed tracker can better fit to tracking from these platforms as it is highly efficient and scale adaptive.
 Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.
 
-We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success} metrics. Precision is computed as the eucl%
+We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
+Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence.
+In precision, we rank the trackers based on the precision numbers at 20 pixels.
+The success rate metric evaluates the overlap between the ground truth and tracking output.
+The intersection-to-union ratio of two regions over the frames of one sequence.
+Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames.
+We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}.
+Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers.
+These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
+Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset.
 
-\begin{figure}
-        \begin{subfigure}[b]{0.25\textwidth}
+\begin{figure*}
+        \begin{subfigure}[b]{0.5\textwidth}
                 \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
         \end{subfigure}%
-        \begin{subfigure}[b]{0.25\textwidth}
+        \begin{subfigure}[b]{0.5\textwidth}
                 \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
         \end{subfigure}%
-        \caption{Pictures of animals}\label{fig:animals}
-\end{figure}
+        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
+UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
+Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
+\end{figure*}
 
-\begin{figure}
-        \begin{subfigure}[b]{0.25\textwidth}
+\begin{figure*}
+        \begin{subfigure}[b]{0.5\textwidth}
                 \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
         \end{subfigure}%
-        \begin{subfigure}[b]{0.25\textwidth}
+        \begin{subfigure}[b]{0.5\textwidth}
                 \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
         \end{subfigure}%
-        \caption{Pictures of animals}\label{fig:animals}
-\end{figure}
+        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset.
+OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.
+}\label{fig:OTB100_DATASET}
+\end{figure*}
 

### 2017-04-28 draft.tex
Results Section Finished other than Re-detection

@@
 To verify the usefulness of our algorithm, we ran our algorithm using
-two publicly available datasets:
-OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
-UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
+two publicly available datasets: OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}, UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
 OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects.
@@
 
-We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
-Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence.
-In precision, we rank the trackers based on the precision numbers at 20 pixels.
-The success rate metric evaluates the overlap between the ground truth and tracking output.
-The intersection-to-union ratio of two regions over the frames of one sequence.
-Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames.
-We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}.
-Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers.
-These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
-Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset.
+\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the committee of the correlation filters are important as the each correlation filter addresses the weakness of another one.
+For instance, $R_{t}^{L}$'s main task is to recover from the previous frame where only $R_{s}$ and particle filter's prior distribution are used to estimate scale and translation.
+We set the learning rates ($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$ and $0.010$.
+The desired response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
+Finally, the Gaussian kernel parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$.
+In our particle filter implementation, we employ $1000$ particles and use the \textit{efficient number of samples} metric shown below to determine whether we need to perform importance re-sampling or not to keep reasonable variance.
+\begin{equation}
+  \hat{N}_{eff} = \dfrac{1}{\sum_{i=1}^{P}(w_{p})^{2}}, 
+\end{equation}
+ where $w$ represents the particles' weights and re-sampling is performed only if $\hat{N}_{eff}$ is smaller than three.
+
+\textbf{Features Selections.} We use the fast Histogram of Oriented Gradients (fHoG)\cite{felzenszwalb2010object} and Color-naming\cite{van2009learning} features to learn target and background models.
+$R_{t}^{L}$ uses both fHoG and color features as it covers a large ROI where fHoG features may not be reliable alone.
+On the other hand, $R_{t}^{S}$ is assigned only fHoG features as it covers smaller ROI.
+Finally, $R_{s}$ uses both fHoG and color features as it is assigned lower template size, yielding space to exploit two feature modalities.
 
@@
 
+\textbf{Overall Performance without Re-detection on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
+Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence.
+In precision, we rank the trackers based on the precision numbers at 20 pixels.
+The success rate metric evaluates the overlap between the ground truth and tracking output.
+The intersection-to-union ratio of two regions over the frames of one sequence.
+Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames.
+We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}.
+Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers.
+These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
+Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset.
+The E$n$KCF tracker outperforms the other methods in high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on the same dataset although it is $10$-$20$ times faster than these trackers.
+On the other hand, the E$n$KCF does a decent job on approximating the scale of the target in highly efficient manner.
+This is proved by the fact that it ranks third best tracker in terms of \textit{area under curve} (AUC) value for the success rate plot.
+It outperforms the high speed trackers by about $20\%$-$25\%$ in AUC metric.
+Interestingly, it performs even better than most of the low speed trackers.
+For instance, it outperforms Struct and DSST by $5\%$ and $10\%$ while running at more than $30$ and $10$ times larger operation rate.
+
+\textbf{Overall Performance without Re-detection on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset.
+Again, it performs slightly better than the high speed trackers in precision.
+Interestingly, it outperforms the another correlation filter based tracker, DSST while running only $5\%$ behind of another low-speed scale adaptive SAMF tracker.
+As in UAV123 dataset, the E$n$KCF performs exceptionally in handling the scale changes.
+It is ranked as the fifth best tracker while being the second highest speed tracker behind MOSSE.
+It performs only around $2\%$ worse than SAMF and MEEM trackers in terms of AUC.
+These numbers prove that E$n$KCF is not only a good candidate for tracking on a UAV-based mobile platform but also mobile platforms on smart phones.
+
 %---------------------------------------------------------------------- 

### 2017-04-28 bmvc_review.tex
Format Changed to BMVC Format

--- 2017-04-28 draft.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
+\documentclass{bmvc2k}
 \usepackage{graphicx}
@@
 \usepackage{comment, url}
-\usepackage{subcaption}
+%% Enter your paper number here for the review copy
+\bmvcreviewcopy{825}
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed}
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+% Enter the paper's authors in order
+% \addauthor{Name}{email/homepage}{INSTITUTION_CODE}
+\addauthor{Susan Student}{http://www.vision.inst.ac.uk/~ss}{1}
+\addauthor{Petra Prof}{http://www.vision.inst.ac.uk/~pp}{1}
+\addauthor{Colin Collaborator}{colin@collaborators.com}{2}
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+% Enter the institutions
+% \addinstitution{Name\\Address}
+\addinstitution{
+ The Vision Institute\\
+ University of Borsetshire\\
+ Wimbleham, UK
+}
+\addinstitution{
+ Collaborators, Inc.\\
+ 123 Park Avenue,\\
+ New York, USA
+}
 
-\usepackage{color}
+\runninghead{Student, Prof, Collaborator}{BMVC Author Guidelines}
 
-\newcommand{\matt}[1]{ \color{red} Matt: #1  \color{black}}
-\newcommand{\aneesh}[1]{ \color{blue} Aneesh: #1  \color{black}}
-\newcommand{\burak}[1]{ \color{green} Burak: #1  \color{black}}
-\newcommand{\emmett}[1]{\color{violet} Emmett: #1  \color{black}}
-\usepackage{forloop}
-\newcounter{ct}
-\newcommand{\markdent}[1]{\forloop{ct}{0}{\value{ct} < #1}{\hspace{\algorithmicindent}}}
-\newcommand{\markcomment}[1]{\Statex\markdent{#1}}
+% Any macro definitions you would like to include
+% These are not defined in the style file, because they don't begin
+% with \bmva, so they might conflict with the user's own macros.
+% The \bmvaOneDot macro adds a full stop unless there is one in the
+% text already.
+\def\eg{\emph{e.g}\bmvaOneDot}
+\def\Eg{\emph{E.g}\bmvaOneDot}
+\def\etal{\emph{et al}\bmvaOneDot}
+
+%-------------------------------------------------------------------------
+% Document starts here
 \begin{document}
 
-%%%%%%%%% TITLE
-\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed}
-
-\author{Burak Uzkent\\
-Rochester Institute of Technology\\
-{\tt\small bxu2522@@rit.edu}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-YoungWoo Seo\\
-Independent Robotics Research\\
-{\tt\small youngwoo.blank.seo@gmail.com}
-}
-
 \maketitle
-%\thispagestyle{empty}
 
@@
 \begin{figure}[!t]
+\centering
 \includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
@@
 \begin{equation}
-	w_{p_{t}}(x_{t},y_{t}) = \dfrac{\splitfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1)+}{y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
+	w_{p_{t}}(x_{t},y_{t}) = \dfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1){y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
 \end{equation}
@@
 
-\begin{figure*}
-        \begin{subfigure}[b]{0.5\textwidth}
-                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.5\textwidth}
-                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
-        \end{subfigure}%
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123.pdf}}
+\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123.pdf}}\\
+\end{tabular}
 \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
 UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
+Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}
+\label{fig:UAV123_DATASET}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
+\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
+\end{tabular}
+\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
+\label{fig:OTB100_DATASET}
+\end{figure}
+%\begin{figure}
+%        \begin{subfigure}{0.5\textwidth}
+%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
+%        \end{subfigure}%
+%        \begin{subfigure}{0.5\textwidth}
+%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
+%        \end{subfigure}%
+%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
+UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
 Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
-\end{figure*}
-
-\begin{figure*}
-        \begin{subfigure}[b]{0.5\textwidth}
-                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.5\textwidth}
-                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
-        \end{subfigure}%
-        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset.
+%\end{figure}
+%
+%\begin{figure}
+%        \begin{subfigure}{0.5\textwidth}
+%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
+%        \end{subfigure}%
+%        \begin{subfigure}{0.5\textwidth}
+%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
+%        \end{subfigure}%
+%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset.
 OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.
 }\label{fig:OTB100_DATASET}
-\end{figure*}
+%\end{figure}
 
@@
 
-\small
-\bibliographystyle{ieee}
 \bibliography{draft}
-
 \end{document}

### 2017-04-28 bmvc_review.tex
Revised the introduction.

@@
 A recent proliferation of air/ground/water unmanned vehicle
-technologies has ever increased interests on deployment of intelligent
+technologies has ever increased interests on deploying intelligent
 algorithms on embedded or mobile platforms. Among those technologies,
 computer vision algorithms are getting more attentions primarily
-because payloads of those mobile platforms are limited to carry other
-sensors than a lightweight or an array of monocular cameras. For
+because payloads of those mobile platforms are limited to carry any
+other sensors than a lightweight or an array of monocular cameras. For
 example, instead of having just bare flight function with video
-recording, an unmanned air vehicle (UAV) equipped with object or
-feature following would make it more useful in the application of
-monitoring/surveillance/surveying on private
+recording, an unmanned air vehicle (UAV) equipped with an object or
+feature following functionality would make it more useful in the
+application of monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
@@
 
-In this paper, we propose a single-target tracking that aims at
-running on any embedded or mobile platforms that doesn't require an
-offline training, and can run on an embedded system. In particular, we
-would like to make our algorithm 1) learn the appearance model of a
-target on the fly and 2) run as fast on a typical desktop as up to
-400Hz so that it could run up to 40Hz when it is deployed on a
+In this paper, we propose a single-target tracking aiming at running
+on any embedded or mobile platforms that doesn't require an offline
+training, and can run on an embedded system. In particular, we would
+like to make our algorithm 1) learn the appearance model of a target
+on the fly and 2) run as fast on a typical desktop as up to 300Hz so
+that it could run, at least, faster than 30Hz when it is deployed on a
 low-end, embedded system. With these features, our tracking algorithm

### 2017-04-28 bmvc_review.tex
Revised the introduction.

@@
 frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
-this reformulation, a complete pipeline of an object tracker based on
-the correlation filter can be easily implemented and run very
-efficiently in an online fashion. In fact, a variant of the
-correlation filter, kernelized correlation filter with multi-channel
-features, outperformed other state-of-the-art tracking algorithms in
-VOT15 challenge, in terms of run-time and tracking accuracy. However,
-the vanilla form of such an online tracker is prone to drift, and
-fails to track a target over a long period of time primarily
-\cite{henriques2015high} because of the dilemma of
+this reformulation, an object tracking pipeline based on the
+correlation filter can be easily implemented and run very efficiently
+in an online fashion. In fact, a variant of the correlation filter,
+the kernelized correlation filter with multi-channel features
+\cite{henriques2015high} showed impressive object trackin results and
+outperformed other state-of-the-art tracking algorithms, for example,
+in VOT15 challenge, in terms of run-time and tracking
+accuracy. However, the vanilla form of such an online tracker is prone
+to drift, and fails to track a target over a long period of time
+primarily \cite{henriques2015high} because of the dilemma of
 stability-plasticity in updating appearance model, where the
@@
 find the target
-\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
-because of computational nature of correlation filter, this approach
-would merely increase the computational complexity of tracking by
-running detection with multiple templates.
+\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
+to the computational nature of correlation filter, however, this
+approach would merely increase the computational complexity because it
+has to run the correlation filter multiple times on each frame.
 
@@
 \begin{itemize}
-
-\item \textbf{Novel Single-Target Tracking in High-Speed for Long-Term
-  Tracking} To be practical, the execution time of an object tracking
-  is important. We proposed a new object tracking algorithm that is a
-  collection of kernelized correlation filters (KCF). Each of KCFs is
-  designed to address two challenges of object tracking: scale and
-  translation. We also incorporate a Bayes filter to prevent from
-  being drift.
+\item \textbf{Novel Single-Target Tracking in a Very High-Speed} Our
+  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
+  efficiently address the scale variance and the dynamic maneuver of a
+  target while perserving run-time performance as high as possible. To
+  minimize any potential performance gap from transiting one KCF to
+  another, we use a Bayes filter.
 

### 2017-04-29 bmvc_review.tex
EnKCF technical explanation added - KCF needs to be trimmed now

@@
   minimize any potential performance gap from transiting one KCF to
-  another, we use a Bayes filter.
+  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
+  be visualized in fig.~\ref{Workflow_figure}.
 
@@
 
-The workflow of our MKCF based long-term target following method can
-be visualized in fig.~\ref{Workflow_figure}. Summarize what we discuss
-in the next sections.
 \begin{figure*}[!t]
@@
 
-The KCF with multi-channel features outperform the other
-state-of-the-art object traking algorithms in VOT15 challenge in terms of run-time
-performance and tracking accuracy. However, it lacks scale adaptation
-module or the naive scale adaptation method added into the KCF reduces
-the frames per second from $\geq300$ fps to less than $100$ fps. One
-straightforward method is to run detection on ROIs with different
-sizes determined by pre-defined scale ratios
-\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. All
-these method increases the computational complexity of tracking by
-running detection on a number of ROIs. Another scale update method in
-Correlation Filter framework was proposed by \cite{zhang2014fast}. It
-uses the MOSSE tracker to estimate translation of an object. The scale
-is updated in a naive way where the confidence map is used to
-determine the scale change between successive frames. For instance,
-their method assumes similar scale in between two consecutive frames
-given similar confidences. With this simple method, we do not need to
-run detection on different ROIs at a given frame and perform tracking
-at $\geq300$ fps. In this study, we propose the use of Ensemble KCFs
+In this study, we propose application of an ensemble of KCFs
 in an intuitive way to perform robust scale-adaptive tracking at more
@@
 the target at the estimated position. Application of translation and
-scale filter at each frame reduces run-time performance ($\leq50 fps$)
+scale filter at each frame decreases run-time performance ($\leq50 fps$)
 as we need to run detection on each scale candidate and perform training on both filters. Similarly,
 we learn three different correlation filters specializing on different
-aspects of tracking and addresses the weakness of each other,
+aspects of tracking and addressing the weakness of each other,
 resulting in more robust tracking. We name these filters as
@@
 \textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
-each frame, we can achieve the targeted operation frame rate. The
-fig.~\ref{fig:Filters} shows the size of the ROIs associated with
+($R_{t}^{L}$). The fig.~\ref{fig:Filters} shows the size of the ROIs associated with
 $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
-windows assigned and desired Gaussian responses assigned to each one.
+windows assigned and desired Gaussian responses assigned to each one. Unlike \cite{ma2015long}, by running a single filter at
+each frame, we can achieve the targeted operation frame rate.
+In our framework, each filter is only trained after it is run to estimate translation or scale.
+This makes more sense as neighboring frames show large correlation.
+Thus, skipping a few frames to train a filter does not result in dramatic information loss in the learned object model.
 
@@
  to learn the scale filter, resulting in higher speed scale
-estimation module. Finally, the scale filter help us on the track
+estimation module and earning us some time to update scale. Finally, the scale filter help us on the track
 re-initialization module which includes running an object proposals
-algorithm to boxes bounding the objects in the scene. By using the
+algorithm to extract proposals from salient regions. By using the
 scale filter in re-initialization module, we can reduce the
@@
 is assigned a larger template size than $R_{s}$ and smaller than
-$R_{t}^{L}$. It is employed to estimate translation and scale similar
+$R_{t}^{L}$. It estimates only translation similar
 to \cite{henriques2015high}. Finally, the \textit{target+large
-  background} area translation filter, $R_{t}^{L}$ , estimates only
-the translation of a target. We propose scale estimation at every $n$ number of frames using the scale filter. In our experiments on $OTB100$ and $UAV123$,
+  background} area translation filter, $R_{t}^{L}$ , estimates translation of a target as $R_{t}^{S}$.
+We propose scale estimation at every $n$ number of frames using the scale filter.
+In our experiments on $OTB100$ and $UAV123$,
 we observed that $n$ = 5 gives the best results in terms of precision and success overlap rates. The \textit{target+large background} translation filter is run
-in the next frame after the scale filter as we want to avoid drifts.
-Considering large ROI for $R_{t}^{L}$ can degrade its performance due to low resolution template.
-For this reason, we employ \textit{Color} and \textit{HoG} features for $R_{t}^{L}$ correlation filter.
-Finally, $R_{t}^{S}$ is applied after $R_{t}^{L}$ to avoid any target loss due to low resolution template used by $R_{t}^{L}$.
-Unlike $R_{t}^{L}$, we only employ the \textit{HoG} features for the $R_{t}^{S}$ correlation filter.
-Fig.~\ref{Workflow_figure} displays the proposed tracking framework using Ensemble of KCFs.
-Also, the pseudo-code of the proposed $EnKCF$ is shown in alg.~\ref{alg:MKCF}.
+in the next frame after the scale filter as we want to avoid drifts which is more likely to happen running only $R_{s}$.
+Considering a large ROI for $R_{t}^{L}$ can degrade its performance due to information loss resulting from ROI resizing.
+On the other hand, only HoG features are used in $R_{t}^{S}$ as it focuses on a smaller ROI, giving us more discriminative HoG features.
+In our framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$.
+$R_{t}^{S}$, on the other hand, focuses on the shape features of the target that is not fully exploited in $R_{t}^{L}$ and $R_{t}^{S}$.
+For this reason, we employ \textit{HoG} features in $R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in $R_{t}^{L}$.
+Fig.~\ref{Workflow_figure} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC.
+Also, the pseudo-code of the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.
 

### 2017-04-29 bmvc_review.tex
EnKCF technical explanation added - KCF trimmed

@@
 increasingly popular due to its operation at hundreds of frames per
-second with state-of-the-art tracking capabilities in challenging
-cases. Its computational efficiency arises from its use of the
+second with state-of-the-art tracking capabilities even in challenging
+cases such as VOT15 dataset. Its computational efficiency arises from its use of the
 discrete fourier transform of the circulant matrix and frequency
-domain element-wise operations knows hadamard product and
+domain element-wise operations known as hadamard product and
 division. The first example of frequency domain trackers is the Linear
@@
 \begin{equation}
-E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}g*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
+E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
 \label{eq:Closedform_RidgeReg}
@@
 background patches at a similar computational complexity. A circulant
-matrix $C$ includes the circularly shifted patches of the positive
-training sample $x$ by the cylic shift operator $P$. By applying
-shifting operation to the base sample, we can generate the circulant
-matrix as
-\begin{equation}
-C = Px.
-\label{eq:CirculantMatrixGeneration}
-\end{equation}
-The circulant matrix of a base sample $x$ can be interpreted as the
-rows of a training matrix $X$ where each row represents features of a
-training sample. Mathematically, this can be written as
-\begin{equation}
-X = C(x)
-\label{eq:CIrculantMatrixTrainingData}
-\end{equation}
+matrix includes the circularly shifted patches of the positive
+training sample $x$ by a cylic shift operator.
+
+%By applying shifting operation to the base sample, we can generate the circulant
+%matrix as
+%\begin{equation}
+%C = Px.
+%\label{eq:CirculantMatrixGeneration}
+%\end{equation}
+%The circulant matrix of a base sample $x$ can be interpreted as the
+%rows of a training matrix $X$ where each row represents features of a
+%training sample. Mathematically, this can be written as
+%\begin{equation}
+%X = C(x)
+%\label{eq:CIrculantMatrixTrainingData}
+%\end{equation}
+
 In this form, eq.~\ref{eq:SpatialSolution}
@@
 \begin{equation}
-X = Fdiag(\hat{x})F^{H}.
+X = Fdiag(\hat{x})F^{H},
 \label{eq:CirculantMatrixDFT}
@@
 where $F$ denotes a constant Fourier Transform matrix and $x$ is the
-Discrete Fourier Transform of the base sample $x$. To simplify the
-cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
-$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
-\begin{equation}
-X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
-\label{eq:SimplificationX} 
-\end{equation}
-Finally, the eq.~\ref{eq:SimplificationX} can used to formulate the
-solution vector in Fourier domain $\hat{w}$ as
+Discrete Fourier Transform of the base sample $x$. 
+%To simplify the
+%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
+%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
+%\begin{equation}
+%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
+%\label{eq:SimplificationX} 
+%\end{equation}
+The solution vector in the Fourier domain $\hat{w}$ is formulated as
 \begin{equation}
@@
 \begin{equation}
-\alpha = y(K+\lambda I)^{-1}
+\alpha = y(K+\lambda I)^{-1},
 \end{equation}
-wjere $K$ and $\alpha$ represent the kernel matrix and corresponding
-dual space solution. \cite{henriques2015high} states that kernel
-matrices is circulant for datasets of circular cylic satisfying the
-following theorem.
-\begin{equation}
-k(x,x^{'}) = k(Mx,Mx^{'})
-\label{eq:KernelCirculantTheorem}
-\end{equation}
-where $M$ represents the permutation matrix. Some kernels satisfying
-the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
-\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
-kernels. Similar to the diagonalization in the linear ridge regression
+where $K$ and $\alpha$ represent the kernel matrix and corresponding
+dual space solution.
+
+%\cite{henriques2015high} states that kernel
+%matrices is circulant for datasets of circular cylic satisfying the
+%following theorem.
+%\begin{equation}
+%k(x,x^{'}) = k(Mx,Mx^{'}),
+%\label{eq:KernelCirculantTheorem}
+%\end{equation}
+%where $M$ represents the permutation matrix. Some kernels satisfying
+%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
+%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
+%kernels.
+
+Similar to the diagonalization in the linear ridge regression
 solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized
@@
 documentation of the application of other kernels to the Correlation
-Filters. For single channel features, the Gaussian kernelization is
+Filters. The Gaussian kernelization is
 expressed as
-\begin{equation}
-k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
-\label{eq:GaussianCorrelationSingleChannel}
-\end{equation}
-The first correlation filter based trackers used grayscale feature to
-learn the solution vector $w$, however, the multi-channel features
-such as HoG and Color were later exploited to improve tracking
-accuracy
-\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
-multi-channel feature integration into the Gaussian Kernelization
-function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
-in a very straight-forward way by summing the correlation result in
-all the channels as
 \begin{equation}
@@
 \end{equation}
+%\begin{equation}
+%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
+%\label{eq:GaussianCorrelationSingleChannel}
+%\end{equation}
+The first correlation filter based trackers used grayscale feature ($C=1$) to
+learn the solution vector $w$, however, the multi-channel features
+such as HoG and Color were later exploited to improve tracking
+accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
+multi-channel feature integration into the Gaussian Kernelization
+function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
+in a very straight-forward way by summing the correlation result over the channels.
+
 Such non-linearization process does not increase the computational
@@
 as we only need to sum over the $n$ dimensional feature
-channels. Training shown in eq:~\ref{eq:FourierDualDomainSolution}
+channels. Training shown in eq.~\ref{eq:FourierDualDomainSolution}
 gives us $\hat{a}$ learned in time step $t$. We can accumulate

### 2017-04-29 bmvc_review.tex
EnKCF technical explanation added - KCF trimmed - PF Left
EnKCF2 Added

@@
 \begin{itemize}
-\item \textbf{Novel Single-Target Tracking in a Very High-Speed} Our
+\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
   algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
@@
   another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
-  be visualized in fig.~\ref{Workflow_figure}.
+  be visualized in fig.~\ref{Workflow_figure_EnKCF}.
 
-\item \textbf{Re-Detection} A target loss is inevitable in object
+\item \textbf{More Accurate Single-Target Tracking in a Relatively Lower-Speed ( $\geq 150$ fps)} Our second algorithm, 
+{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose. The original {\it E}nKCF is slighlty
+modified to perform more accurate in more challenging scenarios, particularly the ones with large ego-motion and object
+motion. We do not integrate the particle filter in {\it E}nKCF2 as we test it on a dataset (UAV123$\_$10fps) including sequences
+with large ego-motion on the UAV platform. The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
+
+\begin{comment}\item \textbf{Re-Detection} A target loss is inevitable in object
   tracking. To cope with this, we developed a new target, re-detection
@@
 
-\begin{comment}
 \item We build a highly efficient ($\geq300$ fps) scale adaptive
@@
 \caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
-\label{Workflow_figure}
+\label{Workflow_figure_EnKCF}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
+\caption{The workflow of our EnKCF2 tracker that is more robust to large camera and fast object motion than our EnKCF tracker.}
+\label{Workflow_figure_EnKCF2}
 \end{figure*}
@@
 For this reason, we employ \textit{HoG} features in $R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in $R_{t}^{L}$.
-Fig.~\ref{Workflow_figure} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC.
+Fig.~\ref{Workflow_figure_EnKCF} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC.
 Also, the pseudo-code of the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.
@@
 
-WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE
-POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
-\section{Track Re-initilization via Re-detection}
-\label{sc:Re-initialization}
-
 %\section{Geometry Estimation between Target and Drone}
@@
 Finally, the Gaussian kernel parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$.
+We note that all the hyper-parameters are same for EnKCF and EnKCF2 trackers.
+We only set the learning rate of $R_{t}^{L}$ to $0.12$.
 In our particle filter implementation, we employ $1000$ particles and use the \textit{efficient number of samples} metric shown below to determine whether we need to perform importance re-sampling or not to keep reasonable variance.
+
 \begin{equation}
@@
 Finally, $R_{s}$ uses both fHoG and color features as it is assigned lower template size, yielding space to exploit two feature modalities.
+We emphasize that same features are applied to the correlations filters in EnKCF and EnKCF2 trackers.
 
@@
 \end{figure}
-%\begin{figure}
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
-%        \end{subfigure}%
-%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
-UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
-Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
-%\end{figure}
-%
-%\begin{figure}
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
-%        \end{subfigure}%
-%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset.
-OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.
-}\label{fig:OTB100_DATASET}
-%\end{figure}
 
-\textbf{Overall Performance without Re-detection on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
+\textbf{Overall Performance on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
 Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence.
@@
 
-\textbf{Overall Performance without Re-detection on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset.
+\textbf{Overall Performance on UAV123$\_$10fps Dataset.}
+
+\textbf{Overall Performance on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset.
 Again, it performs slightly better than the high speed trackers in precision.

### 2017-04-30 bmvc_review.tex
Revised the introduction and technical section.

--- 2017-04-29 bmvc_review.tex
@@
 \includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
-\caption{The workflow of our Multiple KCF and Particle Filter based tracking method without the track re-detection module.}
+\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
 \label{Workflow_figure}
@@
 
-In this study, we propose application of an ensemble of KCFs
-in an intuitive way to perform robust scale-adaptive tracking at more
-than $300$ fps. Our approach is inspired by \cite{ma2015long} where
-two KCFs are employed as translation and scale filters. It first
-estimates translation using the translation filter learned on
-\textit{target}$+$\textit{background} area. Then, the scale filter
-learned on the \textit{target} area is used to estimate new scale of
-the target at the estimated position. Application of translation and
-scale filter at each frame decreases run-time performance ($\leq50 fps$)
-as we need to run detection on each scale candidate and perform training on both filters. Similarly,
-we learn three different correlation filters specializing on different
-aspects of tracking and addressing the weakness of each other,
-resulting in more robust tracking. We name these filters as
-\textit{target}+\textit{small background} translation filter
-($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
-\textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). The fig.~\ref{fig:Filters} shows the size of the ROIs associated with
-$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
-windows assigned and desired Gaussian responses assigned to each one. Unlike \cite{ma2015long}, by running a single filter at
-each frame, we can achieve the targeted operation frame rate.
-In our framework, each filter is only trained after it is run to estimate translation or scale.
-This makes more sense as neighboring frames show large correlation.
-Thus, skipping a few frames to train a filter does not result in dramatic information loss in the learned object model.
+In this paper, we extends the KCF in that multiple KCFs are deployed,
+in turn, to address a target's scale change and dynamic maneuvers
+while preserving the overall execution time very fast, i.e., $\ge$ 300
+fps. The efficient nature of KCF computation results in a
+small-footprint, executable. Such a fast execution will facilitate to
+deploy the proposed algorithm on any embedded systems.
+
+The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
+first filter, $R_{t}^{S}$, focuses on learning the target area and its
+background, \textit{target}+\textit{small background} for addressing a
+marginal translation by a target, the second filter, $R_{s}$, focuses
+entirely on learning the target's scale, \textit{target-only}, and the
+last filter, $R_{t}^{L}$, focuses on the target area and its
+background twice bigger than that of the first filter, $R_{t}^{S}$,
+\textit{target}+\textit{large background}. We set up {\it E}nKCF in
+this way because we believe a correlation filter for learning a
+target's translation should include its background to better
+discriminate the target from its background and another correlation
+filter is prepared to focus on the target itself to estimate the right
+size or scale of the target. Figure \ref{fig:Filters} shows examples
+of the region of interest (ROI) covered by each of three filters. We
+believe that a filter for learning a target's translation should
+include its background. In addition, making the ROI for the scale
+filter, $R_{s}$, tighter reduces the size of the template for the
+elementwise multiplication, resulting in a scale estimation in a
+higher speed.
+
+After Heriques and his colleagues' presented impressive tracking
+results of KCF \cite{henriques2015high}, many variation of KCF were
+investigated. In particular, \cite{ma2015long} and
+\cite{danelljan2014accurate} used a scale filter to learn the target
+area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
+used a correlation filter learned on the target area and its
+surrounding background in different size to learn the optimal scale of
+the target. Our approach is particularly similar to that of
+\cite{ma2015long} in that more than one KCF is used to address the
+challenges of single target tracking. But ours is different from that
+of \cite{ma2015long} in that we do not use those three KCFs together
+at every frame, but alternatively at every three frame. The way our
+algorithm is alternating multiple KCFs in different goals intuitively
+makes sense in that the appearance of consecutive images does not
+change much. Although it varies based on the scene, learning a
+correlation filter a frame would not be much different from the one
+learned using the image few or $k$ frames later. By alternating three
+KCFs in turn, our algorithm runs as fast as or faster than the
+original KCF. From our experiments, we empirically found that five is
+the optimal for $k$ in terms of precision and success rates. We'll
+detail this at the experimental section later.
 
@@
 
-Our MKCF based tracking framework employs different capabilities and
-tasks to each correlation filter learned temporally. In
-\cite{ma2015long, danelljan2014accurate}, a scale filter is learned on
-\textit{target-only} area whereas \cite{henriques2015high,
-  li2014scale, bibi2015multi, tang2015multi} uses a correlation filter
-learned on \textit{target+background} area to find the optimal scale
-in scale space. To learn the scale filter, $R_{s}$, we follow a
-similar approach to \cite{ma2015long}. We believe that translation
-filter needs to include background information to better discriminate
-target from background, however, the goal of the scale filter is to
-estimate the right size of the target, not to discriminate it from
-background. Also, by using a smaller ROI we can reduce the template size
- to learn the scale filter, resulting in higher speed scale
-estimation module and earning us some time to update scale. Finally, the scale filter help us on the track
-re-initialization module which includes running an object proposals
-algorithm to extract proposals from salient regions. By using the
-scale filter in re-initialization module, we can reduce the
-element-wise operations compared to the translation filters. Also, we can 
-avoid false target re-initialization in the case of rapid background change as $R_{t}^{s}$ and
-$R_{t}^{L}$ learn background in addition to target. The \textit{target+small background} area translation filter, $R_{t}^{S}$,
-is assigned a larger template size than $R_{s}$ and smaller than
-$R_{t}^{L}$. It estimates only translation similar
-to \cite{henriques2015high}. Finally, the \textit{target+large
-  background} area translation filter, $R_{t}^{L}$ , estimates translation of a target as $R_{t}^{S}$.
-We propose scale estimation at every $n$ number of frames using the scale filter.
-In our experiments on $OTB100$ and $UAV123$,
-we observed that $n$ = 5 gives the best results in terms of precision and success overlap rates. The \textit{target+large background} translation filter is run
-in the next frame after the scale filter as we want to avoid drifts which is more likely to happen running only $R_{s}$.
-Considering a large ROI for $R_{t}^{L}$ can degrade its performance due to information loss resulting from ROI resizing.
-On the other hand, only HoG features are used in $R_{t}^{S}$ as it focuses on a smaller ROI, giving us more discriminative HoG features.
-In our framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$.
-$R_{t}^{S}$, on the other hand, focuses on the shape features of the target that is not fully exploited in $R_{t}^{L}$ and $R_{t}^{S}$.
-For this reason, we employ \textit{HoG} features in $R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in $R_{t}^{L}$.
-Fig.~\ref{Workflow_figure} displays the proposed tracking framework called Ensemble of KCFs {\it E}nKC.
-Also, the pseudo-code of the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.
+The order of deploying these three KCFs is {\it Burak: Answer this}
+
+The \textit{target+large background} translation filter, $R_{t}^{L}$,
+is designed to run in right next frame after the scale filter,
+$R_s$. We deploy these two filters in this way because we want to
+minimize any drifts, which are likely to happen running only $R_{s}$.
+
+{\it Burak: Rewrite the following two sentences.}
+
+Considering a large ROI for $R_{t}^{L}$ can degrade its performance
+due to information loss resulting from ROI resizing.
+
+On the other hand, only HoG features are used in $R_{t}^{S}$ as it
+focuses on a smaller ROI, giving us more discriminative HoG
+features.
+
+The reason why our {\it E}nKCF comes with two KCF for translation {\it
+  Burak: Answer this.}
+
+In our framework, $R_{t}^{S}$ addresses the absence of scale
+adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
+focuses on addressing the absence of translation estimation module in
+$R_{S}$.
+
+$R_{t}^{S}$, on the other hand, focuses on the shape features
+of the target that is not fully exploited in $R_{t}^{L}$ and
+$R_{t}^{S}$. For this reason, we employ \textit{HoG} features in
+$R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in
+$R_{t}^{L}$. Fig.~\ref{Workflow_figure} displays the proposed tracking
+framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of
+the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.
 
@@
 
+\subsection{Kernelized Correlation Filter} \label{sec:kcf}
 The Kernelized Correlation Filter tracker has recently been
@@
 second with state-of-the-art tracking capabilities even in challenging
-cases such as VOT15 dataset. Its computational efficiency arises from its use of the
-discrete fourier transform of the circulant matrix and frequency
-domain element-wise operations known as hadamard product and
+cases such as VOT15 dataset. Its computational efficiency arises from
+its use of the discrete fourier transform of the circulant matrix and
+frequency domain element-wise operations known as hadamard product and
 division. The first example of frequency domain trackers is the Linear
@@
 
-\section{Particle Filter}
-\label{sc:PF}
+\subsection{Particle Filter} \label{sc:PF}
 The proposed MKCF algorithm can cause undesired drift and noise in
@@
 
-WE SHOULD ASSIGN THE PRIOR WEIGHTS TO EXPECTED MEAN ESTIMATION OF THE
-POSTERIORS WHEN THE RE-SAMPLING IS SKIPPED.
-\section{Track Re-initilization via Re-detection}
-\label{sc:Re-initialization}
-
-%\section{Geometry Estimation between Target and Drone}
-%\label{sc:Geometry}
-
 %----------------------------------------------------------------------
@@
 %---------------------------------------------------------------------- 
-To verify the usefulness of our algorithm, we ran our algorithm using
-two publicly available datasets: OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}, UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
-OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects.
-The proposed $EnKCF$ method can better handle slow motions.
-Also, the UAVs use mobiles platforms with limited computational power.
-We believe that the proposed tracker can better fit to tracking from these platforms as it is highly efficient and scale adaptive.
-Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.
+To verify the usefulness of our algorithm, we ran the proposed
+algorithm against two publicly, available datasets:
+OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
+UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. OTB100
+dataset contains video sequences for 100 objects whereas UAV123
+dataset contains aerial footage of 123 objects.
 
-\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the committee of the correlation filters are important as the each correlation filter addresses the weakness of another one.
-For instance, $R_{t}^{L}$'s main task is to recover from the previous frame where only $R_{s}$ and particle filter's prior distribution are used to estimate scale and translation.
-We set the learning rates ($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$ and $0.010$.
-The desired response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
-Finally, the Gaussian kernel parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$.
-In our particle filter implementation, we employ $1000$ particles and use the \textit{efficient number of samples} metric shown below to determine whether we need to perform importance re-sampling or not to keep reasonable variance.
+The proposed $E$nKCF method can better handle slow motions. Also, the
+UAVs use mobiles platforms with limited computational power. We
+believe that the proposed tracker can better fit to tracking from
+these platforms as it is highly efficient and scale adaptive. Taking
+into account these reasons, it is more appropriate to test it on
+aerial videos captured by UAVs.
+
+\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the
+committee of the correlation filters are important as the each
+correlation filter addresses the weakness of another one. For
+instance, $R_{t}^{L}$'s main task is to recover from the previous
+frame where only $R_{s}$ and particle filter's prior distribution are
+used to estimate scale and translation. We set the learning rates
+($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$
+and $0.010$. The desired response and hanning window for each KCF is
+shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel
+parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for
+$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. In our particle filter
+implementation, we employ $1000$ particles and use the
+\textit{efficient number of samples} metric shown below to determine
+whether we need to perform importance re-sampling or not to keep
+reasonable variance.
 \begin{equation}
@@
 
-\textbf{Features Selections.} We use the fast Histogram of Oriented Gradients (fHoG)\cite{felzenszwalb2010object} and Color-naming\cite{van2009learning} features to learn target and background models.
-$R_{t}^{L}$ uses both fHoG and color features as it covers a large ROI where fHoG features may not be reliable alone.
-On the other hand, $R_{t}^{S}$ is assigned only fHoG features as it covers smaller ROI.
-Finally, $R_{s}$ uses both fHoG and color features as it is assigned lower template size, yielding space to exploit two feature modalities.
+\textbf{Features Selections.} We use the fast Histogram of Oriented
+Gradients (fHoG)\cite{felzenszwalb2010object} and
+Color-naming\cite{van2009learning} features to learn target and
+background models. $R_{t}^{L}$ uses both fHoG and color features as it
+covers a large ROI where fHoG features may not be reliable alone. On
+the other hand, $R_{t}^{S}$ is assigned only fHoG features as it
+covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features
+as it is assigned lower template size, yielding space to exploit two
+feature modalities.
 
@@
 
-\textbf{Overall Performance without Re-detection on UAV123 Dataset.} We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success\:Rate} metrics.
-Precision is computed by thresholding the average euclidean distance between the ground truth and tracking output over the frames of one sequence.
-In precision, we rank the trackers based on the precision numbers at 20 pixels.
-The success rate metric evaluates the overlap between the ground truth and tracking output.
-The intersection-to-union ratio of two regions over the frames of one sequence.
-Finally, we count the number of frames with overlap larger than the success rate threshold and divide it by the number of frames.
-We compare our tracker to some other high-speed ($\geq$300 fps) state-of-the-art trackers including KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast}, MOSSE\cite{bolme2010visual,henriques2015high}.
-Also, some relatively lower-speed ($\geq$50) trackers are used to evaluate the robustness of the proposed trackers.
-These trackers include SAMF\cite{li2014scale}, DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long}, MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
-Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset.
-The E$n$KCF tracker outperforms the other methods in high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on the same dataset although it is $10$-$20$ times faster than these trackers.
-On the other hand, the E$n$KCF does a decent job on approximating the scale of the target in highly efficient manner.
-This is proved by the fact that it ranks third best tracker in terms of \textit{area under curve} (AUC) value for the success rate plot.
-It outperforms the high speed trackers by about $20\%$-$25\%$ in AUC metric.
-Interestingly, it performs even better than most of the low speed trackers.
-For instance, it outperforms Struct and DSST by $5\%$ and $10\%$ while running at more than $30$ and $10$ times larger operation rate.
+\textbf{Overall Performance without Re-detection on UAV123 Dataset.}
+We compare the proposed tracker to other state-of-the-art high speed
+trackers using the \textit{Precision} and \textit{Success\:Rate}
+metrics. Precision is computed by thresholding the average euclidean
+distance between the ground truth and tracking output over the frames
+of one sequence. In precision, we rank the trackers based on the
+precision numbers at 20 pixels. The success rate metric evaluates the
+overlap between the ground truth and tracking output. The
+intersection-to-union ratio of two regions over the frames of one
+sequence. Finally, we count the number of frames with overlap larger
+than the success rate threshold and divide it by the number of
+frames. We compare our tracker to some other high-speed ($\geq$300
+fps) state-of-the-art trackers including KCF\cite{henriques2015high},
+CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast},
+MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
+lower-speed ($\geq$50) trackers are used to evaluate the robustness of
+the proposed trackers. These trackers include SAMF\cite{li2014scale},
+DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
+MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
+Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
+dataset. The E$n$KCF tracker outperforms the other methods in
+high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
+accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
+the same dataset although it is $10$-$20$ times faster than these
+trackers. On the other hand, the E$n$KCF does a decent job on
+approximating the scale of the target in highly efficient manner. This
+is proved by the fact that it ranks third best tracker in terms of
+\textit{area under curve} (AUC) value for the success rate plot. It
+outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
+metric. Interestingly, it performs even better than most of the low
+speed trackers. For instance, it outperforms Struct and DSST by $5\%$
+and $10\%$ while running at more than $30$ and $10$ times larger
+operation rate.
 
-\textbf{Overall Performance without Re-detection on OTB100 Dataset.} In addition to UAV123 dataset, we test the E$n$KCF tracker on the OTB100 dataset to evaluate how good it generalizes to a traditional object tracking dataset.
-Again, it performs slightly better than the high speed trackers in precision.
-Interestingly, it outperforms the another correlation filter based tracker, DSST while running only $5\%$ behind of another low-speed scale adaptive SAMF tracker.
-As in UAV123 dataset, the E$n$KCF performs exceptionally in handling the scale changes.
-It is ranked as the fifth best tracker while being the second highest speed tracker behind MOSSE.
-It performs only around $2\%$ worse than SAMF and MEEM trackers in terms of AUC.
-These numbers prove that E$n$KCF is not only a good candidate for tracking on a UAV-based mobile platform but also mobile platforms on smart phones.
+\textbf{Overall Performance without Re-detection on OTB100 Dataset.}
+In addition to UAV123 dataset, we test the E$n$KCF tracker on the
+OTB100 dataset to evaluate how good it generalizes to a traditional
+object tracking dataset. Again, it performs slightly better than the
+high speed trackers in precision. Interestingly, it outperforms the
+another correlation filter based tracker, DSST while running only
+$5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
+UAV123 dataset, the E$n$KCF performs exceptionally in handling the
+scale changes. It is ranked as the fifth best tracker while being the
+second highest speed tracker behind MOSSE. It performs only around
+$2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
+prove that E$n$KCF is not only a good candidate for tracking on a
+UAV-based mobile platform but also mobile platforms on smart phones.
 

### 2017-04-30 bmvc_review.tex
Paper Updated - PF, CFs Order, Some More Updates

@@
   another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
-  be visualized in fig.~\ref{Workflow_figure}.
+  be visualized in fig.~\ref{Workflow_figure_EnKCF}.
+The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
+  datasets.
 
-\item \textbf{Re-Detection} A target loss is inevitable in object
+\item \textbf{Slight Modification of the proposed EnKCF for Handling Large Motion} Our second algorithm, 
+{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose.
+The original {\it E}nKCF is slighlty modified to track fast motions and handle large ego-motion.
+We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on the low frame rate UAV platform.
+Particle Filter can be deployed in case the camera motion is known.
+The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
+
+\begin{comment}\item \textbf{Re-Detection} A target loss is inevitable in object
   tracking. To cope with this, we developed a new target, re-detection
@@
 %---------------------------------------------------------------------- 
-
 \begin{figure*}[!t]
@@
 \caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
-\label{Workflow_figure}
+\label{Workflow_figure_EnKCF}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
+\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
+\label{Workflow_figure_EnKCF2}
 \end{figure*}
@@
 
-After Heriques and his colleagues' presented impressive tracking
+After Henriques and his colleagues' presented impressive tracking
 results of KCF \cite{henriques2015high}, many variation of KCF were
@@
 
-The order of deploying these three KCFs is {\it Burak: Answer this}
-
-The \textit{target+large background} translation filter, $R_{t}^{L}$,
-is designed to run in right next frame after the scale filter,
-$R_s$. We deploy these two filters in this way because we want to
-minimize any drifts, which are likely to happen running only $R_{s}$.
-
-{\it Burak: Rewrite the following two sentences.}
-
-Considering a large ROI for $R_{t}^{L}$ can degrade its performance
-due to information loss resulting from ROI resizing.
-
-On the other hand, only HoG features are used in $R_{t}^{S}$ as it
-focuses on a smaller ROI, giving us more discriminative HoG
-features.
-
-The reason why our {\it E}nKCF comes with two KCF for translation {\it
-  Burak: Answer this.}
-
-In our framework, $R_{t}^{S}$ addresses the absence of scale
-adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
-focuses on addressing the absence of translation estimation module in
-$R_{S}$.
-
-$R_{t}^{S}$, on the other hand, focuses on the shape features
-of the target that is not fully exploited in $R_{t}^{L}$ and
-$R_{t}^{S}$. For this reason, we employ \textit{HoG} features in
-$R_{t}^{S}$ and \textit{HoG} and \textit{Color} features in
-$R_{t}^{L}$. Fig.~\ref{Workflow_figure} displays the proposed tracking
-framework called Ensemble of KCFs {\it E}nKC. Also, the pseudo-code of
+The order of deploying these three KCFs is critical as they need to run with full coherency to perfom robust tracking.
+The \textit{target+large background} translation filter, $R_{t}^{L}$, is designed to run in right next frame after the scale filter, $R_s$, which is applied at every $n=5$ frames.
+We deploy these two filters in this way because we want to minimize any drifts, which are likely to happen running only $R_{s}$.
+Finally, $R_{t}^{S}$ is applied in two consecutive frames before $R_{S}$ and right after two consecutive frames implementation of $R_{t}^{L}$.
+This way, we can integrate more discriminative shape features that can not be fully learned by $R_{t}^{L}$ as it contains contribution of large background in the learned model.
+On the other hand, $R_{t}^{L}$ uses shape and color information together to do a better job in recovering from any drifts due to application of $R_{s}$ in previous frame.
+In this framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it can not learn very useful shape features alone.
+Fig.~\ref{Workflow_figure_EnKCF} displays the proposed high-speed tracking framework called Ensemble of KCFs {\it E}nKC.
+Also, the pseudo-code of
 the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.
@@
 \begin{algorithm}
-	\caption{The EnKCF Tracking Algorithm.}\label{alg:MKCF}
+	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
 	\begin{algorithmic}[1]
@@
 \subsection{Particle Filter} \label{sc:PF}
-The proposed MKCF algorithm can cause undesired drift and noise in
-tracking due to independent application of the correlation filters. To
-mitigate the drift effect and reduce the noise, a Bayes Filter
-representing the evolution of target's motion can be added into the
-MKCF tracking framework. In this study, we consider a variant of a
+The proposed {\it E}nKCF algorithm can cause undesired drift and noise in
+tracking due to independent and less frequent application of the correlation filters. To
+mitigate the drift effect further and reduce the noise, a Bayes Filter
+representing the evolution of target's motion can be added into our
+{\it E}nKCF tracking framework. To achieve this, we consider a variant of a
 Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
-Sequential Monte Carlo method that can approximate posterior
-probability density functions (pdf) of a target motion. The
-approximation becomes optimal with the infinite number of particles,
+Sequential Monte Carlo method that uses a number of sample points to represent
+the posterior probability density functions (pdf) of the target motion. 
+The approximation becomes optimal with the infinite number of particles,
 however, its run-time complexity grows exponentially with the number
@@
 study is to design a high speed tracker, we keep the number of state
-space elements low and implement computationally cheap \textit{Weight
+space elements low and implement computationally efficient \textit{Weight
   Function} and \textit{Importance-Resampling} modules. We represent
@@
 where $x$ and $y$ are the centroid of the target and $V$ represents
-the velocity components. We transit the particles with the well-known
-first order Constant Velocity model. The centroid components are
-applied Gaussian Noise whereas the velocity components are assigned
-uniform noise representative of most of the objects. The observation
-likelihood is modeled based on the confidence map of
-$R_{t}^{L}$,$R_{t}^{S}$, and $R_{s}$. It can also be modeled based on
-the euclidean distance between particle's centroid to the peak of the
-confidence maps, however, we believe that the former approach could
-result in further drifts in the case of multi-modal distributions. The
-weights for the particles are computed with the bilinear interpolation
-method.
+the velocity components. We transit the particles with the first order Constant Velocity model. The centroid components are applied Gaussian Noise whereas the velocity components are assigned
+uniform noise representative of most of the objects in our tests. The observation
+likelihood is formulated based on the confidence map of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. 
+The weights for the particles are computed as
 \begin{equation}
-	w_{p_{t}}(x_{t},y_{t}) = \dfrac{y_{R}(x_{t}-1,y_{t}-1)+y_{R}(x_{t}+1,y_{t}+1){y_{R}(x_{t}+1,y_{t}-1)+y_{R}(x_{t}-1,y_{t}+1)}}{4}
+	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
 \end{equation}
-where $w_{p}$ denotes the weight of the particle. The importance
-re-sampling module is triggered when the number of effective particles
-is smaller than a pre-defined threshold [Cite - Effective Number
-  Samples Metric] to avoid variance getting too small. Re-sampling is
-implemented with highly efficient low-variance ratio method
-[cite]. Finally, the expected mean of the approximated posterior pdf
-is computed as
+where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the size of the window in consideration.
+We can also use the spatial distance of particles to the peak of the confidence map, however, we believe that this approach could result in further drifts in the case of multi-modal distributions.
+
+The importance re-sampling module is triggered when the number of effective particles
+is smaller than a pre-defined threshold to avoid variance getting too small \cite{thrun2005probabilistic}.
+Re-sampling is implemented with efficient low-variance ratio method \cite{thrun2005probabilistic}.
+Finally, the expected mean of the approximated posterior pdf is computed as
 \begin{equation}
-	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}
+	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.
 \end{equation}
-
-The particles are assigned equal weight ($\dfrac{1}{P}$) after the
-importance re-sampling step. It should be emphasized that we skip
-importance re-sampling step in the scale filter operation as the scale
-filter contains \textit{target-only} area. In this case, the particles
-outside of the scale filter ROI do not have weight correspondence in
-the confidence map. Also, it is more likely to get noisy translation
-estimation from the scale filter.
+The particles are assigned equal weight after the importance re-sampling step in approximating the posterior pdf. It should be emphasized that we skip importance re-sampling step in the scale filter 
+operation as the scale filter contains \textit{target-only} area. In this case, the particles
+outside of the scale filter ROI do not have correspondence in the confidence map.
+Additionally, it is more likely to get noisy confidence map from $R_{s}$.
+Finally, at every iteration we check the variance in the velocity components of the particles to re-assign velocities from uniform initial distribution to keep variance high enough.
 
@@
 reasonable variance.
-\begin{equation}
-  \hat{N}_{eff} = \dfrac{1}{\sum_{i=1}^{P}(w_{p})^{2}}, 
-\end{equation}
- where $w$ represents the particles' weights and re-sampling is performed only if $\hat{N}_{eff}$ is smaller than three.
 
@@
 \end{tabular}
-\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
+\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 dataset.
 UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
@@
 \end{tabular}
-\caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
+\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
 \label{fig:OTB100_DATASET}
 \end{figure}
+
 %\begin{figure}
@@
 
-\textbf{Overall Performance without Re-detection on UAV123 Dataset.}
+\textbf{Overall Performance on UAV123 Dataset.}
 We compare the proposed tracker to other state-of-the-art high speed
@@
 Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
-dataset. The E$n$KCF tracker outperforms the other methods in
+dataset. The {\it E}nKCF tracker outperforms the other methods in
 high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
@@
 the same dataset although it is $10$-$20$ times faster than these
-trackers. On the other hand, the E$n$KCF does a decent job on
+trackers. On the other hand, the {\it E}nKCF does a decent job on
 approximating the scale of the target in highly efficient manner. This
@@
 
-\textbf{Overall Performance without Re-detection on OTB100 Dataset.}
-In addition to UAV123 dataset, we test the E$n$KCF tracker on the
+\textbf{Overall Performance on UAV123$\_$10fps Dataset.}
+
+\textbf{Overall Performance on OTB100 Dataset.}
+In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
 OTB100 dataset to evaluate how good it generalizes to a traditional
@@
 $5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
-UAV123 dataset, the E$n$KCF performs exceptionally in handling the
+UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
 scale changes. It is ranked as the fifth best tracker while being the
@@
 $2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
-prove that E$n$KCF is not only a good candidate for tracking on a
+prove that {\it E}nKCF is not only a good candidate for tracking on a
 UAV-based mobile platform but also mobile platforms on smart phones.

### 2017-04-30 bmvc_review.tex
Some More Updates Done - Figure for UAV123_10fps Dataset Added

@@
 
-%\begin{figure}
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
-%        \end{subfigure}%
-%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the UAV123 dataset.
-UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
-Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}\label{fig:UAV123_DATASET}
-%\end{figure}
-%
-%\begin{figure}
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
-%        \end{subfigure}%
-%        \begin{subfigure}{0.5\textwidth}
-%                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
-%        \end{subfigure}%
-%        \caption{Evaluation and comparison of the proposed E$n$KCF tracker on the OTB100 dataset.
-OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.
-}\label{fig:OTB100_DATASET}
-%\end{figure}
-
 \textbf{Overall Performance on UAV123 Dataset.}
@@
 
-\textbf{Overall Performance on UAV123$\_$10fps Dataset.}
+\textbf{Overall Performance on UAV123$\_$10fps Dataset.} We test our slightly modified version of the 
+{\it E}nKCF, {\it E}nKCF2, on the UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps version 
+of the UAV123 dataset. The original dataset is already dominated by fast object motion and large ego-motion. With downsampling, 
+it becomes very challenging with object and ego-motion getting drastically larger. The performance of the proposed {\it E}nKCF2 tracker
+and other already mentioned trackers can be seen in fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other high-speed correlation filter based 
+trackers including KCF, DSST by about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On the other hand, it does decent job in scale estimation. It ranks as $4$th
+in AUC. However, it is $20$-$30$ faster than the ones with higher AUC.
+
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123_10fps.pdf}}
+\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
+\end{tabular}
+\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates.
+This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
+\label{fig:UAV123_10fpsDATASET}
+\end{figure}
 

### 2017-04-30 bmvc_review.tex
Revised the section 2 a bit.

@@
 
-The order of deploying these three KCFs is critical as they need to run with full coherency to perfom robust tracking.
-The \textit{target+large background} translation filter, $R_{t}^{L}$, is designed to run in right next frame after the scale filter, $R_s$, which is applied at every $n=5$ frames.
-We deploy these two filters in this way because we want to minimize any drifts, which are likely to happen running only $R_{s}$.
-Finally, $R_{t}^{S}$ is applied in two consecutive frames before $R_{S}$ and right after two consecutive frames implementation of $R_{t}^{L}$.
-This way, we can integrate more discriminative shape features that can not be fully learned by $R_{t}^{L}$ as it contains contribution of large background in the learned model.
-On the other hand, $R_{t}^{L}$ uses shape and color information together to do a better job in recovering from any drifts due to application of $R_{s}$ in previous frame.
-In this framework, $R_{t}^{S}$ addresses the absence of scale adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$ focuses on addressing the absence of translation estimation module in $R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it can not learn very useful shape features alone.
-Fig.~\ref{Workflow_figure_EnKCF} displays the proposed high-speed tracking framework called Ensemble of KCFs {\it E}nKC.
-Also, the pseudo-code of
-the proposed {\it E}nKC is shown in alg.~\ref{alg:MKCF}.
+The order of running these three KCFs is important as each of these
+filters aims at addressing different chanllenges while perserving
+run-time performance as fast as possible. The \textit{target+large
+  background} translation filter, $R_{t}^{L}$, is intended to run
+right after the scale filter, $R_s$, runs which is applied at every
+$k=5$ frames. We run these two filters this way because we want to
+minimize any drifts that are likely to happen running only $R_{s}$. In
+addition, the filter, $R_{t}^{S}$, is applied to every other frames
+before $R_{S}$ and right after two consecutive frames running
+$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
+features that can not be fully learned by $R_{t}^{L}$ as it contains
+contribution of large background in the learned model. The filter,
+$R_{t}^{L}$ uses shape and color information together to recover from
+any potential drifts -- drifts could happen only looking the target's
+scale by the filter, $R_{s}$.
+
+{\it Burak: Rewrite the following paragraph.}
+
+In summary, the filter, $R_{t}^{S}$, will handle the absence of scale
+adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
+focuses on addressing the absence of translation estimation module in
+$R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it
+can not learn very useful shape features
+alone.
+
+Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
+proposed algorithm and Figure \ref{alg:MKCF} shows the pseudo-code of
+{\it E}nKCF.
 
@@
 \end{algorithm}
+
+{\it Burak: The KCF section doesn't fit the section before and
+  after. In addition, it's still too long.}
 
@@
 \subsection{Particle Filter} \label{sc:PF}
-The proposed {\it E}nKCF algorithm can cause undesired drift and noise in
-tracking due to independent and less frequent application of the correlation filters. To
-mitigate the drift effect further and reduce the noise, a Bayes Filter
-representing the evolution of target's motion can be added into our
-{\it E}nKCF tracking framework. To achieve this, we consider a variant of a
-Bayes Filter, \textit{Particle Filter}. The Particle Filter is a
-Sequential Monte Carlo method that uses a number of sample points to represent
-the posterior probability density functions (pdf) of the target motion. 
-The approximation becomes optimal with the infinite number of particles,
-however, its run-time complexity grows exponentially with the number
-of elements in the state space matrix, $X_{t}$. As the focus of this
-study is to design a high speed tracker, we keep the number of state
-space elements low and implement computationally efficient \textit{Weight
-  Function} and \textit{Importance-Resampling} modules. We represent
-the state space matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$
-where $x$ and $y$ are the centroid of the target and $V$ represents
-the velocity components. We transit the particles with the first order Constant Velocity model. The centroid components are applied Gaussian Noise whereas the velocity components are assigned
-uniform noise representative of most of the objects in our tests. The observation
-likelihood is formulated based on the confidence map of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. 
-The weights for the particles are computed as
+The proposed {\it E}nKCF algorithm can cause undesired drift and noise
+in tracking due to independent and less frequent application of the
+correlation filters.
+
+{\it Burak: When we explain EnKCF, we've already used potential drifts
+  are the reason why we want to have three KCFs. If we're talking
+  about the same, kind of drifts, you have to be more careful. Having
+  this section about particle filter will make it impractical or
+  usefulness to have three KCFs.}
+
+To mitigate the drift effect further and reduce the noise, a Bayes
+Filter representing the evolution of target's motion can be added into
+our {\it E}nKCF tracking framework. To achieve this, we consider a
+variant of a Bayes Filter, \textit{Particle Filter}. The Particle
+Filter is a Sequential Monte Carlo method that uses a number of sample
+points to represent the posterior probability density functions (pdf)
+of the target motion.  The approximation becomes optimal with the
+infinite number of particles, however, its run-time complexity grows
+exponentially with the number of elements in the state space matrix,
+$X_{t}$. As the focus of this study is to design a high speed tracker,
+we keep the number of state space elements low and implement
+computationally efficient \textit{Weight Function} and
+\textit{Importance-Resampling} modules. We represent the state space
+matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$
+are the centroid of the target and $V$ represents the velocity
+components. We transit the particles with the first order Constant
+Velocity model. The centroid components are applied Gaussian Noise
+whereas the velocity components are assigned uniform noise
+representative of most of the objects in our tests. The observation
+likelihood is formulated based on the confidence map of $R_{t}^{L}$,
+$R_{t}^{S}$, and $R_{s}$.  The weights for the particles are computed
+as
 \begin{equation}
@@
 \end{equation}
-where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the size of the window in consideration.
-We can also use the spatial distance of particles to the peak of the confidence map, however, we believe that this approach could result in further drifts in the case of multi-modal distributions.
+where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
+$N$ denotes the size of the window in consideration. We can also use
+the spatial distance of particles to the peak of the confidence map,
+however, we believe that this approach could result in further drifts
+in the case of multi-modal distributions.
 
-The importance re-sampling module is triggered when the number of effective particles
-is smaller than a pre-defined threshold to avoid variance getting too small \cite{thrun2005probabilistic}.
-Re-sampling is implemented with efficient low-variance ratio method \cite{thrun2005probabilistic}.
-Finally, the expected mean of the approximated posterior pdf is computed as
+The importance re-sampling module is triggered when the number of
+effective particles is smaller than a pre-defined threshold to avoid
+variance getting too small \cite{thrun2005probabilistic}. Re-sampling
+is implemented with efficient low-variance ratio method
+\cite{thrun2005probabilistic}. Finally, the expected mean of the
+approximated posterior pdf is computed as
 \begin{equation}
@@
 \end{equation}
-The particles are assigned equal weight after the importance re-sampling step in approximating the posterior pdf. It should be emphasized that we skip importance re-sampling step in the scale filter 
-operation as the scale filter contains \textit{target-only} area. In this case, the particles
-outside of the scale filter ROI do not have correspondence in the confidence map.
-Additionally, it is more likely to get noisy confidence map from $R_{s}$.
-Finally, at every iteration we check the variance in the velocity components of the particles to re-assign velocities from uniform initial distribution to keep variance high enough.
+The particles are assigned equal weight after the importance
+re-sampling step in approximating the posterior pdf. It should be
+emphasized that we skip importance re-sampling step in the scale
+filter operation as the scale filter contains \textit{target-only}
+area. In this case, the particles outside of the scale filter ROI do
+not have correspondence in the confidence map. Additionally, it is
+more likely to get noisy confidence map from $R_{s}$. Finally, at
+every iteration we check the variance in the velocity components of
+the particles to re-assign velocities from uniform initial
+distribution to keep variance high enough.
 
@@
 
-\textbf{Overall Performance on UAV123$\_$10fps Dataset.} We test our slightly modified version of the 
-{\it E}nKCF, {\it E}nKCF2, on the UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps version 
-of the UAV123 dataset. The original dataset is already dominated by fast object motion and large ego-motion. With downsampling, 
-it becomes very challenging with object and ego-motion getting drastically larger. The performance of the proposed {\it E}nKCF2 tracker
-and other already mentioned trackers can be seen in fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other high-speed correlation filter based 
-trackers including KCF, DSST by about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On the other hand, it does decent job in scale estimation. It ranks as $4$th
-in AUC. However, it is $20$-$30$ faster than the ones with higher AUC.
+\textbf{Overall Performance on UAV123$\_$10fps Dataset.} We test our
+slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
+UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps
+version of the UAV123 dataset. The original dataset is already
+dominated by fast object motion and large ego-motion. With
+downsampling, it becomes very challenging with object and ego-motion
+getting drastically larger. The performance of the proposed {\it
+  E}nKCF2 tracker and other already mentioned trackers can be seen in
+fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other
+high-speed correlation filter based trackers including KCF, DSST by
+about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On
+the other hand, it does decent job in scale estimation. It ranks as
+$4$th in AUC. However, it is $20$-$30$ faster than the ones with
+higher AUC.
 

### 2017-05-01 bmvc_review.tex
Comments Answered - Figures Updated - Conclusion Checked

@@
 of the target over frames. In addition, we devised a Bayes filter for
-a smooth transition between individual KCFs' executions. To minimize
-the effect of drifting, we also developed another algorithm that
-detects target-lost, uses an existing object proposal method (e.g.,
-``Edge Box'') to re-detect the lost target, and re-initializes the
-previous tracking for a long-term tracking. To verify the usefulness
-of the proposed method, we compared the performance of ours to those
+a smooth transition between individual KCFs' executions. Also, we slightly
+modify the {\it E}nKCF to perform tracking in low frame rate videos dominated by large ego-motion.
+large ego-motion.To verify the usefulness of the proposed method, we compared the performance of ours to those
 of the existing online tracking methods. Experimental results showed
@@
 like to make our algorithm 1) learn the appearance model of a target
-on the fly and 2) run as fast on a typical desktop as up to 300Hz so
+on the fly and 2) run as fast on a typical desktop as up to $300$-$400$Hz so
 that it could run, at least, faster than 30Hz when it is deployed on a
@@
 is ready to track an object of interest when it is deployed on an
-embedded system. To this end, an online object tracking is more
+embedded system. To this end, an online learning highly efficient object tracking is more
 appropriate.
@@
 solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
-frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
+frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
 this reformulation, an object tracking pipeline based on the
@@
 the kernelized correlation filter with multi-channel features
-\cite{henriques2015high} showed impressive object trackin results and
+\cite{henriques2015high} showed impressive object tracking results and
 outperformed other state-of-the-art tracking algorithms, for example,
@@
 based approach is to find a correct scale at a location where a target
-highly likely appears \cite{zhang2014fast}. In particular, they uses
+highly likely appears \cite{zhang2014fast}. In particular, they use
 the MOSSE tracker to estimate a target's translation. The scale is
 updated in a way where the confidence map is used to determine the
-scale change between successive frames. This is because they assumes
+scale change between successive frames. This is because they assume
 the scale of a target wouldn't change much over two consecutive
 frames. Similarly \cite{ma2015long} used two KCFs to learn the
-translation and scale of a target separately. To more specific, a KCF
+translation and scale of a target separately. To be more specific, a KCF
 is used to learn the translation of the target and its
@@
 idea -- the idea of deploying multiple KCFs to address the issues of
-single target tracking: scale and translation. In this paper, we use
-an ensemble of KCFs in turn, instead of running them all together on
+single target tracking: scale and translation in a highly efficient manner. 
+In this paper, we use an ensemble of KCFs in turn, instead of running them all together on
 every frame. By doing so, we could still address the scale change and
@@
   efficiently address the scale variance and the dynamic maneuver of a
-  target while perserving run-time performance as high as possible. To
+  target while preserving run-time performance as high as possible. To
   minimize any potential performance gap from transiting one KCF to
@@
 
-\item \textbf{Slight Modification of the proposed EnKCF for Handling Large Motion} Our second algorithm, 
+\item \textbf{Slight Modification of the proposed {\it E}nKCF for Handling Large Motion} Our second algorithm, 
 {\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose.
-The original {\it E}nKCF is slighlty modified to track fast motions and handle large ego-motion.
-We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on the low frame rate UAV platform.
+The original {\it E}nKCF is slighlty modified to track in low frame rate videos ($10$fps) dominated by large ego-motion.
+We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on a UAV platform.
 Particle Filter can be deployed in case the camera motion is known.
+The run-time performance decreases to $150$ fps, however, ratio of the video frame rate and run-time performance is similar to {\it E}nKCF.
 The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
@@
 
-In this paper, we extends the KCF in that multiple KCFs are deployed,
+In this paper, we extend the KCF in that multiple KCFs are deployed,
 in turn, to address a target's scale change and dynamic maneuvers
@@
 After Henriques and his colleagues' presented impressive tracking
-results of KCF \cite{henriques2015high}, many variation of KCF were
+results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge, many variation of KCF were
 investigated. In particular, \cite{ma2015long} and
@@
 challenges of single target tracking. But ours is different from that
-of \cite{ma2015long} in that we do not use those three KCFs together
+of \cite{ma2015long} in that we do not use those multiple KCFs together
 at every frame, but alternatively at every three frame. The way our
@@
 makes sense in that the appearance of consecutive images does not
-change much. Although it varies based on the scene, learning a
+change drastically. Although it varies based on the scene, learning a
 correlation filter a frame would not be much different from the one
@@
 contribution of large background in the learned model. The filter,
-$R_{t}^{L}$ uses shape and color information together to recover from
+$R_{t}^{L}$, uses shape and color information together to recover from
 any potential drifts -- drifts could happen only looking the target's
@@
 
-{\it Burak: Rewrite the following paragraph.}
-
-In summary, the filter, $R_{t}^{S}$, will handle the absence of scale
-adaptation module in $R_{t}^{L}$ and $R_{t}^{S}$ whereas $R_{t}^{L}$
-focuses on addressing the absence of translation estimation module in
-$R_{S}$ and $R_{t}^{S}$ addresses the weakness of $R_{t}^{L}$ that it
-can not learn very useful shape features
-alone.
-
+In summary, the scale filter, $R_{s}$, handles the scale change providing more accurate
+ROIs to $R_{t}^{L}$ and $R_{t}^{S}$.
+The translation filter, $R_{t}^{L}$, concentrates on a large search area to better recover from any potential drifts due to application of $R_{S}$ in previous frame.
+$R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area.
 Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
-proposed algorithm and Figure \ref{alg:MKCF} shows the pseudo-code of
-{\it E}nKCF.
+proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of
+{\it E}nKCF. In the following section, we will briefly mention the theory behind the KCF.
 
@@
 				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
-						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
+						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
 						Scale filter (\textit{target-only}) model $R_{s}$.
@@
 				\EndIf
-				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
+				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
 						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
@@
 			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
-		         \State Skip it for $R_{t}^{L}$ (Condition 1),
 				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
+		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
 				\State // Update Translation
-				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
+				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
 			    \State // Model Update
@@
 
+{\it YoungWoo : What do you mean by this?
+Should we move it up before the EnKCF introduction?
+or Should we include more EnKCF-related text in it?
+I trimmed it further.
+I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}
+
 \subsection{Kernelized Correlation Filter} \label{sec:kcf}
@@
 second with state-of-the-art tracking capabilities even in challenging
-cases such as VOT15 dataset. Its computational efficiency arises from
-its use of the discrete fourier transform of the circulant matrix and
-frequency domain element-wise operations known as hadamard product and
-division. The first example of frequency domain trackers is the Linear
-Correlation Filter tracker known as MOSSE tracker. It minimizes the
-ridge regression function in the frequency domain using a single
-template with continous desired gaussian response. The KCF tracker, on
-the other hand, minimizes the regularized ridge regression function
-shown below.
+cases. Its computational efficiency arises from its use of the discrete fourier transform of the circulant matrix and frequency domain element-wise operations known as hadamard product and
+division.
+The first example of frequency domain trackers is the MOSSE tracker running at $700$fps \cite{bolme2010visual}.
+It minimizes the ridge regression function in the frequency domain using a single
+template and intensity features. The KCF tracker, on the other hand, minimizes the regularized ridge regression function shown below.
 \begin{equation}
@@
 eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
-derivative of $E$ w.r.t $w$ to $0$. The solution in the primal domain
-can be formulated as
-\begin{equation}
-w = (X^{T}X+\lambda)^{-1}y
-\label{eq:SpatialSolution}
-\end{equation}
-where $X$ and $\lambda$ represent the training samples and
-regularization term. The same cost function in the Fourier domain can
-be represented as
+derivative of $E$ w.r.t $w$ to $0$. The primal solution in the frequency domain is formulated
+as
+%\begin{equation}
+%w = (X^{T}X+\lambda)^{-1}y
+%\label{eq:SpatialSolution}
+%\end{equation}
 \begin{equation}
@@
 \end{equation}
-More information on the spatial and fourier domain solutions can be
-found in \cite{henriques2015high}. The MOSSE tracker does not make use
-of $\lambda$ and only one training sample with desired response is
-used to update $w$. This framework does not include enough background
-information into the training framework with a single template. The
+where $X^{H}$ and $\lambda$represent the complex-conjugate of training samples and
+regularization term. More documentation on the spatial and fourier domain solutions can be
+found in \cite{henriques2015high}. The MOSSE tracker uses one training sample centred at estimated position of the target. This framework does not include enough background
+information into the learned model,$w$. The
 application of the circulant matrix theorem into the
@@
 
-In this form, eq.~\ref{eq:SpatialSolution}
-and~\ref{eq:FourierSolution} could prohibit us from implementing a
+In this form, eq.~\ref{eq:FourierSolution} could prohibit us from implementing a
 high speed object tracking as we need to perform large number of
@@
 represented diagonally by the Fourier Transform regardless of the base
-sample $x$ as shown below.
-\begin{equation}
-X = Fdiag(\hat{x})F^{H},
-\label{eq:CirculantMatrixDFT}
-\end{equation}
-where $F$ denotes a constant Fourier Transform matrix and $x$ is the
-Discrete Fourier Transform of the base sample $x$. 
+sample $x$.
+%\begin{equation}
+%X = Fdiag(\hat{x})F^{H},
+%\label{eq:CirculantMatrixDFT}
+%\end{equation}
+%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
+%Discrete Fourier Transform of the base sample $x$. 
 %To simplify the
@@
 %\end{equation}
-The solution vector in the Fourier domain $\hat{w}$ is formulated as
+Then, the optimized solution vector in the Fourier domain $\hat{w}$ is formulated as
 \begin{equation}
-\hat{w} = \dfrac{\hat{x}^{*}*\hat{y}}{\hat{x}^{*}*\hat{x}+\lambda}.
+\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
 \label{eq:DiagonalizedPrimalSolution}
 \end{equation}
-For detailed documentation of the circulant matrix theorem based
-frequency domain solution can be found in
-\cite{henriques2012exploiting,henriques2015high}.
-
-The above primal frequency domain solution can be called as Linear
-Correlation Filter which improves the MOSSE tracker by incorporating
-cyclic shifts and regularizer. To further improve the robustness to
-geometric and photographic variations, one can exploit non-linear
-regression function in the Correlation Filter framework
-\cite{henriques2015high}. The solution to the kernelized ridge
-regression function is shown below.
-\begin{equation}
-\alpha = y(K+\lambda I)^{-1},
-\end{equation}
-where $K$ and $\alpha$ represent the kernel matrix and corresponding
-dual space solution.
-
+To further improve the robustness to geometric and photographic variations, one can exploit non-linear
+regression function in the Correlation Filter framework \cite{henriques2015high}. 
+%\begin{equation}
+%\alpha = y(K+\lambda I)^{-1}
+%\end{equation}
+%where $K$ and $\alpha$ represent the kernel matrix and corresponding
+%dual space solution. 
 %\cite{henriques2015high} states that kernel
@@
 %kernels. 
-
 Similar to the diagonalization in the linear ridge regression
@@
 \hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
-\label{eq:FourierDualDomainSolution}.
+\label{eq:FourierDualDomainSolution}
 \end{equation}
@@
 The first correlation filter based trackers used grayscale feature ($C=1$) to
-learn the solution vector $w$, however, the multi-channel features
+learn the solution vector $w$, however, multi-channel features
 such as HoG and Color were later exploited to improve tracking
@@
 
-Such non-linearization process does not increase the computational
-complexity of the linear multi-channel correlation filter dramatically
-as we only need to sum over the $n$ dimensional feature
-channels. Training shown in eq.~\ref{eq:FourierDualDomainSolution}
+Training shown in eq.~\ref{eq:FourierDualDomainSolution}
 gives us $\hat{a}$ learned in time step $t$. We can accumulate
@@
 \subsection{Particle Filter} \label{sc:PF}
-The proposed {\it E}nKCF algorithm can cause undesired drift and noise
-in tracking due to independent and less frequent application of the
-correlation filters.
-
-{\it Burak: When we explain EnKCF, we've already used potential drifts
-  are the reason why we want to have three KCFs. If we're talking
-  about the same, kind of drifts, you have to be more careful. Having
-  this section about particle filter will make it impractical or
-  usefulness to have three KCFs.}
-
-To mitigate the drift effect further and reduce the noise, a Bayes
-Filter representing the evolution of target's motion can be added into
-our {\it E}nKCF tracking framework. To achieve this, we consider a
-variant of a Bayes Filter, \textit{Particle Filter}. The Particle
+The proposed {\it E}nKCF tracker does not update target's translation at every
+$n=5$ frames due to application of a scale filter, $R_{s}$. To avoid this to perform 
+smoother tracking, a Bayes Filter representing the evolution of target's motion can be added into our {\it E}nKCF tracking framework. To achieve this,
+we consider a variant of a Bayes Filter, \textit{Particle Filter}. The Particle
 Filter is a Sequential Monte Carlo method that uses a number of sample
@@
 where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
-$N$ denotes the size of the window in consideration. We can also use
-the spatial distance of particles to the peak of the confidence map,
-however, we believe that this approach could result in further drifts
+$N$ denotes the size of the window in consideration in confidence map. We can also use
+the euclidean distance of particles to the location of maximum response of 
+the confidence map, however, we believe that this approach could result in drifts
 in the case of multi-modal distributions.
@@
 \cite{thrun2005probabilistic}. Finally, the expected mean of the
-approximated posterior pdf is computed as
-\begin{equation}
-	\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.
-\end{equation}
-The particles are assigned equal weight after the importance
+approximated posterior pdf is computed as $\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.$
+The particles are assigned equal weight ($w_{p_{t}}=1/P$) after the importance
 re-sampling step in approximating the posterior pdf. It should be
@@
 filter operation as the scale filter contains \textit{target-only}
-area. In this case, the particles outside of the scale filter ROI do
-not have correspondence in the confidence map. Additionally, it is
+area and focuses on scale estimation. Additionally, it is
 more likely to get noisy confidence map from $R_{s}$. Finally, at
@@
 To verify the usefulness of our algorithm, we ran the proposed
-algorithm against two publicly, available datasets:
+{\it E}nKCF against two publicly, available datasets:
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
-UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. OTB100
-dataset contains video sequences for 100 objects whereas UAV123
-dataset contains aerial footage of 123 objects.
+UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. 
+OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects.
 
-The proposed $E$nKCF method can better handle slow motions. Also, the
-UAVs use mobiles platforms with limited computational power. We
-believe that the proposed tracker can better fit to tracking from
-these platforms as it is highly efficient and scale adaptive. Taking
-into account these reasons, it is more appropriate to test it on
-aerial videos captured by UAVs.
+The UAVs employ mobiles platforms with limited computational resources. We
+believe that the proposed high-speed tracker can better fit to tracking from
+these platforms as it is highly efficient and scale adaptive.
+Taking into account these reasons, we first test it on UAV captured videos (UAV123).
+Later, we test in on OTB100 dataset which mostly contains videos captured from smart phones and cameras controlled by a human.
+Finally, the {\it E}nKCF2 is tested on temporally downsampled version of UAV123 dataset.
 
@@
 parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for
-$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. In our particle filter
-implementation, we employ $1000$ particles and use the
+$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. The learning rate is set to $0.12$
+for $R_{t}^{L}$ as it is run in every frame for $E_{n}KCF2$.
+In our particle filter implementation, we employ $1000$ particles and use the
 \textit{efficient number of samples} metric shown below to determine
@@
 as it is assigned lower template size, yielding space to exploit two
-feature modalities.
+feature modalities. We note that we use the same features for the {\it E}nKCF2 tracker.
 
@@
 the other hand, it does decent job in scale estimation. It ranks as
-$4$th in AUC. However, it is $20$-$30$ faster than the ones with
+$4$th in AUC and it is $20$-$30$ faster than the ones with
 higher AUC.

### 2017-05-01 bmvc_review.tex
Introduction Results Figure Added
Some More Edits in Introduction
All Sundays Work Included - Waiting for More Comments

@@
 
+\begin{figure*}[!t]
+\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
+\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large ($\leq0.5$, or $\geq2$).}
+\label{ResultsIntroduction}
+\end{figure*}
+
 Another way of handling the scale change for the correlation filter
@@
 \textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
+($R_{t}^{L}$). Fig.~\ref{fig:Filters} shows examples of the ROIs
 associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
@@
 
+\begin{figure}[!t]
+\centering
+\begin{tabular}{cc}
+\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
+(a) \\
+\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
+(b)
+\end{tabular}
+\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker (a). It is slightly modified to handle extreme ego-motion
+and we call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
+\label{Workflows}
+\end{figure}
 The contributions of this study are as follows.
@@
   another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
-  be visualized in fig.~\ref{Workflow_figure_EnKCF}.
+  be visualized in fig.~\ref{Workflows}.
 The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
@@
 The run-time performance decreases to $150$ fps, however, ratio of the video frame rate and run-time performance is similar to {\it E}nKCF.
-The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
+The proposed framework can be seen in fig.~\ref{Workflows}.
+%\begin{figure*}[!t]
+%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
+%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
+%\label{Workflow_figure_EnKCF}
+%\end{figure*}
+%\begin{figure*}[!h]
+%\centering
+%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
+%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
+%\label{Workflow_figure_EnKCF2}
+%\end{figure*}
 
@@
 %---------------------------------------------------------------------- 
-\begin{figure*}[!t]
-\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
-\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
-\label{Workflow_figure_EnKCF}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
-\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
-\label{Workflow_figure_EnKCF2}
-\end{figure*}
-
 In this paper, we extend the KCF in that multiple KCFs are deployed,
@@
 filter is prepared to focus on the target itself to estimate the right
-size or scale of the target. Figure \ref{fig:Filters} shows examples
+size or scale of the target. Fig.~\ref{fig:Filters} shows examples
 of the region of interest (ROI) covered by each of three filters. We
@@
 higher speed.
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
+\caption{The three filters denoted as \textit{target+small background} translation filter,
+  \textit{target-only} scale filter and \textit{target+large background} translation filters are
+  shown. Also, the hanning window and desired Gaussian response for
+  each filter is displayed.}
+\label{fig:Filters}
+\end{figure}
 
 After Henriques and his colleagues' presented impressive tracking
-results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge, many variation of KCF were
-investigated. In particular, \cite{ma2015long} and
+results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
+ many variation of KCF were investigated. In particular, \cite{ma2015long} and
 \cite{danelljan2014accurate} used a scale filter to learn the target
@@
 correlation filter a frame would not be much different from the one
-learned using the image few or $k$ frames later. By alternating three
-KCFs in turn, our algorithm runs as fast as or faster than the
+learned using the image few or $k$ frames later. This fact can be visualized in fig.~\ref{fig:Filters_Comparison}.
+By alternating three KCFs in turn, our algorithm runs as fast as or faster than the
 original KCF. From our experiments, we empirically found that five is
@@
 
-\begin{figure}[!t]
+\begin{figure}[!h]
 \centering
-\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
-\caption{The three filters denoted as \textit{target+small background} translation filter,
-  \textit{target-only} scale filter and \textit{target+large background} translation filters are
-  shown. Also, the hanning window and desired Gaussian response for
-  each filter is displayed.}
-\label{fig:Filters}
+\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
+\caption{The video frame and the learned scale correlation filters are shown next to it. 
+The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
+Filters updated every five frame and every frame display very large correlation.}
+\label{fig:Filters_Comparison}
 \end{figure}
@@
 $R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area.
-Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
+Fig.~\ref{Workflows} illustrates the workflow of the
 proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of

### 2017-05-01 bmvc_review.tex
Revised all most, all-the-way.

--- 2017-05-01 bmvc_review.tex
@@
 applications for embedded systems. This is primarily because most of
-the embedded systems already includes image acquisition pipeline and a
+embedded systems already includes image acquisition pipeline and a
 tremendous amount of progresses on research has been made for many
@@
 vision algorithm on any existing embedded systems, a vision algorithm
-needs to satisfy some criteria: minimal, manual intervention after
-deployment and small footprint of computing resource consumption and
-on executable code, with the assumption of reasonably good
+needs to satisfy, at least, two criteria: minimal, manual intervention
+after deployment and small footprint of computing resource consumption
+and on executable code, with the assumption of reasonably good
 performance. To this end, in this paper, we propose an ensemble of the
@@
 of the target over frames. In addition, we devised a Bayes filter for
-a smooth transition between individual KCFs' executions. Also, we slightly
-modify the {\it E}nKCF to perform tracking in low frame rate videos dominated by large ego-motion.
-large ego-motion.To verify the usefulness of the proposed method, we compared the performance of ours to those
-of the existing online tracking methods. Experimental results showed
-that the performance of ours are 72.53\% for precision on 20 pixels
-and 52.90\% for success rate for OTB100 data, and 55.71\% and 41.71\%
-for UAV123 data. These results confirmed that our method outperformed
-the existing ones over 5\% on precision on 20 pixels and 10-20\% on
-AUC on average. Our implementation ran at 340 fps for OTB100 and at
-416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
-and KCF (292 fps), DCF (457 fps), and STC (350 fps) for UAV123.
+a smooth transition between individual KCFs' executions. Also, we
+slightly modify the {\it E}nKCF to perform tracking in low frame rate
+videos dominated by large ego-motion.  large ego-motion.  To verify
+the usefulness of the proposed method, we compared the performance of
+ours to those of the existing online tracking methods. Experimental
+results showed that the performance of ours are 72.53\% for precision
+on 20 pixels and 52.90\% for success rate for OTB100 data, and 55.71\%
+and 41.71\% for UAV123 data. These results confirmed that our method
+outperformed the existing ones over 5\% on precision on 20 pixels and
+10-20\% on AUC on average. Our implementation ran at 340 fps for
+OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
+fps) for OTB100 and KCF (292 fps), DCF (457 fps), and STC (350 fps)
+for UAV123.
 \end{abstract}
@@
 like to make our algorithm 1) learn the appearance model of a target
-on the fly and 2) run as fast on a typical desktop as up to $300$-$400$Hz so
-that it could run, at least, faster than 30Hz when it is deployed on a
-low-end, embedded system. With these features, our tracking algorithm
-is ready to track an object of interest when it is deployed on an
-embedded system. To this end, an online learning highly efficient object tracking is more
-appropriate.
+on the fly and 2) run as fast on a typical desktop as up to
+$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
+is deployed on a low-end, embedded system. With these features, our
+tracking algorithm is ready to track an object of interest when it is
+deployed on an embedded system. To this end, an online learning highly
+efficient object tracking is more appropriate.
 
@@
 
+\begin{figure*}[!t]
+\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
+\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large or small($\leq0.5$, or $\geq2$).}
+\label{Workflow_figure_EnKCF}
+\end{figure*}
+
 Another way of handling the scale change for the correlation filter
@@
 frames. Similarly \cite{ma2015long} used two KCFs to learn the
-translation and scale of a target separately. To be more specific, a KCF
-is used to learn the translation of the target and its
+translation and scale of a target separately. To be more specific, a
+KCF is used to learn the translation of the target and its
 background. Given this, another KCF is used to learn the target area
@@
 idea -- the idea of deploying multiple KCFs to address the issues of
-single target tracking: scale and translation in a highly efficient manner. 
-In this paper, we use an ensemble of KCFs in turn, instead of running them all together on
-every frame. By doing so, we could still address the scale change and
-estimate target's motion efficiently while increasing run-time
-performance. In particular, we deploy three KCF in turn:
-\textit{target}+\textit{small background} translation filter
-($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+single target tracking: scale and translation in a highly efficient
+manner.  In this paper, we use an ensemble of KCFs in turn, instead of
+running them all together on every frame. By doing so, we could still
+address the scale change and estimate target's motion efficiently
+while increasing run-time performance. In particular, we deploy three
+KCF in turn: \textit{target}+\textit{small background} translation
+filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
 \textit{target}+\textit{large background} translation filter
@@
 
-\item \textbf{Slight Modification of the proposed {\it E}nKCF for Handling Large Motion} Our second algorithm, 
-{\it E}nKCF2 leverages the flexibility of the ensemble of KCFs approach we propose.
-The original {\it E}nKCF is slighlty modified to track in low frame rate videos ($10$fps) dominated by large ego-motion.
-We do not integrate the particle filter in {\it E}nKCF2 as we test it on a temporally downsampled UAV123 dataset (UAV123$\_$10fps) including sequences with large ego-motion on a UAV platform.
-Particle Filter can be deployed in case the camera motion is known.
-The run-time performance decreases to $150$ fps, however, ratio of the video frame rate and run-time performance is similar to {\it E}nKCF.
-The proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
+\item \textbf{Slight Modification of the proposed {\it E}nKCF for
+  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
+  the flexibility of the ensemble of KCFs approach we propose. The
+  original {\it E}nKCF is slighlty modified to track in low frame rate
+  videos ($10$fps) dominated by large ego-motion. We do not integrate
+  the particle filter in {\it E}nKCF2 as we test it on a temporally
+  downsampled UAV123 dataset (UAV123$\_$10fps) including sequences
+  with large ego-motion on a UAV platform. Particle Filter can be
+  deployed in case the camera motion is known. The run-time
+  performance decreases to $150$ fps, however, ratio of the video
+  frame rate and run-time performance is similar to {\it E}nKCF. The
+  proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
 
-\begin{comment}\item \textbf{Re-Detection} A target loss is inevitable in object
+\begin{comment}
+
+\item \textbf{Re-Detection} A target loss is inevitable in object
   tracking. To cope with this, we developed a new target, re-detection
@@
   fps to less than $100$ fps.
-
-\item We integrate the Particle Filter into the Multiple KCFs tracking
-  as an additional filter that can avoid the drift due to one of the
-  correlation filters we employ in our framework.
 
@@
 After Henriques and his colleagues' presented impressive tracking
-results of KCF \cite{henriques2015high} on VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge, many variation of KCF were
-investigated. In particular, \cite{ma2015long} and
-\cite{danelljan2014accurate} used a scale filter to learn the target
-area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
-used a correlation filter learned on the target area and its
-surrounding background in different size to learn the optimal scale of
-the target. Our approach is particularly similar to that of
-\cite{ma2015long} in that more than one KCF is used to address the
-challenges of single target tracking. But ours is different from that
-of \cite{ma2015long} in that we do not use those multiple KCFs together
-at every frame, but alternatively at every three frame. The way our
-algorithm is alternating multiple KCFs in different goals intuitively
-makes sense in that the appearance of consecutive images does not
-change drastically. Although it varies based on the scene, learning a
-correlation filter a frame would not be much different from the one
-learned using the image few or $k$ frames later. By alternating three
-KCFs in turn, our algorithm runs as fast as or faster than the
-original KCF. From our experiments, we empirically found that five is
-the optimal for $k$ in terms of precision and success rates. We'll
-detail this at the experimental section later.
+results of KCF \cite{henriques2015high} on
+VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
+many variation of KCF were investigated. In particular,
+\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
+to learn the target area only whereas \cite{li2014scale,
+  bibi2015multi, tang2015multi} used a correlation filter learned on
+the target area and its surrounding background in different size to
+learn the optimal scale of the target. Our approach is particularly
+similar to that of \cite{ma2015long} in that more than one KCF is used
+to address the challenges of single target tracking. But ours is
+different from that of \cite{ma2015long} in that we do not use those
+multiple KCFs together at every frame, but alternatively at every
+three frame. The way our algorithm is alternating multiple KCFs in
+different goals intuitively makes sense in that the appearance of
+consecutive images does not change drastically. Although it varies
+based on the scene, learning a correlation filter a frame would not be
+much different from the one learned using the image few or $k$ frames
+later. By alternating three KCFs in turn, our algorithm runs as fast
+as or faster than the original KCF. From our experiments, we
+empirically found that five is the optimal for $k$ in terms of
+precision and success rates. We'll detail this at the experimental
+section later.
 
@@
 
-In summary, the scale filter, $R_{s}$, handles the scale change providing more accurate
-ROIs to $R_{t}^{L}$ and $R_{t}^{S}$.
-The translation filter, $R_{t}^{L}$, concentrates on a large search area to better recover from any potential drifts due to application of $R_{S}$ in previous frame.
-$R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area.
-Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
-proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of
-{\it E}nKCF. In the following section, we will briefly mention the theory behind the KCF.
+In summary, the scale filter, $R_{s}$, is designed to directly handle
+the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
+with more focused ROIs about the target's translation. A translation
+filter, $R_{t}^{L}$, is intended to look at a larger search area to
+estimate the target's translation and recover from any potential
+drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
+designed to addresses the drawback of $R_{t}^{L}$ that it may learn
+noisy shape features due to its large search area. Figure
+\ref{Workflow_figure_EnKCF} illustrates the workflow of the proposed
+algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
+  E}nKCF. In the following section, we will briefly mention the theory
+behind the KCF.
 
@@
 
+\begin{comment}
 {\it Burak: The KCF section doesn't fit the section before and
@@
 I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}
+\end{comment}
 
@@
 second with state-of-the-art tracking capabilities even in challenging
-cases. Its computational efficiency arises from its use of the discrete fourier transform of the circulant matrix and frequency domain element-wise operations known as hadamard product and
-division.
-The first example of frequency domain trackers is the MOSSE tracker running at $700$fps \cite{bolme2010visual}.
-It minimizes the ridge regression function in the frequency domain using a single
-template and intensity features. The KCF tracker, on the other hand, minimizes the regularized ridge regression function shown below.
+cases. Its computational efficiency arises from its use of the
+discrete fourier transform of the circulant matrix and frequency
+domain element-wise operations known as hadamard product and
+division. The first example of frequency domain trackers is the MOSSE
+tracker running at $700$fps \cite{bolme2010visual}. It minimizes the
+ridge regression function in the frequency domain using a single
+template and intensity features. The KCF tracker, on the other hand,
+minimizes the regularized ridge regression function shown below.
 \begin{equation}
@@
 eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
-derivative of $E$ w.r.t $w$ to $0$. The primal solution in the frequency domain is formulated
-as
+derivative of $E$ w.r.t $w$ to $0$. The primal solution in the
+frequency domain is formulated as
 %\begin{equation}
@@
 \end{equation}
-where $X^{H}$ and $\lambda$represent the complex-conjugate of training samples and
-regularization term. More documentation on the spatial and fourier domain solutions can be
-found in \cite{henriques2015high}. The MOSSE tracker uses one training sample centred at estimated position of the target. This framework does not include enough background
-information into the learned model,$w$. The
-application of the circulant matrix theorem into the
-eq.~\ref{eq:Closedform_RidgeReg} makes it possible to include many
-background patches at a similar computational complexity. A circulant
-matrix includes the circularly shifted patches of the positive
-training sample $x$ by a cylic shift operator.
+where $X^{H}$ and $\lambda$represent the complex-conjugate of training
+samples and regularization term. More documentation on the spatial and
+fourier domain solutions can be found in \cite{henriques2015high}. The
+MOSSE tracker uses one training sample centred at estimated position
+of the target. This framework does not include enough background
+information into the learned model,$w$. The application of the
+circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
+makes it possible to include many background patches at a similar
+computational complexity. A circulant matrix includes the circularly
+shifted patches of the positive training sample $x$ by a cylic shift
+operator.
 
@@
 
-In this form, eq.~\ref{eq:FourierSolution} could prohibit us from implementing a
-high speed object tracking as we need to perform large number of
-element-wise division and multiplication operations. However, we know
-from \cite{gray2006toeplitz} that all circulant matrices are
-represented diagonally by the Fourier Transform regardless of the base
-sample $x$.
+In this form, the equation \ref{eq:FourierSolution} could prohibit us
+from implementing a high speed object tracking as we need to perform
+large number of element-wise division and multiplication
+operations. However, we know from \cite{gray2006toeplitz} that all
+circulant matrices are represented diagonally by the Fourier Transform
+regardless of the base sample $x$.
 %\begin{equation}
@@
 
-\subsection{Particle Filter} \label{sc:PF}
-The proposed {\it E}nKCF tracker does not update target's translation at every
-$n=5$ frames due to application of a scale filter, $R_{s}$. To avoid this to perform 
-smoother tracking, a Bayes Filter representing the evolution of target's motion can be added into our {\it E}nKCF tracking framework. To achieve this,
-we consider a variant of a Bayes Filter, \textit{Particle Filter}. The Particle
-Filter is a Sequential Monte Carlo method that uses a number of sample
-points to represent the posterior probability density functions (pdf)
-of the target motion.  The approximation becomes optimal with the
-infinite number of particles, however, its run-time complexity grows
-exponentially with the number of elements in the state space matrix,
-$X_{t}$. As the focus of this study is to design a high speed tracker,
-we keep the number of state space elements low and implement
-computationally efficient \textit{Weight Function} and
-\textit{Importance-Resampling} modules. We represent the state space
-matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$
-are the centroid of the target and $V$ represents the velocity
-components. We transit the particles with the first order Constant
-Velocity model. The centroid components are applied Gaussian Noise
-whereas the velocity components are assigned uniform noise
-representative of most of the objects in our tests. The observation
-likelihood is formulated based on the confidence map of $R_{t}^{L}$,
-$R_{t}^{S}$, and $R_{s}$.  The weights for the particles are computed
-as
+\subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
+As explained earlier, the {\it E}nKCF upates a target's translation at
+every other $k$ frames, particularly for estimating the target's
+scale. Although the strategy of updating every other $k$th frames will
+result in an optimal run-time performance, this may lead any potential
+drifts at the later frames. To prevent such potential mishaps from
+happening, we developed a Bayes filter that incorporates a target's
+motion to smooth any outputs from the {\it E}nKCF. In particular, we
+use a particle filter to estimate the target's image coordinate based
+on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
+Carlo method that uses a finite number of particles or samples to
+estimate the posterior probability density of a state of the system
+\cite{thrun2005probabilistic}. In this study, the state represents a
+target's pixel coordinates and its motion. In particular, the state of
+the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
+v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
+target's centroid, $v_x$ and $v_y$ are the estimated velocity along
+the $x$-axis and $y$-axis. The particle filter predicts, using a
+constant velocity motion model, a target's state by generating a
+predefined number of particles. And then the particle filter uses the
+confidence maps of {\it E}nKCF as observation to update the state. The
+weight of a particle is computed as:
 \begin{equation}
@@
 where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
-$N$ denotes the size of the window in consideration in confidence map. We can also use
-the euclidean distance of particles to the location of maximum response of 
-the confidence map, however, we believe that this approach could result in drifts
-in the case of multi-modal distributions.
+$N$ denotes the size of the window as that of a confidence
+map. Alternatively one can also use the euclidean distance of
+particles to the location of maximum response of the confidence
+map. This alternative, however, would result in drifts.
 
-The importance re-sampling module is triggered when the number of
-effective particles is smaller than a pre-defined threshold to avoid
-variance getting too small \cite{thrun2005probabilistic}. Re-sampling
-is implemented with efficient low-variance ratio method
-\cite{thrun2005probabilistic}. Finally, the expected mean of the
-approximated posterior pdf is computed as $\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.$
-The particles are assigned equal weight ($w_{p_{t}}=1/P$) after the importance
-re-sampling step in approximating the posterior pdf. It should be
-emphasized that we skip importance re-sampling step in the scale
-filter operation as the scale filter contains \textit{target-only}
-area and focuses on scale estimation. Additionally, it is
-more likely to get noisy confidence map from $R_{s}$. Finally, at
-every iteration we check the variance in the velocity components of
-the particles to re-assign velocities from uniform initial
-distribution to keep variance high enough.
+We chooses some particles based on their importance to estimate the
+target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
+\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
+of a particle filter, we skip the importance re-sampling step when the
+scale filter, $R_{s}$, estimates the target's scale change. This is
+because we observe the confidence map from the scale filter, $R_s$ is
+sometime noisy. In addition, at every iteration, we check the variance
+in the velocity components of the particles to re-assign velocities
+from uniform initial distribution to keep variance high enough.
 
@@
 %---------------------------------------------------------------------- 
-To verify the usefulness of our algorithm, we ran the proposed
-{\it E}nKCF against two publicly, available datasets:
-OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
+To verify the usefulness of our algorithm, we choose two public,
+available datasets:
+OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
+and
 UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
-OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects.
+The OTB100 dataset is comprised of the videos about 100 objects
+whereas UAV123 dataset contains aerial footage of 123 objects. We aims
+at developing an object tracking algorithm that ``efficiently'' runs
+in ``high speed,'' $\ge 300$ fps. Given this goal, we believe that the
+UAV123 video data is a better fit in evaluating the performance of the
+proposed algorithm. This is because there are many challenging scenes,
+e.g., abrupt scale/illumination changes as all the targets were
+recorded from bird-eye view. Although we are primarily interested in
+developing an algorithm for mobile, embedded robotic applications, it
+is important to compare the performance of the proposed algorithm with
+those of the state-of-the-art in nominal dataset for comparison. To
+this end, we chose the OTB100 data that contains the videos recorded
+from smart phones and typical cameras in perspective view.
 
-The UAVs employ mobiles platforms with limited computational resources. We
-believe that the proposed high-speed tracker can better fit to tracking from
-these platforms as it is highly efficient and scale adaptive.
-Taking into account these reasons, we first test it on UAV captured videos (UAV123).
-Later, we test in on OTB100 dataset which mostly contains videos captured from smart phones and cameras controlled by a human.
-Finally, the {\it E}nKCF2 is tested on temporally downsampled version of UAV123 dataset.
+{\it Burak: What does this mean?}  Finally, the {\it E}nKCF2 is tested
+on temporally downsampled version of UAV123 dataset.
 
-\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the
-committee of the correlation filters are important as the each
-correlation filter addresses the weakness of another one. For
-instance, $R_{t}^{L}$'s main task is to recover from the previous
-frame where only $R_{s}$ and particle filter's prior distribution are
-used to estimate scale and translation. We set the learning rates
-($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$
-and $0.010$. The desired response and hanning window for each KCF is
-shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel
-parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for
-$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. The learning rate is set to $0.12$
-for $R_{t}^{L}$ as it is run in every frame for $E_{n}KCF2$.
-In our particle filter implementation, we employ $1000$ particles and use the
-\textit{efficient number of samples} metric shown below to determine
-whether we need to perform importance re-sampling or not to keep
-reasonable variance.
+\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
+  E}nKCF is designed for addressing a specific challenge of a single,
+target tracking problem. Thus each of them should have different value
+for the optimal parameters. For instance, the primary task of the
+translation filter, $R_{t}^{L}$ is to estimate the translation of a
+target from the previous frame whereas the scale filter, $R_{s}$ and
+the estimated state of the particle filter are primarily used to
+estimate the scale and translation. Because of this, we set the
+learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
+$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
+$0.010$.
 
-\textbf{Features Selections.} We use the fast Histogram of Oriented
+{\it Burak: This is a dangling sentence.} The desired response and
+hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
+
+For the kernel of the Gaussian neighboring function, we empirically
+found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
+$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
+for $R_{t}^{L}$.
+
+{\it Burak: Did we even mention whether $R_{t}^{L}$ runs on every
+  frame? This might confuse others because all I remembered is we use
+  each of KCFs at every other $k$ or $n$ frames.}
+
+For the particle filter implementation, we found $1000$ is the optimal
+number of particles,
+
+{\it Burak: ?}
+and use the \textit{efficient number of samples}
+metric shown below to determine whether we need to perform importance
+re-sampling or not to keep reasonable variance.
+
+\textbf{Features Selections.} We used the fast Histogram of Oriented
 Gradients (fHoG)\cite{felzenszwalb2010object} and
-Color-naming\cite{van2009learning} features to learn target and
+color-naming\cite{van2009learning} features to learn target and
 background models. $R_{t}^{L}$ uses both fHoG and color features as it
@@
 as it is assigned lower template size, yielding space to exploit two
-feature modalities. We note that we use the same features for the {\it E}nKCF2 tracker.
+feature modalities. We note that we use the same features for the {\it
+  E}nKCF2 tracker.
 
@@
 
-\textbf{Overall Performance on UAV123 Dataset.}
-We compare the proposed tracker to other state-of-the-art high speed
-trackers using the \textit{Precision} and \textit{Success\:Rate}
-metrics. Precision is computed by thresholding the average euclidean
-distance between the ground truth and tracking output over the frames
-of one sequence. In precision, we rank the trackers based on the
-precision numbers at 20 pixels. The success rate metric evaluates the
-overlap between the ground truth and tracking output. The
-intersection-to-union ratio of two regions over the frames of one
-sequence. Finally, we count the number of frames with overlap larger
-than the success rate threshold and divide it by the number of
-frames. We compare our tracker to some other high-speed ($\geq$300
-fps) state-of-the-art trackers including KCF\cite{henriques2015high},
-CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast},
+\textbf{Performance on UAV123 Dataset.}  We compared the performance
+of the proposed tracking algorithm with those of the state-of-the-art
+high speed tracking algorithms in the \textit{Precision} and
+\textit{Success\:Rate} metrics. Precision is computed by thresholding
+the average euclidean distance between the centroid of the ground
+truth and that of an tracking algorithm output.
+
+{\it YoungWoo: End of 04/30/17}
+
+In precision, we rank the trackers based on the precision numbers at
+20 pixels. The success rate metric evaluates the overlap between the
+ground truth and tracking output. The intersection-to-union ratio of
+two regions over the frames of one sequence. Finally, we count the
+number of frames with overlap larger than the success rate threshold
+and divide it by the number of frames. We compare our tracker to some
+other high-speed ($\geq$300 fps) state-of-the-art trackers including
+KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting},
+STC\cite{zhang2014fast},
 MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
@@
 
-\textbf{Overall Performance on UAV123$\_$10fps Dataset.} We test our
+\textbf{Performance on UAV123$\_$10fps Dataset.} We test our
 slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
@@
 
-\textbf{Overall Performance on OTB100 Dataset.}
+\textbf{Performance on OTB100 Dataset.}
 In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the

### 2017-05-01 bmvc_review.tex

@@
 \includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
-\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large or small($\leq0.5$, or $\geq2$).}
-\label{Workflow_figure_EnKCF}
+\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large ($\leq0.5$, or $\geq2$).}
+\label{ResultsIntroduction}
 \end{figure*}
@@
   frame rate and run-time performance is similar to {\it E}nKCF. The
-  proposed framework can be seen in fig.~\ref{Workflow_figure_EnKCF2}.
+  proposed framework can be seen in fig.~\ref{Workflows}.
+%\begin{figure*}[!t]
+%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
+%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
+%\label{Workflow_figure_EnKCF}
+%\end{figure*}
+%\begin{figure*}[!h]
+%\centering
+%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
+%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
+%\label{Workflow_figure_EnKCF2}
+%\end{figure*}
 
@@
 higher speed.
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
+\caption{The three filters denoted as \textit{target+small background} translation filter,
+  \textit{target-only} scale filter and \textit{target+large background} translation filters are
+  shown. Also, the hanning window and desired Gaussian response for
+  each filter is displayed.}
+\label{fig:Filters}
+\end{figure}
 

### 2017-05-02 bmvc_review.tex
Complete a first round of proofreading.

@@
 
-\textbf{Features Selections.} We used the fast Histogram of Oriented
-Gradients (fHoG)\cite{felzenszwalb2010object} and
-color-naming\cite{van2009learning} features to learn target and
-background models. $R_{t}^{L}$ uses both fHoG and color features as it
-covers a large ROI where fHoG features may not be reliable alone. On
-the other hand, $R_{t}^{S}$ is assigned only fHoG features as it
-covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features
-as it is assigned lower template size, yielding space to exploit two
-feature modalities. We note that we use the same features for the {\it
-  E}nKCF2 tracker.
+\textbf{Features Selections.} As each of three KCFs in the {\it E}nKCF
+has different goals to accomplish, we used different features for each
+of them. In particular, the translation filter, $R_{t}^{L}$, uses both
+the fast Histograms of Oriented Gradients
+(fHoG)\cite{felzenszwalb2010object} and
+color-naming\cite{van2009learning} features to learn the background
+around the target more effectively. In fact we empirically found fHoG
+only didn't work well to cover the larger ROI. Another translation
+filter, $R_{t}^{S}$, used fHoG features only. The scale filter,
+$R_{s}$ used both fHoG and color features to learn the scale change
+more accurately.
 
@@
 
-{\it YoungWoo: End of 04/30/17}
+{\it Burak: What do mean by the following sentence? We had graphs
+  about precision, but I don't see any tables or anything else to rank
+  the algorithms based on the precision at 20 pixels.}
 
 In precision, we rank the trackers based on the precision numbers at
-20 pixels. The success rate metric evaluates the overlap between the
-ground truth and tracking output. The intersection-to-union ratio of
-two regions over the frames of one sequence. Finally, we count the
-number of frames with overlap larger than the success rate threshold
-and divide it by the number of frames. We compare our tracker to some
-other high-speed ($\geq$300 fps) state-of-the-art trackers including
-KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting},
-STC\cite{zhang2014fast},
+20 pixels.
+
+The success rate metric counts how many outputs from a tracking
+algorithm successfully overlap with those of the ground truth greater
+than a given threshold. The overlap is specifically computed by the
+Intersection-Over-Union (IoU) between a tracking output and that of
+the ground truth. Given the number of the correct frames based an IoU
+threshod, the success rate is the ratio of the correct frames to the
+number of the total frames for testing.
+
+{\it Burak: After you remove some of the trackers, replace that number
+  with ``some'' at the below as well as removing their names from the
+  following paragraph.}
+
+We compare our tracker to some other high-speed ($\geq$300 fps)
+state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
+\cite{henriques2012exploiting}, STC\cite{zhang2014fast},
 MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
@@
 Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
-dataset. The {\it E}nKCF tracker outperforms the other methods in
-high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
-accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
-the same dataset although it is $10$-$20$ times faster than these
-trackers. On the other hand, the {\it E}nKCF does a decent job on
-approximating the scale of the target in highly efficient manner. This
-is proved by the fact that it ranks third best tracker in terms of
-\textit{area under curve} (AUC) value for the success rate plot. It
-outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
-metric. Interestingly, it performs even better than most of the low
-speed trackers. For instance, it outperforms Struct and DSST by $5\%$
-and $10\%$ while running at more than $30$ and $10$ times larger
-operation rate.
+dataset.
+
+{\it Burak: I will re-write the text at below after you clean up the graphs.}
+
+{\it E}nKCF outperformed other, high-speed tracking methods by
+$3\%$-$15\%$ at 20 pixels precision metric whereas it is only $5\%$
+worse than SAMF, DSST and Struck on the same dataset although it is
+$10$-$20$ times faster than these trackers. On the other hand, the
+{\it E}nKCF does a decent job on approximating the scale of the target
+in highly efficient manner. This is proved by the fact that it ranks
+third best tracker in terms of \textit{area under curve} (AUC) value
+for the success rate plot. It outperforms the high speed trackers by
+about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even
+better than most of the low speed trackers. For instance, it
+outperforms Struct and DSST by $5\%$ and $10\%$ while running at more
+than $30$ and $10$ times larger operation rate.
 

### 2017-05-02 bmvc_review.tex
Comments Answered

@@
 noisy shape features due to its large search area. Figure
-\ref{Workflow_figure_EnKCF} illustrates the workflow of the proposed
+\ref{Workflows} illustrates the workflow of the proposed
 algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
-  E}nKCF. In the following section, we will briefly mention the theory
+  E}nKCF. We do not have a seperate pseudeo-code for {\it E}nKCF2 as there are only two differences between 
+  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
+to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
+tracker due to large ego-motion. In the following section, we will briefly mention the theory
 behind the KCF.
@@
 this end, we chose the OTB100 data that contains the videos recorded
-from smart phones and typical cameras in perspective view.
-
-{\it Burak: What does this mean?}  Finally, the {\it E}nKCF2 is tested
-on temporally downsampled version of UAV123 dataset.
+from smart phones and typical cameras in perspective view. Finally, the {\it E}nKCF2 is tested
+on temporally down-sampled version of the UAV123 dataset which is named UAV123$\_$10fps dataset.
 
@@
 $R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
-$0.010$.
-
-{\it Burak: This is a dangling sentence.} The desired response and
-hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
-
+$0.010$. The desired template response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
 For the kernel of the Gaussian neighboring function, we empirically
@@
 
-{\it Burak: Did we even mention whether $R_{t}^{L}$ runs on every
-  frame? This might confuse others because all I remembered is we use
-  each of KCFs at every other $k$ or $n$ frames.}
-
-For the particle filter implementation, we found $1000$ is the optimal
-number of particles,
-
-{\it Burak: ?}
-and use the \textit{efficient number of samples}
-metric shown below to determine whether we need to perform importance
-re-sampling or not to keep reasonable variance.
+We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
+The re-sampling is only performed when the \textit{efficient number of samples} (eq.~\ref{eq:Neff_PF}) is lower than a
+pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
+\begin{equation}
+	\hat{N}_{eff} \approx \dfrac{1}{\sum_{p=1}^{P}w_{p}^{2}}
+	\label{eq:Neff_PF}
+\end{equation}
 
@@
 
+{\it YoungWoo : Trackers are ranked in the legend in the graphs - the numbers next 
+to each tracker is precision at 20 px and AUC for the success rate. It is how people rank
+trackers in precision and success plots. I agree with you that we can have an additional table. Let me know what
+you think about it now.}
+
 In precision, we rank the trackers based on the precision numbers at
@@
 threshod, the success rate is the ratio of the correct frames to the
-number of the total frames for testing.
+number of the total frames for testing.  In the success rate plots, trackers are
+ranked based on AUC scores.
 
@@
 
-We compare our tracker to some other high-speed ($\geq$300 fps)
+{\it YoungWoo :  I thought we were going to do that tomorrow. I have generated figures and 
+I can easily remove any ones. SRDCF and MEEM are the top two as of now. I am working on removing them as of now. Please 
+consider that we do not have SRDCF and MEEM while you are editing the results section.}
+
+We compare our tracker to other high-speed ($\geq$300 fps)
 state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
@@
 the proposed trackers. These trackers include SAMF\cite{li2014scale},
-DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
-MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
+DSST\cite{danelljan2014accurate}, MEEM\cite{zhang2014meem}, Struck\cite{hare2012efficient}, and SRDCF\cite{danelljan2015learning}.
 Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123

### 2017-05-02 bmvc_review.tex
Paper trimmed for 9 pages Limit - Excluding References

@@
 slightly modify the {\it E}nKCF to perform tracking in low frame rate
-videos dominated by large ego-motion.  large ego-motion.  To verify
-the usefulness of the proposed method, we compared the performance of
-ours to those of the existing online tracking methods. Experimental
-results showed that the performance of ours are 72.53\% for precision
-on 20 pixels and 52.90\% for success rate for OTB100 data, and 55.71\%
-and 41.71\% for UAV123 data. These results confirmed that our method
+videos dominated by large ego-motion.  large ego-motion. Experimental
+results showed that the performance of ours are 70.10\% for precision
+on 20 pixels and 53.00\% for success rate for OTB100 data, and 54.50\%
+and 40.2\% for UAV123 data. These results confirmed that our method
 outperformed the existing ones over 5\% on precision on 20 pixels and
@@
 OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
-fps) for OTB100 and KCF (292 fps), DCF (457 fps), and STC (350 fps)
-for UAV123.
+fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
 \end{abstract}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
+\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
 \caption{The three filters denoted as \textit{target+small background} translation filter,
@@
 behind the KCF.
-
-\begin{algorithm}
+\begin{algorithm}[h]
+\small
 	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
@@
 			    \State // Model Update
-				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
 			    \State Update $R_{s}$ (Condition 1);
-				\EndIf							 
-				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
 			    \State Update $R_{t}^{L}$ (Condition 2);
-				\EndIf	
 			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
@@
 \end{algorithm}
-
 \begin{comment}
@@
 second with state-of-the-art tracking capabilities even in challenging
-cases. Its computational efficiency arises from its use of the
+cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
 discrete fourier transform of the circulant matrix and frequency
-domain element-wise operations known as hadamard product and
-division. The first example of frequency domain trackers is the MOSSE
-tracker running at $700$fps \cite{bolme2010visual}. It minimizes the
-ridge regression function in the frequency domain using a single
-template and intensity features. The KCF tracker, on the other hand,
-minimizes the regularized ridge regression function shown below.
+domain. The KCF tracker minimizes the regularized ridge regression function shown below.
 \begin{equation}
@@
 eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
-derivative of $E$ w.r.t $w$ to $0$. The primal solution in the
+derivative of $E$ w.r.t $w$ to $0$. 
+\begin{comment}The primal solution in the
 frequency domain is formulated as
@@
 %\end{equation}
-Then, the optimized solution vector in the Fourier domain $\hat{w}$ is formulated as
+\end{comment}
+Then, the Circulant-matrix based solution vector in the Fourier domain $\hat{w}$ is formulated as
 \begin{equation}
@@
 %kernels. 
-Similar to the diagonalization in the linear ridge regression
-solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized
-ridge regression can be made diagonal using the same circulant matrix
-theorem.  The diagonalized Fourier domain dual form solution can be
+The diagonalized Fourier domain dual form solution can be
 expressed as
@@
 where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
-known as \textit{gram matrix}. In this study, we will only focus on
-application of the Gaussian Kernel to the Correlation Filters. We
-refer the readers to \cite{henriques2015high} for the detailed
-documentation of the application of other kernels to the Correlation
-Filters. The Gaussian kernelization is
-expressed as
+known as \textit{gram matrix} and it is expressed as
 \begin{equation}
@@
 such as HoG and Color were later exploited to improve tracking
-accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
-multi-channel feature integration into the Gaussian Kernelization
+accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
+\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
 function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
@@
 \end{equation}
-
+\end{comment}
 Finally, detection step in multi-channel KCF framework is performed as
@@
 where $r$ denotes the correlation response at all cylic shifts of the
-first row of the kernel matrix $K$. The peak point of the response
-function gives us the estimated translation of the object from time
-step $t$-$1$ to $t$.
+first row of the kernel matrix.
 
@@
 $R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
-$0.010$. The desired template response and hanning window for each KCF is shown in fig.~\ref{fig:Filters}.
-For the kernel of the Gaussian neighboring function, we empirically
+$0.010$. For the kernel of the Gaussian neighboring function, we empirically
 found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
@@
 We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
-The re-sampling is only performed when the \textit{efficient number of samples} (eq.~\ref{eq:Neff_PF}) is lower than a
-pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
+The re-sampling is only performed when the \textit{efficient number of samples} ($	\hat{N}_{eff} \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1}
+$) is lower than a pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
 \begin{equation}
-	\hat{N}_{eff} \approx \dfrac{1}{\sum_{p=1}^{P}w_{p}^{2}}
 	\label{eq:Neff_PF}
@@
 
-\begin{figure}
-\centering
-\begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123.pdf}}
-\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123.pdf}}\\
-\end{tabular}
-\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 dataset.
-UAV123 Dataset consists of $123$ video sequences captured from a micro UAV including large camera motion, low resolution objects, partial and full occlusions.
-Our tracker better fits to tracking from aerial platforms as the scale change in successive frames are not dramatic.}
-\label{fig:UAV123_DATASET}
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_OTB100.pdf}}
-\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_OTB100.pdf}}\\
-\end{tabular}
-\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
-\label{fig:OTB100_DATASET}
-\end{figure}
-
 \textbf{Performance on UAV123 Dataset.}  We compared the performance
@@
 high speed tracking algorithms in the \textit{Precision} and
-\textit{Success\:Rate} metrics. Precision is computed by thresholding
-the average euclidean distance between the centroid of the ground
-truth and that of an tracking algorithm output.
+\textit{Success\:Rate} metrics. In precision, we rank the trackers based on the precision numbers at
+20 pixels whereas in the success rate plots, trackers are
+ranked based on area under curve (AUC) scores.
 
+\begin{comment}
 {\it Burak: What do mean by the following sentence? We had graphs
@@
 you think about it now.} 
+\end{comment}
 
-In precision, we rank the trackers based on the precision numbers at
-20 pixels.
-
-The success rate metric counts how many outputs from a tracking
-algorithm successfully overlap with those of the ground truth greater
-than a given threshold. The overlap is specifically computed by the
-Intersection-Over-Union (IoU) between a tracking output and that of
-the ground truth. Given the number of the correct frames based an IoU
-threshod, the success rate is the ratio of the correct frames to the
-number of the total frames for testing.  In the success rate plots, trackers are
-ranked based on AUC scores.
-
+\begin{comment}
 {\it Burak: After you remove some of the trackers, replace that number
@@
 consider that we do not have SRDCF and MEEM while you are editing the results section.}
-
+\end{comment}
 We compare our tracker to other high-speed ($\geq$300 fps)
 state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, STC\cite{zhang2014fast},
-MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
+\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and MOSSE\cite{bolme2010visual,henriques2015high}. Also, five relatively
 lower-speed ($\geq$50) trackers are used to evaluate the robustness of
 the proposed trackers. These trackers include SAMF\cite{li2014scale},
-DSST\cite{danelljan2014accurate}, MEEM\cite{zhang2014meem}, Struck\cite{hare2012efficient}, and SRDCF\cite{danelljan2015learning}.
-Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
+DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient}, MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and
+OAB \cite{zhang2012robust}. Fig.~\ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
 dataset.
@@
 in highly efficient manner. This is proved by the fact that it ranks
-third best tracker in terms of \textit{area under curve} (AUC) value
+second best tracker in terms of \textit{area under curve} (AUC) value
 for the success rate plot. It outperforms the high speed trackers by
@@
 than $30$ and $10$ times larger operation rate.
+
+\textbf{Performance on OTB100 Dataset.}
+In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
+OTB100 dataset to evaluate how good it generalizes to a traditional
+object tracking dataset. Again, it performs slightly better than the
+high speed trackers in precision. Interestingly, it outperforms the
+another correlation filter based tracker, DSST while running only
+$5\%$ behind of another low-speed scale adaptive SAMF tracker as shown in fig.~\ref{fig:UAV123_OTB100_DATASET}. As in
+UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
+scale changes. It is ranked as the third best tracker while being the
+second highest speed tracker behind MOSSE. These numbers
+prove that {\it E}nKCF is not only a good candidate for tracking on a
+UAV-based mobile platform but also mobile platforms on smart phones.
+\begin{figure}[!h]
+\centering
+\begin{tabular}{ccc}
+\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123.pdf}}
+\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123.pdf}}
+\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_OTB100.pdf}}
+\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
+\end{tabular}
+\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 (a) and OTB100 (b) datasets.}
+\label{fig:UAV123_OTB100_DATASET}
+\end{figure}
 
@@
 the other hand, it does decent job in scale estimation. It ranks as
-$4$th in AUC and it is $20$-$30$ faster than the ones with
-higher AUC.
-
-\begin{figure}
+second in AUC while running about $150$ faster than the MUSTER tracker.
+\begin{figure}[!h]
 \centering
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=4.00cm]{./figures/Precision_UAV123_10fps.pdf}}
-\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
+\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123_10fps.pdf}}
+\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
 \end{tabular}
@@
 
-\textbf{Performance on OTB100 Dataset.}
-In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
-OTB100 dataset to evaluate how good it generalizes to a traditional
-object tracking dataset. Again, it performs slightly better than the
-high speed trackers in precision. Interestingly, it outperforms the
-another correlation filter based tracker, DSST while running only
-$5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
-UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
-scale changes. It is ranked as the fifth best tracker while being the
-second highest speed tracker behind MOSSE. It performs only around
-$2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
-prove that {\it E}nKCF is not only a good candidate for tracking on a
-UAV-based mobile platform but also mobile platforms on smart phones.
-
+%\begin{figure}[!h]
+%\centering
+%\begin{tabular}{cc}
+%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
+%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
+%\end{tabular}
+%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
+%\label{fig:OTB100_DATASET}
+%\end{figure}
 %---------------------------------------------------------------------- 

### 2017-05-02 bmvc_review.tex
Edited on experiment.

@@
 this end, we chose the OTB100 data that contains the videos recorded
-from smart phones and typical cameras in perspective view. Finally, the {\it E}nKCF2 is tested
-on temporally down-sampled version of the UAV123 dataset which is named UAV123$\_$10fps dataset.
+from smart phones and typical cameras in perspective view. Finally,
+the {\it E}nKCF2 is tested on temporally down-sampled version of the
+UAV123 dataset which is named UAV123$\_$10fps dataset.
 
@@
 $R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
-$0.010$. For the kernel of the Gaussian neighboring function, we empirically
-found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
-$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
-for $R_{t}^{L}$.
-
-We tuned the number of particles in the particle filter to $1000$ after carrying out experiments, 
-The re-sampling is only performed when the \textit{efficient number of samples} ($	\hat{N}_{eff} \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1}
-$) is lower than a pre-defined threshold. This way, we can continuously keep reasonable variance among particles.
-\begin{equation}
-	\label{eq:Neff_PF}
-\end{equation}
+$0.010$. For the kernel of the Gaussian neighboring function, we
+empirically found the optimal values of $\alpha$ as $0.6$, $0.4$, and
+$0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate
+as $0.12$ for $R_{t}^{L}$. For the particle filter, we empirically set
+the number of particles to $1000$ to balance the run-time performance
+and accuracy. To keep the level of variance among the particles
+reasonable, we performed the re-sampling only when the
+\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
+(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
+threshold.
 
@@
 high speed tracking algorithms in the \textit{Precision} and
-\textit{Success\:Rate} metrics. In precision, we rank the trackers based on the precision numbers at
-20 pixels whereas in the success rate plots, trackers are
-ranked based on area under curve (AUC) scores.
+\textit{Success\:Rate} metrics. In precision, we rank the trackers
+based on the precision numbers at 20 pixels whereas in the success
+rate plots, trackers are ranked based on area under curve (AUC)
+scores. The tracking algorithms used for the comparison include ones
+in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high}, CSK
+\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
+MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
+lower-speed ($\geq$50), i.e., SAMF\cite{li2014scale},
+DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
+MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
+\cite{zhang2012robust}.
 
-\begin{comment}
-{\it Burak: What do mean by the following sentence? We had graphs
-  about precision, but I don't see any tables or anything else to rank
-  the algorithms based on the precision at 20 pixels.}
-
-{\it YoungWoo : Trackers are ranked in the legend in the graphs - the numbers next 
-to each tracker is precision at 20 px and AUC for the success rate. It is how people rank
-trackers in precision and success plots. I agree with you that we can have an additional table. Let me know what
-you think about it now.} 
-\end{comment}
-
-\begin{comment}
-{\it Burak: After you remove some of the trackers, replace that number
-  with ``some'' at the below as well as removing their names from the
-  following paragraph.}
-
-{\it YoungWoo :  I thought we were going to do that tomorrow. I have generated figures and 
-I can easily remove any ones. SRDCF and MEEM are the top two as of now. I am working on removing them as of now. Please 
-consider that we do not have SRDCF and MEEM while you are editing the results section.}
-\end{comment}
-We compare our tracker to other high-speed ($\geq$300 fps)
-state-of-the-art trackers including KCF\cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and MOSSE\cite{bolme2010visual,henriques2015high}. Also, five relatively
-lower-speed ($\geq$50) trackers are used to evaluate the robustness of
-the proposed trackers. These trackers include SAMF\cite{li2014scale},
-DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient}, MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and
-OAB \cite{zhang2012robust}. Fig.~\ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
-dataset.
-
-{\it Burak: I will re-write the text at below after you clean up the graphs.}
-
-{\it E}nKCF outperformed other, high-speed tracking methods by
-$3\%$-$15\%$ at 20 pixels precision metric whereas it is only $5\%$
-worse than SAMF, DSST and Struck on the same dataset although it is
-$10$-$20$ times faster than these trackers. On the other hand, the
-{\it E}nKCF does a decent job on approximating the scale of the target
-in highly efficient manner. This is proved by the fact that it ranks
-second best tracker in terms of \textit{area under curve} (AUC) value
-for the success rate plot. It outperforms the high speed trackers by
-about $20\%$-$25\%$ in AUC metric. Interestingly, it performs even
-better than most of the low speed trackers. For instance, it
-outperforms Struct and DSST by $5\%$ and $10\%$ while running at more
-than $30$ and $10$ times larger operation rate.
+Figure \ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
+dataset. {\it E}nKCF outperformed most of the high-speed tracking
+methods by $3\%$-$15\%$ at 20 pixels precision metric. Three
+algorithms, SAMF, DSST, and Struck did about 5\% better than ours in
+accuracy, but 10-20\% slower than ours. For the scale adaptation, {\it
+  E}nKCF did second best in terms of \textit{area under curve} (AUC)
+value for the success rate plot. It outperformed other tracking
+methods in high-speed by about $20\%$-$25\%$ in AUC metric. In
+addition, it performed even better than those algorithms that are
+slow, but a bit better in precision. For example, for AUC, {\it E}nKCF
+outperformed Struct and DSST by $5\%$ and $10\%$ while running at more
+than $10$ and $30$ times faster.
 

### 2017-05-02 bmvc_review.tex
Revised the section about experiment.

@@
 
-\textbf{Performance on OTB100 Dataset.}
-In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
-OTB100 dataset to evaluate how good it generalizes to a traditional
-object tracking dataset. Again, it performs slightly better than the
-high speed trackers in precision. Interestingly, it outperforms the
-another correlation filter based tracker, DSST while running only
-$5\%$ behind of another low-speed scale adaptive SAMF tracker as shown in fig.~\ref{fig:UAV123_OTB100_DATASET}. As in
-UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
-scale changes. It is ranked as the third best tracker while being the
-second highest speed tracker behind MOSSE. These numbers
-prove that {\it E}nKCF is not only a good candidate for tracking on a
-UAV-based mobile platform but also mobile platforms on smart phones.
+\textbf{Performance on OTB100 Dataset.}  We evaluated the performance
+of the {\it E}nKCF tracker on the OTB100 dataset, and observed a
+performance similar to that of UAV123 data. Figure
+\ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
+dataset. For the precision metric, {\it E}nKCF performed slightly
+better than most of tracking algorithms in high-speed
+trackers. Interestingly, it outperformed another correlation filter
+based tracker, DSST, but performing $5\%$ behind of another low-speed
+scale adaptive SAMF tracker.
+
+As in UAV123 dataset, the {\it E}nKCF
+performs exceptionally in handling the scale changes. It is ranked as
+the third best tracker while being the second highest speed tracker
+behind MOSSE. These numbers prove that {\it E}nKCF is not only a good
+candidate for tracking on a UAV-based mobile platform but also mobile
+platforms on smart phones.
 \begin{figure}[!h]

### 2017-05-02 bmvc_review.tex
Completed to do a proofreading on the experimental section.

@@
 \textbf{Performance on OTB100 Dataset.}  We evaluated the performance
-of the {\it E}nKCF tracker on the OTB100 dataset, and observed a
-performance similar to that of UAV123 data. Figure
+of the {\it E}nKCF tracker on the OTB100 dataset. Figure
 \ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
-dataset. For the precision metric, {\it E}nKCF performed slightly
+dataset. Like in UAV123 dataset, we observed a similar performance. In
+particular, {\it E}nKCF showed a good performance for handling the
+scale changes. It was the third best and the second fastest tracking
+algorithm. For the precision metric, {\it E}nKCF performed slightly
 better than most of tracking algorithms in high-speed
@@
 scale adaptive SAMF tracker. 
-
-As in UAV123 dataset, the {\it E}nKCF
-performs exceptionally in handling the scale changes. It is ranked as
-the third best tracker while being the second highest speed tracker
-behind MOSSE. These numbers prove that {\it E}nKCF is not only a good
-candidate for tracking on a UAV-based mobile platform but also mobile
-platforms on smart phones.
 \begin{figure}[!h]

### 2017-05-02 bmvc_review.tex
Wrote a conclusion.

@@
 %---------------------------------------------------------------------- 
+Running a computer vision algorithm would be very attractive for any
+mobile, unmanned robotic solutions on real-world applications. To make
+such applications practical, those algorithms should run faster with
+small footprint of computation resouce consumption. To this end, we
+proposed an extension of KCF that deploys three KCFs in turn to
+address the scale change and dynamic maneuvers of a target. The way we
+ran three KCFs in a harmonious way optimal in a sense that efficiently
+handled the scale change and effectively learned the translation of
+the target. However, by doing so, our algorithm may introduce any
+potential drifts. To prevent this from happening, we developed a Bayes
+filter, particle filter, to smooth the transition between three
+KCFs. In particular, the particle filter estimated the target's pixel
+coordinates using information about the target's motion observed over
+frames. Experimental results showed that the performance of ours are
+70.10\% for precision on 20 pixels and 53.00\% for success rate for
+OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These results
+confirmed that our method outperformed the existing ones over 5\% on
+precision on 20 pixels and 10-20\% on AUC on average. Our
+implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
+DCF (457 fps) for UAV123.
 

### 2017-05-02 bmvc_review.tex
Draft was spell-checked.

@@
   the flexibility of the ensemble of KCFs approach we propose. The
-  original {\it E}nKCF is slighlty modified to track in low frame rate
+  original {\it E}nKCF is slightly modified to track in low frame rate
   videos ($10$fps) dominated by large ego-motion. We do not integrate
   the particle filter in {\it E}nKCF2 as we test it on a temporally
-  downsampled UAV123 dataset (UAV123$\_$10fps) including sequences
+  down-sampled UAV123 dataset (UAV123$\_$10fps) including sequences
   with large ego-motion on a UAV platform. Particle Filter can be
@@
 filter, $R_{s}$, tighter reduces the size of the template for the
-elementwise multiplication, resulting in a scale estimation in a
+element-wise multiplication, resulting in a scale estimation in a
 higher speed.
@@
 The order of running these three KCFs is important as each of these
-filters aims at addressing different chanllenges while perserving
+filters aims at addressing different challenges while preserving
 run-time performance as fast as possible. The \textit{target+large
@@
 noisy shape features due to its large search area. Figure
-\ref{Workflows} illustrates the workflow of the proposed
+\ref{Workflows} illustrates the work-flow of the proposed
 algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
-  E}nKCF. We do not have a seperate pseudeo-code for {\it E}nKCF2 as there are only two differences between 
+  E}nKCF. We do not have a separate pseudo-code for {\it E}nKCF2 as there are only two differences between 
   {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
@@
 cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
-discrete fourier transform of the circulant matrix and frequency
+discrete Fourier transform of the circulant matrix and frequency
 domain. The KCF tracker minimizes the regularized ridge regression function shown below.
@@
 \end{equation}
-where $y$ represents the desired continous response whereas $h$ and
+where $y$ represents the desired continuous response whereas $h$ and
 $x_{c}$ represents the learned correlation filter and training
@@
 \cite{henriques2015high,galoogahi2013multi} makes it possible to
-integrate multi-channel features such as HoG and colour into the ridge
+integrate multi-channel features such as HoG and color into the ridge
 regression function. The closed-form solution for the
@@
 samples and regularization term. More documentation on the spatial and
-fourier domain solutions can be found in \cite{henriques2015high}. The
-MOSSE tracker uses one training sample centred at estimated position
+Fourier domain solutions can be found in \cite{henriques2015high}. The
+MOSSE tracker uses one training sample centered at estimated position
 of the target. This framework does not include enough background
@@
 computational complexity. A circulant matrix includes the circularly
-shifted patches of the positive training sample $x$ by a cylic shift
+shifted patches of the positive training sample $x$ by a cyclic shift
 operator.
@@
 \end{equation}
-where $r$ denotes the correlation response at all cylic shifts of the
+where $r$ denotes the correlation response at all cyclic shifts of the
 first row of the kernel matrix.
@@
 \subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
-As explained earlier, the {\it E}nKCF upates a target's translation at
+As explained earlier, the {\it E}nKCF updates a target's translation at
 every other $k$ frames, particularly for estimating the target's
@@
 $N$ denotes the size of the window as that of a confidence
-map. Alternatively one can also use the euclidean distance of
+map. Alternatively one can also use the Euclidean distance of
 particles to the location of maximum response of the confidence
@@
 slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
-UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps
+UAV123$\_$10fps dataset. This dataset is down-sampled at $10$ fps
 version of the UAV123 dataset. The original dataset is already
 dominated by fast object motion and large ego-motion. With
-downsampling, it becomes very challenging with object and ego-motion
+down-sampling, it becomes very challenging with object and ego-motion
 getting drastically larger. The performance of the proposed {\it
@@
 %---------------------------------------------------------------------- 
-Running a computer vision algorithm would be very attractive for any
-mobile, unmanned robotic solutions on real-world applications. To make
-such applications practical, those algorithms should run faster with
-small footprint of computation resouce consumption. To this end, we
-proposed an extension of KCF that deploys three KCFs in turn to
-address the scale change and dynamic maneuvers of a target. The way we
-ran three KCFs in a harmonious way optimal in a sense that efficiently
-handled the scale change and effectively learned the translation of
-the target. However, by doing so, our algorithm may introduce any
-potential drifts. To prevent this from happening, we developed a Bayes
-filter, particle filter, to smooth the transition between three
-KCFs. In particular, the particle filter estimated the target's pixel
-coordinates using information about the target's motion observed over
-frames. Experimental results showed that the performance of ours are
-70.10\% for precision on 20 pixels and 53.00\% for success rate for
-OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These results
-confirmed that our method outperformed the existing ones over 5\% on
-precision on 20 pixels and 10-20\% on AUC on average. Our
-implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
-DCF (457 fps) for UAV123.
-
+Running a computer vision algorithm would be economically and
+practically, very attractive for any mobile, unmanned robotic
+solutions on real-world applications. To make such pipelines more
+realistic, however, those algorithms should run faster with small
+footprint of computation resource consumption. To make an object
+tracking algorithm with these practical requirements available, we
+proposed an extension of KCF that essentially deploys three KCFs, in
+turn, to address the scale change and dynamic maneuvers of a
+target. The way we ran three KCFs in a harmonious way optimal in a
+sense that efficiently handled the scale change and effectively
+learned the translation of the target. However, by doing so, our
+algorithm may introduce any potential drifts. To prevent this from
+happening, we developed a Bayes filter, particle filter, to smooth the
+transition between three KCFs. In particular, the particle filter
+estimated the target's pixel coordinates using information about the
+target's motion observed over frames. We used two publicly available
+dataset to evaluate the performance of the proposed algorithm and
+found that the performance of ours are 70.10\% for precision on 20
+pixels and 53.00\% for success rate for OTB100 data, and 54.50\% and
+40.2\% for UAV123 data. On average our method outperformed the
+existing ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
+average. Our implementation ran at 340 fps for OTB100 and at 416 fps
+for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
+(292 fps), DCF (457 fps) for UAV123. 
 %--------------

### 2017-05-02 bmvc_review.tex
Revised the KCF section partially.

@@
 \subsection{Kernelized Correlation Filter} \label{sec:kcf}
-The Kernelized Correlation Filter tracker has recently been
-increasingly popular due to its operation at hundreds of frames per
-second with state-of-the-art tracking capabilities even in challenging
-cases \cite{henriques2012exploiting,henriques2015high}. Its computational efficiency arises from its use of the
-discrete Fourier transform of the circulant matrix and frequency
-domain. The KCF tracker minimizes the regularized ridge regression function shown below.
+The Kernelized Correlation Filter is a well, known single target
+tracking method and thetheory and its workflowhas been detailed in
+other papers already
+\cite{henriques2012exploiting,henriques2015high}. This section briefly
+goes over the parts of the KCF relevantto thisstudy. Its
+computational efficiency arises from its use of the discrete Fourier
+transform of the circulant matrix and frequency domain. The KCF
+essentially solves the problem of a regression in the form of the
+regularized ridge regression as:
 \begin{equation}
@@
 $x_{c}$ represents the learned correlation filter and training
-template for the given channel. The $c$ parameter included in
-\cite{henriques2015high,galoogahi2013multi} makes it possible to
-integrate multi-channel features such as HoG and color into the ridge
-regression function. The closed-form solution for the
-eq.~\ref{eq:Closedform_RidgeReg} can be obtained by setting the
-derivative of $E$ w.r.t $w$ to $0$. 
-\begin{comment}The primal solution in the
-frequency domain is formulated as
-%\begin{equation}
-%w = (X^{T}X+\lambda)^{-1}y
-%\label{eq:SpatialSolution}
-%\end{equation}
-\begin{equation}
-w = (X^{H}X+\lambda I)^{-1}X^{T}y
-\label{eq:FourierSolution}
-\end{equation}
-where $X^{H}$ and $\lambda$represent the complex-conjugate of training
-samples and regularization term. More documentation on the spatial and
-Fourier domain solutions can be found in \cite{henriques2015high}. The
-MOSSE tracker uses one training sample centered at estimated position
-of the target. This framework does not include enough background
-information into the learned model,$w$. The application of the
-circulant matrix theorem into the eq.~\ref{eq:Closedform_RidgeReg}
-makes it possible to include many background patches at a similar
-computational complexity. A circulant matrix includes the circularly
-shifted patches of the positive training sample $x$ by a cyclic shift
-operator.
+template for the given channel. The parameter $c$ enabled one to
+integrate features in multiple channels, such as HoG and color, in
+this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
+solution for Equaiton \ref{eq:Closedform_RidgeReg} is available by
+taking the derivative of $E$ w.r.t $w$ to $0$. To make this
+closed-form solution with
 
-%By applying shifting operation to the base sample, we can generate the circulant
-%matrix as
-%\begin{equation}
-%C = Px.
-%\label{eq:CirculantMatrixGeneration}
-%\end{equation}
-%The circulant matrix of a base sample $x$ can be interpreted as the
-%rows of a training matrix $X$ where each row represents features of a
-%training sample. Mathematically, this can be written as
-%\begin{equation}
-%X = C(x)
-%\label{eq:CIrculantMatrixTrainingData}
-%\end{equation}
-
-In this form, the equation \ref{eq:FourierSolution} could prohibit us
-from implementing a high speed object tracking as we need to perform
-large number of element-wise division and multiplication
-operations. However, we know from \cite{gray2006toeplitz} that all
-circulant matrices are represented diagonally by the Fourier Transform
-regardless of the base sample $x$.
-%\begin{equation}
-%X = Fdiag(\hat{x})F^{H},
-%\label{eq:CirculantMatrixDFT}
-%\end{equation}
-%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
-%Discrete Fourier Transform of the base sample $x$. 
-%To simplify the
-%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
-%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
-%\begin{equation}
-%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
-%\label{eq:SimplificationX} 
-%\end{equation}
-\end{comment}
-Then, the Circulant-matrix based solution vector in the Fourier domain $\hat{w}$ is formulated as
+Then, the Circulant-matrix based solution vector in the Fourier domain
+$\hat{w}$ is formulated as
 \begin{equation}

### 2017-05-02 bmvc_review.tex
KCF section, half-way through.

@@
 this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
-solution for Equaiton \ref{eq:Closedform_RidgeReg} is available by
-taking the derivative of $E$ w.r.t $w$ to $0$. To make this
-closed-form solution with
-
-Then, the Circulant-matrix based solution vector in the Fourier domain
-$\hat{w}$ is formulated as
+solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
+taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
+$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
+multiplication in frequency domain was proposed as a sub-linear
+solution for $\hat{w}$:
 \begin{equation}
@@
 \end{equation}
-To further improve the robustness to geometric and photographic variations, one can exploit non-linear
-regression function in the Correlation Filter framework \cite{henriques2015high}. 
+To make the above, closed-form solution more robust to any geometric
+and photometric variations, a non-linear version is also proposed
+\cite{henriques2015high}.
 %\begin{equation}

### 2017-05-02 bmvc_review.tex
Figures Updated

@@
 later. By alternating three KCFs in turn, our algorithm runs as fast
-as or faster than the original KCF. From our experiments, we
-empirically found that five is the optimal for $k$ in terms of
-precision and success rates. We'll detail this at the experimental
-section later.
-
+as or faster than the original KCF. 
 \begin{figure}[!h]
@@
 \bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
+\centering \footnotesize (a) Precision and Success rates for UAV123 \quad \quad \quad \quad \quad (b) Precision and Success rates for OTB100
 \end{tabular}

### 2017-05-02 bmvc_review.tex
Completed to proofreading on KCF part.

--- 2017-05-02 bmvc_review.tex
@@
 \end{equation}
-To make the above, closed-form solution more robust to any geometric
-and photometric variations, a non-linear version is also proposed
-\cite{henriques2015high}.
-%\begin{equation}
-%\alpha = y(K+\lambda I)^{-1}
-%\end{equation}
-%where $K$ and $\alpha$ represent the kernel matrix and corresponding
-%dual space solution. 
-%\cite{henriques2015high} states that kernel
-%matrices is circulant for datasets of circular cylic satisfying the
-%following theorem.
-%\begin{equation}
-%k(x,x^{'}) = k(Mx,Mx^{'}),
-%\label{eq:KernelCirculantTheorem}
-%\end{equation}
-%where $M$ represents the permutation matrix. Some kernels satisfying
-%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
-%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
-%kernels. 
-The diagonalized Fourier domain dual form solution can be
-expressed as
+In fact, a non-linear version of this closed-form solution is proposed
+to make it more robust to any geometric and photometric variations
+\cite{henriques2015high}. In particular, the diagonalized Fourier
+domain dual form solution is expressed as
 \begin{equation}
@@
 \end{equation}
-%\begin{equation}
-%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
-%\label{eq:GaussianCorrelationSingleChannel}
-%\end{equation}
-The first correlation filter based trackers used grayscale feature ($C=1$) to
-learn the solution vector $w$, however, multi-channel features
-such as HoG and Color were later exploited to improve tracking
-accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
-\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
-function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
-in a very straight-forward way by summing the correlation result over the channels.
-
-Training shown in eq.~\ref{eq:FourierDualDomainSolution}
-gives us $\hat{a}$ learned in time step $t$. We can accumulate
-$\hat{a}$ over time to integrate more temporal information. This can
-be expressed as
-\begin{equation}
-\hat{a}_{t} = (1-\beta)\hat{a}_{t-1} + \beta\hat{a}_{t}. 
-\end{equation}
-\end{comment}
-Finally, detection step in multi-channel KCF framework is performed as
+An early version based on this formulation used grayscale feature
+($C=1$) to learn the solution vector $w$ and multi-channel features
+such as HoG and Color showed improved accuracy
+\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
+one can execute an object detection using this kernelized correlation
+filter with multi-channel features as 
 \begin{equation}

### 2017-05-02 bmvc_review.tex
Second-round of editing has began.

@@
 Computer vision technologies are very attractive for practical
-applications for embedded systems. This is primarily because most of
+applications on embedded systems. This is primarily because most of
 embedded systems already includes image acquisition pipeline and a
@@
 needs to satisfy, at least, two criteria: minimal, manual intervention
-after deployment and small footprint of computing resource consumption
-and on executable code, with the assumption of reasonably good
-performance. To this end, in this paper, we propose an ensemble of the
-kernelized correlation filters (KCF), we call {\it E}nKCF, for a
-single-target object tracking. In particular, we developed a committee
-of KCFs to specifically address the scale-change and dynamic maneuver
-of the target over frames. In addition, we devised a Bayes filter for
-a smooth transition between individual KCFs' executions. Also, we
-slightly modify the {\it E}nKCF to perform tracking in low frame rate
-videos dominated by large ego-motion.  large ego-motion. Experimental
-results showed that the performance of ours are 70.10\% for precision
-on 20 pixels and 53.00\% for success rate for OTB100 data, and 54.50\%
-and 40.2\% for UAV123 data. These results confirmed that our method
-outperformed the existing ones over 5\% on precision on 20 pixels and
-10-20\% on AUC on average. Our implementation ran at 340 fps for
-OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
-fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
+after deployment and small footprint of consuming computational
+resources and on executable code, with the assumption of reasonably
+good performance. To this end, in this paper, we propose an ensemble
+of the kernelized correlation filters (KCF), we call {\it E}nKCF, for
+the problem of a single-target object tracking. In particular, we
+developed a committee of KCFs to specifically address the scale-change
+and dynamic maneuver of the target over frames. In addition, we
+devised a Bayes filter for a smooth transition between individual
+KCFs' executions. Experimental results showed that the performance of
+ours are 70.10\% for precision on 20 pixels and 53.00\% for success
+rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. In other
+words, these results showed that our method is better than existing
+ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
+average. Our implementation ran at 340 fps for OTB100 and at 416 fps
+for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
+(292 fps), DCF (457 fps) for UAV123.
 \end{abstract}
@@
 \section{Introduction}
-\begin{comment}
-\begin{itemize}
-\item YoungWoo: Clean up the introduction
-\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
-\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
-\item By Monday, we'll have a draft ready to submit.
-\end{itemize}
-\end{comment}
 A recent proliferation of air/ground/water unmanned vehicle
 technologies has ever increased interests on deploying intelligent
-algorithms on embedded or mobile platforms. Among those technologies,
-computer vision algorithms are getting more attentions primarily
-because payloads of those mobile platforms are limited to carry any
-other sensors than a lightweight or an array of monocular cameras. For
-example, instead of having just bare flight function with video
-recording, an unmanned air vehicle (UAV) equipped with an object or
-feature following functionality would make it more useful in the
-application of monitoring/surveillance/surveying on private
-properties/wild-life/crop, video recording on sports/movies/events,
-many others.
+algorithms to any existing embedded and/or mobile platforms. Among
+those technologies, computer vision algorithms are getting more
+attentions primarily because payloads of those mobile platforms are
+limited to carry any other sensors than a lightweight or an array of
+monocular cameras. For example, instead of having just bare flight
+function with video recording, an unmanned air vehicle (UAV) equipped
+with an object or feature following functionality would make it more
+useful in the application of monitoring/surveillance/surveying on
+private properties/wild-life/crop, video recording on
+sports/movies/events, many others.
 
-In this paper, we propose a single-target tracking aiming at running
-on any embedded or mobile platforms that doesn't require an offline
-training, and can run on an embedded system. In particular, we would
-like to make our algorithm 1) learn the appearance model of a target
-on the fly and 2) run as fast on a typical desktop as up to
+In this paper, we propose a single-target tracking algorithm aiming at
+running on any embedded or mobile platforms that doesn't require an
+offline training, and can run on an embedded system. In particular, we
+would like to make our algorithm 1) learn the appearance model of a
+target on the fly and 2) run as fast on a typical desktop as up to
 $300$-$400$Hz so that it could run, at least, faster than 30Hz when it
-is deployed on a low-end, embedded system. With these features, our
-tracking algorithm is ready to track an object of interest when it is
-deployed on an embedded system. To this end, an online learning highly
-efficient object tracking is more appropriate.
+is deployed on a low-end, embedded system.\footnote{We empirically
+  come up with this computation about an 1/10th scale down of
+  computational resources from a typical PC to an embedded system.}
 
@@
 \cite{henriques2015high}. One can optimally solve this regression
-problem using a ridge regression in a closed form. However, such a
+problem using a ridge regression in a closed form. However, this
 solution involves in expensive matrix operations
@@
 in VOT15 challenge, in terms of run-time and tracking
-accuracy. However, the vanilla form of such an online tracker is prone
+accuracy. However, a vanilla form of such an online tracker is prone
 to drift, and fails to track a target over a long period of time
@@
 implemented \cite{santner2010prost}. For example, a naive way of
-handling a scale change of a target could reduce the run-time
+handling a scale change of a target by just having multiple
+correlation filters running on each frame could reduce the run-time
 performance from 300 to 100 fps. A seemingly obvious way of addressing
@@
 \includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
-\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large ($\leq0.5$, or $\geq2$).}
+\caption{Examples of tracking results by the proposed method on the
+  ``UAV123'' dataset. This ``UAV123'' dataset is challenging for
+  object tracking as a target's scale is changed drastically with a
+  few frames.}
 \label{ResultsIntroduction}
@@
 Another way of handling the scale change for the correlation filter
-based approach is to find a correct scale at a location where a target
-highly likely appears \cite{zhang2014fast}. In particular, they use
-the MOSSE tracker to estimate a target's translation. The scale is
-updated in a way where the confidence map is used to determine the
-scale change between successive frames. This is because they assume
-the scale of a target wouldn't change much over two consecutive
+based approach is to estimate a correct scale at a location where a
+target highly likely appears \cite{zhang2014fast} -- estimate a
+target's translation first and estimate a correct scale afterward. In
+particular, they use the MOSSE tracker to estimate a target's
+translation. And then they attemped to update the scale of the target
+a way where the confidence map is used to determine the scale change
+between successive frames. This is based on an assumption that the
+scale of a target wouldn't change much over two consecutive
 frames. Similarly \cite{ma2015long} used two KCFs to learn the
@@
 idea -- the idea of deploying multiple KCFs to address the issues of
-single target tracking: scale and translation in a highly efficient
-manner.  In this paper, we use an ensemble of KCFs in turn, instead of
-running them all together on every frame. By doing so, we could still
-address the scale change and estimate target's motion efficiently
-while increasing run-time performance. In particular, we deploy three
-KCF in turn: \textit{target}+\textit{small background} translation
-filter ($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
-\textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). Fig.~\ref{fig:Filters} shows examples of the ROIs
-associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
-\begin{comment}
-{\it We may not need this.}
-The recent progress on development of convolutional neural networks
-(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
-the record for the ImageNet competition, at every year, new and better
-results are reported. Moreover, there have been many attempts to
-deploy CNN on the mobile devices
-\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
-a supervised learning based object tracking is that an either online
-\cite{nam2016} or offline \cite{held2016} training tracker has to be
-prior to deploy the algorithm.
-\end{comment}
+single target tracking: scale and translation, but in a more efficient
+way. To be more specific, we use an ensemble of KCFs in turn, instead
+of running them all together on every frame. In particular, we deploy
+three KCF in turn: \textit{target}+\textit{small background}
+translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
+($R_{s}$) and \textit{target}+\textit{large background} translation
+filter ($R_{t}^{L}$). By doing so, we could still address the scale
+change and estimate target's motion efficiently while increasing
+run-time performance. Figure \ref{fig:Filters} shows examples of the
+ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
 
@@
   proposed framework can be seen in fig.~\ref{Workflows}.
-%\begin{figure*}[!t]
-%\includegraphics[width=\textwidth]{figures/Workflow_MKCF+PF.pdf}
-%\caption{The workflow of the proposed {\it E}nKCF with a particle filter.}
-%\label{Workflow_figure_EnKCF}
-%\end{figure*}
-%\begin{figure*}[!h]
-%\centering
-%\includegraphics[width=0.75\textwidth]{figures/Workflow_EnKCF2+PF.pdf}
-%\caption{The workflow of our {\it E}nKCF2 tracker designed to handle large object motion and ego-motion.}
-%\label{Workflow_figure_EnKCF2}
-%\end{figure*}
-
-\begin{comment}
-
-\item \textbf{Re-Detection} A target loss is inevitable in object
-  tracking. To cope with this, we developed a new target, re-detection
-  that reliably detects when to lose the target and effectively
-  re-detect the lost target. {\it How we can show how good our
-    re-detection method is?}
-
-\item We build a highly efficient ($\geq300$ fps) scale adaptive
-  multiple kernelized correlation filter based tracker that
-  outperforms the original KCF implementation with fixed scale
-  framework both in terms of accuracy and performance. The studies
-  following the KCF improved the fixed scale framework by running
-  detection on a number of candidate ROIs to figure out the new scale
-  of the object after estimating the translation of the object. This
-  approach adds additional complexity to the original KCF
-  implementation and drags down the run-time performance from $300$
-  fps to less than $100$ fps.
-
-\item We propose a target re-detection module that can minimize the
-  target loss due to the scale filter that learns the object model
-  using only-object area. Also, the target re-detection step is
-  required to handle severe occlusions, pose variations, illumination
-  changes and fast motion.
-
-\item Since our visual tracker mostly focuses on tracking objects from
-  aerial moving platforms, we design a new robust target-to-camera
-  distance estimation method. This way, a safe distance between the
-  target and the camera-platform can be preserved.
-\end{comment}
-
 \end{itemize}
@@
 %---------------------------------------------------------------------- 
-In this paper, we extend the KCF in that multiple KCFs are deployed,
-in turn, to address a target's scale change and dynamic maneuvers
-while preserving the overall execution time very fast, i.e., $\ge$ 300
-fps. The efficient nature of KCF computation results in a
-small-footprint, executable. Such a fast execution will facilitate to
-deploy the proposed algorithm on any embedded systems.
+In this paper, we extend the KCF in that three KCFs are deployed, in
+turn, to address a target's scale change and dynamic maneuvers while
+preserving the overall execution time very fast, i.e., $\ge$ 300
+fps. The efficient nature of the KCF computation results in a
+small-footprint, executable. Our design principle is, if we could
+deploy these KCFs in an efficient way, that the proposed algorithm
+could achieve a high, run-time performance while effectively
+addressing the scale variation and dynamic maneuvers of a target.
 

### 2017-05-03 bmvc_review.tex
Intermediate editing.

@@
 is deployed on a low-end, embedded system.\footnote{We empirically
-  come up with this computation about an 1/10th scale down of
-  computational resources from a typical PC to an embedded system.}
+  found this computation reasonable -- the computation about an 1/10th
+  scale down of computational resources from a typical PC to an
+  embedded system.}
 
@@
 \includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
-\caption{Examples of tracking results by the proposed method on the
-  ``UAV123'' dataset. This ``UAV123'' dataset is challenging for
-  object tracking as a target's scale is changed drastically with a
-  few frames.}
+\caption{Examples of tracking results (yellow rectangles) by the
+  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
+  is challenging for object tracking as a target's scale is changed
+  drastically in a few frames.}
 \label{ResultsIntroduction}
@@
 run-time performance. Figure \ref{fig:Filters} shows examples of the
-ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
+ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$. Figure
+\ref{Workflows} illustrates the work-flow of the {\it E}nKCF.
 
@@
 \end{tabular}
-\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker (a). It is slightly modified to handle extreme ego-motion
-and we call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
+\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker
+  (a). It is slightly modified to handle extreme ego-motion and we
+  call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
 \label{Workflows}
 \end{figure}
-The contributions of this study are as follows.
-\begin{itemize}
-\item \textbf{Novel Single-Target Tracking in a Very High-Speed ($\geq300$ fps) } Our
-  algorithm, {\it E}nKCF, deploys an ensemble of KCF in turn to more
-  efficiently address the scale variance and the dynamic maneuver of a
-  target while preserving run-time performance as high as possible. To
-  minimize any potential performance gap from transiting one KCF to
-  another, we use a Bayes filter. The workflow of the  {\it E}nKCF can
-  be visualized in fig.~\ref{Workflows}.
-The proposed tracker is tested on UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}} and OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
-  datasets.
 
-\item \textbf{Slight Modification of the proposed {\it E}nKCF for
-  Handling Large Motion} Our second algorithm, {\it E}nKCF2 leverages
-  the flexibility of the ensemble of KCFs approach we propose. The
-  original {\it E}nKCF is slightly modified to track in low frame rate
-  videos ($10$fps) dominated by large ego-motion. We do not integrate
-  the particle filter in {\it E}nKCF2 as we test it on a temporally
-  down-sampled UAV123 dataset (UAV123$\_$10fps) including sequences
-  with large ego-motion on a UAV platform. Particle Filter can be
-  deployed in case the camera motion is known. The run-time
-  performance decreases to $150$ fps, however, ratio of the video
-  frame rate and run-time performance is similar to {\it E}nKCF. The
-  proposed framework can be seen in fig.~\ref{Workflows}.
-\end{itemize}
+The contribution of this study is a novel, single-target tracking
+algorithm running a very high-speed, $\geq 300$ fps. In particular,
+the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCF, in
+turn, to more effectively address the scale variance and the dynamic
+maneuver of a target while preserving run-time performance as high as
+possible. To minimize any potential performance gap from transiting
+one KCF to another, we use a Bayes filter.
 
@@
 filter is prepared to focus on the target itself to estimate the right
-size or scale of the target. Fig.~\ref{fig:Filters} shows examples
+size or scale of the target. Figkure \ref{fig:Filters} shows examples
 of the region of interest (ROI) covered by each of three filters. We
@@
 higher speed.
+
 \begin{figure}[!h]
@@
 \includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
-\caption{The three filters denoted as \textit{target+small background} translation filter,
-  \textit{target-only} scale filter and \textit{target+large background} translation filters are
-  shown. Also, the hanning window and desired Gaussian response for
-  each filter is displayed.}
+\caption{Examples of three filters; the translation filter,
+  \textit{target+small background}, the scale filter,
+  \textit{target-only} and another translation filter,
+  \textit{target+large background}, and their Hanning window and
+  expected Gaussian response.}
 \label{fig:Filters}
@@
 \includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
-\caption{The video frame and the learned scale correlation filters are shown next to it. 
-The models in the top row correspond to the scale filter trained every frame whereas the bottom row shows the scale filter updated every $5$ frames. 
-Filters updated every five frame and every frame display very large correlation.}
+\caption{This figure shows that there is marginal difference among the
+  scale filters learned either at every frame or at every 5
+  frames. The sub-figures at the top row show the scale filters
+  trained from every frame and those at the bottom row show the scale
+  filters estimated every 5 frames.}
 \label{fig:Filters_Comparison}
@@
 noisy shape features due to its large search area. Figure
-\ref{Workflows} illustrates the work-flow of the proposed
-algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
-  E}nKCF. We do not have a separate pseudo-code for {\it E}nKCF2 as there are only two differences between 
-  {\it E}nKCF and {\it E}nKCF2. First, the {\it E}nKCF2 runs $R_{t}^{L}$ every frame
-to better tackle large ego-motion at low video frame rates. Second, we remove the particle filter in the {\it E}nKCF2 
-tracker due to large ego-motion. In the following section, we will briefly mention the theory
-behind the KCF.
+\ref{Workflows} illustrates the work-flow of the proposed algorithm
+and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. We do not
+have a separate pseudo-code for {\it E}nKCF2 as there are only two
+differences between {\it E}nKCF and {\it E}nKCF2. First, the {\it
+  E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
+ego-motion at low video frame rates. Second, we remove the particle
+filter in the {\it E}nKCF2 tracker due to large ego-motion. In the
+following section, we will briefly mention the theory behind the KCF.
 \begin{algorithm}[h]
 \small
-	\caption{The {\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
+	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
 	\begin{algorithmic}[1]
@@
 \end{algorithm}
-\begin{comment}
-{\it Burak: The KCF section doesn't fit the section before and
-  after. In addition, it's still too long.}
-
-{\it YoungWoo : What do you mean by this?
-Should we move it up before the EnKCF introduction?
-or Should we include more EnKCF-related text in it?
-I trimmed it further.
-I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}
-\end{comment}
 
@@
 
-\subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
+\subsection{Particle Filter for Smoothing Transition among KCFs} \label{sc:PF}
 As explained earlier, the {\it E}nKCF updates a target's translation at

### 2017-05-03 bmvc_review.tex
EnkCF2 figure removed

@@
 \bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
-(a) \\
-\bmvaHangBox{\includegraphics[width=10.0cm]{./figures/Workflow_EnKCF2+PF.pdf}}\\
-(b)
+
 \end{tabular}
-\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker
-  (a). It is slightly modified to handle extreme ego-motion and we
-  call it the {\it E}nKCF2 tracker (b) running at $\geq100$fps.}
+\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker.}
 \label{Workflows}

### 2017-05-03 bmvc_review.tex
Final stretch.

@@
 \bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
-
 \end{tabular}
-\caption{The workflow of the proposed $\geq300$fps {\it E}nKCF tracker.}
+\caption{The workflow of {\it E}nKCF tracking algorithm.}
 \label{Workflows}
@@
 \centering
-\includegraphics[width=0.4\textwidth]{figures/Filters_Details.pdf}
+\includegraphics[width=0.6\textwidth]{figures/Filters_Details.pdf}
 \caption{Examples of three filters; the translation filter,
@@
 \begin{equation}
-k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
+k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
 \label{eq:GaussianCorrelationSingleChannel}
@@
 
-\textbf{Features Selections.} As each of three KCFs in the {\it E}nKCF
+\textbf{Features Selections} As each of three KCFs in the {\it E}nKCF
 has different goals to accomplish, we used different features for each
@@
 
-\textbf{Performance on UAV123 Dataset.}  We compared the performance
+\textbf{Performance on UAV123 Dataset} We compared the performance
 of the proposed tracking algorithm with those of the state-of-the-art
@@
 
-\textbf{Performance on OTB100 Dataset.}  We evaluated the performance
-of the {\it E}nKCF tracker on the OTB100 dataset. Figure
+\textbf{Performance on OTB100 Dataset} We evaluated the performance of
+the {\it E}nKCF tracker on the OTB100 dataset. Figure
 \ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
@@
 
-\textbf{Performance on UAV123$\_$10fps Dataset.} We test our
-slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
-UAV123$\_$10fps dataset. This dataset is down-sampled at $10$ fps
-version of the UAV123 dataset. The original dataset is already
-dominated by fast object motion and large ego-motion. With
-down-sampling, it becomes very challenging with object and ego-motion
-getting drastically larger. The performance of the proposed {\it
-  E}nKCF2 tracker and other already mentioned trackers can be seen in
-fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other
-high-speed correlation filter based trackers including KCF, DSST by
-about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On
+\textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight
+digression from the main idea -- the idea of deploying multiple KCFs
+to make a very fast and effective, single target tracking
+available. We found that, with a slight modification, the proposed
+method can effectively handle tracking of object in fast motion and in
+large camera motion.
+
+{\it Burak: What modification we made to change {\it E}nKCF to {\it E}nKCF2?}
+
+In particular, the UAV123 data has another version where the original
+dataset was temporally down-sampled at $10$ fps and makes the
+challenging original dataset, because of objects in fast motion and
+large ego-motion, more challenging. This is because the magnitude of
+those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
+compares the performance of the modified version of {\it E}nKCF and
+other tracking methods. Our tracker outperforms other high-speed
+correlation filter based trackers including KCF, DSST by about
+$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
 the other hand, it does decent job in scale estimation. It ranks as
-second in AUC while running about $150$ faster than the MUSTER tracker.
+second in AUC while running about $150$ faster than the MUSTER
+tracker.
 \begin{figure}[!h]
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123_10fps.pdf}}
-\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
+\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Precision_UAV123_10fps.pdf}}
+\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
 \end{tabular}

### 2017-05-03 bmvc_review.tex
Comment Answered
Another editing.

@@
 method can effectively handle tracking of object in fast motion and in
-large camera motion.
-
-{\it Burak: What modification we made to change {\it E}nKCF to {\it E}nKCF2?}
-
-In particular, the UAV123 data has another version where the original
-dataset was temporally down-sampled at $10$ fps and makes the
-challenging original dataset, because of objects in fast motion and
-large ego-motion, more challenging. This is because the magnitude of
-those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
+large camera motion. Specifically we modified {\it E}nKCF by running
+$R_{t}^{L}$ every frame and remove the particle filter instead. We
+tested this modified {\it E}nKCF with another vision of the UAV123 that
+the original dataset was temporally down-sampled at $10$ fps and makes
+the challenging original dataset, because of objects in fast motion
+and large ego-motion, more challenging. This is because the magnitude
+of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
 compares the performance of the modified version of {\it E}nKCF and

### 2017-05-03 bmvc_review.tex
Revised the body a bit.

@@
 Computer vision technologies are very attractive for practical
-applications on embedded systems. This is primarily because most of
-embedded systems already includes image acquisition pipeline and a
+applications deployed on embedded systems. This is primarily because
+most of embedded systems already have image acquisition pipeline and a
 tremendous amount of progresses on research has been made for many
@@
 and dynamic maneuver of the target over frames. In addition, we
-devised a Bayes filter for a smooth transition between individual
+developed a Bayes filter for a smooth transition between individual
 KCFs' executions. Experimental results showed that the performance of
-ours are 70.10\% for precision on 20 pixels and 53.00\% for success
-rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. In other
-words, these results showed that our method is better than existing
-ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
-average. Our implementation ran at 340 fps for OTB100 and at 416 fps
-for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
-(292 fps), DCF (457 fps) for UAV123.
+ours are 70.10\% for precision at 20 pixels and 53.00\% for success
+rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
+results showed that our method is better than existing ones over 5\%
+on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
+implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
+DCF (457 fps) for UAV123.
 \end{abstract}
@@
 running on any embedded or mobile platforms that doesn't require an
-offline training, and can run on an embedded system. In particular, we
+offline training, and can run on an embedded system. Specifically, we
 would like to make our algorithm 1) learn the appearance model of a
@@
 correlation filters running on each frame could reduce the run-time
-performance from 300 to 100 fps. A seemingly obvious way of addressing
-the scale change is to scan the region of interest (ROI) with
-templates in different dimensions based on pre-defined scale ratios to
-find the target
+performance from 300 to 100 fps. An intuitive way of addressing the
+scale change is to scan the region of interest (ROI) with templates in
+different dimensions based on pre-defined scale ratios to find the
+target
 \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
@@
 run-time performance. Figure \ref{fig:Filters} shows examples of the
-ROIs associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$. Figure
-\ref{Workflows} illustrates the work-flow of the {\it E}nKCF.
-
+region of interest (ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and
+$R_{s}$. Figure \ref{Workflows} illustrates the work-flow of the {\it
+  E}nKCF.
 \begin{figure}[!t]
@@
 \end{figure}
-
 The contribution of this study is a novel, single-target tracking
-algorithm running a very high-speed, $\geq 300$ fps. In particular,
+algorithm running in a very high-speed, $\geq 300$ fps. In particular,
 the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCF, in
@@
 
-The proposed algorithm, {\it E}nKCF, deploys three KCFs in turn: The
+The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
 first filter, $R_{t}^{S}$, focuses on learning the target area and its
@@
 size or scale of the target. Figkure \ref{fig:Filters} shows examples
-of the region of interest (ROI) covered by each of three filters. We
-believe that a filter for learning a target's translation should
-include its background. In addition, making the ROI for the scale
-filter, $R_{s}$, tighter reduces the size of the template for the
-element-wise multiplication, resulting in a scale estimation in a
-higher speed.
+of the ROI covered by each of three filters. We believe that a filter
+for learning a target's translation should include its background. In
+addition, making the ROI for the scale filter, $R_{s}$, tighter
+reduces the size of the template for the element-wise multiplication,
+resulting in a scale estimation in a higher speed.
 
@@
 After Henriques and his colleagues' presented impressive tracking
-results of KCF \cite{henriques2015high} on
-VOT15\footnote{\url{http://www.votchallenge.net/vot2015/}} challenge,
-many variation of KCF were investigated. In particular,
-\cite{ma2015long} and \cite{danelljan2014accurate} used a scale filter
-to learn the target area only whereas \cite{li2014scale,
-  bibi2015multi, tang2015multi} used a correlation filter learned on
-the target area and its surrounding background in different size to
-learn the optimal scale of the target. Our approach is particularly
-similar to that of \cite{ma2015long} in that more than one KCF is used
-to address the challenges of single target tracking. But ours is
-different from that of \cite{ma2015long} in that we do not use those
-multiple KCFs together at every frame, but alternatively at every
-three frame. The way our algorithm is alternating multiple KCFs in
-different goals intuitively makes sense in that the appearance of
-consecutive images does not change drastically. Although it varies
-based on the scene, learning a correlation filter a frame would not be
-much different from the one learned using the image few or $k$ frames
-later. By alternating three KCFs in turn, our algorithm runs as fast
-as or faster than the original KCF. 
+results of KCF \cite{henriques2015high} on VOT15
+challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
+variation of KCF were investigated. In particular, \cite{ma2015long}
+and \cite{danelljan2014accurate} used a scale filter to learn the
+target area only whereas \cite{li2014scale, bibi2015multi,
+  tang2015multi} used a correlation filter learned on the target area
+and its surrounding background in different size to learn the optimal
+scale of the target. Our approach is particularly similar to that of
+\cite{ma2015long} in that more than one KCF is used to address the
+challenges of single target tracking. But ours is different from that
+of \cite{ma2015long} in that we do not use those multiple KCFs
+together at every frame, but alternatively at every three frame. The
+way our algorithm is alternating multiple KCFs in different goals
+intuitively makes sense in that the appearance of consecutive images
+does not change drastically. Although it varies based on the scene,
+learning a correlation filter a frame would not be much different from
+the one learned using the image few or $k$ frames later. Figure
+\ref{fig:Filters_Comparison} shows examples supporting this
+observation.
 \begin{figure}[!h]
@@
 
-The order of running these three KCFs is important as each of these
-filters aims at addressing different challenges while preserving
-run-time performance as fast as possible. The \textit{target+large
-  background} translation filter, $R_{t}^{L}$, is intended to run
-right after the scale filter, $R_s$, runs which is applied at every
-$k=5$ frames. We run these two filters this way because we want to
-minimize any drifts that are likely to happen running only $R_{s}$. In
-addition, the filter, $R_{t}^{S}$, is applied to every other frames
-before $R_{S}$ and right after two consecutive frames running
-$R_{t}^{L}$. By doing so, we can integrate more discriminative shape
+{\it Burak: What we wrote here didn't match what you told me. Go over
+  the following paragraph and change the numbers correctly.}
+
+The order of running these three KCFs is important because each of
+these filters aims at addressing different challenges; The
+\textit{target+large background} translation filter, $R_{t}^{L}$, is
+applied to the $i$th image frame, another translation filter,
+$R_{t}^{S}$ is applied to the $i+1$th image frame, and then the scale
+filter, $R_{s}$ is applied to the $i+2$the image. This order repeats
+until the end of the image frames. The translation filter,
+$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
+runs which is applied at every other $i+2$ frames. We run these two
+filters this way because we want to minimize any drifts that are
+likely to happen running only $R_{s}$. In addition, the filter,
+$R_{t}^{S}$, is applied to every other frames before $R_{s}$ and right
+after two consecutive frames running $R_{t}^{L}$. By iterating this
+order of learning KCFs, we can integrate more discriminative shape
 features that can not be fully learned by $R_{t}^{L}$ as it contains
@@
 \ref{Workflows} illustrates the work-flow of the proposed algorithm
-and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. We do not
-have a separate pseudo-code for {\it E}nKCF2 as there are only two
-differences between {\it E}nKCF and {\it E}nKCF2. First, the {\it
-  E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
+and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
+
+{\it Burak: Remove this EnKCF2 part from the text and from the pseudo code.}
+
+We do not have a separate pseudo-code for {\it E}nKCF2 as there are
+only two differences between {\it E}nKCF and {\it E}nKCF2. First, the
+{\it E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
 ego-motion at low video frame rates. Second, we remove the particle

### 2017-05-03 bmvc_review.tex
Revised the body a bit.

@@
 %---------------------------------------------------------------------- 
-Running a computer vision algorithm would be economically and
-practically, very attractive for any mobile, unmanned robotic
-solutions on real-world applications. To make such pipelines more
-realistic, however, those algorithms should run faster with small
-footprint of computation resource consumption. To make an object
-tracking algorithm with these practical requirements available, we
-proposed an extension of KCF that essentially deploys three KCFs, in
-turn, to address the scale change and dynamic maneuvers of a
-target. The way we ran three KCFs in a harmonious way optimal in a
-sense that efficiently handled the scale change and effectively
-learned the translation of the target. However, by doing so, our
-algorithm may introduce any potential drifts. To prevent this from
-happening, we developed a Bayes filter, particle filter, to smooth the
-transition between three KCFs. In particular, the particle filter
-estimated the target's pixel coordinates using information about the
-target's motion observed over frames. We used two publicly available
-dataset to evaluate the performance of the proposed algorithm and
-found that the performance of ours are 70.10\% for precision on 20
-pixels and 53.00\% for success rate for OTB100 data, and 54.50\% and
-40.2\% for UAV123 data. On average our method outperformed the
-existing ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
+Running a computer vision algorithm on any existing embedded systems
+for real-world applications is economically and practically very
+attractive. To make such pipelines more plausible, however, those
+algorithms should run faster with small footprint of computation
+resource consumption. To make an object tracking algorithm with these
+practical requirements available, we proposed an extension of KCF that
+essentially deploys three KCFs, in turn, to address the scale change
+and dynamic maneuvers of a target. The way we ran three KCFs is
+optimal in a sense that efficiently handled the scale change and
+effectively learned the translation of the target. We also developed a
+Bayes filter, particle filter, to smooth the transition between three
+KCFs. In particular, the particle filter estimated the target's pixel
+coordinates using information about the target's motion observed over
+frames. We used two publicly available dataset to evaluate the
+performance of the proposed algorithm and found, on average, the
+performance of the proposed algorithm is better than those of the
+existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
 average. Our implementation ran at 340 fps for OTB100 and at 416 fps
@@
 (292 fps), DCF (457 fps) for UAV123.
+
+As future work, we investigates a way of re-initializing a target when
+the target is lost, due to occlusion, illumination change, drastic
+camera motion, etc.
 %--------------

### 2017-05-03 bmvc_review.tex
COmments Replied

@@
 \textit{target+large background} translation filter, $R_{t}^{L}$, is
-applied to the $i$th image frame, another translation filter,
-$R_{t}^{S}$ is applied to the $i+1$th image frame, and then the scale
-filter, $R_{s}$ is applied to the $i+2$the image. This order repeats
+applied to the $i$th and $i+1$th image frame, another translation filter,
+$R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image frame, and then the scale
+filter, $R_{s}$ is applied to the $i+4$the image. This order repeats
 until the end of the image frames. The translation filter,
@@
 \ref{Workflows} illustrates the work-flow of the proposed algorithm
-and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
-
-{\it Burak: Remove this EnKCF2 part from the text and from the pseudo code.}
-
-We do not have a separate pseudo-code for {\it E}nKCF2 as there are
-only two differences between {\it E}nKCF and {\it E}nKCF2. First, the
-{\it E}nKCF2 runs $R_{t}^{L}$ every frame to better tackle large
-ego-motion at low video frame rates. Second, we remove the particle
-filter in the {\it E}nKCF2 tracker due to large ego-motion. In the
+and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. In the
 following section, we will briefly mention the theory behind the KCF.

### 2017-05-03 bmvc_review.tex
revision.

@@
 
-{\it Burak: What we wrote here didn't match what you told me. Go over
-  the following paragraph and change the numbers correctly.}
-
 The order of running these three KCFs is important because each of
@@
 \textit{target+large background} translation filter, $R_{t}^{L}$, is
-applied to the $i$th and $i+1$th image frame, another translation filter,
-$R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image frame, and then the scale
-filter, $R_{s}$ is applied to the $i+4$the image. This order repeats
-until the end of the image frames. The translation filter,
-$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
-runs which is applied at every other $i+2$ frames. We run these two
-filters this way because we want to minimize any drifts that are
-likely to happen running only $R_{s}$. In addition, the filter,
-$R_{t}^{S}$, is applied to every other frames before $R_{s}$ and right
-after two consecutive frames running $R_{t}^{L}$. By iterating this
-order of learning KCFs, we can integrate more discriminative shape
-features that can not be fully learned by $R_{t}^{L}$ as it contains
-contribution of large background in the learned model. The filter,
-$R_{t}^{L}$, uses shape and color information together to recover from
-any potential drifts -- drifts could happen only looking the target's
-scale by the filter, $R_{s}$.
+applied to the $i$th and $i+1$th image frame, another translation
+filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image frame,
+and then the scale filter, $R_{s}$ is applied to the $i+4$the
+image. This order repeats until the end of the image frames. The
+translation filter, $R_{t}^{L}$, is intended to run right after the
+scale filter, $R_s$, runs which is applied at every other $i+4$
+frames. We run these filters in this way because we want to minimize
+any drifts that are likely to happen running only $R_{s}$. In
+addition, the filter, $R_{t}^{S}$, is applied to every other two
+frames before $R_{s}$ and right after two consecutive frames running
+$R_{t}^{L}$. By repeating this order of learning KCFs, we can
+integrate more discriminative shape features that cannot be learned by
+$R_{t}^{L}$ because it incorporates a large area about background in
+the learned model. The filter, $R_{t}^{L}$, uses shape and color
+information together to recover from any potential drifts -- drifts
+could happen only looking the target's scale by the filter, $R_{s}$.
 

### 2017-05-03 bmvc_review.tex
Final Changes

@@
 \centering
-\includegraphics[width=0.6\textwidth]{figures/Filters_Details.pdf}
+\includegraphics[width=0.45\textwidth]{figures/Filters_Details.pdf}
 \caption{Examples of three filters; the translation filter,
@@
 \begin{tabular}{ccc}
-\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_UAV123.pdf}}
-\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_UAV123.pdf}}
-\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Precision_OTB100.pdf}}
-\bmvaHangBox{\includegraphics[width=3.0cm]{./figures/Success_OTB100.pdf}}\\
+\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=2.8cm]{./figures/Precision_OTB100.eps}}
+\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_OTB100.eps}}\\
 \centering \footnotesize (a) Precision and Success rates for UAV123 \quad \quad \quad \quad \quad (b) Precision and Success rates for OTB100
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Precision_UAV123_10fps.pdf}}
-\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
+\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_UAV123_10fps.eps}}
+\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_UAV123_10fps.eps}}\\
 \end{tabular}

### 2017-05-03 bmvc_review.tex
Minor Update
Last stretch.

@@
 learning a correlation filter a frame would not be much different from
-the one learned using the image few or $k$ frames later. Figure
+the one learned using the image few or $k$ frames later. 
+\begin{comment}
+Figure
 \ref{fig:Filters_Comparison} shows examples supporting this
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figures/LearnedFilterComparison.pdf}
+\includegraphics[width=0.5\textwidth]{figures/LearnedFilterComparison.pdf}
 \caption{This figure shows that there is marginal difference among the
@@
 \end{figure}
-
+\end{comment}
 The order of running these three KCFs is important because each of
@@
 could happen only looking the target's scale by the filter, $R_{s}$.
-
+\begin{comment}
 In summary, the scale filter, $R_{s}$, is designed to directly handle
@@
 designed to addresses the drawback of $R_{t}^{L}$ that it may learn
-noisy shape features due to its large search area. Figure
-\ref{Workflows} illustrates the work-flow of the proposed algorithm
-and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. In the
-following section, we will briefly mention the theory behind the KCF.
+noisy shape features due to its large search area.
+\end{comment}
+Figure \ref{Workflows} illustrates the work-flow of the proposed
+ algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
+   E}nKCF. In the following section, we will briefly mention the
+ theory behind the KCF.
 \begin{algorithm}[h]
@@
 \subsection{Particle Filter for Smoothing Transition among KCFs} \label{sc:PF}
-As explained earlier, the {\it E}nKCF updates a target's translation at
-every other $k$ frames, particularly for estimating the target's
+As explained earlier, the {\it E}nKCF updates a target's translation
+at every other $k$ frames, particularly for estimating the target's
 scale. Although the strategy of updating every other $k$th frames will
@@
 confidence maps of {\it E}nKCF as observation to update the state. The
-weight of a particle is computed as:
-\begin{equation}
-w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
-\end{equation}
-where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
-$N$ denotes the size of the window as that of a confidence
-map. Alternatively one can also use the Euclidean distance of
-particles to the location of maximum response of the confidence
-map. This alternative, however, would result in drifts.
-
+weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
+\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$,  where $w_{p}$
+denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
+size of the window as that of a confidence map. Alternatively one can
+also use the Euclidean distance of particles to the location of
+maximum response of the confidence map. This alternative, however,
+would result in drifts.
+\begin{comment}
 We chooses some particles based on their importance to estimate the
@@
 from uniform initial distribution to keep variance high enough.
-
+\end{comment}
 %----------------------------------------------------------------------
@@
 
-\textbf{Performance on UAV123 Dataset} We compared the performance
-of the proposed tracking algorithm with those of the state-of-the-art
+\textbf{Performance on UAV123 Dataset} We compared the performance of
+the proposed tracking algorithm with those of the state-of-the-art
 high speed tracking algorithms in the \textit{Precision} and
@@
 MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
-\cite{zhang2012robust}.
-
-Figure \ref{fig:UAV123_OTB100_DATASET} shows the results on the UAV123
-dataset. {\it E}nKCF outperformed most of the high-speed tracking
-methods by $3\%$-$15\%$ at 20 pixels precision metric. Three
-algorithms, SAMF, DSST, and Struck did about 5\% better than ours in
-accuracy, but 10-20\% slower than ours. For the scale adaptation, {\it
-  E}nKCF did second best in terms of \textit{area under curve} (AUC)
-value for the success rate plot. It outperformed other tracking
-methods in high-speed by about $20\%$-$25\%$ in AUC metric. In
-addition, it performed even better than those algorithms that are
-slow, but a bit better in precision. For example, for AUC, {\it E}nKCF
-outperformed Struct and DSST by $5\%$ and $10\%$ while running at more
-than $10$ and $30$ times faster.
+\cite{zhang2012robust}. Figure \ref{fig:UAV123_OTB100_DATASET} shows
+the results on the UAV123 dataset. {\it E}nKCF outperformed most of
+the high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
+metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
+than ours in accuracy, but 10-20\% slower than ours. For the scale
+adaptation, {\it E}nKCF did second best in terms of \textit{area under
+  curve} (AUC) value for the success rate plot. It outperformed other
+tracking methods in high-speed by about $20\%$-$25\%$ in AUC
+metric. In addition, it performed even better than those algorithms
+that are slow, but a bit better in precision. For example, for AUC,
+{\it E}nKCF outperformed Struct and DSST by $5\%$ and $10\%$ while
+running at more than $10$ and $30$ times faster.
 
@@
 \end{tabular}
-\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the UAV123 (a) and OTB100 (b) datasets.}
+\caption{Comparison of the slightly, modified version of {\it E}nKCF
+  for the UAV123 (a) and OTB100 (b) datasets.}
 \label{fig:UAV123_OTB100_DATASET}

### 2017-05-10 bmvc_review.tex
Final Changes

@@
 			    \State // Model Update
+			    \State Update $R_{t}^{S}$ (Condition 3);
+			    \State Update $R_{t}^{L}$ (Condition 2);
+			     \If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
 				\State Update $R_{s}$ (Condition 1);
-			    \State Update $R_{t}^{L}$ (Condition 2);
-			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
-				\State Update $R_{t}^{S}$ (Condition 3);
 			     \EndIf		
@@
 \begin{tabular}{ccc}
-\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=2.8cm]{./figures/Precision_OTB100.eps}}
-\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_OTB100.eps}}\\
-\centering \footnotesize (a) Precision and Success rates for UAV123 \quad \quad \quad \quad \quad (b) Precision and Success rates for OTB100
+\bmvaHangBox{\includegraphics[width=4.80cm]{./figures/Precision_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_UAV123.eps}}
 \end{tabular}
-\caption{Comparison of the slightly, modified version of {\it E}nKCF
-  for the UAV123 (a) and OTB100 (b) datasets.}
+\caption{Comparison of {\it E}nKCF
+  for the UAV123 dataset.}
+\label{fig:UAV123_OTB100_DATASET}
+\end{figure}
+\begin{figure}[!h]
+\centering
+\begin{tabular}{ccc}
+\bmvaHangBox{\includegraphics[width=4.80cm]{./figures/Precision_OTB100.eps}}
+\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_OTB100.eps}}\\
+\end{tabular}
+\caption{Comparison of {\it E}nKCF
+  for the OTB100 dataset.}
 \label{fig:UAV123_OTB100_DATASET}
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_UAV123_10fps.eps}}
-\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_UAV123_10fps.eps}}\\
+\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Precision_UAV123_10fps.eps}}
+\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_UAV123_10fps.eps}}\\
 \end{tabular}

### 2017-05-23 bmvc_review.tex
Revised the introduction.

@@
 Computer vision technologies are very attractive for practical
-applications deployed on embedded systems. This is primarily because
-most of embedded systems already have image acquisition pipeline and a
-tremendous amount of progresses on research has been made for many
-areas in computer vision. However, to successfully deploy a computer
-vision algorithm on any existing embedded systems, a vision algorithm
-needs to satisfy, at least, two criteria: minimal, manual intervention
-after deployment and small footprint of consuming computational
-resources and on executable code, with the assumption of reasonably
-good performance. To this end, in this paper, we propose an ensemble
-of the kernelized correlation filters (KCF), we call {\it E}nKCF, for
-the problem of a single-target object tracking. In particular, we
-developed a committee of KCFs to specifically address the scale-change
-and dynamic maneuver of the target over frames. In addition, we
-developed a Bayes filter for a smooth transition between individual
-KCFs' executions. Experimental results showed that the performance of
-ours are 70.10\% for precision at 20 pixels and 53.00\% for success
-rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
-results showed that our method is better than existing ones over 5\%
-on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
-implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
-DCF (457 fps) for UAV123.
+applications running on embedded systems. This is primarily because
+most of embedded systems already come with an image acquisition
+pipeline, and a tremendous amount of progresses on research has been
+made for many areas in computer vision. However, to successfully
+deploy a computer vision algorithm on any existing embedded systems, a
+vision algorithm needs to satisfy, at least, two criteria with
+assumption of reasonably good performance: minimal, manual
+intervention after deployment and small footprint of consuming
+computational resources and on executable code. To develop a single,
+target tracking system in high accuracy and run-time performance, we
+propose an ensemble of the kernelized correlation filters (KCF), we
+call {\it E}nKCF. In particular, we developed a committee of KCFs to
+specifically address the scale-change and dynamic maneuver of the
+target over frames. To guarantee a high-speed, runtime performance, we
+deploy each of KCFs in turn. For a smooth transition between
+individual KCFs' executions, we developed a Bayes filter. Experimental
+results showed that the performance of ours are, on average, 70.10\%
+for precision at 20 pixels, 53.00\% for success rate for OTB100 data,
+and 54.50\% and 40.2\% for UAV123 data. These results showed that our
+method is better than existing ones over 5\% on precision on 20 pixels
+and 10-20\% on AUC on average. Moreover our implementation ran at 340
+fps for OTB100 and at 416 fps for UAV123 data that is faster than DCF
+(292 fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
 \end{abstract}
@@
 \section{Introduction}
-A recent proliferation of air/ground/water unmanned vehicle
-technologies has ever increased interests on deploying intelligent
-algorithms to any existing embedded and/or mobile platforms. Among
-those technologies, computer vision algorithms are getting more
-attentions primarily because payloads of those mobile platforms are
-limited to carry any other sensors than a lightweight or an array of
-monocular cameras. For example, instead of having just bare flight
-function with video recording, an unmanned air vehicle (UAV) equipped
-with an object or feature following functionality would make it more
-useful in the application of monitoring/surveillance/surveying on
-private properties/wild-life/crop, video recording on
-sports/movies/events, many others.
+A recent advancement of air/ground/water unmanned vehicle technologies
+has increased interests on deploying intelligent algorithms to
+existing embedded and mobile platforms. Among those technologies,
+computer vision algorithms are getting more attentions primarily
+because payloads of those mobile platforms are limited to carry other
+sensors than a lightweight or an array of monocular cameras. For
+example, instead of having just bare flight function with video
+recording, an unmanned air vehicle (UAV) equipped with an object or
+feature following functionality would make it more useful in the
+application of monitoring/surveillance/surveying on private
+properties/wild-life/crop, video recording on sports/movies/events,
+many others.
 
@@
 target on the fly and 2) run as fast on a typical desktop as up to
-$300$-$400$Hz so that it could run, at least, faster than 30Hz when it
-is deployed on a low-end, embedded system.\footnote{We empirically
-  found this computation reasonable -- the computation about an 1/10th
-  scale down of computational resources from a typical PC to an
-  embedded system.}
+$300$-$400$ fps so that it could run, at least, faster than 30 fps
+when it is deployed on a low-end, embedded system.\footnote{We
+  empirically found this computation useful and reasonable -- the
+  computation about an 1/10th scale down of computational resources
+  from a typical PC to an embedded system.}
 
@@
 problem as a regression problem in the frequency domain. This
-framework assumes that the target location is given at the very first
-image frame like other online tracking algorithms
+framework assumes that a target location is given at the beginning
+like other online tracking algorithms
 \cite{smeulders2014survey}. Given this positive example for the
@@
 correlation filter can be easily implemented and run very efficiently
-in an online fashion. In fact, a variant of the correlation filter,
-the kernelized correlation filter with multi-channel features
+on the fly. In fact, an extension of a linear correlation filter, the
+kernelized correlation filter with multi-channel features
 \cite{henriques2015high} showed impressive object tracking results and
-outperformed other state-of-the-art tracking algorithms, for example,
-in VOT15 challenge, in terms of run-time and tracking
-accuracy. However, a vanilla form of such an online tracker is prone
-to drift, and fails to track a target over a long period of time
-primarily \cite{henriques2015high} because of the dilemma of
-stability-plasticity in updating appearance model, where the
-appearance model will be overfitted to only the images used to train
-and a compromise on the frequency of updating the model is carefully
-implemented \cite{santner2010prost}. For example, a naive way of
-handling a scale change of a target by just having multiple
-correlation filters running on each frame could reduce the run-time
-performance from 300 to 100 fps. An intuitive way of addressing the
-scale change is to scan the region of interest (ROI) with templates in
-different dimensions based on pre-defined scale ratios to find the
-target
-\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. Due
-to the computational nature of correlation filter, however, this
-approach would merely increase the computational complexity because it
-has to run the correlation filter multiple times on each frame.
+outperformed other state-of-the-art tracking algorithms in terms of
+run-time and tracking accuracy. However, a vanilla form of such an
+online tracker is prone to drift, and fails to track a target over a
+long period of time primarily \cite{henriques2015high}. This is
+primarily due to the dilemma of stability-plasticity in updating
+appearance model, where the appearance model will be overfitted to
+only the images used to train, unless a compromise on the frequency of
+updating the model is carefully implemented
+\cite{santner2010prost}. For example, one may handle a target's scale
+variation by just concatenating multiple correlation filters including
+KCF and running them on each frame. Alternatively one could think of
+scanning the region of interest (ROI) with a list of templates in
+predefined scale ratios to find the target in appropriate scale
+\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
+these approaches will drastically reduce run-time performance because
+they are proposed to run multiple of a correlation filter including
+KCF on each frame.
 
@@
 target's translation first and estimate a correct scale afterward. In
-particular, they use the MOSSE tracker to estimate a target's
-translation. And then they attemped to update the scale of the target
-a way where the confidence map is used to determine the scale change
-between successive frames. This is based on an assumption that the
-scale of a target wouldn't change much over two consecutive
-frames. Similarly \cite{ma2015long} used two KCFs to learn the
-translation and scale of a target separately. To be more specific, a
-KCF is used to learn the translation of the target and its
+particular, Zhang and his colleagues use the MOSSE tracker to estimate
+a target's translation. And then they attemped to update the scale of
+the target by further analyzing image, sub-regions with high
+confidence to figure out the scale of a target. This is based on an
+assumption that the scale of a target would not change much over two
+consecutive frames. Similarly \cite{ma2015long} used two KCFs to learn
+the translation and scale of a target separately. To be more specific,
+a KCF is used to learn the translation of the target and its
 background. Given this, another KCF is used to learn the target area
@@
 single target tracking: scale and translation, but in a more efficient
-way. To be more specific, we use an ensemble of KCFs in turn, instead
-of running them all together on every frame. In particular, we deploy
-three KCF in turn: \textit{target}+\textit{small background}
-translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
-($R_{s}$) and \textit{target}+\textit{large background} translation
-filter ($R_{t}^{L}$). By doing so, we could still address the scale
-change and estimate target's motion efficiently while increasing
-run-time performance. Figure \ref{fig:Filters} shows examples of the
-region of interest (ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and
-$R_{s}$. Figure \ref{Workflows} illustrates the work-flow of the {\it
-  E}nKCF.
+way. In particular, we use an ensemble of KCFs in turn, instead of
+running them all together on every frame. We deploy three KCF in turn:
+\textit{target}+\textit{small background} translation filter
+($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+\textit{target}+\textit{large background} translation filter
+($R_{t}^{L}$). By doing so, we could still address the scale change
+and estimate target's motion efficiently while maintaining or
+increasing run-time performance. Figure \ref{fig:Filters} shows
+examples of the region of interest (ROI) associated with $R_{t}^{S}$,
+$R_{t}^{L}$, and $R_{s}$. Figure \ref{Workflows} illustrates the
+work-flow of the {\it E}nKCF.
 \begin{figure}[!t]

### 2017-05-24 bmvc_review.tex
Revised Section 2.

@@
 %---------------------------------------------------------------------- 
-In this paper, we extend the KCF in that three KCFs are deployed, in
-turn, to address a target's scale change and dynamic maneuvers while
-preserving the overall execution time very fast, i.e., $\ge$ 300
-fps. The efficient nature of the KCF computation results in a
-small-footprint, executable. Our design principle is, if we could
-deploy these KCFs in an efficient way, that the proposed algorithm
-could achieve a high, run-time performance while effectively
-addressing the scale variation and dynamic maneuvers of a target.
+In this paper, we propose a novel way of utilizing multiple of the KCF
+\cite{henriques2015high} to effectively handle scale variations and
+dynamic maneuvers of a target. To maintain or improve the run-time
+performance of the original KCF (e.g., $\ge$ 300), we deploy three
+KCFs in turn, not on the same image frame together. Each of these KCFs
+is designed to address specific challenges, i.e., scale and
+translation. By alternating their deployments, our algorithm will
+improve the performance of the original KCF while preserving the
+efficient nature and small-footprint of the KCF computation.
 
@@
 last filter, $R_{t}^{L}$, focuses on the target area and its
-background twice bigger than that of the first filter, $R_{t}^{S}$,
-\textit{target}+\textit{large background}. We set up {\it E}nKCF in
-this way because we believe a correlation filter for learning a
-target's translation should include its background to better
-discriminate the target from its background and another correlation
-filter is prepared to focus on the target itself to estimate the right
-size or scale of the target. Figkure \ref{fig:Filters} shows examples
-of the ROI covered by each of three filters. We believe that a filter
-for learning a target's translation should include its background. In
-addition, making the ROI for the scale filter, $R_{s}$, tighter
-reduces the size of the template for the element-wise multiplication,
-resulting in a scale estimation in a higher speed.
+background, at least twice, bigger than that of the first filter,
+$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
+  E}nKCF in this way because, we believe, a correlation filter for
+learning a target's translation should include its background to
+better discriminate the target from its background, and another
+correlation filter should focus on the target itself to estimate the
+right size or scale of the target. Figkure \ref{fig:Filters} shows
+examples of the ROI covered by each of three filters.
 
@@
   \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
+  expected Gaussian response. Instead of using a single, correlation
+  filter for estimating change of a target's scale and translation, it
+  would be better to use more than one correlation filter for better
+  estimating change of scale and translation individually.}
 \label{fig:Filters}
@@
 
-After Henriques and his colleagues' presented impressive tracking
+Since Henriques and his colleagues' presented impressive tracking
 results of KCF \cite{henriques2015high} on VOT15
 challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
-variation of KCF were investigated. In particular, \cite{ma2015long}
-and \cite{danelljan2014accurate} used a scale filter to learn the
-target area only whereas \cite{li2014scale, bibi2015multi,
-  tang2015multi} used a correlation filter learned on the target area
-and its surrounding background in different size to learn the optimal
-scale of the target. Our approach is particularly similar to that of
-\cite{ma2015long} in that more than one KCF is used to address the
-challenges of single target tracking. But ours is different from that
-of \cite{ma2015long} in that we do not use those multiple KCFs
-together at every frame, but alternatively at every three frame. The
-way our algorithm is alternating multiple KCFs in different goals
-intuitively makes sense in that the appearance of consecutive images
-does not change drastically. Although it varies based on the scene,
-learning a correlation filter a frame would not be much different from
-the one learned using the image few or $k$ frames later. 
-\begin{comment}
-Figure
-\ref{fig:Filters_Comparison} shows examples supporting this
-observation.
+variation of KCF were investigated. For example, \cite{ma2015long} and
+\cite{danelljan2014accurate} used a scale filter to learn the target
+area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
+used a correlation filter learned on the target area and its
+surrounding background in different size to learn the optimal scale of
+the target. Our approach is similar to that of \cite{ma2015long} in
+that more than one KCF is used to address the challenges of single
+target tracking. But ours is different from their approach because we
+do not use those multiple KCFs together at every frame, but
+alternatively at every $k$ frame (e.g., $k=3$). It intuitively makes
+sense to alternatively use multiple KCFs with different purposes
+because the appearance of a target does not change drastically over
+consecutive image frames. For most case, even it looks the appearance
+changes, learning a correlation filter over consecutive frames would
+not be much different from the one learned using the image few or $k$
+frames later. Figure \ref{fig:Filters_Comparison} shows examples
+supporting this observation.
+
 \begin{figure}[!h]
@@
 \end{figure}
-\end{comment}
+
 The order of running these three KCFs is important because each of
@@
 integrate more discriminative shape features that cannot be learned by
-$R_{t}^{L}$ because it incorporates a large area about background in
-the learned model. The filter, $R_{t}^{L}$, uses shape and color
-information together to recover from any potential drifts -- drifts
-could happen only looking the target's scale by the filter, $R_{s}$.
-\begin{comment}
+$R_{t}^{L}$. This is because it incorporates a large area about
+background in the learned model. The filter, $R_{t}^{L}$, uses shape
+and color information together to recover from any potential drifts --
+drifts could happen only looking the target's scale by the filter,
+$R_{s}$.
+
 In summary, the scale filter, $R_{s}$, is designed to directly handle
@@
 designed to addresses the drawback of $R_{t}^{L}$ that it may learn
-noisy shape features due to its large search area.
-\end{comment}
-Figure \ref{Workflows} illustrates the work-flow of the proposed
- algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
-   E}nKCF. In the following section, we will briefly mention the
- theory behind the KCF.
+noisy shape features due to its large search area. Figure
+\ref{Workflows} illustrates the work-flow of the proposed algorithm
+and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. In the
+following section, we will briefly mention the theory behind the KCF.
+
 \begin{algorithm}[h]

### 2017-05-24 bmvc_review.tex
Revised the introduction a bit.

@@
 $300$-$400$ fps so that it could run, at least, faster than 30 fps
-when it is deployed on a low-end, embedded system.\footnote{We
-  empirically found this computation useful and reasonable -- the
-  computation about an 1/10th scale down of computational resources
-  from a typical PC to an embedded system.}
+when it is deployed on a low-end, embedded system.\footnote{In
+  general, it would be very hard to compare an Intel or AMD processor
+  running on a desktop or a laptop with that, e.g., ARM, of a
+  single-board, embedded system in terms of run-time performance of a
+  computer vision algorithm. This is primarily because of difference
+  in their architectures. But we empirically found this computation
+  useful and reasonable based on specific processors, e.g., Intel's i7
+  quad-core vs ARM Cortex A53 -- the computation about an 1/10th scale
+  down of computational resources from a typical PC to an embedded
+  system.}
 

### 2017-05-26 bmvc_review.tex
Completed to revise the draft.

@@
 particular, Zhang and his colleagues use the MOSSE tracker to estimate
-a target's translation. And then they attemped to update the scale of
+a target's translation. And then they attempted to update the scale of
 the target by further analyzing image, sub-regions with high
@@
 \end{tabular}
-\caption{The workflow of {\it E}nKCF tracking algorithm.}
+\caption{The work-flow of {\it E}nKCF tracking algorithm.}
 \label{Workflows}
@@
 correlation filter should focus on the target itself to estimate the
-right size or scale of the target. Figkure \ref{fig:Filters} shows
+right size or scale of the target. Figure \ref{fig:Filters} shows
 examples of the ROI covered by each of three filters.
@@
 \ref{Workflows} illustrates the work-flow of the proposed algorithm
-and alg.\ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF. In the
-following section, we will briefly mention the theory behind the KCF.
+and the algorithm \ref{alg:MKCF} shows the pseudo-code of {\it
+  E}nKCF. In the following section, we will briefly describe the
+features of the KCF related to this work.
 
@@
 The Kernelized Correlation Filter is a well, known single target
-tracking method and thetheory and its workflowhas been detailed in
+tracking method and the theory and its work flow has been detailed in
 other papers already
 \cite{henriques2012exploiting,henriques2015high}. This section briefly
-goes over the parts of the KCF relevantto thisstudy. Its
-computational efficiency arises from its use of the discrete Fourier
-transform of the circulant matrix and frequency domain. The KCF
-essentially solves the problem of a regression in the form of the
-regularized ridge regression as:
+goes over the parts of the KCF relevant to this study. Its
+computational efficiency is derived from the fact that the correlation
+filter framework represents training examples as the circulant matrix
+and the circulant matrix can be represented as a diagonal matrix by
+the discrete Fourier transform.
+
+{\it Burak: The above paragraph didn't connect to the following
+  paragraphs. You'll have to finish up the sentence about a
+  correlation filter's, not KCF yet, computational efficiency and then
+  continue to explain how this a regularized correlation filter will
+  be transformed into KCF w/ the same computational complexity.}
+
+The KCF essentially solves the problem of a regression in the form of
+the regularized ridge regression as:
 \begin{equation}
@@
 result in an optimal run-time performance, this may lead any potential
-drifts at the later frames. To prevent such potential mishaps from
-happening, we developed a Bayes filter that incorporates a target's
-motion to smooth any outputs from the {\it E}nKCF. In particular, we
-use a particle filter to estimate the target's image coordinate based
-on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
-Carlo method that uses a finite number of particles or samples to
-estimate the posterior probability density of a state of the system
-\cite{thrun2005probabilistic}. In this study, the state represents a
-target's pixel coordinates and its motion. In particular, the state of
-the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
-v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
-target's centroid, $v_x$ and $v_y$ are the estimated velocity along
-the $x$-axis and $y$-axis. The particle filter predicts, using a
+drifts at the later frames. To prevent such potential drifts, we
+developed a Bayes filter that incorporates a target's motion to smooth
+any intermediate outputs from individual KCFs of the {\it E}nKCF. In
+particular, we use a particle filter to estimate the target's image
+coordinate based on the {\it E}nKCF's outputs. A particle filter is a
+sequential Monte Carlo method that uses a finite number of particles
+or samples to estimate the posterior probability density of a state of
+the system \cite{thrun2005probabilistic}. In this study, the state
+represents a target's pixel coordinates and its motion. In particular,
+the state of the particle filter, $X_t$, is represented by $\lbrace x,
+y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
+of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
+along the $x$-axis and $y$-axis. The particle filter predicts, using a
 constant velocity motion model, a target's state by generating a
@@
 also use the Euclidean distance of particles to the location of
-maximum response of the confidence map. This alternative, however,
-would result in drifts.
+maximum response of the confidence map. 
 \begin{comment}
@@
 \end{comment}
+
 %----------------------------------------------------------------------
@@
 %---------------------------------------------------------------------- 
-To verify the usefulness of our algorithm, we choose two public,
-available datasets:
+To evaluate the performance of the proposed algorithm, we choose two
+public, available datasets:
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
@@
 The OTB100 dataset is comprised of the videos about 100 objects
-whereas UAV123 dataset contains aerial footage of 123 objects. We aims
-at developing an object tracking algorithm that ``efficiently'' runs
-in ``high speed,'' $\ge 300$ fps. Given this goal, we believe that the
-UAV123 video data is a better fit in evaluating the performance of the
-proposed algorithm. This is because there are many challenging scenes,
-e.g., abrupt scale/illumination changes as all the targets were
-recorded from bird-eye view. Although we are primarily interested in
-developing an algorithm for mobile, embedded robotic applications, it
-is important to compare the performance of the proposed algorithm with
-those of the state-of-the-art in nominal dataset for comparison. To
-this end, we chose the OTB100 data that contains the videos recorded
-from smart phones and typical cameras in perspective view. Finally,
-the {\it E}nKCF2 is tested on temporally down-sampled version of the
-UAV123 dataset which is named UAV123$\_$10fps dataset.
+whereas UAV123 dataset contains aerial footages of 123 objects. We
+aims at developing an object tracking algorithm that ``efficiently''
+runs on an embedded system in ``high speed,'' $\ge 300$ fps, e.g.,
+running our tracking algorithms on a drone. Given this, we believe
+that the UAV123 video data is a better fit in evaluating the
+performance of the proposed algorithm than any other existing tracking
+datasets. This is because there are many challenging scenes, e.g.,
+abrupt scale/illumination changes. Although we are primarily
+interested in developing an algorithm for mobile, embedded robotic
+applications, it is important to compare the performance of the
+proposed algorithm with those of the state-of-the-art in nominal
+dataset for comparison. To this end, we chose the OTB100 data that
+contains the videos recorded from smart phones and typical cameras in
+perspective view. Finally, the {\it E}nKCF2 is tested on temporally
+down-sampled version of the UAV123 dataset, we call
+``UAV123$\_$10fps'' dataset.
+
+{\it Burak: You need to explain why it is useful or meaningful to
+  evaluate our algorithm w/ a down-sampled version of the UAV123
+  dataset.}
 
@@
 \textbf{Performance on UAV123 Dataset} We compared the performance of
-the proposed tracking algorithm with those of the state-of-the-art
-high speed tracking algorithms in the \textit{Precision} and
-\textit{Success\:Rate} metrics. In precision, we rank the trackers
+the proposed algorithm with those of the state-of-the-art high speed
+tracking algorithms by the \textit{Precision} and
+\textit{Success\:Rate} metrics. For the precision, we rank the trackers
 based on the precision numbers at 20 pixels whereas in the success
@@
 MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
-\cite{zhang2012robust}. Figure \ref{fig:UAV123_OTB100_DATASET} shows
-the results on the UAV123 dataset. {\it E}nKCF outperformed most of
-the high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
+\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
+results on the UAV123 dataset. {\it E}nKCF outperformed most of the
+high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
 metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
@@
 
-\textbf{Performance on OTB100 Dataset} We evaluated the performance of
-the {\it E}nKCF tracker on the OTB100 dataset. Figure
-\ref{fig:UAV123_OTB100_DATASET} shows the results on the OTB100
-dataset. Like in UAV123 dataset, we observed a similar performance. In
-particular, {\it E}nKCF showed a good performance for handling the
-scale changes. It was the third best and the second fastest tracking
-algorithm. For the precision metric, {\it E}nKCF performed slightly
-better than most of tracking algorithms in high-speed
-trackers. Interestingly, it outperformed another correlation filter
-based tracker, DSST, but performing $5\%$ behind of another low-speed
-scale adaptive SAMF tracker.
+\textbf{Performance on OTB100 Dataset} Figure \ref{fig:OTB100_DATASET}
+shows the results on the OTB100 dataset. Same as with UAV123 dataset,
+we observed a similar performance. In particular, {\it E}nKCF showed a
+good performance for handling the scale changes. It was the third best
+and the second fastest tracking algorithm. For the precision metric,
+{\it E}nKCF performed slightly better than most of tracking algorithms
+in high-speed trackers. Interestingly, it outperformed another
+correlation filter based tracker, DSST, but performing $5\%$ behind of
+another low-speed scale adaptive SAMF tracker.
 \begin{figure}[!h]
@@
   for the UAV123 dataset.}
-\label{fig:UAV123_OTB100_DATASET}
+\label{fig:UAV123_DATASET}
 \end{figure}
@@
   for the OTB100 dataset.}
-\label{fig:UAV123_OTB100_DATASET}
+\label{fig:OTB100_DATASET}
 \end{figure}
+
+{\it Burak: I don't think I agreed to put the following part as a part
+  of our submission.}
 
@@
 \caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates.
-This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
+This dataset consists of temporally down-sampled $123$ video sequences captured from a micro UAV.}
 \label{fig:UAV123_10fpsDATASET}

### 2017-05-30 bmvc_review.tex
Comments Replied

@@
 tracking method and the theory and its work flow has been detailed in
-other papers already
-\cite{henriques2012exploiting,henriques2015high}. This section briefly
+other papers already \cite{henriques2012exploiting,henriques2015high}. This section briefly
 goes over the parts of the KCF relevant to this study. Its
-computational efficiency is derived from the fact that the correlation
-filter framework represents training examples as the circulant matrix
-and the circulant matrix can be represented as a diagonal matrix by
-the discrete Fourier transform.
+computational efficiency is derived from the correlation
+filter framework representing training examples as a circulant matrix. To reduce complexity, the
+circulant matrix can be diagonalized by Discrete Fourier Transform.  This way, off-diagonal elements become
+zero whereas the diagonal elements represent the eigenvalues of the circulant matrix. The egienvalues are equal
+to the DFT transformation of the base sample ($x$) elements. The Kernelized Correlation Filter, on the other hand,
+applies a kernel to $x$ to transform to a more discriminative domain. The circulant matrix is then formed by applying
+cylic shifts on the kernelized $x$. Such kernelization operation does not introduce additional complexity to the baseline
+correlation filter framework.
 
@@
   be transformed into KCF w/ the same computational complexity.}
+
+{\it YoungWoo : I edited it based on your comment}
 
@@
 perspective view. Finally, the {\it E}nKCF2 is tested on temporally
-down-sampled version of the UAV123 dataset, we call
-``UAV123$\_$10fps'' dataset.
+down-sampled version of the UAV123 dataset, called UAV123$\_$10fps dataset. 
+This way, by modifying the proposed {\it E}nKCF framework slightly we can tackle scenarios dominated by extreme camera and object
+motion as we run multiple correlation filter at each frame. One can also perform such modifications based on the hardware specifications. 
+A more sophisticated hardware can be more friendly to apply multiple correlation filter ({\it E}nKCF2) at one frame
+whereas the ones on the low end can only accommodate a single correlation filter at each frame ({\it E}nKCF).
 
@@
   dataset.}
+
+{\it YoungWoo: I edited the preceding paragraph based on your comment.}
 

### 2017-05-30 bmvc_review.tex
Algorithm Place Modified
Algorithm Cleaned - Used a Better Format

@@
 \usepackage{mathtools} % mathtools builds on and extends amsmath package
-\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
+% \usepackage{algorithm}		% http://ctan.org/pkg/algorithms
 \usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
 \usepackage{comment, url}
+\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
+
 %% Enter your paper number here for the review copy
@@
 
+\begin{algorithm}[h]
+\small
+\DontPrintSemicolon
+\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, scale filter frequency $n = 5$,}
+\KwOut{	\uIf{$fc\:\%\:n=0$ (Condition 1)}
+			{
+				Estimated Target State $(x_{t},y_{t},s_{t})$,
+				Scale filter (\textit{target-only}) model $R_{s}$.
+			}			  
+			 \ElseIf{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$ (Condition 2)}
+			 {
+				Estimated Target State $(x_{t},y_{t},s_{t})$,
+			  	Large Area Translation Filter model $R_{t}^{L}$.
+			}			 
+			 \Else (\textit{Condition 3})
+			{			 
+				 Estimated Target State $(x_{t},y_{t},s_{t})$,
+				Small Area Translation Filter model $R_{t}^{S}$.				
+			}	
+		}
+\SetKwBlock{Begin}{function}{end function}
+\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
+{
+ 	// \textit{Translation Estimation - Particle Filter} \\
+	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $(x_{t},y_{t},s_{t-1})$ \\
+     // \textit{Translation Estimation - Correlation Filter} \\
+	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position ($x_{t}$,$y_{t}$),\\
+	// \textit{Scale Estimation - Correlation Filter}\\
+	Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$ (Condition 1),\\ 
+	Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$,\\
+	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($s_{t}$=$s_{t-1}$)\\
+	// \textit{Update Translation - Particle Filter}\\
+	Do Importance Re-sampling (if necessary) and compute the 
+	mean of posterior pdf $(x_{t},y_{t})$\\
+	// \textit{Model Update}\\
+	Update $R_{t}^{S}$ (Condition 3),\\
+	Update $R_{t}^{L}$ (Condition 2),\\
+	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
+		Update $R_{s}$ (Condition 1)}
+  \label{endfor}
+  \Return{($x_{t},y_{t},s_{t}$)}
+}
+\caption{{\it E}nKCF Tracking Algorithm}\label{costalgorithm}
+\end{algorithm}
+
+%\begin{algorithm}[h]
+%\small
+%	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
+%	\begin{algorithmic}[1]
+%	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
+%	\State \textbf{Output} : 
+%				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
+%						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
+%						Scale filter (\textit{target-only}) model $R_{s}$.
+%			     \EndIf
+%				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
+%						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
+%						Large Area Translation Filter model $R_{t}^{L}$.
+%				\EndIf
+%				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
+%						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
+%						Small Area Translation Filter model $R_{t}^{S}$.
+%				\EndIf
+%	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
+%				\State // Translation Estimation
+%				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
+%				\State // Translation Estimation
+%				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
+%				and estimate translation ($x_{t}$,$y_{t}$),
+%				\State Skip translation estimation for $R_{s}$ (Condition 1);
+%				\State // Scale Estimation
+%			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
+%				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
+%		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($s_{t}$=$s_{t-1}$),
+%				\State // Update Translation
+%				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
+%			    \State // Model Update
+%			    \State Update $R_{t}^{S}$ (Condition 3);
+%			    \State Update $R_{t}^{L}$ (Condition 2);
+%			     \If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
+%				\State Update $R_{s}$ (Condition 1);
+%			     \EndIf		
+%	\EndProcedure	
+%	\end{algorithmic}
+%\end{algorithm}
+
 The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The
@@
 features of the KCF related to this work.
-
-\begin{algorithm}[h]
-\small
-	\caption{{\it E}nKCF Tracking Algorithm.}\label{alg:MKCF}
-	\begin{algorithmic}[1]
-	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
-	\State \textbf{Output} : 
-				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
-						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
-						Scale filter (\textit{target-only}) model $R_{s}$.
-			     \EndIf
-				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
-						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
-						Large Area Translation Filter model $R_{t}^{L}$.
-				\EndIf
-				\If{$fc\:\%\:n=3\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
-						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
-						Small Area Translation Filter model $R_{t}^{S}$.
-				\EndIf
-	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
-				\State // Translation Estimation
-				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
-				\State // Translation Estimation
-				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
-				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
-				\State Skip translation estimation for $R_{s}$ (Condition 1);
-				\State // Scale Estimation
-			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
-				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
-		        \State Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ (Condition 1, and 2),
-				\State // Update Translation
-				\State Perform Importance Re-sampling (if necessary) for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
-			    \State // Model Update
-			    \State Update $R_{t}^{S}$ (Condition 3);
-			    \State Update $R_{t}^{L}$ (Condition 2);
-			     \If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
-				\State Update $R_{s}$ (Condition 1);
-			     \EndIf		
-	\EndProcedure	
-	\end{algorithmic}
-\end{algorithm}
 

### 2017-05-30 bmvc_review.tex
Algorithm Updated Further

--- 2017-05-30 bmvc_review.tex
@@
 
+\begin{algorithm}[h]
+\small
+\DontPrintSemicolon
+\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, scale filter frequency $n = 5$,}
+\KwOut{	\uIf{$fc\:\%\:n=0$ (Condition 1)}
+			{
+				Estimated Target State $(x_{t},y_{t},s_{t})$,
+				Scale filter (\textit{target-only}) model $R_{s}$.
+			}			  
+			 \ElseIf{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$ (Condition 2)}
+			 {
+				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
+			  	Large Area Translation Filter model $R_{t}^{L}$.
+			}			 
+			 \Else (\textit{Condition 3})
+			{			 
+				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
+				Small Area Translation Filter model $R_{t}^{S}$.				
+			}	
+		}
+\SetKwBlock{Begin}{function}{end function}
+\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
+{
+ 	// \textit{Translation Estimation - Particle Filter} \\
+	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
+     // \textit{Translation Estimation - Correlation Filter} \\
+	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{max(y_{R_{t}})}$\\
+	// \textit{Scale Estimation - Correlation Filter}\\
+	Scale pool for $R_{s}$ : $S = \lbrace1.05,1.0,1/1.05\rbrace$,\\
+	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{argmax}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
+	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$)\\
+	// \textit{Update Translation - Particle Filter}\\
+	Do Importance Re-sampling (if necessary) and compute the 
+	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
+	// \textit{Model Update}\\
+	Update $R_{t}^{S}$,\\
+	Update $R_{t}^{L}$\\
+	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
+		Update $R_{s}$ (Condition 1)}
+  \label{endfor}
+  \Return{($x_{t},y_{t},s_{t}$)}
+}
+\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
+\end{algorithm}
+
 The proposed algorithm, {\it E}nKCF, learns three KCFs in turn: The

### 2017-05-30 bmvc_review.tex
Figures 3 and 4 Updated

@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/Filters_Details.pdf}
+\includegraphics[width=0.75\textwidth]{figures/Filters_Details.pdf}
 \caption{Examples of three filters; the translation filter,
@@
   \textit{target+large background}, and their Hanning window and
-  expected Gaussian response. Instead of using a single, correlation
-  filter for estimating change of a target's scale and translation, it
-  would be better to use more than one correlation filter for better
-  estimating change of scale and translation individually.}
+  expected Gaussian response.}
 \label{fig:Filters}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{figures/LearnedFilterComparison.pdf}
+\includegraphics[width=1\textwidth]{figures/LearnedFiltersComparison2.pdf}
 \caption{This figure shows that there is marginal difference among the
   scale filters learned either at every frame or at every 5
-  frames. The sub-figures at the top row show the scale filters
-  trained from every frame and those at the bottom row show the scale
-  filters estimated every 5 frames.}
+  frames. The sub-figures at the the left show the scale filters
+  trained at every frame and those at the right show the scale
+  filters trained at every 5 frames.}
 \label{fig:Filters_Comparison}

### 2017-05-30 bmvc_review.tex
Revised the drafts on the comments.

@@
 The Kernelized Correlation Filter is a well, known single target
-tracking method and the theory and its work flow has been detailed in
-other papers already \cite{henriques2012exploiting,henriques2015high}. This section briefly
-goes over the parts of the KCF relevant to this study. Its
-computational efficiency is derived from the correlation
-filter framework representing training examples as a circulant matrix. To reduce complexity, the
-circulant matrix can be diagonalized by Discrete Fourier Transform.  This way, off-diagonal elements become
-zero whereas the diagonal elements represent the eigenvalues of the circulant matrix. The egienvalues are equal
-to the DFT transformation of the base sample ($x$) elements. The Kernelized Correlation Filter, on the other hand,
-applies a kernel to $x$ to transform to a more discriminative domain. The circulant matrix is then formed by applying
-cylic shifts on the kernelized $x$. Such kernelization operation does not introduce additional complexity to the baseline
-correlation filter framework.
-
+tracking method and its work flow has been detailed in other papers
+already \cite{henriques2012exploiting,henriques2015high}. This section
+briefly goes over the parts of the KCF relevant to this study. Its
+computational efficiency is derived from the correlation filter
+framework representing training examples as a circulant matrix. The
+fact that a circulant matrix can be diagonalized by Discrete Fourier
+transform is the key to reduce the complexity of any tracking method
+based on correlation filter. The off-diagonal elements become zero
+whereas the diagonal elements represent the eigenvalues of the
+circulant matrix. The egienvalues are equal to the DFT transformation
+of the base sample ($x$) elements. The Kernelized Correlation Filter,
+in particular, applies a kernel to $x$ to transform to a more
+discriminative domain. The circulant matrix is then formed by applying
+cylic shifts on the kernelized $x$. Such kernelization operation does
+not introduce additional complexity to the baseline correlation filter
+framework.
+\begin{comment}
 {\it Burak: The above paragraph didn't connect to the following
@@
 {\it YoungWoo : I edited it based on your comment}
-
+\end{comment}
 The KCF essentially solves the problem of a regression in the form of
@@
 aims at developing an object tracking algorithm that ``efficiently''
-runs on an embedded system in ``high speed,'' $\ge 300$ fps, e.g.,
-running our tracking algorithms on a drone. Given this, we believe
-that the UAV123 video data is a better fit in evaluating the
-performance of the proposed algorithm than any other existing tracking
-datasets. This is because there are many challenging scenes, e.g.,
-abrupt scale/illumination changes. Although we are primarily
-interested in developing an algorithm for mobile, embedded robotic
-applications, it is important to compare the performance of the
-proposed algorithm with those of the state-of-the-art in nominal
-dataset for comparison. To this end, we chose the OTB100 data that
-contains the videos recorded from smart phones and typical cameras in
-perspective view. Finally, the {\it E}nKCF2 is tested on temporally
-down-sampled version of the UAV123 dataset, called UAV123$\_$10fps dataset. 
-This way, by modifying the proposed {\it E}nKCF framework slightly we can tackle scenarios dominated by extreme camera and object
-motion as we run multiple correlation filter at each frame. One can also perform such modifications based on the hardware specifications. 
-A more sophisticated hardware can be more friendly to apply multiple correlation filter ({\it E}nKCF2) at one frame
-whereas the ones on the low end can only accommodate a single correlation filter at each frame ({\it E}nKCF).
+runs on an embedded system (e.g., a drone) in ``high speed,'' $\ge
+300$ fps, e.g. Given this, we believe that the UAV123 video data is a
+better fit in evaluating the performance of the proposed algorithm
+than any other existing tracking datasets. This is because there are
+many challenging scenes, e.g., abrupt scale/illumination
+changes. Although we are primarily interested in developing an
+algorithm for mobile, embedded robotic applications, it is important
+to compare the performance of the proposed algorithm with those of the
+state-of-the-art in nominal dataset for comparison. To this end, we
+chose the OTB100 data that contains the videos recorded from smart
+phones and typical cameras in perspective view.
 
-{\it Burak: You need to explain why it is useful or meaningful to
-  evaluate our algorithm w/ a down-sampled version of the UAV123
-  dataset.}
+Lastly, we tested the proposed algorithm on a temporally down-sampled
+version of the UAV123 dataset, called UAV123$\_$10fps dataset. What we
+would like to see from this experiment is to evaluate how robust the
+proposed algorithm is to drastic motions of camera and targets.
 
-{\it YoungWoo: I edited the preceding paragraph based on your comment.}
+{\it Burak: We have never told what EnKCF2 is before the following sentence. Just don't mention EnKCF2, but say a modification of EnKCF!}
+
+\begin{comment}
+Finally, the {\it E}nKCF2 is tested on temporally down-sampled version
+of the UAV123 dataset, called UAV123$\_$10fps dataset.  This way, by
+modifying the proposed {\it E}nKCF framework slightly we can tackle
+scenarios dominated by extreme camera and object motion as we run
+multiple correlation filter at each frame. One can also perform such
+modifications based on the hardware specifications.  A more
+sophisticated hardware can be more friendly to apply multiple
+correlation filter ({\it E}nKCF2) at one frame whereas the ones on the
+low end can only accommodate a single correlation filter at each frame
+({\it E}nKCF).
+\end{comment}
 
@@
 
-{\it Burak: I don't think I agreed to put the following part as a part
-  of our submission.}
-
 \textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight

### 2017-05-31 bmvc_review.tex
Figures 2-3 Updated

@@
 \end{tabular}
-\caption{The work-flow of {\it E}nKCF tracking algorithm.}
+\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the first seven frames of
+tracking where the first frame is the initialization frame. The tracking in between frames
+7-11, and 12-16 etc. is the repetition of tracking in frames 2-6.}
 \label{Workflows}

### 2017-05-31 bmvc_review.tex
Comments Answered

@@
 
+{\it YoungWoo :  I understand your point. It will give them the feeling of a new algorithm called EnKCF2. I will change the precision and success figures to EnKCF.}
+
 \begin{comment}
@@
 \end{tabular}
-\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates.
+\caption{Evaluation and comparison of the modified {\it E}nKCF tracker on the UAV123$\_$10fps dataset in terms of the precision and success rates.
 This dataset consists of temporally down-sampled $123$ video sequences captured from a micro UAV.}

### 2017-05-31 bmvc_review.tex
Algorithm Improved

@@
 \KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, scale filter frequency $n = 5$,}
-\KwOut{	\uIf{$fc\:\%\:n=0$ (Condition 1)}
+\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
 			{
 				Estimated Target State $(x_{t},y_{t},s_{t})$,
-				Scale filter (\textit{target-only}) model $R_{s}$.
+				Scale filter (\textit{target-only}) model $R_{s}$
 			}			  
-			 \ElseIf{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$ (Condition 2)}
+			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
 			 {
 				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
-			  	Large Area Translation Filter model $R_{t}^{L}$.
+			  	Large Area Translation Filter model $R_{t}^{L}$
 			}			 
-			 \Else (\textit{Condition 3})
+			 \Else (\textit{\textbf{Condition 3}})
 			{			 
 				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
-				Small Area Translation Filter model $R_{t}^{S}$.				
+				Small Area Translation Filter model $R_{t}^{S}$			
 			}	
@@
      // \textit{Translation Estimation - Correlation Filter} \\
-	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{max(y_{R_{t}})}$\\
+	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
 	// \textit{Scale Estimation - Correlation Filter}\\
 	Scale pool for $R_{s}$ : $S = \lbrace1.05,1.0,1/1.05\rbrace$,\\
-	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{argmax}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
+	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
 	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$)\\

### 2017-05-31 bmvc_review.tex
Revised the text and some comments on figure.

--- 2017-05-31 bmvc_review.tex
@@
 way. In particular, we use an ensemble of KCFs in turn, instead of
-running them all together on every frame. We deploy three KCF in turn:
+running them all together on every frame. We deploy three KCFs in turn:
 \textit{target}+\textit{small background} translation filter
@@
 \end{tabular}
-\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the first seven frames of
-tracking where the first frame is the initialization frame. The tracking in between frames
-7-11, and 12-16 etc. is the repetition of tracking in frames 2-6.}
+\caption{The workflow of {\it E}nKCF tracking algorithm. We show the
+  first seven frames of tracking where the first frame is the
+  initialization frame. Afterward, the order of deploying three KCFs
+  is repeating.}
 \label{Workflows}
@@
 algorithm running in a very high-speed, $\geq 300$ fps. In particular,
-the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCF, in
+the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCFs, in
 turn, to more effectively address the scale variance and the dynamic
@@
 examples of the ROI covered by each of three filters.
+
+{\it Burak: Please remove the in-figure text ``Correlation Filters
+  employed...'' from Figure 3. Can you make the examples of these
+  filters using the picture of ``David'' shown at Figure 2.}
 
@@
 tracking method and its work flow has been detailed in other papers
-already \cite{henriques2012exploiting,henriques2015high}. This section
-briefly goes over the parts of the KCF relevant to this study. Its
+\cite{henriques2012exploiting,henriques2015high}. This section briefly
+goes over the parts of the KCF relevant to this study. Its
 computational efficiency is derived from the correlation filter
@@
 discriminative domain. The circulant matrix is then formed by applying
-cylic shifts on the kernelized $x$. Such kernelization operation does
+cyclic shifts on the kernelized $x$. Such kernelization operation does
 not introduce additional complexity to the baseline correlation filter
 framework.
-\begin{comment}
-{\it Burak: The above paragraph didn't connect to the following
-  paragraphs. You'll have to finish up the sentence about a
-  correlation filter's, not KCF yet, computational efficiency and then
-  continue to explain how this a regularized correlation filter will
-  be transformed into KCF w/ the same computational complexity.}
 
-{\it YoungWoo : I edited it based on your comment}
-\end{comment}
-The KCF essentially solves the problem of a regression in the form of
-the regularized ridge regression as:
+The KCF solves essentially the problem of a regression in the form of
+the regularization:
 \begin{equation}
@@
 this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
-solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
-taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
-$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
-multiplication in frequency domain was proposed as a sub-linear
-solution for $\hat{w}$:
+solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
+closed-form solution less complex, an element-wise, multiplication in
+frequency domain was proposed for $\hat{w}$:
 \begin{equation}
@@
 \end{equation}
-In fact, a non-linear version of this closed-form solution is proposed
-to make it more robust to any geometric and photometric variations
+A non-linear version of this closed-form solution is proposed to make
+it more robust to any geometric and photometric variations
 \cite{henriques2015high}. In particular, the diagonalized Fourier
@@
 
-{\it Burak: We have never told what EnKCF2 is before the following sentence. Just don't mention EnKCF2, but say a modification of EnKCF!}
-
-\begin{comment}
-Finally, the {\it E}nKCF2 is tested on temporally down-sampled version
-of the UAV123 dataset, called UAV123$\_$10fps dataset.  This way, by
-modifying the proposed {\it E}nKCF framework slightly we can tackle
-scenarios dominated by extreme camera and object motion as we run
-multiple correlation filter at each frame. One can also perform such
-modifications based on the hardware specifications.  A more
-sophisticated hardware can be more friendly to apply multiple
-correlation filter ({\it E}nKCF2) at one frame whereas the ones on the
-low end can only accommodate a single correlation filter at each frame
-({\it E}nKCF).
-\end{comment}
-
-\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
+\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
   E}nKCF is designed for addressing a specific challenge of a single,
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF
-  for the UAV123 dataset.}
+\caption{Comparison of {\it E}nKCF's performance with those of the
+  state-of-the-art tracking algorithms on the UAV123 dataset.}
 \label{fig:UAV123_DATASET}
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF
-  for the OTB100 dataset.}
+\caption{Comparison of {\it E}nKCF's performance with those of the
+  state-of-the-art tracking algorithms on the OTB100 dataset.}
 \label{fig:OTB100_DATASET}
@@
 \end{tabular}
-\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates.
-This dataset consists of temporally down-sampled $123$ video sequences captured from a micro UAV.}
+\caption{Comparison of a modified {\it E}nKCF's performance with those
+  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
+  dataset where the original UAV123 data was temporally downsampled.}
 \label{fig:UAV123_10fpsDATASET}
@@
 
-%\begin{figure}[!h]
-%\centering
-%\begin{tabular}{cc}
-%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
-%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
-%\end{tabular}
-%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
-%\label{fig:OTB100_DATASET}
-%\end{figure}
 %---------------------------------------------------------------------- 

### 2017-06-01 bmvc_review.tex
Filters Details Figure Updated
TEXT ADDED

@@
 \usepackage[ruled, vlined, linesnumbered]{algorithm2e}
+\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}
 
@@
 
+{\it YoungWoo : I just did it. Let me know if you see any problem with it.}
+
 \begin{figure}[!h]
@@
 discriminative domain. The circulant matrix is then formed by applying
-cyclic shifts on the kernelized $x$. Such kernelization operation does
-not introduce additional complexity to the baseline correlation filter
-framework.
+cyclic shifts on the kernelized $x$. Such kernelization operation maintains 
+O($nlog(n)$) complexity unlike other kernel algorithms leading to O($n^{2}$) or even higher 
+complexities.
 

### 2017-06-01 bmvc_review.tex
Revised the text.

@@
 sensors than a lightweight or an array of monocular cameras. For
-example, instead of having just bare flight function with video
-recording, an unmanned air vehicle (UAV) equipped with an object or
+example, instead of just flying to record a video based on manual
+commands, an unmanned air vehicle (UAV) equipped with an object or
 feature following functionality would make it more useful in the
@@
 running on any embedded or mobile platforms that doesn't require an
-offline training, and can run on an embedded system. Specifically, we
-would like to make our algorithm 1) learn the appearance model of a
-target on the fly and 2) run as fast on a typical desktop as up to
-$300$-$400$ fps so that it could run, at least, faster than 30 fps
-when it is deployed on a low-end, embedded system.\footnote{In
-  general, it would be very hard to compare an Intel or AMD processor
-  running on a desktop or a laptop with that, e.g., ARM, of a
-  single-board, embedded system in terms of run-time performance of a
-  computer vision algorithm. This is primarily because of difference
-  in their architectures. But we empirically found this computation
-  useful and reasonable based on specific processors, e.g., Intel's i7
-  quad-core vs ARM Cortex A53 -- the computation about an 1/10th scale
-  down of computational resources from a typical PC to an embedded
-  system.}
+offline training. Specifically, we would like to make our algorithm 1)
+learn the appearance model of a target on the fly and 2) run as fast
+on a typical desktop as up to $300-400$ fps so that it could run, at
+least, faster than 30 fps when it is deployed on a low-end, embedded
+system.\footnote{In general, it would be very hard to compare an Intel
+  or AMD processor running on a desktop or a laptop with that, e.g.,
+  ARM, of a single-board, embedded system in terms of run-time
+  performance of a computer vision algorithm. This is primarily
+  because of difference in their architectures. But we empirically
+  found this computation useful and reasonable based on specific
+  processors, e.g., Intel's i7 quad-core vs ARM Cortex A53 -- the
+  computation about an 1/10th scale down of computational resources
+  from a typical PC to an embedded system.}
 
@@
 this reformulation, an object tracking pipeline based on the
-correlation filter can be easily implemented and run very efficiently
-on the fly. In fact, an extension of a linear correlation filter, the
+correlation filter can run very efficiently and be even easily
+implemented. In fact, an extension of a linear correlation filter, the
 kernelized correlation filter with multi-channel features
@@
 online tracker is prone to drift, and fails to track a target over a
-long period of time primarily \cite{henriques2015high}. This is
-primarily due to the dilemma of stability-plasticity in updating
-appearance model, where the appearance model will be overfitted to
-only the images used to train, unless a compromise on the frequency of
-updating the model is carefully implemented
-\cite{santner2010prost}. For example, one may handle a target's scale
-variation by just concatenating multiple correlation filters including
-KCF and running them on each frame. Alternatively one could think of
-scanning the region of interest (ROI) with a list of templates in
-predefined scale ratios to find the target in appropriate scale
+long period of time \cite{henriques2015high}. This is primarily due to
+the dilemma of stability-plasticity in updating appearance model,
+where the appearance model will be overfitted to only the images used
+to train, unless a compromise on the frequency of updating the model
+is carefully implemented \cite{santner2010prost}. For example, one may
+handle a target's scale variation by just concatenating multiple
+correlation filters including KCF and running them on each
+frame. Alternatively one could think of scanning the region of
+interest (ROI) with a list of templates in predefined scale ratios to
+find the target in appropriate scale
 \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
@@
 assumption that the scale of a target would not change much over two
-consecutive frames. Similarly \cite{ma2015long} used two KCFs to learn
-the translation and scale of a target separately. To be more specific,
-a KCF is used to learn the translation of the target and its
-background. Given this, another KCF is used to learn the target area
-to estimate a new scale of the target. However, because of running
-more than a KCF on each frame, this method degrades its run-time
-performance (i.e., $\leq 50 fps$). Our method is motivated by this
-idea -- the idea of deploying multiple KCFs to address the issues of
-single target tracking: scale and translation, but in a more efficient
-way. In particular, we use an ensemble of KCFs in turn, instead of
-running them all together on every frame. We deploy three KCFs in turn:
+consecutive frames. Similarly, Ma and his colleagues used two KCFs to
+learn the translation and scale of a target separately
+\cite{ma2015long}. In particular, a KCF is used to learn the
+translation of the target and its background. Given this, another KCF
+is used to learn the target area to estimate a new scale of the
+target. However, because of running more than a KCF on each frame,
+this method degrades its run-time performance (i.e., $\leq 50
+fps$). Our method is motivated by this idea -- the idea of deploying
+multiple KCFs to address the issues of single target tracking: scale
+and translation, but in a more efficient way. In particular, we use an
+ensemble of KCFs in turn, instead of running them all together on
+every frame. We deploy three KCFs in turn:
 \textit{target}+\textit{small background} translation filter
@@
 \textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). By doing so, we could still address the scale change
-and estimate target's motion efficiently while maintaining or
-increasing run-time performance. Figure \ref{fig:Filters} shows
-examples of the region of interest (ROI) associated with $R_{t}^{S}$,
-$R_{t}^{L}$, and $R_{s}$. Figure \ref{Workflows} illustrates the
-work-flow of the {\it E}nKCF.
+($R_{t}^{L}$). By doing so, we could address the scale change and
+estimate target's motion efficiently while maintaining or increasing
+run-time performance. Figure \ref{fig:Filters} shows examples of the
+region of interest (ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and
+$R_{s}$. Figure \ref{Workflows} illustrates the work-flow of the {\it
+  E}nKCF.
 \begin{figure}[!t]
@@
 examples of the ROI covered by each of three filters.
-
-{\it Burak: Please remove the in-figure text ``Correlation Filters
-  employed...'' from Figure 3. Can you make the examples of these
-  filters using the picture of ``David'' shown at Figure 2.}
-
-{\it YoungWoo : I just did it. Let me know if you see any problem with it.}
 

### 2017-06-01 bmvc_review.tex
Revised the text again; maybe this is a last stretch for a while before revising this again.

@@
 
-\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed}
+\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for
+  High-Speed, Object Tracking}
 
@@
 computer vision algorithms are getting more attentions primarily
-because payloads of those mobile platforms are limited to carry other
-sensors than a lightweight or an array of monocular cameras. For
+because payloads of those mobile platforms are limited to carry any
+other sensors than a lightweight or an array of monocular cameras. For
 example, instead of just flying to record a video based on manual
@@
 
-In this paper, we propose a single-target tracking algorithm aiming at
-running on any embedded or mobile platforms that doesn't require an
-offline training. Specifically, we would like to make our algorithm 1)
-learn the appearance model of a target on the fly and 2) run as fast
-on a typical desktop as up to $300-400$ fps so that it could run, at
-least, faster than 30 fps when it is deployed on a low-end, embedded
+In this paper, we propose a single-target tracking algorithm, with no
+offline training, aiming at running on any embedded or mobile
+platforms. Specifically, we would like to make our algorithm 1) learn
+the appearance model of a target on the fly and 2) run as fast on a
+typical desktop as up to $300-400$ fps so that it could run, at least,
+faster than 30 fps when it is deployed on a low-end, embedded
 system.\footnote{In general, it would be very hard to compare an Intel
@@
 multiple KCFs to address the issues of single target tracking: scale
-and translation, but in a more efficient way. In particular, we use an
-ensemble of KCFs in turn, instead of running them all together on
-every frame. We deploy three KCFs in turn:
-\textit{target}+\textit{small background} translation filter
-($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
-\textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). By doing so, we could address the scale change and
-estimate target's motion efficiently while maintaining or increasing
-run-time performance. Figure \ref{fig:Filters} shows examples of the
-region of interest (ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and
-$R_{s}$. Figure \ref{Workflows} illustrates the work-flow of the {\it
-  E}nKCF.
+and translation, but in a more efficient way. In particular, we use a
+multiple of KCFs, in an order of maximizing run-time performance and
+accuracy, instead of running them all together on every frame. We
+deploy three KCFs in turn: \textit{target}+\textit{small background}
+translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
+($R_{s}$) and \textit{target}+\textit{large background} translation
+filter ($R_{t}^{L}$). By doing so, we could address the scale change
+and estimate target's motion efficiently while maintaining or
+increasing run-time performance. Figure \ref{fig:Filters} shows
+examples of the region of interest (ROI) associated with $R_{t}^{S}$,
+$R_{t}^{L}$, and $R_{s}$. Figure \ref{Workflows} illustrates the
+work-flow of the {\it E}nKCF.
 \begin{figure}[!t]
@@
 %---------------------------------------------------------------------- 
-In this paper, we propose a novel way of utilizing multiple of the KCF
+In this paper, we propose a novel way of utilizing a multiple of the KCFs
 \cite{henriques2015high} to effectively handle scale variations and
@@
 learning a target's translation should include its background to
-better discriminate the target from its background, and another
+better discriminate the target from its surrounding, and another
 correlation filter should focus on the target itself to estimate the
-right size or scale of the target. Figure \ref{fig:Filters} shows
-examples of the ROI covered by each of three filters.
+right scale of the target. Figure \ref{fig:Filters} shows examples of
+the image, sub-regions covered by each of these filters.
 
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figures/Filters_Details.pdf}
+\includegraphics[width=1.0\textwidth]{figures/Filters_Details.pdf}
 \caption{Examples of three filters; the translation filter,
@@
 \end{equation}
-where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
+where $\hat{k}^{xx}$ represents the first row of the kernel matrix $K$
 known as \textit{gram matrix} and it is expressed as
@@
 To evaluate the performance of the proposed algorithm, we choose two
-public, available datasets:
+publicly, available datasets:
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
@@
 aims at developing an object tracking algorithm that ``efficiently''
-runs on an embedded system (e.g., a drone) in ``high speed,'' $\ge
-300$ fps, e.g. Given this, we believe that the UAV123 video data is a
-better fit in evaluating the performance of the proposed algorithm
-than any other existing tracking datasets. This is because there are
-many challenging scenes, e.g., abrupt scale/illumination
-changes. Although we are primarily interested in developing an
-algorithm for mobile, embedded robotic applications, it is important
-to compare the performance of the proposed algorithm with those of the
-state-of-the-art in nominal dataset for comparison. To this end, we
-chose the OTB100 data that contains the videos recorded from smart
-phones and typical cameras in perspective view.
-
-Lastly, we tested the proposed algorithm on a temporally down-sampled
-version of the UAV123 dataset, called UAV123$\_$10fps dataset. What we
-would like to see from this experiment is to evaluate how robust the
-proposed algorithm is to drastic motions of camera and targets.
+runs on an embedded system, a drone, for example, in ``high speed,''
+$\ge 300$ fps. Given this, we believe that the UAV123 data is a good
+fit in evaluating the performance of the proposed algorithm. In
+addition, in the UAV123 data, there are many challenging, realistic
+scenes, e.g., abrupt scale/illumination changes. Although we are
+primarily interested in developing an algorithm for mobile, embedded
+robotic applications, it is also important to compare the performance
+of the proposed algorithm with those of the state-of-the-art in a
+nominal dataset for comparison. To this end, we chose the OTB100 data
+that contains the videos recorded from smart phones and typical
+cameras in perspective view. Lastly, we tested the proposed algorithm
+on a temporally down-sampled version of the UAV123 dataset, called
+UAV123$\_$10fps dataset. What we would like to see from this
+experiment is to evaluate how robust the proposed algorithm is to
+drastic motions of camera and targets.
 
 \textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
-  E}nKCF is designed for addressing a specific challenge of a single,
-target tracking problem. Thus each of them should have different value
-for the optimal parameters. For instance, the primary task of the
-translation filter, $R_{t}^{L}$ is to estimate the translation of a
-target from the previous frame whereas the scale filter, $R_{s}$ and
+  E}nKCF is designed for addressing specific challenges in single,
+target tracking problem. Thus each of them should have different
+values for the optimal parameters. For instance, the primary task of
+the translation filter, $R_{t}^{L}$ is to estimate the translation of
+a target from the previous frame whereas the scale filter, $R_{s}$ and
 the estimated state of the particle filter are primarily used to
@@
 $0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate
-as $0.12$ for $R_{t}^{L}$. For the particle filter, we empirically set
-the number of particles to $1000$ to balance the run-time performance
-and accuracy. To keep the level of variance among the particles
-reasonable, we performed the re-sampling only when the
+as $0.12$ for $R_{t}^{L}$. For our particle filter implementation, we
+empirically set the number of particles to $1000$ to balance the
+run-time performance and accuracy. To keep the level of variance among
+the particles reasonable, we performed the re-sampling only when the
 \textit{efficient number of samples} ($ \hat{N}_{eff} \approx
@@
 of them. In particular, the translation filter, $R_{t}^{L}$, uses both
-the fast Histograms of Oriented Gradients
-(fHoG)\cite{felzenszwalb2010object} and
-color-naming\cite{van2009learning} features to learn the background
-around the target more effectively. In fact we empirically found fHoG
-only didn't work well to cover the larger ROI. Another translation
-filter, $R_{t}^{S}$, used fHoG features only. The scale filter,
-$R_{s}$ used both fHoG and color features to learn the scale change
-more accurately.
+the fast Histograms of Oriented Gradients (fHoG)
+\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
+features to learn the background around the target more
+effectively. In fact we empirically found fHoG only didn't work well
+to cover the larger ROI. Another translation filter, $R_{t}^{S}$, used
+fHoG features only. The scale filter, $R_{s}$ used both fHoG and color
+features to learn the scale change more accurately.
 
@@
 tracker.
+
 \begin{figure}[!h]
@@
 algorithms should run faster with small footprint of computation
-resource consumption. To make an object tracking algorithm with these
-practical requirements available, we proposed an extension of KCF that
+resource consumption. To make an object tracking algorithm meet these
+practical requirements, we proposed an extension of KCF that
 essentially deploys three KCFs, in turn, to address the scale change

### 2017-06-12 C++_Implementation/RunTracking/OneTimeRun.sh
README File

@@ -1,20 +1,0 @@
-#!/bin/sh
-
-i=1
-
-# UAV123
-cd /home/buzkent/Downloads/UAV123_10fps/data_seq/UAV123_10fps/
-
-# VOT15
-# cd /home/buzkent/Downloads/VOT15/
-
-for item in *
-
-   do 
-
-    # echo "Item : $item"
-    # UAV123
-    /home/buzkent/paper/C++_Implementation/build/EnKCF -e image -d /home/buzkent/Downloads/UAV123_10fps/data_seq/UAV123_10fps/"$item"/ -g /home/buzkent/Downloads/UAV123_10fps/anno/UAV123_10fps/"$item".txt -p "$item"
-    # VOT15
-    # /home/buzkent/paper/C++_Implementation/build/EnKCF -e image -d /home/buzkent/Downloads/VOT15/"$item"/ -g /home/buzkent/Downloads/VOT15/"$item"/groundtruth.txt -p "$item"
-   done

### 2017-06-12 C++_Implementation/RunTracking/avgPrecision.cpp

@@ -1,118 +1,0 @@
-#include <iostream>
-#include <fstream>
-#include <sstream>
-#include <iomanip>
-#include <iterator>
-#include <vector>
-#include <string>
-#include <unistd.h>
-#include <dirent.h>
-
-int main(int argc, char* argv[]){
-
-    float indPrecision, indSuccessOverlap;
-    std::vector<std::vector<float> > avgPrecision(2);
-    std::ofstream precisionFile("/home/buzkent/Downloads/Results/AveragePrecision/Precision.txt");
-    std::ofstream successFile("/home/buzkent/Downloads/Results/AveragePrecision/Success.txt");
-    std::ifstream runTimeFile("/home/buzkent/Downloads/Results/RunTime/RunTimes.txt");
-
-    // Parse through all the Text Files and Compute Average Precision
-    struct dirent *pDirent;
-    DIR *pDir = opendir("/home/buzkent/Downloads/Results/Precision/");
-    int fileFirst = 0;
-    char ch;
-    while ((pDirent = readdir(pDir)) != NULL) {
-
-       std::string fileName = pDirent->d_name;
-       std::string homeDir = "/home/buzkent/Downloads/Results/Precision/";
-       std::string fullDir = homeDir.append(fileName);
-       std::ifstream prFile(fullDir);
-       std::string toAvoid = ".";
-       if (fileName.compare(toAvoid) == 0 || fileName.compare("..") == 0){
-          continue;
-       }
-       if (!prFile)
-       {
-         return 0;
-       }
-       int index = 0;
-       while (prFile >> indPrecision){
-	   std::cout << indPrecision << std::endl;
-           if (fileFirst == 0){
-              avgPrecision[0].push_back(indPrecision);
-           }
-           else{
-              avgPrecision[0][index] += indPrecision;
-              index++;
-           }
-       }
-       fileFirst++;
-       
-    }
-    closedir(pDir);
-
-    // Save the Results into Another Text File
-    for (int i = 0; i < avgPrecision[0].size() ; i++){
-        avgPrecision[0][i] /= fileFirst;
-        precisionFile << avgPrecision[0][i];
-        precisionFile << std::endl;
-    }
-
-    // struct dirent *pDirent; 
-    pDir = opendir("/home/buzkent/Downloads/Results/Success/");
-    int fileFirst2 = 0;
-    while ((pDirent = readdir(pDir)) != NULL) {
-
-       std::string fileName = pDirent->d_name;
[…]

### 2017-06-12 C++_Implementation/detector/src/kcftracker.cpp
Fixed Template Size Added

@@ -90,9 +90,9 @@ KCFTracker::KCFTracker(bool hog, bool fixed_window, bool multiscale, bool lab)
 
 
     if (multiscale) { // Multiscale KCF Implementation
-        template_size = 96;       // Template Size for the Translation Filter
-        template_size_w_roi = 96; // Template Size for the Wide ROI Translation Filter
-        template_size_scale = 64; // Template Size for the Scale Filter
+        template_size = 64*64;       // Template Size for the Translation Filter
+        template_size_w_roi = 64*64; // Template Size for the Wide ROI Translation Filter
+        template_size_scale = 48*48; // Template Size for the Scale Filter
         scale_step = 1.05;     	  // Scale Factor for the Multiscale Search
         scale_weight = 2.0 - scale_step;    // Priority is given to the Same Scale with Previous Frame Scale
         if (!fixed_window) {     // Fixed Window KCF Implementation during Tracking
@@ -147,9 +147,6 @@ cv::Rect KCFTracker::update(cv::Mat image)
     float cx = _roi.x + _roi.width / 2.0f;
     float cy = _roi.y + _roi.height / 2.0f;
 
-    // Transfer to the Global ROI
-    gROI = _roi;
-
     // Detect the Target Translation
     float peak_value;
     cv::Point2f res = detect(_tmpl, getFeatures(image, 0, 1.0f), peak_value);
@@ -191,9 +188,6 @@ cv::Rect KCFTracker::updateWROI(cv::Mat image)
     float cx = _roi_w.x + _roi_w.width / 2.0f;
     float cy = _roi_w.y + _roi_w.height / 2.0f;
 
-    // Transfer ROI to the Global ROI
-    gROI = _roi_w;
-
     // Detect the Target Translation
     float peak_value;
     cv::Point2f res = detectWROI(_tmpl_w_roi, getFeaturesWROI(image, 0, 1.0f), peak_value);
@@ -228,10 +222,6 @@ cv::Rect KCFTracker::updateWROI(cv::Mat image)
 // Update position based on the new frame
 cv::Rect KCFTracker::updateScale(cv::Mat image)
 {
-
-    // Transfer to the GLobal ROI
-    gROI = _roi_scale;
-
     ///
     /// Detect the Peak at the Same Scale and Corresponding Value
     ///
@@ -310,8 +300,6 @@ cv::Point2f KCFTracker::detect(cv::Mat z, cv::Mat x, float &peak_value)
     // Transfer to the global response map
[…]

### 2017-06-12 C++_Implementation/main/src/runtracker.cpp

@@ -142,9 +142,9 @@ int main(int argc, char* argv[])
    /// \param[in] Q : Transition Noise Variance
    /// \param[in] R : Measurement Noise Variance
    ///
-   int N_Particles = 300;     // Number of Particles
+   int N_Particles = 1000;     // Number of Particles
    int dimension = 4;          // State Space Dimensionality
-   vector<double> Q{10,10,2,2}; // Transition Noise Variance
+   vector<double> Q{20,20,4,4}; // Transition Noise Variance
    double R = 5;               // Measurement Noise Variance
    double beta = 0.1;         // Likelihood Parameter
    Particle_Filter PfTracker(N_Particles,dimension,beta,Q,R);
@@ -212,7 +212,7 @@ char ch;
    std::string seqName; 
    std::string seqNameID;
    std::string matchString = prDataFile;
-   std::ifstream startFrame("/home/buzkent/Desktop/startFrames_UAV123.txt");
+   std::ifstream startFrame("/Users/buzkent/Downloads/UAV123/startFrames_UAV123.txt");
    while(startFrame >> fFrame >> lFrame >> seqNameID >> seqName){
      if (seqNameID.compare(matchString) == 0){
          frameID = fFrame;
@@ -397,6 +397,7 @@ char ch;
         // TRACKING RESULTS OVERLAID ON THE FRAME
         cv::rectangle( frame, cv::Point(result.x,result.y), cv::Point(result.x+result.width,result.y+result.height), cv::Scalar(255,0,0),4,8);
         cv::rectangle( frame, cv::Point(gX,gY), cv::Point(gX+gWidth,gY+gHeight), cv::Scalar(0,255,0),4,8);
+        cv::rectangle( frame, cv::Point(tracker.gROI.x,tracker.gROI.y), cv::Point(tracker.gROI.x+tracker.gROI.width,tracker.gROI.y+tracker.gROI.height), cv::Scalar(0,255,0),4,8);	
 	std::string confidence = to_string(int(PSR));
         cv::putText(frame,confidence, cv::Point(result.x-result.width/2,result.y-result.height/2), fontFace, 4, cv::Scalar::all(255), thickness, 4);
 
@@ -460,7 +461,7 @@ char ch;
       if (!SILENT) {
 	// cv::resize(frame,frame,Size(300,150));
         cv::imshow("Name", frame);
-        cv::waitKey(0);
+        cv::waitKey(2);
       }
    }
    // Estimate Precision Curve

### 2017-06-12 C++_Implementation/tracker/src/Function_Definitions.cpp

@@ -83,11 +83,7 @@ void Particle_Filter::particle_weights_cfMap(cv::Mat response, cv::Rect_<int> RO
 	else{
 	   int xCoord = abs(particles[i*ss_dimension] - ROI.x);
            int yCoord = abs(particles[i*ss_dimension+1] - ROI.y);
-           Weights[i] = response.at<double>(yCoord,xCoord);
-	   cv::Point2i pi;
-	   double pv;
-           cv::minMaxLoc(response, NULL, &pv, NULL, &pi);
-	   cout << pi.x << "---" << pi.y << "---" << response.rows << "---" << response.cols << endl;
+           Weights[i] = response.at<float>(yCoord,xCoord);
         }
         Acc += Weights[i];             // Cumulative Sum
     }
@@ -107,7 +103,7 @@ void Particle_Filter::particle_resampling()
     double r = double(randomDevice(generator))/(1000*N_Particles);
     double c = Weights[0];
     int i = 0;
-    if ((1/Neff) < (N_Particles / 0.50)){
+    // if ((1/Neff) < (N_Particles / 2.00)){
        for (int m = 0; m < N_Particles; m++){
 	   U = r + m * (1/double(N_Particles));	// Update
 	
@@ -122,7 +118,7 @@ void Particle_Filter::particle_resampling()
            particles[m*ss_dimension + 3] = particles[i*ss_dimension + 3]; // Sample with Replacement  	
        }
        rsFlag = 1;
-    }
+    // }
 }
 
 void Particle_Filter::mean_estimation(vector<double>& State_Mean)

### 2017-06-13 bmvc_review.tex
Table - Differen KCF Combinations Added

@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{|l|c|c|c|c|c|c|}
+\hline
+Metric/Method & $R_{t}^{L}$+$R_{t}^{S}$+$R_{s}$ ({\it E}nKCF) & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & LCT \cite{ma2015long}\\
+\hline\hline
+Precision ($20$px) & \textbf{54.5} & 48.09 & & & &\\
+Success Rate ($50\%$) & \textbf{40.2} & 36.04 & & & & \\
+Frame Per Second & \textbf{416} & 370 & & & & \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Evalutions of the different combinations of the proposed KCFs in UAV123 dataset.
+We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.}
+\end{table}
+
 \textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight

### 2017-06-13 bmvc_review.tex
Revised the draft based on the comments.

@@
 specifically address the scale-change and dynamic maneuver of the
-target over frames. To guarantee a high-speed, runtime performance, we
+target over frames. To guarantee a high-speed, run-time performance, we
 deploy each of KCFs in turn. For a smooth transition between
@@
   ARM, of a single-board, embedded system in terms of run-time
-  performance of a computer vision algorithm. This is primarily
-  because of difference in their architectures. But we empirically
-  found this computation useful and reasonable based on specific
-  processors, e.g., Intel's i7 quad-core vs ARM Cortex A53 -- the
-  computation about an 1/10th scale down of computational resources
-  from a typical PC to an embedded system.}
+  performance of a computer vision algorithm. This is primarily due to
+  the difference in their architectures. To derive this number, we
+  assume that there is roughly, at least, an 1/10th scale down of
+  computational resources from a typical PC to an embedded system. We
+  found such a scale-down in computation based on exemplar processors,
+  e.g., Intel's i7 quad-core vs ARMv8 dual-core.}
 
-One of the dominant frameworks for online object tracking is the
+One of the dominant frameworks for online, object tracking is the
 correlation filter that essentially solves a single-target tracking
@@
 the target by further analyzing image, sub-regions with high
-confidence to figure out the scale of a target. This is based on an
-assumption that the scale of a target would not change much over two
-consecutive frames. Similarly, Ma and his colleagues used two KCFs to
-learn the translation and scale of a target separately
-\cite{ma2015long}. In particular, a KCF is used to learn the
-translation of the target and its background. Given this, another KCF
-is used to learn the target area to estimate a new scale of the
-target. However, because of running more than a KCF on each frame,
-this method degrades its run-time performance (i.e., $\leq 50
+confidence. This is based on an assumption that the scale of a target
+would not change much over two consecutive frames. Similarly, Ma and
+his colleagues used two KCFs to learn the translation and scale of a
+target separately \cite{ma2015long}. In particular, a KCF is used to
+learn the translation of the target and its background. Given this,
+another KCF is used to learn the target area to estimate a new scale
+of the target. However, because of running more than a KCF on each
+frame, this method degrades its run-time performance (i.e., $\leq 50
 fps$). Our method is motivated by this idea -- the idea of deploying
 multiple KCFs to address the issues of single target tracking: scale
-and translation, but in a more efficient way. In particular, we use a
-multiple of KCFs, in an order of maximizing run-time performance and
-accuracy, instead of running them all together on every frame. We
-deploy three KCFs in turn: \textit{target}+\textit{small background}
-translation filter ($R_{t}^{S}$), \textit{target-only} scale filter
-($R_{s}$) and \textit{target}+\textit{large background} translation
-filter ($R_{t}^{L}$). By doing so, we could address the scale change
-and estimate target's motion efficiently while maintaining or
+and translation, but in a more efficient way. Figure \ref{Workflows}
+illustrates the work-flow of the {\it E}nKCF. In particular, to
+maximize run-time performance and accuracy, instead of running them
+all together on every frame, we deploy three KCFs in turn:
+\textit{target}+\textit{small background} translation filter
+($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
+\textit{target}+\textit{large background} translation filter
+($R_{t}^{L}$). By doing so, our method aims at addressing a scale
+change and estimate target's motion efficiently while maintaining or
 increasing run-time performance. Figure \ref{fig:Filters} shows
 examples of the region of interest (ROI) associated with $R_{t}^{S}$,
-$R_{t}^{L}$, and $R_{s}$. Figure \ref{Workflows} illustrates the
-work-flow of the {\it E}nKCF.
+$R_{t}^{L}$, and $R_{s}$.
 \begin{figure}[!t]
@@
 \end{tabular}
-\caption{The workflow of {\it E}nKCF tracking algorithm. We show the
+\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
   first seven frames of tracking where the first frame is the
@@
 \end{figure}
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=1.0\textwidth]{figures/Filters_Details.pdf}
+\caption{Examples of three filters; the translation filter,
+  \textit{target+small background}, the scale filter,
+  \textit{target-only} and another translation filter,
+  \textit{target+large background}, and their Hanning window and
+  expected Gaussian response.}
+\label{fig:Filters}
+\end{figure}
 The contribution of this study is a novel, single-target tracking
-algorithm running in a very high-speed, $\geq 300$ fps. In particular,
-the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCFs, in
-turn, to more effectively address the scale variance and the dynamic
-maneuver of a target while preserving run-time performance as high as
-possible. To minimize any potential performance gap from transiting
-one KCF to another, we use a Bayes filter.
+algorithm running in a very high-speed, $\geq 300$ fps that deploys an
+ensemble of KCFs, in turn, to more effectively address the scale
+variance and the dynamic maneuver of a target while preserving
+run-time performance as high as possible. To minimize any potential
+performance gap from transiting one KCF to another, we use a Bayes
+filter.
 
@@
 %---------------------------------------------------------------------- 
-In this paper, we propose a novel way of utilizing a multiple of the KCFs
-\cite{henriques2015high} to effectively handle scale variations and
-dynamic maneuvers of a target. To maintain or improve the run-time
+In this paper, we propose a novel way of utilizing a multiple of the
+KCFs \cite{henriques2015high} to effectively handle scale variations
+and dynamic maneuvers of a target. To maintain or improve the run-time
 performance of the original KCF (e.g., $\ge$ 300), we deploy three
-KCFs in turn, not on the same image frame together. Each of these KCFs
-is designed to address specific challenges, i.e., scale and
-translation. By alternating their deployments, our algorithm will
-improve the performance of the original KCF while preserving the
-efficient nature and small-footprint of the KCF computation.
+KCFs in turn, instead of applying them on the same image frame
+together. Each of these KCFs is designed to address specific
+challenges, i.e., scale and translation. By alternating their
+deployments, our algorithm will improve the performance of the
+original KCF while preserving the efficient nature and small-footprint
+of the KCF computation.
 
@@
 \DontPrintSemicolon
-\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, scale filter frequency $n = 5$,}
+\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
 \KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
@@
 correlation filter should focus on the target itself to estimate the
-right scale of the target. Figure \ref{fig:Filters} shows examples of
-the image, sub-regions covered by each of these filters.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=1.0\textwidth]{figures/Filters_Details.pdf}
-\caption{Examples of three filters; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
-\label{fig:Filters}
-\end{figure}
+right scale of the target.
 
@@
 do not use those multiple KCFs together at every frame, but
-alternatively at every $k$ frame (e.g., $k=3$). It intuitively makes
-sense to alternatively use multiple KCFs with different purposes
-because the appearance of a target does not change drastically over
-consecutive image frames. For most case, even it looks the appearance
-changes, learning a correlation filter over consecutive frames would
-not be much different from the one learned using the image few or $k$
-frames later. Figure \ref{fig:Filters_Comparison} shows examples
-supporting this observation.
+alternatively at every $k$ frame. It intuitively makes sense to
+alternatively use multiple KCFs with different purposes because the
+appearance of a target does not change drastically over consecutive
+image frames. For most case, even it looks the appearance changes,
+learning a correlation filter over consecutive frames would not be
+much different from the one learned using the image few or $k$ frames
+later. Figure \ref{fig:Filters_Comparison} shows examples supporting
+this observation.
 
@@
 \includegraphics[width=1\textwidth]{figures/LearnedFiltersComparison2.pdf}
-\caption{This figure shows that there is marginal difference among the
-  scale filters learned either at every frame or at every 5
+\caption{This figure shows that there is a marginal difference among
+  the scale filters learned either at every frame or at every 5
   frames. The sub-figures at the the left show the scale filters
-  trained at every frame and those at the right show the scale
-  filters trained at every 5 frames.}
+  trained at every frame and those at the right show the scale filters
+  trained at every 5 frames.}
 \label{fig:Filters_Comparison}
@@
 
+The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
 The order of running these three KCFs is important because each of
@@
 \textit{target+large background} translation filter, $R_{t}^{L}$, is
-applied to the $i$th and $i+1$th image frame, another translation
-filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image frame,
-and then the scale filter, $R_{s}$ is applied to the $i+4$the
+applied to the $i$th and $i+1$th image frames, another translation
+filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image
+frames, and then the scale filter, $R_{s}$ is applied to the $i+4$the
 image. This order repeats until the end of the image frames. The
@@
 designed to addresses the drawback of $R_{t}^{L}$ that it may learn
-noisy shape features due to its large search area. Figure
-\ref{Workflows} illustrates the work-flow of the proposed algorithm
-and the algorithm \ref{alg:MKCF} shows the pseudo-code of {\it
-  E}nKCF. In the following section, we will briefly describe the
-features of the KCF related to this work.
+noisy shape features due to its large search area. In what follows, we
+will briefly describe the parts of the KCF related to this work.
 
-\subsection{Kernelized Correlation Filter} \label{sec:kcf}
-The Kernelized Correlation Filter is a well, known single target
-tracking method and its work flow has been detailed in other papers
+\textbf{Kernelized Correlation Filter} The Kernelized Correlation
+Filter is a well, known single target tracking method and its work
+flow has been detailed in other papers
 \cite{henriques2012exploiting,henriques2015high}. This section briefly
@@
 discriminative domain. The circulant matrix is then formed by applying
-cyclic shifts on the kernelized $x$. Such kernelization operation maintains 
-O($nlog(n)$) complexity unlike other kernel algorithms leading to O($n^{2}$) or even higher 
-complexities.
+cyclic shifts on the kernelized $x$. Such kernelization operation
+maintains O($nlog(n)$) complexity unlike other kernel algorithms
+leading to O($n^{2}$) or even higher complexities.
 
@@
 
-\subsection{Particle Filter for Smoothing Transition among KCFs} \label{sc:PF}
-As explained earlier, the {\it E}nKCF updates a target's translation
-at every other $k$ frames, particularly for estimating the target's
+\textbf{Particle Filter for Smoothing Transition among KCFs} As
+explained earlier, the {\it E}nKCF updates a target's translation at
+every other $k$ frames, particularly for estimating the target's
 scale. Although the strategy of updating every other $k$th frames will
@@
 tracking algorithms by the \textit{Precision} and
-\textit{Success\:Rate} metrics. For the precision, we rank the trackers
-based on the precision numbers at 20 pixels whereas in the success
-rate plots, trackers are ranked based on area under curve (AUC)
-scores. The tracking algorithms used for the comparison include ones
-in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
+\textit{Success\:Rate} metrics. For the precision, we rank the
+trackers based on the precision numbers at 20 pixels whereas in the
+success rate plots, trackers are ranked based on area under curve
+(AUC) scores. The tracking algorithms used for the comparison include
+ones in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high},
+CSK \cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
 MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
@@
 that are slow, but a bit better in precision. For example, for AUC,
-{\it E}nKCF outperformed Struct and DSST by $5\%$ and $10\%$ while
+{\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while
 running at more than $10$ and $30$ times faster.
@@
 \end{center}
-\caption{Evalutions of the different combinations of the proposed KCFs in UAV123 dataset.
+\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
 We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.}

### 2017-06-13 bmvc_review.tex
Table Updated

@@
 \begin{table}
+\small
 \begin{center}
@@
 \hline\hline
-Precision ($20$px) & \textbf{54.5} & 48.09 & & & &\\
-Success Rate ($50\%$) & \textbf{40.2} & 36.04 & & & & \\
-Frame Per Second & \textbf{416} & 370 & & & & \\
+Precision ($20$px) & \textbf{54.5} & 48.09 & 52.50 & 51.88 & 51.29 &\\
+Success Rate ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 35.12 & 34.42 & \\
+Frame Per Second & \textbf{416} & 370 & 343 & 367 & 490 & \\
 \hline

### 2017-06-14 bmvc_review.tex
Table Updated

--- 2017-06-13 bmvc_review.tex
@@
 \hline\hline
-Precision ($20$px) & \textbf{54.5} & 48.09 & & & &\\
-Success Rate ($50\%$) & \textbf{40.2} & 36.04 & & & & \\
-Frame Per Second & \textbf{416} & 370 & & & & \\
+Precision ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 51.88 & 51.29 & 52.14 \\
+Success Rate ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 35.12 & 34.42 & 38.51\\
+Frame Per Second & \textbf{416} & 370 & 425 & 367 & 490 & 151 \\
 \hline
@@
 \caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
-We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.}
+We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
+$R_{t}^{S}$ and $R_{s}$ are used as proposed in
+\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used to perform realistic comparison.
+In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
 \end{table}

### 2017-06-14 bmvc_review.tex
Table Updated

@@
 \begin{table}
-\small
+\smaller
 \begin{center}
@@
 \hline
-Metric/Method & $R_{t}^{L}$+$R_{t}^{S}$+$R_{s}$ ({\it E}nKCF) & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & LCT \cite{ma2015long}\\
+Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{S}$+$R_{s}$) & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
 \hline\hline
-Precision ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 51.88 & 51.29 & 52.14 \\
-Success Rate ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 35.12 & 34.42 & 38.51\\
-Frame Per Second & \textbf{416} & 370 & 425 & 367 & 490 & 151 \\
+Pr. ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 52.14 & &  \\
+SR ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 38.51 & & \\
+FPS & 416 & 370 & 425  & 151 & & \\
 \hline
@@
 We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
-$R_{t}^{S}$ and $R_{s}$ are used as proposed in
-\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used to perform realistic comparison.
+The KCFs highlighted in LCT are applied in every frame as proposed in
+\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison.
 In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
 \end{table}
+
+%\begin{table}
+%\smaller
+%\begin{center}
+%\begin{tabular*}{\textwidth}{|l|c|c|c|c|c|c|c|c|}
+%\hline
+% & $R_{t}^{L}$+$R_{t}^{S}$+$R_{s}$ ({\it E}nKCF) & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & LCT  $R_{t}^{S}$+$R_{s}$ & LCT  $R_{t}^{L}$+$R_{s}$ & LCT  $R_{t}^{L}+R_{t}^{S}$+$R_{s}$\\
+%\hline\hline
+%Pr. ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 51.88 & 51.29 & 52.14 & &  \\
+%SR ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 35.12 & 34.42 & 38.51 & & \\
+%FPS & 416 & 370 & 425 & 367 & \textbf{490} & 151 & & \\
+%\hline
+%\end{tabular*}
+%\end{center}
+%\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
+We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
+$R_{t}^{S}$ and $R_{s}$ are used as proposed in
+%\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used to perform realistic comparison.
+In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
+%\end{table}
 

### 2017-06-14 bmvc_review.tex
Comments to table 1 added - figures squeezed

@@
 
-\textbf{Performance on OTB100 Dataset} Figure \ref{fig:OTB100_DATASET}
+We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
+By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
+run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
+$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
+tracker and run $R_{t}^{L}$, $R_{t}^{s}$, and $R_{s}$ in every frame in the given order. Interestingly, running two complementary translation filter results in significant improvement
+at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
+high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
+\begin{table}[!h]
+\smaller
+\begin{center}
+\begin{tabular}{|l|c|c|c|c|c|c|}
+\hline
+Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{S}$+$R_{s}$) & LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
+\hline\hline
+Pr. ($20$px) & \color{red} 53.9 & 48.09 & 52.50 & & 52.14 & \textbf{58.16} \\
+SR ($50\%$) & \color{red} 40.2 & 36.04 & 37.85 & & 38.51 & \textbf{41.58} \\
+FPS & \color{red} 416 & 370 & \textbf{425}  & & 151 & 99 \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
+The 2nd method removes $R_{t}^{S}$ (fig.~\ref{Workflows}) and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$.
+We decouple the re-detection module of the LCT tracker and particle filter from all the methods as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
+The KCFs highlighted in LCT are applied in every frame in the listed order as proposed in
+\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison.
+In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
+\label{table:Comparison_to_LCT}
+\end{table}
+
+\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
 shows the results on the OTB100 dataset. Same as with UAV123 dataset,
@@
 \begin{tabular}{ccc}
-\bmvaHangBox{\includegraphics[width=4.80cm]{./figures/Precision_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_OTB100.eps}}
+\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_OTB100.eps}}\\
 \end{tabular}
@@
 \end{figure}
-\begin{figure}[!h]
-\centering
-\begin{tabular}{ccc}
-\bmvaHangBox{\includegraphics[width=4.80cm]{./figures/Precision_OTB100.eps}}
-\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_OTB100.eps}}\\
-\end{tabular}
-\caption{Comparison of {\it E}nKCF's performance with those of the
-  state-of-the-art tracking algorithms on the OTB100 dataset.}
-\label{fig:OTB100_DATASET}
-\end{figure}
-
-\begin{table}
-\smaller
-\begin{center}
-\begin{tabular}{|l|c|c|c|c|c|c|}
-\hline
-Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{S}$+$R_{s}$) & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
-\hline\hline
-Pr. ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 52.14 & &  \\
-SR ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 38.51 & & \\
-FPS & 416 & 370 & 425  & 151 & & \\
-\hline
-\end{tabular}
-\end{center}
-\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
-We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
-The KCFs highlighted in LCT are applied in every frame as proposed in
-\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison.
-In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
-\end{table}
+%\begin{figure}[!h]
+%\centering
+%\begin{tabular}{ccc}
+%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
+%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
+%\end{tabular}
+%\caption{Comparison of {\it E}nKCF's performance with those of the
+%  state-of-the-art tracking algorithms on the OTB100 dataset.}
+%\label{fig:OTB100_DATASET}
+%\end{figure}
 
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Precision_UAV123_10fps.eps}}
-\bmvaHangBox{\includegraphics[width=5.30cm]{./figures/Success_UAV123_10fps.eps}}\\
+\bmvaHangBox{\includegraphics[width=4.30cm]{./figures/Precision_UAV123_10fps.eps}}
+\bmvaHangBox{\includegraphics[width=4.30cm]{./figures/Success_UAV123_10fps.eps}}\\
 \end{tabular}

### 2017-06-14 bmvc_review.tex
Table Finished - Text Updated

@@
 $R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
-tracker and run $R_{t}^{L}$, $R_{t}^{s}$, and $R_{s}$ in every frame in the given order. Interestingly, running two complementary translation filter results in significant improvement
+tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
+translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
 at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
@@
 \hline
-Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{S}$+$R_{s}$) & LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
+Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{S}$+$R_{s}$) & {\it m}LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
 \hline\hline
-Pr. ($20$px) & \color{red} 53.9 & 48.09 & 52.50 & & 52.14 & \textbf{58.16} \\
-SR ($50\%$) & \color{red} 40.2 & 36.04 & 37.85 & & 38.51 & \textbf{41.58} \\
-FPS & \color{red} 416 & 370 & \textbf{425}  & & 151 & 99 \\
+Pr. ($20$px) & 53.9 & 48.09 & 52.50 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
+SR ($50\%$) & \color{red} 40.2 & 36.04 & 37.85 & 39.89 & 38.51 & \textbf{41.58} \\
+FPS & \color{red} 416 & 370 & \textbf{425}  & 135 & 151 & 99 \\
 \hline

### 2017-06-14 C++_Implementation/detector/src/kcftracker.cpp
Camera Motion Model Removal Step Added

@@ -1153,3 +1153,4 @@ float KCFTracker::computePSR(const Mat &correlation_mat)
 
     return (max_val - mean.val[0]) / stddev.val[0];     //Compute PSR
 }
+

### 2017-06-14 C++_Implementation/main/include/findHom.hpp

@@ -1,0 +1,5 @@
+#include <iostream>
+#include <opencv2/core/core.hpp>
+#include <opencv2/opencv.hpp>
+
+cv::Mat cameraMotionModel(cv::Mat frame_reference,cv::Mat frame_test);

### 2017-06-14 C++_Implementation/main/src/findHom.cpp

@@ -1,0 +1,82 @@
+#include <stdio.h>
+#include <iostream>
+#include "opencv2/core.hpp"
+#include "opencv2/features2d.hpp"
+#include "opencv2/highgui.hpp"
+#include "opencv2/calib3d.hpp"
+#include "opencv2/xfeatures2d.hpp"
+#include <opencv2/imgcodecs.hpp>
+#include <opencv2/imgproc.hpp>
+
+using namespace cv;
+using namespace cv::xfeatures2d;
+
+cv::Mat cameraMotionModel(cv::Mat frame_r, cv::Mat frame_t){
+
+  // Convert to GrayScale Imagery
+  cv::cvtColor(frame_r,frame_r, CV_RGB2GRAY);
+  cv::cvtColor(frame_t,frame_t, CV_RGB2GRAY);
+
+  //-- Step 1: Detect the keypoints using SURF Detector
+  int minHessian = 800;
+
+  // Instantiate SURF Object
+  Ptr<Feature2D> features = SURF::create(minHessian);
+
+  //-- Step 2: Calculate descriptors (feature vectors)
+  std::vector<KeyPoint> keypoints_reference, keypoints_test;
+  cv::Mat descriptors_reference, descriptors_test;
+  features->detect(frame_r, keypoints_reference);
+  features->detect(frame_t, keypoints_test);
+  
+  //-- Draw only "good" matches (i.e. whose distance is less than 3*min_dist )
+  std::vector< DMatch > good_matches;
+  features->compute( frame_r, keypoints_reference, descriptors_reference);
+  features->compute( frame_t, keypoints_test, descriptors_test);
+
+  //-- Step 3: Matching descriptor vectors using FLANN matcher
+  FlannBasedMatcher matcher;
+  std::vector<DMatch> matches;
+  matcher.match( descriptors_reference, descriptors_test, matches);
+
+  double max_dist = 0; double min_dist = 100;
+  //-- Quick calculation of max and min distances between keypoints
+  for( int i = 0; i < descriptors_reference.rows; i++ )
+  { 
+    double dist = matches[i].distance;
+    if( dist < min_dist ) min_dist = dist;
+    if( dist > max_dist ) max_dist = dist;
+  }
+
+  // Find the Good Matches
+  for( int i = 0; i < descriptors_reference.rows; i++ )
+  { 
+     if(matches[i].distance<3*min_dist)
+     { 
[…]

### 2017-06-14 C++_Implementation/main/src/runtracker.cpp

@@ -5,6 +5,7 @@
 #include <algorithm>
 #include "kcftracker.hpp"
 #include "Filter_Definition.h"
+#include "../include/findHom.hpp"
 #include <vector>
 #include <math.h>
 #include <string>
@@ -338,6 +339,10 @@ char ch;
       }
       else {
         /// -------------------- UPDATE STEP --------------------------------------------
+	/// Apply Camera Motion Model	
+	cv::Mat homography = cameraMotionModel(frame_old,frame);
+        frame_old = frame.clone();
+
 	/// Perform PF Transition
 	State_Mean[0] = 0; State_Mean[1] = 0;
         PfTracker.particle_transition();	
@@ -355,14 +360,17 @@ char ch;
 	tic();
 	float PSR;
 	if ((nFrames % 5 > 0) && (nFrames % 5 < 3)){
-           result = tracker.updateWROI(frame);  // Estimate Translation using Wider ROI
+  	   tracker._roi = tracker.applyHomography(homography, frame, tracker._roi);      
+	   result = tracker.updateWROI(frame);  // Estimate Translation using Wider ROI
            PSR = tracker.PSR_wroi;
 	}
         if ((nFrames % 5 == 3) || (nFrames % 5 == 4)){
-           result = tracker.update(frame);      // Estimate Translation using Smaller ROI
+ 	   tracker._roi_w = tracker.applyHomography(homography, frame, tracker._roi_w);          
+	   result = tracker.update(frame);      // Estimate Translation using Smaller ROI
            PSR = tracker.PSR_sroi;
 	}
 	if (nFrames % 5 == 0){
+           tracker._roi_scale = tracker.applyHomography(homography, frame, tracker._roi_scale);
            result = tracker.updateScale(frame); // Estimate Scale using Scale Filter
            PSR = tracker.PSR_scale;
 	}
@@ -374,8 +382,8 @@ char ch;
         // Update Particle Filter Weights
 	Obs[0] = result.x + result.width/2.0;
 	Obs[1] = result.y + result.height/2.0;
-	// PfTracker.particle_weights(Obs); 
-	PfTracker.particle_weights_cfMap(tracker.cfResponse, tracker.gROI);
+	PfTracker.particle_weights(Obs); 
+	// PfTracker.particle_weights_cfMap(tracker.cfResponse, tracker.gROI);
 
 	// Perform Re-Sampling
 	PfTracker.particle_resampling();

### 2017-06-15 bmvc_review.tex
Particle Filter Comparison Added

@@
 
+Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter and without particle filter.
+To do so, we use the 50 video sequences with no abrupt camera motion as annotated by the authors.
+Also, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs to further evaluate the robustness of particle filter.
+In this settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.
+In conclusion, the proposed particle filter can be a useful tool in {\it E}nKCF framework with the removal of global camera motion.
+
 \textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
@@
 \caption{Comparison of {\it E}nKCF's performance with those of the
-  state-of-the-art tracking algorithms on the UAV123 dataset.}
+  state-of-the-art tracking algorithms on the UAV123 and OTB100 datasets.}
 \label{fig:UAV123_DATASET}
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=4.30cm]{./figures/Precision_UAV123_10fps.eps}}
-\bmvaHangBox{\includegraphics[width=4.30cm]{./figures/Success_UAV123_10fps.eps}}\\
+\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_UAV123_10fps.eps}}
+\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_UAV123_10fps.eps}}\\
 \end{tabular}

### 2017-06-15 bmvc_review.tex
Table Updated

@@
 \usepackage{mathtools} % mathtools builds on and extends amsmath package
-% \usepackage{algorithm}		% http://ctan.org/pkg/algorithms
 \usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
@@
 the appearance model of a target on the fly and 2) run as fast on a
-typical desktop as up to $300-400$ fps so that it could run, at least,
+typical desktop as up to $300-450$ fps so that it could run, at least,
 faster than 30 fps when it is deployed on a low-end, embedded
@@
 \begin{figure*}[!t]
+\centering
 \includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
@@
 whereas UAV123 dataset contains aerial footages of 123 objects. We
-aims at developing an object tracking algorithm that ``efficiently''
+aim at developing an object tracking algorithm that ``efficiently''
 runs on an embedded system, a drone, for example, in ``high speed,''
@@
 $0.010$. For the kernel of the Gaussian neighboring function, we
-empirically found the optimal values of $\alpha$ as $0.6$, $0.4$, and
-$0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate
-as $0.12$ for $R_{t}^{L}$. For our particle filter implementation, we
+empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
+$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
+threshold, $T_{R_{s}}$, to 4. For our particle filter implementation, we
 empirically set the number of particles to $1000$ to balance the
@@
 the proposed algorithm with those of the state-of-the-art high speed
-tracking algorithms by the \textit{Precision} and
-\textit{Success\:Rate} metrics. For the precision, we rank the
-trackers based on the precision numbers at 20 pixels whereas in the
-success rate plots, trackers are ranked based on area under curve
+tracking algorithms by the \textit{Precision} and \textit{Success\:Rate} metrics. 
+For the precision, we rank the trackers based on the precision numbers at 20 pixels 
+whereas in the success rate plots, trackers are ranked based on area under curve
 (AUC) scores. The tracking algorithms used for the comparison include
@@
 metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
-than ours in accuracy, but 10-20\% slower than ours. For the scale
+than ours in accuracy, but 10-20 times slower than ours. For the scale
 adaptation, {\it E}nKCF did second best in terms of \textit{area under
@@
 running at more than $10$ and $30$ times faster.
+\begin{figure}[!h]
+\raggedright
+\begin{tabular}{ccc}
+\tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
+\bmvaHangBox{\includegraphics[width=2.90cm]{./figures/Precision_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=3.35cm]{./figures/Success_UAV123.eps}}
+\bmvaHangBox{\includegraphics[width=2.90cm]{./figures/Precision_OTB100.eps}}
+\bmvaHangBox{\includegraphics[width=3.35cm]{./figures/Success_OTB100.eps}}\\
+\end{tabular}
+\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
+\label{fig:UAV123_DATASET}
+\end{figure}
 
@@
 \begin{center}
-\begin{tabular}{|l|c|c|c|c|c|c|}
+\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|}
 \hline
-Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{S}$+$R_{s}$) & {\it m}LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT($R_{t}^{L}$+$R_{s}$) & LCT($R_{t}^{S}$+$R_{s}$) & {\it m}LCT($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
 \hline\hline
-Pr. ($20$px) & 53.9 & 48.09 & 52.50 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
-SR ($50\%$) & \color{red} 40.2 & 36.04 & 37.85 & 39.89 & 38.51 & \textbf{41.58} \\
-FPS & \color{red} 416 & 370 & \textbf{425}  & 135 & 151 & 99 \\
+Pr. ($20$px) & 53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
+SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 39.89 & 38.51 & \textbf{41.58} \\
+FPS & \color{red} 416 & 412 & 370 & \textbf{425}  & 135 & 151 & 99 \\
 \hline
-\end{tabular}
+\end{tabular}}
 \end{center}
 \caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
-The 2nd method removes $R_{t}^{S}$ (fig.~\ref{Workflows}) and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$.
+The 2nd method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}).
+The 3th method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$.
 We decouple the re-detection module of the LCT tracker and particle filter from all the methods as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
@@
 \cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison.
-In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
+In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\approx30$fps).}
 \label{table:Comparison_to_LCT}
@@
 another low-speed scale adaptive SAMF tracker.
-\begin{figure}[!h]
-\centering
-\begin{tabular}{ccc}
-\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_OTB100.eps}}
-\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_OTB100.eps}}\\
-\end{tabular}
-\caption{Comparison of {\it E}nKCF's performance with those of the
-  state-of-the-art tracking algorithms on the UAV123 and OTB100 datasets.}
-\label{fig:UAV123_DATASET}
-\end{figure}
 %\begin{figure}[!h]

### 2017-06-15 bmvc_review.tex
Figures Updated

@@
 \tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
-\bmvaHangBox{\includegraphics[width=2.90cm]{./figures/Precision_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=3.35cm]{./figures/Success_UAV123.eps}}
-\bmvaHangBox{\includegraphics[width=2.90cm]{./figures/Precision_OTB100.eps}}
-\bmvaHangBox{\includegraphics[width=3.35cm]{./figures/Success_OTB100.eps}}\\
+\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
+\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
+\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
+\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
 \end{tabular}
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_UAV123_10fps.eps}}
-\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Success_UAV123_10fps.eps}}\\
+\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123_10fps.eps}}
+\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123_10fps.eps}}\\
 \end{tabular}

### 2017-06-16 bmvc_review.tex
Table Updated

@@
 \hline
-Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT($R_{t}^{L}$+$R_{s}$) & LCT($R_{t}^{S}$+$R_{s}$) & {\it m}LCT($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
 \hline\hline
@@
 \caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
-The 2nd method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}).
-The 3th method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$.
-We decouple the re-detection module of the LCT tracker and particle filter from all the methods as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
-The KCFs highlighted in LCT are applied in every frame in the listed order as proposed in
-\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison.
-In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\approx30$fps).}
+The $2^{nd}$ method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}).
+The $3^{th}$ method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one removes $R_{t}^{L}$.
+The methods denoted with "*" run the filters in every frame in the listed order.
+The LCT tracker \cite{ma2015long} runs a translation and scale filter in every frame (similar to $6^{th}$ method) and couples a re-detection method to perform long-term tracking at $\approx30$ fps.}
 \label{table:Comparison_to_LCT}

### 2017-06-16 bmvc_review.tex
Table Colors Added

@@
 \begin{center}
+\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
 \resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|}
@@
 \hline\hline
-Pr. ($20$px) & 53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
-SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 39.89 & 38.51 & \textbf{41.58} \\
-FPS & \color{red} 416 & 412 & 370 & \textbf{425}  & 135 & 151 & 99 \\
+Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
+SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
+FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425  & 135 & 151 & 99 \\
 \hline

### 2017-06-16 bmvc_review.tex
Table Updated with R_S and R_L

@@
 \color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
-\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|}
+\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
 \hline
-Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
 \hline\hline
-Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
-SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
-FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425  & 135 & 151 & 99 \\
+Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
+SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
+FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
 \hline

### 2017-06-16 bmvc_review.tex
Table Updated with R_S and R_L
Revised the draft between experiments and conclusion.

@@
 The OTB100 dataset is comprised of the videos about 100 objects
-whereas UAV123 dataset contains aerial footages of 123 objects. We
-aim at developing an object tracking algorithm that ``efficiently''
-runs on an embedded system, a drone, for example, in ``high speed,''
-$\ge 300$ fps. Given this, we believe that the UAV123 data is a good
-fit in evaluating the performance of the proposed algorithm. In
-addition, in the UAV123 data, there are many challenging, realistic
-scenes, e.g., abrupt scale/illumination changes. Although we are
-primarily interested in developing an algorithm for mobile, embedded
-robotic applications, it is also important to compare the performance
-of the proposed algorithm with those of the state-of-the-art in a
-nominal dataset for comparison. To this end, we chose the OTB100 data
-that contains the videos recorded from smart phones and typical
-cameras in perspective view. Lastly, we tested the proposed algorithm
-on a temporally down-sampled version of the UAV123 dataset, called
+whereas UAV123 dataset contains aerial footages of 123 objects. We aim
+at developing an object tracking algorithm that ``efficiently'' runs
+on an embedded system, a drone, for example, in ``high speed,'' $\ge
+300$ fps. Given this, we believe that the UAV123 data is a good fit in
+evaluating the performance of the proposed algorithm. In addition, in
+the UAV123 data, there are many challenging, realistic scenes, e.g.,
+abrupt scale/illumination changes. Although we are primarily
+interested in developing an algorithm for mobile, embedded robotic
+applications, it is also important to compare the performance of the
+proposed algorithm with those of the state-of-the-art in a nominal
+dataset for comparison. To this end, we chose the OTB100 data that
+contains the videos recorded from smart phones and typical cameras in
+perspective view. Lastly, we tested the proposed algorithm on a
+temporally down-sampled version of the UAV123 dataset, called
 UAV123$\_$10fps dataset. What we would like to see from this
@@
 empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
-$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
-threshold, $T_{R_{s}}$, to 4. For our particle filter implementation, we
-empirically set the number of particles to $1000$ to balance the
-run-time performance and accuracy. To keep the level of variance among
-the particles reasonable, we performed the re-sampling only when the
+$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
+filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
+ratio. For our particle filter implementation, we empirically set the
+number of particles to $1000$ to balance the run-time performance and
+accuracy. To keep the level of variance among the particles
+reasonable, we performed the re-sampling only when the
 \textit{efficient number of samples} ($ \hat{N}_{eff} \approx
@@
 
-\textbf{Features Selections} As each of three KCFs in the {\it E}nKCF
-has different goals to accomplish, we used different features for each
-of them. In particular, the translation filter, $R_{t}^{L}$, uses both
-the fast Histograms of Oriented Gradients (fHoG)
-\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
-features to learn the background around the target more
-effectively. In fact we empirically found fHoG only didn't work well
-to cover the larger ROI. Another translation filter, $R_{t}^{S}$, used
-fHoG features only. The scale filter, $R_{s}$ used both fHoG and color
-features to learn the scale change more accurately.
+\textbf{Features Selections} We used different features for each of
+three KCFs as each of them has different goals to accomplish. In
+particular, the translation filter, $R_{t}^{L}$, uses both the fast
+Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
+and color-naming \cite{van2009learning} features to learn the
+background around the target more effectively. However we found,
+through experiments, that only fHoG didn't work well to cover a larger
+ROI. In a same way, we found that another translation filter,
+$R_{t}^{S}$, worked well when it used fHoG features only and the scale
+filter, $R_{s}$ did when it used both fHoG and color features.
 
-\textbf{Performance on UAV123 Dataset} We compared the performance of
-the proposed algorithm with those of the state-of-the-art high speed
-tracking algorithms by the \textit{Precision} and \textit{Success\:Rate} metrics. 
-For the precision, we rank the trackers based on the precision numbers at 20 pixels 
-whereas in the success rate plots, trackers are ranked based on area under curve
-(AUC) scores. The tracking algorithms used for the comparison include
-ones in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high},
-CSK \cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
+\textbf{Performance on UAV123 Dataset} We compared, using the
+precision and success rate metrics, the performance of the proposed
+algorithm with those of the state-of-the-art high speed tracking
+algorithms. For the precision, we rank the trackers based on the
+precision numbers at 20 pixels whereas in the success rate plots,
+trackers are ranked based on area under curve (AUC) scores. The
+tracking algorithms under the comparison include ones in high-speed
+($\geq$300 fps): KCF\cite{henriques2015high}, CSK
+\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
 MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
-lower-speed ($\geq$50), i.e., SAMF\cite{li2014scale},
+lower-speed ($\geq$50): SAMF\cite{li2014scale},
 DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
-MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
+MUSTER \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
 \cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
 results on the UAV123 dataset. {\it E}nKCF outperformed most of the
-high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
-metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
-than ours in accuracy, but 10-20 times slower than ours. For the scale
-adaptation, {\it E}nKCF did second best in terms of \textit{area under
-  curve} (AUC) value for the success rate plot. It outperformed other
-tracking methods in high-speed by about $20\%$-$25\%$ in AUC
-metric. In addition, it performed even better than those algorithms
-that are slow, but a bit better in precision. For example, for AUC,
-{\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while
-running at more than $10$ and $30$ times faster.
+high-speed tracking methods by $3\%$-$15\%$ in 20 pixels
+precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
+better than ours in accuracy, but 10-20 times slower. For the scale
+adaptation, {\it E}nKCF did second best in terms of AUC for the
+success rate plot. It outperformed other tracking methods in
+high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
+even better than those algorithms that are slow, but a slightly better
+in precision. For example, for AUC, {\it E}nKCF outperformed Struck
+and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
+times faster.
 \begin{figure}[!h]
@@
 
-We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
-By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
-run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
-$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
-tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
-translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
-at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
-high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
+{\it Burak: Remove LCT part!}
+
+We also compare the proposed {\it E}nKCF tracker to the LCT
+\cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}.  By
+using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
+we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
+$R_{t}^{S}$ with similar run-time performance. On the other hand, we
+employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as
+we run filters in every frame. Running another filter, $R_{t}^{L}$ or
+$R_{t}^{S}$, in the {\it E}nKCF framework not only gives us
+significantly higher run-time performance but also higher
+accuracy. Finally, we modify the LCT tracker ({\it m}LCT) and run
+$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given
+order. $R_{t}^{S}$ uses the translation estimation given by
+$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
+translation estimation given by $R_{t}^{S}$ to update
+scale. Interestingly, running two complementary translation filter
+results in significant improvement at the cost of decreased run-time
+performance. In conclusion, running two complementary translation
+filter and a scale filter in the {\it E}nKCF framework not only
+provides high speed but also more accurate tracker than the baseline
+methods having one translation and one scale filter.
 \begin{table}[!h]
@@
 \hline
-Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
 \hline\hline
@@
 \end{center}
-\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
-The $2^{nd}$ method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}).
-The $3^{th}$ method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one removes $R_{t}^{L}$.
-The methods denoted with "*" run the filters in every frame in the listed order.
-The LCT tracker \cite{ma2015long} runs a translation and scale filter in every frame (similar to $6^{th}$ method) and couples a re-detection method to perform long-term tracking at $\approx30$ fps.}
+\caption{Evaluations of the different combinations of the proposed
+  KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of
+  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
+  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
+  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
+  the filters in every frame in the listed order. The LCT tracker
+  \cite{ma2015long} runs a translation and scale filter in every frame
+  (similar to $6^{th}$ method) and couples a re-detection method to
+  perform long-term tracking at $\approx30$ fps.}
 \label{table:Comparison_to_LCT}

### 2017-06-16 bmvc_review.tex
Some More Cleaning

@@
 
-{\it Burak: Remove LCT part!}
-
-We also compare the proposed {\it E}nKCF tracker to the LCT
-\cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}.  By
-using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
+We also evaluate the performances of the different combinations of the
+proposed correlation filters and compare them to the {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
+By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
 we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
 $R_{t}^{S}$ with similar run-time performance. On the other hand, we
-employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as
-we run filters in every frame. Running another filter, $R_{t}^{L}$ or
-$R_{t}^{S}$, in the {\it E}nKCF framework not only gives us
-significantly higher run-time performance but also higher
-accuracy. Finally, we modify the LCT tracker ({\it m}LCT) and run
-$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given
-order. $R_{t}^{S}$ uses the translation estimation given by
-$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
-translation estimation given by $R_{t}^{S}$ to update
+employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ and run them in every frame in a similar way
+to the multiple correlation filter framework of the LCT tracker \cite{ma2015long}. Running another filter, $R_{t}^{L}$ or
+$R_{t}^{S}$, in the {\it E}nKCF framework not only boosts run-time performance but also increases
+accuracy. Finally, we run  $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every frame in the in the given order. 
+$R_{t}^{S}$ uses the translation estimation given by
+$R_{t}^{L}$ to update translation and finally $R_{s}$ uses the final
+translation estimation given by $R_{t}^{S}$ to update the
 scale. Interestingly, running two complementary translation filter

### 2017-06-16 bmvc_review.tex
Text Cleaned

@@
 
-We also evaluate the performances of the different combinations of the
-proposed correlation filters and compare them to the {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
+We also evaluate the performances of different combinations of the proposed correlation filters and 
+compare them to {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
 By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
@@
 \caption{Evaluations of the different combinations of the proposed
-  KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of
+  KCFs in UAV123 dataset. The particle filter is decoupled from all the methods for fair comparison. 
+  The $2^{nd}$ method swaps the order of
   $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
@@
 
-Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter and without particle filter.
-To do so, we use the 50 video sequences with no abrupt camera motion as annotated by the authors.
-Also, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs to further evaluate the robustness of particle filter.
-In this settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.
-In conclusion, the proposed particle filter can be a useful tool in {\it E}nKCF framework with the removal of global camera motion.
+Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter to the one without particle filter.
+To do so, we use 50 sequences labeled as no abrupt camera motion in the dataset.
+To evaluate the robustness of particle filter, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs.
+In these settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.
+In conclusion, with the removal of global camera motion, the integration of particle filter into the {\it E}nKCF as shown in fig.~\ref{Workflows} can further improve the results.
 

### 2017-06-16 bmvc_review.tex
More HyperParameters Added

@@
 learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
-$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
+$R_{t}^{S}$, and $R_{s}$ differently as $0.012$, $0.020$ and
 $0.010$. For the kernel of the Gaussian neighboring function, we
@@
 filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
-ratio. For our particle filter implementation, we empirically set the
+ratio. Finally, the padding size for the correlation filters is tuned to $3$ for $R_{t}^{L}$, $2$ for $R_{t}^{S}$, 
+and $1$ for $R_{s}$. For our particle filter implementation, we empirically set the
 number of particles to $1000$ to balance the run-time performance and
@@
 \begin{tabular}{ccc}
-\tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
+\tiny\:\:\:\:\:\:\textbf{UAV123}\hspace{.44\linewidth}\:\:\:\textbf{OTB100}\\
 \bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}

### 2017-06-16 bmvc_review.tex
More HyperParameters Added

@@
 
-As future work, we investigates a way of re-initializing a target when
+As future work, we investigate a way of re-initializing a target when
 the target is lost, due to occlusion, illumination change, drastic

### 2017-06-17 bmvc_review.tex
Final Results Update

@@
 learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
-$R_{t}^{S}$, and $R_{s}$ differently as $0.012$, $0.020$ and
+$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
 $0.010$. For the kernel of the Gaussian neighboring function, we
@@
 filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
-ratio. Finally, the padding size for the correlation filters is tuned to $3$ for $R_{t}^{L}$, $2$ for $R_{t}^{S}$, 
+ratio. Finally, the padding size for the correlation filters is tuned to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, 
 and $1$ for $R_{s}$. For our particle filter implementation, we empirically set the

### 2017-06-19 bmvc_review.tex
Revised the experimental section and went over the draft.

@@
 perspective view. Lastly, we tested the proposed algorithm on a
-temporally down-sampled version of the UAV123 dataset, called
-UAV123$\_$10fps dataset. What we would like to see from this
-experiment is to evaluate how robust the proposed algorithm is to
+temporally down-sampled version of the UAV123 dataset, we call it
+UAV123$\_$10fps dataset. What we would like to evaluate using this
+modified dataset is how robust the proposed algorithm is to the
 drastic motions of camera and targets.
@@
 \textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
-  E}nKCF is designed for addressing specific challenges in single,
-target tracking problem. Thus each of them should have different
-values for the optimal parameters. For instance, the primary task of
-the translation filter, $R_{t}^{L}$ is to estimate the translation of
-a target from the previous frame whereas the scale filter, $R_{s}$ and
+  E}nKCF is designed to address specific challenges in single, target
+tracking problem. Thus each of them should have different values for
+the optimal parameters. For instance, the primary task of the
+translation filter, $R_{t}^{L}$ is to estimate the translation of a
+target from the previous frame whereas the scale filter, $R_{s}$ and
 the estimated state of the particle filter are primarily used to
@@
 filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
-ratio. Finally, the padding size for the correlation filters is tuned to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, 
-and $1$ for $R_{s}$. For our particle filter implementation, we empirically set the
-number of particles to $1000$ to balance the run-time performance and
-accuracy. To keep the level of variance among the particles
+ratio. Finally, the padding size for the correlation filters is tuned
+to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
+$R_{s}$. For our particle filter implementation, we empirically set
+the number of particles to $1000$ to balance the run-time performance
+and accuracy. To keep the level of variance among the particles
 reasonable, we performed the re-sampling only when the
@@
 Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
-and color-naming \cite{van2009learning} features to learn the
-background around the target more effectively. However we found,
-through experiments, that only fHoG didn't work well to cover a larger
-ROI. In a same way, we found that another translation filter,
-$R_{t}^{S}$, worked well when it used fHoG features only and the scale
-filter, $R_{s}$ did when it used both fHoG and color features.
+and color-naming \cite{van2009learning} features to more effectively
+learn the background around the target. Through experiments, we found
+that only fHoG didn't work well to cover a larger ROI; another
+translation filter, $R_{t}^{S}$, worked well when it used fHoG
+features only; the scale filter, $R_{s}$ did when it used both fHoG
+and color features.
 
-\textbf{Performance on UAV123 Dataset} We compared, using the
-precision and success rate metrics, the performance of the proposed
+\textbf{Performance on UAV123 Dataset} We used the precision and
+success rate metrics to compare the performance of the proposed
 algorithm with those of the state-of-the-art high speed tracking
@@
 tracking algorithms under the comparison include ones in high-speed
-($\geq$300 fps): KCF\cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
-MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
-lower-speed ($\geq$50): SAMF\cite{li2014scale},
-DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
-MUSTER \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
+($\geq$300 fps): KCF \cite{henriques2015high}, CSK
+\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, and
+MOSSE \cite{bolme2010visual,henriques2015high} and ones in relatively
+lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
+\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
+\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
 \cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
 results on the UAV123 dataset. {\it E}nKCF outperformed most of the
-high-speed tracking methods by $3\%$-$15\%$ in 20 pixels
+high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
 precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
@@
 
-We also evaluate the performances of different combinations of the proposed correlation filters and 
-compare them to {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
-By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
-we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
-$R_{t}^{S}$ with similar run-time performance. On the other hand, we
-employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ and run them in every frame in a similar way
-to the multiple correlation filter framework of the LCT tracker \cite{ma2015long}. Running another filter, $R_{t}^{L}$ or
-$R_{t}^{S}$, in the {\it E}nKCF framework not only boosts run-time performance but also increases
-accuracy. Finally, we run  $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every frame in the in the given order. 
-$R_{t}^{S}$ uses the translation estimation given by
-$R_{t}^{L}$ to update translation and finally $R_{s}$ uses the final
+Table \ref{table:Comparison_to_LCT} presents the performance of
+different combinations of the proposed algorithm. In short, we
+empirically verified that \textit{E}nKCF is an optimal combination in
+terms of tracking accuracy and run-time performance. We could achieve
+4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$ at every
+frame, but this combination wills sacrifice run-time performance 317
+fps.  To be more specific, we employ $R_{s}$ and $R_{t}^{L}$ or
+$R_{t}^{S}$ to run them in every frame in a similar way to the
+multiple correlation filter framework of the LCT tracker
+\cite{ma2015long}. Running another filter, $R_{t}^{L}$ or $R_{t}^{S}$,
+in the {\it E}nKCF framework not only boosts run-time performance but
+also increases accuracy. Lastly, we run $R_{L}$, $R_{t}^{S}$ and
+$R_{s}$ in every frame.  $R_{t}^{S}$ uses the translation estimated by
+$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
 translation estimation given by $R_{t}^{S}$ to update the
@@
 results in significant improvement at the cost of decreased run-time
-performance. In conclusion, running two complementary translation
-filter and a scale filter in the {\it E}nKCF framework not only
-provides high speed but also more accurate tracker than the baseline
-methods having one translation and one scale filter.
+performance. In summary, running two (complementary) translation
+filters and a scale filter as {\it E}nKCF not only increases run-time
+performance but also offers more accurate tracker than the baseline
+method with one translation and one scale filter.
 \begin{table}[!h]
@@
 \end{center}
-\caption{Evaluations of the different combinations of the proposed
-  KCFs in UAV123 dataset. The particle filter is decoupled from all the methods for fair comparison. 
-  The $2^{nd}$ method swaps the order of
-  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
-  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
-  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
-  the filters in every frame in the listed order. The LCT tracker
-  \cite{ma2015long} runs a translation and scale filter in every frame
-  (similar to $6^{th}$ method) and couples a re-detection method to
-  perform long-term tracking at $\approx30$ fps.}
+\caption{Evaluations on different combinations of the KCFs for UAV123
+  dataset. We removed the particle filter from this experiment. The
+  $2^{nd}$ method fliped the way of deploying $R_{t}^{L}$ and
+  $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
+  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one
+  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} The methods
+  marked with "*" run the filters on every frame in the listed
+  order. The LCT tracker \cite{ma2015long} runs a translation and
+  scale filter in every frame (similar to the method at the $6^{th}$
+  column {\it Burak: Not in $7^{th}$?} and couples a re-detection
+  method to perform long-term tracking at $\approx30$ fps.}
 \label{table:Comparison_to_LCT}
@@
 
-Finally, on the $UAV123$ dataset, we compare the {\it E}nKCF with particle filter to the one without particle filter.
-To do so, we use 50 sequences labeled as no abrupt camera motion in the dataset.
-To evaluate the robustness of particle filter, we add noise, drawn from a uniform distribution ($[-20,20]$), to the translation estimations of the KCFs.
-In these settings, the {\it E}nKCF with particle filter achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it E}nKCF by $6.32\%$.
-In conclusion, with the removal of global camera motion, the integration of particle filter into the {\it E}nKCF as shown in fig.~\ref{Workflows} can further improve the results.
+For the $UAV123$ dataset, we also evaluated the performance of the
+{\it E}nKCF with and without the particle filter. In particular, we
+use 50 sequences labeled as no abrupt camera motion in the dataset. To
+evaluate the robustness of particle filter, we add noise, drawn from a
+uniform distribution ($[-20,20]$), to the translation estimations of
+the KCFs. In these settings, the {\it E}nKCF with particle filter
+achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it
+  E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
+  particle filter?} In summary, with the removal of global camera
+motion, the integration of particle filter into the {\it E}nKCF as
+shown in fig.~\ref{Workflows} further improved the results.
 

### 2017-06-20 bmvc_review.tex
Text Edited

@@
   $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
-  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $3^{th}$ one
-  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} The methods
+  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $4^{th}$ one
+  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} {\it YoungWoo : I meant to say $4^{th}$} The methods
   marked with "*" run the filters on every frame in the listed
   order. The LCT tracker \cite{ma2015long} runs a translation and
-  scale filter in every frame (similar to the method at the $6^{th}$
-  column {\it Burak: Not in $7^{th}$?} and couples a re-detection
+  scale filter in every frame (similar to the methods at the $7^{th}$ and $8^{th}$
+  columns) {\it Burak: Not in $7^{th}$?} {\it YoungWoo: I meant to say $7^{th}$ and $8^{th}$} and couples a re-detection
   method to perform long-term tracking at $\approx30$ fps.}
@@
   E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
-  particle filter?} In summary, with the removal of global camera
+  particle filter?} {\it YoungWoo : Yes, the baseline is the one without Particle Filter.} 
+In summary, with the removal of global camera
 motion, the integration of particle filter into the {\it E}nKCF as

### 2017-06-21 bmvc_review.tex
STC Tracker Added into the Results

@@
 ($\geq$300 fps): KCF \cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, and
-MOSSE \cite{bolme2010visual,henriques2015high} and ones in relatively
+\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
+MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
 lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST

### 2017-06-21 bmvc_review.tex
Revised the experimental section.

@@
 
-Table \ref{table:Comparison_to_LCT} presents the performance of
-different combinations of the proposed algorithm. In short, we
-empirically verified that \textit{E}nKCF is an optimal combination in
-terms of tracking accuracy and run-time performance. We could achieve
-4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$ at every
-frame, but this combination wills sacrifice run-time performance 317
-fps.  To be more specific, we employ $R_{s}$ and $R_{t}^{L}$ or
-$R_{t}^{S}$ to run them in every frame in a similar way to the
-multiple correlation filter framework of the LCT tracker
-\cite{ma2015long}. Running another filter, $R_{t}^{L}$ or $R_{t}^{S}$,
-in the {\it E}nKCF framework not only boosts run-time performance but
-also increases accuracy. Lastly, we run $R_{L}$, $R_{t}^{S}$ and
-$R_{s}$ in every frame.  $R_{t}^{S}$ uses the translation estimated by
-$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
-translation estimation given by $R_{t}^{S}$ to update the
-scale. Interestingly, running two complementary translation filter
-results in significant improvement at the cost of decreased run-time
-performance. In summary, running two (complementary) translation
-filters and a scale filter as {\it E}nKCF not only increases run-time
-performance but also offers more accurate tracker than the baseline
-method with one translation and one scale filter.
+\textbf{Finding Optimal Combination and Deployment Order of Multiple
+  KCFs} In addition to the comparison with other tracking methods, we
+also conducted an experiment to see what combination and deployment
+order of the KCF work best. Table \ref{table:Comparison_to_LCT}
+presents results of this experiment. For this experiment, we removed
+the particle filter. The method at the $2^{nd}$ column fliped the
+order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
+\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
+and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
+removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
+every frame in the listed order. The methods at the $7^{th}$ and
+$8^{th}$ columns ran a translation and a scale filter on every frame
+which is very similar to the way the LCT tracker \cite{ma2015long}
+runs. To be precise, the LCT tracker comes with a re-detection method
+for a long-term tracking. In short, we empirically verified that
+\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
+tracking accuracy and run-time performance. For example, we could
+achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
+at every frame, but this combination wills sacrifice run-time
+performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
+and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
+estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
+final translation estimation given by $R_{t}^{S}$ to update the scale.
 \begin{table}[!h]
@@
 \end{center}
-\caption{Evaluations on different combinations of the KCFs for UAV123
-  dataset. We removed the particle filter from this experiment. The
-  $2^{nd}$ method fliped the way of deploying $R_{t}^{L}$ and
-  $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
-  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $4^{th}$ one
-  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} {\it YoungWoo : I meant to say $4^{th}$} The methods
-  marked with "*" run the filters on every frame in the listed
-  order. The LCT tracker \cite{ma2015long} runs a translation and
-  scale filter in every frame (similar to the methods at the $7^{th}$ and $8^{th}$
-  columns) {\it Burak: Not in $7^{th}$?} {\it YoungWoo: I meant to say $7^{th}$ and $8^{th}$} and couples a re-detection
-  method to perform long-term tracking at $\approx30$ fps.}
+\caption{Results of running different combinations of the KCFs for
+  UAV123 dataset. This table empirically supported the usefulness of
+  combining multiple KCFs as long as the deployment order is optimal.}
 \label{table:Comparison_to_LCT}
@@
 uniform distribution ($[-20,20]$), to the translation estimations of
-the KCFs. In these settings, the {\it E}nKCF with particle filter
-achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it
-  E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
-  particle filter?} {\it YoungWoo : Yes, the baseline is the one without Particle Filter.} 
-In summary, with the removal of global camera
-motion, the integration of particle filter into the {\it E}nKCF as
-shown in fig.~\ref{Workflows} further improved the results.
+the KCFs. In these setup, the {\it E}nKCF with particle filter
+achieves $51.98\%$ precision ($20$px), outperforming the one without
+particle filter {\it E}nKCF by $6.32\%$. Thus, with the removal of
+global camera motion, the integration of particle filter into the {\it
+  E}nKCF as shown in Figure \ref{Workflows} further improved the
+results.
 

### 2017-06-21 bmvc_review.tex
Final Adjustments

@@
 \begin{tabular}{ccc}
-\tiny\:\:\:\:\:\:\textbf{UAV123}\hspace{.44\linewidth}\:\:\:\textbf{OTB100}\\
-\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
+\tiny\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
+\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/pr_uav123.eps}}
 \bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
@@
 
-\textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight
+\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
 digression from the main idea -- the idea of deploying multiple KCFs

### 2017-06-21 bmvc_review.tex
Update Figures

@@
 \begin{tabular}{ccc}
-\tiny\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
-\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/pr_uav123.eps}}
-\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
+\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
+\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
+\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123.eps}}
 \bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
-\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
+\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_otb100.eps}}\\
 \end{tabular}
@@
 \bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123_10fps.eps}}
-\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123_10fps.eps}}\\
+\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123_10fps.eps}}\\
 \end{tabular}

### 2017-08-02 wacv_for_review.tex
WACV with Deep Features Added

--- 2017-06-21 bmvc_review.tex
@@
-\documentclass{bmvc2k}
+\documentclass[10pt,twocolumn,letterpaper]{article}
+
+\usepackage{wacv}
+\usepackage{times}
+\usepackage{epsfig}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{graphicx}
@@
 
-%% Enter your paper number here for the review copy
-\bmvcreviewcopy{825}
+% Include other packages here, before hyperref.
 
-\title{ {\it E}nKCF: Ensemble of Kernelized Correlation Filters for
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+
+%\wacvfinalcopy % *** Uncomment this line for the final submission
+
+\def\wacvPaperID{****} % *** Enter the wacv Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+\ifwacvfinal\pagestyle{empty}\fi
+\setcounter{page}{1}
+\begin{document}
+
+%%%%%%%%% TITLE
+\title{{\it E}nKCF: Ensemble of Kernelized Correlation Filters for
   High-Speed, Object Tracking}
 
-% Enter the paper's authors in order
-% \addauthor{Name}{email/homepage}{INSTITUTION_CODE}
-\addauthor{Susan Student}{http://www.vision.inst.ac.uk/~ss}{1}
-\addauthor{Petra Prof}{http://www.vision.inst.ac.uk/~pp}{1}
-\addauthor{Colin Collaborator}{colin@collaborators.com}{2}
-
-% Enter the institutions
-% \addinstitution{Name\\Address}
-\addinstitution{
- The Vision Institute\\
- University of Borsetshire\\
- Wimbleham, UK
-}
-\addinstitution{
- Collaborators, Inc.\\
- 123 Park Avenue,\\
- New York, USA
+% Authors at the same institution
+%\author{First Author \hspace{2cm} Second Author \\
+%Institution1\\
+%{\tt\small firstauthor@i1.org}
+%}
+% Authors at different institutions
+\author{First Author \\
+Institution1\\
+{\tt\small firstauthor@i1.org}
+\and
+Second Author \\
+Institution2\\
+{\tt\small secondauthor@i2.org}
 }
 
-\runninghead{Student, Prof, Collaborator}{BMVC Author Guidelines}
-
-% Any macro definitions you would like to include
-% These are not defined in the style file, because they don't begin
-% with \bmva, so they might conflict with the user's own macros.
-% The \bmvaOneDot macro adds a full stop unless there is one in the
-% text already.
-\def\eg{\emph{e.g}\bmvaOneDot}
-\def\Eg{\emph{E.g}\bmvaOneDot}
-\def\etal{\emph{et al}\bmvaOneDot}
-
-%-------------------------------------------------------------------------
-% Document starts here
-\begin{document}
-
 \maketitle
+\ifwacvfinal\thispagestyle{empty}\fi
 
@@
 
+\begin{figure*}[!h]
+\centering
+\includegraphics[width=\textwidth]{./figures/ResultsIntroduction.pdf}
+\caption{Examples of tracking results (yellow rectangles) by the
+  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
+  is challenging for object tracking as a target's scale is changed
+  drastically in a few frames.}
+\label{ResultsIntroduction}
+\end{figure*}
+
 In this paper, we propose a single-target tracking algorithm, with no
@@
   e.g., Intel's i7 quad-core vs ARMv8 dual-core.}
+
+\begin{figure*}[!h]
+\centering
+\begin{tabular}{cc}
+\includegraphics[width=14.00cm]{./figures/Workflow_MKCF+PF.pdf}\\
+\end{tabular}
+\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
+  first seven frames of tracking where the first frame is the
+  initialization frame. Afterward, the order of deploying three KCFs
+  is repeating.}
+\label{Workflows}
+\end{figure*}
 
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!h]
 \centering
-\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
-\caption{Examples of tracking results (yellow rectangles) by the
-  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
-  is challenging for object tracking as a target's scale is changed
-  drastically in a few frames.}
-\label{ResultsIntroduction}
+\includegraphics[width=0.70\textwidth]{./figures/Filters_Details.pdf}
+\caption{Examples of three filters; the translation filter,
+  \textit{target+small background}, the scale filter,
+  \textit{target-only} and another translation filter,
+  \textit{target+large background}, and their Hanning window and
+  expected Gaussian response.}
+\label{fig:Filters}
 \end{figure*}
@@
 $R_{t}^{L}$, and $R_{s}$.
-\begin{figure}[!t]
-\centering
-\begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
-\end{tabular}
-\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
-  first seven frames of tracking where the first frame is the
-  initialization frame. Afterward, the order of deploying three KCFs
-  is repeating.}
-\label{Workflows}
-\end{figure}
 
-\begin{figure}[!h]
-\centering
-\includegraphics[width=1.0\textwidth]{figures/Filters_Details.pdf}
-\caption{Examples of three filters; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
-\label{fig:Filters}
-\end{figure}
 The contribution of this study is a novel, single-target tracking
@@
 
-\begin{algorithm}[h]
+\begin{algorithm*}[h]
 \small
@@
 \caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
-\end{algorithm}
+\end{algorithm*}
 
@@
 
-\begin{figure}[!h]
+\begin{figure*}[!h]
 \centering
-\includegraphics[width=1\textwidth]{figures/LearnedFiltersComparison2.pdf}
+\includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
 \caption{This figure shows that there is a marginal difference among
@@
 \label{fig:Filters_Comparison}
-\end{figure}
+\end{figure*}
 
@@
 
+\begin{figure*}[h]
+\centering
+\begin{tabular}{ccc}
+\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
+\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
+\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
+\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
+\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
+\end{tabular}
+\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
+\label{fig:UAV123_DATASET}
+\end{figure*}
+
 \textbf{Features Selections} We used different features for each of
@@
 times faster.
-\begin{figure}[!h]
-\raggedright
-\begin{tabular}{ccc}
-\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
-\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
-\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123.eps}}
-\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
-\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_otb100.eps}}\\
-\end{tabular}
-\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
-\label{fig:UAV123_DATASET}
-\end{figure}
 
@@
 final translation estimation given by $R_{t}^{S}$ to update the scale.
-\begin{table}[!h]
+\begin{table*}[!h]
 \smaller
@@
 \label{table:Comparison_to_LCT}
-\end{table}
+\end{table*}
 
@@
 another low-speed scale adaptive SAMF tracker.
+
+\textbf{Deep Learning Features} Our focus so far was to build a high speed tracker
+that can run about 30fps on a low-end hardware. In this direction, we used HoG and
+color features in an efficient way in the proposed {\it E}nKCF tracking concept. Deep Learning
+features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
+danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF tracker can run more reliably with deep learning
+features on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
+and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
+the first convolutional layer features lead to slightly better precision and success rates than the second
+layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the third convolutional layer
+features to get the response map. In the next stage, they use the translation estimation from the first stage to
+employ second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
+position estimated in the second stage. This coarse-to-fine position estimation approach allows embedding 
+more representative features of the object. However, such approach requires multiple runs of a KCF at a single
+frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
+deep learning features.
+
+Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
+considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
+spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$.
+Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$).
+This feature assignment is represented as  \textit{conv224-VGG}.
+Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}.
+We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.
+
+As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings of the deep features outperform the HoG and color features as proposed in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success rates (AUC).
+On the other hand, the \textit{conv224-VGG} setting performs slightly better than  \textit{conv222-VGG} in precision while achieving similar success rate (AUC).
+
+\begin{figure}[h]
+\begin{tabular}{ccc}
+\tiny\quad\quad\quad\textbf{UAV123}\\
+\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
+\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
+\end{tabular}
+\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
+\label{fig:UAV123_DATASET_DeepFeatures}
+\end{figure}
+
 %\begin{figure}[!h]
@@
 \begin{tabular}{cc}
-\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123_10fps.eps}}
-\bmvaHangBox{\includegraphics[width=3.25cm]{./figures/sr_uav123_10fps.eps}}\\
+\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
+\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
 \end{tabular}
@@
 camera motion, etc.
-%--------------
-%\section*{Acknowledgements}
-%put stuff here for the accepted , but not the ICCV version
 
+{\small
+\bibliographystyle{ieee}
 \bibliography{draft}
+}
+
 \end{document}

### 2017-08-04 wacv_for_review.tex
Deep features figure added

@@
 Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$).
-This feature assignment is represented as  \textit{conv224-VGG}.
+This feature assignment is represented as  \textit{conv224-VGG} and shown in fig.~\ref{fig:Filters_CNN}.
 Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}.
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
+\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target information loss.}
+\label{fig:Filters_CNN}
+\end{figure}
+
+\begin{figure}[t]
 \begin{tabular}{ccc}

### 2017-08-04 wacv_for_review.tex
Deep features figure added

@@
 \caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target information loss.}
+to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
 \label{fig:Filters_CNN}
@@
 \begin{figure}[t]
+\centering
 \begin{tabular}{ccc}

### 2017-08-05 wacv_for_review.tex
Figures Updated - Text Cleaned

@@
 
-\begin{figure*}[!h]
-\centering
-\includegraphics[width=0.70\textwidth]{./figures/Filters_Details.pdf}
-\caption{Examples of three filters; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
-\label{fig:Filters}
-\end{figure*}
-
 Another way of handling the scale change for the correlation filter
@@
 $R_{t}^{L}$, and $R_{s}$.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
+\caption{Examples of three filters; the translation filter,
+  \textit{target+small background}, the scale filter,
+  \textit{target-only} and another translation filter,
+  \textit{target+large background}, and their Hanning window and
+  expected Gaussian response.}
+\label{fig:Filters}
+\end{figure}
 
@@
 \begin{tabular}{ccc}
-\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
+\tiny\quad\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
 \includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
@@
 final translation estimation given by $R_{t}^{S}$ to update the scale.
-\begin{table*}[!h]
-\smaller
-\begin{center}
-\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
-\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
-\hline
-Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
-\hline\hline
-Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
-SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
-FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
-\hline
-\end{tabular}}
-\end{center}
-\caption{Results of running different combinations of the KCFs for
-  UAV123 dataset. This table empirically supported the usefulness of
-  combining multiple KCFs as long as the deployment order is optimal.}
-\label{table:Comparison_to_LCT}
-\end{table*}
 
@@
 
-\textbf{Deep Learning Features} Our focus so far was to build a high speed tracker
-that can run about 30fps on a low-end hardware. In this direction, we used HoG and
-color features in an efficient way in the proposed {\it E}nKCF tracking concept. Deep Learning
+\begin{table*}[h]
+\smaller
+\begin{center}
+\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
+\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
+\hline
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
+\hline\hline
+Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
+SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
+FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
+\hline
+\end{tabular}}
+\end{center}
+\caption{Results of running different combinations of the KCFs for
+  UAV123 dataset. This table empirically supported the usefulness of
+  combining multiple KCFs as long as the deployment order is optimal.}
+\label{table:Comparison_to_LCT}
+\end{table*}
+
+\textbf{Evaluation with Deep Features} Our focus so far was to build a high speed object tracker
+that can run at about 30fps on a low-end hardware. In this direction, we used HoG and
+color features in an efficient way in the proposed {\it E}nKCF. Deep
 features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
-danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF tracker can run more reliably with deep learning
-features on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
+danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF can run more reliably with deep learning
+features at the targeted frame rate on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
 and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
 the first convolutional layer features lead to slightly better precision and success rates than the second
-layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the third convolutional layer
+layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the activations of third convolutional layer
 features to get the response map. In the next stage, they use the translation estimation from the first stage to
-employ second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
-position estimated in the second stage. This coarse-to-fine position estimation approach allows embedding 
-more representative features of the object. However, such approach requires multiple runs of a KCF at a single
+employ the second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
+position estimated in the second stage. This coarse-to-fine tracking approach allows embedding 
+more representative features of the object, however, such approach requires multiple runs of a KCF at a single
 frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
@@
 
-Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
-considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
+Our {\it E}nKCF framework provides us flexibility to exploit different level of abstractions in different KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
+considers more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
 spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$.
@@
 \begin{tabular}{ccc}
-\tiny\quad\quad\quad\textbf{UAV123}\\
+\tiny\quad\quad\textbf{UAV123}\\
 \includegraphics[width=3.30cm]{./figures/pr_deep.eps}
-\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
+\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
 \end{tabular}

### 2017-08-07 wacv_for_review.tex
Revised the draft.

--- 2017-08-04 wacv_for_review.tex
@@
 intervention after deployment and small footprint of consuming
-computational resources and on executable code. To develop a single,
-target tracking system in high accuracy and run-time performance, we
-propose an ensemble of the kernelized correlation filters (KCF), we
-call {\it E}nKCF. In particular, we developed a committee of KCFs to
-specifically address the scale-change and dynamic maneuver of the
-target over frames. To guarantee a high-speed, run-time performance, we
-deploy each of KCFs in turn. For a smooth transition between
-individual KCFs' executions, we developed a Bayes filter. Experimental
-results showed that the performance of ours are, on average, 70.10\%
-for precision at 20 pixels, 53.00\% for success rate for OTB100 data,
-and 54.50\% and 40.2\% for UAV123 data. These results showed that our
-method is better than existing ones over 5\% on precision on 20 pixels
-and 10-20\% on AUC on average. Moreover our implementation ran at 340
-fps for OTB100 and at 416 fps for UAV123 data that is faster than DCF
-(292 fps) for OTB100 and KCF (292 fps), DCF (457 fps) for UAV123.
+computational resources and executable code. To develop a single,
+target tracking system in high accuracy and run-time performance while
+these criteria kept in mind, we propose an ensemble of the kernelized
+correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
+is specifically designed to address the scale-change and dynamic
+maneuver of the target over frames. In particular, to guarantee a
+high-speed, run-time performance, we deploy each of KCFs in turn. For
+a smooth transition between individual KCFs' executions, we developed
+a Bayes filter. Experimental results showed that the performance of
+ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
+success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
+data. These results showed that our method is better than existing
+ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
+average. Moreover our implementation ran at 340 fps for OTB100 and at
+416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
+and KCF (292 fps), DCF (457 fps) for UAV123.
 \end{abstract}
@@
 because payloads of those mobile platforms are limited to carry any
-other sensors than a lightweight or an array of monocular cameras. For
-example, instead of just flying to record a video based on manual
-commands, an unmanned air vehicle (UAV) equipped with an object or
+other sensors than a lightweight or an array of monocular
+cameras. Given such a trend, instead of just manually flying for video
+recording, an unmanned air vehicle (UAV) equipped with an object or
 feature following functionality would make it more useful in the
@@
 
-In this paper, we propose a single-target tracking algorithm, with no
-offline training, aiming at running on any embedded or mobile
+In this paper, we propose a single-target tracking algorithm that does
+not require offline training and can run on any embedded or mobile
 platforms. Specifically, we would like to make our algorithm 1) learn
 the appearance model of a target on the fly and 2) run as fast on a
-typical desktop as up to $300-450$ fps so that it could run, at least,
+typical desktop as up to $300-450$ fps, aiming at running, at least,
 faster than 30 fps when it is deployed on a low-end, embedded
-system.\footnote{In general, it would be very hard to compare an Intel
-  or AMD processor running on a desktop or a laptop with that, e.g.,
-  ARM, of a single-board, embedded system in terms of run-time
-  performance of a computer vision algorithm. This is primarily due to
-  the difference in their architectures. To derive this number, we
-  assume that there is roughly, at least, an 1/10th scale down of
-  computational resources from a typical PC to an embedded system. We
-  found such a scale-down in computation based on exemplar processors,
-  e.g., Intel's i7 quad-core vs ARMv8 dual-core.}
+system.\footnote{In general, it would not be easy to compare run-time
+  performance of a computer vision algorithm at an Intel or AMD
+  processor running on a desktop or a laptop and at that, e.g., ARM,
+  of a single-board, embedded system. This is primarily due to the
+  difference in their architectures and available computing
+  resources. To derive these numbers (300 and 30 fps), we assume that
+  there is roughly, at least, an 1/10th scale down of computational
+  resources from a typical PC to an embedded system. We found such a
+  scale-down in computation based on exemplar processors, e.g.,
+  Intel's i7 quad-core vs ARMv8 dual-core.}
 
@@
 regression problem, a set of negative examples is collected around the
-initial, target bounding box and represented as a circulant matrix
-\cite{henriques2015high}. One can optimally solve this regression
-problem using a ridge regression in a closed form. However, this
-solution involves in expensive matrix operations
+initial, target bounding box and represented as a form of the
+circulant matrix \cite{henriques2015high}. One can optimally solve
+this regression problem using a ridge regression in a closed
+form. However, this solution involves in expensive matrix operations
 $\mathcal{O}(n^{3})$. The correlation filter offers a less complex
@@
 
-\textbf{Deep Learning Features} Our focus so far was to build a high speed tracker
-that can run about 30fps on a low-end hardware. In this direction, we used HoG and
-color features in an efficient way in the proposed {\it E}nKCF tracking concept. Deep Learning
-features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
-danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF tracker can run more reliably with deep learning
-features on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
-and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
-the first convolutional layer features lead to slightly better precision and success rates than the second
-layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the third convolutional layer
-features to get the response map. In the next stage, they use the translation estimation from the first stage to
-employ second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
-position estimated in the second stage. This coarse-to-fine position estimation approach allows embedding 
-more representative features of the object. However, such approach requires multiple runs of a KCF at a single
-frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
-deep learning features.
+\textbf{Deep Learning Features} Our focus so far was to build a high
+speed tracker that can run about 30fps on a single-board, embedded
+system. Given this goal, we used HoG and color features in an
+efficient way for the proposed {\it E}nKCF. Deep Learning features, on
+the other hand, recently have been proved to boost tracking accuracy
+of some of the online tracking algorthms \cite{ma2015hierarchical,
+  danelljan2015convolutional}. For this reason, we believe that, the
+{\it E}nKCF tracker can perform better with deep learning features if
+a target embedded system has GPUs.
 
-Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
-considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
-spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$.
-Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$).
-This feature assignment is represented as  \textit{conv224-VGG} and shown in fig.~\ref{fig:Filters_CNN}.
-Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}.
-We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.
+{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
+  Features.'' My edit stopped at the above paragraph because I got
+  confused. At least you'll have to explain the point of adding this
+  section.
 
-As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings of the deep features outperform the HoG and color features as proposed in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success rates (AUC).
-On the other hand, the \textit{conv224-VGG} setting performs slightly better than  \textit{conv222-VGG} in precision while achieving similar success rate (AUC).
+  I don't know why Figure 6 is presented separately from Figure 5. If
+  you want to keep this way, you need, at least, to have their scales
+  same -- precision should have the same range, say 0.8 as the max
+  value.
 
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target information loss.}
-\label{fig:Filters_CNN}
-\end{figure}
+  It seems most of reference on DNN hasn't added to the .bib file yet.
+}
 
-\begin{figure}[t]
+For example, \cite{danelljan2015convolutional} used the activations of
+the first and second convolutional layer features of the VGGNet
+\cite{simonyan2014very} where their experiments showed that the first
+convolutional layer features lead to slightly better precision and
+success rates than the second layer. \cite{ma2015hierarchical}
+proposed a KCF tracker with deeper features. Their method employs the
+third convolutional layer features to get the response map. In the
+next stage, they use the translation estimation from the first stage
+to employ second convolutional layer features. Finally, the first
+convolutional layer features is extracted from the position estimated
+in the second stage. This coarse-to-fine position estimation approach
+allows embedding more representative features of the object. However,
+such approach requires multiple runs of a KCF at a single frame,
+increasing the run-time complexity. For this reason, we follow a
+similar approach to \cite{danelljan2015convolutional} to embed deep
+learning features.
+
+Our {\it E}nKCF framework provides us flexibility to exploit different
+feature  representations.  The  translation filters,  $R_{t}^{L}$  and
+$R_{t}^{S}$,   considers  at   more  than   twice  larger   area  than
+$R_{s}$.  Taking  this into  account,  we  can assign  deeper  feature
+encodings  to $R_{s}$  as it  requires less  spatial information  than
+$R_{t}^{L}$ and $R_{t}^{S}$.  Hence, we assign the  activations of the
+fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
+whereas $R_{t}^{L}$  and $R_{t}^{S}$  are assigned the  activations of
+the  second  layer  features  ($109\times109\times64$).  This  feature
+assignment  is represented  as \textit{conv224-VGG}.  Additionally, we
+assign  the  second convolutional  layer  features  to $R_{s}$  as  in
+$R_{t}^{L}$    and    $R_{t}^{S}$    and    compare    this    setting
+(\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the  VGGNet as
+it provides  higher spatial resolution  at the first layers  than than
+AlexNet \cite{krizhevsky2012imagenet}.
+
+As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings
+of the deep features outperform the HoG and color features as proposed
+in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$
+in success rates (AUC). On the other hand, the \textit{conv224-VGG}
+setting performs slightly better than \textit{conv222-VGG} in
+precision while achieving similar success rate (AUC).
+
+\begin{figure}[h]
 \begin{tabular}{ccc}

### 2017-08-07 wacv_for_review.tex

@@
 
-\textbf{Deep Learning Features} Our focus so far was to build a high
+\begin{table*}[h]
+\smaller
+\begin{center}
+\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
+\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
+\hline
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
+\hline\hline
+Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
+SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
+FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
+\hline
+\end{tabular}}
+\end{center}
+\caption{Results of running different combinations of the KCFs for
+  UAV123 dataset. This table empirically supported the usefulness of
+  combining multiple KCFs as long as the deployment order is optimal.}
+\label{table:Comparison_to_LCT}
+\end{table*}
+
+\textbf{Evaluation with Deep Features}Our focus so far was to build a high
 speed tracker that can run about 30fps on a single-board, embedded
@@
 
-  I don't know why Figure 6 is presented separately from Figure 5. If
+  I don't know why Figure 7 is presented separately from Figure 5. If
   you want to keep this way, you need, at least, to have their scales
@@
   value.
-
-  It seems most of reference on DNN hasn't added to the .bib file yet.
 }
@@
 Our {\it E}nKCF framework provides us flexibility to exploit different
-feature  representations.  The  translation filters,  $R_{t}^{L}$  and
-$R_{t}^{S}$,   considers  at   more  than   twice  larger   area  than
-$R_{s}$.  Taking  this into  account,  we  can assign  deeper  feature
+level of abstractions in different KCFs. The translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice larger area
+than $R_{s}$. Taking this into account, we can assign deeper feature
 encodings to $R_{s}$ as it requires less spatial information than
@@
 the second layer features ($109\times109\times64$). This feature
-assignment  is represented  as \textit{conv224-VGG}.  Additionally, we
-assign  the  second convolutional  layer  features  to $R_{s}$  as  in
-$R_{t}^{L}$    and    $R_{t}^{S}$    and    compare    this    setting
-(\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the  VGGNet as
-it provides  higher spatial resolution  at the first layers  than than
-AlexNet \cite{krizhevsky2012imagenet}.
+assignment is represented as \textit{conv224-VGG} and shown in
+fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
+convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
+$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
+\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
+resolution at the first layers than than AlexNet
+\cite{krizhevsky2012imagenet}.
 
@@
 setting performs slightly better than \textit{conv222-VGG} in
-precision while achieving similar success rate (AUC).
+precision while achieving similar success rate (AUC).  >>>>>>>
 
-\begin{figure}[h]
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
+\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
+\label{fig:Filters_CNN}
+\end{figure}
+
+\begin{figure}[t]
+\centering
 \begin{tabular}{ccc}
-\tiny\quad\quad\quad\textbf{UAV123}\\
+\tiny\quad\quad\textbf{UAV123}\\
 \includegraphics[width=3.30cm]{./figures/pr_deep.eps}
-\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
+\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
 \end{tabular}

### 2017-08-10 wacv_for_review.tex
Comments Replied

@@
 
-\textbf{Evaluation with Deep Features}Our focus so far was to build a high
-speed tracker that can run about 30fps on a single-board, embedded
+\textbf{Evaluation with Deep Features} Our focus so far was to build a high
+speed tracker that can run at 30fps on a single-board, embedded
 system. Given this goal, we used HoG and color features in an
-efficient way for the proposed {\it E}nKCF. Deep Learning features, on
+efficient way for the proposed {\it E}nKCF. Deep features, on
 the other hand, recently have been proved to boost tracking accuracy
-of some of the online tracking algorthms \cite{ma2015hierarchical,
+of the KCFs based trackers \cite{ma2015hierarchical,
   danelljan2015convolutional}. For this reason, we believe that, the
-{\it E}nKCF tracker can perform better with deep learning features if
-a target embedded system has GPUs.
+{\it E}nKCF tracker can perform better with deep features trained
+on ImageNet dataset. Accomodating deep features on a single-board
+system prohibits from tracking at targeted speed. However, with the
+availability of GPUs on the embedded system, {\it E}nKCF tracker can
+afford convolutional neural network features (CNN) to improve tracking
+accuracy. Therefore, we wanted to evaluate how much accuracy gain we
+can achieve by switching from hand-crafted features to CNN features.
 
@@
   value.
+
+  \it YoungWoo : The point of adding this section is to evaluate the
+  same tracker with deep features (CNN) and see how much accuracy improvement
+  we get. However, I tried to highlight that, by employing deep features
+  the targeted embedded system changes from low-end (CPU-only) to 
+  higher-end system (GPUs). The two papers I cited employs the features
+  from the first several layers of the VGGNet. This is a common practice
+  in supporting the trackers with CNN features. If I add this to figure 5,
+  it does not make sense, because all the trackers we compare, use hand-crafted
+  features and run on CPU. For this reason, I wanted to compare EnKCF 
+  with deep features (higher-end system) and hand-crafted features (low-end system).
+
+  The figure 7(a) and figure 5 have almost the same range (0,73 and 0.70)
+  I will update the figure 5 to have 0.73 range as well. I test the EnKCF
+  with CNN features only on the UAV123 dataset.
 }
 
-For example, \cite{danelljan2015convolutional} used the activations of
+There has been numerous studies on applying a pretrained CNN features
+to tracking-by-detection algorithms. For example, 
+\cite{danelljan2015convolutional} used the activations of
 the first and second convolutional layer features of the VGGNet

### 2017-08-13 wacv_for_review.tex
Revised the section about DNN features.

@@
 
-\textbf{Evaluation with Deep Features} Our focus so far was to build a high
-speed tracker that can run at 30fps on a single-board, embedded
+\textbf{Evaluation with Deep Features} Our focus so far was to build a
+high speed tracker that can run at 30fps on a single-board, embedded
 system. Given this goal, we used HoG and color features in an
-efficient way for the proposed {\it E}nKCF. Deep features, on
-the other hand, recently have been proved to boost tracking accuracy
-of the KCFs based trackers \cite{ma2015hierarchical,
-  danelljan2015convolutional}. For this reason, we believe that, the
-{\it E}nKCF tracker can perform better with deep features trained
-on ImageNet dataset. Accomodating deep features on a single-board
-system prohibits from tracking at targeted speed. However, with the
-availability of GPUs on the embedded system, {\it E}nKCF tracker can
-afford convolutional neural network features (CNN) to improve tracking
-accuracy. Therefore, we wanted to evaluate how much accuracy gain we
-can achieve by switching from hand-crafted features to CNN features.
-
+efficient way for the proposed {\it E}nKCF. Deep features, on the
+other hand, recently have been used to boost tracking accuracy of the
+KCFs based trackers \cite{ma2015hierarchical,
+  danelljan2015convolutional}. We hypothesize that the {\it E}nKCF
+tracker could perform better with deep features trained on ImageNet
+dataset. Utilizing pretrained deep features would not be applicable to
+all the a single-board, embedded system due to their limited
+computational resources. But as these days some of the single-board
+systems offer GPU, we would like to see how much accuracy we can
+achieve by feeding {\it E}nKCF w/ CNN features.
+\begin{comment}
 {\it Burak: I'm not sure what you wanted to say with ``Deep Learning
@@
 
-  \it YoungWoo : The point of adding this section is to evaluate the
+  YoungWoo : The point of adding this section is to evaluate the
   same tracker with deep features (CNN) and see how much accuracy improvement
@@
   from the first several layers of the VGGNet. This is a common practice
-  in supporting the trackers with CNN features. If I add this to figure 5,
-  it does not make sense, because all the trackers we compare, use hand-crafted
-  features and run on CPU. For this reason, I wanted to compare EnKCF 
-  with deep features (higher-end system) and hand-crafted features (low-end system).
+  in supporting the trackers with CNN features.
+
+  Burak: I'm not saying what you did -- use CNN features to feed an
+  online tracker. Yes, many people did such before. My worry is to
+  make our paper look a christmas tree -- a paper w/ too many stuffs
+  to evaluate under a certain theme. And, adding these new stuffs
+  along the way of preparing any submissions continuously asks us to
+  rewrite this paper from the top to all the way down. We need to
+  focus on a certain idea when to submit a paper to a
+  conference. Adding a bit more meats and stuffs to the main idea is
+  usually done in a journal paper.
+
+  If I add this to figure 5, it does not make sense, because all the
+  trackers we compare, use hand-crafted features and run on CPU. For
+  this reason, I wanted to compare EnKCF with deep features
+  (higher-end system) and hand-crafted features (low-end system).
+
+  Burak: Given what we agreed upon what you did, I think you can still
+  put them together in that we're comparing different versions of
+  apples, not orange, under the same criterion. Think about it.
 
@@
   with CNN features only on the UAV123 dataset.
-}
 
-There has been numerous studies on applying a pretrained CNN features
-to tracking-by-detection algorithms. For example, 
-\cite{danelljan2015convolutional} used the activations of
-the first and second convolutional layer features of the VGGNet
-\cite{simonyan2014very} where their experiments showed that the first
-convolutional layer features lead to slightly better precision and
-success rates than the second layer. \cite{ma2015hierarchical}
-proposed a KCF tracker with deeper features. Their method employs the
-third convolutional layer features to get the response map. In the
-next stage, they use the translation estimation from the first stage
-to employ second convolutional layer features. Finally, the first
-convolutional layer features is extracted from the position estimated
-in the second stage. This coarse-to-fine position estimation approach
-allows embedding more representative features of the object. However,
-such approach requires multiple runs of a KCF at a single frame,
-increasing the run-time complexity. For this reason, we follow a
-similar approach to \cite{danelljan2015convolutional} to embed deep
-learning features.
+  Burak: We don't expect the reviewers or readers to exactly see what
+  we saw here. Keep their scales same -- whatever maximum value you
+  choose for the y-axis for one graph, use the same scale to all other
+  same graphs.}
+\end{comment}
+There have been many studies on applying a pretrained CNN features to
+tracking-by-detection algorithms. For example,
+\cite{danelljan2015convolutional} used the activations of the first
+and second convolutional layer features of the VGGNet
+\cite{simonyan2014very} for this idea where their experiments showed
+that the first convolutional layer features lead to slightly better
+precision and success rates than the second
+layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
+features. Their method employs the third convolutional layer features
+to get the response map. In the next stage, they used the estimation
+of the target's transition from the first stage to use the second
+convolutional layer features. Finally, the first convolutional layer
+features is extracted from the position estimated in the second
+stage. This coarse-to-fine position estimation approach allows to
+utilize more representative features of the object. However, such
+approach requires multiple runs of a KCF at a single frame, increasing
+the run-time complexity. For this reason, we follow a similar approach
+to \cite{danelljan2015convolutional} to embed deep learning features.
 
-Our {\it E}nKCF framework provides us flexibility to exploit different
+Our {\it E}nKCF framework provides us with a flexibility to exploit different
 level of abstractions in different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice larger area
+$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice bigger area
 than $R_{s}$. Taking this into account, we can assign deeper feature
@@
 
-As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings
-of the deep features outperform the HoG and color features as proposed
-in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$
-in success rates (AUC). On the other hand, the \textit{conv224-VGG}
-setting performs slightly better than \textit{conv222-VGG} in
-precision while achieving similar success rate (AUC).  >>>>>>>
+Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
+results of utilizing DNN features. Two settings of utilizing the deep
+features outperformed the HoG and color features as proposed in {\it
+  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
+success rates (AUC). The \textit{conv224-VGG} setting performed
+slightly better than \textit{conv222-VGG} in precision while achieving
+similar success rate (AUC).
 

### 2017-08-29 wacv_for_review.tex
Revised for Deep Features

@@
 maneuver of the target over frames. In particular, to guarantee a
-high-speed, run-time performance, we deploy each of KCFs in turn. For
-a smooth transition between individual KCFs' executions, we developed
+high-speed, run-time performance, we deploy each of KCFs in turn and assign 
+them hand-crafted features including histogram of oriented gradients and color features.
+For a smooth transition between individual KCFs' executions, we developed
 a Bayes filter. Experimental results showed that the performance of
@@
 416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
-and KCF (292 fps), DCF (457 fps) for UAV123.
+and KCF (292 fps), DCF (457 fps) for UAV123. Finally, for the embedded
+systems with GPUs, we explored different levels of deep features for different
+correlation filters to boost tracking performance. 
 \end{abstract}
@@
 change and estimate target's motion efficiently while maintaining or
-increasing run-time performance. Figure \ref{fig:Filters} shows
-examples of the region of interest (ROI) associated with $R_{t}^{S}$,
-$R_{t}^{L}$, and $R_{s}$.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
-\caption{Examples of three filters; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
-\label{fig:Filters}
-\end{figure}
+increasing run-time performance.
 
@@
 %----------------------------------------------------------------------
+
 In this paper, we propose a novel way of utilizing a multiple of the
@@
 this observation.
-
+\begin{figure}[!b]
+\centering
+\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
+\caption{Examples of three filters with hand-crafted features; the translation filter,
+  \textit{target+small background}, the scale filter,
+  \textit{target-only} and another translation filter,
+  \textit{target+large background}, and their Hanning window and
+  expected Gaussian response.}
+\label{fig:Filters}
+\end{figure}
 \begin{figure*}[!h]
@@
 will briefly describe the parts of the KCF related to this work.
+
+\textbf{{\it E}nKCF with Hand-crafted Features}
+We, first, explore traditional features to run  {\it E}nKCF on any embedded system as it is the primary
+objective of this study. In this direction, we employ two highly efficient features; fHoG \cite{felzenszwalb2010object}
+and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
+$R_{t}^{L}$, and $R_{s}$ assigned hand-crafted features, . This version of {\it E}nKCF is dedicated to run
+on any embedded system at real-time ($30$fps).
+
+\textbf{{\it E}nKCF with Convolutional Neural Network Features}
+In addition to hand-crafted featurres, we explore deep features
+to boost tracking performance. This version of {\it E}nKCF, on the other hand, 
+is dedicated to run on high-end embedded systems (GPUs).
+
+There have been many studies on applying a pretrained CNN features to
+tracking-by-detection algorithms. For example,
+\cite{danelljan2015convolutional} used the activations of the first
+and second convolutional layer features of the VGGNet
+\cite{simonyan2014very} for this idea where their experiments showed
+that the first convolutional layer features lead to slightly better
+precision and success rates than the second
+layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
+features. Their method employs the third convolutional layer features
+to get the response map. In the next stage, they used the estimation
+of the target's transition from the first stage to use the second
+convolutional layer features. Finally, the first convolutional layer
+features is extracted from the position estimated in the second
+stage. This coarse-to-fine position estimation approach allows to
+utilize more representative features of the object. However, such
+approach requires multiple runs of a KCF at a single frame, increasing
+the run-time complexity. For this reason, we follow a similar approach
+to \cite{danelljan2015convolutional} to embed deep learning features.
+
+Our {\it E}nKCF framework provides us with a flexibility to exploit different
+level of abstractions in different KCFs. The translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice bigger area
+than $R_{s}$. Taking this into account, we can assign deeper feature
+encodings to $R_{s}$ as it requires less spatial information than
+$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
+fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
+whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
+the second layer features ($109\times109\times64$). This feature
+assignment is represented as \textit{conv224-VGG} and shown in
+fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
+convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
+$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
+\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
+resolution at the first layers than than AlexNet
+\cite{krizhevsky2012imagenet}.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
+\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
+\label{fig:Filters_CNN}
+\end{figure}
 
@@
 %---------------------------------------------------------------------- 
-To evaluate the performance of the proposed algorithm, we choose two
+To evaluate the performance of the proposed  {\it
+  E}nKCF with hand-crafted features, we choose two
 publicly, available datasets:
@@
 and color-naming \cite{van2009learning} features to more effectively
-learn the background around the target. Through experiments, we found
-that only fHoG didn't work well to cover a larger ROI; another
+learn the background around the target as shown in figure~\ref{fig:Filters}. 
+Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
 translation filter, $R_{t}^{S}$, worked well when it used fHoG
@@
 
+\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
+digression from the main idea -- the idea of deploying multiple KCFs
+to make a very fast and effective, single target tracking
+available. We found that, with a slight modification, the proposed
+method can effectively handle tracking of object in fast motion and in
+large camera motion. Specifically we modified {\it E}nKCF by running
+$R_{t}^{L}$ every frame and remove the particle filter instead. We
+tested this modified {\it E}nKCF with another vision of the UAV123 that
+the original dataset was temporally down-sampled at $10$ fps and makes
+the challenging original dataset, because of objects in fast motion
+and large ego-motion, more challenging. This is because the magnitude
+of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
+compares the performance of the modified version of {\it E}nKCF and
+other tracking methods. Our tracker outperforms other high-speed
+correlation filter based trackers including KCF, DSST by about
+$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
+the other hand, it does decent job in scale estimation. It ranks as
+second in AUC while running about $150$ faster than the MUSTER
+tracker.
+
+\begin{figure}[!h]
+\centering
+\begin{tabular}{cc}
+\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
+\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
+\end{tabular}
+\caption{Comparison of a modified {\it E}nKCF's performance with those
+  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
+  dataset where the original UAV123 data was temporally downsampled.}
+\label{fig:UAV123_10fpsDATASET}
+\end{figure}
+
 \textbf{Evaluation with Deep Features} Our focus so far was to build a
@@
 systems offer GPU, we would like to see how much accuracy we can
-achieve by feeding {\it E}nKCF w/ CNN features.
+achieve by feeding {\it E}nKCF w/ conv features as shown in figure~\ref{fig:Filters_CNN}.
 \begin{comment}
@@
 \end{comment}
-There have been many studies on applying a pretrained CNN features to
-tracking-by-detection algorithms. For example,
-\cite{danelljan2015convolutional} used the activations of the first
-and second convolutional layer features of the VGGNet
-\cite{simonyan2014very} for this idea where their experiments showed
-that the first convolutional layer features lead to slightly better
-precision and success rates than the second
-layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
-features. Their method employs the third convolutional layer features
-to get the response map. In the next stage, they used the estimation
-of the target's transition from the first stage to use the second
-convolutional layer features. Finally, the first convolutional layer
-features is extracted from the position estimated in the second
-stage. This coarse-to-fine position estimation approach allows to
-utilize more representative features of the object. However, such
-approach requires multiple runs of a KCF at a single frame, increasing
-the run-time complexity. For this reason, we follow a similar approach
-to \cite{danelljan2015convolutional} to embed deep learning features.
-
-Our {\it E}nKCF framework provides us with a flexibility to exploit different
-level of abstractions in different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice bigger area
-than $R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it requires less spatial information than
-$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
-fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
-whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
-the second layer features ($109\times109\times64$). This feature
-assignment is represented as \textit{conv224-VGG} and shown in
-fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
-convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
-$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
-resolution at the first layers than than AlexNet
-\cite{krizhevsky2012imagenet}.
 
 Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
-results of utilizing DNN features. Two settings of utilizing the deep
+results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
 features outperformed the HoG and color features as proposed in {\it
@@
 similar success rate (AUC).
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
-\label{fig:Filters_CNN}
-\end{figure}
 
@@
 
-\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
-digression from the main idea -- the idea of deploying multiple KCFs
-to make a very fast and effective, single target tracking
-available. We found that, with a slight modification, the proposed
-method can effectively handle tracking of object in fast motion and in
-large camera motion. Specifically we modified {\it E}nKCF by running
-$R_{t}^{L}$ every frame and remove the particle filter instead. We
-tested this modified {\it E}nKCF with another vision of the UAV123 that
-the original dataset was temporally down-sampled at $10$ fps and makes
-the challenging original dataset, because of objects in fast motion
-and large ego-motion, more challenging. This is because the magnitude
-of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
-compares the performance of the modified version of {\it E}nKCF and
-other tracking methods. Our tracker outperforms other high-speed
-correlation filter based trackers including KCF, DSST by about
-$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
-the other hand, it does decent job in scale estimation. It ranks as
-second in AUC while running about $150$ faster than the MUSTER
-tracker.
-
-\begin{figure}[!h]
-\centering
-\begin{tabular}{cc}
-\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
-\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
-\end{tabular}
-\caption{Comparison of a modified {\it E}nKCF's performance with those
-  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
-  dataset where the original UAV123 data was temporally downsampled.}
-\label{fig:UAV123_10fpsDATASET}
-\end{figure}
-
 %---------------------------------------------------------------------- 

### 2017-08-31 wacv_for_review.tex
Updated Figure Order
Burak Final Commits

@@
 416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
-and KCF (292 fps), DCF (457 fps) for UAV123. Finally, for the embedded
+and KCF (292 fps), DCF (457 fps) for UAV123. Finally, dedicated for the embedded
 systems with GPUs, we explored different levels of deep features for different
-correlation filters to boost tracking performance. 
+correlation filters to boost tracking performance and call it Deep{\it E}nKCF. 
 \end{abstract}
@@
 performance gap from transiting one KCF to another, we use a Bayes
-filter.
+filter. Finally, we explore deep features with varying levels of abstraction
+in the proposed {\it E}nKCF to improve tracking performance.
 
@@
 and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
-$R_{t}^{L}$, and $R_{s}$ assigned hand-crafted features, . This version of {\it E}nKCF is dedicated to run
+$R_{t}^{L}$, and $R_{s}$. This version of {\it E}nKCF is dedicated to run
 on any embedded system at real-time ($30$fps).
 
+We used different features for each of three KCFs as each of them 
+has different goals to accomplish. In particular, the translation filter, $R_{t}^{L}$, 
+uses both the fHoG \cite{felzenszwalb2010object}
+and color-naming \cite{van2009learning} features to more effectively
+learn the large background area around the target as shown in figure~\ref{fig:Filters}. The color features
+compensate for the noisier shape features due to the large ROI considered by $R_{t}^{L}$.
+On the other hand, color features is not assigned to $R_{t}^{S}$ as it learns more useful shape
+features than $R_{t}^{L}$ due to smaller padding size. Finally, $R_{s}$ is assigned both fHoG 
+and color-naming features since we believe that the lower template resolution (64 x n) assigned to
+$R_{s}$ might lead to less discriminative shape features. Smaller template size is assigned to 
+$R_{s}$ as it estimates the scale by correlating the filter with three ROIs as shown in alg.~\ref{alg:MKCF}. 
+This way, we can keep the run-time complexity of the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that 
+only run correlation filter on a single ROI. By doing so, we can avoid fluctuating run-time performance 
+which is not desired in embedded systems.
+%Through experiments, we found that only fHoG didn't work well 
+%to cover a larger ROI; another translation filter, $R_{t}^{S}$, worked well when it used fHoG
+%features only; the scale filter, $R_{s}$ did when it used both fHoG
+%and color features.
+
 \textbf{{\it E}nKCF with Convolutional Neural Network Features}
-In addition to hand-crafted featurres, we explore deep features
-to boost tracking performance. This version of {\it E}nKCF, on the other hand, 
+In addition to hand-crafted features, we explore deep features
+to boost tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, 
 is dedicated to run on high-end embedded systems (GPUs).
 
-There have been many studies on applying a pretrained CNN features to
+There have been large volume of stuides on utilizing a pre-trained CNN features to
 tracking-by-detection algorithms. For example,
@@
 features. Their method employs the third convolutional layer features
-to get the response map. In the next stage, they used the estimation
-of the target's transition from the first stage to use the second
-convolutional layer features. Finally, the first convolutional layer
-features is extracted from the position estimated in the second
-stage. This coarse-to-fine position estimation approach allows to
-utilize more representative features of the object. However, such
-approach requires multiple runs of a KCF at a single frame, increasing
+to estimate the response map. In the next stage, they used the estimation
+of the target's transition from the first phase to use the second
+convolutional layer features and update transition estimation. 
+Finally, the first convolutional layer features is extracted from the ROI estimated 
+in the second stage. This coarse-to-fine position estimation approach accommodates
+different levels of abstractions of the object. However, such
+approach runs multiple KCFs at a single frame, increasing
 the run-time complexity. For this reason, we follow a similar approach
-to \cite{danelljan2015convolutional} to embed deep learning features.
+to \cite{danelljan2015convolutional} to embed deep features in {\it E}nKCF.
 
-Our {\it E}nKCF framework provides us with a flexibility to exploit different
-level of abstractions in different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice bigger area
+Our {\it E}nKCF framework allows us to exploit different
+level of feature encodings in different KCFs. The translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area
 than $R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it requires less spatial information than
+encodings to $R_{s}$ as it relies on less spatial information than
 $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
@@
 the second layer features ($109\times109\times64$). This feature
-assignment is represented as \textit{conv224-VGG} and shown in
+assignment scheme is represented as \textit{conv224-VGG} and shown in
 fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
@@
 \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
-resolution at the first layers than than AlexNet
+resolution at the first layers than AlexNet
 \cite{krizhevsky2012imagenet}.
@@
 \includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework to use deep features in {\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not applied as it would result in target boundary information loss.}
+\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
 \label{fig:Filters_CNN}
@@
 \textbf{Kernelized Correlation Filter} The Kernelized Correlation
-Filter is a well, known single target tracking method and its work
+Filter is a well-known single target tracking method and its work
 flow has been detailed in other papers
@@
 %---------------------------------------------------------------------- 
-To evaluate the performance of the proposed  {\it
-  E}nKCF with hand-crafted features, we choose two
-publicly, available datasets:
+We first evaluate the performance of {\it E}nKCF with hand-crafted features.
+In this direction, we choose two publicly, available datasets:
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
-and
-UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
+and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
 The OTB100 dataset is comprised of the videos about 100 objects
@@
 on an embedded system, a drone, for example, in ``high speed,'' $\ge
-300$ fps. Given this, we believe that the UAV123 data is a good fit in
+300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
 evaluating the performance of the proposed algorithm. In addition, in
-the UAV123 data, there are many challenging, realistic scenes, e.g.,
+the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
 abrupt scale/illumination changes. Although we are primarily
@@
 proposed algorithm with those of the state-of-the-art in a nominal
-dataset for comparison. To this end, we chose the OTB100 data that
+dataset for comparison. To this end, we chose the OTB100 dataset that
 contains the videos recorded from smart phones and typical cameras in
 perspective view. Lastly, we tested the proposed algorithm on a
-temporally down-sampled version of the UAV123 dataset, we call it
+temporally down-sampled version of the UAV123 dataset, called
 UAV123$\_$10fps dataset. What we would like to evaluate using this
@@
 \begin{tabular}{ccc}
-\tiny\quad\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
+\tiny\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
 \includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
@@
 
-\textbf{Features Selections} We used different features for each of
-three KCFs as each of them has different goals to accomplish. In
-particular, the translation filter, $R_{t}^{L}$, uses both the fast
-Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
-and color-naming \cite{van2009learning} features to more effectively
-learn the background around the target as shown in figure~\ref{fig:Filters}. 
-Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
-translation filter, $R_{t}^{S}$, worked well when it used fHoG
-features only; the scale filter, $R_{s}$ did when it used both fHoG
-and color features.
+%\textbf{Features Selections} We used different features for each of
+%three KCFs as each of them has different goals to accomplish. In
+%particular, the translation filter, $R_{t}^{L}$, uses both the fast
+%Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
+%and color-naming \cite{van2009learning} features to more effectively
+%learn the background around the target as shown in figure~\ref{fig:Filters}. 
+%Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
+%translation filter, $R_{t}^{S}$, worked well when it used fHoG
+%features only; the scale filter, $R_{s}$ did when it used both fHoG
+%and color features.
 
@@
 
+\begin{table*}[!h]
+\smaller
+\begin{center}
+\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
+\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
+\hline
+Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
+\hline\hline
+Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
+SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
+FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
+\hline
+\end{tabular}}
+\end{center}
+\caption{Results of running different combinations of the KCFs for
+  UAV123 dataset. This table empirically supported the usefulness of
+  combining multiple KCFs as long as the deployment order is optimal.}
+\label{table:Comparison_to_LCT}
+\end{table*}
+
 \textbf{Finding Optimal Combination and Deployment Order of Multiple
@@
 
-For the $UAV123$ dataset, we also evaluated the performance of the
+\textbf{Evalution on Particle Filter Contribution} For the $UAV123$ dataset, we also evaluated the performance of the
 {\it E}nKCF with and without the particle filter. In particular, we
@@
 
-\begin{table*}[h]
-\smaller
-\begin{center}
-\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
-\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
-\hline
-Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
-\hline\hline
-Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
-SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
-FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
-\hline
-\end{tabular}}
-\end{center}
-\caption{Results of running different combinations of the KCFs for
-  UAV123 dataset. This table empirically supported the usefulness of
-  combining multiple KCFs as long as the deployment order is optimal.}
-\label{table:Comparison_to_LCT}
-\end{table*}
+\begin{figure}[!h]
+\centering
+\begin{tabular}{cc}
+\tiny\quad\textbf{UAV123$\_$10fps}\\
+\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
+\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
+\end{tabular}
+\caption{Comparison of a modified {\it E}nKCF's performance with those
+  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
+  dataset where the original UAV123 data was temporally downsampled.}
+\label{fig:UAV123_10fpsDATASET}
+\end{figure}
 
@@
 
-\begin{figure}[!h]
-\centering
-\begin{tabular}{cc}
-\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
-\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
-\end{tabular}
-\caption{Comparison of a modified {\it E}nKCF's performance with those
-  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
-  dataset where the original UAV123 data was temporally downsampled.}
-\label{fig:UAV123_10fpsDATASET}
-\end{figure}
-
 \textbf{Evaluation with Deep Features} Our focus so far was to build a
 high speed tracker that can run at 30fps on a single-board, embedded
-system. Given this goal, we used HoG and color features in an
+system. Given this goal, we used fHoG and color-naming features in an
 efficient way for the proposed {\it E}nKCF. Deep features, on the
@@
 KCFs based trackers \cite{ma2015hierarchical,
-  danelljan2015convolutional}. We hypothesize that the {\it E}nKCF
-tracker could perform better with deep features trained on ImageNet
-dataset. Utilizing pretrained deep features would not be applicable to
+  danelljan2015convolutional}. Following the recent trend, we hypothesize 
+that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
+dataset. Utilizing pre-trained deep features would not be applicable to
 all the a single-board, embedded system due to their limited
-computational resources. But as these days some of the single-board
+computational resources. However, as these days some of the single-board
 systems offer GPU, we would like to see how much accuracy we can
-achieve by feeding {\it E}nKCF w/ conv features as shown in figure~\ref{fig:Filters_CNN}.
+achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in figure~\ref{fig:Filters_CNN}.
 \begin{comment}
@@
 slightly better than \textit{conv222-VGG} in precision while achieving
-similar success rate (AUC).
-
-\begin{figure}[t]
+similar success rate (AUC) indicating that higher level feature absractions 
+works better for the smaller ROIs.
+\begin{figure}[!h]
 \centering
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
+\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
+dataset.}
 \label{fig:UAV123_DATASET_DeepFeatures}

### 2017-09-03 wacv_for_review.tex
Revised a bit.

@@
 applications running on embedded systems. This is primarily because
-most of embedded systems already come with an image acquisition
-pipeline, and a tremendous amount of progresses on research has been
-made for many areas in computer vision. However, to successfully
-deploy a computer vision algorithm on any existing embedded systems, a
-vision algorithm needs to satisfy, at least, two criteria with
-assumption of reasonably good performance: minimal, manual
-intervention after deployment and small footprint of consuming
-computational resources and executable code. To develop a single,
-target tracking system in high accuracy and run-time performance while
-these criteria kept in mind, we propose an ensemble of the kernelized
+most of embedded systems come with an image acquisition pipeline, and
+a tremendous amount of progresses on computer vision research has been
+made for the past few decades. However, to successfully deploy a
+computer vision algorithm on any existing embedded systems, a vision
+algorithm needs to satisfy, at least, two criteria with the assumption
+of reasonably good performance: minimal, manual intervention after
+deployment and small footprint of consuming computational
+resources. While these criteria kept in mind, to develop a single,
+target tracking system, we propose an ensemble of the kernelized
 correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
@@
 maneuver of the target over frames. In particular, to guarantee a
-high-speed, run-time performance, we deploy each of KCFs in turn and assign 
-them hand-crafted features including histogram of oriented gradients and color features.
-For a smooth transition between individual KCFs' executions, we developed
-a Bayes filter. Experimental results showed that the performance of
-ours are, on average, 70.10\% for precision at 20 pixels, 53.00\% for
-success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
-data. These results showed that our method is better than existing
-ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
-average. Moreover our implementation ran at 340 fps for OTB100 and at
-416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
-and KCF (292 fps), DCF (457 fps) for UAV123. Finally, dedicated for the embedded
-systems with GPUs, we explored different levels of deep features for different
-correlation filters to boost tracking performance and call it Deep{\it E}nKCF. 
+high-speed, run-time performance, we deploy each of KCFs in turn. We
+also developed a Bayes filter to minimize any potential drifts between
+individual KCFs' transitions. Experimental results showed that the
+performance of ours are, on average, 70.10\% for precision at 20
+pixels, 53.00\% for success rate for OTB100 data, and 54.50\% and
+40.2\% for UAV123 data. These results showed that our method is better
+than existing ones over 5\% on precision on 20 pixels and 10-20\% on
+AUC on average. Moreover our implementation ran at 340 fps for OTB100
+and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
+OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. To increase
+flexibility of the proposed {\it E}nKCF running on various one-chip
+computer, e.g., one with GPUs, we explored different levels of deep
+features.
 \end{abstract}
@@
 because payloads of those mobile platforms are limited to carry any
-other sensors than a lightweight or an array of monocular
-cameras. Given such a trend, instead of just manually flying for video
-recording, an unmanned air vehicle (UAV) equipped with an object or
-feature following functionality would make it more useful in the
-application of monitoring/surveillance/surveying on private
+other sensors than a monocular camera. Instead of just manually being
+flew for video recording, an unmanned air vehicle (UAV) equipped with
+an object or feature following functionality would make it more useful
+in the application of monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
@@
   performance of a computer vision algorithm at an Intel or AMD
-  processor running on a desktop or a laptop and at that, e.g., ARM,
+  processor running on a desktop or a laptop and at that (e.g., ARM)
   of a single-board, embedded system. This is primarily due to the
@@
 framework assumes that a target location is given at the beginning
-like other online tracking algorithms
+like any other online tracking algorithms
 \cite{smeulders2014survey}. Given this positive example for the
@@
 
-The contribution of this study is a novel, single-target tracking
+The contribution of this paper is a novel, single-target tracking
 algorithm running in a very high-speed, $\geq 300$ fps that deploys an
@@
 variance and the dynamic maneuver of a target while preserving
-run-time performance as high as possible. To minimize any potential
-performance gap from transiting one KCF to another, we use a Bayes
-filter. Finally, we explore deep features with varying levels of abstraction
-in the proposed {\it E}nKCF to improve tracking performance.
+run-time performance as high as possible. We also developed a Bayes
+filter to minimize any potential drifts while transiting one KCF to
+another. In addition, we explore deep features with varying levels of
+abstraction in the proposed {\it E}nKCF to improve tracking
+performance and increase its flexibility being deployed on high-end,
+one-chip computer with GPUs.
 
@@
 noisy shape features due to its large search area. In what follows, we
-will briefly describe the parts of the KCF related to this work.
-
-\textbf{{\it E}nKCF with Hand-crafted Features}
-We, first, explore traditional features to run  {\it E}nKCF on any embedded system as it is the primary
-objective of this study. In this direction, we employ two highly efficient features; fHoG \cite{felzenszwalb2010object}
-and color-naming \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of the region of interest (ROI) associated with $R_{t}^{S}$,
-$R_{t}^{L}$, and $R_{s}$. This version of {\it E}nKCF is dedicated to run
-on any embedded system at real-time ($30$fps).
-
-We used different features for each of three KCFs as each of them 
-has different goals to accomplish. In particular, the translation filter, $R_{t}^{L}$, 
-uses both the fHoG \cite{felzenszwalb2010object}
-and color-naming \cite{van2009learning} features to more effectively
-learn the large background area around the target as shown in figure~\ref{fig:Filters}. The color features
-compensate for the noisier shape features due to the large ROI considered by $R_{t}^{L}$.
-On the other hand, color features is not assigned to $R_{t}^{S}$ as it learns more useful shape
-features than $R_{t}^{L}$ due to smaller padding size. Finally, $R_{s}$ is assigned both fHoG 
-and color-naming features since we believe that the lower template resolution (64 x n) assigned to
-$R_{s}$ might lead to less discriminative shape features. Smaller template size is assigned to 
-$R_{s}$ as it estimates the scale by correlating the filter with three ROIs as shown in alg.~\ref{alg:MKCF}. 
-This way, we can keep the run-time complexity of the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that 
-only run correlation filter on a single ROI. By doing so, we can avoid fluctuating run-time performance 
-which is not desired in embedded systems.
-%Through experiments, we found that only fHoG didn't work well 
-%to cover a larger ROI; another translation filter, $R_{t}^{S}$, worked well when it used fHoG
-%features only; the scale filter, $R_{s}$ did when it used both fHoG
-%and color features.
-
-\textbf{{\it E}nKCF with Convolutional Neural Network Features}
-In addition to hand-crafted features, we explore deep features
-to boost tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, 
-is dedicated to run on high-end embedded systems (GPUs).
-
-There have been large volume of stuides on utilizing a pre-trained CNN features to
-tracking-by-detection algorithms. For example,
-\cite{danelljan2015convolutional} used the activations of the first
-and second convolutional layer features of the VGGNet
-\cite{simonyan2014very} for this idea where their experiments showed
-that the first convolutional layer features lead to slightly better
-precision and success rates than the second
-layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
-features. Their method employs the third convolutional layer features
-to estimate the response map. In the next stage, they used the estimation
-of the target's transition from the first phase to use the second
-convolutional layer features and update transition estimation. 
-Finally, the first convolutional layer features is extracted from the ROI estimated 
-in the second stage. This coarse-to-fine position estimation approach accommodates
-different levels of abstractions of the object. However, such
-approach runs multiple KCFs at a single frame, increasing
-the run-time complexity. For this reason, we follow a similar approach
-to \cite{danelljan2015convolutional} to embed deep features in {\it E}nKCF.
-
-Our {\it E}nKCF framework allows us to exploit different
-level of feature encodings in different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area
-than $R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it relies on less spatial information than
-$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
-fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
-whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
-the second layer features ($109\times109\times64$). This feature
-assignment scheme is represented as \textit{conv224-VGG} and shown in
-fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
-convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
-$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
-resolution at the first layers than AlexNet
-\cite{krizhevsky2012imagenet}.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
-\label{fig:Filters_CNN}
-\end{figure}
+will detail each part of the KCF.
 
@@
 
+\textbf{{\it E}nKCF with Hand-Crafted Features}
+
+{\it Burak: You need to rewrite this section and the section about
+  deep features! Try to make it concise with short sentences! It is
+  even hard for me to read this section and catch the main idea.}
+
+We, first, use two
+conventional features, fHoG \cite{felzenszwalb2010object} and
+color-naming \cite{li2014scale}, to make {\it E}nKCF run on any
+embedded systems faster than 30 fps. {\it Burak: You need to make
+  these two sentences connected -- the one begin with ``We, first,
+  use,'' and ``Figure ..''}
+
+Figure \ref{fig:Filters} shows examples of the region of interest
+(ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
+
+We used different features for each of three KCFs to address different
+challenges. In particular, the translation filter, $R_{t}^{L}$, uses
+both the fHoG \cite{felzenszwalb2010object} and color-naming
+\cite{van2009learning} features to learn the large background area
+around the target as shown in Figure~\ref{fig:Filters}. {\it Burak:
+  There are three subfigures in Figure \ref{fig:Filters}. You need to
+  tell the readers of this paper which one they need to look at if
+  they want to.}
+
+The color features compensate for the noisier shape features due to
+the large ROI considered by $R_{t}^{L}$. {\it Burak: You meant ``the
+  color features are used to compensate for shape features' weakness
+  -- what's weakness?}
+
+On the other hand, color features is not assigned to $R_{t}^{S}$ as it
+learns more useful shape features than $R_{t}^{L}$ due to smaller
+padding size. {\it Burak: color features are not used for $R_{t}^{S}$ because?}
+
+Both fHoG and color-naming features are used for $R_{s}$ to ? {\it
+  Burak: DO NOT USE $R_s$ just only, alway use them with their names,
+  the scale filter. This would just confuse the reader! Don't expect
+  for them to remember what you said earlier!}
+
+since we believe that the lower template resolution (64 x n)
+assigned to $R_{s}$ might lead to less discriminative shape
+features.
+
+Smaller template size is assigned to $R_{s}$ as it estimates
+the scale by correlating the filter with three ROIs as shown in
+alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
+the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
+correlation filter on a single ROI. By doing so, we can avoid
+fluctuating run-time performance which is not desired in embedded
+systems.
+
+\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
+addition to hand-crafted features, we explore deep features to boost
+tracking performance. {\it Burak: Did EnKCF w/ deep features really
+  improve the performance -- the performance tested on the same data?
+  or did you just compare the performance numbers?}
+
+This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
+devised to make {\it E}nKCF run on high-end embedded systems with GPUs
+installed.
+
+There has been a large volume of studies on utilizing a pre-trained
+CNN features to tracking-by-detection algorithms. For example,
+\cite{danelljan2015convolutional} used the activations of the first
+and second convolutional layer of the VGGNet \cite{simonyan2014very}
+as features for this idea where their experiments showed that the
+first convolutional layer features lead to slightly better precision
+and success rates than the second layer. \cite{ma2015hierarchical}
+proposed a KCF tracker with deeper features. Their method employs the
+third convolutional layer features to estimate the response map. In
+the next stage, they used the estimation of the target's transition
+from the first phase to use the second convolutional layer features
+and update transition estimation.  Finally, the first convolutional
+layer features is extracted from the ROI estimated in the second
+stage. This coarse-to-fine position estimation approach accommodates
+different levels of abstractions of the object. However, such approach
+runs multiple KCFs at a single frame, increasing the run-time
+complexity. For this reason, we follow a similar approach to
+\cite{danelljan2015convolutional} to embed deep features in {\it
+  E}nKCF.
+
+Our {\it E}nKCF framework allows us to exploit different level of
+feature encodings with different KCFs. The translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
+$R_{s}$. Taking this into account, we can assign deeper feature
+encodings to $R_{s}$ as it relies on less spatial information than
+$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
+fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
+whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
+the second layer features ($109\times109\times64$). This feature
+assignment scheme is represented as \textit{conv224-VGG} and shown in
+fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
+convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
+$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
+\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
+resolution at the first layers than AlexNet
+\cite{krizhevsky2012imagenet}.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
+\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
+\label{fig:Filters_CNN}
+\end{figure}
+
 \textbf{Particle Filter for Smoothing Transition among KCFs} As
@@
 %---------------------------------------------------------------------- 
+{\it Burak: We cannot just begin with a detail. You need to give the
+  readers an overview of what they'll be reading.}
+
 We first evaluate the performance of {\it E}nKCF with hand-crafted features.
@@
 
-\textbf{Evalution on Particle Filter Contribution} For the $UAV123$ dataset, we also evaluated the performance of the
-{\it E}nKCF with and without the particle filter. In particular, we
-use 50 sequences labeled as no abrupt camera motion in the dataset. To
-evaluate the robustness of particle filter, we add noise, drawn from a
-uniform distribution ($[-20,20]$), to the translation estimations of
-the KCFs. In these setup, the {\it E}nKCF with particle filter
-achieves $51.98\%$ precision ($20$px), outperforming the one without
-particle filter {\it E}nKCF by $6.32\%$. Thus, with the removal of
-global camera motion, the integration of particle filter into the {\it
-  E}nKCF as shown in Figure \ref{Workflows} further improved the
-results.
+\textbf{Evalution on Particle Filter Contribution} For the $UAV123$
+dataset, we also evaluated the performance of the {\it E}nKCF with and
+without the particle filter. In particular, we use 50 sequences
+labeled as no abrupt camera motion in the dataset. To evaluate the
+robustness of particle filter, we add noise, drawn from a uniform
+distribution ($[-20,20]$), to the translation estimations of the
+KCFs. In these setup, the {\it E}nKCF with particle filter achieves
+$51.98\%$ precision ($20$px), outperforming the one without particle
+filter {\it E}nKCF by $6.32\%$. Thus, with the removal of global
+camera motion, the integration of particle filter into the {\it E}nKCF
+as shown in Figure \ref{Workflows} further improved the results.
 
@@
 
+{\it Burak: No summary on EnKCF w/ deep features?}
+
 As future work, we investigate a way of re-initializing a target when

### 2017-09-05 wacv_for_review.tex
Comments Replied

@@
 \usepackage{amssymb}
+\usepackage{subfig}
 \usepackage{graphicx}
@@
 correlation filter should focus on the target itself to estimate the
-right scale of the target.
+right scale of the target as shown in Figure~\ref{fig:Filters}.
 
@@
 this observation.
-\begin{figure}[!b]
+\begin{figure}[!h]
 \centering
 \includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
+   \\[-3ex]
+\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
+\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
+\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
 \caption{Examples of three filters with hand-crafted features; the translation filter,
@@
 \end{figure}
+
 \begin{figure*}[!h]
@@
 
-We, first, use two
-conventional features, fHoG \cite{felzenszwalb2010object} and
-color-naming \cite{li2014scale}, to make {\it E}nKCF run on any
-embedded systems faster than 30 fps. {\it Burak: You need to make
-  these two sentences connected -- the one begin with ``We, first,
-  use,'' and ``Figure ..''}
+We, first, use two hand-crafted features, fHoG \cite{felzenszwalb2010object} 
+and color-naming \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
+This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
+$30$ fps.
 
-Figure \ref{fig:Filters} shows examples of the region of interest
-(ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
-
-We used different features for each of three KCFs to address different
-challenges. In particular, the translation filter, $R_{t}^{L}$, uses
+In particular, the translation filter, $R_{t}^{L}$, uses
 both the fHoG \cite{felzenszwalb2010object} and color-naming
 \cite{van2009learning} features to learn the large background area
-around the target as shown in Figure~\ref{fig:Filters}. {\it Burak:
-  There are three subfigures in Figure \ref{fig:Filters}. You need to
-  tell the readers of this paper which one they need to look at if
-  they want to.}
-
-The color features compensate for the noisier shape features due to
-the large ROI considered by $R_{t}^{L}$. {\it Burak: You meant ``the
+around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
+compensate for the noisier fHoG features due to the large ROI considered 
+by $R_{t}^{L}$. {\it Burak: You meant ``the
   color features are used to compensate for shape features' weakness
@@
 
-On the other hand, color features is not assigned to $R_{t}^{S}$ as it
-learns more useful shape features than $R_{t}^{L}$ due to smaller
-padding size. {\it Burak: color features are not used for $R_{t}^{S}$ because?}
-
-Both fHoG and color-naming features are used for $R_{s}$ to ? {\it
-  Burak: DO NOT USE $R_s$ just only, alway use them with their names,
-  the scale filter. This would just confuse the reader! Don't expect
-  for them to remember what you said earlier!}
-
-since we believe that the lower template resolution (64 x n)
-assigned to $R_{s}$ might lead to less discriminative shape
-features.
-
-Smaller template size is assigned to $R_{s}$ as it estimates
-the scale by correlating the filter with three ROIs as shown in
+  {\it YoungWoo : The weakness is the more background you include the noisier
+  HoG features become.}
+On the other hand, the color features is not assigned to the small area translation 
+filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
+padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
+\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
+than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used for $R_{s}$, the scale filter, 
+since the lower template resolution (64 x n)
+assigned to $R_{s}$ leads to less discriminative shape
+features as in Figure~\ref{fig:Filters}.c. Smaller template size is assigned to $R_{s}$ as it estimates
+the scale by correlating the filter with multiple ROIs as shown in
 alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
@@
 correlation filter on a single ROI. By doing so, we can avoid
-fluctuating run-time performance which is not desired in embedded
+fluctuating run-time performance among KCFs which is not desired in embedded
 systems.
@@
   or did you just compare the performance numbers?}
-
+  {\it YoungWoo : EnkCF with deep features improved the performance on the same set of data.}
 This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
@@
 and second convolutional layer of the VGGNet \cite{simonyan2014very}
-as features for this idea where their experiments showed that the
+for this idea where their experiments showed that the
 first convolutional layer features lead to slightly better precision
 and success rates than the second layer. \cite{ma2015hierarchical}
-proposed a KCF tracker with deeper features. Their method employs the
-third convolutional layer features to estimate the response map. In
+proposed a KCF tracker integrating features with higher abstraction capacity. 
+Their method first employs the third convolutional layer features to estimate the response map. In
 the next stage, they used the estimation of the target's transition
@@
 layer features is extracted from the ROI estimated in the second
-stage. This coarse-to-fine position estimation approach accommodates
+stage. This coarse-to-fine approach accommodates
 different levels of abstractions of the object. However, such approach
@@
 $R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
-$R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it relies on less spatial information than
+the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
+encodings to $R_{s}$ as it learns less spatial information than
 $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
@@
 \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
-resolution at the first layers than AlexNet
+resolution at the first several layers than AlexNet
 \cite{krizhevsky2012imagenet}.
@@
 
-We first evaluate the performance of {\it E}nKCF with hand-crafted features.
+In this section, we evaluate the performance of the proposed {\it E}nKCF
+tracker and its variants on the object tracking benchmarks. 
 In this direction, we choose two publicly, available datasets:
@@
 The OTB100 dataset is comprised of the videos about 100 objects
-whereas UAV123 dataset contains aerial footages of 123 objects. We aim
+whereas UAV123 dataset contains aerial footages of 123 objects.
+We first evaluate the performance of {\it E}nKCF 
+with hand-crafted features.  With this tracker, we aim
 at developing an object tracking algorithm that ``efficiently'' runs
@@
 system. Given this goal, we used fHoG and color-naming features in an
-efficient way for the proposed {\it E}nKCF. Deep features, on the
+efficient way in the proposed {\it E}nKCF. Deep features, on the
 other hand, recently have been used to boost tracking accuracy of the
@@
 slightly better than \textit{conv222-VGG} in precision while achieving
-similar success rate (AUC) indicating that higher level feature absractions 
+similar success rate (AUC) indicating that higher level feature absraction
 works better for the smaller ROIs.
@@
 for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
-(292 fps), DCF (457 fps) for UAV123.
-
-{\it Burak: No summary on EnKCF w/ deep features?}
+(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
+feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
+To further improve the performance, we employed deeper features to the scale filter as it learns smaller ROI
+than the translation filters.
 

### 2017-09-05 wacv_for_review.tex
Comments Replied
Another revision.

@@
 and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
-OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. To increase
-flexibility of the proposed {\it E}nKCF running on various one-chip
-computer, e.g., one with GPUs, we explored different levels of deep
-features.
+OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. In addition, to
+increase flexibility of the proposed {\it E}nKCF running on various
+one-chip computer, e.g., one with GPUs, we explored different levels
+of deep features.
 \end{abstract}
@@
 KCFs \cite{henriques2015high} to effectively handle scale variations
-and dynamic maneuvers of a target. To maintain or improve the run-time
-performance of the original KCF (e.g., $\ge$ 300), we deploy three
-KCFs in turn, instead of applying them on the same image frame
+and dynamic maneuvers of a target. To maintain or even improve the
+run-time performance of the original KCF (e.g., $\ge$ 300), we deploy
+three KCFs in turn, instead of applying them on the same image frame
 together. Each of these KCFs is designed to address specific
@@
 correlation filter should focus on the target itself to estimate the
-right scale of the target as shown in Figure~\ref{fig:Filters}.
+right scale of the target. {\it Burak: We only explained two kinds of
+  filters: translation and scale filter. But we do have two filters
+  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
+  the sentence about translation filter with details.}
+
+{\it Burak: DO NOT use ``Figure~\ref{fig:Filters}'' just write ``Figure \ref{fig:Filters}''}
+\begin{comment}
+ as shown in Figure~\ref{fig:Filters}.
+\end{comment}
+
+Figure \ref{fig:Filters} shows examples of three filters.
 
@@
 \quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
-\caption{Examples of three filters with hand-crafted features; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
+\caption{Examples of three filters with hand-crafted features: the
+  translation filter, \textit{target+small background}, another
+  translation filter for capturing the bigger background,
+  \textit{target+large background}, and the scale filter,
+  \textit{target-only} depicted in their Hanning windows and expected
+  Gaussian response.}
 \label{fig:Filters}
@@
 integrate more discriminative shape features that cannot be learned by
-$R_{t}^{L}$. This is because it incorporates a large area about
-background in the learned model. The filter, $R_{t}^{L}$, uses shape
-and color information together to recover from any potential drifts --
-drifts could happen only looking the target's scale by the filter,
-$R_{s}$.
+learning only $R_{t}^{L}$. This is because it incorporates a large
+area about background in the learned model. The filter, $R_{t}^{L}$,
+uses shape and color information together to recover from any
+potential drifts -- drifts potentially occurring only by learning the
+target's scale with the scale filter, $R_{s}$.
 
@@
 drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
-designed to addresses the drawback of $R_{t}^{L}$ that it may learn
-noisy shape features due to its large search area. In what follows, we
-will detail each part of the KCF.
+designed to addresses the drawback of $R_{t}^{L}$ that may learn noisy
+shape features due to its large search area. In what follows, we will
+detail each part of the {\it E}nKCF.
 
@@
 
-We, first, use two hand-crafted features, fHoG \cite{felzenszwalb2010object} 
-and color-naming \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
-This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
-$30$ fps.
+{\it Burak: This section does NOT connect to the previous section.}
 
-In particular, the translation filter, $R_{t}^{L}$, uses
-both the fHoG \cite{felzenszwalb2010object} and color-naming
-\cite{van2009learning} features to learn the large background area
-around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
-compensate for the noisier fHoG features due to the large ROI considered 
-by $R_{t}^{L}$. {\it Burak: You meant ``the
-  color features are used to compensate for shape features' weakness
-  -- what's weakness?}
+We, first, use two hand-crafted features, fHoG
+\cite{felzenszwalb2010object} and color-naming \cite{li2014scale} in
+the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. {\it Burak:
+  Figure \ref{fig:Filters} is placed a way before this sentence -- We
+  don't want the readers to look back while reading a certain
+  sentence. And I don't see fHoG and color-naming or descriptions of
+  them from that Figure.}
 
-  {\it YoungWoo : The weakness is the more background you include the noisier
-  HoG features become.}
-On the other hand, the color features is not assigned to the small area translation 
-filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
-padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
-\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
-than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used for $R_{s}$, the scale filter, 
-since the lower template resolution (64 x n)
-assigned to $R_{s}$ leads to less discriminative shape
-features as in Figure~\ref{fig:Filters}.c. Smaller template size is assigned to $R_{s}$ as it estimates
-the scale by correlating the filter with multiple ROIs as shown in
-alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
-the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI. By doing so, we can avoid
-fluctuating run-time performance among KCFs which is not desired in embedded
-systems.
+This version of the {\it E}nKCF is designed to execute a single,
+target tracking on any embedded systems at $30$ fps.
+
+The translation filter, $R_{t}^{L}$, uses both the fHoG
+\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
+features to learn the large background area around the target. Figure
+\ref{fig:Filters} (b) shows an example of this translation filter. The
+color features are also used to make the feature vector more
+discriminative. In other words, for the case that the fHoG is the only
+feature, the bigger the area for HoG is the more noises the resulting
+fHoG feature contains. Adding color information to the feature vector
+will make the feature vector more robust to the noises from the
+background around the target. However, this is not the case for the
+translation filter, $R_{t}^{S}$, for capturing a smaller area. This is
+because the translation filter, {\it target + small background}, does
+not contain much of the background area around the target. Figure
+\ref{fig:Filters} (a) shows an example of this translation filter.
+
+\begin{comment}
+On the other hand, the color features is not assigned to the small
+area translation filter, $R_{t}^{S}$, as it learns more useful fHoG
+features than $R_{t}^{L}$ due to smaller padding size as seen in
+Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used
+  for $R_{t}^{S}$ because?  \it YoungWoo : We do not use color
+  features because $R_{t}^{S}$ concentrates on smaller ROI than
+  $R_{t}^{L}$}.
+\end{comment}
+
+We use both fHoG and color-naming features for the scale filter, $R_{s}$.
+
+{\it Burak: The following sentence was NOT clear. Rewrite. Look at
+  what I wrote about the translation filter, $R_{t}^{L}$.}  since the
+lower template resolution (64 x n) assigned to $R_{s}$ leads to less
+discriminative shape features as in Figure~\ref{fig:Filters}.c.
+
+Smaller template size is assigned to $R_{s}$ as it estimates the scale
+by correlating the filter with multiple ROIs as shown in
+alg.~\ref{alg:MKCF}.  {\it Burak: Try to minimize such a
+  BACK-reference. No one like looking back the parts of a paper you
+  already read!}
+
+This way, we can keep the run-time complexity of the $R_{S}$ similar
+to $R_{t}^{L}$ and $R_{t}^{S}$ that only run correlation filter on a
+single ROI. {\it Burak: Why do we need to keep the run-time complexity
+  of $R_{S}$ and $R_{t}^{L}$ the same?}
+
+By doing so, we can avoid fluctuating run-time performance among KCFs
+which is not desired in embedded systems. {\it Burak: By doing what,
+  you can avoid fluctuating run-time performance? Rewrite this
+  sentence in connection with the above-mentioned!}
 
@@
 addition to hand-crafted features, we explore deep features to boost
-tracking performance. {\it Burak: Did EnKCF w/ deep features really
+tracking performance.
+
+{\it Burak: Did EnKCF w/ deep features really
   improve the performance -- the performance tested on the same data?
   or did you just compare the performance numbers?}
-  {\it YoungWoo : EnkCF with deep features improved the performance on the same set of data.}
+
+{\it YoungWoo :
+  EnkCF with deep features improved the performance on the same set of
+  data.}
+
+{\it Burak: If EnKCF w/ deep features improved the performance of
+  EnKCF on the same set of data, why didn't you plot their curves
+  together? And if this is true, we'll have to revise the abstract and
+  introduction as well!}
+
 This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
@@
 
-\textbf{Particle Filter for Smoothing Transition among KCFs} As
-explained earlier, the {\it E}nKCF updates a target's translation at
-every other $k$ frames, particularly for estimating the target's
+\textbf{Particle Filter for Smoothing Transition among KCFs}
+
+{\it Burak: Does what this section explains still hold good? If what
+  this section explains still makes sense, the translation filter,
+  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
+  this section.}
+
+As explained earlier, the {\it E}nKCF updates a target's translation
+at every other $k$ frames, particularly for estimating the target's
 scale. Although the strategy of updating every other $k$th frames will
@@
 %---------------------------------------------------------------------- 
-{\it Burak: We cannot just begin with a detail. You need to give the
-  readers an overview of what they'll be reading.}
-
 In this section, we evaluate the performance of the proposed {\it E}nKCF
@@
 drastic motions of camera and targets.
+
+{\it Burak: What happened to the experiment of DNN features? You'll
+  have to preview whatever the readers will read below this section!}
 
@@
 for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
-(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
-feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
-To further improve the performance, we employed deeper features to the scale filter as it learns smaller ROI
-than the translation filters.
+(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects
+with deep feature encodings to boost tracking performance by about
+$5\%$ on embedded systems with GPUs.  To further improve the
+performance, we employed deeper features to the scale filter as it
+learns smaller ROI than the translation filters. {\it Burak: We
+  employed deeper features and then what happened?}
 

### 2017-09-05 wacv_for_review.tex
Final Replies to Comments

--- 2017-09-05 wacv_for_review.tex
@@
 
-We, first, use two hand-crafted features, fHoG \cite{felzenszwalb2010object} 
-and color-naming \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
+We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
+and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
 This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
-$30$ fps.
+$30$ fps, particularly on the ones without GPU units.
 
-In particular, the translation filter, $R_{t}^{L}$, uses
+In particular, the translation filter, $R_{t}^{L}$, employs
 both the fHoG \cite{felzenszwalb2010object} and color-naming
@@
 around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
-compensate for the noisier fHoG features due to the large ROI considered 
+compensate for the noisier fHoG features due to the large background area considered 
 by $R_{t}^{L}$. {\it Burak: You meant ``the
@@
 \it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
-than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used for $R_{s}$, the scale filter, 
-since the lower template resolution (64 x n)
-assigned to $R_{s}$ leads to less discriminative shape
-features as in Figure~\ref{fig:Filters}.c. Smaller template size is assigned to $R_{s}$ as it estimates
+than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
+since the ROI is resized to a lower template resolution (64 x n) than the translation filters. This leads to 
+less discriminative shape features as in Figure~\ref{fig:Filters}.c. The $R_{s}$ estimates
 the scale by correlating the filter with multiple ROIs as shown in
-alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
+alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
+number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
+due to two major reasons: (1) zero padding size and (2) integration of color features.
+This way, we keep the run-time complexity of
 the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI. By doing so, we can avoid
-fluctuating run-time performance among KCFs which is not desired in embedded
-systems.
+correlation filter on a single ROI. By doing so, fluctuating run-time performances among KCFs are avoided which is
+desired in embedded systems.
 
@@
 \cite{danelljan2015convolutional} used the activations of the first
-and second convolutional layer of the VGGNet \cite{simonyan2014very}
-for this idea where their experiments showed that the
-first convolutional layer features lead to slightly better precision
-and success rates than the second layer. \cite{ma2015hierarchical}
+and second convolutional layer of the VGGNet \cite{simonyan2014very}.
+They report that the first convolutional layer features lead to slightly better precision
+and success rates than the second layer due to lost spatial information this layer. \cite{ma2015hierarchical}
 proposed a KCF tracker integrating features with higher abstraction capacity. 
 Their method first employs the third convolutional layer features to estimate the response map. In
-the next stage, they used the estimation of the target's transition
-from the first phase to use the second convolutional layer features
-and update transition estimation.  Finally, the first convolutional
-layer features is extracted from the ROI estimated in the second
-stage. This coarse-to-fine approach accommodates
-different levels of abstractions of the object. However, such approach
-runs multiple KCFs at a single frame, increasing the run-time
+the next stage, the KCF, concentrating on the second convolutional layer features, is run to update
+transition. The third KCF then works on the transition given by the previous KCF and learns the first convolutional
+layer features to update the transition. This coarse-to-fine approach accommodates
+different levels of abstractions of the object. However, it
+runs multiple KCFs in a sequential fashion, increasing the run-time
 complexity. For this reason, we follow a similar approach to
@@
 feature encodings with different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
+$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
 the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
@@
 $R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
+\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
 resolution at the first several layers than AlexNet
@@
 We first evaluate the performance of {\it E}nKCF 
-with hand-crafted features.  With this tracker, we aim
-at developing an object tracking algorithm that ``efficiently'' runs
+with hand-crafted features as shown in Figure~\ref{fig:Filters}.  
+With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
 on an embedded system, a drone, for example, in ``high speed,'' $\ge
@@
 feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
-To further improve the performance, we employed deeper features to the scale filter as it learns smaller ROI
-than the translation filters.
+To further improve the performance, we employed deeper features in the scale filter since it has zero
+padding around the target.
 

### 2017-09-05 wacv_for_review.tex

@@
 correlation filter should focus on the target itself to estimate the
-right scale of the target as shown in Figure~\ref{fig:Filters}.
+right scale of the target {\it Burak: We only explained two kinds of
+  filters: translation and scale filter. But we do have two filters
+  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
+  the sentence about translation filter with details.} 
+  {\it YoungWoo : In this paragraph, we mention two of the translation filters and then we say
+  translation filter needs background whereas the scale filter does not.}
+Figure \ref{fig:Filters} shows examples of three filters.
 
@@
 
+{\it Burak: This section does NOT connect to the previous section.}
+
+{\it YoungWoo : I placed EnKCF with traditional and deep features section right after EnKCF section. Later, you
+placed them after the Kernelized Correlation Filter section. }
+
+\textbf{{\it E}nKCF with Hand-Crafted Features} 
+We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
+and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
+This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
+$30$ fps, particularly on the ones without GPU units.
+
+The translation filter, $R_{t}^{L}$, uses both the fHoG
+\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
+features to learn the large background area around the target. Figure
+\ref{fig:Filters} (b) shows an example of this translation filter. The
+color features are also used to make the feature vector more
+discriminative. In other words, for the case that the fHoG is the only
+feature, the bigger the area for HoG is the more noises the resulting
+fHoG feature contains. Adding color information to the feature vector
+will make the feature vector more robust to the noises from the
+background around the target. However, this is not the case for the
+translation filter, $R_{t}^{S}$, for capturing a smaller area. This is
+because the translation filter, {\it target + small background}, does
+not contain much of the background area around the target. Figure
+\ref{fig:Filters} (a) shows an example of this translation filter. 
+Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
+The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters} (c). 
+This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
+The $R_{s}$ estimates the scale by correlating the filter with multiple ROIs as shown in
+alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
+number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
+due to two major reasons: (1) zero padding size and (2) integration of color features.
+This way, we keep the run-time complexity of
+the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
+correlation filter on a single ROI. {\it Burak: Why do we need to keep the run-time complexity
+  of $R_{S}$ and $R_{t}^{L}$ the same?} {\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$ to 
+  have similar fps (30fps) to avoid missing frames on an embedded system. We can think of each one as an individual tracker
+  and we do not want one operating at 10fps while others running at 30 fps.} By reducing the template size of $R_{s}$,
+   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.
+
+\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
+addition to hand-crafted features, we explore deep features to boost
+tracking performance.
+
+{\it Burak: Did EnKCF w/ deep features really
+  improve the performance -- the performance tested on the same data?
+  or did you just compare the performance numbers?}
+
+{\it YoungWoo :
+  EnkCF with deep features improved the performance on the same set of
+  data.}
+
+{\it Burak: If EnKCF w/ deep features improved the performance of
+  EnKCF on the same set of data, why didn't you plot their curves
+  together? And if this is true, we'll have to revise the abstract and
+  introduction as well!}
+
+  {\it YoungWoo : I compare the EnKCF with all the other trackers that does not use deep features. For this reason
+  it does not make sense to put DeepEnKCF in the same figure (Figure 6). We have a separate section 
+  showing how much improvement we get by using deep features and in this section I plot them in the same figure ( Figure (8) ).}
+
+This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
+devised to make {\it E}nKCF run on high-end embedded systems with GPUs
+installed.
+
+There has been a large volume of studies on utilizing a pre-trained
+CNN features to tracking-by-detection algorithms. For example,
+\cite{danelljan2015convolutional} used the activations of the first
+and second convolutional layer of the VGGNet \cite{simonyan2014very}.
+They report that the first convolutional layer features lead to slightly better precision
+and success rates than the second layer due to lost spatial information this layer. \cite{ma2015hierarchical}
+proposed a KCF tracker integrating features with higher abstraction capacity. 
+Their method first employs the third convolutional layer features to estimate the response map. In
+the next stage, the KCF, concentrating on the second convolutional layer features, is run to update
+transition. The third KCF then works on the transition given by the previous KCF and learns the first convolutional
+layer features to update the transition. This coarse-to-fine approach accommodates
+different levels of abstractions of the object. However, it
+runs multiple KCFs in a sequential fashion, increasing the run-time
+complexity. For this reason, we follow a similar approach to
+\cite{danelljan2015convolutional} to embed deep features in {\it
+  E}nKCF.
+
+Our {\it E}nKCF framework allows us to exploit different level of
+feature encodings with different KCFs. The translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
+the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
+encodings to $R_{s}$ as it learns less spatial information than
+$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
+fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
+whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
+the second layer features ($109\times109\times64$). This feature
+assignment scheme is represented as \textit{conv224-VGG} and shown in
+fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
+convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
+$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
+\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
+resolution at the first several layers than AlexNet
+\cite{krizhevsky2012imagenet}.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
+\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
+\label{fig:Filters_CNN}
+\end{figure}
+
 \textbf{Kernelized Correlation Filter} The Kernelized Correlation
@@
 
-\textbf{{\it E}nKCF with Hand-Crafted Features}
+\textbf{Particle Filter for Smoothing Transition among KCFs} 
+{\it Burak: Does what this section explains still hold good? If what
+  this section explains still makes sense, the translation filter,
+  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
+  this section.}
 
-{\it Burak: You need to rewrite this section and the section about
-  deep features! Try to make it concise with short sentences! It is
-  even hard for me to read this section and catch the main idea.}
+  {\it YoungWoo : I did not understand what $R_{t}^{L}$ has to do with 
+  particle filter}
 
-We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
-and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
-This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
-$30$ fps, particularly on the ones without GPU units.
-
-In particular, the translation filter, $R_{t}^{L}$, employs
-both the fHoG \cite{felzenszwalb2010object} and color-naming
-\cite{van2009learning} features to learn the large background area
-around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
-compensate for the noisier fHoG features due to the large background area considered 
-by $R_{t}^{L}$. {\it Burak: You meant ``the
-  color features are used to compensate for shape features' weakness
-  -- what's weakness?}
-
-  {\it YoungWoo : The weakness is the more background you include the noisier
-  HoG features become.}
-On the other hand, the color features is not assigned to the small area translation 
-filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
-padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
-\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
-than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
-since the ROI is resized to a lower template resolution (64 x n) than the translation filters. This leads to 
-less discriminative shape features as in Figure~\ref{fig:Filters}.c. The $R_{s}$ estimates
-the scale by correlating the filter with multiple ROIs as shown in
-alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
-number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
-due to two major reasons: (1) zero padding size and (2) integration of color features.
-This way, we keep the run-time complexity of
-the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI. By doing so, fluctuating run-time performances among KCFs are avoided which is
-desired in embedded systems.
-
-\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
-addition to hand-crafted features, we explore deep features to boost
-tracking performance. {\it Burak: Did EnKCF w/ deep features really
-  improve the performance -- the performance tested on the same data?
-  or did you just compare the performance numbers?}
-  {\it YoungWoo : EnkCF with deep features improved the performance on the same set of data.}
-This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
-devised to make {\it E}nKCF run on high-end embedded systems with GPUs
-installed.
-
-There has been a large volume of studies on utilizing a pre-trained
-CNN features to tracking-by-detection algorithms. For example,
-\cite{danelljan2015convolutional} used the activations of the first
-and second convolutional layer of the VGGNet \cite{simonyan2014very}.
-They report that the first convolutional layer features lead to slightly better precision
-and success rates than the second layer due to lost spatial information this layer. \cite{ma2015hierarchical}
-proposed a KCF tracker integrating features with higher abstraction capacity. 
-Their method first employs the third convolutional layer features to estimate the response map. In
-the next stage, the KCF, concentrating on the second convolutional layer features, is run to update
-transition. The third KCF then works on the transition given by the previous KCF and learns the first convolutional
-layer features to update the transition. This coarse-to-fine approach accommodates
-different levels of abstractions of the object. However, it
-runs multiple KCFs in a sequential fashion, increasing the run-time
-complexity. For this reason, we follow a similar approach to
-\cite{danelljan2015convolutional} to embed deep features in {\it
-  E}nKCF.
-
-Our {\it E}nKCF framework allows us to exploit different level of
-feature encodings with different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
-the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it learns less spatial information than
-$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
-fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
-whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
-the second layer features ($109\times109\times64$). This feature
-assignment scheme is represented as \textit{conv224-VGG} and shown in
-fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
-convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
-$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
-resolution at the first several layers than AlexNet
-\cite{krizhevsky2012imagenet}.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
-\label{fig:Filters_CNN}
-\end{figure}
-
-\textbf{Particle Filter for Smoothing Transition among KCFs} As
-explained earlier, the {\it E}nKCF updates a target's translation at
+As explained earlier, the {\it E}nKCF updates a target's translation at
 every other $k$ frames, particularly for estimating the target's
@@
 We first evaluate the performance of {\it E}nKCF 
-with hand-crafted features as shown in Figure~\ref{fig:Filters}.  
+with hand-crafted features as shown in Figure \ref{fig:Filters}.  
 With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
@@
 contains the videos recorded from smart phones and typical cameras in
-perspective view. Lastly, we tested the proposed algorithm on a
+perspective view. Also, we tested the proposed algorithm on a
 temporally down-sampled version of the UAV123 dataset, called
@@
 modified dataset is how robust the proposed algorithm is to the
-drastic motions of camera and targets.
+drastic motions of camera and targets. Finally, we evaluate the Deep{\it E}nKCF, 
+{\it E}nKCF with deep features, on the UAV123 dataset to observe how much gain
+we can achieve over hand-crafted features.
 
@@
 %and color-naming \cite{van2009learning} features to more effectively
-%learn the background around the target as shown in figure~\ref{fig:Filters}. 
+%learn the background around the target as shown in Figure \ref{fig:Filters}. 
 %Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
@@
 systems offer GPU, we would like to see how much accuracy we can
-achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in figure~\ref{fig:Filters_CNN}.
+achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in Figure \ref{fig:Filters_CNN}.
 \begin{comment}
@@
 feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
-To further improve the performance, we employed deeper features in the scale filter since it has zero
+We further improved the performance by employing deeper features in the scale filter since it has zero
 padding around the target.

### 2017-09-06 wacv_for_review.tex
Some more revision

@@
 last filter, $R_{t}^{L}$, focuses on the target area and its
-background, at least twice, bigger than that of the first filter,
-$R_{t}^{S}$, \textit{target}+\textit{large background}. We set up {\it
-  E}nKCF in this way because, we believe, a correlation filter for
+background bigger than that of the first filter, $R_{t}^{S}$, \textit{target}+\textit{large background}. 
+We set up {\it E}nKCF in this way because, we believe, a correlation filter for
 learning a target's translation should include its background to
@@
   translation filter needs background whereas the scale filter does not.}
-Figure \ref{fig:Filters} shows examples of three filters.
+Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.
 
@@
 noisy shape features due to its large search area. In what follows, we
-will detail each part of the KCF.
+will detail the {\it E}nKC with hand-crafted features, dedicated to run
+on low-end embedded systems, and deep features, designed to run on
+the systems with GPUs. Later, we will briefly document the fundamental 
+concepts of the KCF and Particle Filter, designed to smooth transitions 
+between KCFs.
 
@@
 {\it YoungWoo : I placed EnKCF with traditional and deep features section right after EnKCF section. Later, you
-placed them after the Kernelized Correlation Filter section. }
+placed them after the Kernelized Correlation Filter section. To me, it makes more
+sense to place them right after the EnKCF section.}
 
@@
 features to learn the large background area around the target. Figure
-\ref{fig:Filters} (b) shows an example of this translation filter. The
+\ref{fig:Filters}(b) shows an example of this translation filter. The
 color features are also used to make the feature vector more
 discriminative. In other words, for the case that the fHoG is the only
-feature, the bigger the area for HoG is the more noises the resulting
+feature, the bigger the area for HoG is the more noise the resulting
 fHoG feature contains. Adding color information to the feature vector
@@
 background around the target. However, this is not the case for the
-translation filter, $R_{t}^{S}$, for capturing a smaller area. This is
-because the translation filter, {\it target + small background}, does
-not contain much of the background area around the target. Figure
-\ref{fig:Filters} (a) shows an example of this translation filter. 
+translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
+does not contain much of the background area around the target. Figure
+\ref{fig:Filters}(a) shows an example of this translation filter. 
 Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
-The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters} (c). 
+The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
 This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
-The $R_{s}$ estimates the scale by correlating the filter with multiple ROIs as shown in
-alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
-number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
-due to two major reasons: (1) zero padding size and (2) integration of color features.
-This way, we keep the run-time complexity of
+The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
+alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
+To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
+This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
+and (2) integration of color features. This way, we keep the run-time complexity of
 the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
@@
 constant velocity motion model, a target's state by generating a
-predefined number of particles. And then the particle filter uses the
-confidence maps of {\it E}nKCF as observation to update the state. The
-weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
-\sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$, where $w_{p}$
-denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
+predefined number of particles. Then it uses the confidence maps of 
+{\it E}nKCF as observation to update the state. The weight of a particle is computed as
+\begin{equation}
+w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j), 
+\end{equation}
+where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
 size of the window as that of a confidence map. Alternatively one can
@@
 feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
-We further improved the performance by employing deeper features in the scale filter since it has zero
-padding around the target.
+We further improved the performance by employing deeper features in the scale filter 
+with zero padding around the target.
 

### 2017-09-06 wacv_for_review.tex
Spell-Checking Performed

@@
 \usepackage{amssymb}
-\usepackage{mathtools} % mathtools builds on and extends amsmath package
+\usepackage{mathtools} % mathtools builds on and exten0))ds amsmath package
 \usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
@@
 whereas the diagonal elements represent the eigenvalues of the
-circulant matrix. The egienvalues are equal to the DFT transformation
+circulant matrix. The eigenvalues are equal to the DFT transformation
 of the base sample ($x$) elements. The Kernelized Correlation Filter,
@@
 presents results of this experiment. For this experiment, we removed
-the particle filter. The method at the $2^{nd}$ column fliped the
+the particle filter. The method at the $2^{nd}$ column flipped the
 order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
@@
 
-\textbf{Evalution on Particle Filter Contribution} For the $UAV123$
+\textbf{Evaluation on Particle Filter Contribution} For the $UAV123$
 dataset, we also evaluated the performance of the {\it E}nKCF with and
@@
 slightly better than \textit{conv222-VGG} in precision while achieving
-similar success rate (AUC) indicating that higher level feature absraction
+similar success rate (AUC) indicating that higher level feature abstraction
 works better for the smaller ROIs.

### 2017-09-06 wacv_for_review.tex
Added more comments.

@@
 last filter, $R_{t}^{L}$, focuses on the target area and its
-background bigger than that of the first filter, $R_{t}^{S}$, \textit{target}+\textit{large background}. 
+background bigger than that of the first filter, $R_{t}^{S}$,
+\textit{target}+\textit{large background}.
+
 We set up {\it E}nKCF in this way because, we believe, a correlation filter for
@@
 correlation filter should focus on the target itself to estimate the
-right scale of the target {\it Burak: We only explained two kinds of
+right scale of the target
+
+{\it Burak: We only explained two kinds of
   filters: translation and scale filter. But we do have two filters
@@
   the sentence about translation filter with details.}
-  {\it YoungWoo : In this paragraph, we mention two of the translation filters and then we say
-  translation filter needs background whereas the scale filter does not.}
+
+{\it YoungWoo : In this paragraph, we mention two of the translation
+  filters and then we say translation filter needs background whereas
+  the scale filter does not.}
+
+{\it Burak: The paragraph I'm referring to begins ``We set up...'' The
+  paragraph before this explain what each of the KCFs is for, but
+  didn't say why at the next paragraph ``We set up...''}
+
 Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.
@@
 
-{\it YoungWoo : I placed EnKCF with traditional and deep features section right after EnKCF section. Later, you
-placed them after the Kernelized Correlation Filter section. To me, it makes more
-sense to place them right after the EnKCF section.}
+{\it YoungWoo : I placed EnKCF with traditional and deep features
+  section right after EnKCF section. Later, you placed them after the
+  Kernelized Correlation Filter section. To me, it makes more sense to
+  place them right after the EnKCF section.}
+
+{\it Burak: I don't think that's a good way of arranging this. You
+  talked about EnKCF, then KCF should come out before any variants of
+  KCF w/ conventional feature and w/ deep features. Otherwise, what is
+  the point of having KCF section after you explained all the usage of
+  KCF? So, it should EnKCF, KCF, KCF w/ hand-craft features and KCF w/
+  deep features. Given this order, two paragraphs before and after
+  this didn't connect!}
 
@@
 the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI. {\it Burak: Why do we need to keep the run-time complexity
-  of $R_{S}$ and $R_{t}^{L}$ the same?} {\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$ to 
-  have similar fps (30fps) to avoid missing frames on an embedded system. We can think of each one as an individual tracker
-  and we do not want one operating at 10fps while others running at 30 fps.} By reducing the template size of $R_{s}$,
+correlation filter on a single ROI.
+
+{\it Burak: Why do we need to keep the run-time complexity
+  of $R_{S}$ and $R_{t}^{L}$ the same?}
+
+{\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$
+  to have similar fps (30fps) to avoid missing frames on an embedded
+  system. We can think of each one as an individual tracker and we do
+  not want one operating at 10fps while others running at 30 fps.}
+
+{\it Burak: What you told me is purely empirical which is fine. But
+  you'll have to tell the readers why we wanted to keep the run-time
+  complexity of those filters same!}
+
+By reducing the template size of $R_{s}$,
    fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.
@@
 
+{\it Burak: We can put these together if their performances from the
+  same data -- don't need to use the same features to be on the same
+  graph! We said EnKCF w/ deep features improved the performance, then
+  what's the point to separate them into two graphs?}
+
 This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
@@
 and second convolutional layer of the VGGNet \cite{simonyan2014very}.
-They report that the first convolutional layer features lead to slightly better precision
-and success rates than the second layer due to lost spatial information this layer. \cite{ma2015hierarchical}
-proposed a KCF tracker integrating features with higher abstraction capacity. 
-Their method first employs the third convolutional layer features to estimate the response map. In
-the next stage, the KCF, concentrating on the second convolutional layer features, is run to update
-transition. The third KCF then works on the transition given by the previous KCF and learns the first convolutional
-layer features to update the transition. This coarse-to-fine approach accommodates
-different levels of abstractions of the object. However, it
-runs multiple KCFs in a sequential fashion, increasing the run-time
+They report that the first convolutional layer features lead to
+slightly better precision and success rates than the second layer due
+to lost spatial information this layer. \cite{ma2015hierarchical}
+proposed a KCF tracker integrating features with higher abstraction
+capacity.  Their method first employs the third convolutional layer
+features to estimate the response map. In the next stage, the KCF,
+concentrating on the second convolutional layer features, is run to
+update transition. The third KCF then works on the transition given by
+the previous KCF and learns the first convolutional layer features to
+update the transition. This coarse-to-fine approach accommodates
+different levels of abstractions of the object. However, it runs
+multiple KCFs in a sequential fashion, increasing the run-time
 complexity. For this reason, we follow a similar approach to
@@
   particle filter}
+
+{\it Burak: Earlier we told the readers why we wanted to have two
+  translation filters: one for smaller region, $R_{t}^{S}$, and
+  another for larger region, $R_{t}^{L}$. The reason why we have two
+  translation filter, instead of one because we wanted to minimize any
+  drifts, yes? Read the line from 354 to 374. Then if we say again
+  here we have a particle filter for smoothing transition among KCFs,
+  they might think those two translation filters do not do their jobs
+  well?}
 
@@
 for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
-(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
-feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
-We further improved the performance by employing deeper features in the scale filter 
-with zero padding around the target.
+(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects
+with deep feature encodings to boost tracking performance by about
+$5\%$ on embedded systems with GPUs.  We further improved the
+performance by employing deeper features in the scale filter with zero
+padding around the target.
 

### 2017-09-06 wacv_for_review.tex
Figure Updated DeeEnKCF

--- 2017-09-06 wacv_for_review.tex
@@
   \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
+  \textit{target+large background}, and their hanning window and
   expected Gaussian response.}
@@
 \includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
+\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied hanning window
 to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
@@
 systems offer GPU, we would like to see how much accuracy we can
-achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) as shown in Figure \ref{fig:Filters_CNN}.
+achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) learned by the VGGNet
+as shown in Figure \ref{fig:Filters_CNN}.
 \begin{comment}
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
+\caption{Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
 dataset.}

### 2017-09-07 wacv_for_review.tex
Comments replied

--- 2017-09-06 wacv_for_review.tex
@@
 correlation filter should focus on the target itself to estimate the
-right scale of the target
+right scale of the target. By setting a transition filter with larger padding size, 
+$R_{t}^{L}$, we can recover from potential drifts after the frames we only run the
+scale filter. Additionally, we design a translation filter with smaller 
+padding size, $R_{t}^{S}$, to better pinpoint target position after the 
+frames we only run $R_{t}^{L}$.
 
@@
   didn't say why at the next paragraph ``We set up...''}
-
-Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.
 
@@
 this observation.
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
-   \\[-3ex]
-\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
-\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
-\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
-\caption{Examples of three filters with hand-crafted features; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their Hanning window and
-  expected Gaussian response.}
-\label{fig:Filters}
-\end{figure}
 
@@
 noisy shape features due to its large search area. In what follows, we
-will detail the {\it E}nKC with hand-crafted features, dedicated to run
-on low-end embedded systems, and deep features, designed to run on
-the systems with GPUs. Later, we will briefly document the fundamental 
-concepts of the KCF and Particle Filter, designed to smooth transitions 
-between KCFs.
-
+will detail the main idea behind the KCF.
+
+\begin{comment}
 {\it Burak: This section does NOT connect to the previous section.}
@@
   this didn't connect!}
-
-\textbf{{\it E}nKCF with Hand-Crafted Features} 
-We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
-and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
-This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
-$30$ fps, particularly on the ones without GPU units.
-
-The translation filter, $R_{t}^{L}$, uses both the fHoG
-\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
-features to learn the large background area around the target. Figure
-\ref{fig:Filters}(b) shows an example of this translation filter. The
-color features are also used to make the feature vector more
-discriminative. In other words, for the case that the fHoG is the only
-feature, the bigger the area for HoG is the more noise the resulting
-fHoG feature contains. Adding color information to the feature vector
-will make the feature vector more robust to the noises from the
-background around the target. However, this is not the case for the
-translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
-does not contain much of the background area around the target. Figure
-\ref{fig:Filters}(a) shows an example of this translation filter. 
-Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
-The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
-This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
-The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
-alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
-To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
-This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
-and (2) integration of color features. This way, we keep the run-time complexity of
-the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI.
-
-{\it Burak: Why do we need to keep the run-time complexity
-  of $R_{S}$ and $R_{t}^{L}$ the same?}
-
-{\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$
-  to have similar fps (30fps) to avoid missing frames on an embedded
-  system. We can think of each one as an individual tracker and we do
-  not want one operating at 10fps while others running at 30 fps.}
-
-{\it Burak: What you told me is purely empirical which is fine. But
-  you'll have to tell the readers why we wanted to keep the run-time
-  complexity of those filters same!}
-
-By reducing the template size of $R_{s}$,
-   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.
-
-\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
-addition to hand-crafted features, we explore deep features to boost
-tracking performance.
-
-{\it Burak: Did EnKCF w/ deep features really
-  improve the performance -- the performance tested on the same data?
-  or did you just compare the performance numbers?}
-
-{\it YoungWoo :
-  EnkCF with deep features improved the performance on the same set of
-  data.}
-
-{\it Burak: If EnKCF w/ deep features improved the performance of
-  EnKCF on the same set of data, why didn't you plot their curves
-  together? And if this is true, we'll have to revise the abstract and
-  introduction as well!}
-
-  {\it YoungWoo : I compare the EnKCF with all the other trackers that does not use deep features. For this reason
-  it does not make sense to put DeepEnKCF in the same figure (Figure 6). We have a separate section 
-  showing how much improvement we get by using deep features and in this section I plot them in the same figure ( Figure (8) ).}
-
-{\it Burak: We can put these together if their performances from the
-  same data -- don't need to use the same features to be on the same
-  graph! We said EnKCF w/ deep features improved the performance, then
-  what's the point to separate them into two graphs?}
-
-This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
-devised to make {\it E}nKCF run on high-end embedded systems with GPUs
-installed.
-
-There has been a large volume of studies on utilizing a pre-trained
-CNN features to tracking-by-detection algorithms. For example,
-\cite{danelljan2015convolutional} used the activations of the first
-and second convolutional layer of the VGGNet \cite{simonyan2014very}.
-They report that the first convolutional layer features lead to
-slightly better precision and success rates than the second layer due
-to lost spatial information this layer. \cite{ma2015hierarchical}
-proposed a KCF tracker integrating features with higher abstraction
-capacity.  Their method first employs the third convolutional layer
-features to estimate the response map. In the next stage, the KCF,
-concentrating on the second convolutional layer features, is run to
-update transition. The third KCF then works on the transition given by
-the previous KCF and learns the first convolutional layer features to
-update the transition. This coarse-to-fine approach accommodates
-different levels of abstractions of the object. However, it runs
-multiple KCFs in a sequential fashion, increasing the run-time
-complexity. For this reason, we follow a similar approach to
-\cite{danelljan2015convolutional} to embed deep features in {\it
-  E}nKCF.
-
-Our {\it E}nKCF framework allows us to exploit different level of
-feature encodings with different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
-the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it learns less spatial information than
-$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
-fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
-whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
-the second layer features ($109\times109\times64$). This feature
-assignment scheme is represented as \textit{conv224-VGG} and shown in
-fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
-convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
-$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
-resolution at the first several layers than AlexNet
-\cite{krizhevsky2012imagenet}.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied Hanning Window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
-\label{fig:Filters_CNN}
-\end{figure}
+\end{comment}
 
@@
 
+\textbf{{\it E}nKCF with Hand-Crafted Features} 
+We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
+and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
+This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
+$30$ fps, particularly on the ones without GPU units.
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
+   \\[-3ex]
+\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
+\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
+\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
+\caption{Examples of three filters with hand-crafted features; the translation filter,
+  \textit{target+small background}, the scale filter,
+  \textit{target-only} and another translation filter,
+  \textit{target+large background}, and their hanning window and
+  expected Gaussian response.}
+\label{fig:Filters}
+\end{figure}
+
+The translation filter, $R_{t}^{L}$, uses both the fHoG
+\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
+features to learn the large background area around the target. Figure
+\ref{fig:Filters}(b) shows an example of this translation filter. The
+color features are also used to make the feature vector more
+discriminative. In other words, for the case that the fHoG is the only
+feature, the bigger the area for HoG is the more noise the resulting
+fHoG feature contains. Adding color information to the feature vector
+will make the feature vector more robust to the noises from the
+background around the target. However, this is not the case for the
+translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
+does not contain much of the background area around the target. Figure
+\ref{fig:Filters}(a) shows an example of this translation filter. 
+Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
+The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
+This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
+The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
+alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
+To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
+This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
+and (2) integration of color features. This way, we keep the run-time complexity of
+the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
+correlation filter on a single ROI. By reducing the template size of $R_{s}$, fluctuating run-time
+performances among $R_{s}$ and, $R_{t}^{L}$ and $R_{t}^{S}$, are avoided which 
+is desired in embedded systems.
+
+{\it Burak: Why do we need to keep the run-time complexity
+  of $R_{S}$ and $R_{t}^{L}$ the same?}
+
+{\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$
+  to have similar fps (30fps) to avoid missing frames on an embedded
+  system. We can think of each one as an individual tracker and we do
+  not want one operating at 10fps while others running at 30 fps.}
+
+{\it Burak: What you told me is purely empirical which is fine. But
+  you'll have to tell the readers why we wanted to keep the run-time
+  complexity of those filters same!}
+
+\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
+addition to hand-crafted features, we explore deep features to boost
+tracking performance.
+
+{\it Burak: Did EnKCF w/ deep features really
+  improve the performance -- the performance tested on the same data?
+  or did you just compare the performance numbers?}
+
+{\it YoungWoo :
+  EnkCF with deep features improved the performance on the same set of
+  data.}
+
+{\it Burak: If EnKCF w/ deep features improved the performance of
+  EnKCF on the same set of data, why didn't you plot their curves
+  together? And if this is true, we'll have to revise the abstract and
+  introduction as well!}
+
+  {\it YoungWoo : I compare the EnKCF with all the other trackers that does not use deep features. For this reason
+  it does not make sense to put DeepEnKCF in the same figure (Figure 6). We have a separate section 
+  showing how much improvement we get by using deep features and in this section I plot them in the same figure ( Figure (8) ).}
+
+{\it Burak: We can put these together if their performances from the
+  same data -- don't need to use the same features to be on the same
+  graph! We said EnKCF w/ deep features improved the performance, then
+  what's the point to separate them into two graphs?}
+
+{\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
+implementations, I thought it would be more clear to seperate them, (2) I do not have 
+results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
+of this paper, showing them in the same figure with all the trackers might lead the authors to 
+underestimate EnKCF.
+ }
+
+This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
+devised to make {\it E}nKCF run on high-end embedded systems with GPUs
+installed.
+
+There has been a large volume of studies on utilizing a pre-trained
+CNN features to tracking-by-detection algorithms. For example,
+\cite{danelljan2015convolutional} used the activations of the first
+and second convolutional layer of the VGGNet \cite{simonyan2014very}.
+They report that the first convolutional layer features lead to
+slightly better precision and success rates than the second layer due
+to lost spatial information this layer. \cite{ma2015hierarchical}
+proposed a KCF tracker integrating features with higher abstraction
+capacity.  Their method first employs the third convolutional layer
+features to estimate the response map. In the next stage, the KCF,
+concentrating on the second convolutional layer features, is run to
+update transition. The third KCF then works on the transition given by
+the previous KCF and learns the first convolutional layer features to
+update the transition. This coarse-to-fine approach accommodates
+different levels of abstractions of the object. However, it runs
+multiple KCFs in a sequential fashion, increasing the run-time
+complexity. For this reason, we follow a similar approach to
+\cite{danelljan2015convolutional} to embed deep features in {\it
+  E}nKCF.
+
+Our {\it E}nKCF framework allows us to exploit different level of
+feature encodings with different KCFs. The translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
+the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
+encodings to $R_{s}$ as it learns less spatial information than
+$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
+fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
+whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
+the second layer features ($109\times109\times64$). This feature
+assignment scheme is represented as \textit{conv224-VGG} and shown in
+fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
+convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
+$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
+\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
+resolution at the first several layers than AlexNet
+\cite{krizhevsky2012imagenet}.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
+\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied hanning window
+to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
+\label{fig:Filters_CNN}
+\end{figure}
+
 \textbf{Particle Filter for Smoothing Transition among KCFs} 
@@
   well?}
+
+{\it YoungWoo : Particle filter smoothes the translations in between the
+transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
+we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
+on the other hand aims at reducing the drifts and jumps further by bringing in the 
+motion information.}
 

### 2017-09-07 wacv_for_review.tex
Figure Updated

@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
-
 \usepackage{wacv}
@@
 the appearance model of a target on the fly and 2) run as fast on a
-typical desktop as up to $300-450$ fps, aiming at running, at least,
+typical desktop as up to $300$-$450$ fps, aiming at running, at least,
 faster than 30 fps when it is deployed on a low-end, embedded
@@
 \textit{target+large background} translation filter, $R_{t}^{L}$, is
-applied to the $i$th and $i+1$th image frames, another translation
-filter, $R_{t}^{S}$ is applied to the $i+2$th and $i+3$th image
-frames, and then the scale filter, $R_{s}$ is applied to the $i+4$the
+applied to the $i$th and $i$+$1$th image frames, another translation
+filter, $R_{t}^{S}$ is applied to the $i$+$2$th and $i$+$3$th image
+frames, and then the scale filter, $R_{s}$ is applied to the $i$+$4$the
 image. This order repeats until the end of the image frames. The
 translation filter, $R_{t}^{L}$, is intended to run right after the
-scale filter, $R_s$, runs which is applied at every other $i+4$
+scale filter, $R_s$, runs which is applied at every other $i$+$4$
 frames. We run these filters in this way because we want to minimize
@@
 where $r$ denotes the correlation response at all cyclic shifts of the
-first row of the kernel matrix.
+first row of the kernel matrix. In what follows, we will detail two feature types to be deployed
+in KCFs in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and (2) deep convolutional features.
 
@@
 Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
-The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
+The ROI considered by $R_{s}$ is resized to a smaller template resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c). 
 This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
@@
 {\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
-implementations, I thought it would be more clear to seperate them, (2) I do not have 
+implementations, I thought it would be more clear to separate them, (2) I do not have 
 results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
@@
 assignment scheme is represented as \textit{conv224-VGG} and shown in
-fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
+Figure~\ref{fig:Filters_CNN}. Additionally, we assign the second
 convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
@@
 \includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied hanning window
-to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered as it would result in target boundary information loss.}
+\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied an 
+hanning window to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered to avoid target boundary information loss.}
 \label{fig:Filters_CNN}
@@
 
-{\it YoungWoo : Particle filter smoothes the translations in between the
+{\it YoungWoo : Particle filter smoothen the translations in between the
 transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
@@
 \textbf{Evaluation with Deep Features} Our focus so far was to build a
-high speed tracker that can run at 30fps on a single-board, embedded
+high speed tracker that can run at $30$fps on a single-board, embedded
 system. Given this goal, we used fHoG and color-naming features in an

### 2017-09-08 wacv_for_review.tex
Figure Updated
Reviewed the entire draft.

@@
 background bigger than that of the first filter, $R_{t}^{S}$,
-\textit{target}+\textit{large background}.
-
-We set up {\it E}nKCF in this way because, we believe, a correlation filter for
-learning a target's translation should include its background to
-better discriminate the target from its surrounding, and another
-correlation filter should focus on the target itself to estimate the
-right scale of the target. By setting a transition filter with larger padding size, 
-$R_{t}^{L}$, we can recover from potential drifts after the frames we only run the
-scale filter. Additionally, we design a translation filter with smaller 
-padding size, $R_{t}^{S}$, to better pinpoint target position after the 
-frames we only run $R_{t}^{L}$.
-
-{\it Burak: We only explained two kinds of
-  filters: translation and scale filter. But we do have two filters
-  for target's translation, $R_{t}^{S}$ and $R_{t}^{L}$. Revise the
-  the sentence about translation filter with details.}
-
-{\it YoungWoo : In this paragraph, we mention two of the translation
-  filters and then we say translation filter needs background whereas
-  the scale filter does not.}
-
-{\it Burak: The paragraph I'm referring to begins ``We set up...'' The
-  paragraph before this explain what each of the KCFs is for, but
-  didn't say why at the next paragraph ``We set up...''}
+\textit{target}+\textit{large background}. We set up {\it E}nKCF in
+this way because, we believe, a correlation filter for learning a
+target's translation should include the background of the target to
+better discriminate it from its surrounding, and another correlation
+filter should focus on the target itself to estimate the right scale
+of the target. By setting a transition filter with larger padding
+size, $R_{t}^{L}$, we can recover from potential drifts after the
+frames we only run the scale filter. Additionally, we design a
+translation filter with smaller padding size, $R_{t}^{S}$, to better
+localize the position of the target after the frames we only run
+$R_{t}^{L}$.
 
@@
 the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
-with more focused ROIs about the target's translation. A translation
-filter, $R_{t}^{L}$, is intended to look at a larger search area to
-estimate the target's translation and recover from any potential
-drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
+with more focused ROIs about the target's translation. On the other
+hands, a translation filter, $R_{t}^{L}$, is designed to look at a
+larger search area to estimate the target's translation and recover
+from any potential drifts. Another translation filter, $R_{t}^{S}$, is
 designed to addresses the drawback of $R_{t}^{L}$ that it may learn
@@
 will detail the main idea behind the KCF.
-
-\begin{comment}
-{\it Burak: This section does NOT connect to the previous section.}
-
-{\it YoungWoo : I placed EnKCF with traditional and deep features
-  section right after EnKCF section. Later, you placed them after the
-  Kernelized Correlation Filter section. To me, it makes more sense to
-  place them right after the EnKCF section.}
-
-{\it Burak: I don't think that's a good way of arranging this. You
-  talked about EnKCF, then KCF should come out before any variants of
-  KCF w/ conventional feature and w/ deep features. Otherwise, what is
-  the point of having KCF section after you explained all the usage of
-  KCF? So, it should EnKCF, KCF, KCF w/ hand-craft features and KCF w/
-  deep features. Given this order, two paragraphs before and after
-  this didn't connect!}
-\end{comment}
 
@@
 where $r$ denotes the correlation response at all cyclic shifts of the
-first row of the kernel matrix. In what follows, we will detail two feature types to be deployed
-in KCFs in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and (2) deep convolutional features.
-
-\textbf{{\it E}nKCF with Hand-Crafted Features} 
-We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
-and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
-This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
-$30$ fps, particularly on the ones without GPU units.
+first row of the kernel matrix.
+
+In what follows, we will detail two different types of features used
+in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and
+(2) deep convolutional features.
+
+\textbf{{\it E}nKCF with Hand-Crafted Features} We, first, use two
+conventional hand-crafted features, fHoG (shape)
+\cite{felzenszwalb2010object} and color-naming (color)
+\cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
+features. This setup of the {\it E}nKCF is designed to perform
+tracking on any embedded systems at $30$ fps, ones without GPUs.
 \begin{figure}[!h]
@@
 
-The translation filter, $R_{t}^{L}$, uses both the fHoG
-\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
-features to learn the large background area around the target. Figure
-\ref{fig:Filters}(b) shows an example of this translation filter. The
-color features are also used to make the feature vector more
-discriminative. In other words, for the case that the fHoG is the only
-feature, the bigger the area for HoG is the more noise the resulting
-fHoG feature contains. Adding color information to the feature vector
-will make the feature vector more robust to the noises from the
-background around the target. However, this is not the case for the
-translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
-does not contain much of the background area around the target. Figure
-\ref{fig:Filters}(a) shows an example of this translation filter. 
-Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
-The ROI considered by $R_{s}$ is resized to a smaller template resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c). 
-This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
-The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
-alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
-To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
-This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
-and (2) integration of color features. This way, we keep the run-time complexity of
-the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI. By reducing the template size of $R_{s}$, fluctuating run-time
-performances among $R_{s}$ and, $R_{t}^{L}$ and $R_{t}^{S}$, are avoided which 
-is desired in embedded systems.
+We use both fHoG \cite{felzenszwalb2010object} and color-naming
+\cite{van2009learning} for the large area, translation filter,
+$R_{t}^{L}$. This is because the fHoG applied to relatively larger
+area is tended to be noisy and less discriminative and adding color
+information makes the feature vector for the translation filter,
+$R_{t}^{L}$, more robust to noise and more discriminative. Figure
+\ref{fig:Filters}(b) shows an example of this translation filter. But,
+this is not the case for the small area, translation filter,
+$R_{t}^{S}$, because this translation filter does not contain much of
+the background area around the target. Figure \ref{fig:Filters}(a)
+shows an example of this translation filter. Lastly, we use both fHoG
+and color-naming features again for the scale filter,
+$R_{s}$. Although we are using the same feature representations for
+the scale filter learning relatively smaller area just around the
+target, the reason of using two feature sets is sightly different in
+that the area to learn is too small for the fHoG to represent the area
+well. In addition, the scale filter, explained earlier in the
+algorithm \ref{alg:MKCF}, estimates the scale of a target by
+correlating it with three candidate ROIs. This search may increase the
+run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
+$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
+practical, we use a smaller template size (i.e., 64$\times n$) for the
+scale filter, $R_{s}$. The smaller template size does not degrade the
+tracking performance neither because of 1) zero padding around the
+target and 2) use of color feature.
+\begin{comment}
+The ROI considered by $R_{s}$ is resized to a smaller template
+resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
+This leads to less discriminative shape features. To reduce the noise
+in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
+scale by correlating the filter with three candidate ROIs as detailed
+in alg.~\ref{alg:MKCF}.  This increases the complexity from
+$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
+reduce the number of operations, we assign a smaller template size to
+$R_{s}$.  This does not degrade the tracking performance due to two
+reasons: (1) zero padding around the target and (2) integration of
+color features. This way, we keep the run-time complexity of the
+$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
+correlation filter on a single ROI. By reducing the template size of
+$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
+$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
+systems.
 
@@
   complexity of those filters same!}
-
+\end{comment}
 \textbf{{\it E}nKCF with Convolutional Neural Network Features} In
 addition to hand-crafted features, we explore deep features to boost
-tracking performance.
-
+tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF is
+designed to make {\it E}nKCF run on high-end embedded systems with GPUs
+installed.
+\begin{comment}
 {\it Burak: Did EnKCF w/ deep features really
@@
  }
-
-This version of {\it E}nKCF, Deep{\it E}nKCF, on the other hand, is
-devised to make {\it E}nKCF run on high-end embedded systems with GPUs
-installed.
+\end{comment}
 
@@
 \cite{danelljan2015convolutional} to embed deep features in {\it
-  E}nKCF.
-
-Our {\it E}nKCF framework allows us to exploit different level of
-feature encodings with different KCFs. The translation filters,
-$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
-the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
-encodings to $R_{s}$ as it learns less spatial information than
-$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
-fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
-whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
-the second layer features ($109\times109\times64$). This feature
-assignment scheme is represented as \textit{conv224-VGG} and shown in
-Figure~\ref{fig:Filters_CNN}. Additionally, we assign the second
+  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
+level of feature encodings with different KCFs. The translation
+filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
+area than the scale filter, $R_{s}$. Given this, we can assign deeper
+feature encodings to $R_{s}$ as it learns less spatial information
+than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
+the fourth convolutional layer features ($26\times26\times128$) to
+$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
+activations of the second layer features
+($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
+this feature assignment. Additionally, we assign the second
 convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
 $R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
+\textit{conv224-VGG}. {\it Burak: I don't see any differenciation
+  between conv222-VGG and conv224-VGG from the figure, at least labels
+  of them.} We use the VGGNet since it provides higher spatial
 resolution at the first several layers than AlexNet
@@
 \includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction framework in Deep{\it E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ are applied an 
-hanning window to avoid distortion due to FFT operation whereas $R_{s}$ is not filtered to avoid target boundary information loss.}
+\caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF.
+$R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ is not filtered {\it Burak: What do you mean by ``not filtered''?} to avoid target boundary information loss.}
 \label{fig:Filters_CNN}
@@
 \textbf{Particle Filter for Smoothing Transition among KCFs}
+\begin{comment}
 {\it Burak: Does what this section explains still hold good? If what
@@
 motion information.}
-
-As explained earlier, the {\it E}nKCF updates a target's translation at
-every other $k$ frames, particularly for estimating the target's
+\end{comment}  
+As explained earlier, the {\it E}nKCF updates a target's translation
+at every other $k$ frames, particularly for estimating the target's
 scale. Although the strategy of updating every other $k$th frames will
-result in an optimal run-time performance, this may lead any potential
-drifts at the later frames. To prevent such potential drifts, we
-developed a Bayes filter that incorporates a target's motion to smooth
-any intermediate outputs from individual KCFs of the {\it E}nKCF. In
-particular, we use a particle filter to estimate the target's image
-coordinate based on the {\it E}nKCF's outputs. A particle filter is a
-sequential Monte Carlo method that uses a finite number of particles
-or samples to estimate the posterior probability density of a state of
-the system \cite{thrun2005probabilistic}. In this study, the state
-represents a target's pixel coordinates and its motion. In particular,
-the state of the particle filter, $X_t$, is represented by $\lbrace x,
-y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates
-of the target's centroid, $v_x$ and $v_y$ are the estimated velocity
-along the $x$-axis and $y$-axis. The particle filter predicts, using a
-constant velocity motion model, a target's state by generating a
-predefined number of particles. Then it uses the confidence maps of 
-{\it E}nKCF as observation to update the state. The weight of a particle is computed as
+result in an optimal run-time performance, this may lead drifts at the
+later frames. To prevent such potential drifts, we developed a Bayes
+filter that incorporates a target's motion to smooth any intermediate
+outputs from individual KCFs. In particular, we use a particle filter
+to estimate the target's image coordinate based on the {\it E}nKCF's
+outputs. The state in this paper, $X_t$, represents a target's pixel
+coordinates and its velocity, $X_t = \lbrace x, y, v_{x}, v_{y}
+\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
+centroid, $v_x$ and $v_y$ are the velocity estimated along the
+$x$-axis and $y$-axis. The particle filter predicts, using a constant
+velocity motion model, a target's next state by generating a predefined
+number of particles. Then it uses the confidence maps of {\it E}nKCF
+as observation to update the state. The weight of a particle is
+computed as
 \begin{equation}
@@
 %---------------------------------------------------------------------- 
-In this section, we evaluate the performance of the proposed {\it E}nKCF
-tracker and its variants on the object tracking benchmarks. 
-In this direction, we choose two publicly, available datasets:
+We evaluate the performance of the proposed {\it E}nKCF tracker and
+its variants using the object tracking benchmark
+datasets. Particularly, we choose two publicly, available datasets:
 OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
-and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
+and
+UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
 The OTB100 dataset is comprised of the videos about 100 objects
-whereas UAV123 dataset contains aerial footages of 123 objects.
-We first evaluate the performance of {\it E}nKCF 
-with hand-crafted features as shown in Figure \ref{fig:Filters}.  
-With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
-on an embedded system, a drone, for example, in ``high speed,'' $\ge
-300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
+whereas UAV123 dataset contains aerial footages of 123 objects.  We
+first evaluate the performance of {\it E}nKCF with two hand-crafted
+features, fHoG and color-naming.  With this tracker, we aim at
+developing an object tracking algorithm that ``efficiently'' runs on
+an embedded system, a drone, for example, in ``high speed,'' $\ge 30$
+fps. Given this, we believe that the UAV123 dataset is a good fit in
 evaluating the performance of the proposed algorithm. In addition, in
-the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
-abrupt scale/illumination changes. Although we are primarily
+the UAV123 dataset, there are many challenging, realistic scenes,
+e.g., abrupt scale/illumination changes. Although we are primarily
 interested in developing an algorithm for mobile, embedded robotic
@@
 modified dataset is how robust the proposed algorithm is to the
-drastic motions of camera and targets. Finally, we evaluate the Deep{\it E}nKCF, 
-{\it E}nKCF with deep features, on the UAV123 dataset to observe how much gain
-we can achieve over hand-crafted features.
+drastic motions of camera and targets. Finally, we evaluate the
+Deep{\it E}nKCF, {\it E}nKCF with deep features, on the UAV123 dataset
+to observe how much gain we can achieve over hand-crafted features.
 
@@
 high speed tracker that can run at $30$fps on a single-board, embedded
-system. Given this goal, we used fHoG and color-naming features in an
-efficient way in the proposed {\it E}nKCF. Deep features, on the
-other hand, recently have been used to boost tracking accuracy of the
-KCFs based trackers \cite{ma2015hierarchical,
-  danelljan2015convolutional}. Following the recent trend, we hypothesize 
-that the {\it E}nKCF tracker could be improved with deep features trained on ImageNet
-dataset. Utilizing pre-trained deep features would not be applicable to
-all the a single-board, embedded system due to their limited
-computational resources. However, as these days some of the single-board
-systems offer GPU, we would like to see how much accuracy we can
-achieve by feeding {\it E}nKCF w/ deep features (Deep{\it E}nKCF) learned by the VGGNet
-as shown in Figure \ref{fig:Filters_CNN}.
+system. To this end, we used two conventional features, fHoG and
+color-naming for the {\it E}nKCF. At the same time, we observed that
+the feature vectors learned from DNN have been used to improve the
+performance of the trackers based on KCF \cite{ma2015hierarchical,
+  danelljan2015convolutional}, and some of the single-board, embedded
+systems have GPUs. We believe that the performance of the {\it E}nKCF
+could be also improved with deep features trained on ImageNet dataset
+and like to see how much performance boost we could gain. 
 \begin{comment}
@@
 Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
-results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
-features outperformed the HoG and color features as proposed in {\it
-  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
-success rates (AUC). The \textit{conv224-VGG} setting performed
-slightly better than \textit{conv222-VGG} in precision while achieving
-similar success rate (AUC) indicating that higher level feature abstraction
+results that we ran Deep{\it E }nKCF on UAV123 Dataset. Two Deep {\it
+  E}nKCF settings outperformed those with the HoG and color features
+by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success
+rates (AUC). The \textit{conv224-VGG} setting performed slightly
+better than \textit{conv222-VGG} in precision while achieving similar
+success rate (AUC) indicating that higher level feature abstraction
 works better for the smaller ROIs.
+{\it Burak: You'll have to explain 1) why, you think, DeepEnKCF worked better, 2) why DeepEnKCF didn't perform a way better than EnKCF, 3) why did conv224-VGG perform better than conv222-VGG.}
 \begin{figure}[!h]
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
+\caption{{\it Burak: Make this figure bigger if the space permitted.} Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
 dataset.}
@@
 with deep feature encodings to boost tracking performance by about
-$5\%$ on embedded systems with GPUs.  We further improved the
-performance by employing deeper features in the scale filter with zero
-padding around the target.
+$5\%$ on embedded systems with GPUs.
 

### 2017-09-08 wacv_for_review.tex
Final Edits - 8 Pages Paper

@@
 \title{{\it E}nKCF: Ensemble of Kernelized Correlation Filters for
-  High-Speed, Object Tracking}
+  High-Speed Object Tracking}
 
@@
 these approaches will drastically reduce run-time performance because
-they are proposed to run multiple of a correlation filter including
-KCF on each frame.
+they are proposed to run multiple KCF on each frame.
 
@@
 the scale filter learning relatively smaller area just around the
-target, the reason of using two feature sets is sightly different in
+target, the reason of using two feature sets is slightly different in
 that the area to learn is too small for the fHoG to represent the area
@@
 \end{comment}
+
 \textbf{{\it E}nKCF with Convolutional Neural Network Features} In
@@
 $R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. {\it Burak: I don't see any differenciation
-  between conv222-VGG and conv224-VGG from the figure, at least labels
-  of them.} We use the VGGNet since it provides higher spatial
-resolution at the first several layers than AlexNet
+\textit{conv224-VGG}. The conv222 setting stands for the assignment of 
+the activations of $2^{th}$, $2^{th}$ and $4^{th}$ convolutional layer features
+of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
+since it provides higher spatial resolution at the first several layers than AlexNet
 \cite{krizhevsky2012imagenet}.
@@
 \caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF.
-$R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ is not filtered {\it Burak: What do you mean by ``not filtered''?} to avoid target boundary information loss.}
+$R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ does not, to avoid target boundary information loss.}
 \label{fig:Filters_CNN}
@@
 as observation to update the state. The weight of a particle is
-computed as
-\begin{equation}
-w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j), 
-\end{equation}
+computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$,
 where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
-size of the window as that of a confidence map. Alternatively one can
-also use the Euclidean distance of particles to the location of
-maximum response of the confidence map.
+size of the window as that of a confidence map. 
+%Alternatively one can
+%also use the Euclidean distance of particles to the location of
+%maximum response of the confidence map.
 \begin{comment}
@@
 proposed algorithm with those of the state-of-the-art in a nominal
-dataset for comparison. To this end, we chose the OTB100 dataset that
+dataset. To this end, we chose the OTB100 dataset that
 contains the videos recorded from smart phones and typical cameras in
@@
 reasonable, we performed the re-sampling only when the
-\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
-(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
+\textit{efficient number of samples}, ($ \hat{N}_{eff} \approx
+(\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a pre-defined
 threshold.
@@
   UAV123 dataset. This table empirically supported the usefulness of
-  combining multiple KCFs as long as the deployment order is optimal.}
+  combining multiple KCFs as long as the deployment order is optimal. The '$*$' represents
+  sequential approach where multiple KCFs are run in the given order in every frame as in LCT \cite{ma2015long}.}
 \label{table:Comparison_to_LCT}
@@
 which is very similar to the way the LCT tracker \cite{ma2015long}
-runs. To be precise, the LCT tracker comes with a re-detection method
+runs. To be precise, the LCT tracker comes with a re-detection module
 for a long-term tracking. In short, we empirically verified that
@@
 method can effectively handle tracking of object in fast motion and in
-large camera motion. Specifically we modified {\it E}nKCF by running
+large camera motion. Specifically, we modified {\it E}nKCF by running
 $R_{t}^{L}$ every frame and remove the particle filter instead. We
@@
 the other hand, it does decent job in scale estimation. It ranks as
-second in AUC while running about $150$ faster than the MUSTER
-tracker.
+second in AUC while running about $150$ faster than MUSTER.
 
@@
 systems have GPUs. We believe that the performance of the {\it E}nKCF
-could be also improved with deep features trained on ImageNet dataset
-and like to see how much performance boost we could gain. 
+could be also improved with deep convolutional features trained on ImageNet dataset.
 \begin{comment}
@@
 
-Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
-results that we ran Deep{\it E }nKCF on UAV123 Dataset. Two Deep {\it
-  E}nKCF settings outperformed those with the HoG and color features
+Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows
+Deep{\it E }nKCF's performance on UAV123 Dataset. Deep{\it
+  E}nKCF outperformed the {\it E}nKCF with hand-crafted features
 by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success
@@
 success rate (AUC) indicating that higher level feature abstraction
-works better for the smaller ROIs.
-{\it Burak: You'll have to explain 1) why, you think, DeepEnKCF worked better, 2) why DeepEnKCF didn't perform a way better than EnKCF, 3) why did conv224-VGG perform better than conv222-VGG.}
+works better for the smaller ROIs. By using feature abstractions
+from the VGGNet pre-trained on millions of images, we can better represent
+the low level features of the object than hand-crafted features
+in challenging cases such as low contrast ROIs. However, the contribution 
+of the deep features is constrained by two factors : (1) low spatial resolution in deeper layers and (2) 
+lost targets due to large target and camera motion in the UAV123 dataset.
+
+\begin{comment}
+{\it Burak: You'll have to explain 1) why, you think, DeepEnKCF worked better, 2) 
+why DeepEnKCF didn't perform a way better than EnKCF, 3) why did conv224-VGG perform better than conv222-VGG.}
+\end{comment}
 \begin{figure}[!h]
@@
 \end{tabular}
-\caption{{\it Burak: Make this figure bigger if the space permitted.} Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
+\caption{Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
 dataset.}
@@
 Bayes filter, particle filter, to smooth the transition between three
-KCFs. In particular, the particle filter estimated the target's pixel
-coordinates using information about the target's motion observed over
-frames. We used two publicly available dataset to evaluate the
+KCFs. Two public datasets were used to evaluate the
 performance of the proposed algorithm and found, on average, the
@@
 for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
-(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects
-with deep feature encodings to boost tracking performance by about
-$5\%$ on embedded systems with GPUs.
-
-As future work, we investigate a way of re-initializing a target when
+(292 fps), DCF (457 fps) for UAV123. Finally, we encoded objects
+with deep features to boost tracking performance by $5\%$ on embedded 
+systems with GPUs. As future work, we investigate a way of re-initializing a target when
 the target is lost, due to occlusion, illumination change, drastic

### 2017-09-08 wacv_for_review.tex
Hyperrefs added, spellcheck done

@@
 \newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}
+\usepackage[hidelinks]{hyperref}
 
@@
 The KCF solves essentially the problem of a regression in the form of
-the regularization:
+the regularization (ridge regression):
 \begin{equation}
@@
 solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
-closed-form solution less complex, an element-wise, multiplication in
+closed-form solution less complex, an element-wise multiplication in
 frequency domain was proposed for $\hat{w}$:
@@
 scale by correlating the filter with three candidate ROIs as detailed
-in alg.~\ref{alg:MKCF}.  This increases the complexity from
+in algorithm~\ref{alg:MKCF}.  This increases the complexity from
 $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
@@
 color-naming for the {\it E}nKCF. At the same time, we observed that
-the feature vectors learned from DNN have been used to improve the
+the feature vectors learned from CNN have been used to improve the
 performance of the trackers based on KCF \cite{ma2015hierarchical,

### 2017-09-08 wacv_for_review.tex
Hyperrefs added, spellcheck done

@@
 $R_{t}^{L}$. This is because the fHoG applied to relatively larger
-area is tended to be noisy and less discriminative and adding color
+area tends to be noisy and less discriminative and adding color
 information makes the feature vector for the translation filter,

### 2017-09-08 wacv_for_review.tex
Burak Final Edit Before Submission

@@
 with more focused ROIs about the target's translation. On the other
-hands, a translation filter, $R_{t}^{L}$, is designed to look at a
+hand, a translation filter, $R_{t}^{L}$, is designed to look at a
 larger search area to estimate the target's translation and recover
@@
 \textit{conv224-VGG}. The conv222 setting stands for the assignment of 
-the activations of $2^{th}$, $2^{th}$ and $4^{th}$ convolutional layer features
+the activations of $2^{th}$ convolutional layer features
 of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
@@
 \textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
-  E}nKCF is designed to address specific challenges in single, target
+  E}nKCF is designed to address specific challenges in single target
 tracking problem. Thus each of them should have different values for
@@
 estimate the scale and translation. Because of this, we set the
-learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
+learning rates of individual filters, $R_{t}^{L}$,
 $R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
@@
 tracking accuracy and run-time performance. For example, we could
-achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
-at every frame, but this combination wills sacrifice run-time
-performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
+achieve 4.26\% higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
+at every frame, but this combination decreases run-time
+performance to 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
 and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
@@
 
-\textbf{Evaluation on Particle Filter Contribution} For the $UAV123$
+\textbf{Evaluation on Particle Filter Contribution} For the UAV123
 dataset, we also evaluated the performance of the {\it E}nKCF with and
@@
 
-\begin{figure}[!h]
-\centering
-\begin{tabular}{cc}
-\tiny\quad\textbf{UAV123$\_$10fps}\\
-\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
-\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
-\end{tabular}
-\caption{Comparison of a modified {\it E}nKCF's performance with those
-  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
-  dataset where the original UAV123 data was temporally downsampled.}
-\label{fig:UAV123_10fpsDATASET}
-\end{figure}
-
 \textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
@@
 second in AUC while running about $150$ faster than MUSTER.
+
+\begin{figure}[!h]
+\centering
+\begin{tabular}{cc}
+\tiny\quad\textbf{UAV123$\_$10fps}\\
+\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
+\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
+\end{tabular}
+\caption{Comparison of a modified {\it E}nKCF's performance with those
+  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
+  dataset where the original UAV123 data was temporally downsampled.}
+\label{fig:UAV123_10fpsDATASET}
+\end{figure}
 
@@
 Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows
-Deep{\it E }nKCF's performance on UAV123 Dataset. Deep{\it
+DeepE{\it n}KCF's performance on UAV123 Dataset. Deep{\it
   E}nKCF outperformed the {\it E}nKCF with hand-crafted features

### 2017-09-09 wacv_for_review.tex
Last stretch. This draft is ready to submit.

@@
 deployment and small footprint of consuming computational
-resources. While these criteria kept in mind, to develop a single,
-target tracking system, we propose an ensemble of the kernelized
-correlation filters (KCF), we call {\it E}nKCF. This committee of KCFs
-is specifically designed to address the scale-change and dynamic
-maneuver of the target over frames. In particular, to guarantee a
-high-speed, run-time performance, we deploy each of KCFs in turn. We
-also developed a Bayes filter to minimize any potential drifts between
-individual KCFs' transitions. Experimental results showed that the
-performance of ours are, on average, 70.10\% for precision at 20
-pixels, 53.00\% for success rate for OTB100 data, and 54.50\% and
-40.2\% for UAV123 data. These results showed that our method is better
-than existing ones over 5\% on precision on 20 pixels and 10-20\% on
-AUC on average. Moreover our implementation ran at 340 fps for OTB100
-and at 416 fps for UAV123 data that is faster than DCF (292 fps) for
-OTB100 and KCF (292 fps), DCF (457 fps) for UAV123. To increase
-flexibility of the proposed {\it E}nKCF running on various one-chip
-computer, e.g., one with GPUs, we explored different levels of deep
-features.
+resources. Kept these criteria in mind, to develop a single, target
+tracking system, we propose an ensemble of the kernelized correlation
+filters (KCF), we call {\it E}nKCF. This committee of KCFs is
+specifically designed to address the scale-change and dynamic maneuver
+of the target over frames. In particular, to guarantee a high-speed,
+run-time performance, we deploy each of KCFs in turn, instead of
+applying multiple KCFs on each frame. To minimize any potential drifts
+between individual KCFs' transition, we developed a Bayes
+filter. Experimental results showed that the performance of ours are,
+on average, 70.10\% for precision at 20 pixels, 53.00\% for success
+rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
+results showed that our method is better than existing ones over 5\%
+on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
+implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
+DCF (457 fps) for UAV123. To increase flexibility of the proposed {\it
+  E}nKCF running on various single-board computers, particularly, ones
+with GPUs, we explored different levels of deep features.
 \end{abstract}
@@
 \end{tabular}
-\caption{The work-flow of {\it E}nKCF tracking algorithm. We show the
-  first seven frames of tracking where the first frame is the
-  initialization frame. Afterward, the order of deploying three KCFs
-  is repeating.}
+\caption{The work-flow of the proposed single-target tracking
+  algorithm, {\it E}nKCF. We show the first seven frames of tracking
+  where the first frame is the initialization frame. Afterward, the
+  order of deploying three KCFs is repeating.}
 \label{Workflows}
@@
 \cite{henriques2015high} showed impressive object tracking results and
-outperformed other state-of-the-art tracking algorithms in terms of
-run-time and tracking accuracy. However, a vanilla form of such an
-online tracker is prone to drift, and fails to track a target over a
-long period of time \cite{henriques2015high}. This is primarily due to
-the dilemma of stability-plasticity in updating appearance model,
-where the appearance model will be overfitted to only the images used
-to train, unless a compromise on the frequency of updating the model
-is carefully implemented \cite{santner2010prost}. For example, one may
-handle a target's scale variation by just concatenating multiple
-correlation filters including KCF and running them on each
-frame. Alternatively one could think of scanning the region of
-interest (ROI) with a list of templates in predefined scale ratios to
-find the target in appropriate scale
+outperformed other state-of-the-art, online tracking algorithms in
+terms of run-time and tracking accuracy. However, a vanilla form of
+such an online tracker is prone to drift, and fails to track a target
+over a long period of time \cite{henriques2015high}. This is primarily
+due to the dilemma of stability-plasticity in updating appearance
+model, where the appearance model will be overfitted to only the
+images used to train, unless a compromise on the frequency of updating
+the model is carefully implemented \cite{santner2010prost}. For
+example, one may handle a target's scale variation by just
+concatenating multiple correlation filters including KCF and running
+them on each frame. Alternatively one could think of scanning the
+region of interest (ROI) with a list of templates in predefined scale
+ratios to find the target in appropriate scale
 \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
@@
 multiple KCFs to address the issues of single target tracking: scale
-and translation, but in a more efficient way. Figure \ref{Workflows}
-illustrates the work-flow of the {\it E}nKCF. In particular, to
-maximize run-time performance and accuracy, instead of running them
-all together on every frame, we deploy three KCFs in turn:
+and translation, but in a more efficient way. To maximize run-time
+performance and accuracy, instead of running them all together on
+every frame, we deploy three KCFs in turn:
 \textit{target}+\textit{small background} translation filter
@@
 change and estimate target's motion efficiently while maintaining or
-increasing run-time performance.
+increasing run-time performance. Figure \ref{Workflows} illustrates
+the work-flow of the {\it E}nKCF.
 
@@
 performance and increase its flexibility being deployed on high-end,
-one-chip computer with GPUs.
+single-board computer with GPUs.
 
@@
 
-In this paper, we propose a novel way of utilizing a multiple of the
-KCFs \cite{henriques2015high} to effectively handle scale variations
-and dynamic maneuvers of a target. To maintain or improve the run-time
+We propose a novel way of utilizing a multiple of the KCFs
+\cite{henriques2015high} to effectively handle scale variations and
+dynamic maneuvers of a target. To maintain or improve the run-time
 performance of the original KCF (e.g., $\ge$ 300), we deploy three
@@
 together. Each of these KCFs is designed to address specific
-challenges, i.e., scale and translation. By alternating their
-deployments, our algorithm will improve the performance of the
-original KCF while preserving the efficient nature and small-footprint
-of the KCF computation.
+challenges: scale and translation. By alternating their deployments,
+our algorithm will improve the performance of the original KCF while
+preserving the efficient nature and small-footprint of the KCF
+computation.
 
@@
 
+Our approach is similar to that of \cite{ma2015long} in that more than
+one KCF is used to address the challenges of single target
+tracking. But ours is different from their approach because we do not
+use those multiple KCFs together at every frame, but alternatively at
+every $k$ frame. It intuitively makes sense to alternatively use
+multiple KCFs with different purposes because the appearance of a
+target does not change drastically over consecutive image frames. For
+most case, even it looks the appearance changes, learning a
+correlation filter over consecutive frames would not be much different
+from the one learned using the image few or $k$ frames later. Figure
+\ref{fig:Filters_Comparison} shows examples supporting this
+observation.
+
+\begin{comment}
 Since Henriques and his colleagues' presented impressive tracking
@@
 this observation.
+\end{comment}
 
@@
 The order of running these three KCFs is important because each of
-these filters aims at addressing different challenges; The
+these filters aims at addressing different challenges. The
 \textit{target+large background} translation filter, $R_{t}^{L}$, is
@@
 filter, $R_{t}^{S}$ is applied to the $i$+$2$th and $i$+$3$th image
-frames, and then the scale filter, $R_{s}$ is applied to the $i$+$4$the
-image. This order repeats until the end of the image frames. The
-translation filter, $R_{t}^{L}$, is intended to run right after the
-scale filter, $R_s$, runs which is applied at every other $i$+$4$
-frames. We run these filters in this way because we want to minimize
-any drifts that are likely to happen running only $R_{s}$. In
+frames, and then the scale filter, $R_{s}$ is applied to the
+$i$+$4$the image. This order repeats until the end of the image
+frames. The translation filter, $R_{t}^{L}$, is intended to run right
+after the scale filter, $R_s$, runs which is applied at every other
+$i$+$4$ frames. We run these filters in this way because we want to
+minimize any drifts that are likely to happen running only $R_{s}$. In
 addition, the filter, $R_{t}^{S}$, is applied to every other two
@@
 $R_{t}^{L}$. By repeating this order of learning KCFs, we can
-integrate more discriminative shape features that cannot be learned by
-$R_{t}^{L}$. This is because it incorporates a large area about
-background in the learned model. The filter, $R_{t}^{L}$, uses shape
-and color information together to recover from any potential drifts --
-drifts could happen only looking the target's scale by the filter,
-$R_{s}$.
+integrate more discriminative shape features that cannot be learned
+just by $R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color
+information together to recover from any potential drifts -- drifts
+could happen only looking the target's scale by the filter, $R_{s}$.
 
 In summary, the scale filter, $R_{s}$, is designed to directly handle
-the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
-with more focused ROIs about the target's translation. On the other
-hand, a translation filter, $R_{t}^{L}$, is designed to look at a
-larger search area to estimate the target's translation and recover
-from any potential drifts. Another translation filter, $R_{t}^{S}$, is
-designed to addresses the drawback of $R_{t}^{L}$ that it may learn
-noisy shape features due to its large search area. In what follows, we
-will detail the main idea behind the KCF.
+the scale change of a target and provides other translation filters
+$R_{t}^{L}$ and $R_{t}^{S}$ with more focused ROIs about the target's
+translation. On the other hand, a translation filter, $R_{t}^{L}$, is
+designed to look at a larger search area to estimate the target's
+translation and recover from any potential drifts. Another translation
+filter, $R_{t}^{S}$, is designed to addresses the drawback of
+$R_{t}^{L}$ that it may learn noisy shape features due to its large
+search area. In what follows, we will detail the main idea behind the
+KCF.
 
@@
 
-In what follows, we will detail two different types of features used
-in {\it E}nKCF : (1) hand-crafted features (fHoG + color-naming) and
-(2) deep convolutional features.
+In the following sections, we will detail two different types of
+features used in {\it E}nKCF : (1) hand-crafted features (fHoG +
+color-naming) and (2) deep convolutional features.
 
@@
 \quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
-\caption{Examples of three filters with hand-crafted features; the translation filter,
-  \textit{target+small background}, the scale filter,
-  \textit{target-only} and another translation filter,
-  \textit{target+large background}, and their hanning window and
-  expected Gaussian response.}
+\caption{Examples of three filters with hand-crafted features.}
 \label{fig:Filters}
@@
 \includegraphics[width=0.48\textwidth]{./figures/Filters_Details_CNN.pdf}
-\caption{The proposed conv224-VGGNet feature extraction in Deep{\it E}nKCF.
-$R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to avoid distortion caused by FFT operation whereas $R_{s}$ does not, to avoid target boundary information loss.}
+\caption{The proposed conv224-VGGNet feature extraction in Deep{\it
+    E}nKCF. $R_{t}^{L}$ and $R_{t}^{s}$ used an hanning window to
+  avoid distortion caused by FFT operation whereas $R_{s}$ does not,
+  in order to avoid target boundary information loss.}
 \label{fig:Filters_CNN}
@@
 %---------------------------------------------------------------------- 
-We evaluate the performance of the proposed {\it E}nKCF tracker and
-its variants using the object tracking benchmark
-datasets. Particularly, we choose two publicly, available datasets:
-OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
+We evaluate, using the object tracking benchmark datasets, the
+performance of the proposed algorithm {\it E}nKCF and its variants.
+Particularly, we choose two publicly, available datasets:
+OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
 and
-UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
+UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
 The OTB100 dataset is comprised of the videos about 100 objects
@@
 first evaluate the performance of {\it E}nKCF with two hand-crafted
-features, fHoG and color-naming.  With this tracker, we aim at
-developing an object tracking algorithm that ``efficiently'' runs on
-an embedded system, a drone, for example, in ``high speed,'' $\ge 30$
+features, fHoG and color-naming.  With this version, we would like to
+have an object tracking algorithm that ``efficiently'' runs on an
+embedded system, a drone, for example, in ``high speed,'' $\ge 30$
 fps. Given this, we believe that the UAV123 dataset is a good fit in
@@
 proposed algorithm with those of the state-of-the-art in a nominal
-dataset. To this end, we chose the OTB100 dataset that
-contains the videos recorded from smart phones and typical cameras in
-perspective view. Also, we tested the proposed algorithm on a
-temporally down-sampled version of the UAV123 dataset, called
-UAV123$\_$10fps dataset. What we would like to evaluate using this
-modified dataset is how robust the proposed algorithm is to the
-drastic motions of camera and targets. Finally, we evaluate the
-Deep{\it E}nKCF, {\it E}nKCF with deep features, on the UAV123 dataset
-to observe how much gain we can achieve over hand-crafted features.
-
-\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
-  E}nKCF is designed to address specific challenges in single target
-tracking problem. Thus each of them should have different values for
-the optimal parameters. For instance, the primary task of the
-translation filter, $R_{t}^{L}$ is to estimate the translation of a
-target from the previous frame whereas the scale filter, $R_{s}$ and
-the estimated state of the particle filter are primarily used to
-estimate the scale and translation. Because of this, we set the
-learning rates of individual filters, $R_{t}^{L}$,
-$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
-$0.010$. For the kernel of the Gaussian neighboring function, we
-empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
-$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
-filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
-ratio. Finally, the padding size for the correlation filters is tuned
-to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
-$R_{s}$. For our particle filter implementation, we empirically set
-the number of particles to $1000$ to balance the run-time performance
-and accuracy. To keep the level of variance among the particles
-reasonable, we performed the re-sampling only when the
-\textit{efficient number of samples}, ($ \hat{N}_{eff} \approx
-(\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a pre-defined
-threshold.
+dataset. To this end, we chose the OTB100 dataset that contains the
+videos recorded from smart phones and typical cameras in perspective
+view. Also, we tested the proposed algorithm on a temporally
+down-sampled version of the UAV123 dataset, called UAV123$\_$10fps
+dataset. What we would like to evaluate using this modified dataset is
+how robust the proposed algorithm is to the drastic motions of camera
+and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
+with deep features, on the UAV123 dataset to observe how much gain we
+can achieve over hand-crafted features.
+
+\textbf{Finding Optimal Hyper-parameters} As each of three KCFs in
+       {\it E}nKCF is designed to address specific challenges in
+       single target tracking problem, the optimal parameters for
+       individual KCFs should be different. We set the learning rates
+       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
+       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
+       the Gaussian neighboring function, we empirically found the
+       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
+       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
+       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
+       ratio. The padding size for the correlation filters is tuned to
+       $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
+       $R_{s}$. For our particle filter implementation, we empirically
+       set the number of particles to $1,000$ to balance the run-time
+       performance and accuracy. To keep the level of variance among
+       the particles reasonable, we performed the re-sampling only
+       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
+       \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a
+       pre-defined threshold.
 
@@
 \textbf{Performance on UAV123 Dataset} We used the precision and
-success rate metrics to compare the performance of the proposed
-algorithm with those of the state-of-the-art high speed tracking
-algorithms. For the precision, we rank the trackers based on the
+success rate to compare the performance of the proposed algorithm with
+those of the state-of-the-art, online algorithms for high speed
+tracking. For the precision, we rank the trackers based on the
 precision numbers at 20 pixels whereas in the success rate plots,
@@
 ($\geq$300 fps): KCF \cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
-MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
-lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
-\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
-\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
-\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
-results on the UAV123 dataset. {\it E}nKCF outperformed most of the
-high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
-precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
-better than ours in accuracy, but 10-20 times slower. For the scale
-adaptation, {\it E}nKCF did second best in terms of AUC for the
-success rate plot. It outperformed other tracking methods in
-high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
-even better than those algorithms that are slow, but a slightly better
-in precision. For example, for AUC, {\it E}nKCF outperformed Struck
-and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
-times faster.
+\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
+\cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast}
+and ones in relatively lower-speed ($\geq$50): SAMF
+\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
+\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
+\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. Figure
+\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. {\it
+  E}nKCF outperformed most of the high-speed tracking methods by
+$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
+Struck did about 5\% better than ours in accuracy, but 10-20 times
+slower. For the scale adaptation, {\it E}nKCF did second best in terms
+of AUC for the success rate plot. It outperformed other tracking
+methods in high-speed by about $20\%$-$25\%$ in AUC. In addition, it
+performed even better than those algorithms that are slow, but a
+slightly better in precision. For example, for AUC, {\it E}nKCF
+outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
+than $10$ and $30$ times faster.
 
@@
 \caption{Results of running different combinations of the KCFs for
-  UAV123 dataset. This table empirically supported the usefulness of
-  combining multiple KCFs as long as the deployment order is optimal. The '$*$' represents
+  UAV123 dataset.  The '$*$' represents
   sequential approach where multiple KCFs are run in the given order in every frame as in LCT \cite{ma2015long}.}
@@
 order of the KCF work best. Table \ref{table:Comparison_to_LCT}
-presents results of this experiment. For this experiment, we removed
-the particle filter. The method at the $2^{nd}$ column flipped the
-order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
-\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
-and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
-removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
-every frame in the listed order. The methods at the $7^{th}$ and
-$8^{th}$ columns ran a translation and a scale filter on every frame
-which is very similar to the way the LCT tracker \cite{ma2015long}
-runs. To be precise, the LCT tracker comes with a re-detection module
-for a long-term tracking. In short, we empirically verified that
+presents results of this experiment. For this experiment, we did not
+use the particle filter to evaluate which order would work best,
+without any extra components. The method at the $2^{nd}$ column
+flipped the order of deploying $R_{t}^{L}$ and $R_{t}^{S}$. The one at
+the $3^{th}$ column removed $R_{t}^{S}$ and replaces with $R_{t}^{L}$
+whereas the one at the $4^{th}$ column removes $R_{t}^{L}$. The
+methods marked with ``*'' ran the filters on every frame in the listed
+order. The methods at the $7^{th}$ and $8^{th}$ columns ran a
+translation and a scale filter on every frame which is very similar to
+the way the LCT tracker \cite{ma2015long} runs.\footnote{To be
+  precise, the LCT tracker comes with a re-detection module for a
+  long-term tracking.} In short, we empirically verified that
 \textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
@@
 achieve 4.26\% higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
-at every frame, but this combination decreases run-time
-performance to 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
-and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
-estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
-final translation estimation given by $R_{t}^{S}$ to update the scale.
+at every frame, but this combination decreases run-time performance to
+317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every
+frame where $R_{t}^{S}$ uses the translation estimated by $R_{t}^{L}$
+to update translation and $R_{s}$ uses the final translation
+estimation given by $R_{t}^{S}$ to update the scale. Table
+\ref{table:Comparison_to_LCT} indeed showed that it is very useful to
+deploy more than one KCF as long as the deployment order is optimal.
 
@@
 
-Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows
-DeepE{\it n}KCF's performance on UAV123 Dataset. Deep{\it
-  E}nKCF outperformed the {\it E}nKCF with hand-crafted features
-by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success
-rates (AUC). The \textit{conv224-VGG} setting performed slightly
-better than \textit{conv222-VGG} in precision while achieving similar
-success rate (AUC) indicating that higher level feature abstraction
-works better for the smaller ROIs. By using feature abstractions
-from the VGGNet pre-trained on millions of images, we can better represent
-the low level features of the object than hand-crafted features
-in challenging cases such as low contrast ROIs. However, the contribution 
-of the deep features is constrained by two factors : (1) low spatial resolution in deeper layers and (2) 
-lost targets due to large target and camera motion in the UAV123 dataset.
+Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows DeepE{\it n}KCF's
+performance on UAV123 dataset. Deep{\it E}nKCF outperformed the {\it
+  E}nKCF with hand-crafted features by about $3\%$ to $5\%$ in
+precision (20 px) and $2\%$ in success rates (AUC). The
+\textit{conv224-VGG} setting performed slightly better than
+\textit{conv222-VGG} in precision while achieving similar success rate
+(AUC). This indicates that higher level feature abstraction works
+better for the smaller ROIs. By using feature abstractions from the
+VGGNet pre-trained on millions of images, we can better represent the
+low level features of the object than hand-crafted features in
+challenging cases such as low contrast ROIs. However, we believe that
+the contribution of the deep features is limited by two factors: (1)
+low spatial resolution in deeper layers and (2) lost targets due to
+large target and camera motion in the UAV123 dataset.
 
@@
 Bayes filter, particle filter, to smooth the transition between three
-KCFs. Two public datasets were used to evaluate the
-performance of the proposed algorithm and found, on average, the
-performance of the proposed algorithm is better than those of the
-existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
-average. Our implementation ran at 340 fps for OTB100 and at 416 fps
-for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
-(292 fps), DCF (457 fps) for UAV123. Finally, we encoded objects
-with deep features to boost tracking performance by $5\%$ on embedded 
-systems with GPUs. As future work, we investigate a way of re-initializing a target when
+KCFs. Two public datasets were used to evaluate the performance of the
+proposed algorithm and found, on average, the performance of the
+proposed algorithm is better than those of the existing ones over 5\%
+on precision at 20 pixels and 10-20\% on AUC on average. Our
+implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
+DCF (457 fps) for UAV123. Finally, we encoded objects with deep
+features to boost tracking performance by $5\%$ on embedded systems
+with GPUs.
+
+As future work, we investigate a way of re-initializing a target when
 the target is lost, due to occlusion, illumination change, drastic

### 2017-09-09 wacv_for_review.tex
Final WACV submission

@@
 most case, even it looks the appearance changes, learning a
-correlation filter over consecutive frames would not be much different
+correlation filter over consecutive frames would not be substantially different
 from the one learned using the image few or $k$ frames later. Figure
@@
 color-naming for the {\it E}nKCF. At the same time, we observed that
-the feature vectors learned from CNN have been used to improve the
+the feature vectors learned from a CNN have been used to improve the
 performance of the trackers based on KCF \cite{ma2015hierarchical,
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF's ({\it fhog} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
+\caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
 dataset.}
@@
 Bayes filter, particle filter, to smooth the transition between three
-KCFs. Two public datasets were used to evaluate the performance of the
+KCFs. In particular, the particle filter estimated the target’s pixel 
+coordinates using evolution of the target’s motion observed over frames.
+Two public datasets were used to evaluate the performance of the
 proposed algorithm and found, on average, the performance of the

### 2017-11-26 wacv_for_review.tex
Final WACV submission
Reviewer 2 comments replied

@@
 
-One of the dominant frameworks for online, object tracking is the
+One of the dominant frameworks for online object tracking is the
 correlation filter that essentially solves a single-target tracking
@@
 target's translation first and estimate a correct scale afterward. In
-particular, Zhang and his colleagues use the MOSSE tracker to estimate
-a target's translation. And then they attempted to update the scale of
+particular, Zhang and his colleagues use the MOSSE tracker \cite{bolme2010visual} to 
+estimate the target's translation. And then they attempted to update the scale of
 the target by further analyzing image, sub-regions with high
@@
 this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
-solution for Equation \ref{eq:Closedform_RidgeReg} exists. To make the
-closed-form solution less complex, an element-wise multiplication in
+solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
+closed-form solution, an element-wise multiplication in
 frequency domain was proposed for $\hat{w}$:
@@
 \end{equation}
-A non-linear version of this closed-form solution is proposed to make
-it more robust to any geometric and photometric variations
+A non-linear version of this closed-form solution is proposed to increase robustness
+to any geometric and photometric variations
 \cite{henriques2015high}. In particular, the diagonalized Fourier
@@
 \end{equation}
-where $\hat{k}^{xx}$ represents the first row of the kernel matrix $K$
-known as \textit{gram matrix} and it is expressed as
+where $\lambda$ represents the regularization weight whereas $\hat{k}^{xx}$ denotes
+ the first row of the kernel matrix $K$ known as \textit{gram matrix} and it is expressed as
 \begin{equation}
@@
 such as HoG and Color showed improved accuracy
-\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. Specifically,
-one can execute an object detection using this kernelized correlation
+\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
+Specifically, one can execute an object detection task using this kernelized correlation
 filter with multi-channel features as
@@
 this is not the case for the small area, translation filter,
-$R_{t}^{S}$, because this translation filter does not contain much of
-the background area around the target. Figure \ref{fig:Filters}(a)
+$R_{t}^{S}$, because it does not contain much of
+the background area around the target. For this reason, the $R_{t}^{S}$ only
+employs the fHoG features. Figure \ref{fig:Filters}(a)
 shows an example of this translation filter. Lastly, we use both fHoG
 and color-naming features again for the scale filter,
-$R_{s}$. Although we are using the same feature representations for
-the scale filter learning relatively smaller area just around the
-target, the reason of using two feature sets is slightly different in
-that the area to learn is too small for the fHoG to represent the area
-well. In addition, the scale filter, explained earlier in the
+$R_{s}$. By assigning fHoG and color-naming features, we ensure
+that the likelihood of inaccurate scale estimation is reduced in comparison to the scale filter
+with only fHoG features. This is more important in our case as the scale filter is operated in every 5 frames
+in the proposed tracker. Also, the scale filter, explained earlier in the
 algorithm \ref{alg:MKCF}, estimates the scale of a target by
@@
 scale filter, $R_{s}$. The smaller template size does not degrade the
-tracking performance neither because of 1) zero padding around the
-target and 2) use of color feature.
+tracking performance because of 1) zero padding around the
+target (smaller ROI) and 2) use of color-naming features.
 \begin{comment}
@@
 as observation to update the state. The weight of a particle is
-computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)$,
-where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and $N$ denotes the
-size of the window as that of a confidence map. 
+computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} y_{R}(x_{t}-i,y_{t}-j)$,
+where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
+size of rows and columns of the confidence map. 
 %Alternatively one can
@@
 \cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
-\cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast}
-and ones in relatively lower-speed ($\geq$50): SAMF
+\cite{bolme2010visual}, and STC \cite{zhang2014fast}
+and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
+CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
 \cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
@@
 \tiny\quad\quad\textbf{UAV123}\\
-\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
-\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
+\includegraphics[width=3.60cm]{./figures/pr_deep.eps}
+\includegraphics[width=3.70cm]{./figures/sr_deep.eps}\\
 \end{tabular}

### 2017-11-26 wacv_for_review.tex
Matrices and vectors represented in bold

@@
 The contribution of this paper is a novel, single-target tracking
-algorithm running in a very high-speed, $\geq 300$ fps that deploys an
+algorithm running in a very high-speed ($\geq300$ fps), that deploys an
 ensemble of KCFs, in turn, to more effectively address the scale
@@
 circulant matrix. The eigenvalues are equal to the DFT transformation
-of the base sample ($x$) elements. The Kernelized Correlation Filter,
-in particular, applies a kernel to $x$ to transform to a more
+of the base sample ($\mathbf{x}$) elements. The Kernelized Correlation Filter,
+in particular, applies a kernel to $\mathbf{x}$ to transform to a more
 discriminative domain. The circulant matrix is then formed by applying
-cyclic shifts on the kernelized $x$. Such kernelization operation
+cyclic shifts on the kernelized $\mathbf{x}$. Such kernelization operation
 maintains O($nlog(n)$) complexity unlike other kernel algorithms
@@
 \begin{equation}
-E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
+E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
 \label{eq:Closedform_RidgeReg}
 \end{equation}
-where $y$ represents the desired continuous response whereas $h$ and
-$x_{c}$ represents the learned correlation filter and training
+where $\mathbf{y}$ represents the desired continuous response whereas $\mathbf{h}$ and
+$\mathbf{x_{c}}$ represents the learned correlation filter and training
 template for the given channel. The parameter $c$ enabled one to
@@
 \begin{equation}
-\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
+\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
 \label{eq:DiagonalizedPrimalSolution}
@@
 \begin{equation}
-\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
+\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
 \label{eq:FourierDualDomainSolution}
 \end{equation}
-where $\lambda$ represents the regularization weight whereas $\hat{k}^{xx}$ denotes
- the first row of the kernel matrix $K$ known as \textit{gram matrix} and it is expressed as
+where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
+ the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and it is expressed as
 \begin{equation}
-k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'})))
+\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'})))
 \label{eq:GaussianCorrelationSingleChannel}
@@
 An early version based on this formulation used grayscale feature
-($C=1$) to learn the solution vector $w$ and multi-channel features
+($C=1$) to learn the solution vector $\mathbf{w}$ and multi-channel features
 such as HoG and Color showed improved accuracy
@@
 \begin{equation}
-r(z) = F^{-1}(\hat{k}^{xz} \odot \hat{\alpha})
+\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
 \end{equation}
-where $r$ denotes the correlation response at all cyclic shifts of the
+where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
 first row of the kernel matrix.
@@
 to estimate the target's image coordinate based on the {\it E}nKCF's
-outputs. The state in this paper, $X_t$, represents a target's pixel
-coordinates and its velocity, $X_t = \lbrace x, y, v_{x}, v_{y}
+outputs. The state in this paper, $\mathbf{X_t}$, represents the target's pixel
+coordinates and its velocity, $\mathbf{X_t} = \lbrace x, y, v_{x}, v_{y}
 \rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
@@
 as observation to update the state. The weight of a particle is
-computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} y_{R}(x_{t}-i,y_{t}-j)$,
+computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$,
 where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
@@
        when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
-       \approx (\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a
+       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower than a
        pre-defined threshold.

### 2017-11-26 wacv_for_review.tex
Typos and grammar mistakes fixed

@@
 	// \textit{Scale Estimation - Correlation Filter}\\
-	Scale pool for $R_{s}$ : $S = \lbrace1.05,1.0,1/1.05\rbrace$,\\
+	Scale pool for $R_{s}$ : $\mathbf{S} = \lbrace1.05,1.0,1/1.05\rbrace$,\\
 	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
@@
 
-Our approach is similar to that of \cite{ma2015long} in that more than
-one KCF is used to address the challenges of single target
-tracking. But ours is different from their approach because we do not
-use those multiple KCFs together at every frame, but alternatively at
-every $k$ frame. It intuitively makes sense to alternatively use
+Our approach is similar to that of \cite{ma2015long} which employs more than
+multiple KCFs sequentially in every frame to address the challenges of single target
+tracking. However, ours is different from their approach because we operate multiple KCFs
+in an alternating manner. It intuitively makes sense to alternatively use
 multiple KCFs with different purposes because the appearance of a
 target does not change drastically over consecutive image frames. For
-most case, even it looks the appearance changes, learning a
-correlation filter over consecutive frames would not be substantially different
-from the one learned using the image few or $k$ frames later. Figure
+most cases, learning a correlation filter over consecutive frames would not be substantially different
+from the one updated with smaller frequency. Figure
 \ref{fig:Filters_Comparison} shows examples supporting this
@@
 available. We found that, with a slight modification, the proposed
-method can effectively handle tracking of object in fast motion and in
-large camera motion. Specifically, we modified {\it E}nKCF by running
+method can effectively handle large displacement of objects in successive frames due to object
+and camera motion. Specifically, we modified {\it E}nKCF by running
 $R_{t}^{L}$ every frame and remove the particle filter instead. We
@@
 Bayes filter, particle filter, to smooth the transition between three
-KCFs. In particular, the particle filter estimated the target’s pixel 
-coordinates using evolution of the target’s motion observed over frames.
+KCFs. In particular, the particle filter estimated the target's pixel 
+coordinates using the evolution of the target's motion observed over frames.
 Two public datasets were used to evaluate the performance of the
-proposed algorithm and found, on average, the performance of the
-proposed algorithm is better than those of the existing ones over 5\%
-on precision at 20 pixels and 10-20\% on AUC on average. Our
+proposed algorithm and it was found that, on average, the performance of the
+proposed algorithm is better than other high-speed trackers over 5\%
+on precision at 20 pixels and 10-20\% on AUC. Our
 implementation ran at 340 fps for OTB100 and at 416 fps for UAV123

### 2017-11-27 wacv_for_review.tex
References updated with ECO, CCOT and SCT

@@
 made for the past few decades. However, to successfully deploy a
-computer vision algorithm on any existing embedded systems, a vision
+computer vision algorithm on any existing embedded system, a vision
 algorithm needs to satisfy, at least, two criteria with the assumption
@@
 deployment and small footprint of consuming computational
-resources. Kept these criteria in mind, to develop a single, target
-tracking system, we propose an ensemble of the kernelized correlation
-filters (KCF), we call {\it E}nKCF. This committee of KCFs is
+resources. Keeping these criterias in mind, we propose an ensemble of the 
+kernelized correlation filters (KCF), called {\it E}nKCF, to develop a single target
+tracking system. This committee of KCFs is
 specifically designed to address the scale-change and dynamic maneuver
-of the target over frames. In particular, to guarantee a high-speed,
+of the target over frames. In particular, to guarantee a high-speed
 run-time performance, we deploy each of KCFs in turn, instead of
@@
 rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
-results showed that our method is better than existing ones over 5\%
-on precision on 20 pixels and 10-20\% on AUC on average. Moreover our
+results showed that our method is better than other high-speed trackers over 5\%
+on precision on 20 pixels and 10-20\% on AUC on average. Moreover, our
 implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
-DCF (457 fps) for UAV123. To increase flexibility of the proposed {\it
-  E}nKCF running on various single-board computers, particularly, ones
-with GPUs, we explored different levels of deep features.
+dataset that is faster than DCF (292 fps) for OTB100 and KCF (292 fps) 
+for UAV123. To increase flexibility of the proposed {\it E}nKCF running on 
+various single-board computers, particularly ones
+with GPUs, we explored different levels of deep convolutional features.
 \end{abstract}

### 2017-11-27 wacv_for_review.tex
References updated with ECO, CCOT and SCT

@@
 	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
-	Skip it for $R_{t}^{L}$ and $R_{t}^{S}$ ($\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$)\\
+	Skip it for $R_{t}^{L}$ (Condition 2) and $R_{t}^{S}$ (Condition 3), $\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$\\
 	// \textit{Update Translation - Particle Filter}\\
@@
 	// \textit{Model Update}\\
-	Update $R_{t}^{S}$,\\
-	Update $R_{t}^{L}$\\
+	Update $R_{t}^{S}$ (Condition 3),\\
+	Update $R_{t}^{L}$ (Condition 2),\\
 	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
@@
 There has been a large volume of studies on utilizing a pre-trained
-CNN features to tracking-by-detection algorithms. For example,
+CNN features in tracking-by-detection algorithms. For example,
 \cite{danelljan2015convolutional} used the activations of the first
@@
 slightly better precision and success rates than the second layer due
-to lost spatial information this layer. \cite{ma2015hierarchical}
+to increased translational invariance in this layer. \cite{ma2015hierarchical}
 proposed a KCF tracker integrating features with higher abstraction

### 2017-11-27 wacv_for_review.tex
ECO, CCOT and SCT trackers added into the experiments
Results Text Updated based on the figures

@@
 \section{Introduction}
+\label{introduction}
 A recent advancement of air/ground/water unmanned vehicle technologies
@@
 \cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
-\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. Figure
-\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. {\it
-  E}nKCF outperformed most of the high-speed tracking methods by
+\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
+originally uses deep convolutional features. For the sake of fair comparison, we employ fHoG
+and color-naming features similar to our study. Figure \ref{fig:UAV123_DATASET} shows 
+the results on the UAV123 dataset. {\it  E}nKCF outperformed most of the high-speed tracking methods by
 $3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
-Struck did about 5\% better than ours in accuracy, but 10-20 times
-slower. For the scale adaptation, {\it E}nKCF did second best in terms
-of AUC for the success rate plot. It outperformed other tracking
-methods in high-speed by about $20\%$-$25\%$ in AUC. In addition, it
-performed even better than those algorithms that are slow, but a
-slightly better in precision. For example, for AUC, {\it E}nKCF
-outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
+Struck did about $5\%$ better than ours in accuracy, but 10-20 times
+slower. The more recent trackers, ECO and CCOT, on the other hand, outperforms
+{\it  E}nKCF by $15\%$ while running at 10-15 times slower speed. 
+For the scale adaptation, {\it E}nKCF did fourth best in terms
+of AUC for the success rate plot. It outperformed other high-speed trackers
+ by about $20\%$-$25\%$ in AUC. In addition, it performed even better than some of the lower-speed trackers. 
+For example, for AUC, {\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
 than $10$ and $30$ times faster.
@@
 \textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
-shows the results on the OTB100 dataset. Same as with UAV123 dataset,
-we observed a similar performance. In particular, {\it E}nKCF showed a
-good performance for handling the scale changes. It was the third best
-and the second fastest tracking algorithm. For the precision metric,
-{\it E}nKCF performed slightly better than most of tracking algorithms
-in high-speed trackers. Interestingly, it outperformed another
+shows the results on the OTB100 dataset. The relative performance of {\it E}nKCF 
+is similar to the UAV123 dataset. In particular, it performed reasonably at approximating target scale. 
+It was the fifth best and the second fastest tracking algorithm. Among the other high-speed trackers,
+it delivers the highest precision and success rates. Interestingly, it outperformed another
 correlation filter based tracker, DSST, but performing $5\%$ behind of
-another low-speed scale adaptive SAMF tracker.
+another low-speed scale adaptive SAMF tracker. Finally, the ECO, and CCOT achieve $15\%$-$20\%$ higher
+precision and success rates than ours while operating at 10-20 times slower rates.
 
@@
 digression from the main idea -- the idea of deploying multiple KCFs
-to make a very fast and effective, single target tracking
+to make a very fast and effective single target tracking
 available. We found that, with a slight modification, the proposed
@@
 and large ego-motion, more challenging. This is because the magnitude
-of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
+of those motions is even bigger. Also, we can observe the sensitivity of 
+the state-of-the-art lower speed trackers to the video frame rate b
+y running them on this downsampled dataset. Figure \ref{fig:UAV123_10fpsDATASET}
 compares the performance of the modified version of {\it E}nKCF and
@@
 the other hand, it does decent job in scale estimation. It ranks as
-second in AUC while running about $150$ faster than MUSTER.
+fourth in AUC while running about 10 to 100 times faster than the top three trackers.
+
+In the lower frame rate scenarios (10 fps), the ECO and CCOT's precision rates drop about
+$10\%$ worse than the original frame rate scenarios. We believe that this is an indicator of
+how good of a performance we can expect from these trackers on low-end hardware. The projected
+frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5 and $\simeq$0.3 by using our 
+convention described in section~\ref{introduction}. In this case, it would be reasonable to expect these
+trackers to perform drastically worse on such hardware whereas the {\it E}nKCF can still perform similarly
+due to its real-time speed on a low-end hardware. Our observations are also supported by \cite{mueller2017context}
+that evaluates the correlation filter-driven trackers at variable frame rates matching their operation rates.
 
@@
 \tiny\quad\textbf{UAV123$\_$10fps}\\
-\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
-\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
+\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
+\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
 \end{tabular}

### 2017-11-28 wacv_for_review.tex
More typos fixed, and grammar mistakes corrected

@@
 computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$,
-where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
-size of rows and columns of the confidence map. 
+where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and 
+$N$ and $M$ represent the number of rows and columns of the confidence map. 
 %Alternatively one can
@@
 %---------------------------------------------------------------------- 
-We evaluate, using the object tracking benchmark datasets, the
-performance of the proposed algorithm {\it E}nKCF and its variants.
-Particularly, we choose two publicly, available datasets:
+We evaluate the performance of the proposed algorithm {\it E}nKCF and its variants 
+using the object tracking benchmark datasets. Particularly, we choose two publicly available datasets:
 OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
-and
-UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
-The OTB100 dataset is comprised of the videos about 100 objects
+and UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
+The OTB100 dataset is comprised of the videos of 100 objects
 whereas UAV123 dataset contains aerial footages of 123 objects.  We
-first evaluate the performance of {\it E}nKCF with two hand-crafted
-features, fHoG and color-naming.  With this version, we would like to
+first test the {\it E}nKCF with two hand-crafted
+features, fHoG and color-naming.  With this version, our goal is to
 have an object tracking algorithm that ``efficiently'' runs on an
-embedded system, a drone, for example, in ``high speed,'' $\ge 30$
-fps. Given this, we believe that the UAV123 dataset is a good fit in
+embedded system, a drone, in ``high speed,'' $\ge 30$
+fps. Given this goal, we believe that the UAV123 dataset is a good fit in
 evaluating the performance of the proposed algorithm. In addition, in
@@
 and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
-with deep features, on the UAV123 dataset to observe how much gain we
-can achieve over hand-crafted features.
+with deep convolutional features, on the UAV123 dataset to observe how much gain we
+can achieve over the hand-crafted features.
 
@@
 success rate to compare the performance of the proposed algorithm with
-those of the state-of-the-art, online algorithms for high speed
+those of the state-of-the-art, online algorithms for high and low speed
 tracking. For the precision, we rank the trackers based on the
@@
 \cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
-originally uses deep convolutional features. For the sake of fair comparison, we employ fHoG
-and color-naming features similar to our study. Figure \ref{fig:UAV123_DATASET} shows 
-the results on the UAV123 dataset. {\it  E}nKCF outperformed most of the high-speed tracking methods by
+originally uses deep convolutional features, however, for the sake of fair comparison, we employ fHoG
+and color-naming features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows 
+the results on the UAV123 dataset. The {\it  E}nKCF outperformed other high-speed trackers by
 $3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
@@
 \textbf{Finding Optimal Combination and Deployment Order of Multiple
-  KCFs} In addition to the comparison with other tracking methods, we
+  KCFs} In addition to comparison with other trackers, we
 also conducted an experiment to see what combination and deployment
@@
 presents results of this experiment. For this experiment, we did not
-use the particle filter to evaluate which order would work best,
+use the particle filter to evaluate which order would work best
 without any extra components. The method at the $2^{nd}$ column
@@
 methods marked with ``*'' ran the filters on every frame in the listed
-order. The methods at the $7^{th}$ and $8^{th}$ columns ran a
-translation and a scale filter on every frame which is very similar to
-the way the LCT tracker \cite{ma2015long} runs.\footnote{To be
+order. The trackers at the $7^{th}$ and $8^{th}$ columns ran a
+translation and a scale filter on every frame which is similar to
+the LCT tracker \cite{ma2015long}.\footnote{To be
   precise, the LCT tracker comes with a re-detection module for a
@@
 tracking accuracy and run-time performance. For example, we could
-achieve 4.26\% higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
+achieve $4.26\%$ higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
 at every frame, but this combination decreases run-time performance to
@@
 $R_{t}^{L}$ every frame and remove the particle filter instead. We
-tested this modified {\it E}nKCF with another vision of the UAV123 that
-the original dataset was temporally down-sampled at $10$ fps and makes
-the challenging original dataset, because of objects in fast motion
-and large ego-motion, more challenging. This is because the magnitude
-of those motions is even bigger. Also, we can observe the sensitivity of 
-the state-of-the-art lower speed trackers to the video frame rate b
-y running them on this downsampled dataset. Figure \ref{fig:UAV123_10fpsDATASET}
-compares the performance of the modified version of {\it E}nKCF and
+tested this modified {\it E}nKCF on the temporally downsampled version of the UAV123 dataset, called 
+UAV123$\_$10fps dataset. The downsampling operation makes the already challenging original dataset, 
+because of objects in fast motion and large ego-motion, more challenging. This is because the magnitude
+of those motions is even bigger. Also, we can measure the sensitivity of 
+the state-of-the-art lower speed trackers to the smaller video frame rates. 
+Figure \ref{fig:UAV123_10fpsDATASET} compares the performance of the modified version of {\it E}nKCF and
 other tracking methods. Our tracker outperforms other high-speed
@@
 the other hand, it does decent job in scale estimation. It ranks as
-fourth in AUC while running about 10 to 100 times faster than the top three trackers.
-
-In the lower frame rate scenarios (10 fps), the ECO and CCOT's precision rates drop about
-$10\%$ worse than the original frame rate scenarios. We believe that this is an indicator of
-how good of a performance we can expect from these trackers on low-end hardware. The projected
+fourth in AUC while running about $10$ to $100$ times faster than the top three trackers.
+
+On the lower frame rate dataset ($10$ fps), the ECO and CCOT's precision rates drop about
+$10\%$ worse than the original dataset. We believe that this is an indicator of
+how good of a performance can be expected from these trackers on a limited hardware. The projected
 frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5 and $\simeq$0.3 by using our 
@@
 \textbf{Evaluation with Deep Features} Our focus so far was to build a
-high speed tracker that can run at $30$fps on a single-board, embedded
-system. To this end, we used two conventional features, fHoG and
-color-naming for the {\it E}nKCF. At the same time, we observed that
-the feature vectors learned from a CNN have been used to improve the
-performance of the trackers based on KCF \cite{ma2015hierarchical,
-  danelljan2015convolutional}, and some of the single-board, embedded
-systems have GPUs. We believe that the performance of the {\it E}nKCF
-could be also improved with deep convolutional features trained on ImageNet dataset.
+high speed tracker that can run at $30$fps on a single-board low-end 
+embedded system. To this end, we used two conventional features, fHoG and
+color-naming for the {\it E}nKCF. To further boost the tracking accuracy, we replace
+the conventional features with deep convolutional features similar to \cite{ma2015hierarchical,
+  danelljan2015convolutional}. However, this performance boost comes with the cost
+  of running the {\it E}nKCF on an embedded system with GPUs.
 \begin{comment}
@@
 
-Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows DeepE{\it n}KCF's
+Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows the DeepE{\it n}KCF's
 performance on UAV123 dataset. Deep{\it E}nKCF outperformed the {\it
@@
 the contribution of the deep features is limited by two factors: (1)
-low spatial resolution in deeper layers and (2) lost targets due to
+increased translational invariance in deeper layers and (2) lost targets due to
 large target and camera motion in the UAV123 dataset.
@@
 and dynamic maneuvers of a target. The way we ran three KCFs is
-optimal in a sense that efficiently handled the scale change and
+optimal in a sense that it efficiently handled the scale change and
 effectively learned the translation of the target. We also developed a
-Bayes filter, particle filter, to smooth the transition between three
-KCFs. In particular, the particle filter estimated the target's pixel 
-coordinates using the evolution of the target's motion observed over frames.
+Bayes filter to smooth the transition between three
+KCFs, especially the transition between the scale and large ROI translation filter. 
 Two public datasets were used to evaluate the performance of the
@@
 implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
-DCF (457 fps) for UAV123. Finally, we encoded objects with deep
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps) 
+for UAV123. Such operation rate tracker can potentially run at real-time
+on a low-end embedded system. Finally, we encoded objects with deep
 features to boost tracking performance by $5\%$ on embedded systems

### 2017-11-28 wacv_for_review.tex
Revise the draft before the experiments.

--- 2017-11-27 wacv_for_review.tex
@@
 most of embedded systems come with an image acquisition pipeline, and
-a tremendous amount of progresses on computer vision research has been
+a tremendous amount of progress on computer vision research has been
 made for the past few decades. However, to successfully deploy a
@@
 deployment and small footprint of consuming computational
-resources. Keeping these criterias in mind, we propose an ensemble of the 
-kernelized correlation filters (KCF), called {\it E}nKCF, to develop a single target
-tracking system. This committee of KCFs is
-specifically designed to address the scale-change and dynamic maneuver
-of the target over frames. In particular, to guarantee a high-speed
-run-time performance, we deploy each of KCFs in turn, instead of
-applying multiple KCFs on each frame. To minimize any potential drifts
-between individual KCFs' transition, we developed a Bayes
-filter. Experimental results showed that the performance of ours are,
-on average, 70.10\% for precision at 20 pixels, 53.00\% for success
-rate for OTB100 data, and 54.50\% and 40.2\% for UAV123 data. These
-results showed that our method is better than other high-speed trackers over 5\%
-on precision on 20 pixels and 10-20\% on AUC on average. Moreover, our
-implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-dataset that is faster than DCF (292 fps) for OTB100 and KCF (292 fps) 
-for UAV123. To increase flexibility of the proposed {\it E}nKCF running on 
-various single-board computers, particularly ones
-with GPUs, we explored different levels of deep convolutional features.
+resources. To develop a single-target tracking algorithm that
+satisfies these criteria, we propose an ensemble of the kernelized
+correlation filters (KCF), we call it {\it E}nKCF. A committee of KCFs
+is specifically designed to address the scale-change and dynamic
+maneuver of the target over frames. In particular, to guarantee a
+high-speed run-time performance, we deploy each of KCFs in turn,
+instead of applying multiple KCFs to each frame. To minimize any
+potential drifts between individual KCFs' transition, we developed a
+Bayes filter. Experimental results showed that the performance of ours
+is, on average, 70.10\% for precision at 20 pixels, 53.00\% for
+success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
+data. The results showed that our method is better than other
+high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
+AUC on average. Moreover, our implementation ran at 340 fps for OTB100
+and at 416 fps for UAV123 dataset that is faster than DCF (292 fps)
+for OTB100 and KCF (292 fps) for UAV123. To increase flexibility of
+the proposed {\it E}nKCF running on various single-board computers,
+particularly ones with GPUs, we also explored different levels of deep
+convolutional features.
 \end{abstract}
@@
 system.\footnote{In general, it would not be easy to compare run-time
-  performance of a computer vision algorithm at an Intel or AMD
-  processor running on a desktop or a laptop and at that (e.g., ARM)
-  of a single-board, embedded system. This is primarily due to the
-  difference in their architectures and available computing
-  resources. To derive these numbers (300 and 30 fps), we assume that
-  there is roughly, at least, an 1/10th scale down of computational
-  resources from a typical PC to an embedded system. We found such a
-  scale-down in computation based on exemplar processors, e.g.,
-  Intel's i7 quad-core vs ARMv8 dual-core.}
+  performance of a computer vision algorithm running on an Intel or
+  AMD desktop or a laptop and on that (e.g., ARM) of a single-board,
+  embedded system. This is primarily due to the difference in their
+  architectures and available computing resources. To derive these
+  numbers (``300'' and ``30'' fps), we assume that there is roughly an
+  1/10th scale down of computational resources from a typical PC to an
+  embedded system. We found such a scale-down in computation based on
+  exemplar processors, e.g., Intel's i7 quad-core vs ARMv8 dual-core.}
 
@@
 \end{tabular}
-\caption{The work-flow of the proposed single-target tracking
-  algorithm, {\it E}nKCF. We show the first seven frames of tracking
-  where the first frame is the initialization frame. Afterward, the
-  order of deploying three KCFs is repeating.}
+\caption{The workflow of the {\it E}nKCF. The first frame is used to
+  initialize the tracking algorithm and a particle filter. For the
+  next six frames, each of three KCF is deployed in turn to estimate
+  the translation and scale change of a target. Afterward, the order
+  of deploying three KCFs is repeating.}
 \label{Workflows}
@@
 this regression problem using a ridge regression in a closed
-form. However, this solution involves in expensive matrix operations
-$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
-solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
-frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
-this reformulation, an object tracking pipeline based on the
-correlation filter can run very efficiently and be even easily
-implemented. In fact, an extension of a linear correlation filter, the
-kernelized correlation filter with multi-channel features
-\cite{henriques2015high} showed impressive object tracking results and
-outperformed other state-of-the-art, online tracking algorithms in
-terms of run-time and tracking accuracy. However, a vanilla form of
-such an online tracker is prone to drift, and fails to track a target
-over a long period of time \cite{henriques2015high}. This is primarily
-due to the dilemma of stability-plasticity in updating appearance
-model, where the appearance model will be overfitted to only the
-images used to train, unless a compromise on the frequency of updating
-the model is carefully implemented \cite{santner2010prost}. For
-example, one may handle a target's scale variation by just
-concatenating multiple correlation filters including KCF and running
-them on each frame. Alternatively one could think of scanning the
-region of interest (ROI) with a list of templates in predefined scale
-ratios to find the target in appropriate scale
+form. However, this solution has to deal with expensive matrix
+operations $\mathcal{O}(n^{3})$. The correlation filter offers a less
+complex solution, $\mathcal{O}(n\log n)$ over element-wise
+multiplication in a frequency domain
+\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
+an object tracking pipeline based on the correlation filter can run
+very efficiently and be even easily implemented. In fact, an extension
+of a linear correlation filter, the kernelized correlation filter with
+multi-channel features \cite{henriques2015high} showed impressive
+object tracking results and outperformed other state-of-the-art,
+online tracking algorithms in terms of run-time and tracking
+accuracy. However, a vanilla form of such an online tracker is prone
+to drift, and fails to track a target over a long period of time
+\cite{henriques2015high}. This is primarily due to the dilemma of
+stability-plasticity in updating appearance model, where the
+appearance model will be overfitted to only the images used to train,
+unless a compromise on the frequency of updating the model is
+carefully implemented \cite{santner2010prost}. For example, one may
+handle a target's scale variation by just concatenating multiple
+correlation filters including KCF and running them on each
+frame. Alternatively one could think of scanning the region of
+interest (ROI) with a list of templates in predefined scale ratios to
+find the target in appropriate scale
 \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
@@
 target highly likely appears \cite{zhang2014fast} -- estimate a
-target's translation first and estimate a correct scale afterward. In
-particular, Zhang and his colleagues use the MOSSE tracker \cite{bolme2010visual} to 
-estimate the target's translation. And then they attempted to update the scale of
-the target by further analyzing image, sub-regions with high
-confidence. This is based on an assumption that the scale of a target
-would not change much over two consecutive frames. Similarly, Ma and
-his colleagues used two KCFs to learn the translation and scale of a
-target separately \cite{ma2015long}. In particular, a KCF is used to
-learn the translation of the target and its background. Given this,
-another KCF is used to learn the target area to estimate a new scale
-of the target. However, because of running more than a KCF on each
-frame, this method degrades its run-time performance (i.e., $\leq 50
+target's translation first and then estimate correct scale. For
+example, Zhang and his colleagues used the MOSSE tracker
+\cite{bolme2010visual} to estimate the target's translation. And then
+they attempted to update the scale of the target by further analyzing
+image, sub-regions in high confidence. Their method is based on an
+assumption that the scale of a target would not change much over two
+consecutive frames. Similarly, Ma and his colleagues used two KCFs to
+learn the translation and scale of a target separately
+\cite{ma2015long}. In particular, a KCF is used to learn the
+translation of the target and its background. Given this, another KCF
+is used to learn the target area to estimate a new scale of the
+target. However, because of running more than a KCF on each frame,
+this method degrades its run-time performance (i.e., $\leq 50
 fps$). Our method is motivated by this idea -- the idea of deploying
@@
 \textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). By doing so, our method aims at addressing a scale
+($R_{t}^{L}$). By doing so, our method aims at addressing scale
 change and estimate target's motion efficiently while maintaining or
 increasing run-time performance. Figure \ref{Workflows} illustrates
-the work-flow of the {\it E}nKCF.
+the workflow of the {\it E}nKCF.
 
 The contribution of this paper is a novel, single-target tracking
-algorithm running in a very high-speed ($\geq300$ fps), that deploys an
-ensemble of KCFs, in turn, to more effectively address the scale
-variance and the dynamic maneuver of a target while preserving
-run-time performance as high as possible. We also developed a Bayes
-filter to minimize any potential drifts while transiting one KCF to
-another. In addition, we explore deep features with varying levels of
-abstraction in the proposed {\it E}nKCF to improve tracking
-performance and increase its flexibility being deployed on high-end,
-single-board computer with GPUs.
+algorithm running in a very high-speed ($\geq300$ fps). In particular,
+to effectively address the changes in scale and translation of a
+target, the proposed algorithm deploys each of three, special-purpose
+KCFs in turn. Because of such a deployment strategy, the run-time
+performance of the proposed algorithm perserves high. To minimize any
+potential drifts while switching KCFs, we developed a Bayes filter. In
+addition, to increase the flexibility of the proposed algorithm's
+usage, we explore deep features with varying levels of abstraction for
+the proposed {\it E}nKCF to improve performance.
 
@@
 %---------------------------------------------------------------------- 
-
 We propose a novel way of utilizing a multiple of the KCFs
@@
 KCFs in turn, instead of applying them on the same image frame
-together. Each of these KCFs is designed to address specific
-challenges: scale and translation. By alternating their deployments,
-our algorithm will improve the performance of the original KCF while
-preserving the efficient nature and small-footprint of the KCF
-computation.
+together. Each of these KCFs is designed to address the challenge of
+single-target tracking -- variance in scale and translation. By
+deploying each of three KCFs in turn, our algorithm will improve the
+performance of the original KCF while preserving the original KCF's
+high run-time performance and small-footprint.
 
@@
 first filter, $R_{t}^{S}$, focuses on learning the target area and its
-background, \textit{target}+\textit{small background} for addressing a
-marginal translation by a target, the second filter, $R_{s}$, focuses
-entirely on learning the target's scale, \textit{target-only}, and the
-last filter, $R_{t}^{L}$, focuses on the target area and its
-background bigger than that of the first filter, $R_{t}^{S}$,
-\textit{target}+\textit{large background}. We set up {\it E}nKCF in
-this way because, we believe, a correlation filter for learning a
-target's translation should include the background of the target to
-better discriminate it from its surrounding, and another correlation
-filter should focus on the target itself to estimate the right scale
-of the target. By setting a transition filter with larger padding
-size, $R_{t}^{L}$, we can recover from potential drifts after the
-frames we only run the scale filter. Additionally, we design a
-translation filter with smaller padding size, $R_{t}^{S}$, to better
-localize the position of the target after the frames we only run
-$R_{t}^{L}$.
-
-Our approach is similar to that of \cite{ma2015long} which employs more than
-multiple KCFs sequentially in every frame to address the challenges of single target
-tracking. However, ours is different from their approach because we operate multiple KCFs
-in an alternating manner. It intuitively makes sense to alternatively use
-multiple KCFs with different purposes because the appearance of a
-target does not change drastically over consecutive image frames. For
-most cases, learning a correlation filter over consecutive frames would not be substantially different
-from the one updated with smaller frequency. Figure
-\ref{fig:Filters_Comparison} shows examples supporting this
-observation.
+background for addressing a marginal translation by a target, the
+second filter, $R_{s}$, focuses entirely on learning the target's
+scale, and the last filter, $R_{t}^{L}$, focuses on the target area
+and its background bigger than that of the first filter,
+$R_{t}^{S}$. We set up {\it E}nKCF in this way so that a correlation
+filter for learning a target's translation could include the
+background of the target to better discriminate it from its
+surrounding, and another correlation filter could focus on the target
+itself to estimate the right scale of the target. In particular, a
+transition filter with larger padding size, $R_{t}^{L}$ will enable
+{\it E}nKCF to recover from potential drifts after a scale filter is
+applied to the input images. Whereas another translation filter with
+smaller padding size, $R_{t}^{S}$ will help {\it E}nKCF to better
+localize the position of the target after a translation filter is
+applied.
+
+Our approach is similar to that of \cite{ma2015long} which
+sequentially applied more than one KCF to every frame, but different
+in that we operate multiple KCFs in an alternating manner. It
+intuitively makes sense to alternatively use multiple KCFs with
+different purposes because the appearance of a target does not change
+drastically over consecutive images. In other words, for most cases,
+learning a correlation filter over consecutive frames would not be
+substantially different from the one updated with smaller
+frequency. Figure \ref{fig:Filters_Comparison} shows examples
+supporting this observation.
 
@@
 The order of running these three KCFs is important because each of
-these filters aims at addressing different challenges. The
-\textit{target+large background} translation filter, $R_{t}^{L}$, is
-applied to the $i$th and $i$+$1$th image frames, another translation
-filter, $R_{t}^{S}$ is applied to the $i$+$2$th and $i$+$3$th image
-frames, and then the scale filter, $R_{s}$ is applied to the
-$i$+$4$the image. This order repeats until the end of the image
-frames. The translation filter, $R_{t}^{L}$, is intended to run right
-after the scale filter, $R_s$, runs which is applied at every other
-$i$+$4$ frames. We run these filters in this way because we want to
-minimize any drifts that are likely to happen running only $R_{s}$. In
-addition, the filter, $R_{t}^{S}$, is applied to every other two
-frames before $R_{s}$ and right after two consecutive frames running
-$R_{t}^{L}$. By repeating this order of learning KCFs, we can
-integrate more discriminative shape features that cannot be learned
-just by $R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color
-information together to recover from any potential drifts -- drifts
-could happen only looking the target's scale by the filter, $R_{s}$.
+these filters aims at addressing different challenges. A translation
+filter, $R_{t}^{L}$, is applied to the $i$th and $i$+$1$th image
+frames, another translation filter, $R_{t}^{S}$ is applied to the
+$i$+$2$th and $i$+$3$th image frames, and then the scale filter,
+$R_{s}$ is applied to the $i$+$4$the image. This order repeats until
+the last image is presented. Note that the translation filter,
+$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
+runs which is applied at every other $i$+$4$ frames. We run these
+filters in this way because we want to minimize any drifts that are
+likely to happen running only $R_{s}$. In addition, the filter,
+$R_{t}^{S}$, is applied to every other two frames before $R_{s}$ and
+right after two consecutive frames running $R_{t}^{L}$. By repeating
+this order of learning three KCFs, we can integrate more
+discriminative shape features that cannot be learned just by
+$R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color information
+together to recover from any potential drifts -- drifts could happen
+only looking the target's scale by the filter, $R_{s}$.
 
@@
 \textbf{Kernelized Correlation Filter} The Kernelized Correlation
-Filter is a well-known single target tracking method and its work
-flow has been detailed in other papers
+Filter is a well-known single target tracking method and its workflow
+has been detailed in other papers
 \cite{henriques2012exploiting,henriques2015high}. This section briefly
@@
 circulant matrix. The eigenvalues are equal to the DFT transformation
-of the base sample ($\mathbf{x}$) elements. The Kernelized Correlation Filter,
-in particular, applies a kernel to $\mathbf{x}$ to transform to a more
-discriminative domain. The circulant matrix is then formed by applying
-cyclic shifts on the kernelized $\mathbf{x}$. Such kernelization operation
-maintains O($nlog(n)$) complexity unlike other kernel algorithms
-leading to O($n^{2}$) or even higher complexities.
+of the base sample ($\mathbf{x}$) elements. The Kernelized Correlation
+Filter, in particular, applies a kernel to $\mathbf{x}$ to transform
+to a more discriminative domain. The circulant matrix is then formed
+by applying cyclic shifts on the kernelized $\mathbf{x}$. Such
+kernelization operation maintains O($nlog(n)$) complexity unlike other
+kernel algorithms leading to O($n^{2}$) or even higher complexities.
 
@@
 this is not the case for the small area, translation filter,
-$R_{t}^{S}$, because it does not contain much of
-the background area around the target. For this reason, the $R_{t}^{S}$ only
-employs the fHoG features. Figure \ref{fig:Filters}(a)
-shows an example of this translation filter. Lastly, we use both fHoG
-and color-naming features again for the scale filter,
-$R_{s}$. By assigning fHoG and color-naming features, we ensure
-that the likelihood of inaccurate scale estimation is reduced in comparison to the scale filter
-with only fHoG features. This is more important in our case as the scale filter is operated in every 5 frames
-in the proposed tracker. Also, the scale filter, explained earlier in the
-algorithm \ref{alg:MKCF}, estimates the scale of a target by
-correlating it with three candidate ROIs. This search may increase the
-run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
-$\mathcal{O}(3(n\log n))$. To ensure actual filtering operations
-practical, we use a smaller template size (i.e., 64$\times n$) for the
-scale filter, $R_{s}$. The smaller template size does not degrade the
-tracking performance because of 1) zero padding around the
-target (smaller ROI) and 2) use of color-naming features.
-\begin{comment}
-The ROI considered by $R_{s}$ is resized to a smaller template
-resolution ($64\times n$) as shown in Figure~\ref{fig:Filters}(c).
-This leads to less discriminative shape features. To reduce the noise
-in $R_{s}$, we concatenate color features.  The $R_{s}$ estimates the
-scale by correlating the filter with three candidate ROIs as detailed
-in algorithm~\ref{alg:MKCF}.  This increases the complexity from
-$\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$.  To
-reduce the number of operations, we assign a smaller template size to
-$R_{s}$.  This does not degrade the tracking performance due to two
-reasons: (1) zero padding around the target and (2) integration of
-color features. This way, we keep the run-time complexity of the
-$R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
-correlation filter on a single ROI. By reducing the template size of
-$R_{s}$, fluctuating run-time performances among $R_{s}$ and,
-$R_{t}^{L}$ and $R_{t}^{S}$, are avoided which is desired in embedded
-systems.
-
-{\it Burak: Why do we need to keep the run-time complexity
-  of $R_{S}$ and $R_{t}^{L}$ the same?}
-
-{\it YoungWoo : Because we want $R_{t}^{S}$, $R_{t}^{L}$ and $R_{s}$
-  to have similar fps (30fps) to avoid missing frames on an embedded
-  system. We can think of each one as an individual tracker and we do
-  not want one operating at 10fps while others running at 30 fps.}
-
-{\it Burak: What you told me is purely empirical which is fine. But
-  you'll have to tell the readers why we wanted to keep the run-time
-  complexity of those filters same!}
-\end{comment}
-
-\textbf{{\it E}nKCF with Convolutional Neural Network Features} In
-addition to hand-crafted features, we explore deep features to boost
-tracking performance. This version of {\it E}nKCF, Deep{\it E}nKCF is
-designed to make {\it E}nKCF run on high-end embedded systems with GPUs
+$R_{t}^{S}$, because it does not contain much of the background area
+around the target. For this reason, the $R_{t}^{S}$ only employs the
+fHoG features. Figure \ref{fig:Filters}(a) shows an example of this
+translation filter. Lastly, we use both fHoG and color-naming features
+again for the scale filter, $R_{s}$. By assigning fHoG and
+color-naming features, we ensure that the likelihood of inaccurate
+scale estimation is reduced in comparison to the scale filter with
+only fHoG features. This is more important in our case as the scale
+filter is operated in every 5 frames in the proposed tracker. Also,
+the scale filter, explained earlier in the algorithm \ref{alg:MKCF},
+estimates the scale of a target by correlating it with three candidate
+ROIs. This search may increase the run-time complexity of the scale
+filter from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$. To
+ensure actual filtering operations practical, we use a smaller
+template size (i.e., 64$\times n$) for the scale filter, $R_{s}$. The
+smaller template size does not degrade the tracking performance
+because of 1) zero padding around the target (smaller ROI) and 2) use
+of color-naming features.
+
+\textbf{{\it E}nKCF with Deep Convolutional Features} In addition to
+hand-crafted features, we explore deep features to boost tracking
+performance. This version of {\it E}nKCF, Deep{\it E}nKCF is designed
+to make {\it E}nKCF run on high-end embedded systems with GPUs
 installed.
@@
 slightly better precision and success rates than the second layer due
-to increased translational invariance in this layer. \cite{ma2015hierarchical}
-proposed a KCF tracker integrating features with higher abstraction
-capacity.  Their method first employs the third convolutional layer
-features to estimate the response map. In the next stage, the KCF,
-concentrating on the second convolutional layer features, is run to
-update transition. The third KCF then works on the transition given by
-the previous KCF and learns the first convolutional layer features to
-update the transition. This coarse-to-fine approach accommodates
-different levels of abstractions of the object. However, it runs
-multiple KCFs in a sequential fashion, increasing the run-time
-complexity. For this reason, we follow a similar approach to
-\cite{danelljan2015convolutional} to embed deep features in {\it
-  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
-level of feature encodings with different KCFs. The translation
-filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
-area than the scale filter, $R_{s}$. Given this, we can assign deeper
-feature encodings to $R_{s}$ as it learns less spatial information
-than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
-the fourth convolutional layer features ($26\times26\times128$) to
-$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
-activations of the second layer features
+to increased translational invariance in this
+layer. \cite{ma2015hierarchical} proposed a KCF tracker integrating
+features with higher abstraction capacity.  Their method first employs
+the third convolutional layer features to estimate the response
+map. In the next stage, the KCF, concentrating on the second
+convolutional layer features, is run to update transition. The third
+KCF then works on the transition given by the previous KCF and learns
+the first convolutional layer features to update the transition. This
+coarse-to-fine approach accommodates different levels of abstractions
+of the object. However, it runs multiple KCFs in a sequential fashion,
+increasing the run-time complexity. For this reason, we follow an
+approach similar to \cite{danelljan2015convolutional}, in order to
+embed deep features in {\it E}nKCF. Our {\it E}nKCF algorithm enables
+us to exploit different level of feature encodings with different
+KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider
+at least twice bigger area than the scale filter, $R_{s}$. Given this,
+we can assign deeper feature encodings to $R_{s}$ as it learns less
+spatial information than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign
+the activations of the fourth convolutional layer features
+($26\times26\times128$) to $R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$
+are assigned the activations of the second layer features
 ($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
@@
 \textit{conv224-VGG}. The conv222 setting stands for the assignment of
-the activations of $2^{th}$ convolutional layer features
-of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
-since it provides higher spatial resolution at the first several layers than AlexNet
-\cite{krizhevsky2012imagenet}.
+the activations of $2^{th}$ convolutional layer features of VGGNet to
+$R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it
+provides higher spatial resolution at the first several layers than
+AlexNet \cite{krizhevsky2012imagenet}.
 
@@
 to estimate the target's image coordinate based on the {\it E}nKCF's
-outputs. The state in this paper, $\mathbf{X_t}$, represents the target's pixel
-coordinates and its velocity, $\mathbf{X_t} = \lbrace x, y, v_{x}, v_{y}
-\rbrace$, where $x$ and $y$ are the pixel coordinates of the target's
-centroid, $v_x$ and $v_y$ are the velocity estimated along the
-$x$-axis and $y$-axis. The particle filter predicts, using a constant
-velocity motion model, a target's next state by generating a predefined
-number of particles. Then it uses the confidence maps of {\it E}nKCF
-as observation to update the state. The weight of a particle is
-computed as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$,
-where $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$ and $M$ denote the
-size of rows and columns of the confidence map. 
-%Alternatively one can
-%also use the Euclidean distance of particles to the location of
-%maximum response of the confidence map.
+outputs. The state in this paper, $\mathbf{X_t}$, represents the
+target's pixel coordinates and its velocity, $\mathbf{X_t} = \lbrace
+x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
+coordinates of the target's centroid, $v_x$ and $v_y$ are the velocity
+estimated along the $x$-axis and $y$-axis. The particle filter
+predicts, using a constant velocity motion model, a target's next
+state by generating a predefined number of particles. Then it uses the
+confidence maps of {\it E}nKCF as observation to update the state. The
+weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
+\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
+$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
+and $M$ denote the size of rows and columns of the confidence map.
+
 \begin{comment}

### 2017-11-28 wacv_for_review.tex

@@
 to estimate the target's image coordinate based on the {\it E}nKCF's
-outputs. The state in this paper, $\mathbf{X_t}$, represents the
+outputs. The state in this paper, $\mathbf{x_t}$, represents the
 target's pixel coordinates and its velocity, $\mathbf{X_t} = \lbrace
@@
 
-\begin{comment}
-We chooses some particles based on their importance to estimate the
-target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
-\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
-of a particle filter, we skip the importance re-sampling step when the
-scale filter, $R_{s}$, estimates the target's scale change. This is
-because we observe the confidence map from the scale filter, $R_s$ is
-sometime noisy. In addition, at every iteration, we check the variance
-in the velocity components of the particles to re-assign velocities
-from uniform initial distribution to keep variance high enough.
-\end{comment}
-
 %----------------------------------------------------------------------
@@
 %---------------------------------------------------------------------- 
-We evaluate, using the object tracking benchmark datasets, the
-performance of the proposed algorithm {\it E}nKCF and its variants.
-Particularly, we choose two publicly, available datasets:
+We evaluate the performance of the proposed algorithm {\it E}nKCF and
+its variants using the object tracking benchmark
+datasets. Particularly, we choose two publicly available datasets:
 OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
@@
 UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
-The OTB100 dataset is comprised of the videos about 100 objects
-whereas UAV123 dataset contains aerial footages of 123 objects.  We
-first evaluate the performance of {\it E}nKCF with two hand-crafted
-features, fHoG and color-naming.  With this version, we would like to
-have an object tracking algorithm that ``efficiently'' runs on an
-embedded system, a drone, for example, in ``high speed,'' $\ge 30$
-fps. Given this, we believe that the UAV123 dataset is a good fit in
-evaluating the performance of the proposed algorithm. In addition, in
-the UAV123 dataset, there are many challenging, realistic scenes,
-e.g., abrupt scale/illumination changes. Although we are primarily
-interested in developing an algorithm for mobile, embedded robotic
-applications, it is also important to compare the performance of the
-proposed algorithm with those of the state-of-the-art in a nominal
-dataset. To this end, we chose the OTB100 dataset that contains the
-videos recorded from smart phones and typical cameras in perspective
-view. Also, we tested the proposed algorithm on a temporally
-down-sampled version of the UAV123 dataset, called UAV123$\_$10fps
-dataset. What we would like to evaluate using this modified dataset is
-how robust the proposed algorithm is to the drastic motions of camera
-and targets. Finally, we evaluate the Deep{\it E}nKCF, {\it E}nKCF
-with deep features, on the UAV123 dataset to observe how much gain we
-can achieve over hand-crafted features.
+The OTB100 dataset is comprised of the videos of 100 objects whereas
+UAV123 dataset contains aerial footages of 123 objects.  We first test
+the {\it E}nKCF with two hand-crafted features, fHoG and color-naming.
+With this version, our goal is to have an object tracking algorithm
+that ``efficiently'' runs on an embedded system, a drone, in ``high
+speed,'' $\ge 30$ fps. Given this goal, we believe that the UAV123
+dataset is a good fit in evaluating the performance of the proposed
+algorithm. In addition, in the UAV123 dataset, there are many
+challenging, realistic scenes, e.g., abrupt scale/illumination
+changes. Although we are primarily interested in developing an
+algorithm for mobile, embedded robotic applications, it is also
+important to compare the performance of the proposed algorithm with
+those of the state-of-the-art in a nominal dataset. To this end, we
+chose the OTB100 dataset that contains the videos recorded from smart
+phones and typical cameras in perspective view. Also, we tested the
+proposed algorithm on a temporally down-sampled version of the UAV123
+dataset, called UAV123$\_$10fps dataset. What we would like to
+evaluate using this modified dataset is how robust the proposed
+algorithm is to the drastic motions of camera and targets. Finally, we
+evaluate the Deep{\it E}nKCF, {\it E}nKCF with deep convolutional
+features, on the UAV123 dataset to observe how much gain we can
+achieve over the hand-crafted features.
 
@@
 
-%\textbf{Features Selections} We used different features for each of
-%three KCFs as each of them has different goals to accomplish. In
-%particular, the translation filter, $R_{t}^{L}$, uses both the fast
-%Histograms of Oriented Gradients (fHoG) \cite{felzenszwalb2010object}
-%and color-naming \cite{van2009learning} features to more effectively
-%learn the background around the target as shown in Figure \ref{fig:Filters}. 
-%Through experiments, we found that only fHoG didn't work well to cover a larger ROI; another
-%translation filter, $R_{t}^{S}$, worked well when it used fHoG
-%features only; the scale filter, $R_{s}$ did when it used both fHoG
-%and color features.
-
 \textbf{Performance on UAV123 Dataset} We used the precision and
 success rate to compare the performance of the proposed algorithm with
-those of the state-of-the-art, online algorithms for high speed
-tracking. For the precision, we rank the trackers based on the
+those of the state-of-the-art, online algorithms for high and low
+speed tracking. For the precision, we rank the trackers based on the
 precision numbers at 20 pixels whereas in the success rate plots,
@@
 \cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
-\cite{bolme2010visual}, and STC \cite{zhang2014fast}
-and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
-CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
+\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
+relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, CCOT
+\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
 \cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
 \cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
-\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
-originally uses deep convolutional features. For the sake of fair comparison, we employ fHoG
-and color-naming features similar to our study. Figure \ref{fig:UAV123_DATASET} shows 
-the results on the UAV123 dataset. {\it  E}nKCF outperformed most of the high-speed tracking methods by
-$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
-Struck did about $5\%$ better than ours in accuracy, but 10-20 times
-slower. The more recent trackers, ECO and CCOT, on the other hand, outperforms
-{\it  E}nKCF by $15\%$ while running at 10-15 times slower speed. 
-For the scale adaptation, {\it E}nKCF did fourth best in terms
-of AUC for the success rate plot. It outperformed other high-speed trackers
- by about $20\%$-$25\%$ in AUC. In addition, it performed even better than some of the lower-speed trackers. 
-For example, for AUC, {\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
-than $10$ and $30$ times faster.
+\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
+CCOT trackers originally uses deep convolutional features, however,
+for the sake of fair comparison, we employ fHoG and color-naming
+features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
+the results on the UAV123 dataset. The {\it E}nKCF outperformed other
+high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
+algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
+accuracy, but 10-20 times slower. The more recent trackers, ECO and
+CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
+running at 10-15 times slower speed.  For the scale adaptation, {\it
+  E}nKCF did fourth best in terms of AUC for the success rate plot. It
+outperformed other high-speed trackers by about $20\%$-$25\%$ in
+AUC. In addition, it performed even better than some of the
+lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
+Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
+and $30$ times faster.
 
@@
 \textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
-shows the results on the OTB100 dataset. The relative performance of {\it E}nKCF 
-is similar to the UAV123 dataset. In particular, it performed reasonably at approximating target scale. 
-It was the fifth best and the second fastest tracking algorithm. Among the other high-speed trackers,
-it delivers the highest precision and success rates. Interestingly, it outperformed another
-correlation filter based tracker, DSST, but performing $5\%$ behind of
-another low-speed scale adaptive SAMF tracker. Finally, the ECO, and CCOT achieve $15\%$-$20\%$ higher
-precision and success rates than ours while operating at 10-20 times slower rates.
+shows the results on the OTB100 dataset. The relative performance of
+{\it E}nKCF is similar to the UAV123 dataset. In particular, it
+performed reasonably at approximating target scale.  It was the fifth
+best and the second fastest tracking algorithm. Among the other
+high-speed trackers, it delivers the highest precision and success
+rates. Interestingly, it outperformed another correlation filter based
+tracker, DSST, but performing $5\%$ behind of another low-speed scale
+adaptive SAMF tracker. Finally, the ECO, and CCOT achieve
+$15\%$-$20\%$ higher precision and success rates than ours while
+operating at 10-20 times slower rates.
 
@@
 digression from the main idea -- the idea of deploying multiple KCFs
-to make a very fast and effective single target tracking
-available. We found that, with a slight modification, the proposed
-method can effectively handle large displacement of objects in successive frames due to object
-and camera motion. Specifically, we modified {\it E}nKCF by running
-$R_{t}^{L}$ every frame and remove the particle filter instead. We
-tested this modified {\it E}nKCF with another vision of the UAV123 that
-the original dataset was temporally down-sampled at $10$ fps and makes
-the challenging original dataset, because of objects in fast motion
-and large ego-motion, more challenging. This is because the magnitude
-of those motions is even bigger. Also, we can observe the sensitivity of 
-the state-of-the-art lower speed trackers to the video frame rate b
-y running them on this downsampled dataset. Figure \ref{fig:UAV123_10fpsDATASET}
-compares the performance of the modified version of {\it E}nKCF and
-other tracking methods. Our tracker outperforms other high-speed
-correlation filter based trackers including KCF, DSST by about
-$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
-the other hand, it does decent job in scale estimation. It ranks as
-fourth in AUC while running about 10 to 100 times faster than the top three trackers.
+to make a very fast and effective single target tracking available. We
+found that, with a slight modification, the proposed method can
+effectively handle large displacement of objects in successive frames
+due to object and camera motion. Specifically, we modified {\it E}nKCF
+by running $R_{t}^{L}$ every frame and remove the particle filter
+instead. We tested this modified {\it E}nKCF on the temporally
+downsampled version of the UAV123 dataset, called UAV123$\_$10fps
+dataset. The downsampling operation makes the already challenging
+original dataset, because of objects in fast motion and large
+ego-motion, more challenging. This is because the magnitude of those
+motions is even bigger. Also, we can measure the sensitivity of the
+state-of-the-art lower speed trackers to the smaller video frame
+rates.  Figure \ref{fig:UAV123_10fpsDATASET} compares the performance
+of the modified version of {\it E}nKCF and other tracking methods. Our
+tracker outperforms other high-speed correlation filter based trackers
+including KCF, DSST by about $15\%$-$20\%$ and showed a precision rate
+similar to that of SAMF. On the other hand, it does decent job in
+scale estimation. It ranks as fourth in AUC while running about $10$
+to $100$ times faster than the top three trackers.
 
-In the lower frame rate scenarios (10 fps), the ECO and CCOT's precision rates drop about
-$10\%$ worse than the original frame rate scenarios. We believe that this is an indicator of
-how good of a performance we can expect from these trackers on low-end hardware. The projected
-frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5 and $\simeq$0.3 by using our 
-convention described in section~\ref{introduction}. In this case, it would be reasonable to expect these
-trackers to perform drastically worse on such hardware whereas the {\it E}nKCF can still perform similarly
-due to its real-time speed on a low-end hardware. Our observations are also supported by \cite{mueller2017context}
-that evaluates the correlation filter-driven trackers at variable frame rates matching their operation rates.
+On the lower frame rate dataset ($10$ fps), the ECO and CCOT's
+precision rates drop about $10\%$ worse than the original dataset. We
+believe that this is an indicator of how good of a performance can be
+expected from these trackers on a limited hardware. The projected
+frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5
+and $\simeq$0.3 by using our convention described in
+section~\ref{introduction}. In this case, it would be reasonable to
+expect these trackers to perform drastically worse on such hardware
+whereas the {\it E}nKCF can still perform similarly due to its
+real-time speed on a low-end hardware. Our observations are also
+supported by \cite{mueller2017context} that evaluates the correlation
+filter-driven trackers at variable frame rates matching their
+operation rates.
 
@@
 and dynamic maneuvers of a target. The way we ran three KCFs is
-optimal in a sense that efficiently handled the scale change and
+optimal in a sense that it efficiently handled the scale change and
 effectively learned the translation of the target. We also developed a
-Bayes filter, particle filter, to smooth the transition between three
-KCFs. In particular, the particle filter estimated the target's pixel 
-coordinates using the evolution of the target's motion observed over frames.
+Bayes filter to smooth the transition between three KCFs, especially
+the transition between the scale and large ROI translation filter.
 Two public datasets were used to evaluate the performance of the
-proposed algorithm and it was found that, on average, the performance of the
-proposed algorithm is better than other high-speed trackers over 5\%
-on precision at 20 pixels and 10-20\% on AUC. Our
+proposed algorithm and it was found that, on average, the performance
+of the proposed algorithm is better than other high-speed trackers
+over 5\% on precision at 20 pixels and 10-20\% on AUC. Our
 implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
-DCF (457 fps) for UAV123. Finally, we encoded objects with deep
-features to boost tracking performance by $5\%$ on embedded systems
-with GPUs.
+data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps)
+for UAV123. Such operation rate tracker can potentially run at
+real-time on a low-end embedded system. Finally, we encoded objects
+with deep features to boost tracking performance by $5\%$ on embedded
+systems with GPUs.
 

### 2017-11-28 wacv_for_review.tex
More typos fixed, and grammar mistakes corrected

@@
 they attempted to update the scale of the target by further analyzing
-image, sub-regions in high confidence. Their method is based on an
+image sub-regions in high confidence. Their method is based on an
 assumption that the scale of a target would not change much over two
@@
 	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
-	Skip it for $R_{t}^{L}$ (Condition 2) and $R_{t}^{S}$ (Condition 3), $\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$\\
 	// \textit{Update Translation - Particle Filter}\\
@@
 $i$+$2$th and $i$+$3$th image frames, and then the scale filter,
-$R_{s}$ is applied to the $i$+$4$the image. This order repeats until
+$R_{s}$ is applied to the $i$+$4$th image. This order repeats until
 the last image is presented. Note that the translation filter,
@@
 \end{equation}
-where $\mathbf{y}$ represents the desired continuous response whereas $\mathbf{h}$ and
-$\mathbf{x_{c}}$ represents the learned correlation filter and training
-template for the given channel. The parameter $c$ enabled one to
-integrate features in multiple channels, such as HoG and color, in
-this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
-solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
+where we seek for $\mathbf{h}$ that minimizes $E$ given the desired 
+continuous response, $\mathbf{y}$, and the training template $\mathbf{x}$. 
+The parameter $c$ enables one to integrate features in the form of 
+multiple channels, such as HoG and color, in this setup \cite{henriques2015high,galoogahi2013multi}. 
+A closed-form solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
 closed-form solution, an element-wise multiplication in
-frequency domain was proposed for $\hat{w}$:
+frequency domain was proposed to learn the frequency domain correspondence of $\mathbf{h}$, $\mathbf{\hat{w}}$:
 \begin{equation}
@@
 \end{equation}
-A non-linear version of this closed-form solution is proposed to increase robustness
+A non-linear version of $\mathbf{\hat{w}}$, $\mathbf{\hat{\alpha}}$ , is proposed to increase robustness
 to any geometric and photometric variations
-\cite{henriques2015high}. In particular, the diagonalized Fourier
+\cite{henriques2015high}. In particular, the diagonalized non-linear Fourier
 domain dual form solution is expressed as
@@
 where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
- the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and it is expressed as
+ the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and is expressed as
 \begin{equation}
-\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'})))
+\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'}))).
 \label{eq:GaussianCorrelationSingleChannel}
@@
 An early version based on this formulation used grayscale feature
-($C=1$) to learn the solution vector $\mathbf{w}$ and multi-channel features
+($C=1$) to learn the solution vector $\mathbf{w}$ and integrating multi-channel features
 such as HoG and Color showed improved accuracy
 \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
-Specifically, one can execute an object detection task using this kernelized correlation
-filter with multi-channel features as
+In the detection phase,  the learned correlation filter is correlated with the first row of the gram matrix,
+$\mathbf{k^{xz^{'}}}$, which contains the similarity values between the learned feature template $\mathbf{x}$
+and the new test template $\mathbf{z}$. This can be formulated as
 \begin{equation}
@@
 first row of the kernel matrix.
+
+In practice, the solution vector, $\mathbf{\hat{\alpha}}$, and 
+the feature template matrix, $\mathbf{x}$, are accumulated over time
+to integrate temporal information as
+\begin{align}
+ \mathbf{\hat{\alpha}_{t}} =  (1 - \beta)  \mathbf{\hat{\alpha}_{t-1}} +  \beta \mathbf{\hat{\alpha}_{t}} \\
+  \mathbf{x_{t}} =  (1 - \beta)  \mathbf{x_{t-1}} + \beta  \mathbf{x_{t}}
+\end{align}
+
+where $\beta$ is the learning rate and mostly tuned to a small value.
 
@@
 Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
-and $30$ times faster.
+and $30$ times faster. We believe that there can be two reasons why {\it E}nKCF
+outperforms the DSST that updates the scale every frame searching over
+33 scale ratios. (1) The DSST uses a 1-D scale filter whereas ours applies a 2-D scale
+filter. This might reduce the spatial information learned in the scale filter. (2) The
+DSST scale filter originally employs only fHoG features whereas ours combines
+both fHoG and color-naming features.
 
@@
 On the lower frame rate dataset ($10$ fps), the ECO and CCOT's
-precision rates drop about $10\%$ worse than the original dataset. We
+precision rates drop about $10\%$ than the original dataset. We
 believe that this is an indicator of how good of a performance can be

### 2017-11-29 wacv_for_review.tex
Typos fixed

@@
 translation of the target and its background. Given this, another KCF
-is used to learn the target area to estimate a new scale of the
+is used to learn the target area to estimate the new scale of the
 target. However, because of running more than a KCF on each frame,
@@
 addition, to increase the flexibility of the proposed algorithm's
-usage, we explore deep features with varying levels of abstraction for
-the proposed {\it E}nKCF to improve performance.
+usage, we explore deep convolutional features with varying levels of abstraction to boost 
+tracking performance.
 
@@
 %---------------------------------------------------------------------- 
-We propose a novel way of utilizing a multiple of the KCFs
+We propose a novel way of utilizing an ensemble of the KCFs
 \cite{henriques2015high} to effectively handle scale variations and
@@
 KCFs in turn, instead of applying them on the same image frame
-together. Each of these KCFs is designed to address the challenge of
+together. Each of these KCFs is designed to address the challenges of
 single-target tracking -- variance in scale and translation. By
@@
 {\it E}nKCF to recover from potential drifts after a scale filter is
-applied to the input images. Whereas another translation filter with
-smaller padding size, $R_{t}^{S}$ will help {\it E}nKCF to better
+applied to the input images. On the other hand, another translation filter with
+smaller padding size, $R_{t}^{S}$, will help {\it E}nKCF to better
 localize the position of the target after a translation filter is
@@
 together to recover from any potential drifts -- drifts could happen
-only looking the target's scale by the filter, $R_{s}$.
+due to only scale filter operation in certain frames.
 
 In summary, the scale filter, $R_{s}$, is designed to directly handle
-the scale change of a target and provides other translation filters
-$R_{t}^{L}$ and $R_{t}^{S}$ with more focused ROIs about the target's
-translation. On the other hand, a translation filter, $R_{t}^{L}$, is
-designed to look at a larger search area to estimate the target's
-translation and recover from any potential drifts. Another translation
-filter, $R_{t}^{S}$, is designed to addresses the drawback of
-$R_{t}^{L}$ that it may learn noisy shape features due to its large
+the scale change of a target and provides the translation filters
+, $R_{t}^{L}$ and $R_{t}^{S}$, more accurate ROIs. On the other hand, 
+a translation filter, $R_{t}^{L}$, is designed to look at a larger search 
+area to estimate the target's translation and recover from any potential 
+drifts. Another translation filter, $R_{t}^{S}$, is designed to address the drawback of
+$R_{t}^{L}$ that it may learn noisy shape features due to its relatively larger
 search area. In what follows, we will detail the main idea behind the
@@
 
+\begin{comment}
 In practice, the solution vector, $\mathbf{\hat{\alpha}}$, and 
@@
 where $\beta$ is the learning rate and mostly tuned to a small value.
+\end{comment}
 
@@
 features. This setup of the {\it E}nKCF is designed to perform
-tracking on any embedded systems at $30$ fps, ones without GPUs.
+tracking at $30$ fps on low-end embedded systems without GPUs.
 \begin{figure}[!h]
@@
 We use both fHoG \cite{felzenszwalb2010object} and color-naming
-\cite{van2009learning} for the large area, translation filter,
+\cite{van2009learning} for the large area translation filter,
 $R_{t}^{L}$. This is because the fHoG applied to relatively larger
-area tends to be noisy and less discriminative and adding color
-information makes the feature vector for the translation filter,
-$R_{t}^{L}$, more robust to noise and more discriminative. Figure
-\ref{fig:Filters}(b) shows an example of this translation filter. But,
-this is not the case for the small area, translation filter,
-$R_{t}^{S}$, because it does not contain much of the background area
-around the target. For this reason, the $R_{t}^{S}$ only employs the
-fHoG features. Figure \ref{fig:Filters}(a) shows an example of this
+area tends to be noisier and less discriminative and adding color
+information makes the feature vector for the translation filter 
+more discriminative. Figure \ref{fig:Filters}(b) shows an example of 
+this translation filter. But, this is not the case for the small area 
+translation filter, $R_{t}^{S}$, because it contains relatively smaller background area. 
+For this reason, the $R_{t}^{S}$ only employs the fHoG features. 
+Figure \ref{fig:Filters}(a) shows an example of this
 translation filter. Lastly, we use both fHoG and color-naming features
@@
 \textbf{{\it E}nKCF with Deep Convolutional Features} In addition to
-hand-crafted features, we explore deep features to boost tracking
+hand-crafted features, we explore deep convolutional features to boost tracking
 performance. This version of {\it E}nKCF, Deep{\it E}nKCF is designed

### 2017-11-29 wacv_for_review.tex
Typos in Experiments Section Fixed

@@
 \end{comment}  
-As explained earlier, the {\it E}nKCF updates a target's translation
-at every other $k$ frames, particularly for estimating the target's
-scale. Although the strategy of updating every other $k$th frames will
-result in an optimal run-time performance, this may lead drifts at the
-later frames. To prevent such potential drifts, we developed a Bayes
+As explained earlier, the {\it E}nKCF updates the target's scale
+at every other $k$ frames. Although the strategy of updating every other 
+$k$th frames will result in an optimal run-time performance, this may lead 
+drifts at the later frames. To prevent such potential drifts, we developed a Bayes
 filter that incorporates a target's motion to smooth any intermediate
@@
 to estimate the target's image coordinate based on the {\it E}nKCF's
-outputs. The state in this paper, $\mathbf{x_t}$, represents the
-target's pixel coordinates and its velocity, $\mathbf{X_t} = \lbrace
+outputs. The state in this paper, $\mathbf{X_{t}}$, represents the
+target's pixel coordinates and its velocity, $\mathbf{X_{t}} = \lbrace
 x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
-coordinates of the target's centroid, $v_x$ and $v_y$ are the velocity
+coordinates of the target's centroid, $v_x$ and $v_y$ are the velocities
 estimated along the $x$-axis and $y$-axis. The particle filter
-predicts, using a constant velocity motion model, a target's next
+predicts, using a constant velocity motion model, the target's next
 state by generating a predefined number of particles. Then it uses the
-confidence maps of {\it E}nKCF as observation to update the state. The
-weight of a particle is computed as, $w_{p_{t}}(x_{t},y_{t}) =
+confidence maps of {\it E}nKCF as observation to update its state. The
+particle weight is computed as, $w_{p_{t}}(x_{t},y_{t}) =
 \sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
 $w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
-and $M$ denote the size of rows and columns of the confidence map.
+and $M$ denote the number of rows and columns of the confidence map.
 
@@
 %---------------------------------------------------------------------- 
-We evaluate the performance of the proposed algorithm {\it E}nKCF and
-its variants using the object tracking benchmark
+We evaluate the performance of the proposed {\it E}nKCF tracker and
+its variants on the object tracking benchmark
 datasets. Particularly, we choose two publicly available datasets:
@@
        ratio. The padding size for the correlation filters is tuned to
-       $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
+       $2$ for $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for
        $R_{s}$. For our particle filter implementation, we empirically
@@
 success rate to compare the performance of the proposed algorithm with
-those of the state-of-the-art, online algorithms for high and low
-speed tracking. For the precision, we rank the trackers based on the
-precision numbers at 20 pixels whereas in the success rate plots,
-trackers are ranked based on area under curve (AUC) scores. The
+those of the state-of-the-art high-speed and low-speed trackers. 
+For the precision, we rank the trackers based on the precision numbers 
+at 20 pixels whereas in the success rate plots, trackers are ranked based 
+on area under curve (AUC) scores. The
 tracking algorithms under the comparison include ones in high-speed
@@
 \cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
-relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, CCOT
+relatively lower-speed ($\leq$50): ECO \cite{DanelljanCVPR2017}, CCOT
 \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF

### 2017-11-30 wacv_for_review.tex
another stretch.

@@
 Computer vision technologies are very attractive for practical
-applications running on embedded systems. This is primarily because
-most of embedded systems come with an image acquisition pipeline, and
-a tremendous amount of progress on computer vision research has been
-made for the past few decades. However, to successfully deploy a
-computer vision algorithm on any existing embedded system, a vision
-algorithm needs to satisfy, at least, two criteria with the assumption
-of reasonably good performance: minimal, manual intervention after
-deployment and small footprint of consuming computational
-resources. To develop a single-target tracking algorithm that
-satisfies these criteria, we propose an ensemble of the kernelized
-correlation filters (KCF), we call it {\it E}nKCF. A committee of KCFs
-is specifically designed to address the scale-change and dynamic
-maneuver of the target over frames. In particular, to guarantee a
-high-speed run-time performance, we deploy each of KCFs in turn,
-instead of applying multiple KCFs to each frame. To minimize any
-potential drifts between individual KCFs' transition, we developed a
-Bayes filter. Experimental results showed that the performance of ours
-is, on average, 70.10\% for precision at 20 pixels, 53.00\% for
-success rate for OTB100 data, and 54.50\% and 40.2\% for UAV123
-data. The results showed that our method is better than other
+applications running on embedded systems. For such an application, it
+is desirable for the deployed algorithms to run in high-speed and
+require no offline training. To develop a single-target tracking
+algorithm with these properties, we propose an ensemble of the
+kernelized correlation filters (KCF), we call it {\it E}nKCF. A
+committee of KCFs is specifically designed to address the variations
+in scale and translation of moving objects. To guarantee a high-speed
+run-time performance, we deploy each of KCFs in turn, instead of
+applying multiple KCFs to each frame. To minimize any potential drifts
+between individual KCFs' transition, we developed a particle
+filter. Experimental results showed that the performance of ours is,
+on average, 70.10\% for precision at 20 pixels, 53.00\% for success
+rate for the OTB100 data, and 54.50\% and 40.2\% for the UAV123
+data. Experimental results showed that our method is better than other
 high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
-AUC on average. Moreover, our implementation ran at 340 fps for OTB100
-and at 416 fps for UAV123 dataset that is faster than DCF (292 fps)
-for OTB100 and KCF (292 fps) for UAV123. To increase flexibility of
-the proposed {\it E}nKCF running on various single-board computers,
-particularly ones with GPUs, we also explored different levels of deep
-convolutional features.
+AUC on average. Moreover, our implementation ran at 340 fps for the
+OTB100 and at 416 fps for the UAV123 dataset that is faster than DCF
+(292 fps) for the OTB100 and KCF (292 fps) for the UAV123. To increase
+flexibility of the proposed {\it E}nKCF running on various platforms,
+we also explored different levels of deep convolutional features.
 \end{abstract}
@@
 flew for video recording, an unmanned air vehicle (UAV) equipped with
-an object or feature following functionality would make it more useful
-in the application of monitoring/surveillance/surveying on private
+an object or feature following function would make it more useful for
+the application of monitoring/surveillance/surveying on private
 properties/wild-life/crop, video recording on sports/movies/events,
@@
 \includegraphics[width=\textwidth]{./figures/ResultsIntroduction.pdf}
-\caption{Examples of tracking results (yellow rectangles) by the
-  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
-  is challenging for object tracking as a target's scale is changed
-  drastically in a few frames.}
+\caption{Examples of some tracking results (yellow rectangles) by the
+  proposed method on the ``UAV123'' dataset. The ``UAV123'' dataset is
+  challenging for object tracking as the scale and translation of a
+  target can be drastically changed in a few frames.}
 \label{ResultsIntroduction}
@@
 In this paper, we propose a single-target tracking algorithm that does
-not require offline training and can run on any embedded or mobile
-platforms. Specifically, we would like to make our algorithm 1) learn
+not require offline training and can run in a
+high-speed. Specifically, we would like to have our algorithm 1) learn
 the appearance model of a target on the fly and 2) run as fast on a
-typical desktop as up to $300$-$450$ fps, aiming at running, at least,
-faster than 30 fps when it is deployed on a low-end, embedded
-system.\footnote{In general, it would not be easy to compare run-time
-  performance of a computer vision algorithm running on an Intel or
-  AMD desktop or a laptop and on that (e.g., ARM) of a single-board,
-  embedded system. This is primarily due to the difference in their
-  architectures and available computing resources. To derive these
-  numbers (``300'' and ``30'' fps), we assume that there is roughly an
-  1/10th scale down of computational resources from a typical PC to an
-  embedded system. We found such a scale-down in computation based on
-  exemplar processors, e.g., Intel's i7 quad-core vs ARMv8 dual-core.}
+typical desktop as up to $300$-$450$ fps.
 
@@
 \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
-these approaches will drastically reduce run-time performance because
-they are proposed to run multiple KCF on each frame.
+these approaches would drastically reduce run-time performance because
+multiple KCFs run on each frame.
 
@@
 to effectively address the changes in scale and translation of a
-target, the proposed algorithm deploys each of three, special-purpose
-KCFs in turn. Because of such a deployment strategy, the run-time
-performance of the proposed algorithm perserves high. To minimize any
-potential drifts while switching KCFs, we developed a Bayes filter. In
-addition, to increase the flexibility of the proposed algorithm's
-usage, we explore deep convolutional features with varying levels of abstraction to boost 
-tracking performance.
+target, we extended the KCF and deployed each of three KCFs in
+turn. Because of such a deployment strategy, the run-time performance
+of the proposed algorithm maintains high without sacrificing the
+accuracy of tracking. To minimize any potential drifts while switching
+KCFs, we developed a particle filter. In addition, to increase the
+flexibility of the proposed algorithm's usage, we explore deep
+convolutional features with varying levels of abstraction.
 
@@
 
-\begin{comment}
-Since Henriques and his colleagues' presented impressive tracking
-results of KCF \cite{henriques2015high} on VOT15
-challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
-variation of KCF were investigated. For example, \cite{ma2015long} and
-\cite{danelljan2014accurate} used a scale filter to learn the target
-area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
-used a correlation filter learned on the target area and its
-surrounding background in different size to learn the optimal scale of
-the target. Our approach is similar to that of \cite{ma2015long} in
-that more than one KCF is used to address the challenges of single
-target tracking. But ours is different from their approach because we
-do not use those multiple KCFs together at every frame, but
-alternatively at every $k$ frame. It intuitively makes sense to
-alternatively use multiple KCFs with different purposes because the
-appearance of a target does not change drastically over consecutive
-image frames. For most case, even it looks the appearance changes,
-learning a correlation filter over consecutive frames would not be
-much different from the one learned using the image few or $k$ frames
-later. Figure \ref{fig:Filters_Comparison} shows examples supporting
-this observation.
-\end{comment}
-
 \begin{figure*}[!h]
@@
 \includegraphics[width=1\textwidth]{./figures/LearnedFiltersComparison2.pdf}
-\caption{This figure shows that there is a marginal difference among
-  the scale filters learned either at every frame or at every 5
-  frames. The sub-figures at the the left show the scale filters
+\caption{These examples show that there is a marginal difference
+  between the scale filters learned at every frame and the one learned
+  at every 5 frames. The left, sub-figures show the scale filters
   trained at every frame and those at the right show the scale filters
@@
 In summary, the scale filter, $R_{s}$, is designed to directly handle
-the scale change of a target and provides the translation filters
-, $R_{t}^{L}$ and $R_{t}^{S}$, more accurate ROIs. On the other hand, 
-a translation filter, $R_{t}^{L}$, is designed to look at a larger search 
-area to estimate the target's translation and recover from any potential 
-drifts. Another translation filter, $R_{t}^{S}$, is designed to address the drawback of
-$R_{t}^{L}$ that it may learn noisy shape features due to its relatively larger
-search area. In what follows, we will detail the main idea behind the
-KCF.
+the scale change of a target and provides the translation filters,
+$R_{t}^{L}$ and $R_{t}^{S}$, with more accurate ROIs. On the other
+hand, a translation filter, $R_{t}^{L}$, is devised to look into a
+larger search area to estimate the target's translation and recover
+from any potential drifts. Another translation filter, $R_{t}^{S}$, is
+designed to address the drawback of $R_{t}^{L}$ that it may learn
+noisy shape features due to its relatively larger search area. In what
+follows, we will detail the main idea behind the KCF.
 
@@
 where we seek for $\mathbf{h}$ that minimizes $E$ given the desired
-continuous response, $\mathbf{y}$, and the training template $\mathbf{x}$. 
-The parameter $c$ enables one to integrate features in the form of 
-multiple channels, such as HoG and color, in this setup \cite{henriques2015high,galoogahi2013multi}. 
-A closed-form solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
-closed-form solution, an element-wise multiplication in
-frequency domain was proposed to learn the frequency domain correspondence of $\mathbf{h}$, $\mathbf{\hat{w}}$:
+continuous response, $\mathbf{y}$, and the training template
+$\mathbf{x}$.  The parameter $c$ enables one to integrate features in
+the form of multiple channels, such as HoG and color, in this setup
+\cite{henriques2015high,galoogahi2013multi}.  A closed-form solution
+for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
+closed-form solution, an element-wise multiplication in frequency
+domain was proposed to learn the frequency domain correspondence of
+$\mathbf{h}$, $\mathbf{\hat{w}}$:
 \begin{equation}
@@
 An early version based on this formulation used grayscale feature
-($C=1$) to learn the solution vector $\mathbf{w}$ and integrating multi-channel features
-such as HoG and Color showed improved accuracy
+($C=1$) to learn the solution vector $\mathbf{w}$ and integrating
+multi-channel features such as HoG and Color showed improved accuracy
 \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
-In the detection phase,  the learned correlation filter is correlated with the first row of the gram matrix,
-$\mathbf{k^{xz^{'}}}$, which contains the similarity values between the learned feature template $\mathbf{x}$
-and the new test template $\mathbf{z}$. This can be formulated as
+In the detection phase, the learned correlation filter is correlated
+with the first row of the gram matrix, $\mathbf{k^{xz^{'}}}$, which
+contains the similarity values between the learned feature template
+$\mathbf{x}$ and the new test template $\mathbf{z}$. This can be
+formulated as
 \begin{equation}
@@
 
-\begin{comment}
-In practice, the solution vector, $\mathbf{\hat{\alpha}}$, and 
-the feature template matrix, $\mathbf{x}$, are accumulated over time
-to integrate temporal information as
-\begin{align}
- \mathbf{\hat{\alpha}_{t}} =  (1 - \beta)  \mathbf{\hat{\alpha}_{t-1}} +  \beta \mathbf{\hat{\alpha}_{t}} \\
-  \mathbf{x_{t}} =  (1 - \beta)  \mathbf{x_{t-1}} + \beta  \mathbf{x_{t}}
-\end{align}
-
-where $\beta$ is the learning rate and mostly tuned to a small value.
-\end{comment}
-
 In the following sections, we will detail two different types of
-features used in {\it E}nKCF : (1) hand-crafted features (fHoG +
-color-naming) and (2) deep convolutional features.
+features used in {\it E}nKCF: hand-crafted features (fHoG +
+color-naming) and deep convolutional features.
 
@@
 $R_{t}^{L}$. This is because the fHoG applied to relatively larger
-area tends to be noisier and less discriminative and adding color
-information makes the feature vector for the translation filter 
-more discriminative. Figure \ref{fig:Filters}(b) shows an example of 
-this translation filter. But, this is not the case for the small area 
-translation filter, $R_{t}^{S}$, because it contains relatively smaller background area. 
-For this reason, the $R_{t}^{S}$ only employs the fHoG features. 
-Figure \ref{fig:Filters}(a) shows an example of this
-translation filter. Lastly, we use both fHoG and color-naming features
-again for the scale filter, $R_{s}$. By assigning fHoG and
-color-naming features, we ensure that the likelihood of inaccurate
-scale estimation is reduced in comparison to the scale filter with
-only fHoG features. This is more important in our case as the scale
-filter is operated in every 5 frames in the proposed tracker. Also,
-the scale filter, explained earlier in the algorithm \ref{alg:MKCF},
-estimates the scale of a target by correlating it with three candidate
+area tends to be more noisy and less discriminative, and adding color
+information makes the feature vector for the translation filter more
+discriminative. Figure \ref{fig:Filters}(b) shows an example of this
+translation filter. By contrast, the $R_{t}^{S}$ only employs the fHoG
+features because it covers a relatively smaller area.  Figure
+\ref{fig:Filters}(a) shows an example of this translation
+filter. Lastly, we use both fHoG and color-naming features again for
+the scale filter, $R_{s}$. By assigning fHoG and color-naming
+features, we ensure that the likelihood of inaccurate scale estimation
+is reduced in comparison to the scale filter with only fHoG
+features. This is more important in our case as the scale filter is
+operated in every 5 frames in the proposed tracker. Also, the scale
+filter, explained earlier in the algorithm \ref{alg:MKCF}, estimates
+the scale of a target by correlating it with three candidate
 ROIs. This search may increase the run-time complexity of the scale
@@
 \textbf{{\it E}nKCF with Deep Convolutional Features} In addition to
-hand-crafted features, we explore deep convolutional features to boost tracking
-performance. This version of {\it E}nKCF, Deep{\it E}nKCF is designed
-to make {\it E}nKCF run on high-end embedded systems with GPUs
-installed.
-\begin{comment}
-{\it Burak: Did EnKCF w/ deep features really
-  improve the performance -- the performance tested on the same data?
-  or did you just compare the performance numbers?}
-
-{\it YoungWoo :
-  EnkCF with deep features improved the performance on the same set of
-  data.}
-
-{\it Burak: If EnKCF w/ deep features improved the performance of
-  EnKCF on the same set of data, why didn't you plot their curves
-  together? And if this is true, we'll have to revise the abstract and
-  introduction as well!}
-
-  {\it YoungWoo : I compare the EnKCF with all the other trackers that does not use deep features. For this reason
-  it does not make sense to put DeepEnKCF in the same figure (Figure 6). We have a separate section 
-  showing how much improvement we get by using deep features and in this section I plot them in the same figure ( Figure (8) ).}
-
-{\it Burak: We can put these together if their performances from the
-  same data -- don't need to use the same features to be on the same
-  graph! We said EnKCF w/ deep features improved the performance, then
-  what's the point to separate them into two graphs?}
-
-{\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
-implementations, I thought it would be more clear to separate them, (2) I do not have 
-results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
-of this paper, showing them in the same figure with all the trackers might lead the authors to 
-underestimate EnKCF.
- }
-\end{comment}
+hand-crafted features, we explore deep convolutional features to
+extend the applicability of the {\it E}nKCF and boost tracking
+performance.
 
@@
 CNN features in tracking-by-detection algorithms. For example,
-\cite{danelljan2015convolutional} used the activations of the first
+\cite{danelljan2015convolutional} used the activation of the first
 and second convolutional layer of the VGGNet \cite{simonyan2014very}.
@@
 spatial information than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign
-the activations of the fourth convolutional layer features
+the activation of the fourth convolutional layer features
 ($26\times26\times128$) to $R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$
-are assigned the activations of the second layer features
+are assigned the activation of the second layer features
 ($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
@@
 \textit{conv224-VGG}. The conv222 setting stands for the assignment of
-the activations of $2^{th}$ convolutional layer features of VGGNet to
+the activation of $2^{th}$ convolutional layer features of VGGNet to
 $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it
@@
 
-\textbf{Particle Filter for Smoothing Transition among KCFs}
-\begin{comment}
-{\it Burak: Does what this section explains still hold good? If what
-  this section explains still makes sense, the translation filter,
-  $R_{t}^{L}$ doesn't do a good job. Isn't it? If it's not, revise
-  this section.}
-
-  {\it YoungWoo : I did not understand what $R_{t}^{L}$ has to do with 
-  particle filter}
-
-{\it Burak: Earlier we told the readers why we wanted to have two
-  translation filters: one for smaller region, $R_{t}^{S}$, and
-  another for larger region, $R_{t}^{L}$. The reason why we have two
-  translation filter, instead of one because we wanted to minimize any
-  drifts, yes? Read the line from 354 to 374. Then if we say again
-  here we have a particle filter for smoothing transition among KCFs,
-  they might think those two translation filters do not do their jobs
-  well?}
-
-{\it YoungWoo : Particle filter smoothen the translations in between the
-transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
-we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
-on the other hand aims at reducing the drifts and jumps further by bringing in the 
-motion information.}
-\end{comment}  
-As explained earlier, the {\it E}nKCF updates the target's scale
-at every other $k$ frames. Although the strategy of updating every other 
-$k$th frames will result in an optimal run-time performance, this may lead 
-drifts at the later frames. To prevent such potential drifts, we developed a Bayes
-filter that incorporates a target's motion to smooth any intermediate
-outputs from individual KCFs. In particular, we use a particle filter
-to estimate the target's image coordinate based on the {\it E}nKCF's
-outputs. The state in this paper, $\mathbf{X_{t}}$, represents the
-target's pixel coordinates and its velocity, $\mathbf{X_{t}} = \lbrace
-x, y, v_{x}, v_{y} \rbrace$, where $x$ and $y$ are the pixel
-coordinates of the target's centroid, $v_x$ and $v_y$ are the velocities
-estimated along the $x$-axis and $y$-axis. The particle filter
-predicts, using a constant velocity motion model, the target's next
-state by generating a predefined number of particles. Then it uses the
-confidence maps of {\it E}nKCF as observation to update its state. The
-particle weight is computed as, $w_{p_{t}}(x_{t},y_{t}) =
-\sum_{i=1}^{N}\sum_{j=1}^{M} \mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where
-$w_{p}$ denotes the weight of the particle $p$ at time $t$, and $N$
-and $M$ denote the number of rows and columns of the confidence map.
+\textbf{Particle Filter for Smoothing Transition among KCFs} As
+explained earlier, the {\it E}nKCF updates the target's scale at every
+other $k$ frames. Although the strategy of updating every other $k$th
+frames will result in an optimal run-time performance, this may lead
+drifts at the later frames. To prevent such potential drifts, we
+developed a Bayes filter that incorporates a target's motion to smooth
+any intermediate outputs from individual KCFs. In particular, we use a
+particle filter to estimate the target's image coordinate based on the
+{\it E}nKCF's outputs. The state in this paper, $\mathbf{X_{t}}$,
+represents the target's pixel coordinates and its velocity,
+$\mathbf{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$ and
+$y$ are the pixel coordinates of the target's centroid, $v_x$ and
+$v_y$ are the velocities estimated along the $x$-axis and
+$y$-axis. The particle filter predicts, using a constant velocity
+motion model, the target's next state by generating a predefined
+number of particles. Then it uses the confidence maps of {\it E}nKCF
+as observation to update its state. The particle weight is computed
+as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
+\mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ denotes the weight of
+the particle $p$ at time $t$, and $N$ and $M$ denote the number of
+rows and columns of the confidence map.
 
@@
 %----------------------------------------------------------------------
-We evaluate the performance of the proposed {\it E}nKCF tracker and
-its variants on the object tracking benchmark
-datasets. Particularly, we choose two publicly available datasets:
-OTB100\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
-and
-UAV123\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
-The OTB100 dataset is comprised of the videos of 100 objects whereas
-UAV123 dataset contains aerial footages of 123 objects.  We first test
-the {\it E}nKCF with two hand-crafted features, fHoG and color-naming.
-With this version, our goal is to have an object tracking algorithm
-that ``efficiently'' runs on an embedded system, a drone, in ``high
-speed,'' $\ge 30$ fps. Given this goal, we believe that the UAV123
-dataset is a good fit in evaluating the performance of the proposed
-algorithm. In addition, in the UAV123 dataset, there are many
-challenging, realistic scenes, e.g., abrupt scale/illumination
-changes. Although we are primarily interested in developing an
-algorithm for mobile, embedded robotic applications, it is also
-important to compare the performance of the proposed algorithm with
-those of the state-of-the-art in a nominal dataset. To this end, we
-chose the OTB100 dataset that contains the videos recorded from smart
-phones and typical cameras in perspective view. Also, we tested the
-proposed algorithm on a temporally down-sampled version of the UAV123
-dataset, called UAV123$\_$10fps dataset. What we would like to
-evaluate using this modified dataset is how robust the proposed
-algorithm is to the drastic motions of camera and targets. Finally, we
-evaluate the Deep{\it E}nKCF, {\it E}nKCF with deep convolutional
-features, on the UAV123 dataset to observe how much gain we can
-achieve over the hand-crafted features.
+So far we explained how the proposed algorithm could efficiently
+perform a single-target tracking while effectively addressing
+variations in scale and translation of moving objects. To accurately
+evaluate the performance of the proposed algorithm in terms of the
+goal of this paper, we need data with challenging variations in scale
+and translation. To this end, we chose the UAV123
+data\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}
+that contains 123 video sequences of moving objects captured from
+low-altitude UAVs. Because of the nature of the video acquisition --
+the targets and the camera are moving together, this data pose a great
+deal of challenges as the scale and position of the targets can be
+drastically changed in a few frames. To verify that our algorithm is
+useful not only for the image data with such extreme challenges but
+also for the one with nominal difficulties in single-object tracking,
+we also used the OTB100
+data\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
+that contains the videos recorded from smart phones and typical
+cameras in perspective view. In addition, we temporarily down-sampled
+the UAV123 data to check how robust our algorithm is to drastic
+motions of camera and moving targets. Lastly, we evaluate the proposed
+algorithm with deep convolutional features, on the UAV123 dataset to
+investigate how much performance gain we can achieve in using deep
+features over the conventional features like fHoG and color-naming.
 
@@
        individual KCFs should be different. We set the learning rates
-       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$
-       differently as $0.020$, $0.020$ and $0.010$. For the kernel of
-       the Gaussian neighboring function, we empirically found the
-       optimal values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for
-       $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter
-       update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
-       ratio. The padding size for the correlation filters is tuned to
-       $2$ for $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for
-       $R_{s}$. For our particle filter implementation, we empirically
-       set the number of particles to $1,000$ to balance the run-time
+       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as
+       $0.020$, $0.020$ and $0.010$. For the kernel of the Gaussian
+       neighboring function, we empirically found the optimal values
+       of $\alpha$ as $0.7$, $0.6$, and $0.9$ for $R_{t}^{L}$,
+       $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
+       threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR) ratio. The
+       padding size for the correlation filters is tuned to $2$ for
+       $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for $R_{s}$. For
+       our particle filter implementation, we empirically set the
+       number of particles to $1,000$ to balance the run-time
        performance and accuracy. To keep the level of variance among
@@
        when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
-       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower than a
-       pre-defined threshold.
+       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower
+       than a pre-defined threshold.
 
@@
 success rate to compare the performance of the proposed algorithm with
-those of the state-of-the-art high-speed and low-speed trackers. 
-For the precision, we rank the trackers based on the precision numbers 
-at 20 pixels whereas in the success rate plots, trackers are ranked based 
-on area under curve (AUC) scores. The
-tracking algorithms under the comparison include ones in high-speed
-($\geq$300 fps): KCF \cite{henriques2015high}, CSK
-\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
-\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
-relatively lower-speed ($\leq$50): ECO \cite{DanelljanCVPR2017}, CCOT
-\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
-\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
-\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
-\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
-CCOT trackers originally uses deep convolutional features, however,
-for the sake of fair comparison, we employ fHoG and color-naming
-features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
-the results on the UAV123 dataset. The {\it E}nKCF outperformed other
-high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
-algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
-accuracy, but 10-20 times slower. The more recent trackers, ECO and
-CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
-running at 10-15 times slower speed.  For the scale adaptation, {\it
-  E}nKCF did fourth best in terms of AUC for the success rate plot. It
+those of the state-of-the-art tracking algorithms. For the precision,
+we rank the trackers based on the precision numbers at 20 pixels
+whereas in the success rate plots, they are ranked based on area under
+curve (AUC) scores. The tracking algorithms under the comparison
+include ones in high-speed ($\geq$300 fps): KCF
+\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
+\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
+\cite{zhang2014fast} and ones in relatively lower-speed ($\leq$50):
+ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
+\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
+\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
+\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
+\cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
+convolutional features, however, for the fair comparison, we employ
+fHoG and color-naming features similar to our tracker. Figure
+\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
+    {\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
+    at 20 pixels precision. In particular, three algorithms, SAMF,
+    DSST, and Struck did about $5\%$ better than ours in accuracy, but
+    10-20 times slower. The more recent trackers, ECO and CCOT, on the
+    other hand, outperforms {\it E}nKCF by $15\%$ while running at
+    10-15 times slower. For the scale adaptation, {\it E}nKCF did
+    fourth best in terms of AUC for the success rate plot. It
     outperformed other high-speed trackers by about $20\%$-$25\%$ in
     AUC. In addition, it performed even better than some of the
-lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
-Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
-and $30$ times faster. We believe that there can be two reasons why {\it E}nKCF
-outperforms the DSST that updates the scale every frame searching over
-33 scale ratios. (1) The DSST uses a 1-D scale filter whereas ours applies a 2-D scale
-filter. This might reduce the spatial information learned in the scale filter. (2) The
-DSST scale filter originally employs only fHoG features whereas ours combines
-both fHoG and color-naming features.
+    lower-speed trackers.  For example, for AUC, {\it E}nKCF
+    outperformed Struck and DSST by $5\%$ and $10\%$ while running at
+    more than $10$ and $30$ times faster. It is somewhat obvious that
+    why the {\it E}nKCF outperformed the DSST because our scale filter
+    learned more information about the target because ours used a 2-D
+    filter, instead of a 1-D one and both fHoG and color-naming
+    features, instead of just fHoG.
 
@@
 \caption{Results of running different combinations of the KCFs for
-  UAV123 dataset.  The '$*$' represents
-  sequential approach where multiple KCFs are run in the given order in every frame as in LCT \cite{ma2015long}.}
+  UAV123 dataset. The '$*$' represents a sequential approach where
+  multiple KCFs are, in the given order, applied to every frame like
+  in LCT \cite{ma2015long}.}
 \label{table:Comparison_to_LCT}
@@
 \textbf{Finding Optimal Combination and Deployment Order of Multiple
-  KCFs} In addition to comparison with other trackers, we
+  KCFs} In addition to performance comparison with other trackers, we
 also conducted an experiment to see what combination and deployment
 order of the KCF work best. Table \ref{table:Comparison_to_LCT}
-presents results of this experiment. For this experiment, we did not
-use the particle filter to evaluate which order would work best
-without any extra components. The method at the $2^{nd}$ column
-flipped the order of deploying $R_{t}^{L}$ and $R_{t}^{S}$. The one at
-the $3^{th}$ column removed $R_{t}^{S}$ and replaces with $R_{t}^{L}$
-whereas the one at the $4^{th}$ column removes $R_{t}^{L}$. The
-methods marked with ``*'' ran the filters on every frame in the listed
-order. The trackers at the $7^{th}$ and $8^{th}$ columns ran a
-translation and a scale filter on every frame which is similar to
-the LCT tracker \cite{ma2015long}.\footnote{To be
-  precise, the LCT tracker comes with a re-detection module for a
-  long-term tracking.} In short, we empirically verified that
-\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
-tracking accuracy and run-time performance. For example, we could
-achieve $4.26\%$ higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
-at every frame, but this combination decreases run-time performance to
-317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every
-frame where $R_{t}^{S}$ uses the translation estimated by $R_{t}^{L}$
-to update translation and $R_{s}$ uses the final translation
-estimation given by $R_{t}^{S}$ to update the scale. Table
-\ref{table:Comparison_to_LCT} indeed showed that it is very useful to
-deploy more than one KCF as long as the deployment order is optimal.
+presents results of this experiment. For the fair comparison, we did
+not use the particle filter. The combination presented at the $2^{nd}$
+column switched the order of deploying $R_{t}^{L}$ and
+$R_{t}^{S}$. The one at the $3^{th}$ column removed $R_{t}^{S}$ and
+replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
+removes $R_{t}^{L}$. The combinations with the ``*'' marker ran the
+filters on every frame in the listed order. The trackers at the
+$7^{th}$ and $8^{th}$ columns ran a translation and a scale filter on
+every frame which is similar to the LCT tracker
+\cite{ma2015long}.\footnote{To be precise, the LCT tracker comes with
+  a re-detection module for a long-term tracking.} This experiment
+empirically verified that \textit{E}nKCF is an optimal way of using
+multiple KCFs, in terms of both tracking accuracy and run-time
+performance. For example, we could achieve $4.26\%$ higher in accuracy
+by running $R_{t}^{L}$ and $R_{S}$ at every frame, but this
+combination decreases run-time performance to 317 fps.
 
@@
 dataset, we also evaluated the performance of the {\it E}nKCF with and
-without the particle filter. In particular, we use 50 sequences
-labeled as no abrupt camera motion in the dataset. To evaluate the
-robustness of particle filter, we add noise, drawn from a uniform
-distribution ($[-20,20]$), to the translation estimations of the
-KCFs. In these setup, the {\it E}nKCF with particle filter achieves
-$51.98\%$ precision ($20$px), outperforming the one without particle
-filter {\it E}nKCF by $6.32\%$. Thus, with the removal of global
-camera motion, the integration of particle filter into the {\it E}nKCF
-as shown in Figure \ref{Workflows} further improved the results.
+without the particle filter. In particular, we use 50 video sequences
+with no drastic camera motion. To evaluate the robustness of particle
+filter, we add noise from a uniform distribution ($[-20,20]$), to the
+translation estimations of the KCFs. For this experiment, the {\it
+  E}nKCF with particle filter achieves $51.98\%$ precision ($20$px),
+outperforming the one without particle filter {\it E}nKCF by
+$6.32\%$. This experiment validated that the integration of particle
+filter into the {\it E}nKCF can further improve the performance.
 
 \textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
-shows the results on the OTB100 dataset. The relative performance of
-{\it E}nKCF is similar to the UAV123 dataset. In particular, it
-performed reasonably at approximating target scale.  It was the fifth
-best and the second fastest tracking algorithm. Among the other
-high-speed trackers, it delivers the highest precision and success
-rates. Interestingly, it outperformed another correlation filter based
-tracker, DSST, but performing $5\%$ behind of another low-speed scale
-adaptive SAMF tracker. Finally, the ECO, and CCOT achieve
-$15\%$-$20\%$ higher precision and success rates than ours while
-operating at 10-20 times slower rates.
+shows the results on the OTB100 dataset. The performance of {\it
+  E}nKCF on the OTB100 data is similar to that of the UAV123
+dataset. Specifically, it performed reasonably well at estimating
+target scale in that it showed the highest precision and success rates
+among the other high-speed trackers. Interestingly, it outperformed
+another correlation filter based tracker, DSST, but performing $5\%$
+behind of another low-speed scale adaptive SAMF tracker. Finally, the
+ECO, and CCOT achieve $15\%$-$20\%$ higher precision and success rates
+than ours while operating at 10-20 times slower rates.
 
-\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
-digression from the main idea -- the idea of deploying multiple KCFs
-to make a very fast and effective single target tracking available. We
-found that, with a slight modification, the proposed method can
-effectively handle large displacement of objects in successive frames
-due to object and camera motion. Specifically, we modified {\it E}nKCF
-by running $R_{t}^{L}$ every frame and remove the particle filter
-instead. We tested this modified {\it E}nKCF on the temporally
-downsampled version of the UAV123 dataset, called UAV123$\_$10fps
-dataset. The downsampling operation makes the already challenging
-original dataset, because of objects in fast motion and large
-ego-motion, more challenging. This is because the magnitude of those
-motions is even bigger. Also, we can measure the sensitivity of the
-state-of-the-art lower speed trackers to the smaller video frame
-rates.  Figure \ref{fig:UAV123_10fpsDATASET} compares the performance
-of the modified version of {\it E}nKCF and other tracking methods. Our
-tracker outperforms other high-speed correlation filter based trackers
+\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
+how the frame rate of a testing video would affect the performance of
+a tracking algorithm. To this end, we temporarily down-sampled the
+UAV123 called UAV123$\_$10fps dataset. We believe the downsampling
+would make the original UAV123 data more challenging because the
+displacements of the moving objects get even bigger. We also slightly
+modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
+removed the particle filter. Figure \ref{fig:UAV123_10fpsDATASET}
+shows the performance of the modified version of {\it E}nKCF and other
+tracking methods. The precision rates of the ECO and CCOT's dropped
+about $10\%$ from those with the original UAV123 dataset. Our tracker
+outperforms other high-speed correlation filter based trackers
 including KCF, DSST by about $15\%$-$20\%$ and showed a precision rate
-similar to that of SAMF. On the other hand, it does decent job in
-scale estimation. It ranks as fourth in AUC while running about $10$
-to $100$ times faster than the top three trackers.
-
-On the lower frame rate dataset ($10$ fps), the ECO and CCOT's
-precision rates drop about $10\%$ than the original dataset. We
-believe that this is an indicator of how good of a performance can be
-expected from these trackers on a limited hardware. The projected
-frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5
-and $\simeq$0.3 by using our convention described in
-section~\ref{introduction}. In this case, it would be reasonable to
-expect these trackers to perform drastically worse on such hardware
-whereas the {\it E}nKCF can still perform similarly due to its
-real-time speed on a low-end hardware. Our observations are also
-supported by \cite{mueller2017context} that evaluates the correlation
-filter-driven trackers at variable frame rates matching their
-operation rates.
+similar to that of SAMF. It ranks as fourth in AUC while running about
+$10$ to $100$ times faster than the top three trackers. It was
+interesting to observe how sensitive the frame rate is to the
+performance of the state-of-the-art tracking algorithms, and, with a
+slight modification, the proposed method effectively handled large
+displacement of objects in successive frames.
 
@@
 \caption{Comparison of a modified {\it E}nKCF's performance with those
-  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
-  dataset where the original UAV123 data was temporally downsampled.}
+  of the state-of-the-art tracking algorithms on a lower frame rate
+  data.}
 \label{fig:UAV123_10fpsDATASET}
@@
 
-\textbf{Evaluation with Deep Features} Our focus so far was to build a
-high speed tracker that can run at $30$fps on a single-board low-end 
-embedded system. To this end, we used two conventional features, fHoG and
-color-naming for the {\it E}nKCF. To further boost the tracking accuracy, we replace
-the conventional features with deep convolutional features similar to \cite{ma2015hierarchical,
-  danelljan2015convolutional}. However, this performance boost comes with the cost
-  of running the {\it E}nKCF on an embedded system with GPUs.
-\begin{comment}
-{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
-  Features.'' My edit stopped at the above paragraph because I got
-  confused. At least you'll have to explain the point of adding this
-  section.
+\textbf{Evaluation with Deep Features} Our focus so far was to develop
+a single-target tracker that does not require offline learning to
+effectively address the variations in scale and translation, and can
+run at a high-speed, $\ge 300$fps. We would like to see how much the
+performance gain we could achieve by replacing the conventional
+features, fHoG and color-naming with deep convolutional features. We
+use deep convolutional features similar to \cite{ma2015hierarchical,
+  danelljan2015convolutional}. Note that running the {\it E}nKCF with
+deep features would obviously increase the computational cost and
+degrade the run-time performance.
 
-  I don't know why Figure 7 is presented separately from Figure 5. If
-  you want to keep this way, you need, at least, to have their scales
-  same -- precision should have the same range, say 0.8 as the max
-  value.
-
-  YoungWoo : The point of adding this section is to evaluate the
-  same tracker with deep features (CNN) and see how much accuracy improvement
-  we get. However, I tried to highlight that, by employing deep features
-  the targeted embedded system changes from low-end (CPU-only) to 
-  higher-end system (GPUs). The two papers I cited employs the features
-  from the first several layers of the VGGNet. This is a common practice
-  in supporting the trackers with CNN features.
-
-  Burak: I'm not saying what you did -- use CNN features to feed an
-  online tracker. Yes, many people did such before. My worry is to
-  make our paper look a christmas tree -- a paper w/ too many stuffs
-  to evaluate under a certain theme. And, adding these new stuffs
-  along the way of preparing any submissions continuously asks us to
-  rewrite this paper from the top to all the way down. We need to
-  focus on a certain idea when to submit a paper to a
-  conference. Adding a bit more meats and stuffs to the main idea is
-  usually done in a journal paper.
-
-  If I add this to figure 5, it does not make sense, because all the
-  trackers we compare, use hand-crafted features and run on CPU. For
-  this reason, I wanted to compare EnKCF with deep features
-  (higher-end system) and hand-crafted features (low-end system).
-
-  Burak: Given what we agreed upon what you did, I think you can still
-  put them together in that we're comparing different versions of
-  apples, not orange, under the same criterion. Think about it.
-
-  The figure 7(a) and figure 5 have almost the same range (0,73 and 0.70)
-  I will update the figure 5 to have 0.73 range as well. I test the EnKCF
-  with CNN features only on the UAV123 dataset.
-
-  Burak: We don't expect the reviewers or readers to exactly see what
-  we saw here. Keep their scales same -- whatever maximum value you
-  choose for the y-axis for one graph, use the same scale to all other
-  same graphs.}
-\end{comment}
-
-Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows the DeepE{\it n}KCF's
-performance on UAV123 dataset. Deep{\it E}nKCF outperformed the {\it
-  E}nKCF with hand-crafted features by about $3\%$ to $5\%$ in
+Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows the DeepE{\it
+  n}KCF's performance on UAV123 dataset. Deep{\it E}nKCF outperformed
+the {\it E}nKCF with hand-crafted features by about $3\%$ to $5\%$ in
 precision (20 px) and $2\%$ in success rates (AUC). The
@@
 challenging cases such as low contrast ROIs. However, we believe that
-the contribution of the deep features is limited by two factors: (1)
-increased translational invariance in deeper layers and (2) lost targets due to
-large target and camera motion in the UAV123 dataset.
+the contribution of the deep features is limited by two factors:
+increased translational invariance in deeper layers and losing targets
+due to large target and camera motion in the UAV123 dataset.
 
-\begin{comment}
-{\it Burak: You'll have to explain 1) why, you think, DeepEnKCF worked better, 2) 
-why DeepEnKCF didn't perform a way better than EnKCF, 3) why did conv224-VGG perform better than conv222-VGG.}
-\end{comment}
 \begin{figure}[!h]
@@
 
-%\begin{figure}[!h]
-%\centering
-%\begin{tabular}{ccc}
-%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
-%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
-%\end{tabular}
-%\caption{Comparison of {\it E}nKCF's performance with those of the
-%  state-of-the-art tracking algorithms on the OTB100 dataset.}
-%\label{fig:OTB100_DATASET}
-%\end{figure}
-
-%\begin{table}
-%\smaller
-%\begin{center}
-%\begin{tabular*}{\textwidth}{|l|c|c|c|c|c|c|c|c|}
-%\hline
-% & $R_{t}^{L}$+$R_{t}^{S}$+$R_{s}$ ({\it E}nKCF) & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$ & $R_{t}^{S}$ & LCT  $R_{t}^{S}$+$R_{s}$ & LCT  $R_{t}^{L}$+$R_{s}$ & LCT  $R_{t}^{L}+R_{t}^{S}$+$R_{s}$\\
-%\hline\hline
-%Pr. ($20$px) & \textbf{53.9} & 48.09 & 52.50 & 51.88 & 51.29 & 52.14 & &  \\
-%SR ($50\%$) & \textbf{40.2} & 36.04 & 37.85 & 35.12 & 34.42 & 38.51 & & \\
-%FPS & 416 & 370 & 425 & 367 & \textbf{490} & 151 & & \\
-%\hline
-%\end{tabular*}
-%\end{center}
-%\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset.
-We decouple the re-detection module of the LCT tracker as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF.
-$R_{t}^{S}$ and $R_{s}$ are used as proposed in
-%\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used to perform realistic comparison.
-In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).}
-%\end{table}
-
 %---------------------------------------------------------------------- 
@@
 for real-world applications is economically and practically very
-attractive. To make such pipelines more plausible, however, those
-algorithms should run faster with small footprint of computation
-resource consumption. To make an object tracking algorithm meet these
-practical requirements, we proposed an extension of KCF that
-essentially deploys three KCFs, in turn, to address the scale change
-and dynamic maneuvers of a target. The way we ran three KCFs is
-optimal in a sense that it efficiently handled the scale change and
-effectively learned the translation of the target. We also developed a
-Bayes filter to smooth the transition between three KCFs, especially
-the transition between the scale and large ROI translation filter.
-Two public datasets were used to evaluate the performance of the
-proposed algorithm and it was found that, on average, the performance
-of the proposed algorithm is better than other high-speed trackers
-over 5\% on precision at 20 pixels and 10-20\% on AUC. Our
-implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
-data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps)
-for UAV123. Such operation rate tracker can potentially run at
-real-time on a low-end embedded system. Finally, we encoded objects
-with deep features to boost tracking performance by $5\%$ on embedded
-systems with GPUs.
+attractive. Among other practical considerations, it would be
+desirable if such computer vision algorithms require no offline
+training and execute in high-speed. To develop a single-target
+tracking algorithm to meet these properties, we proposed an extension
+of KCF that applies three KCFs, in turn, to address the variations in
+scale and translation of moving objects. We also developed a particle
+filter to smooth the transition between three KCFs, especially the
+transition between the scale and large ROI translation filter. Through
+experiments, we found that the way the {\it E}nKCF deployed three KCFs
+was optimal and the particle filter contributed to boost the
+performance. We used two public datasets to evaluate the performance
+of the proposed algorithm and other state-of-the-art tracking
+algorithms, and found that, on average, the performance of the
+proposed algorithm is better than other high-speed trackers over 5\%
+on precision at 20 pixels and 10-20\% on AUC. Our implementation ran
+at 340 fps for OTB100 and at 416 fps for UAV123 data that is faster
+than DCF (292 fps) for OTB100 and KCF (292 fps) for UAV123. Finally,
+we explored the idea of utilizing deep features for the proposed
+algorithm and found that the deep features helped the proposed
+algorithm improve the performance by $5\%$.
 
-As future work, we investigate a way of re-initializing a target when
-the target is lost, due to occlusion, illumination change, drastic
-camera motion, etc.
+As future work, we would like to investigate a way of re-initializing
+a target when the target is lost, due to occlusion, illumination
+change, drastic camera motion, etc.
 

### 2017-12-01 wacv_for_review.tex
Some Comments Added

@@
 In this paper, we propose a single-target tracking algorithm that does
-not require offline training and can run in a
-high-speed. Specifically, we would like to have our algorithm 1) learn
-the appearance model of a target on the fly and 2) run as fast on a
-typical desktop as up to $300$-$450$ fps.
+not require offline training and can run in high-speed. Specifically, 
+we would like to have our algorithm 1) learn
+the appearance model of a target on the fly and 2) run on a
+typical desktop as fast as $300$-$450$ fps.
 
@@
 regression problem, a set of negative examples is collected around the
-initial, target bounding box and represented as a form of the
+initial target bounding box and represented as a form of the
 circulant matrix \cite{henriques2015high}. One can optimally solve
@@
 image sub-regions in high confidence. Their method is based on an
-assumption that the scale of a target would not change much over two
+assumption that the scale of a target would not change drastically over two
 consecutive frames. Similarly, Ma and his colleagues used two KCFs to
@@
 ($R_{t}^{L}$). By doing so, our method aims at addressing scale
-change and estimate target's motion efficiently while maintaining or
+change and estimating target's motion efficiently while maintaining or
 increasing run-time performance. Figure \ref{Workflows} illustrates
@@
 accuracy of tracking. To minimize any potential drifts while switching
-KCFs, we developed a particle filter. In addition, to increase the
+KCFs, we developed a particle filter. Additionally, to increase the
 flexibility of the proposed algorithm's usage, we explore deep
@@
 filter, $R_{t}^{L}$, is applied to the $i$th and $i$+$1$th image
-frames, another translation filter, $R_{t}^{S}$ is applied to the
+frames, another translation filter, $R_{t}^{S}$, is applied to the
 $i$+$2$th and $i$+$3$th image frames, and then the scale filter,
-$R_{s}$ is applied to the $i$+$4$th image. This order repeats until
+$R_{s}$, is applied to the $i$+$4$th image. This order repeats until
 the last image is presented. Note that the translation filter,
@@
 filter from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$. To
-ensure actual filtering operations practical, we use a smaller
+ensure practical actual filtering operations, we use a smaller
 template size (i.e., 64$\times n$) for the scale filter, $R_{s}$. The
@@
 So far we explained how the proposed algorithm could efficiently
-perform a single-target tracking while effectively addressing
+perform a single-target tracking task while effectively addressing
 variations in scale and translation of moving objects. To accurately
@@
 \textbf{Performance on UAV123 Dataset} We used the precision and
-success rate to compare the performance of the proposed algorithm with
+success rates to compare the performance of the proposed algorithm with
 those of the state-of-the-art tracking algorithms. For the precision,
 we rank the trackers based on the precision numbers at 20 pixels
-whereas in the success rate plots, they are ranked based on area under
+whereas in the success rate plots, they are ranked based on the area under
 curve (AUC) scores. The tracking algorithms under the comparison
@@
 \cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
-convolutional features, however, for the fair comparison, we employ
+convolutional features, however, to perform fair comparison, we employ
 fHoG and color-naming features similar to our tracker. Figure
@@
 outperformed Struck and DSST by $5\%$ and $10\%$ while running at
-    more than $10$ and $30$ times faster. It is somewhat obvious that
-    why the {\it E}nKCF outperformed the DSST because our scale filter
-    learned more information about the target because ours used a 2-D
-    filter, instead of a 1-D one and both fHoG and color-naming
-    features, instead of just fHoG.
+more than $10$ and $30$ times faster. 
+\textit{YoungWoo : Does the following part make sense to you?}
+The DSST assigns a 1-D scale filter and searches over 33 candidates in the scale pool whereas the {\it E}nKCF
+uses a 2-D scale filter and 3 candidates. Although the DSST searches for the scale in a larger search space, the {\it E}nKCF
+achieves higher AUC. We believe this can be due to two reasons. First, the DSST's 1-D scale filter lacks spatial information about
+the target. Second, the DSST scale filter employs only fHoG whereas the {\it E}nKCF uses both color-naming and fHoG features
+in the scale filter.
 
@@
 how the frame rate of a testing video would affect the performance of
-a tracking algorithm. To this end, we temporarily down-sampled the
-UAV123 called UAV123$\_$10fps dataset. We believe the downsampling
+a tracking algorithm. To this end, we use the temporarily down-sampled version
+of the UAV123, called UAV123$\_$10fps dataset. We believe the downsampling
 would make the original UAV123 data more challenging because the
-displacements of the moving objects get even bigger. We also slightly
-modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
+displacements of the moving objects become even bigger. To tackle this challenge, w
+e slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
 removed the particle filter. Figure \ref{fig:UAV123_10fpsDATASET}
 shows the performance of the modified version of {\it E}nKCF and other
-tracking methods. The precision rates of the ECO and CCOT's dropped
-about $10\%$ from those with the original UAV123 dataset. Our tracker
+tracking methods. The precision rates of the ECO and CCOT dropped
+about $10\%$ in comparison to the original UAV123 dataset. Our tracker
 outperforms other high-speed correlation filter based trackers
@@
 similar to that of SAMF. It ranks as fourth in AUC while running about
-$10$ to $100$ times faster than the top three trackers. It was
-interesting to observe how sensitive the frame rate is to the
+$10$ to $100$ times faster than the top three trackers. 
+\textit{YoungWoo : I did not get this part clearly. How sensitive the frame rate 
+or how sensitive the tracker is
+?} It was interesting to observe how sensitive the frame rate is to the
 performance of the state-of-the-art tracking algorithms, and, with a
@@
 desirable if such computer vision algorithms require no offline
-training and execute in high-speed. To develop a single-target
-tracking algorithm to meet these properties, we proposed an extension
+training and operate at high-speed. To develop a single-target
+tracking algorithm to meet these features, we proposed an extension
 of KCF that applies three KCFs, in turn, to address the variations in
@@
 transition between the scale and large ROI translation filter. Through
-experiments, we found that the way the {\it E}nKCF deployed three KCFs
+experiments, it was found that the way the {\it E}nKCF deployed three KCFs
 was optimal and the particle filter contributed to boost the
-performance. We used two public datasets to evaluate the performance
+performance in the existence of noise. 
+We used two public datasets to evaluate the performance
 of the proposed algorithm and other state-of-the-art tracking
@@
 algorithm and found that the deep features helped the proposed
-algorithm improve the performance by $5\%$.
+algorithm boost the performance by $10\%$.
 

### 2017-12-01 wacv_for_review.tex
Some Comments Added

@@
 order of the KCF work best. Table \ref{table:Comparison_to_LCT}
-presents results of this experiment. For the fair comparison, we did
+presents results of this experiment. To achieve fair comparison, we did
 not use the particle filter. The combination presented at the $2^{nd}$
@@
 multiple KCFs, in terms of both tracking accuracy and run-time
-performance. For example, we could achieve $4.26\%$ higher in accuracy
+performance. For example, one could achieve $4.26\%$ higher in accuracy
 by running $R_{t}^{L}$ and $R_{S}$ at every frame, but this
@@
 would make the original UAV123 data more challenging because the
-displacements of the moving objects become even bigger. To tackle this challenge, w
-e slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
-removed the particle filter. Figure \ref{fig:UAV123_10fpsDATASET}
+displacements of the moving objects become even bigger. To tackle this challenge, we 
+slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
+removed the particle filter due to larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET}
 shows the performance of the modified version of {\it E}nKCF and other
@@
 displacement of objects in successive frames. 
+\textit{YoungWoo : I also believe that we should emphasize how the state-of-the-art
+trackers perform in lower frame rates. And I believe this is what this paper \cite{mueller2017context}
+says. They rank the trackers by evaluating them on videos matching their fps. I was thinking of running 
+ECO and CCOT in UAV123 in 5 fps videos and mention how they degrade with respect to the decreasing fps.
+I believe this is our contribution and we should emphasize it.}
 
@@
 \end{tabular}
-\caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming}) performance with Deep{\it E}nKCF on the UAV123
+\caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming}) 
+performance with Deep{\it E}nKCF on the UAV123
 dataset.}

### 2017-12-01 wacv_for_review.tex
last stretch.

@@
 properties/wild-life/crop, video recording on sports/movies/events,
-many others.
+many others. To this end, in this paper, we propose a single-target
+tracking algorithm that does not require offline training and can run
+in high-speed. Specifically, we would like to have our algorithm 1)
+learn the appearance model of a target on the fly and 2) run on a
+typical desktop as fast as $300$-$450$ fps.
 
@@
 \end{figure*}
-
-In this paper, we propose a single-target tracking algorithm that does
-not require offline training and can run in high-speed. Specifically, 
-we would like to have our algorithm 1) learn
-the appearance model of a target on the fly and 2) run on a
-typical desktop as fast as $300$-$450$ fps.
 
@@
 regression problem, a set of negative examples is collected around the
-initial target bounding box and represented as a form of the
-circulant matrix \cite{henriques2015high}. One can optimally solve
-this regression problem using a ridge regression in a closed
-form. However, this solution has to deal with expensive matrix
-operations $\mathcal{O}(n^{3})$. The correlation filter offers a less
-complex solution, $\mathcal{O}(n\log n)$ over element-wise
-multiplication in a frequency domain
-\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
-an object tracking pipeline based on the correlation filter can run
-very efficiently and be even easily implemented. In fact, an extension
-of a linear correlation filter, the kernelized correlation filter with
-multi-channel features \cite{henriques2015high} showed impressive
-object tracking results and outperformed other state-of-the-art,
-online tracking algorithms in terms of run-time and tracking
-accuracy. However, a vanilla form of such an online tracker is prone
-to drift, and fails to track a target over a long period of time
-\cite{henriques2015high}. This is primarily due to the dilemma of
-stability-plasticity in updating appearance model, where the
-appearance model will be overfitted to only the images used to train,
-unless a compromise on the frequency of updating the model is
-carefully implemented \cite{santner2010prost}. For example, one may
-handle a target's scale variation by just concatenating multiple
-correlation filters including KCF and running them on each
-frame. Alternatively one could think of scanning the region of
-interest (ROI) with a list of templates in predefined scale ratios to
-find the target in appropriate scale
+initial target bounding box and represented as a form of the circulant
+matrix \cite{henriques2015high}. One can optimally solve this
+regression problem using a ridge regression in a closed form. However,
+this solution has to deal with expensive matrix operations
+$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
+solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
+frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
+this reformulation, an object tracking pipeline based on the
+correlation filter can run very efficiently and be even easily
+implemented. In fact, an extension of a linear correlation filter, the
+kernelized correlation filter with multi-channel features
+\cite{henriques2015high} showed impressive object tracking results and
+outperformed other state-of-the-art, online tracking algorithms in
+terms of run-time and tracking accuracy. However, a vanilla form of
+such an online tracker is prone to drift, and fails to track a target
+over a long period of time \cite{henriques2015high}. This is primarily
+due to the dilemma of stability-plasticity in updating appearance
+model, where the appearance model will be overfitted to only the
+images used to train, unless a compromise on the frequency of updating
+the model is carefully implemented \cite{santner2010prost}. For
+example, one may handle a target's scale variation by just
+concatenating multiple correlation filters including KCF and running
+them on each frame. Alternatively one could think of scanning the
+region of interest (ROI) with a list of templates in predefined scale
+ratios to find the target in appropriate scale
 \cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
@@
 \textbf{Performance on UAV123 Dataset} We used the precision and
-success rates to compare the performance of the proposed algorithm with
-those of the state-of-the-art tracking algorithms. For the precision,
-we rank the trackers based on the precision numbers at 20 pixels
-whereas in the success rate plots, they are ranked based on the area under
-curve (AUC) scores. The tracking algorithms under the comparison
-include ones in high-speed ($\geq$300 fps): KCF
+success rates to compare the performance of the proposed algorithm
+with those of the state-of-the-art tracking algorithms. For the
+precision, we rank the trackers based on the precision numbers at 20
+pixels whereas in the success rate plots, they are ranked based on the
+area under curve (AUC) scores. The tracking algorithms under the
+comparison include ones in high-speed ($\geq$300 fps): KCF
 \cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
@@
     outperformed Struck and DSST by $5\%$ and $10\%$ while running at
-more than $10$ and $30$ times faster. 
-\textit{YoungWoo : Does the following part make sense to you?}
-The DSST assigns a 1-D scale filter and searches over 33 candidates in the scale pool whereas the {\it E}nKCF
-uses a 2-D scale filter and 3 candidates. Although the DSST searches for the scale in a larger search space, the {\it E}nKCF
-achieves higher AUC. We believe this can be due to two reasons. First, the DSST's 1-D scale filter lacks spatial information about
-the target. Second, the DSST scale filter employs only fHoG whereas the {\it E}nKCF uses both color-naming and fHoG features
-in the scale filter.
+    more than $10$ and $30$ times faster. For the DSST, we believe our
+    algorithm outperformed it because, first of all, the DSST uses a
+    1-D scale filter and searches the target's scale over 33
+    candidates in a scale pool whereas our algorithm uses a 2-D scale
+    filter with 3 candidate scales. Learning a 2-D filter would result
+    in learning more spatial information. Second of all, the DSST use
+    only fHoG whereas our algorithm uses both fHoG and color-naming
+    features. Learning more features, not for always, but would
+    provide better understanding on the ROI.
 
@@
 how the frame rate of a testing video would affect the performance of
-a tracking algorithm. To this end, we use the temporarily down-sampled version
-of the UAV123, called UAV123$\_$10fps dataset. We believe the downsampling
-would make the original UAV123 data more challenging because the
-displacements of the moving objects become even bigger. To tackle this challenge, we 
-slightly modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
-removed the particle filter due to larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET}
-shows the performance of the modified version of {\it E}nKCF and other
-tracking methods. The precision rates of the ECO and CCOT dropped
-about $10\%$ in comparison to the original UAV123 dataset. Our tracker
-outperforms other high-speed correlation filter based trackers
-including KCF, DSST by about $15\%$-$20\%$ and showed a precision rate
-similar to that of SAMF. It ranks as fourth in AUC while running about
-$10$ to $100$ times faster than the top three trackers. 
-\textit{YoungWoo : I did not get this part clearly. How sensitive the frame rate 
-or how sensitive the tracker is
-?} It was interesting to observe how sensitive the frame rate is to the
-performance of the state-of-the-art tracking algorithms, and, with a
-slight modification, the proposed method effectively handled large
-displacement of objects in successive frames. 
-\textit{YoungWoo : I also believe that we should emphasize how the state-of-the-art
-trackers perform in lower frame rates. And I believe this is what this paper \cite{mueller2017context}
-says. They rank the trackers by evaluating them on videos matching their fps. I was thinking of running 
-ECO and CCOT in UAV123 in 5 fps videos and mention how they degrade with respect to the decreasing fps.
-I believe this is our contribution and we should emphasize it.}
+a tracking algorithm. To this end, we use the temporarily down-sampled
+version of the UAV123, called UAV123$\_$10fps dataset. We believe the
+downsampling would make the original UAV123 data more challenging
+because the displacements of the moving objects become even bigger. To
+tackle this challenge, we slightly modified the proposed algorithm --
+ran $R_{t}^{L}$ every frame and removed the particle filter due to
+larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET} shows the
+performance of the modified version of {\it E}nKCF and other tracking
+methods. The precision rates of the ECO and CCOT dropped about $10\%$
+in comparison to the original UAV123 dataset. Our tracker outperforms
+other high-speed correlation filter based trackers including KCF, DSST
+by about $15\%$-$20\%$ and showed a precision rate similar to that of
+SAMF. It ranks as fourth in AUC while running about $10$ to $100$
+times faster than the top three trackers. It was interesting to
+observe how sensitive the performance of the state-of-the-art tracking
+algorithms is the frame rate, and, with a slight modification, the
+proposed method effectively handled large displacement of objects in
+successive frames.
+\begin{comment}
+\textit{YoungWoo : I also believe that we should
+  emphasize how the state-of-the-art trackers perform in lower frame
+  rates. And I believe this is what this paper
+  \cite{mueller2017context} says. They rank the trackers by evaluating
+  them on videos matching their fps. I was thinking of running ECO and
+  CCOT in UAV123 in 5 fps videos and mention how they degrade with
+  respect to the decreasing fps.  I believe this is our contribution
+  and we should emphasize it.
 
+  Burak: To be honest with you, it's a cheating -- we modified our
+  algorithm to make it work better, but didn't do anything or
+  modifications to other algorithms. Yes, all other algorithms didn't
+  perform well on a low frame rate, but it was a unfair comparison. So
+  I wouldn't think it's a contribution.  }
+\end{comment}
 \begin{figure}[!h]
@@
 training and operate at high-speed. To develop a single-target
-tracking algorithm to meet these features, we proposed an extension
-of KCF that applies three KCFs, in turn, to address the variations in
+tracking algorithm to meet these features, we proposed an extension of
+KCF that applies three KCFs, in turn, to address the variations in
 scale and translation of moving objects. We also developed a particle
@@
 transition between the scale and large ROI translation filter. Through
-experiments, it was found that the way the {\it E}nKCF deployed three KCFs
-was optimal and the particle filter contributed to boost the
-performance in the existence of noise. 
-We used two public datasets to evaluate the performance
+experiments, we found that the way the {\it E}nKCF deployed three KCFs
+was optimal, and the particle filter contributed to increase the
+performance.  We used two public datasets to evaluate the performance
 of the proposed algorithm and other state-of-the-art tracking
@@
 
-As future work, we would like to investigate a way of re-initializing
-a target when the target is lost, due to occlusion, illumination
-change, drastic camera motion, etc.
+Although the proposed algorithm showed a promising result tested with
+challenging data, we believe the corner case analysis has not been
+extensively done yet. As future work, we would like to thoroughly
+study when and what conditions our algorithm would fail to track
+moving objects. In addition, we also would like to investigate a way
+of re-initializing a target when the target is lost, due to occlusion,
+illumination change, drastic camera motion, etc.
 

### 2017-12-01 wacv_for_review.tex
Last Stretch comments added

@@
 these approaches would drastically reduce run-time performance because
-multiple KCFs run on each frame.
+multiple KCFs run on each frame. \textit{YoungWoo : due to operation of multiple KCFs on each frame?}
 
@@
 itself to estimate the right scale of the target. In particular, a
-transition filter with larger padding size, $R_{t}^{L}$ will enable
-{\it E}nKCF to recover from potential drifts after a scale filter is
+transition filter with larger padding size, $R_{t}^{L}$ \textit{YoungWoo : , $R_{t}^{L}$, ?} 
+will enable {\it E}nKCF to recover from potential drifts after a scale filter is
 applied to the input images. On the other hand, another translation filter with
@@
 that contains 123 video sequences of moving objects captured from
-low-altitude UAVs. Because of the nature of the video acquisition --
+low-altitude UAVs. \textit{YoungWoo: It felt confusing to me} Because of the nature of the video acquisition --
 the targets and the camera are moving together, this data pose a great
@@
 that contains the videos recorded from smart phones and typical
-cameras in perspective view. In addition, we temporarily down-sampled
+cameras in perspective view. \textit{YoungWoo : We did not downsample it, they provide both
+UAV123 and UAV123$\_$1Ofps.} In addition, we temporarily down-sampled
 the UAV123 data to check how robust our algorithm is to drastic
@@
     only fHoG whereas our algorithm uses both fHoG and color-naming
-    features. Learning more features, not for always, but would
+    features. \textit{YoungWoo : The following sentence is confusing to me.} Learning more features, not for always, but would
     provide better understanding on the ROI.
@@
   E}nKCF with particle filter achieves $51.98\%$ precision ($20$px),
-outperforming the one without particle filter {\it E}nKCF by
+outperforming the one \textit{YoungWoo: without particle filter EnKCF or the one without particle filter?} without particle filter {\it E}nKCF by
 $6.32\%$. This experiment validated that the integration of particle
@@
 observe how sensitive the performance of the state-of-the-art tracking
-algorithms is the frame rate, and, with a slight modification, the
+algorithms is to the frame rate, and, with a slight modification, the
 proposed method effectively handled large displacement of objects in
@@
 
+\textit{YoungWoo : I do not agree with this part. In terms of the future work, maybe,
+ we can say we will more extensively test our algorithm on an embedded system and try
+ to improve the accuracy by adaptively finding out when to apply the scale filter to reduce the drifts further. }
 Although the proposed algorithm showed a promising result tested with

### 2017-12-02 wacv_for_review.tex
Last Stretch comments added
last.

--- 2017-12-01 wacv_for_review.tex
@@
 {\it E}nKCF to recover from potential drifts after a scale filter is
-applied to the input images. On the other hand, another translation filter with
-smaller padding size, $R_{t}^{S}$, will help {\it E}nKCF to better
-localize the position of the target after a translation filter is
-applied.
+applied to the input images. On the other hand, another translation
+filter with smaller padding size, $R_{t}^{S}$, will help {\it E}nKCF
+to better localize the position of the target after a translation
+filter is applied.
 
@@
 first row of the kernel matrix.
+\begin{comment}
+As a common practice, to integrate further temporal information into tracker, we
+update the correlation filter and the appearance model as below.
+\begin{align}
+\mathbf{\hat{\alpha}_{t}} = (1-\beta) \mathbf{\hat{\alpha}_{t-1}} + \beta \mathbf{\hat{\alpha}_{t}} \\
+\mathbf{x_{t}} = (1-\beta) \mathbf{x_{t-1}} + \beta \mathbf{x_{t}}.
+\end{align}
+\end{comment}
 
@@
 that contains the videos recorded from smart phones and typical
-cameras in perspective view. In addition, we temporarily down-sampled
-the UAV123 data to check how robust our algorithm is to drastic
-motions of camera and moving targets. Lastly, we evaluate the proposed
-algorithm with deep convolutional features, on the UAV123 dataset to
-investigate how much performance gain we can achieve in using deep
-features over the conventional features like fHoG and color-naming.
+cameras in perspective view. In addition, we use a temporarily
+down-sampled the UAV123 data to check how robust our algorithm is to
+drastic motions of camera and moving targets. Lastly, we evaluate the
+proposed algorithm with deep convolutional features on the UAV123
+dataset to investigate how much performance gain we can achieve in
+using deep features over the conventional features like fHoG and
+color-naming.
 
@@
     candidates in a scale pool whereas our algorithm uses a 2-D scale
-    filter with 3 candidate scales. Learning a 2-D filter would result
-    in learning more spatial information. Second of all, the DSST use
+    filter with 3 candidate scales. Learning a 2-D filter resulted in
+    learning more spatial information. Second of all, the DSST use
     only fHoG whereas our algorithm uses both fHoG and color-naming
-    features. Learning more features, not for always, but would
-    provide better understanding on the ROI.
+    features. Learning more features, not always, but provided a
+    better understanding on the ROI.
 
@@
   E}nKCF with particle filter achieves $51.98\%$ precision ($20$px),
-outperforming the one without particle filter {\it E}nKCF by
-$6.32\%$. This experiment validated that the integration of particle
-filter into the {\it E}nKCF can further improve the performance.
+outperforming the one without particle filter by $6.32\%$. This
+experiment validated that the integration of particle filter into the
+{\it E}nKCF can further improve the performance.
 
@@
 observe how sensitive the performance of the state-of-the-art tracking
-algorithms is the frame rate, and, with a slight modification, the
+algorithms is to the frame rate, and, with a slight modification, the
 proposed method effectively handled large displacement of objects in
 successive frames.
-\begin{comment}
-\textit{YoungWoo : I also believe that we should
-  emphasize how the state-of-the-art trackers perform in lower frame
-  rates. And I believe this is what this paper
-  \cite{mueller2017context} says. They rank the trackers by evaluating
-  them on videos matching their fps. I was thinking of running ECO and
-  CCOT in UAV123 in 5 fps videos and mention how they degrade with
-  respect to the decreasing fps.  I believe this is our contribution
-  and we should emphasize it.
 
-  Burak: To be honest with you, it's a cheating -- we modified our
-  algorithm to make it work better, but didn't do anything or
-  modifications to other algorithms. Yes, all other algorithms didn't
-  perform well on a low frame rate, but it was a unfair comparison. So
-  I wouldn't think it's a contribution.  }
-\end{comment}
 \begin{figure}[!h]

### 2017-12-02 wacv_for_review.tex
final comments in the last stretch

@@
 \usepackage{comment, url}
+\usepackage{bm}
 \usepackage[ruled, vlined, linesnumbered]{algorithm2e}
@@
  	// \textit{Translation Estimation - Particle Filter} \\
-	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
+	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $(x_{t},y_{t},s_{t-1})$ \\
      // \textit{Translation Estimation - Correlation Filter} \\
-	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
+	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $(x_{t},y_{t})$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
 	// \textit{Scale Estimation - Correlation Filter}\\
 	Scale pool for $R_{s}$ : $\mathbf{S} = \lbrace1.05,1.0,1/1.05\rbrace$,\\
-	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\
+	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\underset{i\in S}{\textit{argmax}}(PSR(\boldsymbol{y_{R_{s}^{i}}}))$, and new scale $s_{t} = \alpha * s_{t-1}$,\\
 	// \textit{Update Translation - Particle Filter}\\
 	Do Importance Re-sampling (if necessary) and compute the 
-	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
+	mean of posterior pdf $(x_{t},y_{t})$\\
 	// \textit{Model Update}\\
@@
 	Update $R_{t}^{L}$ (Condition 2),\\
-	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
+	\uIf{$PSR(\boldsymbol{y_{R_{s}}}) \geq T_{R_{s}}$}{
 		Update $R_{s}$ (Condition 1)}
@@
 filter with smaller padding size, $R_{t}^{S}$, will help {\it E}nKCF
-to better localize the position of the target after a translation
+to better localize the position of the target after the large ROI translation
 filter is applied.
@@
 circulant matrix. The eigenvalues are equal to the DFT transformation
-of the base sample ($\mathbf{x}$) elements. The Kernelized Correlation
-Filter, in particular, applies a kernel to $\mathbf{x}$ to transform
+of the base sample ($\boldsymbol{x}$) elements. The Kernelized Correlation
+Filter, in particular, applies a kernel to $\boldsymbol{x}$ to transform
 to a more discriminative domain. The circulant matrix is then formed
-by applying cyclic shifts on the kernelized $\mathbf{x}$. Such
+by applying cyclic shifts on the kernelized $\boldsymbol{x}$. Such
 kernelization operation maintains O($nlog(n)$) complexity unlike other
@@
 \begin{equation}
-E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
+E(h) = \frac{1}{2}||\boldsymbol{y}-\sum_{c=1}^{C}\boldsymbol{h_{c}}*\boldsymbol{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\boldsymbol{h_{c}}||^{2}
 \label{eq:Closedform_RidgeReg}
 \end{equation}
-where we seek for $\mathbf{h}$ that minimizes $E$ given the desired
-continuous response, $\mathbf{y}$, and the training template
-$\mathbf{x}$.  The parameter $c$ enables one to integrate features in
+where we seek for $\boldsymbol{h}$ that minimizes $E$ given the desired
+continuous response, $\boldsymbol{y}$, and the training template
+$\boldsymbol{x}$.  The parameter $c$ enables one to integrate features in
 the form of multiple channels, such as HoG and color, in this setup
@@
 domain was proposed to learn the frequency domain correspondence of
-$\mathbf{h}$, $\mathbf{\hat{w}}$:
+$\boldsymbol{h}$, $\boldsymbol{\hat{w}}$:
 \begin{equation}
-\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
+\boldsymbol{\hat{w}} = \boldsymbol{\hat{x}^{*}}*\boldsymbol{\hat{y}}(\boldsymbol{\hat{x}^{*}}*\boldsymbol{\hat{x}}+\lambda)^{-1}.
 \label{eq:DiagonalizedPrimalSolution}
 \end{equation}
-A non-linear version of $\mathbf{\hat{w}}$, $\mathbf{\hat{\alpha}}$ , is proposed to increase robustness
+A non-linear version of $\boldsymbol{\hat{w}}$, $\boldsymbol{\hat{\alpha}}$ , is proposed to increase robustness
 to any geometric and photometric variations
@@
 \begin{equation}
-\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
+\boldsymbol{\hat{\alpha}} = \boldsymbol{\hat{y}}(\boldsymbol{\hat{k}^{xx}}+\lambda)^{-1}
 \label{eq:FourierDualDomainSolution}
 \end{equation}
-where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
- the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and is expressed as
+where $\lambda$ represents the regularization weight whereas $\boldsymbol{\hat{k}^{xx}}$ denotes
+ the first row of the kernel matrix $\boldsymbol{K}$ known as \textit{gram matrix} and is expressed as
 \begin{equation}
-\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'}))).
+\boldsymbol{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\boldsymbol{x}||^{2}+||\boldsymbol{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\boldsymbol{\hat{x}_{c}}^{*}\odot \boldsymbol{\hat{x}_{c}}^{'}))).
 \label{eq:GaussianCorrelationSingleChannel}
@@
 An early version based on this formulation used grayscale feature
-($C=1$) to learn the solution vector $\mathbf{w}$ and integrating
+($C=1$) to learn the solution vector $\boldsymbol{w}$ and integrating
 multi-channel features such as HoG and Color showed improved accuracy
@@
 In the detection phase, the learned correlation filter is correlated
-with the first row of the gram matrix, $\mathbf{k^{xz^{'}}}$, which
+with the first row of the gram matrix, $\boldsymbol{k^{xz^{'}}}$, which
 contains the similarity values between the learned feature template
-$\mathbf{x}$ and the new test template $\mathbf{z}$. This can be
+$\boldsymbol{x}$ and the new test template $\boldsymbol{z}$. This can be
 formulated as
 \begin{equation}
-\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
+\boldsymbol{r(z)} = F^{-1}(\boldsymbol{\hat{k}^{xz}} \odot \boldsymbol{\hat{\alpha}})
 \end{equation}
-where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
+where $\boldsymbol{r}$ denotes the correlation response at all cyclic shifts of the
 first row of the kernel matrix.
-\begin{comment}
+
+%\begin{comment}
+\textit{YoungWoo : I added the following equations about the update scheme of the KCF.}
 As a common practice, to integrate further temporal information into tracker, we
@@
 \begin{align}
-\mathbf{\hat{\alpha}_{t}} = (1-\beta) \mathbf{\hat{\alpha}_{t-1}} + \beta \mathbf{\hat{\alpha}_{t}} \\
-\mathbf{x_{t}} = (1-\beta) \mathbf{x_{t-1}} + \beta \mathbf{x_{t}}.
+\boldsymbol{\hat{\alpha}_{t}} = (1-\beta) \boldsymbol{\hat{\alpha}_{t-1}} + \beta \boldsymbol{\hat{\alpha}_{t}} \\
+\boldsymbol{\hat{x}_{t}} = (1-\beta) \boldsymbol{\hat{x}_{t-1}} + \beta \boldsymbol{\hat{x}_{t}}
 \end{align}
-\end{comment}
+%\end{comment}
+where $\beta$ represents the learning rate tuned to a small value in practice.
 
@@
 particle filter to estimate the target's image coordinate based on the
-{\it E}nKCF's outputs. The state in this paper, $\mathbf{X_{t}}$,
+{\it E}nKCF's outputs. The state in this paper, $\boldsymbol{X_{t}}$,
 represents the target's pixel coordinates and its velocity,
-$\mathbf{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$ and
+$\boldsymbol{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$ and
 $y$ are the pixel coordinates of the target's centroid, $v_x$ and
@@
 as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
-\mathbf{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ denotes the weight of
+\boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ denotes the weight of
 the particle $p$ at time $t$, and $N$ and $M$ denote the number of
@@
        single target tracking problem, the optimal parameters for
-       individual KCFs should be different. We set the learning rates
+       individual KCFs should be different. We set the learning rates ($\beta$)
        of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as
@@
        when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
-       \approx (\sum_{p=1}^{P}\mathbf{w}_{p}^{2})^{-1} $), is lower
+       \approx (\sum_{p=1}^{P}\boldsymbol{w}_{p}^{2})^{-1} $), is lower
        than a pre-defined threshold.
@@
 \tiny\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
-\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
-\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
-\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
-\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
+\includegraphics[width=3.80cm]{./figures/pr_uav123.eps}
+\includegraphics[width=4.10cm]{./figures/sr_uav123.eps}
+\includegraphics[width=3.80cm]{./figures/pr_otb100.eps}
+\includegraphics[width=4.10cm]{./figures/sr_otb100.eps}\\
 \end{tabular}
@@
     filter with 3 candidate scales. Learning a 2-D filter resulted in
-    learning more spatial information. Second of all, the DSST use
+    learning more spatial information. Second of all, the DSST uses
     only fHoG whereas our algorithm uses both fHoG and color-naming
-    features. Learning more features, not always, but provided a
+    features. \textit{YoungWoo : is this sentence not confusing? Maybe, Learning 
+    more features provided a better understanding of the ROI?} 
+    Learning more features, not always, but provided a
     better understanding on the ROI.
@@
 also conducted an experiment to see what combination and deployment
-order of the KCF work best. Table \ref{table:Comparison_to_LCT}
+order of the KCF works best. Table \ref{table:Comparison_to_LCT}
 presents results of this experiment. To achieve fair comparison, we did
@@
 \tiny\quad\textbf{UAV123$\_$10fps}\\
-\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
-\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
+\includegraphics[width=4.02cm]{./figures/pr_uav123_10fps.eps}
+\includegraphics[width=4.00cm]{./figures/sr_uav123_10fps.eps}\\
 \end{tabular}
@@
 extensively done yet. As future work, we would like to thoroughly
-study when and what conditions our algorithm would fail to track
+study \textit{YoungWoo : should it not be under which conditions?} 
+when and what conditions our algorithm would fail to track
 moving objects. In addition, we also would like to investigate a way

### 2017-12-02 wacv_for_review.tex
Final Submission

@@
 \begin{equation}
-\boldsymbol{\hat{\alpha}} = \boldsymbol{\hat{y}}(\boldsymbol{\hat{k}^{xx}}+\lambda)^{-1}
+\boldsymbol{\hat{\alpha}} = \boldsymbol{\hat{y}}(\boldsymbol{\hat{k}^{xx^{'}}}+\lambda)^{-1}
 \label{eq:FourierDualDomainSolution}
 \end{equation}
-where $\lambda$ represents the regularization weight whereas $\boldsymbol{\hat{k}^{xx}}$ denotes
+where $\lambda$ represents the regularization weight whereas $\boldsymbol{\hat{k}^{xx^{'}}}$ denotes
  the first row of the kernel matrix $\boldsymbol{K}$ known as \textit{gram matrix} and is expressed as
@@
 \begin{equation}
-\boldsymbol{r(z)} = F^{-1}(\boldsymbol{\hat{k}^{xz}} \odot \boldsymbol{\hat{\alpha}})
+\boldsymbol{r(z)} = F^{-1}(\boldsymbol{\hat{k}^{xz^{'}}} \odot \boldsymbol{\hat{\alpha}})
 \end{equation}
@@
 %\begin{comment}
-\textit{YoungWoo : I added the following equations about the update scheme of the KCF.}
 As a common practice, to integrate further temporal information into tracker, we
@@
 the first convolutional layer features to update the transition. This
-coarse-to-fine approach accommodates different levels of abstractions
+coarse-to-fine translation estimation approach accommodates different levels of abstractions
 of the object. However, it runs multiple KCFs in a sequential fashion,
@@
 data\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}
-that contains 123 video sequences of moving objects captured from
+that contains 123 video sequences of objects captured from
 low-altitude UAVs. Because of the nature of the video acquisition --
 the targets and the camera are moving together, this data pose a great
-deal of challenges as the scale and position of the targets can be
-drastically changed in a few frames. To verify that our algorithm is
+deal of challenges as the scale and position of the targets change drastically
+in most of the sequences . To verify that our algorithm is
 useful not only for the image data with such extreme challenges but
@@
 that contains the videos recorded from smart phones and typical
-cameras in perspective view. In addition, we use a temporarily
-down-sampled the UAV123 data to check how robust our algorithm is to
+cameras in perspective view. In addition, we use the temporarily
+down-sampled UAV123 dataset to check how robust our algorithm is to
 drastic motions of camera and moving targets. Lastly, we evaluate the
@@
 \begin{tabular}{ccc}
-\tiny\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
+\tiny\textbf{UAV123}\hspace{.43\linewidth}\textbf{OTB100}\\
 \includegraphics[width=3.80cm]{./figures/pr_uav123.eps}
@@
     only fHoG whereas our algorithm uses both fHoG and color-naming
-    features. \textit{YoungWoo : is this sentence not confusing? Maybe, Learning 
-    more features provided a better understanding of the ROI?} 
-    Learning more features, not always, but provided a
-    better understanding on the ROI.
+    features. Learning complementary features such as color and shape provided a 
+    better understanding of the ROI.
 
@@
 extensively done yet. As future work, we would like to thoroughly
-study \textit{YoungWoo : should it not be under which conditions?} 
-when and what conditions our algorithm would fail to track
-moving objects. In addition, we also would like to investigate a way
+study under what conditions our algorithm would fail to track 
+objects. In addition, we also would like to investigate a way
 of re-initializing a target when the target is lost, due to occlusion,

### 2018-01-09 wacv_for_review.tex
Revision after the second round review.

@@
 run-time performance, we deploy each of KCFs in turn, instead of
-applying multiple KCFs to each frame. To minimize any potential drifts
+applying multiple KCFs to each frame. To reduce any potential drifts
 between individual KCFs' transition, we developed a particle
@@
 of the proposed algorithm maintains high without sacrificing the
-accuracy of tracking. To minimize any potential drifts while switching
+accuracy of tracking. To reduce any potential drifts while switching
 KCFs, we developed a particle filter. Additionally, to increase the
@@
 circulant matrix. The eigenvalues are equal to the DFT transformation
-of the base sample ($\boldsymbol{x}$) elements. The Kernelized Correlation
-Filter, in particular, applies a kernel to $\boldsymbol{x}$ to transform
-to a more discriminative domain. The circulant matrix is then formed
-by applying cyclic shifts on the kernelized $\boldsymbol{x}$. Such
-kernelization operation maintains O($nlog(n)$) complexity unlike other
-kernel algorithms leading to O($n^{2}$) or even higher complexities.
+of the base sample ($\boldsymbol{x}$) elements. The Kernelized
+Correlation Filter, in particular, applies a kernel to
+$\boldsymbol{x}$ to transform to a more discriminative domain. The
+circulant matrix is then formed by applying cyclic shifts on the
+kernelized $\boldsymbol{x}$. Such kernelization operation maintains
+$\mathcal{O}$($nlog(n)$) complexity unlike other kernel algorithms
+leading to $\mathcal{O}$($n^{2}$) or even higher complexities.
 
@@
 \begin{equation}
-E(h) = \frac{1}{2}||\boldsymbol{y}-\sum_{c=1}^{C}\boldsymbol{h_{c}}*\boldsymbol{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\boldsymbol{h_{c}}||^{2}
+E_h = \min_{\boldsymbol{h}}\frac{1}{2}||\boldsymbol{y}-\sum_{c=1}^{C}\boldsymbol{h_{c}}*\boldsymbol{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\boldsymbol{h_{c}}||^{2}
 \label{eq:Closedform_RidgeReg}
@@
 deal of challenges as the scale and position of the targets change drastically
-in most of the sequences . To verify that our algorithm is
+in most of the sequences. To verify that our algorithm is
 useful not only for the image data with such extreme challenges but

### 2018-01-13 wacv_for_review.tex
fps and reference to OTB100 dataset added

@@
 \quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
-\caption{Examples of three filters with hand-crafted features.}
+\caption{Examples of three filters with hand-crafted features. The desired responses by 
+the large and small area translation filters and scale filter are represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$
+and $y_{R_{s}}$.}
 \label{fig:Filters}
@@
 data\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
+\cite{WuLimYang13}
 that contains the videos recorded from smart phones and typical
@@
 performance with Deep{\it E}nKCF on the UAV123
-dataset.}
+dataset. The runtime performance the Deep{\it E}nKCF (conv224) is 30.74 fps 
+whereas the conv222 setting yields to a 35.23 fps tracker on a CPU. }
 \label{fig:UAV123_DATASET_DeepFeatures}

### 2018-01-17 wacv_for_review.tex
revision.

@@
 \end{equation}
-A non-linear version of $\boldsymbol{\hat{w}}$, $\boldsymbol{\hat{\alpha}}$ , is proposed to increase robustness
-to any geometric and photometric variations
-\cite{henriques2015high}. In particular, the diagonalized non-linear Fourier
-domain dual form solution is expressed as
+Where $*$ is an element-wise multiplication. A non-linear version of
+$\boldsymbol{\hat{w}}$ and $\boldsymbol{\hat{\alpha}}$ are proposed to
+increase robustness to any geometric and photometric variations
+\cite{henriques2015high}. In particular, the diagonalized non-linear
+Fourier domain dual form solution is expressed as
 \begin{equation}
@@
 CNN features in tracking-by-detection algorithms. For example,
-\cite{danelljan2015convolutional} used the activation of the first
-and second convolutional layer of the VGGNet \cite{simonyan2014very}.
+\cite{danelljan2015convolutional} used the activation of the first and
+second convolutional layer of the VGGNet \cite{simonyan2014very}.
 They report that the first convolutional layer features lead to
@@
 the first convolutional layer features to update the transition. This
-coarse-to-fine translation estimation approach accommodates different levels of abstractions
-of the object. However, it runs multiple KCFs in a sequential fashion,
-increasing the run-time complexity. For this reason, we follow an
-approach similar to \cite{danelljan2015convolutional}, in order to
-embed deep features in {\it E}nKCF. Our {\it E}nKCF algorithm enables
-us to exploit different level of feature encodings with different
-KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider
-at least twice bigger area than the scale filter, $R_{s}$. Given this,
-we can assign deeper feature encodings to $R_{s}$ as it learns less
-spatial information than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign
-the activation of the fourth convolutional layer features
-($26\times26\times128$) to $R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$
-are assigned the activation of the second layer features
-($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
-this feature assignment. Additionally, we assign the second
-convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
-$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
-\textit{conv224-VGG}. The conv222 setting stands for the assignment of
-the activation of $2^{th}$ convolutional layer features of VGGNet to
-$R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it
-provides higher spatial resolution at the first several layers than
-AlexNet \cite{krizhevsky2012imagenet}.
+coarse-to-fine translation estimation accommodates different levels of
+abstractions of the object. However, it runs multiple KCFs in a
+sequential fashion, increasing the run-time complexity. For this
+reason, we follow an approach similar to
+\cite{danelljan2015convolutional}, in order to embed deep features in
+     {\it E}nKCF. Our {\it E}nKCF algorithm enables us to exploit
+     different level of feature encodings with different KCFs. The
+     translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at
+     least twice bigger area than the scale filter, $R_{s}$. Given
+     this, we can assign deeper feature encodings to $R_{s}$ as it
+     learns less spatial information than $R_{t}^{L}$ and
+     $R_{t}^{S}$. Thus we assign the activation of the fourth
+     convolutional layer features ($26\times26\times128$) to $R_{s}$
+     whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activation
+     of the second layer features ($109\times109\times64$). Figure
+     \ref{fig:Filters_CNN} illustrates this feature
+     assignment. Additionally, we assign the second convolutional
+     layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and
+     compare this setting (\textit{conv222-VGG}) to
+     \textit{conv224-VGG}. The conv222 setting stands for the
+     assignment of the activation of $2^{th}$ convolutional layer
+     features of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We
+     use the VGGNet since it provides higher spatial resolution at the
+     first several layers than AlexNet \cite{krizhevsky2012imagenet}.
 
@@
 represents the target's pixel coordinates and its velocity,
-$\boldsymbol{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$ and
-$y$ are the pixel coordinates of the target's centroid, $v_x$ and
+$\boldsymbol{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$
+and $y$ are the pixel coordinates of the target's centroid, $v_x$ and
 $v_y$ are the velocities estimated along the $x$-axis and
@@
 as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
-\boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ denotes the weight of
-the particle $p$ at time $t$, and $N$ and $M$ denote the number of
-rows and columns of the confidence map.
+\boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ is the weight of
+the particle $p$ at time $t$, $\boldsymbol{y_{R}}$ is the response map
+from one of the KCFs, and $N$ and $M$ denote the number of rows and
+columns of the confidence map.
 
@@
 \caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming})
-performance with Deep{\it E}nKCF on the UAV123
-dataset. The runtime performance the Deep{\it E}nKCF (conv224) is 30.74 fps 
-whereas the conv222 setting yields to a 35.23 fps tracker on a CPU. }
+  performance with Deep{\it E}nKCF on the UAV123 dataset. The frame
+  rate of the Deep{\it E}nKCF (conv224) was, on average, 30.74 fps and
+  the conv222 setting was 35.23 fps on a CPU.}
 \label{fig:UAV123_DATASET_DeepFeatures}

### 2018-01-21 wacv-camera-ready.tex
final revision.

--- 2018-01-17 wacv_for_review.tex
@@
 
-%\wacvfinalcopy % *** Uncomment this line for the final submission
+\wacvfinalcopy % *** Uncomment this line for the final submission
 
@@
 % Authors at different institutions
-\author{First Author \\
+\author{Burak Uzkent \\
 Institution1\\
@@
 \and
-Second Author \\
-Institution2\\
-{\tt\small secondauthor@i2.org}
+YoungWoo Seo \\
+Independent Robotics Research (IR2)\\
+{\tt\small youngwoo.blank.seo@gmail.com}
 }
@@
 Computer vision technologies are very attractive for practical
-applications running on embedded systems. For such an application, it
-is desirable for the deployed algorithms to run in high-speed and
-require no offline training. To develop a single-target tracking
-algorithm with these properties, we propose an ensemble of the
-kernelized correlation filters (KCF), we call it {\it E}nKCF. A
-committee of KCFs is specifically designed to address the variations
-in scale and translation of moving objects. To guarantee a high-speed
-run-time performance, we deploy each of KCFs in turn, instead of
-applying multiple KCFs to each frame. To reduce any potential drifts
+applications running on embedded systems. For such applications, it is
+desirable for the deployed algorithms to run in high-speed and require
+no offline training. To develop a single-target tracking algorithm
+with these properties, we propose an ensemble of the kernelized
+correlation filters (KCF), we call it {\it E}nKCF. A committee of KCFs
+is designed to specifically address the variations in scale and
+translation of moving objects. To guarantee a high-speed run-time
+performance, we deploy each of KCFs in turn, instead of applying
+multiple KCFs to each frame altogether. To reduce any potential drifts
 between individual KCFs' transition, we developed a particle
@@
 rate for the OTB100 data, and 54.50\% and 40.2\% for the UAV123
-data. Experimental results showed that our method is better than other
-high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
-AUC on average. Moreover, our implementation ran at 340 fps for the
-OTB100 and at 416 fps for the UAV123 dataset that is faster than DCF
-(292 fps) for the OTB100 and KCF (292 fps) for the UAV123. To increase
-flexibility of the proposed {\it E}nKCF running on various platforms,
-we also explored different levels of deep convolutional features.
+data. Experimental results showed that our method is, on average,
+better than other high-speed trackers over 5\% on precision on 20
+pixels and 10-20\% on AUC. In addition, our implementation ran at 340
+fps for the OTB100 and at 416 fps for the UAV123 dataset that is
+faster than DCF (292 fps) for the OTB100 and KCF (292 fps) for the
+UAV123. To increase flexibility of the proposed {\it E}nKCF running on
+various platforms, we also explored different levels of deep
+convolutional features.
 \end{abstract}
@@
 has increased interests on deploying intelligent algorithms to
-existing embedded and mobile platforms. Among those technologies,
-computer vision algorithms are getting more attentions primarily
-because payloads of those mobile platforms are limited to carry any
-other sensors than a monocular camera. Instead of just manually being
-flew for video recording, an unmanned air vehicle (UAV) equipped with
-an object or feature following function would make it more useful for
-the application of monitoring/surveillance/surveying on private
-properties/wild-life/crop, video recording on sports/movies/events,
-many others. To this end, in this paper, we propose a single-target
+existing mobile platforms. Among those technologies, computer vision
+algorithms are getting more attentions primarily because payloads of
+those mobile platforms are limited to carry any other sensors than a
+monocular camera. Instead of just manually being flew for video
+recording, an unmanned air vehicle (UAV) equipped with an object or
+feature following function would make it more useful for the
+application of monitoring/surveillance/surveying on private
+properties/wild-life/crop, video recording on various events, many
+others. To this end, in this paper, we propose a single-target
 tracking algorithm that does not require offline training and can run
-in high-speed. Specifically, we would like to have our algorithm 1)
+at high-speed. Specifically, we would like to have our algorithm 1)
 learn the appearance model of a target on the fly and 2) run on a
@@
   challenging for object tracking as the scale and translation of a
-  target can be drastically changed in a few frames.}
+  target can be drastically changed in a few consecutive frames.}
 \label{ResultsIntroduction}
@@
 correlation filter that essentially solves a single-target tracking
-problem as a regression problem in the frequency domain. This
-framework assumes that a target location is given at the beginning
-like any other online tracking algorithms
-\cite{smeulders2014survey}. Given this positive example for the
-regression problem, a set of negative examples is collected around the
-initial target bounding box and represented as a form of the circulant
-matrix \cite{henriques2015high}. One can optimally solve this
-regression problem using a ridge regression in a closed form. However,
-this solution has to deal with expensive matrix operations
+problem as a regression problem in the frequency domain. This method
+assumes that a target location is given at the beginning like any
+other online tracking algorithms \cite{smeulders2014survey}. Given
+this positive example for the regression problem, a set of negative
+examples is collected around the initial target bounding box and
+represented as a form of the circulant matrix
+\cite{henriques2015high}. One can optimally solve this regression
+problem using a ridge regression in a closed form. However, this
+solution has to deal with expensive matrix operations
 $\mathcal{O}(n^{3})$. The correlation filter offers a less complex
-solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
+solution, $\mathcal{O}(n\log n)$ by element-wise multiplication in a
 frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
@@
 ratios to find the target in appropriate scale
-\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
+\cite{bibi2015multi,henriques2015high,li2014scale,ma2015long,tang2015multi}. However,
 these approaches would drastically reduce run-time performance because
@@
 \cite{bolme2010visual} to estimate the target's translation. And then
-they attempted to update the scale of the target by further analyzing
+their method updated the scale of the target by further analyzing
 image sub-regions in high confidence. Their method is based on an
-assumption that the scale of a target would not change drastically over two
-consecutive frames. Similarly, Ma and his colleagues used two KCFs to
-learn the translation and scale of a target separately
+assumption that the scale of a target would not change drastically
+over two consecutive frames. Similarly, Ma and his colleagues used two
+KCFs to learn the translation and scale of a target separately
 \cite{ma2015long}. In particular, a KCF is used to learn the
@@
 fps$). Our method is motivated by this idea -- the idea of deploying
-multiple KCFs to address the issues of single target tracking: scale
-and translation, but in a more efficient way. To maximize run-time
-performance and accuracy, instead of running them all together on
-every frame, we deploy three KCFs in turn:
+multiple KCFs to address the issues of single target tracking the
+drastic variations in scale and translation, but in a more efficient
+way. To maximize run-time performance and accuracy, instead of running
+them all together on every frame, we deploy three KCFs in turn:
 \textit{target}+\textit{small background} translation filter
@@
 \textit{target}+\textit{large background} translation filter
-($R_{t}^{L}$). By doing so, our method aims at addressing scale
-change and estimating target's motion efficiently while maintaining or
-increasing run-time performance. Figure \ref{Workflows} illustrates
-the workflow of the {\it E}nKCF.
+($R_{t}^{L}$). By doing so, our method aims at effectively addressing
+scale change and estimating target's motion while maintaining run-time
+performance at high-speed. Figure \ref{Workflows} illustrates the
+workflow of the {\it E}nKCF.
 
 The contribution of this paper is a novel, single-target tracking
-algorithm running in a very high-speed ($\geq300$ fps). In particular,
+algorithm running at a very high-speed ($\geq300$ fps). In particular,
 to effectively address the changes in scale and translation of a
@@
 \cite{henriques2015high} to effectively handle scale variations and
-dynamic maneuvers of a target. To maintain or improve the run-time
-performance of the original KCF (e.g., $\ge$ 300), we deploy three
-KCFs in turn, instead of applying them on the same image frame
-together. Each of these KCFs is designed to address the challenges of
-single-target tracking -- variance in scale and translation. By
-deploying each of three KCFs in turn, our algorithm will improve the
-performance of the original KCF while preserving the original KCF's
-high run-time performance and small-footprint.
+dynamic maneuvers of a target. To improve the run-time performance and
+maintain the small-footprint of the original KCF (e.g., $\ge$ 300), we
+deploy three KCFs in turn, instead of applying them altogether on the
+same image frame. Each of these KCFs is designed to address the
+challenges of single-target tracking -- variance in scale and
+translation.
 
@@
 first filter, $R_{t}^{S}$, focuses on learning the target area and its
-background for addressing a marginal translation by a target, the
+background for addressing a marginal translation of a target, the
 second filter, $R_{s}$, focuses entirely on learning the target's
@@
 and its background bigger than that of the first filter,
-$R_{t}^{S}$. We set up {\it E}nKCF in this way so that a correlation
-filter for learning a target's translation could include the
-background of the target to better discriminate it from its
-surrounding, and another correlation filter could focus on the target
-itself to estimate the right scale of the target. In particular, a
-transition filter with larger padding size, $R_{t}^{L}$ will enable
-{\it E}nKCF to recover from potential drifts after a scale filter is
-applied to the input images. On the other hand, another translation
-filter with smaller padding size, $R_{t}^{S}$, will help {\it E}nKCF
-to better localize the position of the target after the large ROI translation
-filter is applied.
-
-Our approach is similar to that of \cite{ma2015long} which
-sequentially applied more than one KCF to every frame, but different
-in that we operate multiple KCFs in an alternating manner. It
-intuitively makes sense to alternatively use multiple KCFs with
-different purposes because the appearance of a target does not change
+$R_{t}^{S}$. By designing {\it E}nKCF as a composite of three KCFs, a
+transition filter with larger padding size, $R_{t}^{L}$, will enable
+{\it E}nKCF to recover from potential drifts after a scale filter,
+$R_{s}$, is applied to the input images. Another translation filter
+with smaller padding size, $R_{t}^{S}$, will help {\it E}nKCF to
+better localize the position of the target after the large ROI
+translation filter is applied. Our approach is similar to that of
+\cite{ma2015long} which sequentially applied more than one KCF to
+every frame, but different in that we operate multiple KCFs in an
+alternating manner. It is intuitive to alternate multiple KCFs with
+different goals over a small temporal window of the input image
+sequences, because the appearance of a target does not change
 drastically over consecutive images. In other words, for most cases,
@@
   between the scale filters learned at every frame and the one learned
-  at every 5 frames. The left, sub-figures show the scale filters
-  trained at every frame and those at the right show the scale filters
-  trained at every 5 frames.}
+  at every 5 frames. In each figure, the leftmost, sub-figures show
+  the scale filters trained at every frame and those at the rightmost
+  show the scale filters trained at every 5 frames.}
 \label{fig:Filters_Comparison}
@@
 The order of running these three KCFs is important because each of
-these filters aims at addressing different challenges. A translation
-filter, $R_{t}^{L}$, is applied to the $i$th and $i$+$1$th image
-frames, another translation filter, $R_{t}^{S}$, is applied to the
-$i$+$2$th and $i$+$3$th image frames, and then the scale filter,
-$R_{s}$, is applied to the $i$+$4$th image. This order repeats until
-the last image is presented. Note that the translation filter,
-$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
-runs which is applied at every other $i$+$4$ frames. We run these
-filters in this way because we want to minimize any drifts that are
-likely to happen running only $R_{s}$. In addition, the filter,
-$R_{t}^{S}$, is applied to every other two frames before $R_{s}$ and
-right after two consecutive frames running $R_{t}^{L}$. By repeating
-this order of learning three KCFs, we can integrate more
-discriminative shape features that cannot be learned just by
-$R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color information
-together to recover from any potential drifts -- drifts could happen
-due to only scale filter operation in certain frames.
+these filters aims at addressing different challenges of single-target
+tracking. A translation filter, $R_{t}^{L}$, is applied to the $i$th
+and $i$+$1$th image frames, another translation filter, $R_{t}^{S}$,
+is applied to the $i$+$2$th and $i$+$3$th image frames, and then the
+scale filter, $R_{s}$, is applied to the $i$+$4$th image. This order
+repeats until the last image of an input video is presented. Note that
+the translation filter, $R_{t}^{L}$, is intended to run right after
+the scale filter, $R_s$, runs which is applied at every other $i$+$4$
+frames. We run these filters in this way because we want to minimize
+any drifts that are likely to happen running only $R_{s}$. In
+addition, the filter, $R_{t}^{S}$, is applied to every other two
+frames before $R_{s}$ and right after two consecutive frames running
+$R_{t}^{L}$. By repeating this order of learning three KCFs, we can
+integrate more discriminating shape features that cannot be learned
+just by $R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color
+information together to recover from any potential drifts -- drifts
+could happen due to only scale filter operation in certain frames.
 
@@
 from any potential drifts. Another translation filter, $R_{t}^{S}$, is
-designed to address the drawback of $R_{t}^{L}$ that it may learn
-noisy shape features due to its relatively larger search area. In what
-follows, we will detail the main idea behind the KCF.
+designed to address the drawback of $R_{t}^{L}$ that may learn noisy
+shape features due to its relatively larger search area. In what
+follows, we will brief the main idea behind the KCF.
 
 \textbf{Kernelized Correlation Filter} The Kernelized Correlation
-Filter is a well-known single target tracking method and its workflow
-has been detailed in other papers
-\cite{henriques2012exploiting,henriques2015high}. This section briefly
-goes over the parts of the KCF relevant to this study. Its
+Filter is a well-known single target tracking algorithm. As its
+workflow has been detailed in other papers
+\cite{henriques2012exploiting,henriques2015high}, in this section we
+briefly go over the parts of the KCF relevant to this study. Its
 computational efficiency is derived from the correlation filter
@@
 Correlation Filter, in particular, applies a kernel to
-$\boldsymbol{x}$ to transform to a more discriminative domain. The
+$\boldsymbol{x}$ to transform into a more discriminating domain. The
 circulant matrix is then formed by applying cyclic shifts on the
@@
 \end{equation}
-where we seek for $\boldsymbol{h}$ that minimizes $E$ given the desired
-continuous response, $\boldsymbol{y}$, and the training template
-$\boldsymbol{x}$.  The parameter $c$ enables one to integrate features in
-the form of multiple channels, such as HoG and color, in this setup
-\cite{henriques2015high,galoogahi2013multi}.  A closed-form solution
-for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
-closed-form solution, an element-wise multiplication in frequency
-domain was proposed to learn the frequency domain correspondence of
-$\boldsymbol{h}$, $\boldsymbol{\hat{w}}$:
+where we seek for $\boldsymbol{h}$ that minimizes $E$ given the
+desired continuous response, $\boldsymbol{y}$, and the training
+template $\boldsymbol{x}$.  The parameter $c$ enables one to integrate
+features in the form of multiple channels, such as HoG and color, in
+this setup \cite{galoogahi2013multi,henriques2015high}. To simplify
+the closed-form solution for Equation \ref{eq:Closedform_RidgeReg}, an
+element-wise multiplication in frequency domain was proposed to learn
+the frequency domain correspondence of $\boldsymbol{h}$,
+$\boldsymbol{\hat{w}}$:
 \begin{equation}
@@
 \end{equation}
-An early version based on this formulation used grayscale feature
+An earlier version based on this formulation used grayscale feature
 ($C=1$) to learn the solution vector $\boldsymbol{w}$ and integrating
 multi-channel features such as HoG and Color showed improved accuracy
-\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
-In the detection phase, the learned correlation filter is correlated
-with the first row of the gram matrix, $\boldsymbol{k^{xz^{'}}}$, which
-contains the similarity values between the learned feature template
-$\boldsymbol{x}$ and the new test template $\boldsymbol{z}$. This can be
-formulated as
+\cite{bibi2015multi,galoogahi2013multi,henriques2015high,ma2015long,tang2015multi}.
+In the detection step, the learned correlation filter is correlated
+with the first row of the gram matrix, $\boldsymbol{k^{xz^{'}}}$,
+which contains the similarity values between the learned feature
+template $\boldsymbol{x}$ and the new test template
+$\boldsymbol{z}$. This can be formulated as
 \begin{equation}
@@
 
-%\begin{comment}
-As a common practice, to integrate further temporal information into tracker, we
-update the correlation filter and the appearance model as below.
+To integrate further temporal information into tracker, we update the
+correlation filter and the appearance model as below:
 \begin{align}
@@
 \cite{li2014scale}. Figure \ref{fig:Filters} shows examples of these
-features. This setup of the {\it E}nKCF is designed to perform
-tracking at $30$ fps on low-end embedded systems without GPUs.
+features. This setup of the {\it E}nKCF is designed to develop an
+online tracking algorithm running at high-speed ($\ge$ 300 fps) on a
+typical desktop (and eventually running $\ge 30$ fps on a low-end
+embedded system without GPUs).
 \begin{figure}[!h]
@@
    \\[-3ex]
-\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
-\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
-\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
-\caption{Examples of three filters with hand-crafted features. The desired responses by 
-the large and small area translation filters and scale filter are represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$
-and $y_{R_{s}}$.}
+\subfloat[Small area translation filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
+\quad\subfloat[Large area translation filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
+\quad\quad\subfloat[Scale filter]{\hspace{.12\linewidth}}\label{fig:Rs}
+\caption{Examples of three filters with hand-crafted features. The
+  responses by the large and small area translation filters and scale
+  filter are represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$ and
+  $y_{R_{s}}$.}
 \label{fig:Filters}
@@
 \cite{van2009learning} for the large area translation filter,
-$R_{t}^{L}$. This is because the fHoG applied to relatively larger
-area tends to be more noisy and less discriminative, and adding color
-information makes the feature vector for the translation filter more
-discriminative. Figure \ref{fig:Filters}(b) shows an example of this
-translation filter. By contrast, the $R_{t}^{S}$ only employs the fHoG
-features because it covers a relatively smaller area.  Figure
-\ref{fig:Filters}(a) shows an example of this translation
+$R_{t}^{L}$. This is because the fHoG tends to be noisier and less
+discriminating, when it is applied to relatively larger area, and
+adding color information makes the feature vector for the translation
+filter more discriminating. Figure \ref{fig:Filters} (b) shows an
+example of this translation filter. By contrast, the $R_{t}^{S}$ only
+uses the fHoG features because it covers a relatively smaller area.
+Figure \ref{fig:Filters} (a) shows an example of this translation
 filter. Lastly, we use both fHoG and color-naming features again for
@@
 features, we ensure that the likelihood of inaccurate scale estimation
-is reduced in comparison to the scale filter with only fHoG
+is decreased in comparison to the scale filter with only fHoG
 features. This is more important in our case as the scale filter is
-operated in every 5 frames in the proposed tracker. Also, the scale
-filter, explained earlier in the algorithm \ref{alg:MKCF}, estimates
-the scale of a target by correlating it with three candidate
-ROIs. This search may increase the run-time complexity of the scale
-filter from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$. To
-ensure practical actual filtering operations, we use a smaller
-template size (i.e., 64$\times n$) for the scale filter, $R_{s}$. The
-smaller template size does not degrade the tracking performance
-because of 1) zero padding around the target (smaller ROI) and 2) use
-of color-naming features.
+operated in every 5 frames. Also, the scale filter, explained earlier
+in the algorithm \ref{alg:MKCF}, estimates the scale of a target by
+correlating it with three candidate ROIs. This search may increase the
+run-time complexity of the scale filter from $\mathcal{O}(n\log n)$ to
+$\mathcal{O}(3(n\log n))$. To ensure practically feasible operations,
+we use a smaller template size (i.e., 64$\times n$) for the scale
+filter, $R_{s}$. The smaller template size does not degrade the
+tracking performance because of 1) zero padding around the target
+(smaller ROI) and 2) usage of color-naming features.
 
@@
 There has been a large volume of studies on utilizing a pre-trained
-CNN features in tracking-by-detection algorithms. For example,
+CNN features for tracking-by-detection algorithms. For example,
 \cite{danelljan2015convolutional} used the activation of the first and
 second convolutional layer of the VGGNet \cite{simonyan2014very}.
-They report that the first convolutional layer features lead to
+They reported that the first convolutional layer features lead to
 slightly better precision and success rates than the second layer due
-to increased translational invariance in this
+to increased invariance for translation in this
 layer. \cite{ma2015hierarchical} proposed a KCF tracker integrating
-features with higher abstraction capacity.  Their method first employs
+features with higher abstraction capacity. Their method, firstly used
 the third convolutional layer features to estimate the response
-map. In the next stage, the KCF, concentrating on the second
-convolutional layer features, is run to update transition. The third
-KCF then works on the transition given by the previous KCF and learns
+map. In the next step, the KCF, concentrating on the second
+convolutional layer features, ran to update transition. The third KCF
+then worked on the transition given by the previous KCF, and learned
 the first convolutional layer features to update the transition. This
 coarse-to-fine translation estimation accommodates different levels of
-abstractions of the object. However, it runs multiple KCFs in a
-sequential fashion, increasing the run-time complexity. For this
+abstractions of the object. However, their method runs multiple KCFs
+in a sequential fashion, increasing the run-time complexity. For this
 reason, we follow an approach similar to
 \cite{danelljan2015convolutional}, in order to embed deep features in
-     {\it E}nKCF. Our {\it E}nKCF algorithm enables us to exploit
+     {\it E}nKCF. The {\it E}nKCF algorithm enables us to exploit
      different level of feature encodings with different KCFs. The
@@
      compare this setting (\textit{conv222-VGG}) to
-     \textit{conv224-VGG}. The conv222 setting stands for the
-     assignment of the activation of $2^{th}$ convolutional layer
-     features of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We
-     use the VGGNet since it provides higher spatial resolution at the
-     first several layers than AlexNet \cite{krizhevsky2012imagenet}.
+     \textit{conv224-VGG}, where the \textit{conv222} setting
+     represents the assignment of the activation of $2^{th}$
+     convolutional layer features of VGGNet to $R_{t}^{L}$,
+     $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it provides
+     higher spatial resolution at the first several layers than
+     AlexNet \cite{krizhevsky2012imagenet}.
 
@@
 $v_y$ are the velocities estimated along the $x$-axis and
-$y$-axis. The particle filter predicts, using a constant velocity
-motion model, the target's next state by generating a predefined
-number of particles. Then it uses the confidence maps of {\it E}nKCF
-as observation to update its state. The particle weight is computed
-as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
-\boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ is the weight of
-the particle $p$ at time $t$, $\boldsymbol{y_{R}}$ is the response map
-from one of the KCFs, and $N$ and $M$ denote the number of rows and
-columns of the confidence map.
+$y$-axis. The particle filter predicts, using a motion model with
+constant acceleration assumption, the target's next state by
+generating a predefined number of particles. Then it uses the
+confidence maps of {\it E}nKCF as observation to update its state. The
+particle weight is computed as, $w_{p_{t}}(x_{t},y_{t}) =
+\sum_{i=1}^{N}\sum_{j=1}^{M} \boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$,
+where $w_{p}$ is the weight of the particle $p$ at time $t$,
+$\boldsymbol{y_{R}}$ is the response map from one of the KCFs, and $N$
+and $M$ denote the number of rows and columns of the confidence map.
 
@@
 variations in scale and translation of moving objects. To accurately
-evaluate the performance of the proposed algorithm in terms of the
-goal of this paper, we need data with challenging variations in scale
-and translation. To this end, we chose the UAV123
+evaluate the performance of the proposed algorithm from the
+perspective of this paper's goal, we need data with challenging
+variations in scale and translation. To this end, we chose the UAV123
 data\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}
@@
 the targets and the camera are moving together, this data pose a great
-deal of challenges as the scale and position of the targets change drastically
-in most of the sequences. To verify that our algorithm is
+deal of challenges as the scale and position of the targets change
+drastically in most of the sequences. To verify that our algorithm is
 useful not only for the image data with such extreme challenges but
@@
 data\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
-\cite{WuLimYang13}
-that contains the videos recorded from smart phones and typical
-cameras in perspective view. In addition, we use the temporarily
-down-sampled UAV123 dataset to check how robust our algorithm is to
-drastic motions of camera and moving targets. Lastly, we evaluate the
-proposed algorithm with deep convolutional features on the UAV123
-dataset to investigate how much performance gain we can achieve in
-using deep features over the conventional features like fHoG and
-color-naming.
+\cite{WuLimYang13} that contains the videos recorded from smart phones
+and typical cameras in perspective view. In addition, we use the
+temporarily down-sampled UAV123 dataset to check how robust our
+algorithm is to drastic motions of camera and moving targets. Lastly,
+we evaluate the proposed algorithm with deep convolutional features on
+the UAV123 dataset to investigate how much performance gain we can
+achieve in using deep features over the conventional features like
+fHoG and color-naming.
 
@@
        single target tracking problem, the optimal parameters for
-       individual KCFs should be different. We set the learning rates ($\beta$)
-       of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as
-       $0.020$, $0.020$ and $0.010$. For the kernel of the Gaussian
-       neighboring function, we empirically found the optimal values
-       of $\alpha$ as $0.7$, $0.6$, and $0.9$ for $R_{t}^{L}$,
+       individual KCFs should be different. We set the learning rates
+       ($\beta$) of individual filters, $R_{t}^{L}$, $R_{t}^{S}$, and
+       $R_{s}$ as $0.020$, $0.020$ and $0.010$. For the kernel of the
+       Gaussian neighboring function, we empirically found the optimal
+       values of $\alpha$ as $0.7$, $0.6$, and $0.9$ for $R_{t}^{L}$,
        $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
@@
        $R_{t}^{L}$, $1.50$ for $R_{t}^{S}$, and $0$ for $R_{s}$. For
-       our particle filter implementation, we empirically set the
-       number of particles to $1,000$ to balance the run-time
-       performance and accuracy. To keep the level of variance among
-       the particles reasonable, we performed the re-sampling only
-       when the \textit{efficient number of samples}, ($ \hat{N}_{eff}
-       \approx (\sum_{p=1}^{P}\boldsymbol{w}_{p}^{2})^{-1} $), is lower
-       than a pre-defined threshold.
+       our particle filter implementation, we empirically found 1,000
+       for the number of particles as an optimal one for balancing the
+       run-time performance and accuracy. To keep the level of
+       variance among the particles reasonable, we performed the
+       re-sampling only when the efficient number of samples,
+       $ \hat{N}_{eff} \approx
+       (\sum_{p=1}^{P}\boldsymbol{w}_{p}^{2})^{-1} $, is lower than a
+       pre-defined threshold.
 
@@
 precision, we rank the trackers based on the precision numbers at 20
-pixels whereas in the success rate plots, they are ranked based on the
-area under curve (AUC) scores. The tracking algorithms under the
-comparison include ones in high-speed ($\geq$300 fps): KCF
+pixels whereas in the success rate plots, they are ranked by the area
+under curve (AUC) scores. The tracking algorithms under the comparison
+include ones at high-speed ($\geq$300 fps): KCF
 \cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
 \cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
-\cite{zhang2014fast} and ones in relatively lower-speed ($\leq$50):
+\cite{zhang2014fast} and ones at relatively lower-speed ($\leq$50):
 ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
@@
 \cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
-convolutional features, however, to perform fair comparison, we employ
+convolutional features, however, to perform fair comparison, we use
 fHoG and color-naming features similar to our tracker. Figure
@@
     only fHoG whereas our algorithm uses both fHoG and color-naming
-    features. Learning complementary features such as color and shape provided a 
-    better understanding of the ROI.
+    features. Learning complementary features such as color and shape
+    provided a better understanding of the ROI.
 
@@
 order of the KCF works best. Table \ref{table:Comparison_to_LCT}
-presents results of this experiment. To achieve fair comparison, we did
-not use the particle filter. The combination presented at the $2^{nd}$
-column switched the order of deploying $R_{t}^{L}$ and
+presents results of this experiment. To achieve fair comparison, we
+did not use the particle filter. The combination presented at the
+$2^{nd}$ column switched the order of deploying $R_{t}^{L}$ and
 $R_{t}^{S}$. The one at the $3^{th}$ column removed $R_{t}^{S}$ and
@@
   a re-detection module for a long-term tracking.} This experiment
-empirically verified that \textit{E}nKCF is an optimal way of using
-multiple KCFs, in terms of both tracking accuracy and run-time
-performance. For example, one could achieve $4.26\%$ higher in accuracy
-by running $R_{t}^{L}$ and $R_{S}$ at every frame, but this
-combination decreases run-time performance to 317 fps.
+empirically verified that the way \textit{E}nKCF uses multiple KCFs is
+optimal, in terms of both tracking accuracy and run-time
+performance. For example, one could achieve $4.26\%$ higher in
+accuracy by running $R_{t}^{L}$ and $R_{t}^{S}$, and $R_{s}$ at every
+frame (produced 58.16\% for precision at 20 pixels), but this
+combination decreases run-time performance to 317 fps (=416fps - 99fps).
 
@@
 translation estimations of the KCFs. For this experiment, the {\it
-  E}nKCF with particle filter achieves $51.98\%$ precision ($20$px),
-outperforming the one without particle filter by $6.32\%$. This
-experiment validated that the integration of particle filter into the
-{\it E}nKCF can further improve the performance.
+  E}nKCF with particle filter achieves $51.98\%$ precision at 20
+pixels, outperforming the one without particle filter by
+$6.32\%$. This experiment validated that the integration of particle
+filter into the {\it E}nKCF can further improve the performance.
 
@@
 target scale in that it showed the highest precision and success rates
-among the other high-speed trackers. Interestingly, it outperformed
-another correlation filter based tracker, DSST, but performing $5\%$
-behind of another low-speed scale adaptive SAMF tracker. Finally, the
-ECO, and CCOT achieve $15\%$-$20\%$ higher precision and success rates
-than ours while operating at 10-20 times slower rates.
+among the other high-speed trackers. Interestingly, {\it E}nKCF
+outperformed another correlation filter based tracker, DSST, but
+performing $5\%$ behind of another low-speed scale adaptive SAMF
+tracker. Finally, the ECO, and CCOT achieve $15\%$-$20\%$ higher
+precision and success rates than ours while operating at 10-20 times
+slower rates.
 
@@
 a tracking algorithm. To this end, we use the temporarily down-sampled
-version of the UAV123, called UAV123$\_$10fps dataset. We believe the
-downsampling would make the original UAV123 data more challenging
-because the displacements of the moving objects become even bigger. To
-tackle this challenge, we slightly modified the proposed algorithm --
-ran $R_{t}^{L}$ every frame and removed the particle filter due to
-larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET} shows the
-performance of the modified version of {\it E}nKCF and other tracking
-methods. The precision rates of the ECO and CCOT dropped about $10\%$
-in comparison to the original UAV123 dataset. Our tracker outperforms
-other high-speed correlation filter based trackers including KCF, DSST
-by about $15\%$-$20\%$ and showed a precision rate similar to that of
-SAMF. It ranks as fourth in AUC while running about $10$ to $100$
-times faster than the top three trackers. It was interesting to
-observe how sensitive the performance of the state-of-the-art tracking
-algorithms is to the frame rate, and, with a slight modification, the
-proposed method effectively handled large displacement of objects in
-successive frames.
+version of the UAV123, called UAV123$\_$10fps dataset. The
+downsampling of a given video sequence would obviously make the
+original UAV123 data more challenging because the displacements of the
+moving objects become bigger. To tackle this challenge, we slightly
+modified the proposed algorithm -- ran $R_{t}^{L}$ every frame and
+removed the particle filter due to larger motion. Figure
+\ref{fig:UAV123_10fpsDATASET} shows the performance of the modified
+version of {\it E}nKCF and other tracking methods. The precision rates
+of the ECO and CCOT dropped about $10\%$ in comparison to the original
+UAV123 dataset. Our tracker outperforms other high-speed correlation
+filter based trackers including KCF, DSST by about $15\%$-$20\%$ and
+showed a precision rate similar to that of SAMF. It ranks as fourth in
+AUC while running about $10$ to $100$ times faster than the top three
+trackers. It was interesting to observe how sensitive the performance
+of the state-of-the-art tracking algorithms is to the frame rate, and,
+with a slight modification, the proposed method effectively handled
+large displacement of objects in successive frames.
 
@@
 features, fHoG and color-naming with deep convolutional features. We
-use deep convolutional features similar to \cite{ma2015hierarchical,
-  danelljan2015convolutional}. Note that running the {\it E}nKCF with
-deep features would obviously increase the computational cost and
-degrade the run-time performance.
+use deep convolutional features similar to
+\cite{danelljan2015convolutional,ma2015hierarchical}. Note that
+running the {\it E}nKCF with deep features would obviously increase
+the computational cost and degrade the run-time performance.
 
@@
 precision (20 px) and $2\%$ in success rates (AUC). The
-\textit{conv224-VGG} setting performed slightly better than
+\textit{conv224-VGG} setting performed slightly better than the
 \textit{conv222-VGG} in precision while achieving similar success rate
@@
 training and operate at high-speed. To develop a single-target
-tracking algorithm to meet these features, we proposed an extension of
-KCF that applies three KCFs, in turn, to address the variations in
+tracking algorithm to meet these properties, we proposed an extension
+of KCF that applies three KCFs, in turn, to address the variations in
 scale and translation of moving objects. We also developed a particle
@@
 
-Although the proposed algorithm showed a promising result tested with
+Although the proposed algorithm showed a promising result for the
 challenging data, we believe the corner case analysis has not been
@@
 study under what conditions our algorithm would fail to track
-objects. In addition, we also would like to investigate a way
-of re-initializing a target when the target is lost, due to occlusion,
-illumination change, drastic camera motion, etc.
+objects. In addition, we also would like to investigate, for long-term
+tracking, a way of re-initializing a target when the target is lost,
+due to occlusion, illumination change, drastic camera motion, etc.
 

### 2018-01-21 wacv-camera-ready.tex
Final Comments Before Camera-Ready Submission

@@
 \author{Burak Uzkent \\
-Institution1\\
-{\tt\small firstauthor@i1.org}
+Rochester Institute of Technology\\
+{\tt\small bxu2522@rit.edu}
 \and
@@
 better than other high-speed trackers over 5\% on precision on 20
-pixels and 10-20\% on AUC. In addition, our implementation ran at 340
+pixels and 10-20\% on AUC. \textit{YoungWoo : Two preceeding sentences start with
+experimental results showed that. Should we change the begining of the second sentence?}
+In addition, our implementation ran at 340
 fps for the OTB100 and at 416 fps for the UAV123 dataset that is
-faster than DCF (292 fps) for the OTB100 and KCF (292 fps) for the
+faster than DCF (333 fps) for the OTB100 and KCF (296 fps) for the
 UAV123. To increase flexibility of the proposed {\it E}nKCF running on
@@
 properties/wild-life/crop, video recording on various events, many
-others. To this end, in this paper, we propose a single-target
+others. \textit{YoungWoo : For me, it was hard to get the previous sentence.}
+To this end, in this paper, we propose a single-target
 tracking algorithm that does not require offline training and can run
@@
 \caption{Examples of three filters with hand-crafted features. The
+  \textit{YoungWoo : the responses are target (desired) response for the correlations filters}
   responses by the large and small area translation filters and scale
@@
 \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
-\cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
+\cite{zhang2012robust}. The ECO and CCOT trackers \textit{YoungWoo : it should be "use" I think.}originally uses deep
 convolutional features, however, to perform fair comparison, we use
@@
 combination decreases run-time performance to 317 fps (=416fps - 99fps). 
+\textit{YoungWoo : Should it not be 99fps.}
 
@@
 at 340 fps for OTB100 and at 416 fps for UAV123 data that is faster
-than DCF (292 fps) for OTB100 and KCF (292 fps) for UAV123. Finally,
+than DCF (333 fps) for OTB100 and KCF (296 fps) for UAV123. Finally,
 we explored the idea of utilizing deep features for the proposed
 algorithm and found that the deep features helped the proposed
-algorithm boost the performance by $10\%$.
+algorithm boost the performance by $5\%$.
 

### 2018-01-22 wacv-camera-ready.tex
Fixed Burak's suggestions.

@@
 between individual KCFs' transition, we developed a particle
-filter. Experimental results showed that the performance of ours is,
-on average, 70.10\% for precision at 20 pixels, 53.00\% for success
-rate for the OTB100 data, and 54.50\% and 40.2\% for the UAV123
-data. Experimental results showed that our method is, on average,
-better than other high-speed trackers over 5\% on precision on 20
-pixels and 10-20\% on AUC. \textit{YoungWoo : Two preceeding sentences start with
-experimental results showed that. Should we change the begining of the second sentence?}
-In addition, our implementation ran at 340
-fps for the OTB100 and at 416 fps for the UAV123 dataset that is
-faster than DCF (333 fps) for the OTB100 and KCF (296 fps) for the
-UAV123. To increase flexibility of the proposed {\it E}nKCF running on
-various platforms, we also explored different levels of deep
-convolutional features.
+filter. Experimental results showed that 1) the performance of ours
+is, on average, 70.10\% for precision at 20 pixels, 53.00\% for
+success rate for the OTB100 data, and 54.50\% and 40.2\% for the
+UAV123 data, and 2) our method is, on average, better than other
+high-speed trackers over 5\% on precision on 20 pixels and 10-20\% on
+AUC. In addition, our implementation ran at 340 fps for the OTB100 and
+at 416 fps for the UAV123 dataset that is faster than DCF (333 fps)
+for the OTB100 and KCF (296 fps) for the UAV123. To increase
+flexibility of the proposed {\it E}nKCF running on various platforms,
+we also explored different levels of deep convolutional features.
 \end{abstract}
@@
 properties/wild-life/crop, video recording on various events, many
-others. \textit{YoungWoo : For me, it was hard to get the previous sentence.}
-To this end, in this paper, we propose a single-target
+others. To this end, in this paper, we propose a single-target
 tracking algorithm that does not require offline training and can run
@@
 \caption{Examples of three filters with hand-crafted features. The
-  \textit{YoungWoo : the responses are target (desired) response for the correlations filters}
-  responses by the large and small area translation filters and scale
-  filter are represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$ and
+  responses by the large and small area translation filters, and scale
+  filter represented by $y_{R_{t}^{L}}$, $y_{R_{t}^{S}}$ and
   $y_{R_{s}}$.}
@@
 \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
-\cite{zhang2012robust}. The ECO and CCOT trackers \textit{YoungWoo : it should be "use" I think.}originally uses deep
+\cite{zhang2012robust}. The ECO and CCOT trackers originally use deep
 convolutional features, however, to perform fair comparison, we use
@@
 combination decreases run-time performance to 317 fps (=416fps - 99fps).
-\textit{YoungWoo : Should it not be 99fps.}
+\begin{comment}
+  \textit{YoungWoo : Should it not be 99fps. Burak: 317=416-99, isn't it?}
+\end{comment}
 
